### 2018-03-20 MS-new/1_Introduction.tex
first commit in shubhobm

\section{Introduction}
\label{Section:SP}

Consider a point $\bfx$ from some $\cX \subseteq \BR^p$, and the spatial sign function $\bfS : \cX \times \BR^p \rightarrow \BR^p$, defined as
%
$$
\bfS (\bfx; \bfmu_x) = \frac{\bfx - \bfmu_x}{\| \bfx - \bfmu_x \|}
\BI ( \bfx \ne \bfmu_x ),
$$
%
where $\bfmu_x \in \BR^p$ is a fixed location parameter, $\BI(\cdot)$ is the 0/1 indicator function and $\|.\|$ is the euclidean norm. This is a generalization of the real-valued case of the indicator for whether a point $x \in \BR$ is to the right, left or at a scalar $\mu_{x} \in \BR$, and was first introduced by \cite{MottonenOja95}. Given a data matrix $\bfX = (\bfx_{1}, \ldots, \bfx_{n})^T$, a popular approach of using spatial signs in the literature has been to take spatial signs of the data points, i.e. $\bfS(\bfx_i)$, and use the matrix of signs as a proxy of $\bfX$ to formulate robust versions of location and scale problems  \citep{locantore99, OjaBook10,WangPengLi15}.

The spatial sign maps all data points to the surface of a $p$-dimensional unit sphere (see Figure~\ref{fig:rankplot}). While this transformation has its advantages (i.e. robustness), e.g. the eigenvectors remain the same while limiting the influence of outliers when the points are drawn from an elliptical distribution \citep{taskinen12}, valuable information is lost in the form of magnitudes of sample points. As a result, spatial sign-based procedures suffer from low efficiency. For example, eigenvector estimates obtained from the covariance matrix of spatial sign, which is called the Sign Covariance Matrix (SCM), are asymptotically inadmissible \citep{magyar14}- in the sense that there is an estimator (namely, Tyler's M-estimate of scatter \citep{tyler87}) that has uniformly lower asymptotic risk than the SCM.

\paragraph{}
To utilize the magnitude information of sample points, at the same time preserving the robustness property, we propose a general class weighted spatial sign functions. To this end, we first propose what we call a {\it peripherality function}.

\begin{Definition}\label{defn:peripherality}
For a set of probability measures $\cM$ taking values in $\BR^p$, a {\it peripherality function} $ P : \BR^p \times \cM \rightarrow \BR^+ \cup \{ 0\}$,  is a function that satisfies the following condition:\\

\noindent {\bf (P)} For every probability measure $\BF \in \cM$, there exists a constant $\bfmu_{F} \in \BR^p$ such that for any $t \in [ 0, 1]$ and $\bfx \in \BR^p$,
%
$$ 
P ( \bfmu_{F} ; \BF ) \leq P ( \bfmu_{F} + t ( \bfx - \bfmu_{F} ); \BF ). 
$$ 
%
That is, for every fixed $\BF$, the peripherality function achieves a minimum at $\mu_{F}$, and is non-decreasing in every direction away from $\bfmu_{F}$.
\end{Definition}

The peripherality function quantifies the relative position of $\bfx$ with respect to $\bfmu_{F}$, and condition (P) formalizes a general notion of centrality. A whole class of such functions can be defined from {\it Data Depth} functions \citep{zuo00}, which give the center-outward ranking of points in a multivariate dataset. Data depth has seen extensive use in the past decade, ranging from robust nonparametric classification \citep{jornsten04, ghosh05, dutta12, sguera14} to parametric estimation of means \citep{ZuoCuiHe04}, covariance matrices \citep{ZuoCui05} and sparse multivariate regression coefficients \citep{DuttaGenton17,MajumdarChatterjeeStat}. Peripherality functions can be defined as some inverse ranking based on data depth, and the concept of {\it outlyingness} associated with data depth is essentially same as what we use in this paper. However, traditional depth functions require a wider array of theoretical conditions \citep{zuo00} in addition to our condition (P), and a sizeable portion of methods we discuss do not require the use of depth functions {\it per se} to be implemented. %We use the term {\it peripherality} to keep track of the difference in application contexts and technical assumptions. As an additional objective of this paper, we discuss  some properties and uses of data-depth in real, separable Hilbert spaces.

%For t for which some mathematical 
%preliminaries are necessary for easier exposition. Let $(\Omega, \cA, \alpha)$ 
%be a probability space, and let $\cB$ be the Borel $\sigma$-algebra generated 
%by the norm topology of $\cH$. A $\cH$-valued random variable is a mapping 
%$X :  \Omega \rightarrow \cH$ such that for every $B \in \cB$, $X^{-1} (B) \in \cA$. 
%It is easy to see that $\alpha_{x} = \alpha ( X^{-1} (\cdot ) )$ is a probability 
%measure on the measurable space $(\cH, \cB)$. Mathematical details about 
%such probability measures on Hilbert spaces are available from a number of 
%places, including
%\bredbf
%BLSP notes (my primary reference), Gross, Segal, and what not.
%\eredbf
%
%
%Let $\cM$ be a set of probability measures on $\cH$. 
% If 
%we impose the practical restriction that $\inf_{x} P ( x ; F )$ is finite and 
%bounded below, then we may as well impose without loss of generality 
%$P ( \mu_{F} ; F ) = 0$ and consequently $P ( x ; F ) \geq 0$ for all $x \in \cH$ 
%and  $F \in \cM$. In many cases of interest, $P ( \cdot; \cdot)$ is 
%uniformly bounded above as well.
% 
%We will impose additional conditions on this function 
%as we proceed, but it can be seem immediately that any distance measure between 
%$x$ and $\mu_{F}$ satisfies the bare minimum requirement mentioned above.

\begin{figure}[t]
	\captionsetup{singlelinecheck=off}
	\centering
		\includegraphics[height=6cm]{../Codes/ranks}
	\caption{(Left) 1000 points randomly drawn from $\mathcal N_2\left((0,0)^T, \left(\protect\begin{smallmatrix} 5 & -4 \\ -4 & 5 \protect\end{smallmatrix}\right)\right) $ and (Right) their signed peripherality functions based on halfspace depth}
	\label{fig:rankplot}
\end{figure}

Our weighted sign vector, which we call the {\it signed peripherality} function, is now defined as the product of the spatial sign and transformed peripherality functions:
%
\begin{align}\label{eqn:rank}
\bfR (\bfx; \bfmu_x, \BF) = \bfS(\bfx, \bfmu_x). \kappa_P( P(\bfx, \BF)),
\end{align}
%
where $\kappa_P: \BR \rightarrow \BR$ is a monotone function. Its purpose is to either downweight or upweight the spatial sign of a point based on its peripherality with respect to a data cloud. As seen in the third panel of Figure~\ref{fig:rankplot}, $\bfR (\bfx; \bfmu_x, \BF)$ maps points {\it inside} a ball of finite radius, thus limiting the influence of outlying points {\it and} preserving the magnitude information of data points. In this paper, we demonstrate certain interesting applications of this multivariate rank transformation in robust statistical inference. Notice that for the trivial choice $P( \bfx; \BF) = \| \bfx - \bfmu_{F} \|$ and $\bfmu_x = \bfmu_F, \kappa_P(x)=x$, we get $\bfR (\bfx; \bfmu_x, \BF) = \bfx$. However, in this paper we illustrate how using the rank-transformed data in place of the original data points or their spatial signs leads to interesting robustness results for other choices of the peripherality functions.

The notion of multivariate ranks goes back to \cite{PuriSenBook}, where they take the vector consisting of marginal univariate ranks as multivariate rank vector. Subsequent definitions of multivariate ranks were proposed by \cite{MottonenOja95,HallinPaindaveine02} and \cite{Chernozhukov14}. Compared to them, the advantages of our signed peripherality function are two-fold: interpretability and flexibility. Firstly, as evident in Figure~\ref{fig:rankplot}, our rank transformation preserves the general shape of the data. In fact, if the map $\| \bfx \| \mapsto P(\bfx, \BF)$ is one-one (given a fixed $\BF$), then it is possible to get back $\bfx$ from $\bfR (\bfx; \bfmu_x, \BF)$. It also provides an intuitive extension to any spatial sign-based methodology. Secondly, there is considerable scope of generalization within the present framework. Given any general inner product space, the definition of signed peripherality remains the same when euclidean norm is replaced by the norm induced by the inner product. Even within $\BR^p$, it is possible to generalize the ranking function in \eqref{eqn:rank} by adding separate transformations on the sign and peripherality functions to obtain alternate representations of the data in lower or higher dimensional spaces. However, we limit our discussion in this paper to the original formulation in \eqref{eqn:rank}.

In this paper, we assume $\BF$ to be an elliptical distribution. Following \cite{FangEtal90}, elliptical distributions can be formally defined here using their characteristic function:
%
\begin{Definition}
A $p$-dimensional random vector $\bfX$ is said to elliptically distributed if and only if there exist a vector $\bfmu \in \mathbb R^p$, a positive semi-definite matrix $\Omega \equiv \Sigma^{-1} \in \mathbb R^{p \times p}$ and a function $\phi: \mathbb R_+ \rightarrow \mathbb R$ such that the characteristic function $\bft \mapsto \phi_{\bfX - \bfmu} (\bft)$ of $\bfX - \bfmu$ corresponds to $\bft \mapsto \phi (\bft^T \Sigma \bft), \bft \in \mathbb R^p$.
\end{Definition}
%
\noindent The density function of an elliptically distributed random variable takes the form:
%
$$
h(\bfx; \bfmu, \Sigma) = |\Omega|^{1/2} g ((\bfx - \bfmu)^T \Omega (\bfx - \bfmu)),
$$
%
where $g$ is a non-negative scalar-valued density function that is continuous and strictly increasing, and is called the \textit{density generator} of the elliptical distribution. For ease of notation, we denote such a distribution by $\mathcal{E} (\bfmu, \Sigma, g)$.

%{\it signed-peripherality function} $\kappa (\cdot)$. We define this function 
%with three parameters $\mu_{x} \in \cH$, $F \in \cM$ and  
%$\mu_{y} \in \cH$,  argument $x \in \cH$ and range $\cH$. More precisely,
%we use two functions $\kappa_{s} : \cH \rightarrow \cH$, 
%$\kappa_{p} : \cH \rightarrow \cH$ that are respectively 
%composed with the sign transformation and the peripherality function, and 
%then multiplied together to obtain the function
%$\kappa : \cH \times \cH \times \cM \times \cH \times \cH \rightarrow \cH$ 
%defined as 
%\ban 
%\kappa (x; \mu_{x}, F, \mu_{y} ) = k_{s} (S (x; \mu_{x})) k_{p} (P (x; F)) + \mu_{y}. 
%\ean
%Within this very generic framework, we will explore two simple choices. We consider 
%$\kappa_{s} (x) = x$, thus this is fixed to be the identity transformation. The two 
%alternatives we consider for $\kappa_{p}$ are 
%$\kappa_{p} (x) = x$ and $\kappa_{p} (x) = \exp (- x)$, thus one is linearly 
%increasing with $x$ while the other is exponentially decreasing.
%
%
%Notice that if we consider $\mu_{y} = \mu_{F} = \mu_{x}$,  
%$\kappa_{s} (x) = \kappa_{p} (x) = x$, and take the very 
%simple peripherality  function $P( x; F) = || x - \mu_{F} ||$, we have 
%$\kappa (x; \mu_{x}, F, \mu_{y} ) \equiv x$ for all choices of parameters 
%$\mu_{x}, F, \mu_{y}$.  Consequently, under this choice of parameters for the 
%$\kappa$-transformation, analyzing a dataset $\{ X_{1}, \ldots, X_{n} \}$ and 
%its $\kappa$-transformed version 
%$\{ Y_{i} = \kappa (X_{i}; \ldots), \ i = 1, \ldots, n \}$ are equivalent. However,
%in this paper we illustrate how other choices of the peripherality function 
%lead to interesting robustness results. We have deliberately set the location 
%parameters $\mu_{x}, \mu_{F}, \mu_{y}$ to be potentially non-identical, this 
%additional flexibility has some advantage for robust data analysis. In many 
%applications, the value of these three parameters may be identical, which leads 
%to no conflict in our framework.

\paragraph{Organization of paper.}

\paragraph{Notation.}

### 2018-03-20 MS-new/2_Location.tex
first commit in shubhobm

\section{Weighted sign vectors in location problem}
\label{section:LocSection}
In this section, we focus on the general situation of estimating or testing for the location parameter $\bfmu \equiv \bfmu_F$ using the weighted sign vectors in \eqref{eqn:rank}. We impose the following very general conditions on the weights $w(\bfx, \BF) := \kappa_P(P(\bfx, \BF))$:

\vspace{1em}
\noindent{\bf (A1)} The weights are affine invariant, i.e.
%
$$
w(\bfA \bfx + \bfb, \bfA \BF + \bfb) = w(\bfx, \BF),
$$
%
for any $\bfb \in \BR^p$ and full rank matrix $\bfA \in \BR^{p \times p}$.

\noindent{\bf (A2)} Given a fixed $\BF$, the weights are square-integrable:
%
$$
\int [w(\bfy, \BF)]^2 d\BG(\bfy) < \infty; \BG \in \cM.
$$

\vspace{1em}
\noindent Because of the affine invariance, it is possible to simplify the weight as a function of the norm of $\bfz = \Sigma^{-1/2} (\bfX - \bfmu)$: $w(\bfx, \BF) = f(r)$, with $r = \| \bfz \|$.

A straightforward use of weighted signs in a location problem is to construct an outlier-robust alternative to the Hotelling's $T^2$ test using their sample mean vector and covariance matrix. Formally, this means testing for $H_0: \bfmu = {\bf 0}_p$ vs. $H_1:\bfmu \neq {\bf 0}_p$  based on the test statistic:
%
$$
T_{n,w} = n \bar\bfX_w^T ( \BV \BX_w)^{-1} \bar\bfX_w,
$$
%
({\colrbf define $\BX_w$}) with $\bar\bfX_w = \sum_{i=1}^n \bfX_{w,i}/n$ and $\bfX_{w,i} = w(\bfX_i ) \bfS (\bfX_i)$ for $i=1,2,...,n$. However, the following holds true for this weighted sign test:
%
\begin{Proposition}\label{proposition:SignTest}
Consider $n$ random variables $Z = (\bfZ_1,...,\bfZ_n)^T$ distributed independently and identically as $\mathcal{E}( \bfmu, k \bfI_p, g); k \in \mathbb R$, and the class of hypothesis tests defined above. Then, given any $\alpha \in (0,1)$, local power at $\bfmu \neq {\bf 0}_p$ for the level-$\alpha$ test  based on $T_{n,w}$ is maximum when $w(\bfZ_1) = c$, a constant independent of $\bfZ_1$.
\end{Proposition}
%
\noindent This essentially means that power-wise the (unweighted) spatial sign test \citep{OjaBook10} is optimal in the given class of hypothesis tests when the data comes from a spherically symmetric distribution. Our simulations show that this empirically holds for non-spherical but elliptic distributions as well.

\subsection{The weighted spatial median} 
To explore usage of weighted spatial signs in the location problem that improve upon the state-of-the-art, we concentrate on the following optimization problem:
%
\begin{equation}\label{eqn:WtSpMed}
\bfmu_w = \argmin_{\bfmu_0 \in \mathbb{R}^p} \BE ( w(\bfX) | \bfX - \bfmu_0 |).
\end{equation}
%
This can be seen as a generalization of the Fermat-Weber location problem (which has the spatial median \citep{brown83, Chaudhuri96} as the solution) using data-dependent weights. Using affine equivariant weights in \eqref{eqn:WtSpMed} ensures that the weights are independent of $\bfmu_0$, allowing the optimization problem to have a unique solution. We call this solution the \textit{weighted spatial median} of $\BF$, and denote it by $\bfmu_w$. In a sample setup it is estimated by iteratively solving the equation $\sum_{i=1}^n w(\bfX_i) \bfS (\bfX_i - \hat\bfmu_w)/n = {\bf 0}_p$.

The sample weighted spatial median $\hat\bfmu_w$ is a $\sqrt n$-consistent estimator of $\bfmu_w$, with the following result gives its asymptotic distribution:
%
\begin{Theorem}
Let $\bfA_w, \bfB_w$ be two matrices, dependent on the weight function $w$ such that
%
$$
\bfA_w = \BE \left[ \frac{w( \bfepsilon ) }{\| \bfepsilon \|} \left( 1 - \frac{\bfepsilon \bfepsilon^T}{\| \bfepsilon \|^2} \right) \right];
\quad
\bfB_w = \BE \left[ \frac{(w( \bfepsilon ))^2 \bfepsilon \bfepsilon^T}{\| \bfepsilon \|^2} \right]
$$
%
where $\bfepsilon \sim \mathcal E({\bf 0}, \Sigma, g)$. Then
%
\begin{equation}
\sqrt n (\hat\bfmu_w - \bfmu_w) \leadsto \cN_p ({\bf 0}, \bfA_w^{-1} \bfB_w \bfA_w^{-1})
\end{equation}
\end{Theorem}
%

%We provide a sketch of its proof in the supplementary material, which generalizes equivalent results for the spatial median \citep{OjaBook10}. 
Setting $w(\bfepsilon)=1$ above yields the asymptotic covariance matrix for the spatial median. Following this, the asymptotic relative efficiency (ARE) of $\bfmu_w$ corresponding to some non-uniform weight function with respect to the spatial median, say $\bfmu_s$ will be:
%
$$
ARE( \bfmu_w, \bfmu_s) = \left[ \frac{\text{det} (\bfA^{-1} \bfB \bfA^{-1})}{\text{det} ( \bfA_w^{-1} \bfB_w \bfA_w^{-1})} \right]^{1/p}
$$
%
with $\bfA = \BE [ 1/ \| \bfepsilon \| ( I_p - \bfepsilon \bfepsilon^T/ \| \bfepsilon \|^2 ) ]$ and $\bfB = \BE [ \bfepsilon \bfepsilon^T/ \| \bfepsilon \|^2 ]$. This is further simplified under spherical symmetry:

\begin{Corollary}
For the spherical distribution $\mathcal{E}(\bfmu, k \bfI_p, g); k \in \mathbb R, \bfmu \in \mathbb R^p$, we have
%
$$
ARE( \bfmu_w, \bfmu_s) = \frac{ \left[ \BE \left( \frac{f(r)}{r} \right) \right]^2}{\BE f^2(r) \left[ \BE \left( \frac{1}{r} \right) \right]^2 }
$$
\end{Corollary}
%
\begin{table}[t]
	\centering
    \begin{tabular}{c|ccccc}
    \hline
    & $t_3$   & $t_5$   & $t_{10}$  & $t_{20}$  & Normal \\ \hline
    $p=5$    & 1.28 & 1.20 & 1.16 & 1.14 & 1.13   \\
    $p=10$   & 1.15 & 1.10 & 1.07 & 1.07 & 1.06   \\
    $p=20$   & 1.09 & 1.05 & 1.04 & 1.03 & 1.03   \\
    $p=50$   & 1.05 & 1.02 & 1.01 & 1.01 & 1.01   \\ \hline
    \end{tabular}
    \caption{Table of $ARE(\bfmu_w; \bfmu_s)$ for different spherical distributions}
    \label{table:AREtablewsm}
\end{table}
%
Table \ref{table:AREtablewsm} summarizes the AREs for several families of elliptic distributions, numerically calculated using 10,000 random samples, and taking $f(r) = 1/(1+r)$. It is evident from the table that the weighted spatial median outperforms its unweighted counterpart for all data dimensions and distribution families. While the performance is much better for small values of $p$, weighting the signs seems to have less and less effect as $p$ grows larger. Assuming a first-order autoregressive (AR(1)) covariance structure, i.e. $\sigma_{ij} = \rho^{|i-j|}$ with $ \rho \in (0,1)$, results in largely similar ARE values as those obtained in table \ref{table:AREtablewsm} that assume $\Sigma = \bfI_p$.

\subsection{A high-dimensional test of location}

It is possible to take an alternative approach to the location testing problem by using the covariance-type U-statistic $C_{n,w} = \sum_{i=1}^n \sum_{j=1}^{i-1} \bfX_{w,i}^T \bfX_{w,j}$. This class of test statistics are especially attractive since they are readily generalized to cover high-dimensional situations, i.e. when $p > n$. The Chen and Qin (CQ) high-dimensional test of location for multivariate normal $\bfX_i$ \citep{ChenQin10} is a special case of this test that uses the statistic $C_n = \sum_{i=1}^n \sum_{j=1}^{i-1} \bfX_i^T \bfX_j$. The testing procedure of \cite{WangPengLi15} (from here on referred to as WPL test) shows that one can improve upon the power of the CQ test for non-gaussian elliptical distributions by using spatial signs $\bfS(\bfX_i)$ in place of the actual variables.

Under mild regularity conditions in the lines of \cite{WangPengLi15}, the following results hold for our generalized test statistic $C_{n,w}$ under $H_0$ as $n,p \rightarrow \infty$:
%
\begin{equation}\label{eqn:hdtest1}
\frac{C_{n,w}}{\sqrt{\frac{n(n-1)}{2} \text{Tr}(\bfB_w^2)}} \leadsto N(0,1),
\end{equation}
%
and under contiguous alternatives $H_1: \bfmu = \bfmu_0$,
%
\begin{equation}\label{eqn:hdtest2}
\frac{C_{n,w} - \frac{n(n-1)}{2} \bfmu_0^T \bfA_w^2 \bfmu_0 (1 + o(1)) }{\sqrt{\frac{n(n-1)}{2} \text{Tr}(\bfB_w^2)}} \leadsto N(0,1).
\end{equation}
%
We provide the details behind deriving these two results in the supplementary material, which extend the results of \cite{WangPengLi15} in a weightd sign setup using modified regularity conditions.

Following this, the ARE of this test statistic with respect to its unweighted version, i.e. the WPL statistic, is expressed as:
%
$$
ARE(C_{n,w}, \text{WPL}; \bfmu_0) = \frac{\bfmu_0^T \bfA_w^2 \bfmu_0}{\bfmu_0^T \bfA^2 \bfmu_0} \sqrt\frac{\text{Tr}(\bfB^2)}{\text{Tr}(\bfB_w^2)} (1 + o(1)),
$$
%
when $\Sigma = k \bfI_p$, this again simplifies to $\BE^2(f(r)/r)/[\BE f^2(r). \BE^2(1/r)]$. Thus the ARE values are exactly same as those in Table \ref{table:AREtablewsm}, indicating that for large data dimensions the WPL test and that based on $C_{n,w}$ are almost equivalent.

However, in a practical high-dimensional setup sample sizes are often small. Thus, comparing the the two tests with respect to their \textit{finite sample} efficiencies instead gives a better idea of their practical utility. We do so in table~\ref{table:AREtablehd}, which lists empirical powers calculated from 1000 replications of each setup under an AR(1) covariance structure (with $\rho = 0.8$). While under $H_0: \bfmu = {\bf 0}_p$ all tests have similar performance, $C_{n,w}$ beats the other two under deviations from the null.

\begin{table}
\centering
    \begin{tabular}{cc|ccc}\hline
\multicolumn{5}{l}{$\bfmu = \text{rep}(.15,p)$}\\\hline 
 $p$  & $n$    & CQ   & WPL  & $C_{n,w}$ \\\hline 
  500 & 20 & 0.051 & 0.376 & 0.418 \\
  500 & 50 & 0.060 & 0.832 & 0.866 \\
 1000 & 20 & 0.044 & 0.541 & 0.584 \\
 1000 & 50 & 0.039 & 0.973 & 0.987 \\\hline
\multicolumn{5}{l}{$\bfmu = \text{rep}(0,p)$}\\\hline
 $p$  & $n$    & CQ   & WPL  & $C_{n,w}$ \\\hline 
  500 & 20 & 0.049 & 0.061 & 0.063 \\
  500 & 50 & 0.039 & 0.061 & 0.064 \\
 1000 & 20 & 0.042 & 0.060 & 0.063 \\
 1000 & 50 & 0.043 & 0.050 & 0.050 \\\hline
    \end{tabular}
    \caption{Table of empirical powers of level-0.05 tests for the Chen and Qin (CQ), WPL and $C_{n,w}$ statistics}
    \label{table:AREtablehd}
\end{table}

### 2018-03-20 MS-new/3_Scale.tex
first commit in shubhobm

\section{Inverse depth and estimation of scatter}
\label{section:dcmSection}
We elaborate on the problem estimating the covariance matrix $\Sigma$ and its eigenvectors and eigenvalues using signed peripherality functions in this section. In addition to conditions (P) and (A1), we assume the following conditions on these functions in this section:

\vspace{1em}
\noindent\textbf{(B1)} The following holds:
$$
P(\bfx; \BF) \leq P(\bfmu_F + t(\bfx - \bfmu_F), \BF),
$$
%
for any $\bfx \in \BR^p$ and $t \in (0,1)$.

\noindent\textbf{(B2)} There exists a positive constant $M(P,\BF) $ such that $P(\bfx; \BF) \rightarrow M(P,\BF)$ as $\|\bfx\| \rightarrow \infty $.
\vspace{1em}

Condition (A2) in Section~\ref{section:LocSection} is now replaced by the stronger condition (B2). Note that all the current conditions are essentially the opposite of those imposed on a traditional depth function \citep{zuo00}. Given a depth function, the peripherality functions in this section can be defined as a bounded monotonically decreasing function of it. Consequently, we use the term {\it inverse depth function} in place of peripherality functions in this section, denoting them by $D^-(\bfx,\BF)$, or equivalently $D^-_\bfX(\bfx)$.

Given an inverse depth function $D^-_{\bfX}(\bfx)$ we transform the original random variable as: $\tilde \bfX = D^-_\bfX(\bfx) \bfS(\bfx - \bfmu)$. We attempt to use these vector as the proxy of original data for improved estimation of the components of the population covariance matrix $\Sigma$ in this section. To this end, in Section~\ref{subsec:dcm} we give some results characterizing the population covariance matrix of these vectors, i.e. $\BV \tilde \bfX$, and its affine equivariant counterpart.

%Data depth is as much a property of a vector-valued random variable $\bfX \in \mathbb{R}^p$ as it is of the underlying distribution $F$, so for ease of notation while working with transformed random variables, from now on we shall be using $D_\bfX(\bfx) = D(\bfx, F)$ to denote the depth of a point $\bfx$. Now, given a depth function $D_{\bfX}(\bfx)$ (equivalently, an htped function $D^-_\bfX(\bfx) = D^-(\bfx, F)$), transform the original random variable as: $\tilde \bfx = \tilde D_\bfX(\bfx) \bfS(\bfx - \bfmu)$, $\bfS(.)$ being the spatial sign functional. The transformed random variable $\tilde \bfX$ can be seen as the multivariate rank corresponding to $\bfX$ (e.g. \cite{serfling2006}).

%Figure \ref{fig:rankplot} gives an idea of how the multivariate rank vector $\tilde \bfX$ is distributed when $\bfX$ has a bivariate normal distribution. Compared to the spatial sign, which are distributed on the surface of $p$-dimensional unit ball centered at $\bfmu$, these spatial ranks have the same direction as original data and reside \textit{inside} the $p$-dimensional ball around $\bfmu$ that has radius $M_D(F)$ (which, for the case of halfspace depth, equals 0.5).

\subsection{Depth Covariance Matrix}
\label{subsec:dcm}
Consider the spectral decomposition of $\Sigma$: $\Sigma = \Gamma\Lambda\Gamma^T$, $\Gamma$ being orthogonal and $\Lambda$ diagonal with positive diagonal elements $\lambda_1, \ldots, \lambda_p$. Also normalize the original random variable as $\bfZ = \Gamma^T\Lambda^{-1/2} (\bfX - \bfmu)$. In this setup, we can represent the transformed random variable as
%
\begin{eqnarray}
\tilde \bfX &=& D^-_{\bfX} (\bfX) \bfS(\bfx - \bfmu) \notag \\
&=& D^-_{\Gamma\Lambda^{1/2}\bfZ + \bfmu} (\Gamma\Lambda^{1/2} \bfZ + \bfmu). \bfS(\Gamma\Lambda^{1/2} \bfZ) \notag \\
&=& \Gamma D^-_{\bfZ}(\bfZ) \bfS(\Lambda^{1/2}\bfZ) \notag \\
&=& \Gamma \Lambda^{1/2} D^-_{\bfZ}(\bfZ) \bfS(\bfZ) \frac{\| \bfZ \|}{\|\Lambda^{1/2} \bfZ \|}.
\label{equation:rankdecomp}
\end{eqnarray}
%
%Because of affine (thus rotational) invariance of a depth function, the depth (htped) value at $\bfz$ does not depend on the direction of $\bfz$, i.e. $D^-_{\bfZ}(\bfz)$ and $\bfS(\bfz)$ are independent. Furthermore,
%$$ Cov \left(\bfS (\bfz), \frac{\| \bfz \|}{\|\Lambda^{1/2} \bfz\|} \right) = E \left(\bfS (\bfz). \frac{\| \bfz \|}{\|\Lambda^{1/2} \bfz\|} \right) - E \bfS (\bfz) E \left(\frac{\| \bfz \|}{\|\Lambda^{1/2} \bfz\|} \right) = E \left( \frac{\bfz}{\|\Lambda^{1/2} \bfz\|} \right) = \bf0$$
%both $\bfS (\bfz)$ and $\bfz / \| \Lambda^{1/2}\bfz \|$ are odd functions of $\bfz$, which has a circularly symmetric distribution, hence each of them has expectation $\bf0$. Consequently, we obtain an expression for the covariance matrix of $\tilde \bfX$:

$D^-_\bfZ(\cdot)$ is an even function in its argument because of affine invariance, as is $\| \bfz \| / \|\Lambda^{1/2} \bfz \|$. Since the sign function $\bfS(\cdot)$ is odd in its argument, it follows that $\BE \tilde \bfX = \bf0$. Consequently, we obtain an expression for $\BV \tilde \bfX$, which we call the {\it Depth Covariance Matrix} (DCM):

\begin{Theorem} \label{Theorem:covform}
Let the random variable $\bfX \in \mathbb{R}^p$ follow an elliptical distribution with center $\bfmu$ and covariance matrix $\Sigma = \Gamma\Lambda\Gamma^T$, its spectral decomposition. Then, given a depth function $D_\bfX(.)$ the covariance matrix of the transformed random variable $\tilde\bfX$ is
\begin{equation} \label{equation:covformEq1}
\BV \tilde \bfX) = \Gamma \Lambda_{D} \Gamma^T,\quad\mbox{with}\quad \Lambda_{D} = \mathbb E_\bfZ \left[ (D^-_\bfZ(\bfz))^2 \frac{\Lambda^{1/2} \bfz \bfz^T \Lambda^{1/2}}{\bfz^T \Lambda \bfz} \right],
\end{equation}
where $\bfZ = (Z_1,...,Z_p)^T \sim N({\bf 0}, \bfI_p)$, so that $\Lambda_{D}$ a diagonal matrix with diagonal entries
%
$$
\lambda_{D,i} = \mathbb E_\bfZ \left[ \frac{(D^-_\bfZ(\bfz))^2 \lambda_i z_i^2}{\sum_{j=1}^p \lambda_j z_j^2} \right].
$$
\end{Theorem}

The matrix of eigenvectors $\Gamma$ remains unchanged in the transformation $\bfX \rightarrow \tilde \bfX$. As a result, the multivariate rank vectors can be used for robust principal component analysis, which we are going to discuss shortly. However, as one can see in the above expression, the diagonal entries of $\Lambda_{D}$ do not change if a scale change is done on all entries of $\Lambda$, meaning the $\Lambda_{D}$ matrices corresponding to $\BF$ and $c \BF$ for some $c \neq 0$ will be same. This is the reason the DCM is not equivariant under affine transformations.

We need to follow the general framework of M-estimation with data-dependent weights \citep{HuberBook81} to construct an affine equivariant counterpart of the DCM. Specifically, we implicitly define the Affine-equivariant Depth Covariance Matrix (ADCM) as
%
\begin{equation} \label{eqn:ADCM}
\Sigma_{Dw} = \frac{1}{ \BV \tilde Z_1 } \BE_\bfX \left[ \frac{(D^-_\bfX(\bfx))^2 (\bfx - \bfmu) (\bfx - \bfmu)^T}{(\bfx - \bfmu)^T \Sigma_{Dw}^{-1} (\bfx - \bfmu)} \right].
\end{equation}
%
Its affine equivariance follows from the fact that the weights $(D^-_\bfX (\bfx))^2$ depend only on the standardized quantities $\bfz \sim \cE ({\bf 0}, k \bfI_p, g)$. We solve (\ref{eqn:ADCM}) iteratively by obtaining a sequence of positive definite matrices $\Sigma^{(k)}_{Dw}$ until convergence:
%
$$
\Sigma^{(k+1)}_{Dw} = \frac{1}{\BV \tilde Z_1 } \BE_\bfX \left[ \frac{(D^-_\bfX(\bfx))^2 (\Sigma^{(k)}_{Dw})^{1/2} (\bfx - \bfmu) (\bfx - \bfmu)^T (\Sigma^{(k)}_{Dw})^{1/2}}{(\bfx - \bfmu)^T (\Sigma^{(k)}_{Dw})^{-1} (\bfx - \bfmu)} \right].
$$
%

To ensure existence and uniqueness of this estimator, let us consider the class of scatter estimators $\Sigma_M$ that are obtained as solutions of the following equation:
%
\begin{equation}
E_{\bfZ_M} \left[ u( \| \bfz_M \| )  \frac{\bfz_M \bfz_M^T}{\| \bfz_M \|^2}  - v( \| \bfz_M \| ) I_p \right] = 0
\end{equation}
%
with $\bfz_M = \Sigma_M^{-1/2} (\bfx - \bfmu)$. Under the following assumptions on the scalar valued functions $u$ and $v$, the above equation produces a unique solution \citep{HuberBook81}:
%

\vspace{1em}
\noindent\textbf{(M1)} The function $u(r)/r^2$ is monotone decreasing, and $u(r)>0$ for $r>0$;

\noindent\textbf{(M2)}  The function $v(r)$ is monotone decreasing, and $v(r)>0$ for $r>0$;

\noindent\textbf{(M3)} Both $u(r)$ and $v(r)$ are bounded and continuous;

\noindent\textbf{(M4)} $u(0) / v(0) < p$;

\noindent\textbf{(M5)} For any hyperplane in the sample space $\mathcal X$, (i) $P(H) = E_\bfX 1_{\bfx \in H} < 1 - p v(\infty) / u(\infty)$ and (ii) $P(H) \leq 1/p$.
%

\vspace{1em}
\noindent In our case we take $v(r) = Var(\tilde Z_1)$, i.e. a constant, thus (M2) and (M3) are trivially satisfied. As for $u$, we notice that most well-known depth functions can be expressed as simple functions of the norm of the standardized random variable. For example, $PD_\bfZ (\bfz) = (1 - G(\| \bfz \|); MhD_\bfZ (\bfz) = (1+\| \bfz \|^2)^{-1}; HSD_\bfZ (\bfz) = (1+\| \bfz \|)^{-1}$ etc., so that we can take as $u$ square of the corresponding peripherality functions:
% Var(Z1) breaks into two independent parts: depth and sign. So can check m4 and M5 here itself.
$$
u_{PD} (r) = G^2 (r); \quad u_{MhD}(r)  = \frac{r^4}{(1 + r^2)^2}; \quad u_{HSD}(r)  = \frac{r^2}{(1 + r/G^{-1}(0.75))^2}
$$
%

It is easy to verify that the above choices of $u$ satisfy (M1) and (M3). To check (M4) and (M5), first notice that $\bfZ$ has a spherically symmetric distribution, so that its norm and sign are independent. Since $D_\bfZ(\bfz)$ depends only on $\| \bfz \|$, we have
%
$$
Var (\tilde Z_1) = Var \left( D^-_\bfZ (\bfZ) \frac{Z_1}{ \|\bfZ \|} \right) = Var (D^-_\bfZ (\bfZ)) Var (S_1 (\bfZ)) = \frac{1}{p} Var (D^-_\bfZ (\bfZ))
$$
%
as $Cov(\bfS(\bfZ)) = Cov((S_1(\bfZ), S_2(\bfZ), ..., S_p(\bfZ))^T) = I_p/p$. Now for MhD and HSD $u(\infty)=1, u(0)=0$, so (M4) and (M5) are immediate. To achieve this for PD, we only need to replace $u_{PD}(r)$ with $u_{PD}^*(r) = G^2(r) - 1/4$.

\subsection{Calculating the sample DCM and ADCM}
Let us now consider $n$ iid random draws from our elliptic distribution $F$, say $\bfX_1,...,\bfX_n$. For ease of notation, denote $SS(\bfx; \bfmu) = \bfS(\bfx - \bfmu) \bfS(\bfx - \bfmu)^T$. Then, given the depth function and known location center $\bfmu$, one can show that the vectorized form of $\sqrt n$-times the sample DCM: $\sum_{i=1}^n (D^-_\bfX(\bfx_i))^2SS(\bfx_i; \bfmu) /\sqrt{n}$  has an asymptotic multivariate normal distribution with mean $\sqrt n.vec(E[( (D^-_\bfX (\bfX))^2 SS(\bfx; \bfmu)])$ and a certain covariance matrix by straightforward application of the central limit theorem (CLT). But in practice the population depth function $D_\bfX(\bfx) = D(\bfx, F)$ is estimated by the depth function based on the empirical distribution function, $F_n$. Denote this sample depth by $D^n_\bfX (\bfx) = D(\bfx, F_n)$. Here we make the following assumption regarding how it approximates $D_\bfX(\bfx)$:

\vspace{1em}
\noindent\textbf{(D5)} \textit{Uniform convergence}: $\sup_{\bfx \in \mathbb R^p} | D^n_\bfX (\bfx) - D_\bfX (\bfx) | \rightarrow 0$ as $n \rightarrow \infty $.
\vspace{1em}

The assumption that empirical depths converge uniformly at all points $\bfx$ to their population versions holds under very mild conditions for several well known depth functions: for example projection depth \citep{zuo03} and simplicial depth \citep{Dumbgen92}. One also needs to replace the known location parameter $\bfmu$ by some estimator $\hat\bfmu_n$. Examples of robust estimators of location that are relevant here include the spatial median \citep{haldane48,brown83}, Oja median \citep{oja83}, projection median \citep{zuo03} etc. Now, given $D^n_\bfX(.)$ and $\hat \bfmu_n$, to plug them into the sample DCM and still go through with the CLT we need the following result:

\begin{Lemma} \label{Lemma:lemma1}
Consider a random variable $\bfX \in \mathbb{R}^p$ having a continuous and symmetric distribution with location center $\bfmu$ such that $E\|\bfx - \bfmu \|^{-3/2} < \infty$. Given $n$ random samples from this distribution, suppose $\hat\bfmu_n$ is an estimator of $\bfmu$ so that $\sqrt n (\hat\bfmu_n - \bfmu) = O_P(1) $. Then with the above notations, and given the assumption (D5) we have
%
$$ \sqrt n \left[
\frac{1}{n} \sum_{i=1}^n (D^{-n}_\bfX (\bfx_i))^2 SS(\bfx_i; \hat\bfmu_n) -
\frac{1}{n} \sum_{i=1}^n (D^-_\bfX (\bfx_i))^2 SS(\bfx_i; \bfmu) \right]
\stackrel{P}{\rightarrow} 0 $$
\end{Lemma}

Following this, we are now in a position to state the result for consistency of the sample DCM:

\begin{Theorem} \label{Theorem:rootn}
Consider $n$ iid samples from the distribution in Lemma \ref{Lemma:lemma1}. Then, given a depth function $D_\bfX(.)$ and an estimate of center $\hat\bfmu_n$ so that $\sqrt n(\hat \bfmu_n - \bfmu) = O_P(1)$,
%
$$ \sqrt n \left[ vec\left\{ \frac{1}{n} \sum_{i=1}^n (D^{-n}_\bfX (\bfx_i))^2 SS(\bfx_i; \hat\bfmu_n) \right\} - E \left[ vec\left\{ (D^-_\bfX (\bfx))^2 SS(\bfx; \bfmu) \right\} \right] \right]
\stackrel{D}{\rightarrow}
N_{p^2} ({\bf 0}, V_{D,S}(F)) $$
$$ \text{with } V_{D,S}(F) = Var \left[vec \left\{ (D^-_\bfX (\bfx))^2 SS(\bfx; \bfmu) \right\} \right] $$
\end{Theorem}

\noindent In case $F$ is elliptical, an elaborate form of the covariance matrix $V_{D,S}(F)$ explicitly specifying each of its elements (more directly those of its $\Gamma^T$-rotated version) can be obtained, which is given in Appendix \ref{section:appA}. This form is useful when deriving limiting distributions of eigenvectors and eigenvalues of the sample DCM.

In contrast to the DCM, the issue of estimating $\bfmu$ to plug into the ADCM is easily handled by simultaneously solving for the location and scatter functionals ($\bfmu_{Dw}, \Sigma_{Dw}$):
%
\begin{eqnarray}
E \left[ \frac{\Sigma_{Dw}^{-1/2} (\bfx - \bfmu_{Dw})}{ \| \Sigma_{Dw}^{-1/2}(\bfx - \bfmu_{Dw}) \|} \right] &=& {\bf 0}_p \label{eqn:AffineMedian}\\
E \left[ \frac{(D^-_\bfX(\bfx))^2 \Sigma_{Dw}^{-1/2} (\bfx - \bfmu_{Dw}) (\bfx - \bfmu_{Dw})^T \Sigma_{Dw}^{-1/2}}{(\bfx - \bfmu_{Dw})^T \Sigma_{Dw}^{-1} (\bfx - \bfmu_{Dw})} \right] &=& Var (\tilde Z_1) I_p \label{eqn:AffineCov}
\end{eqnarray}
%
In the framework of (\ref{eqn:ADCM}), for any fixed $\Sigma_M$ there exists a unique and fixed solution of the location problem $E_{\bfZ_M} (w(\| \bfz_M \| \bfz_M) = {\bf 0}_p $ under the following condition:

\vspace{1em}
\noindent\textbf{(M6)} The function $w(r)r$ is monotone increasing for $r>0$.

\vspace{1em}
\noindent This condition is easy to verify for our choice of the weights: $w(\| \bfz_M \| ) = D^-_{\bfZ_M} (\bfz_M) / \| \bfz_M \|$. Uniqueness of simultaneous fixed point solutions of \ref{eqn:AffineMedian} and \ref{eqn:AffineCov} is guaranteed when $\bfX$ has a symmetric distribution \citep{HuberBook81}.

In practice it is difficult to calculate the scale multiple $Var (\tilde Z_1)$ analytically for known depth functions and an arbitrary $F$. Here we instead obtain its standardized version $\Sigma_{Dw}^* = \Sigma_{Dw} / Var(\tilde Z_1)$ (so that the determinant equals 1), alongwith $\bfmu_{Dw}$ using the following iterative algorithm:

\begin{enumerate}
\item Start from some initial estimates $(\bfmu_{Dw}^{(0)}, \Sigma_{Dw,(0)})$. Set $t=0$;

\item Calculate the standardized observations $\bfz_i^{(t)} = \Sigma_{Dw,(t)}^{-1/2} (\bfx_i - \bfmu_{Dw}^{(t)})$;

\item Update the location estimate:
%
$$
\bfmu_{Dw}^{(t+1)} = \frac{\sum_{i=1}^n \tilde \bfx_i / \| \bfz_i^{(t)} \| }{\sum_{i=1}^n 1 / \| \bfz_i^{(t)} \|}
$$
%
\item Update the scatter estimate:
%
$$
\Sigma_{Dw}^{*(t+1)} = \frac{1}{n} \sum_{i=1}^n \frac{(D^{-n}_\bfX (\bfx_i))^2 (\bfx_i - \bfmu_{Dw}^{(t+1)})(\bfx_i - \bfmu_{Dw}^{(t+1)})^T}{\| \bfz_i^{(t)} \|^2}; \quad \Sigma_{Dw}^{*(t+1)} \leftarrow \frac{\Sigma_{Dw}^{*(t+1)}}{\text{det} (\Sigma_{Dw}^{*(t+1)})^{1/p}}
$$
%
\item Continue until convergence.
\end{enumerate}

\subsection{Robust PCA using eigenvectors}

Since we are mainly interested in using the DCM for robust principal components analysis, from now on we assume that the eigenvalues of $\Sigma$ are distinct: $\lambda_1 > \lambda_2 > ... > \lambda_p$ to obtain asymptotic distributions of its eigenvectors. In case any of the eigenvalues have multiplicity larger than 1, limiting distributions of the corresponding eigenprojection matrices can be obtained analogous to those of the sign covariance matrix \citep{magyar14}.

\subsubsection{Influence functions}
We start with deriving the influence functions for eigenvectors of the DCM and ADCM. This will help in demonstrating the robustness of their estimates, as well as deriving the asymptotic distributions of their sample counterparts. Influence functions of the DCM as well as its eigenvectors and eigenvalues, which are essential to understand how much influence a sample point, especially an infinitesimal contamination, has on any functional on the distribution \citep{HampelBook86}. Given any probability distribution $F$, the influence function of any point $\bfx_0$ in the sample space $\mathcal{X}$ for some functional $T(F)$ on the distribution is defined as
%
$$ IF(\bfx_0; T,F) = \lim_{\epsilon \rightarrow 0} \frac{1}{\epsilon} (T(F_\epsilon) - T(F)) $$
%
where $F_\epsilon$ is $F$ with an additional mass of $\epsilon$ at $\bfx_0$, i.e. $F_\epsilon = (1-\epsilon)F + \epsilon \Delta_{\bfx_0}$; $\Delta_{\bfx_0}$ being the distribution with point mass at $\bfx_0$. When $T(F) = E_F g$ for some $F$-integrable function $g$, $IF(\bfx_0; T,F) = g(\bfx_0) - T(F)$. It now follows that for the DCM,
%
$$ IF(\bfx_0; Cov(\tilde \bfX), F) = (D^-_\bfX(\bfx_0))^2 SS(\bfx_0; \bfmu) - Cov(\tilde \bfX) $$

Following \cite{croux00}, we now get the influence function of the $i^\text{th}$ eigenvector of $Cov(\tilde\bfX)$, say $\bfgamma_D = (\bfgamma_{D,1},...,\bfgamma_{D,p}); i = 1,...,p$:
%
\begin{eqnarray}
IF(\bfx_0; \bfgamma_{D,i}, F) &=& \sum_{k=1; k \neq i}^p \frac{1}{\lambda_{D,S,i} - \lambda_{D,S,k}} \left\{ \bfgamma^T_k IF(\bfx_0; Cov(\tilde \bfX), \bfgamma_i) \right\} \bfgamma_k \notag \\
&=& \sum_{k=1; k \neq i}^p \frac{1}{\lambda_{D,S,i} - \lambda_{D,S,k}} \left\{ \bfgamma^T_k (D^-_\bfX(\bfx_0))^2 SS(\bfx_0; \bfmu)\bfgamma_i - \lambda_{D,S,i}\bfgamma_k^T\bfgamma_i \right\} \bfgamma_k \notag \\
&=& \sum_{k=1; k \neq i}^p \frac{\sqrt{\lambda_i \lambda_k} z_{0i} z_{0k}}{\lambda_{D,S,i} - \lambda_{D,S,k}}. \frac{(D^-_\bfZ(\bfz_0))^2 }{\bfz_0^T \Lambda \bfz_0} \bfgamma_k
\end{eqnarray}
%
where $\Gamma^T \Lambda^{-1/2} (\bfx_0 - \bfmu) = \bfz_0 = (z_{01},...,z_{0p})^T$. Clearly this influence function will be bounded, which indicates good robustness properties of principal components.

For the ADCM, we first notice that the influence function of any affine equivariant estimate of scatter can be expressed as
%
$$
IF(\bfx_0, C, F) = \alpha_C (\| \bfz_0 \| ) \frac{\bfz_0 \bfz_0^T}{\bfz_0^T \bfz_0} - \beta_C( \| \bfz_0 \| ) C
$$
%
for scalar valued functions $\alpha_C, \beta_C$ \citep{HampelBook86}. Following this, the influence function of an eigenvector $\bfgamma_{C,i}$ of $C$ is derived:
%
$$
IF(\bfx_0, \bfgamma_{C,i}, F) = \alpha_C(\| \bfz_0 \|) \sum_{k=1, k \neq i}^p \frac{\sqrt {\lambda_i \lambda_k}}{\lambda_i - \lambda_k}. \frac{z_{0i} z_{0k}}{\bfz_0^T \bfz_0} \bfgamma_k
$$
%
When $C=\Sigma_M$, i.e. the solution to (\ref{eqn:ADCM}), then \cite{HuberBook81} shows that
%
$$
\alpha_C (\| \bfz_0 \|) = \frac{p(p+2) u (\| \bfz_0 \|)}{E_{F_0} \left[ p u(\| \bfy \| ) + u'(\| \bfy \|) \| \bfy \| \right] }
$$
%
Setting $u( \| \bfz_0 \|) = ( D^-_\bfZ (\bfz_0))^2$ ensures that the influence function of eigenvectors of the ADCM is bounded as well as increasing in magnitude with $\| \bfz_0 \|$.

\begin{figure}[]
	\centering
		\includegraphics[width=12cm]{../Codes/IFnorm.png}
	\caption{Plot of the norm of influence function for first eigenvector of (a) sample covariance matrix, (b) SCM, (c) Tyler's scatter matrix and DCMs for (d) Halfspace depth, (e) Mahalanobis depth, (f) Projection depth for a bivariate normal distribution with $\bfmu = {\bf 0}, \Sigma = \diag(2,1)$}
	\label{fig:IFnorm}
\end{figure}

In Figure \ref{fig:IFnorm} we consider first eigenvectors of our scatter estimates, as well as teo well-known robust estimates of scatter: the Sign Covariance Matrix (SCM) and Tyler's shape matrix, for the $\mathcal{N}_2((0,0)^T, \diag(2,1))$ and plot norms of these influence functions for different values of $\bfx_0$. Influence function for the $i^\text{th}$ eigenvectors of these two matrices (say $\bfgamma_{S,i}$ and $\bfgamma_{T,i}$, respectively) are as follows:
%
\begin{eqnarray*}
\quad IF(\bfx_0; \bfgamma_{S,i}, F) &=& \sum_{k=1; k \neq i}^p \frac{\sqrt{\lambda_i \lambda_k}}{\lambda_{S,i} - \lambda_{S,k}}. \frac{z_{0i} z_{0k}}{\bfz_0^T \Lambda \bfz_0} \bfgamma_k, \text{ with } \lambda_{S,i} = E_\bfZ \left( \frac{\lambda_i z_i^2}{\sum_{j=1}^p \lambda_j z_j^2} \right) \quad \\
IF(\bfx_0; \bfgamma_{T,i}, F) &=& (p+2) \sum_{k=1; k \neq i}^p \frac{\sqrt{\lambda_i \lambda_k}}{\lambda_i - \lambda_k}. \frac{z_{0i} z_{0k}}{\bfz_0^T \bfz_0} \bfgamma_k \quad 
\end{eqnarray*}
%
Their corresponding plots demonstrate the 'inlier effect', i.e. points close to symmetry center and the center itself having high influence, which results in loss of efficiency. The influence function for the sample covariance matrix is obtained by replacing $(p+2)$ by $\| \bfz_0 \|^2$ in the expression of $IF(\bfx_0; \bfgamma_{T,i}, F)$ above, hence is unbounded and the corresponding eigenvector estimators are not robust. In comparison, all three DCMs considered here have a bounded influence function as well as small values of the influence function at 'deep' points.

\subsubsection{Asymptotic and finite-sample efficiencies}

%Unlike affine equivariant estimators of shape, the Asymptotic Relative Efficiency (ARE) of eigenvectors (with respect to any other affine equivariant estimator) can not be simplified as a ratio of two scalar quantities dependent on only the distribution of $\| \bfz \|$ (e.g. \cite{taskinen12,ollilia03}).
Suppose $\hat C$ is a $\sqrt n$-consistent estimator of a scatter functional $C$. Then the asymptotic variance of its eigenvectors are \cite{anderson}
%
\begin{equation} \label{equation:covevEq}
AVar(\sqrt n\hat \bfgamma_{c,i}) = \sum_{k=1; k \neq i}^p \frac{\lambda_i \lambda_k}{(\lambda_i - \lambda_k)^2} \bfgamma_k \bfgamma_k^T
\end{equation}
%
The asymptotic relative efficiencies of eigenvectors from the sample DCM with respect to the sample covariance matrix can now be derived using (\ref{equation:covevEq}) above and (\ref{equation:DevEq}) from Corollary \ref{Corollary:eigendist}:
%
\begin{eqnarray*}
ARE(\hat\bfgamma^D_i, \hat\bfgamma_i; F) &=& \frac{\Tr( AVar(\sqrt n\hat \bfgamma_i))}{\Tr( AVar(\sqrt n\hat \bfgamma^D_i))}\\
&=& \left[\sum_{k=1; k \neq i}^p \frac{\lambda_i \lambda_k}{(\lambda_i - \lambda_k)^2} \right] \left[ \sum_{k=1; k \neq i}^p \frac{\lambda_i \lambda_k }{(\lambda_{D,s,i} - \lambda_{D,S,k})^2} E \left( \frac{(D^-_\bfZ (\bfz))^4 z_i^2 z_k^2}{(\bfz^T \Lambda \bfz)^2} \right) \right]^{-1}
\end{eqnarray*}

Obtaining ARE of the ADCM is, in comparison to DCM, more straightforward. The asymptotic covariance matrix of an eigenvector of the affine equivariant scatter functional $C$ is given by:
%
$$
AVar (\sqrt n  \hat\bfgamma_{C,j}) = ASV (C_{12}, F_0) \sum_{k=1, k \neq i}^p \frac{\lambda_i \lambda_k}{\lambda_i - \lambda_k}. \bfgamma_i \bfgamma_k^T
$$
%
where $ASV (C_{12}, F_0)$ is the asymptotic variance of an off-diagonal element of $C$ when the underlying distribution is $F_0$. Following \cite{croux00} this equals
%
$$
ASV (C_{12}, F_0) = E_{F_0} \left[ \alpha_c (\| \bfz \|)^2 (S_1(\bfz)S_2 (\bfz))^2 \right] = E_{F_0} \alpha_C (\| \bfz \|)^2 . E_{F_0} (S_1(\bfz)S_2 (\bfz))^2 
$$
% 
again using the fact that $\|\bfZ\|$ and $\bfS(\bfZ)$ are independent with $\bfZ \sim F_0$. It now follows that
%
\begin{equation}
ARE (\hat\bfgamma_{\Sigma_M,i}, \hat\bfgamma_{Cov,i}; F) = \frac{E_{F_0} \alpha_{Cov} (\| \bfz \|)^2}{E_{F_0} \alpha_C (\| \bfz \|)^2} = \frac{E_{F_0} \| \bfz \|^4. \left[ E_{F_0} ( p u \| \bfz\| + u'( \| \bfz \|) \| \bfz \| ) \right]^2}{E_{F_0} (u(\| \bfz \|))^2}
\end{equation}
%

Table \ref{table:AREtable} considers 6 different elliptic distributions (namely, bivariate $t$ with df = 5, 6, 10, 15, 25 and bivariate normal) and summarizes ARE for first eigenvectors for ADCMs corresponding to projection depth (PD-ACM) and halfspace depth (HSD-ACM). Due to difficulty of analytically obtain the AREs, we calculate them using Monte-Carlo simulation of $10^6$ samples and subsequent numerical integration. The ADCM seems to be particularly efficient in lower dimensions for distributions with heavier tails ($t_5$ and $t_6$), while for distributions with lighter tails, the AREs increase with data dimension. At higher values of $p$ the ADCM is almost as efficient as the sample covarnace matrix when the data comes from multivariate normal distribution.

\begin{table}[t]
\centering
    \begin{tabular}{c|cccc|cccc}
    \hline
    & \multicolumn{4}{c|}{PD-ACM} & \multicolumn{4}{c}{HSD-ACM} \\\cline{2-9}
    Distribution & $p=2$  & $p=5$  & $p=10$ & $p=20$ & $p=2$  & $p=5$  & $p=10$ & $p=20$ \\ \hline
    $t_5$           & 4.73 & 3.99 & 3.46 & 3.26 & 4.18 & 3.63 & 3.36 & 3.15 \\
    $t_6$           & 2.97 & 3.28 & 2.49 & 2.36 & 2.59 & 2.45 & 2.37 & 2.32 \\
    $t_{10}$          & 1.45 & 1.47 & 1.49 & 1.52 & 1.30 & 1.37 & 1.43 & 1.49 \\
    $t_{15}$          & 1.15 & 1.19 & 1.23 & 1.27 & 1.01 & 1.10 & 1.17 & 1.24 \\
    $t_{25}$          & 0.97 & 1.02 & 1.07 & 1.11 & 0.85 & 0.94 & 1.02 & 1.08 \\
    MVN          & 0.77 & 0.84 & 0.89 & 0.93 & 0.68 & 0.77 & 0.84 & 0.91 \\ \hline
    \end{tabular}
    \caption{Table of AREs of the ADCM for different choices of $p$ and data-generating distributions, and two choices of depth functions}
    \label{table:AREtable}
\end{table}

We now obtain finite sample efficiencies of the three DCMs as well as their depth-weighted affine equivariant counterparts by a simulation study, and compare them with the same from the SCM and Tyler's scatter matrix. We consider the same 6 elliptical distributions considered in ARE calculations above, and from every distribution draw 10000 samples each for sample sizes $n = 20, 50, 100, 300, 500$. All distributions are centered at ${\bf 0}_p$, and have covariance matrix $\Sigma = \diag(p,p-1,...1)$. We consider 3 choices of $p$: 2, 3 and 4.

We use the concept of principal angles \citep{miao92} to find out error estimates for the first eigenvector of a scatter matrix. In our case, the first eigenvector will be
%
$$ \bfgamma_1 = (1,\overbrace{0,...,0}^{p-1})^T $$
%
For an estimate of the eigenvector, say $\hat\bfgamma_1$, error in prediction is measured by the smallest angle between the two lines, i.e. $ \cos^{-1} | \hat\bfgamma_1^T \hat\bfgamma_1 | $. A smaller absolute value of this angle is equivalent to better prediction. We repeat this 10000 times and calculate the \textbf{Mean Squared Prediction Angle}:
%
$$ MSPA(\hat \bfgamma_1) = \frac{1}{10000} \sum_{m=1}^{10000} \left( \cos^{-1} \left|\bfgamma_1^T \hat\bfgamma^{(m)}_1 \right| \right)^2 $$
%
Finally, the finite sample efficiency of some eigenvector estimate $\hat\bfgamma^E_1$ relative to that obtained from the sample covariance matrix, say $\hat\bfgamma^{Cov}_1$ is obtained as:
$$ FSE(\hat\bfgamma^E_1, \hat\bfgamma^{Cov}_1) = \frac{MSPA(\hat\bfgamma^{Cov}_1)}{MSPA(\hat\bfgamma^E_1)} $$

Tables \ref{table:FSEtable2}, \ref{table:FSEtable3} and \ref{table:FSEtable4} give FSE values for $p=2,3,4$, respectively. In general, all the efficiencies increase as the dimension $p$ goes up. DCM-based estimators (columns 3-5 in each table) outperform SCM and Tyler's scatter matrix, and among the 3 depths considered, projection depth seems to give the best results. Its finite sample performances are better than Tyler's and Huber's M-estimators of scatter as well as their symmetrized counterparts (see Table 4 in \cite{sirkia07}, and quite close to the affine equivariant spatial sign covariance matrix (see Table 2 in \cite{ollilia03}). The depth-weighted iterated versions of these 3 SCMs (columns 6-8 in each table) seem to further better the performance of their corresponding orthogonal equivariant counterparts.

\begin{table}[b]
\begin{footnotesize}
    \begin{tabular}{c|cc|ccc|ccc}
    \hline
    $F$ = Bivariate $t_5$    & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
    $n$=20                   & 0.80 & 0.83  & 0.95   & 0.95   & 0.89  & 1.00    & 0.96    & 0.89   \\
    $n$=50                   & 0.86 & 0.90  & 1.25   & 1.10   & 1.21  & 1.32    & 1.13    & 1.25   \\
    $n$=100                  & 1.02 & 1.04  & 1.58   & 1.20   & 1.54  & 1.67    & 1.24    & 1.63   \\
    $n$=300                  & 1.24 & 1.28  & 1.81   & 1.36   & 1.82  & 1.93    & 1.44    & 1.95   \\
    $n$=500                  & 1.25 & 1.29  & 1.80   & 1.33   & 1.84  & 1.91    & 1.39    & 1.97   \\ \hline
    $F$ = Bivariate $t_6$    & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
    $n$=20                   & 0.77 & 0.79  & 0.92   & 0.92   & 0.86  & 0.96    & 0.92    & 0.85   \\
    $n$=50                   & 0.76 & 0.78  & 1.11   & 1.00   & 1.08  & 1.17    & 1.03    & 1.13   \\
    $n$=100                  & 0.78 & 0.79  & 1.27   & 1.06   & 1.33  & 1.35    & 1.11    & 1.41   \\
    $n$=300                  & 0.88 & 0.91  & 1.29   & 1.09   & 1.35  & 1.38    & 1.15    & 1.45   \\
    $n$=500                  & 0.93 & 0.96  & 1.37   & 1.13   & 1.40  & 1.44    & 1.19    & 1.48   \\ \hline
    $F$ = Bivariate $t_{10}$ & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
    $n$=20                   & 0.70 & 0.72  & 0.83   & 0.84   & 0.77  & 0.89    & 0.87    & 0.79   \\
    $n$=50                   & 0.58 & 0.60  & 0.90   & 0.84   & 0.86  & 0.95    & 0.88    & 0.91   \\
    $n$=100                  & 0.57 & 0.59  & 0.92   & 0.87   & 0.97  & 0.98    & 0.90    & 1.03   \\
    $n$=300                  & 0.62 & 0.64  & 0.93   & 0.85   & 0.99  & 0.99    & 0.91    & 1.06   \\
    $n$=500                  & 0.62 & 0.65  & 0.93   & 0.86   & 1.00  & 1.00    & 0.92    & 1.08   \\ \hline
    $F$ = Bivariate $t_{15}$ & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
    $n$=20                   & 0.63 & 0.66  & 0.76   & 0.78   & 0.72  & 0.81    & 0.81    & 0.73   \\
    $n$=50                   & 0.52 & 0.52  & 0.79   & 0.75   & 0.80  & 0.84    & 0.79    & 0.85   \\
    $n$=100                  & 0.51 & 0.52  & 0.83   & 0.77   & 0.88  & 0.88    & 0.81    & 0.94   \\
    $n$=300                  & 0.55 & 0.56  & 0.84   & 0.79   & 0.91  & 0.89    & 0.84    & 0.98   \\
    $n$=500                  & 0.56 & 0.59  & 0.85   & 0.80   & 0.93  & 0.91    & 0.86    & 0.99   \\ \hline
    $F$ = Bivariate $t_{25}$ & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
    $n$=20                   & 0.63 & 0.65  & 0.77   & 0.79   & 0.74  & 0.80    & 0.81    & 0.74   \\
    $n$=50                   & 0.49 & 0.50  & 0.73   & 0.71   & 0.76  & 0.78    & 0.75    & 0.80   \\
    $n$=100                  & 0.45 & 0.46  & 0.73   & 0.69   & 0.81  & 0.78    & 0.73    & 0.87   \\
    $n$=300                  & 0.51 & 0.52  & 0.78   & 0.75   & 0.87  & 0.83    & 0.79    & 0.94   \\
    $n$=500                  & 0.53 & 0.55  & 0.79   & 0.75   & 0.87  & 0.84    & 0.80    & 0.94   \\ \hline
    $F$ = BVN                & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
    $n$=20                   & 0.56 & 0.60  & 0.69   & 0.71   & 0.67  & 0.73    & 0.74    & 0.68   \\
    $n$=50                   & 0.42 & 0.43  & 0.66   & 0.66   & 0.70  & 0.71    & 0.69    & 0.75   \\
    $n$=100                  & 0.42 & 0.43  & 0.69   & 0.66   & 0.77  & 0.74    & 0.71    & 0.83   \\
    $n$=300                  & 0.47 & 0.49  & 0.71   & 0.69   & 0.82  & 0.76    & 0.73    & 0.88   \\
    $n$=500                  & 0.48 & 0.50  & 0.73   & 0.71   & 0.83  & 0.78    & 0.76    & 0.89   \\ \hline
    \end{tabular}
\end{footnotesize}
\caption{Finite sample efficiencies of several scatter matrices: $p=2$}
\label{table:FSEtable2}
\end{table}

\begin{table}[b]
\begin{footnotesize}
   \begin{tabular}{c|cc|ccc|ccc}
    \hline
    3-variate $t_5$    & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
    $n$=20             & 0.96 & 0.97  & 1.06   & 1.03   & 0.99  & 1.07    & 1.06    & 0.97   \\
    $n$=50             & 1.07 & 1.08  & 1.28   & 1.20   & 1.18  & 1.33    & 1.23    & 1.20   \\
    $n$=100            & 1.12 & 1.15  & 1.49   & 1.31   & 1.40  & 1.57    & 1.38    & 1.48   \\
    $n$=300            & 1.49 & 1.54  & 2.09   & 1.82   & 2.07  & 2.19    & 1.93    & 2.18   \\
    $n$=500            & 1.60 & 1.66  & 2.18   & 1.87   & 2.21  & 2.27    & 1.95    & 2.30   \\ \hline
    3-variate $t_6$    & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
    $n$=20             & 0.90 & 0.92  & 1.00   & 0.99   & 0.95  & 1.02    & 1.01    & 0.94   \\
    $n$=50             & 0.95 & 0.96  & 1.16   & 1.09   & 1.09  & 1.21    & 1.14    & 1.11   \\
    $n$=100            & 0.98 & 0.99  & 1.32   & 1.22   & 1.25  & 1.38    & 1.27    & 1.29   \\
    $n$=300            & 1.10 & 1.14  & 1.57   & 1.40   & 1.58  & 1.62    & 1.47    & 1.64   \\
    $n$=500            & 1.17 & 1.20  & 1.57   & 1.43   & 1.60  & 1.63    & 1.51    & 1.67   \\ \hline
    3-variate $t_{10}$ & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
    $n$=20             & 0.87 & 0.88  & 0.95   & 0.94   & 0.90  & 0.97    & 0.98    & 0.89   \\
    $n$=50             & 0.77 & 0.79  & 0.96   & 0.92   & 0.94  & 0.99    & 0.96    & 0.95   \\
    $n$=100            & 0.75 & 0.76  & 1.02   & 0.95   & 1.01  & 1.06    & 1.00    & 1.05   \\
    $n$=300            & 0.73 & 0.75  & 1.03   & 0.98   & 1.10  & 1.08    & 1.03    & 1.15   \\
    $n$=500            & 0.73 & 0.76  & 1.02   & 0.98   & 1.09  & 1.06    & 1.02    & 1.14   \\ \hline
    3-variate $t_{15}$ & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
    $n$=20             & 0.84 & 0.86  & 0.92   & 0.92   & 0.89  & 0.94    & 0.94    & 0.87   \\
    $n$=50             & 0.75 & 0.76  & 0.92   & 0.90   & 0.90  & 0.96    & 0.94    & 0.93   \\
    $n$=100            & 0.66 & 0.67  & 0.91   & 0.87   & 0.95  & 0.96    & 0.92    & 1.00   \\
    $n$=300            & 0.61 & 0.64  & 0.90   & 0.87   & 1.00  & 0.93    & 0.91    & 1.04   \\
    $n$=500            & 0.65 & 0.67  & 0.89   & 0.87   & 0.99  & 0.93    & 0.91    & 1.03   \\ \hline
    3-variate $t_{25}$ & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
    $n$=20             & 0.78 & 0.79  & 0.87   & 0.89   & 0.87  & 0.89    & 0.92    & 0.86   \\
    $n$=50             & 0.70 & 0.71  & 0.88   & 0.86   & 0.88  & 0.91    & 0.90    & 0.90   \\
    $n$=100            & 0.61 & 0.63  & 0.86   & 0.83   & 0.89  & 0.90    & 0.88    & 0.94   \\
    $n$=300            & 0.58 & 0.59  & 0.83   & 0.80   & 0.92  & 0.87    & 0.85    & 0.98   \\
    $n$=500            & 0.62 & 0.64  & 0.83   & 0.82   & 0.94  & 0.88    & 0.87    & 0.99   \\ \hline
    3-variate Normal   & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
    $n$=20             & 0.76 & 0.78  & 0.85   & 0.87   & 0.84  & 0.87    & 0.90    & 0.83   \\
    $n$=50             & 0.66 & 0.67  & 0.82   & 0.81   & 0.84  & 0.86    & 0.86    & 0.86   \\
    $n$=100            & 0.56 & 0.58  & 0.77   & 0.75   & 0.83  & 0.82    & 0.79    & 0.87   \\
    $n$=300            & 0.53 & 0.55  & 0.75   & 0.74   & 0.85  & 0.79    & 0.78    & 0.90   \\
    $n$=500            & 0.56 & 0.58  & 0.76   & 0.76   & 0.87  & 0.80    & 0.80    & 0.92   \\ \hline
    \end{tabular}
\end{footnotesize}
\caption{Finite sample efficiencies of several scatter matrices: $p=3$}
\label{table:FSEtable3}
\end{table}

\begin{table}[b]
\begin{footnotesize}
    \begin{tabular}{c|cc|ccc|ccc}
    \hline
    4-variate $t_5$    & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
    $n$=20             & 1.04 & 1.02  & 1.10   & 1.07   & 1.02  & 1.09    & 1.07    & 0.98   \\
    $n$=50             & 1.08 & 1.08  & 1.16   & 1.16   & 1.13  & 1.19    & 1.19    & 1.13   \\
    $n$=100            & 1.31 & 1.31  & 1.42   & 1.38   & 1.36  & 1.46    & 1.44    & 1.36   \\
    $n$=300            & 1.46 & 1.54  & 1.81   & 1.76   & 1.95  & 1.88    & 1.88    & 1.95   \\
    $n$=500            & 1.92 & 1.93  & 2.23   & 2.03   & 2.31  & 2.35    & 2.19    & 2.39   \\ \hline
    4-variate $t_6$    & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
    $n$=20             & 1.00 & 1.05  & 1.03   & 1.05   & 1.00  & 1.04    & 1.04    & 0.95   \\
    $n$=50             & 1.03 & 1.01  & 1.13   & 1.12   & 1.11  & 1.19    & 1.17    & 1.10   \\
    $n$=100            & 1.08 & 1.12  & 1.25   & 1.23   & 1.27  & 1.24    & 1.25    & 1.22   \\
    $n$=300            & 1.34 & 1.36  & 1.64   & 1.52   & 1.60  & 1.67    & 1.61    & 1.68   \\
    $n$=500            & 1.26 & 1.34  & 1.55   & 1.49   & 1.60  & 1.65    & 1.61    & 1.69   \\ \hline
    4-variate $t_{10}$ & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
    $n$=20             & 0.90 & 0.89  & 0.95   & 0.98   & 0.98  & 0.96    & 1.01    & 0.95   \\
    $n$=50             & 0.90 & 0.91  & 1.01   & 0.98   & 0.98  & 1.03    & 1.04    & 0.99   \\
    $n$=100            & 0.87 & 0.87  & 0.93   & 0.95   & 1.01  & 0.99    & 1.01    & 1.05   \\
    $n$=300            & 0.87 & 0.87  & 1.09   & 1.09   & 1.17  & 1.14    & 1.16    & 1.23   \\
    $n$=500            & 0.88 & 0.92  & 1.10   & 1.10   & 1.23  & 1.19    & 1.22    & 1.29   \\ \hline
    4-variate $t_{15}$ & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
    $n$=20             & 0.92 & 0.90  & 0.94   & 0.94   & 0.96  & 0.95    & 0.97    & 0.89   \\
    $n$=50             & 0.82 & 0.83  & 0.88   & 0.91   & 0.93  & 0.88    & 0.93    & 0.93   \\
    $n$=100            & 0.84 & 0.87  & 0.92   & 0.95   & 1.00  & 0.93    & 0.96    & 1.00   \\
    $n$=300            & 0.73 & 0.75  & 0.96   & 0.99   & 1.10  & 1.00    & 1.06    & 1.12   \\
    $n$=500            & 0.73 & 0.76  & 0.95   & 0.96   & 1.06  & 0.94    & 0.97    & 1.06   \\ \hline
    4-variate $t_{25}$ & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
    $n$=20             & 0.89 & 0.92  & 0.92   & 0.92   & 0.90  & 0.96    & 0.95    & 0.89   \\
    $n$=50             & 0.82 & 0.84  & 0.89   & 0.90   & 0.91  & 0.93    & 0.96    & 0.92   \\
    $n$=100            & 0.77 & 0.76  & 0.90   & 0.90   & 0.96  & 0.94    & 0.98    & 1.04   \\
    $n$=300            & 0.73 & 0.77  & 0.93   & 0.91   & 0.98  & 1.00    & 0.98    & 1.03   \\
    $n$=500            & 0.67 & 0.71  & 0.83   & 0.83   & 0.96  & 0.88    & 0.90    & 1.00   \\ \hline
    4-variate Normal   & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
    $n$=20             & 0.82 & 0.84  & 0.87   & 0.90   & 0.91  & 0.89    & 0.93    & 0.89   \\
    $n$=50             & 0.80 & 0.81  & 0.87   & 0.88   & 0.88  & 0.88    & 0.92    & 0.88   \\
    $n$=100            & 0.68 & 0.71  & 0.80   & 0.85   & 0.91  & 0.82    & 0.86    & 0.92   \\
    $n$=300            & 0.61 & 0.63  & 0.82   & 0.85   & 0.93  & 0.86    & 0.91    & 0.96   \\
    $n$=500            & 0.60 & 0.64  & 0.77   & 0.80   & 0.90  & 0.82    & 0.86    & 0.96   \\ \hline
    \end{tabular}
\end{footnotesize}
\caption{Finite sample efficiencies of several scatter matrices: $p=4$}
\label{table:FSEtable4}
\end{table}

\subsection{Robust estimation of eigenvalues, and a plug-in estimator of $\Sigma$}

As we have seen in theorem \ref{Theorem:covform}, eigenvalues of the DCM are not same as the population eigenvalues, whereas the ADCM only gives back standardized eigenvalues. However, it is possible to robustly estimate the original eigenvalues by working with the individual columns of the robust score matrix. We do this using the following steps:

\begin{enumerate}
\item Randomly divide the sample indices $\{1,2,...,n\}$ into $k$ disjoint groups $\{G_1,...,G_k \}$ of size $\lfloor n/k \rfloor$ each;

\item Assume the data is centered. Transform the data matrix: $S = \hat\Gamma^T_D X$;

\item Calculate coordinate-wise variances for each group of indices $G_j$:
%
$$
\hat\lambda_{i,j} = \frac{1}{|G_j|} \sum_{l \in G_j} (s_{li} - \bar s_{G_j,i})^2; \quad i = 1,...,p; j = 1,...,k
$$
where $\bar\bfs_{G_j} = (\bar s_{G_j,1}, ..., \bar s_{G_j,p})^T$ is the vector of column-wise means of $S_{G_j}$, the submatrix od $S$ with row indices in $G_j$.
%
\item Obtain estimates of eigenvalues by taking coordinate-wise medians of these variances:
%
$$
\hat \lambda_i = \text{median} (\hat\lambda_{i,1}, ... , \hat\lambda_{i,k} ); \quad i = 1,...,p
$$
%
\end{enumerate}
%
The number of subgroups used to calculate this median-of-small-variances estimator can be determined following \citep{Minsker15}. After this, we construct a consistent plug-in estimator of the population covariance matrix $\Sigma$:

\begin{Theorem}\label{Thm:pluginSigma}
Consider the estimates $\hat\lambda_i$ obtained from the above algorithm, and the matrix of eigenvectors $\hat\Gamma_D$ estimated using the sample DCM. Define $\hat\Sigma = \hat\Gamma_D \hat\Lambda \hat\Gamma_D^T; \hat\Lambda = \text{diag}(\hat\lambda_1, ..., \hat\lambda_p)$. Then as $n \rightarrow \infty$,
%
$$ \| \hat\Sigma - \Sigma \|_F \stackrel{P}{\rightarrow} 0 $$
%
$\|.\|_F$ being the Frobenius norm.
\end{Theorem}

{\colrbf (put in 1 or 2 sentences?)}

### 2018-03-20 MS-new/4_SDR.tex
first commit in shubhobm

\section{Robust PCA and supervised models}

In the presence of a vector of univariate responses, say $\bfY = (Y_1,Y_2,...,Y_n)^T$, there is substantial literature devoted to utilizing the subspace generated by the basis of $Cov(\bfX)$ in modelling $E(Y|\bfX)$. This ranges from the simple Principal Components Regression (PCR) to Partial Least Squares (PLS) and Envelope methods \citep{Cook10}. Here we concentrate on robust inference using Sufficient Dimension Reduction (SDR) \citep{AdragniCook09}, mainly because it provides a general framework for reducing dimensionality of data directly using top eigenvectors of the covariance matrix of $X$ (albeit in a different manner than PCR) or an appropriate affine transformation of it.

SDR attempts to find out a linear transformation $R$ on $\bfX$ such that $E(Y|\bfX) = E(Y|R(\bfX))$. Assuming that $R(\bfX)$ takes values in $\mathbb R^d, d \leq \min(n,p)$, this can be achieved through an inverse regression model:
%
\begin{equation}
\bfX_y = \bar \bfmu + \Gamma \bfv_y + \bfepsilon
\end{equation}
%
where $\bfX_y = \bfX|Y=y, \bar\bfmu = E\bfX$, $\Gamma$ is a $p \times d$ semi-orthogonal basis for $\mathcal S_\Gamma$, the spanning subspace of $\{ E \bfX_y - \bar\bfmu | y \in S _Y \}$ ($S_y$ is sample space of $Y$) and $\bfv_y = (\Gamma^T \Gamma)^{-1} \Gamma^T (E \bfX_y - \bar\bfmu) \in \mathbb R^d$. The random error term $\bfepsilon$ follows a multivariate normal distribution with mean ${\bf 0}_p$ and covariance matrix $\Delta$. This formulation is straightforward to implement when $Y$ is categorical, while for continuous responses, the vector $\bfy$ is divided into a number of slices.

Under this model the minimal sufficient transformation is $R(\bfX) = \Gamma^T \Delta^{-1} \bfX$. The simplest case of this model is when $\Delta = \sigma^2 I_p$, for which the maximum likelihood estimator of $ R(\bfX)$ turns out to be the first $d$ PCs of $Cov(\bfX)$. Taking $\hat E\bfX_y = \bar\bfX_y$ and $\hat{\bar\bfmu} = \bar\bfX$, one can now estimate $\sigma^2$ as: $\hat\sigma^2 = \sum_{i=1}^p s_{ii}/p$, where $s_{ii}$ is the $i^\text{th}$ diagonal element of $\hat{Cov}_Y( \bfX_Y - \bar\bfX - \hat\Gamma \hat\bfv_Y)$. Following this, predictions for a new observation $\bfx$ is obtained as a weighted sum of the responses:
%
$$
\hat E(Y|\bfX=\bfx) = \frac{\sum_{i=1}^n w_i Y_i}{\sum_{i=1}^n w_i}; \quad w_i = \exp \left[ -\frac{1}{\hat\sigma^2}  \| \hat\Gamma^T (\bfx - \bfX_i) \|^2 \right]
$$
%

We formulate a robust version of the above procedure by estimating the quantities $\Gamma, \bar\bfmu, \bfmu_y, \sigma^2$ by robust methods. Specifically, we take:
%
\begin{itemize}
\item $\tilde \Gamma = $ first $d$ eigenvectors of the sample DCM;
%
\item $\tilde{\bar\bfmu} = $ spatial median of the rows of $X$;
%
\item $\tilde \bfmu_y = $ spatial median of the rows of $(X|Y=y)$, for all $y \in S_Y$;
%
\item $\tilde\sigma^2 = \sum_{i=1}^p [\widehat{\text{MAD}}_Y (X_{Y,i} - \tilde{\bar\mu}_i - \tilde\bfgamma_i^T \tilde\bfv_Y)]^2/p$, with $\tilde\Gamma = (\tilde\bfgamma_1, ..., \tilde\bfgamma_p)^T$.
\end{itemize}
%
The following simulation study using the same setup as in \citep{AdragniCook09} compares the performance of our robust SDR with the original method with or without the presence of bad leverage points in the covariate matrix $X$. For a fixed dimension $p$, we take $n=200, d=1$, generate the responses $Y$ as independent standard normal, and the predictors as $\bfX_Y = \bfgamma^* v_Y^* + \bfepsilon$, with $\bfgamma^*_{p\times 1} = (1,...,1)^T, v_Y = Y + Y^2 + Y^3$ and $Var(\bfepsilon) = 25 I_p$. We measure performance of both SDR models by their mean squared prediction error on another set of 200 observations $(Y^*, \bfX^*)$ generated similarly, and taking the average of these errors on 100 such training-test pair of datasets. Finally we repeat the whole setup for different choices of $p = 5,10,25,50,75,100,125,150$.

\begin{figure}[t]
%\captionsetup{justification=centering, font=footnotesize}
\begin{center}
\subfigure[]{\epsfxsize=0.35\linewidth \epsfbox{../Codes/SDRcomparison_noout}}
\subfigure[]{\epsfxsize=0.35\linewidth \epsfbox{../Codes/SDRcomparison_out}}
\caption{Average prediction errors for two methods of SDR (a) in absence and (b) in presence of outliers}
\label{fig:SDRfig}
\end{center}
\end{figure}

Panel (a) of figure \ref{fig:SDRfig} compares prediction errors using robust and maximum likelihood SDR estimates when $X$ contains no outliers, and the two methods are virtually indistinguishable. We now introduce outliers in each of the 100 datasets by adding 100 to first $p/5$ coordinates of the first 10 observations in $X$, and repeat the analysis. Panel (b) of the figure shows that although our robust method performs slightly worse than the case when there were no outliers, it remains more accurate in predicting our of sample observations for all values of $p$.

### 2018-03-20 MS-new/5_Functional.tex
first commit in shubhobm

\section{Robust inference with functional data}

{\colrbf (Some technical notations)}

We use the approach of \cite{BoenteBarrera15} for performing robust PCA on functional data. Given data on $n$ functions, say $f_1, f_2, ..., f_n \in L^2[0,1]$, each observed at a set of common design points $\{ t_1, ..., t_m \} $, we model each function as a linear combination of $p$ mutually orthogonal B-spline basis functions $\delta_1, ..., \delta_p$. Following this, we map data for each of the functions onto the coordinate system formed by the spline basis:
%
\begin{equation}
\tilde x_{ij} = \sum_{l=2}^m f_i(t_l) \delta_j(t_l) (t_l - t_{l-1}); \quad 1 \leq i \leq n, 1 \leq j \leq p
\end{equation}
%
We now do depth-based PCA on the transformed $n \times p$ data matrix $\tilde X$, and obtain the rank-$q$ approximation ($q \leq p$) of the $i^\text{th}$ observation using the robust $p \times q$ loading matrix $\tilde P$ and robust $q \times 1$ score vector $\tilde\bfs_i$:
%
$$ \widehat{\tilde\bfx_i} = \tilde\bfmu + \tilde P \tilde \bfs_i $$
%
with $\tilde\bfmu$ being the spatial median of $\tilde X$. Then we transform this approximation back to the original coordinates: $\hat f_i (t_l) = \sum_{j=1}^p \widehat{ \tilde x}_{ij} \delta_j (t_l)$.

Detection of anomalous observations is of importance in real-life problems involving functional data analysis. We now demonstrate the utility of our robust method for detecting functional outliers through two data examples.

\textbf{(SD and OD definition, cutoffs... from previous manuscript)
}

\begin{figure}[t]
%\captionsetup{justification=centering, font=footnotesize}
\begin{center}
\subfigure[]{\epsfxsize=.32\linewidth\epsfbox{../Codes/Elnino_functional1}}
\subfigure[]{\epsfxsize=.32\linewidth\epsfbox{../Codes/Elnino_functional2}}
\subfigure[]{\epsfxsize=.32\linewidth\epsfbox{../Codes/Elnino_functional3}}\\
\vspace{-1em}
\subfigure[]{\epsfxsize=.32\linewidth\epsfbox{../Codes/Octane_functional1}}
\subfigure[]{\epsfxsize=.32\linewidth\epsfbox{../Codes/Octane_functional2}}
\subfigure[]{\epsfxsize=.32\linewidth\epsfbox{../Codes/Octane_functional3}}
%\subfigure[]{\epsfxsize=0.35\linewidth \epsfbox{../Codes/SDRcomparison_out}}
\caption{Actual sample curves, their spline approximations and diagnostic plots respectively for El-Ni\~no (a-c) and Octane (d-f) datasets}
\label{fig:fPCAfig}
\end{center}
\end{figure}

We first look into the El-Ni\~no data, which is part of a larger dataset on potential factors behind El-Ni\~no oscillations in the tropical pacific available in \url{http://www.cpc.ncep.noaa.gov/data/indices/}. This records monthly average Sea Surface Temperatures from June 1970 to May 2004, and the yearly oscillations follow more or less the same pattern (see panel a of figure \ref{fig:fPCAfig}). Using a cubic spline basis with knots at alternate months starting in June gives a close approximation of the yearly time series data (panel b), and performing depth-based PCA with $q=1$ results in two points having their SD and OD larger than cutoff (panel c). These points correspond to the time periods June 1982 to May 1983 and June 1997 to May 1998 are marked by black curves in panels a and b), and pinpoint the two seasons with strongest El-Ni\~no events.

Our second application is on the Octane data, which consists of 226 variables and 39 observations \citep{esbensen94}. Each sample is a gasoline compound with a certain octane number, and has its NIR absorbance spectra measured in 2 nm intervals between 1100 - 1550 nm. There are 6 outliers here: compounds 25, 26 and 36-39, which contain alcohol. We use the same basis structure as the one in El-Ni\~no data here, and again the top robust PC turns out to be sufficient in identifying all 6 outliers (panels d, e and f of figure \ref{fig:fPCAfig}).

### 2018-03-20 MS-new/6_Conclusion.tex
first commit in shubhobm

\section{Conclusion}\label{section:sec7}

In the above sections we introduce a covariance matrix based on depth-based multivariate ranks that keeps the eigenvectors of the actual population unchanged for elliptical distributions. We provide asymptotic results for the sample DCM, its eigenvalues and eigenvectors. Bounded influence functions as well as simulation studies suggest that the eigenvector estimates obtained from the DCM are highly robust, yet do not lose much in terms of efficiency. Thus it provides a plausible alternative to existing approaches of robust PCA that are based on estimation of covariance matrices (for example SCM, Tyler's scatter matrix, D\"{u}mbgen's symmetrized shape matrix).

{\colrbf (some text)}

### 2018-03-20 MS-new/7_Appendix.tex
first commit in shubhobm

\appendix
\section*{Appendix}
\numberwithin{equation}{section}
\section{\textbf{Form of $V_{D,S}(F)$}}\label{section:appA}

First observe that for $F$ having covariance matrix $\Sigma = \Gamma\Lambda\Gamma^T$,
%
$$ V_{D,S}(F)  = (\Gamma \otimes \Gamma) V_{D,S}(F_\Lambda) (\Gamma \otimes \Gamma)^T$$
%
where $F_\Lambda$ has the same elliptic distribution as $F$, but with covariance matrix $\Lambda$. Now,
%
\begin{eqnarray*}
V_{D,S} (F_\Lambda) &=& E \left[ vec \left\{ \frac{(\tilde D_\bfZ (\bfz))^2 \Lambda^{1/2} \bfz\bfz^T \Lambda^{1/2}}{\bfz^T\Lambda\bfz} - \Lambda_{D,S} \right\} vec^T \left\{ \frac{(\tilde D_\bfZ (\bfz))^2 \Lambda^{1/2} \bfz\bfz^T \Lambda^{1/2}}{\bfz^T\Lambda\bfz} - \Lambda_{D,S} \right\} \right]\\
&=& E \left[ vec \left\{ (\tilde D_\bfZ (\bfz))^2 SS(\Lambda^{1/2}\bfz; \bf0) \right\} vec^T \left\{ (\tilde D_\bfZ (\bfz))^2 SS(\Lambda^{1/2}\bfz; \bf0) \right\} \right]\\
&& - \quad vec(\Lambda_{D,S}) vec^T(\Lambda_{D,S})
\end{eqnarray*}

The matrix $vec(\Lambda_{D,S}) vec^T(\Lambda_{D,S})$ consists of elements $\lambda_i\lambda_j$ at $(i,j)^\text{th}$ position of the $(i,j)^\text{th}$ block, and 0 otherwise. These positions correspond to variance and covariance components of on-diagonal elements. For the expectation matrix, all its elements are of the form $E[\sqrt{\lambda_a \lambda_b \lambda_c \lambda_d} z_a z_b z_c z_d . (\tilde D_\bfZ (\bfz))^4 / (\bfz^T \Lambda \bfz)^2]$, with $1 \leq a,b,c,d \leq p$. Since $(\tilde D_\bfZ (\bfz))^4 / (\bfz^T \Lambda \bfz)^2$ is even in $\bfz$, which has a circularly symmetric distribution, all such expectations will be 0 unless $a=b=c=d$, or they are pairwise equal. Following a similar derivation for spatial sign covariance matrices in \cite{magyar14}, we collect the non-zero elements and write the matrix of expectations:
%
$$ (I_{p^2} + K_{p,p}) \left\{ \sum_{a=1}^p \sum_{b=1}^p \gamma^D_{ab} (\bfe_a \bfe_a^T \otimes  \bfe_b \bfe_b^T) - \sum_{a=1}^p \gamma^D_{aa} (\bfe_a \bfe_a^T \otimes  \bfe_a \bfe_a^T) \right\} + \sum_{a=1}^p \sum_{b=1}^p \gamma^D_{ab} (\bfe_a \bfe_b^T \otimes  \bfe_a \bfe_b^T) $$
%
where $I_k = (\bfe_1,...,\bfe_k), K_{m,n} = \sum_{i=1}^m \sum_{j=1}^n J_{ij} \otimes J_{ij}^T$ with $J_{ij}$ the $m \times n$ matrix having 1 as $(i,j)^\text{th}$ element and 0 elsewhere, and $\gamma^D_{mn} = E[ \lambda_m \lambda_n z_m^2 z_n ^2 . (\tilde D_\bfZ (\bfz))^4 / (\bfz^T \Lambda \bfz)^2]; 1 \leq m,n \leq p$.

\paragraph{}Putting everything together, denote $\hat S^D(F_\Lambda) = \sum_{i=1}^n (\tilde D^n_\bfZ (\bfz_i))^2 SS(\Lambda^{1/2}\bfz_i; \hat \bfmu_n)/n $. Then the different types of elements in the matrix $V_{D,S}(F_\Lambda)$ are as given below ($1 \leq a,b,c,d \leq p$):

\begin{itemize}
\item Variance of on-diagonal elements
%
$$ AVar( \sqrt n \hat S^D_{aa} (F_\Lambda)) = E \left[ \frac{(\tilde D_\bfZ (\bfz))^4 \lambda_a^2 z_a^4}{(\bfz^T \Lambda \bfz)^2} \right] - \lambda_{D,S,a}^2 $$

\item Variance of off-diagonal elements ($a \neq b$)
%
$$ AVar( \sqrt n \hat S^D_{ab} (F_\Lambda)) = E \left[ \frac{(\tilde D_\bfZ (\bfz))^4 \lambda_a \lambda_b z_a^2 z_b^2}{(\bfz^T \Lambda \bfz)^2} \right] $$

\item Covariance of two on-diagonal elements ($a \neq b$)
%
$$ ACov(\sqrt n \hat S^D_{aa} (F_\Lambda), \sqrt n \hat S^D_{bb} (F_\Lambda))
= E \left[ \frac{(\tilde D_\bfZ (\bfz))^4 \lambda_a \lambda_b z_a^2 z_b^2}{(\bfz^T \Lambda \bfz)^2} \right] - \lambda_{D,S,a} \lambda_{D,S,b} $$

\item Covariance of two off-diagonal elements ($a \neq b \neq c \neq d$)
%
$$ ACov(\sqrt n \hat S^D_{ab} (F_\Lambda), \sqrt n \hat S^D_{cd} (F_\Lambda)) = 0 $$

\item Covariance of one off-diagonal and one on-diagonal element ($a \neq b \neq c$)
%
$$ ACov(\sqrt n \hat S^D_{ab} (F_\Lambda), \sqrt n \hat S^D_{cc} (F_\Lambda)) = 0 $$
\end{itemize}

\section{Asymptotics of eigenvectors and eigenvalues}\label{section:appB}
The following result allows us to obtain asymptotic joint distributions of eigenvectors and eigenvalues of the sample DCM, provided we know the limiting distribution of the sample DCM itself:

\begin{Theorem} \label{Theorem:decomp} \citep{taskinen12}
Let $F_\Lambda$ be an elliptical distribution with a diagonal covariance matrix $\Lambda$, and $\hat C$ be any positive definite symmetric $p \times p$ matrix such that at $F_\Lambda$ the limiting distribution of $\sqrt n vec(\hat C - \Lambda)$ is a $p^2$-variate (singular) normal distribution with mean zero. Write the spectral decomposition of $\hat C$ as $\hat C = \hat P \hat\Lambda \hat P^T$. Then the limiting distributions of $\sqrt n vec(\hat P - I_p)$ and $\sqrt n vec(\hat\Lambda - \Lambda)$ are multivariate (singular) normal and
%
\begin{equation} \label{equation:decompEq}
\sqrt n vec (\hat C - \Lambda)  = \left[ (\Lambda \otimes I_p) - (I_p \otimes \Lambda) \right] \sqrt n vec (\hat P - I_p) + \sqrt n vec (\hat\Lambda - \Lambda) + o_P(1)
\end{equation}
\end{Theorem}

The first matrix picks only off-diagonal elements of the LHS and the second one only diagonal elements. We shall now use this as well as the form of the asymptotic covariance matrix of the vec of sample DCM, i.e. $V_{D,S}(F)$ to obtain limiting variance and covariances of eigenvalues and eigenvectors.

\begin{Corollary} \label{Corollary:eigendist}
Consider the sample DCM $ \hat S^D(F) = \sum_{i=1}^n (\tilde D^n_\bfX (\bfx_i))^2 SS(\bfx_i; {\bf \hat\bfmu_n})/n $ and its spectral decomposition $\hat S^D(F) = \hat\Gamma_D \hat\Lambda_D \hat\Gamma_D^T $. Then the matrices $G = \sqrt n (\hat\Gamma_D - \Gamma) $ and $L = \sqrt n (\hat\Lambda_D - \Lambda_{D,S}) $ have independent distributions. The random variable $vec(G)$ asymptotically has a $p^2$-variate normal distribution with mean ${\bf 0}_{p^2}$, and the asymptotic variance and covariance of different columns of $G = (\bfg_1,...,\bfg_p)$ are as follows:
%
\begin{equation} \label{equation:DevEq}
AVar(\bfg_i) = \sum_{k=1; k \neq i}^p \frac{1}{(\lambda_{D,s,k} - \lambda_{D,S,i})^2} E \left[ \frac{(\tilde D_\bfZ (\bfz))^4 \lambda_i \lambda_k z_i^2 z_k^2}{(\bfz^T \Lambda \bfz)^2} \right] \bfgamma_k \bfgamma_k^T
\end{equation}
%
\begin{equation}
ACov(\bfg_i, \bfg_j) = - \frac{1}{(\lambda_{D,s,i} - \lambda_{D,S,j})^2} E \left[ \frac{(\tilde D_\bfZ (\bfz))^4 \lambda_i \lambda_j z_i^2 z_j^2}{(\bfz^T \Lambda \bfz)^2} \right] \bfgamma_j \bfgamma_i^T; \quad i \neq j
\end{equation}
%
where $\Gamma = (\bfgamma_1,...,\bfgamma_p)$. The vector consisting of diagonal elements of $L$, say $\bfl = (\l_1,...,\l_p)^T$ asymptotically has a $p$-variate normal distribution with mean ${\bf 0}_p$ and variance-covariance elements:
%
\begin{eqnarray}
AVar(l_i) &=& E \left[ \frac{(\tilde D_\bfZ (\bfz))^4 \lambda_i^2 z_i^4}{(\bfz^T \Lambda \bfz)^2} \right] - \lambda_{D,S,i}^2\\
ACov(l_i, l_j) &=& E \left[ \frac{(\tilde D_\bfZ (\bfz))^4 \lambda_i \lambda_j z_i^2 z_j^2}{(\bfz^T \Lambda \bfz)^2} \right] - \lambda_{D,S,i} \lambda_{D,S,j}; \quad i \neq j
\end{eqnarray}
%
\end{Corollary}

%\begin{proof}[Proof of Theorem \ref{Theorem:decomp}]
%See \cite{taskinen12}
%\end{proof}

\begin{proof}[Proof of Corollary \ref{Corollary:eigendist}]
In spirit, this corollary is similar to Theorem 13.5.1 in \cite{anderson}. Due to the decomposition (\ref{equation:decompEq}) we have, for the distribution $F_\Lambda$, the following relation between any off-diagonal element of $\hat S^D(F_\Lambda)$ and the corresponding element in the estimate of eigenvectors $\hat\Gamma_D (F_\Lambda)$:

$$ \sqrt n \hat\gamma_{D,ij} (F_\Lambda) = \sqrt n \frac{\hat S^D_{ij} (F_\Lambda)}{\lambda_{D,S,i} - \lambda_{D,S,j}}; \quad i \neq j$$

So that for eigenvector estimates of the original $F$ we have

\begin{equation} \label{equation:app1}
\sqrt n (\hat\bfgamma_{D,i} - \bfgamma_i) = \sqrt n \Gamma (\hat \bfgamma_{D,i}(F_\Lambda) - \bfe_i ) = \sqrt n \left[ \sum_{k=1; k \neq i}^p \hat \gamma_{D,ik}(F_\Lambda)\bfgamma_k + (\hat \gamma_{D,ii}(F_\Lambda) - 1)\bfgamma_i \right]
\end{equation}

$\sqrt n (\hat \gamma_{D,ii}(F_\Lambda) - 1) =  o_P(1)$ and $ACov(\sqrt n \hat S^D_{ik}(F_\Lambda), \sqrt n \hat S^D_{il}(F_\Lambda)) = 0$ for $k \neq l$, so the above equation implies

$$ AVar(\bfg_i) = AVar (\sqrt n (\hat\bfgamma_{D,i} - \bfgamma_i)) = \sum_{k=1; k \neq i}^p \frac{AVar(\sqrt n \hat S^D_{ik}(F_\Lambda))}{(\lambda_{D,s,i} - \lambda_{D,S,k})^2} \bfgamma_k \bfgamma_k^T $$

For the covariance terms, from (\ref{equation:app1}) we get, for $i \neq j$,

\begin{eqnarray*}
ACov(\bfg_i, \bfg_j) &=& ACov (\sqrt n (\hat\bfgamma_{D,i} - \bfgamma_i), \sqrt n (\hat\bfgamma_{D,j} - \bfgamma_j))\\
&=& ACov \left( \sum_{k=1; k \neq i}^p \sqrt n \hat \gamma_{D,ik}(F_\Lambda)\bfgamma_k, \sum_{k=1; k \neq j}^p \sqrt n \hat \gamma_{D,jk}(F_\Lambda)\bfgamma_k \right)\\
&=& ACov \left( \sqrt n \hat \gamma_{D,ij}(F_\Lambda)\bfgamma_j, \sqrt n \hat \gamma_{D,ji}(F_\Lambda)\bfgamma_i \right)\\
&=& - \frac{AVar(\sqrt n \hat S^D_{ij}(\Lambda))}{(\lambda_{D,s,i} - \lambda_{D,S,j})^2} \bfgamma_j \bfgamma_i^T
\end{eqnarray*}

The exact forms given in the statement of the corollary now follows from the  Form of $V_{D,S}$ in Appendix \ref{section:appA}.

\paragraph{}For the on-diagonal elements of $\hat S^D(F_\Lambda)$ Theorem \ref{Theorem:decomp} gives us $ \sqrt n \hat\lambda_{D,s,i} (F_\Lambda) = \sqrt n \hat S^D_{ii}(F_\Lambda)$ for $i = 1,...,p$. Hence

\begin{eqnarray*}
AVar(l_i) &=& AVar(\sqrt n \hat\lambda_{D,s,i} - \sqrt n \lambda_{D,S,i})\\
&=& AVar(\sqrt n \hat\lambda_{D,s,i} (F_\Lambda) - \sqrt n \lambda_{D,S,i}(F_\Lambda))\\
&=& AVar(\sqrt n S^D_{ii}(F_\Lambda))
\end{eqnarray*}

A similar derivation gives the expression for $AVar(l_i,l_j); i \neq j$. Finally, since the asymptotic covariance between an on-diagonal and an off-diagonal element of $\hat S^D(F_\Lambda)$, it follows that the elements of $G$ and diagonal elements of $L$ are independent.
\end{proof}

\section{Proofs}\label{section:appC}

\begin{proof}[Proof of Proposition \ref{proposition:SignTest}]
Under contiguous alternatives $H_0: \bfmu = \bfmu_0$, the weighted sign test statistic $T_{n,w}$ has mean $E (w(\bfZ) \bfS (\bfZ))$. For spherically symmetric $\bfZ$, $w(\bfZ)$ depends on $\bfZ$ only through its norm. Since $\| \bfZ \|$ and $\bfS(\bfZ)$ are independent, we get $E (w(\bfZ) \bfS (\bfZ)) = E w(\bfZ). E \bfS (\bfZ)$. The same kind of decomposition holds for $Cov(w(\bfZ) \bfS(\bfZ))$.

We can now simplify the approximate local power $\beta_{n,w}$ of the level-$\alpha$ ($0 < \alpha < 1$) test based on $T_{n,w}$:
%
\begin{eqnarray*}
\beta_{n,w} &=& K_p \left( \chi^2_{p,\alpha} + n (E (w(\bfZ) \bfS (\bfZ))^T \right.\\
&& \left. [ E (w^2(\bfZ) \bfS (\bfZ) \bfS (\bfZ)^T) ]^{-1} (E (w(\bfZ) \bfS (\bfZ)) \right)\\
&=& K_p \left( \chi^2_{p,\alpha} + \frac{E^2 w(\bfZ)}{Ew^2(\bfZ)}. E\bfS(\bfZ)^T [Cov(\bfS(\bfZ)]^{-1} E\bfS(\bfZ) \right)
\end{eqnarray*}
%
where $K_p$ and $\chi^2_{p,\alpha}$ are distribution function and upper-$\alpha$ cutoff of a $\chi^2_p$ distribution, respectively. Since $E^2 w(\bfZ) \leq Ew(\bfZ)$, $\beta_{n,w}$ the largest possible value of $\beta_{n,w}$ is $K_p ( \chi^2_{p,\alpha} + E\bfS(\bfZ)^T [Cov(\bfS(\bfZ)]^{-1} E\bfS(\bfZ) )$, the approximate power of the unweighted sign test statistic. Equality is of course achieved when $w(\bfZ)$ is a constant independent of $\bfZ$.
\end{proof}

\begin{proof}[Sketch of proofs for equations \ref{eqn:hdtest1} and \ref{eqn:hdtest2}]

A first step to obtain asymptotic normality for the high-dimensional location test statistic $C_{n,w}$ is obtaining an equivalent result of Lemma 2.1 in \cite{WangPengLi15}:

\begin{Lemma}\label{Lemma:HDlemma21} Under the conditions

\noindent\textbf{(C1)}$\text{Tr}(\Sigma^4) = o(\text{Tr}^2(\Sigma^2)) $,

\noindent\textbf{(C2)}$\text{Tr}^4(\Sigma) / \text{Tr}^2(\Sigma^2) \exp[ - \text{Tr}^2(\Sigma) / 128p \lambda^2_{\max}(\Sigma) ] = o(1)$
\vspace{1em}

\noindent when $H_0$ is true we have
%
\begin{eqnarray}
E[ (\bfepsilon_{w1}^T \bfepsilon_{w2})^4 ] &=& O(1) E^2[ (\bfepsilon_{w1}^T \bfepsilon_{w2})^2 ]\\
E[ (\bfepsilon_{w1}^T B_w \bfepsilon_{w1})^2 ] &=& O(1) E^2[ (\bfepsilon_{w1}^T B_w \bfepsilon_{w1})^2 ]\\
E[ (\bfepsilon_{w1}^T B_w \bfepsilon_{w2})^2 ] &=& o(1) E^2[ (\bfepsilon_{w1}^T B_w \bfepsilon_{w1})^2 ]
\end{eqnarray}
%
with $\bfepsilon \sim \mathcal E({\bf 0}_p, \Lambda, G)$ and $\bfepsilon_w = w(\bfepsilon) \bfS(\bfepsilon)$.
\end{Lemma}
%
A proof of this lemma is derived using results in section 3 of \cite{ElKaroui09}, noticing that any-scalar valued 1-Lipschitz function of $\bfepsilon_w$ is a $M_w$-Lipschitz function of $\bfS(\bfepsilon)$, with $M_w = \sup_\bfepsilon w(\bfepsilon)$. Same steps as in the proof of Theorem 2.2 in \cite{WangPengLi15} follow now, using the lemma above in place of Lemma 2.1 therein, to establish asymptotic normality of $C_{n,w}$ under $H_0$.

To derive the asymptotic distribution under contiguous alternatives we need the conditions (C3)-(C6) in \cite{WangPengLi15}, as well as slightly modified versions of Lemmas A.4 and A.5:

\begin{Lemma}
Given that condition (C3) holds, we have $\lambda_{\max} (B_w) \leq 2 \frac{\lambda_{\max}}{\text{Tr} (\Sigma)} (1+o(1))$.
\end{Lemma}

\begin{Lemma}
Define $D_w = E \left[ \frac{w^2(\bfepsilon)}{\| \bfepsilon \|^2} (I_p - \bfS(\bfepsilon) \bfS(\bfepsilon)^T )\right] $. Then $\lambda_{\max} (A_w) \leq E( w(\bfepsilon)/\| \bfepsilon \|)$ and $\lambda_{\max} (D_w) \leq E( w(\bfepsilon)/\| \bfepsilon \|)^2$. Further, if (C3) and (C4) hold then $\lambda_{\min} (A_w) \geq E( w(\bfepsilon)/\| \bfepsilon \|)(1+o(1))/\sqrt 3$.
\end{Lemma}
%
The proof now exactly follows steps in the proof of theorem 2.3 in \cite{WangPengLi15}, replacing vector signs by weighted signs, using the fact that $w(\bfepsilon)$ is bounded above by $M_w$ while applying conditions (C5)-(C6) and lemmas A.1, A.2, A.3, and finally using the above two lemmas in place of lemmas A.4 and A.5 respectively.
\end{proof}

\begin{proof}[Proof of Theorem  \ref{Theorem:covform}]
The proof follows directly from writing out the expression of $Cov ( \tilde \bfX)$:
%
\begin{eqnarray*}
Cov(\tilde\bfX) &=& E(\tilde\bfX \tilde\bfX^T) - E(\tilde\bfX) E(\tilde\bfX)^T\\
&=& \Gamma . E \left[ (\tilde D_\bfZ(\bfz))^2 \frac{\|\bfz\|^2}{\| \Lambda^{1/2}\bfz\|} \Lambda^{1/2} \bfS(\bfz) \bfS(\bfz)^T \Lambda^{1/2} \right] \Gamma^T - {\bf 0}_p {\bf 0}_p^T\\
&=& \Gamma .E \left[ (\tilde D_\bfZ(\bfz))^2 \frac{\Lambda^{1/2} \bfz \bfz^T \Lambda^{1/2}}{\bfz^T \Lambda \bfz} \right] \Gamma^T
\end{eqnarray*}
%
\end{proof}

\begin{proof}[Proof of Lemma \ref{Lemma:lemma1}]
For two positive definite matrices $A,B$, we denote by $A>B$ that $A-B$ is positive definite. Also, denote
%
$$ S_n = \sqrt n \left[ \frac{1}{n} \sum_{i=1}^n \left| (\tilde D^{n} _\bfX (\bfx_i))^2  - (\tilde D_\bfX (\bfx_i))^2 \right| SS(\bfx_i; \hat\bfmu_n) \right] $$
%
%Consider now the quantity $\bft^T S_n \bft$, where $\bft \in \mathbb{R}^p$. Now applying Cauchy-Schwarz inequality we shall have
%%
%\begin{eqnarray}\label{eqn:AppEqn1}
%\frac{(\bft^T S_n \bft)^2}{n} & = & \left[ \frac{1}{n} \sum_{i=1}^n \left| (\tilde D^{n} _\bfX (\bfx_i))^2  - (\tilde D_\bfX (\bfx_i))^2 \right|^2  \bft^T SS(\bfx_i; \hat\bfmu_n) \bft \right]^2 \notag\\
%& \leq & \left[ \frac{1}{n} \sum_{i=1}^n \left| (\tilde D^{n} _\bfX (\bfx_i))^2  - (\tilde D_\bfX (\bfx_i))^2 \right|^2 \right] \left[ \frac{1}{n} \left( \sqrt n.\frac{1}{n} \sum_{i=1}^n  SS(\bfx, \hat\bfmu_n) \right) \right]
%\end{eqnarray}
%%
%with $\hat S_n = \sum_{i=1}^n SS(\bfx_i, \hat\bfmu_n)/ \sqrt n$.
Now due to the assumption of uniform convergence, given $\epsilon>0$ we can find $N \in \mathbb{N}$ such that
%
\begin{equation}
\label{equation:lemma1eq}
| (\tilde D^{n_1}_\bfX(\bfx_i))^2 - (\tilde D_\bfX(\bfx_i))^2 | < \epsilon
\end{equation}
%
for all $n_1 \geq N; i = 1,2,...,n_1$. This implies
%
\begin{eqnarray}
\label{eqn:lemma1eq2}
S_{n_1} &< & \epsilon \sqrt{n_1} \left[ \frac{1}{n_1} \sum_{i=1}^{n_1} SS(\bfx_i; \hat\bfmu_{n_1}) \right]\notag\\
&=& \epsilon \sqrt{n_1} \left[ \frac{1}{n_1} \sum_{i=1}^{n_1} \left\{ SS(\bfx_i; \hat\bfmu_{n_1}) - SS(\bfx_i; \bfmu) \right\} + \frac{1}{n_1} \sum_{i=1}^{n_1} SS(\bfx_i; \bfmu) \right]
\end{eqnarray}

We now construct a sequence of positive definite matrices $\{A_k (B_k+C_k) : k \in \mathbb N\} $ so that
%
$$ A_k = \frac{1}{k}, \quad B_k = \sqrt{N_k} \left[ \frac{1}{N_k} \sum_{i=1}^{N_k} \left\{ SS(\bfx_i; \hat\bfmu_{N_k}) - SS(\bfx_i; \bfmu) \right\} \right]$$
$$\quad C_k = \sqrt{N_k} \left[ \frac{1}{N_k} \sum_{i=1}^{N_k} SS(\bfx_i; \bfmu) \right] $$
%
where $N_k \in \mathbb N$ gives the relation (\ref{equation:lemma1eq}) in place of $N$ when we take $\epsilon = 1/k$. Under conditions $ E\|\bfx - \bfmu\|^{-3/2} < \infty $ and $\sqrt n (\hat\bfmu_n - \bfmu) = O_P(1)$, the sample SCM with unknown location parameter $\hat\bfmu_n$ has the same asymptotic distribution as the SCM with known location $\bfmu$ \citep{durre14}, hence $B_k = o_P(1)$, thus $A_k (B_k+C_k) \stackrel{P}{\rightarrow} 0$.

Now (\ref{eqn:lemma1eq2}) implies that for any $\epsilon_1 > 0$, $S_{N_k} > \epsilon_1 \Rightarrow A_k (B_k + C_k) > \epsilon_1$, which means $ P(S_{N_k} > \epsilon_1) < P(A_k (B_k + C_k) > \epsilon_1)$. Hence the subsequence $\{S_{N_k}\} \stackrel{P}{\rightarrow} 0$. Since the main sequence $\{S_k\}$ is bounded below by 0, this implies $\{S_k\} \stackrel{P}{\rightarrow} 0$. Finally, we have that
%
\begin{eqnarray}
\sqrt n \left[
\frac{1}{n} \sum_{i=1}^n (\tilde D^n_\bfX (\bfx_i))^2 SS(\bfx_i; \hat\bfmu_n) -
\frac{1}{n} \sum_{i=1}^n (\tilde D_\bfX (\bfx_i))^2 SS(\bfx_i; \bfmu) \right] &\leq & \hspace{1em} \notag\\
S_n +  \sqrt{n} \left[ \frac{1}{n} \sum_{i=1}^{n} \left\{ SS(\bfx_i; \hat\bfmu_{n}) - SS(\bfx_i; \bfmu) \right\} \right] &&
\end{eqnarray}
%
Since the second summand on the right hand side is $o_P(1)$ due to \cite{durre14} as mentioned before, we have the needed.
\end{proof}

\begin{proof}[Proof of Theorem \ref{Theorem:rootn}]
The quantity in the statement of the theorem can be broken down as:
%
\begin{eqnarray*}
\sqrt n \left[ vec\left\{ \frac{1}{n} \sum_{i=1}^n (\tilde D^n_\bfX (\bfx_i))^2 SS(\bfx_i; \hat\bfmu_n) \right\} - vec\left\{ \frac{1}{n} \sum_{i=1}^n (\tilde D_\bfX (\bfx_i))^2 SS(\bfx_i; \bfmu) \right\} \right] +\\
\sqrt n \left[ vec\left\{ \frac{1}{n} \sum_{i=1}^n (\tilde D_\bfX (\bfx_i))^2 SS(\bfx_i; \bfmu) \right\} - E \left[ vec\left\{ (\tilde D_\bfX (\bfx))^2 SS(\bfx; \bfmu) \right\} \right] \right]
\end{eqnarray*}
%
The first part goes to 0 in probability by Lemma \ref{Lemma:lemma1}, and applying Slutsky's theorem we get the required convergence.
\end{proof}

\begin{proof}[Proof of Theorem \ref{Thm:pluginSigma}]
We are going to prove the following:
%
\begin{enumerate}
\item $\| \hat\Gamma_D - \Gamma \|_F \stackrel{P}{\rightarrow} 0$, and

\item $\| \hat\Lambda - \Lambda \|_F \stackrel{P}{\rightarrow} 0$
\end{enumerate}
%
as $n \rightarrow \infty$. For (1), we notice $\sqrt n vec(\hat\Gamma_D - \Gamma)$ asymptotically has a (singular) multivariate normal distribution following Corollary \ref{Corollary:eigendist}, so that $\| \hat\Gamma_D - \Gamma \|_F = O_P(1/\sqrt n)$ using Prokhorov's theorem.

It is now enough to prove convergence in probability of the individual eigenvalue estimates $\hat\lambda_i; i = 1,...,p$. For this, define estimates $\tilde\lambda_i$ as median-of-small-variances estimator of the \textit{true} score vectors $\Gamma^T X$. For this we have
%
\begin{equation}\label{eqn:PluginSigmaProof1}
| \tilde\lambda_i - \lambda_i | \stackrel{P}{\rightarrow} 0
\end{equation}
%
using Theorem 3.1 of \cite{Minsker15}, with $\mu = \lambda_i$. Now $ \hat\lambda_i = \text{med}_j (Var( X_{G_j}^T \hat\bfgamma_{D,i} ))$ and $\tilde\lambda_i = \text{med}_j (Var( X_{G_j}^T \bfgamma_i )) $, so that
%
\begin{eqnarray*}
| \hat\lambda_i - \tilde\lambda_i | &\leq & \text{med}_j \left[ Var( X_{G_j}^T ( \hat\bfgamma_{D,i} - \bfgamma_i) ) \right]
\\ &\leq & \| \hat\bfgamma_{D,i} - \bfgamma_i \|^2 \text{med}_j  \left[ \text{Tr} (Cov ( X_{G_j})) \right]
\end{eqnarray*}
%
using Cauchy-Schwarz inequality. Combining the facts $ \| \hat\bfgamma_{D,i} - \bfgamma_i \| = O_P(1/\sqrt n)$ and $ \text{med}_j  [ \text{Tr} (Cov ( X_{G_j})) ] \stackrel{P}{\rightarrow} \text{Tr}(\Sigma)$ \citep{Minsker15} with (\ref{eqn:PluginSigmaProof1}), we get the needed.

\end{proof}

### 2018-03-20 MS-new/KSP_12_29_15_1.tex
first commit in shubhobm

\documentclass[12pt,letterpaper]{article}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{authblk}
\usepackage{color}
\usepackage{epsfig}
\usepackage{graphics}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{pdflscape}
\usepackage{setspace}
\usepackage{soul}
\usepackage{subfigure}
% \usepackage{tikz}
\usepackage{verbatim}
% \usepackage{amsmath,amssymb,amsthm}
% \usepackage{rotating}
\usepackage{wrapfig}
%\usepackage{fullpage}
\usepackage{natbib}
\usepackage{mycommands}

%\newcommand{\BE}{\mathbb{E}}
%\newcommand{\BI}{\mathbb{I}}
%\newcommand{\BR}{\mathbb{R}}
%\newcommand{\BV}{\mathbb{V}}
%
%
%\newcommand{\cX}{\mathcal{X}}

\def\baq#1\eaq{\begin{align}#1\end{align}}
\def\ban#1\ean{\begin{align*}#1\end{align*}}
\def\bredbf#1\eredbf{{\color{red}{\bf ???? #1 ????}}}

\newtheorem{Theorem}{Theorem}[section]
\newtheorem{Lemma}[Theorem]{Lemma}
\newtheorem{Corollary}[Theorem]{Corollary}
\newtheorem{Proposition}[Theorem]{Proposition}
\newtheorem{Conjecture}[Theorem]{Conjecture}
\theoremstyle{definition} \newtheorem{Definition}[Theorem]{Definition}

%\voffset=0.5in
\renewcommand{\baselinestretch}{1.1}

\pagestyle{myheadings}
\markboth{}{\underline{{\bf Notes: (do not circulate)} \hspace{4.5cm} {\sc  Ansu Chatterjee} \hspace{0.25cm}}}

\begin{document}
\bibliographystyle{plain}
\makeatletter
\def\@oddfoot{[\jobname (\today)]\hfil\thepage}
\makeatother

\title{Robust methods for Hilbert-valued (not really) data based kernel signed peripherality 
transformations}

\title{Robust methods  based on the kernel signed peripherality 
transformations}

\section{Introduction}

\bredbf
I will write this section once the rest of the work is complete
\eredbf

We consider data $X_{1}, \ldots, X_{n}$ from some set $\cX \subseteq \BR^{p}$. 
We consider two functions defined below. First, we consider the 
{\it sign function} $S : \BR^{p} \times \BR^{p} \rightarrow \BR^{p}$ for any 
$p$-dimensional vector, defined as 
\ban
S (x; \mu_{x}) = || x - \mu_{x} ||^{-1} (x - \mu_{x}) \mathcal{I}_{ \{ x \ne 0 \}}. 
\ean
This sign function is defined with respect to the {\it location parameter} 
$\mu_{x} \in \BR^{p}$. This is a direct multivariate generalization of the 
univariate $ p = 1$ case of the indicator of whether the point $x$ is to the right, 
left or at $\mu_{x}$. This function has been used many times in statistics, see
\bredbf insert several references. \eredbf

Suppose $\mathcal{F}_{p}$ is the set of all probability 
measures on $\BR^{p}$. The second function we consider is the {\it peripherality function} 
$ P : \BR^{p} \times \mathcal{F}_{p} \rightarrow \BR$, which, for every 
$x \in \BR^{p}$ and every probability measure $F \in \mathcal{F}_{p}$, satisfies the 
condition
\ban 
& \text{ There exists a constant $\mu_{F} \in \BR^{p}$ such that} 
%\\
%& \hspace{0.25cm} 
\text{ for every $t \in [ 0, 1]$ and every } \\
& \hspace{0.5cm} \text{$x \in \BR^{p}$  we have} \ \ 
P \Bigl( \mu_{F} ; F \Bigr) \leq P \Bigl( \mu_{F} + t ( x - \mu_{F} ); F \Bigr). 
\ean 
That is, for every fixed $F$, the peripherality function achieves a minimum at 
$\mu_{F}$, and is non-decreasing in every direction away from $\mu_{F}$. If 
we impose the practical restriction that $\inf_{x} P ( x ; F )$ is bounded below, 
then we may as well impose without loss of generality $P ( \mu_{F} ; F ) = 0$
and consequently $P ( x ; F ) \geq 0$ for all $x \in \BR^{p}$ and 
$F \in \mathcal{F}_{p}$. The peripherality function quantifies whether the point $x$ 
is near or far from $\mu_{F}$. We will impose additional conditions on this function 
as we proceed, but it can be seem immediately that any distance measure between 
$x$ and $\mu_{F}$ satisfies the bare minimum requirement mentioned above.

In this paper, we demonstrate certain interesting applications arising from 
composing the sign function and the peripherality function together, to form the 
{\it signed-peripherality function} $\kappa (\cdot)$. We define this function 
with three parameters $\mu_{x} \in \BR^{p}$, $F \in \mathcal{F}_{p}$ and  
$\mu_{y} \in \BR^{p}$,  argument $x \in \BR^{p}$ and range $\BR^{p}$. More precisely, 
$\kappa : \BR^{p} \times \BR^{p} \times \mathcal{F}_{p} \times \BR^{p} \times 
\BR^{p} \rightarrow \BR^{p}$ is defined as 
\ban 
\kappa (x; \mu_{x}, F, \mu_{y} ) = S (x; \mu_{x}) P (x; F) + \mu_{y}. 
\ean

Notice that if we consider $\mu_{y} = \mu_{F} = \mu_{x}$ and take the very 
simple peripherality  function $P( x; F) = || x - \mu_{F} ||$, we have 
$\kappa (x; \mu_{x}, F, \mu_{y} ) \equiv x$ for all choices of parameters 
$\mu_{x}, F, \mu_{y}$.  Consequently, under this choice of parameters for the 
$\kappa$-transformation, analyzing a dataset $\{ X_{1}, \ldots, X_{n} \}$ and 
its $\kappa$-transformed version 
$\{ Y_{i} = \kappa (X_{i}; \ldots), \ i = 1, \ldots, n \}$ are equivalent. However,
in this paper we illustrate how other choices of the peripherality function 
lead to interesting robustness results. We have deliberately set the location 
parameters $\mu_{x}, \mu_{F}, \mu_{y}$ to be potentially non-identical, this 
additional flexibility has some advantage for robust data analysis. In many 
applications, the value of these three parameters may be identical, which leads 
to no conflict in our framework.

A whole class of peripherality functions can be defined from {\it data - depth},  which are center-outward ranking of multivariate data. Data-depths have been extensively used in statistics also, see \bredbf multiple references. \eredbf Peripherality functions can be defined as some inverse ranking based on data depth, and the concept of {\it outlyingness} associated with data depth is essentially same as what we use in this paper. We use the term {\it peripherality} to keep track of the difference in application contexts and technical assumptions.

In this paper, we consider a few illustrative cases of the use of the $\kappa$-transformation. Suppose the data at hand is $X_{1}, \ldots, X_{n}$, and we define $Y_{i} = \kappa (X_{i}; \mu_{X}, F, \mu_{Y})$ for some choice of parameters $\mu_{X}, F, \mu_{Y}$. For interpretability and convenience, we assume that $\BE S ( X_{i}; \mu_{X}) P ( X_{i}; F) = 0$, thus $\BE Y_{i} = \mu_{Y}$. We thus have 
\ban 
\BV Y_{i} 
& = \BE P ( X_{i}; F)^{2} S ( X_{i}; \mu_{X}) S ( X_{i}; \mu_{X})^{T} \\
& = \BE P ( X_{i}; F)^{2} || X_{i} - \mu_{X} ||^{-2} 
( X_{i} - \mu_{X} ) (X_{i} - \mu_{X})^{T}.
\ean

\bredbf Need to include (a) Biman-PC idea for affine equivariance for $p \ll n$, (b) kernel versions as an example of generalization. (c) anything else? \eredbf

%\section{Testing for a location parameter}
%
%Suppose $W \in \{ 0, 1 \}$, $Z \in \BR^{p}$ and $U \in \BR^{p}$ 
%are independent  random variables, with 
%$W$ having a Bernoulli distribution with parameter $\theta$, 
%and each 
%element of $U$ is an independent standard Cauchy random variable. 
%The random vector $Z$ follows a mean-zero, variance matrix $\Sigma$ Normal distribution 
%$Z \sim N_{p} (0, \Sigma)$. Our choices of $\Sigma$ in the details 
%below include 
%cases where $Cov (Z_{i}, Z_{j}) = \rho^{ | i - j|}$ for some $\rho \in [0, 1)$
%which includes as special case the identity matrix $\BI_{p}$ corresponding to 
%$\rho = 0$, and where $Cov (Z_{i}, Z_{j}) = \rho$. 
%
%We define $X = \mu + W Z + (1 - W) U$, and let the observed data be 
%independent, identically distributed copies $X_{1}, \ldots, X_{n}$ copies of $X$. 
%Note that the conditional distribution of $(X | W = 0)$ does not have finite moments.
%Suppose our goal is to conduct inference on $\mu$, in particular, to test the hypothesis 
%that $\mu = 0 \in \BR^{p}$. 
%The sample mean and variance from the observed data $X_{1}, \ldots, X_{n}$, 
%denoted respectively by $\bar{X} = n^{-1} \sum_{i = 1}^{n} X_{i}$ and
%$S_{X} = (n - 1)^{-1} \sum_{i = 1}^{n} ( X_{i} - \bar{X} )( X_{i} - \bar{X} )^{T}$. 
%These are 
%well-defined quantities, even though their expectations may not exist.
%Assume $p < n$, and thus $S_{x}$ is invertible. 
%
%
%One option for inference on $\mu$ is to ignore the heavy-tailed component of 
%the data, and to use Hotteling's $T^{2}$ statistic given by 
%$T^{2} = n (\bar{X} - \mu_{0})^{T} S_{X}^{-1} (\bar{X} - \mu_{0})$. 
%
%Other, more robust options, is to use the sign function exclusively, 
%or any variety of data-depth functions exclusively. 
%\bredbf suggest 2 or 3 depth functions used earlier for one-sample mean 
%testing, provide references. List details on how these methods would be implemented,
%just do what these references do
% \eredbf
%
%Another alternative is to use the $\kappa$-transformation proposed in this paper. 
%We begin with a robust estimator of $\mu$, for example the co-ordinatewise median, 
%to use as $\mu_{X}$ and $\mu_{F}$. As $F$, we use the $p$-dimensional Normal 
%distribution with mean $\mu_{F}$ and identity covariance matrix. One simple
%peripherality function is $ || x - mu_{F} ||/ (1 + || x - mu_{F} ||)$, which 
%is bounded above and below and achieves a minima at $\mu_{F}$. We take $\mu_{Y}$ 
%to be $\mu$ also, and we may again use the co-ordinatewise median or a different 
%statistic as its estimator like simple sample mean of $Y_{i} = \kappa (X_{i})$.
%(Use the sample mean: we want to sell the idea that after the kappa transformation 
%all standard classical methods like sample moments can be used).
%
%
%We should be able to show that 
%\begin{enumerate}
%
%\item Classical methods like Hotteling is a disaster because of outliers.
%
%\item Sign and depth-based methods lack power, which becomes quite bad when $\rho$ 
%is considerably away from zero.
%
%
%\end{enumerate}
%
%
%\section{Testing for equality of two location parameters}
%
%You know how to develop this. Do both the two sample and paired sample case.
%
%Show simulation results like above.

\section{Develop a robust estimator of variance}
Simply do sample variance of the transformed variables $Y_{i} = \kappa (X_{i})$.

Show simulation results like above.

\section{Outlier detection}

Expand and generalize what you have in the paper already, where I think this is a small 
example. Refer to a standard method for multivariate outlier detection, and show that 
such a method used on $Y_{i} = \kappa (X_{i})$ works. I will send you some papers for 
referencing in this part.

\section{Robust principal component analysis}

This will be one of the bigger and 
 major sections of the paper, essentially copied and pasted
 from the previous version. Don't do anything here as of now.

%\section{Robust Hawkins-regression}
%
%Consider the $p + 1$ dimensional data $\{ 
%(\mathbf{X}_{i} \ Y_{i})^{T} \in \BR^{p +1}, \ i =1, \ldots, n \}$. 
%Do the robust PCA on this, and get all the eigenvectors. The typical eigenvector looks 
%like $( \mathbf{\gamma} \ \gamma_{0} ) \in \BR^{p +1}$. Under the condition that the 
%joint distribution of $(\mathbf{X} \ Y)^{T}$ is absolutely continuous, we have 
%$\gamma_{0} \ne 0$ almost surely. We implement the following for any estimated 
%eigenvector where $|\gamma_{0} | > \epsilon$ for some fixed $\epsilon > 0$: 
%multiply the eigenvector by  $-\gamma_{0}^{-1}$, thus consider 
%$( -\gamma_{0}^{-1} \mathbf{\gamma} \ -1 ) \in \BR^{p +1}$, which is a 
%"Hawkins-regression". The  variance of this linear 
%combination of variables is given by the corresponding eigenvalue times 
%$\gamma_{0}^{-2}$, which may be small or large in the $p + 1$ eigenvectors, so the order 
%in which eigenvalues/vectors appear in PCA may not be maintained here. 
%
%Also look up what Hawkins had originally proposed, and implement those. 
%
%Do a simple simulation, building on the simulation you have for the previous 
%section.

\section{Robust PCA and supervised models}

In the presence of a vector of univariate responses, say $\bfY = (Y_1,Y_2,...,Y_n)^T$, there is substantial literature devoted to utilizing the subspace generated by the basis of $Cov(\bfX)$ in modelling $E(Y|\bfX)$. This ranges from the simple Principal Components Regression (PCR) to Partial Least Squares (PLS) and Envelope methods \citep{Cook10}. Here we concentrate on robust inference using Sufficient Dimension Reduction (SDR) \citep{AdragniCook09}, mainly because it provides a general framework for reducing dimensionality of data directly using top eigenvectors of the covariance matrix of $X$ (albeit in a different manner than PCR) or an appropriate affine transformation of it.

SDR attempts to find out a linear transformation $R$ on $\bfX$ such that $E(Y|\bfX) = E(Y|R(\bfX))$. Assuming that $R(\bfX)$ takes values in $\mathbb R^d, d \leq \min(n,p)$, this can be achieved through an inverse regression model:
%
\begin{equation}
\bfX_y = \bar \bfmu + \Gamma \bfv_y + \bfepsilon
\end{equation}
%
where $\bfX_y = \bfX|Y=y, \bar\bfmu = E\bfX$, $\Gamma$ is a $p \times d$ semi-orthogonal basis for $\mathcal S_\Gamma$, the spanning subspace of $\{ E \bfX_y - \bar\bfmu | y \in S _Y \}$ ($S_y$ is sample space of $Y$) and $\bfv_y = (\Gamma^T \Gamma)^{-1} \Gamma^T (E \bfX_y - \bar\bfmu) \in \mathbb R^d$. The random error term $\bfepsilon$ follows a multivariate normal distribution with mean ${\bf 0}_p$ and covariance matrix $\Delta$. This formulation is straightforward to implement when $Y$ is categorical, while for continuous responses, the vector $\bfy$ is divided into a number of slices.

Under this model the minimal sufficient transformation is $R(\bfX) = \Gamma^T \Delta^{-1} \bfX$. The simplest case of this model is when $\Delta = \sigma^2 I_p$, for which the maximum likelihood estimator of $ R(\bfX)$ turns out to be the first $d$ PCs of $Cov(\bfX)$. Taking $\hat E\bfX_y = \bar\bfX_y$ and $\hat{\bar\bfmu} = \bar\bfX$, one can now estimate $\sigma^2$ as: $\hat\sigma^2 = \sum_{i=1}^p s_{ii}/p$, where $s_{ii}$ is the $i^\text{th}$ diagonal element of $\hat{Cov}_Y( \bfX_Y - \bar\bfX - \hat\Gamma \hat\bfv_Y)$. Following this, predictions for a new observation $\bfx$ is obtained as a weighted sum of the responses:
%
$$
\hat E(Y|\bfX=\bfx) = \frac{\sum_{i=1}^n w_i Y_i}{\sum_{i=1}^n w_i}; \quad w_i = \exp \left[ -\frac{1}{\hat\sigma^2}  \| \hat\Gamma^T (\bfx - \bfX_i) \|^2 \right]
$$
%

We formulate a robust version of the above procedure by estimating the quantities $\Gamma, \bar\bfmu, \bfmu_y, \sigma^2$ by robust methods. Specifically, we take:
%
\begin{itemize}
\item $\tilde \Gamma = $ first $d$ eigenvectors of the sample DCM;
%
\item $\tilde{\bar\bfmu} = $ spatial median of the rows of $X$;
%
\item $\tilde \bfmu_y = $ spatial median of the rows of $(X|Y=y)$, for all $y \in S_Y$;
%
\item $\tilde\sigma^2 = \sum_{i=1}^p \tilde\lambda_i/p$, where $\tilde\lambda_i$ are the median-of-small-variances estimator for $X_{Y,i} - \tilde{\bar\mu}_i - \tilde\bfgamma_i^T \tilde\bfv_Y$, with $\tilde\Gamma = (\tilde\bfgamma_1, ..., \tilde\bfgamma_p)^T$.
\end{itemize}
%
The following simulation study using the same setup as in \citep{AdragniCook09} compares the performance of our robust SDR with the original method with or without the presence of bad leverage points in the covariate matrix $X$. For a fixed dimension $p$, we take $n=200, d=1$, generate the responses $Y$ as independent standard normal, and the predictors as $\bfX_Y = \bfgamma^* v_Y^* + \bfepsilon$, with $\bfgamma^*_{p\times 1} = (1,...,1)^T, v_Y = Y + Y^2 + Y^3$ and $Var(\bfepsilon) = 25 I_p$. We measure performance of both SDR models by their mean squared prediction error on another set of 200 observations $(Y^*, \bfX^*)$ generated similarly, and taking the average of these errors on 100 such training-test pair of datasets. Finally we repeat the whole setup for different choices of $p = 5,10,25,50,75,100,125,150$.

\begin{figure}[t]
%\captionsetup{justification=centering, font=footnotesize}
\begin{center}
\subfigure[]{\epsfxsize=0.35\linewidth \epsfbox{../Codes/SDRcomparison_noout}}
\subfigure[]{\epsfxsize=0.35\linewidth \epsfbox{../Codes/SDRcomparison_out}}
\caption{Average prediction errors for two methods of SDR (a) in absence and (b) in presence of outliers}
\label{fig:SDRfig}
\end{center}
\end{figure}

Panel (a) of figure \ref{fig:SDRfig} compares prediction errors using robust and maximum likelihood SDR estimates when $X$ contains no outliers, and the two methods are virtually indistinguishable. We now introduce outliers in each of the 100 datasets by adding 100 to first $p/5$ coordinates of the first 10 observations in $X$, and repeat the analysis. Panel (b) of the figure shows that although our robust method performs slightly worse than the case when there were no outliers, it remains more accurate in predicting our of sample observations for all values of $p$.

\section{Robust inference with functional data}

This section is to show something beyond the $p \ll n$ setting. Both robust PCA 
and location testing are important problems for functional data. Abhirup can 
take charge of this part once we have everything else settled.

The main idea here is to use any decent location estimator to start with (some 
version of median is fine). Then we may test if the functional location for resting 
and active state are identical or not.

Also do functional PCA robust version, and then maybe project the data on the first few
principal components and then do the 2 sample (or paired sampel) testing again.

(Some technical notations)

We use the approach of \cite{BoenteBarrera15} for performing robust PCA on functional data. Given data on $n$ functions, say $f_1, f_2, ..., f_n \in L^2[0,1]$, each observed at a set of common design points $\{ t_1, ..., t_m \} $, we model each function as a linear combination of $p$ mutually orthogonal B-spline basis functions $\delta_1, ..., \delta_p$. Following this, we map data for each of the functions onto the coordinate system formed by the spline basis:
%
\begin{equation}
\tilde x_{ij} = \sum_{l=2}^m f_i(t_l) \delta_j(t_l) (t_l - t_{l-1}); \quad 1 \leq i \leq n, 1 \leq j \leq p
\end{equation}
%
We now do depth-based PCA on the transformed $n \times p$ data matrix $\tilde X$, and obtain the rank-$q$ approximation ($q \leq p$) of the $i^\text{th}$ observation using the robust $p \times q$ loading matrix $\tilde P$ and robust $q \times 1$ score vector $\tilde\bfs_i$:
%
$$ \widehat{\tilde\bfx_i} = \tilde\bfmu + \tilde P \tilde \bfs_i $$
%
with $\tilde\bfmu$ being the spatial median of $\tilde X$. Then we transform this approximation back to the original coordinates: $\hat f_i (t_l) = \sum_{j=1}^p \widehat{ \tilde x}_{ij} \delta_j (t_l)$.

Detection of anomalous observations is of importance in real-life problems involving functional data analysis. We now demonstrate the utility of our robust method for detecting functional outliers through two data examples.

\textbf{(SD and OD definition, cutoffs... from previous manuscript)
}

\begin{figure}[t]
%\captionsetup{justification=centering, font=footnotesize}
\begin{center}
\subfigure[]{\epsfxsize=.32\linewidth\epsfbox{../Codes/Elnino_functional1}}
\subfigure[]{\epsfxsize=.32\linewidth\epsfbox{../Codes/Elnino_functional2}}
\subfigure[]{\epsfxsize=.32\linewidth\epsfbox{../Codes/Elnino_functional3}}\\
\vspace{-1em}
\subfigure[]{\epsfxsize=.32\linewidth\epsfbox{../Codes/Octane_functional1}}
\subfigure[]{\epsfxsize=.32\linewidth\epsfbox{../Codes/Octane_functional2}}
\subfigure[]{\epsfxsize=.32\linewidth\epsfbox{../Codes/Octane_functional3}}
%\subfigure[]{\epsfxsize=0.35\linewidth \epsfbox{../Codes/SDRcomparison_out}}
\caption{Actual sample curves, their spline approximations and diagnostic plots respectively for El-Ni\~no (a-c) and Octane (d-f) datasets}
\label{fig:fPCAfig}
\end{center}
\end{figure}

We first look into the El-Ni\~no data, which is part of a larger dataset on potential factors behind El-Ni\~no oscillations in the tropical pacific available in \url{http://www.cpc.ncep.noaa.gov/data/indices/}. This records monthly average Sea Surface Temperatures from June 1970 to May 2004, and the yearly oscillations follow more or less the same pattern (see panel a of figure \ref{fig:fPCAfig}). Using a cubic spline basis with knots at alternate months starting in June gives a close approximation of the yearly time series data (panel b), and performing depth-based PCA with $q=1$ results in two points having their SD and OD larger than cutoff (panel c). These points correspond to the time periods June 1982 to May 1983 and June 1997 to May 1998 are marked by black curves in panels a and b), and pinpoint the two seasons with strongest El-Ni\~no events.

Our second application is on the Octane data, which consists of 226 variables and 39 observations \citep{esbensen94}. Each sample is a gasoline compound with a certain octane number, and has its NIR absorbance spectra measured in 2 nm intervals between 1100 - 1550 nm. There are 6 outliers here: compounds 25, 26 and 36-39, which contain alcohol. We use the same basis structure as the one in El-Ni\~no data here, and again the top robust PC turns out to be sufficient in identifying all 6 outliers (panels d, e and f of figure \ref{fig:fPCAfig}).

\section{An example with images}

\section{A depth-based M estimate of scatter}

\subsection{Formulation}
The DCM is orthogonally equivariant and remains constant only under rotations of the original variables. To construct its affine equivariant counterpart, we need to follow the general framework of M-estimation with data-dependent weights \cite{HuberBook81}. Specifically, we first implicitly define the Affine-equivariant Depth Covariance Matrix (ADCM) as
%
\begin{equation} \label{eqn:ADCM}
\Sigma_{Dw} = \frac{1}{Var (\tilde Z_1) } E \left[ \frac{(\tilde D_\bfX(\bfx))^2 (\bfx - \bfmu) (\bfx - \bfmu)^T}{(\bfx - \bfmu)^T \Sigma_{Dw}^{-1} (\bfx - \bfmu)} \right]
\end{equation}
%
Its affine equivariance follows from the fact that the weights $(\tilde D_\bfX (\bfx))^2$ depend only on the standardized quantities $\bfz$ that depend only on the underlying spherical distribution $G$. We solve this iteratively by obtaining a sequence of positive definite matrices $\Sigma^{(k)}_{Dw}$ until convergence:
%
$$ \Sigma^{(k+1)}_{Dw} = \frac{1}{Var (\tilde Z_1) } E \left[ \frac{(\tilde D_\bfX(\bfx))^2 (\Sigma^{(k)}_{Dw})^{1/2} (\bfx - \bfmu) (\bfx - \bfmu)^T (\Sigma^{(k)}_{Dw})^{1/2}}{(\bfx - \bfmu)^T (\Sigma^{(k)}_{Dw})^{-1} (\bfx - \bfmu)} \right] $$
%

To ensure existence and uniqueness of the estimator in \ref{eqn:ADCM}, let us consider the class of scatter estimators $\Sigma_M$ that are obtained as solutions of the following equation:
%
\begin{equation}
E_{\bfZ_M} \left[ u( \| \bfz_M \| )  \frac{\bfz_M \bfz_M^T}{\| \bfz_M \|^2}  - v( \| \bfz_M \| ) I_p \right] = 0
\end{equation}
%
with $\bfz_M = \Sigma_M^{-1/2} (\bfx - \bfmu)$. Under the following assumptions on the scalar valued functions $u$ and $v$, the above equation produces a unique solution \citep{HuberBook81}:
%

\vspace{1em}
\noindent\textbf{(M1)} The function $u(r)/r^2$ is monotone decreasing, and $u(r)>0$ for $r>0$;

\noindent\textbf{(M2)}  The function $v(r)$ is monotone decreasing, and $v(r)>0$ for $r>0$;

\noindent\textbf{(M3)} Both $u(r)$ and $v(r)$ are bounded and continuous;

\noindent\textbf{(M4)} $u(0) / v(0) < p$;

\noindent\textbf{(M5)} For any hyperplane in the sample space $\mathcal X$, (i) $P(H) = E_\bfX 1_{\bfx \in H} < 1 - p v(\infty) / u(\infty)$ and (ii) $P(H) \leq 1/p$.
%

\vspace{1em}
\noindent In our case we take $v(r) = Var(\tilde Z_1)$, i.e. a constant, thus (M2) and (M3) are trivially satisfied. As for $u$, we notice that most well-known depth functions can be expressed as simple functions of the norm of the standardized random variable. For example, $PD_\bfZ (\bfz) = (1 - G(\| \bfz \|); MhD_\bfZ (\bfz) = (1+\| \bfz \|^2)^{-1}; HSD_\bfZ (\bfz) = (1+\| \bfz \|)^{-1}$ etc., so that we can take as $u$ square of the corresponding peripherality functions:
% Var(Z1) breaks into two independent parts: depth and sign. So can check m4 and M5 here itself.
$$
u_{PD} (r) = G^2 (r); \quad u_{MhD}(r)  = \frac{r^4}{(1 + r^2)^2}; \quad u_{HSD}(r)  = \frac{r^2}{(1 + r/G^{-1}(0.75))^2}
$$
%

It is easy to verify the above choices of $u$ satisfy (M1) and (M3). To check (M4) and (M5), first notice that $\bfZ$ has a spherically symmetric distribution, so that its norm and sign are independent. Since $D_\bfZ(\bfz)$ depends only on $\| \bfz \|$, we have
%
$$
Var (\tilde Z_1) = Var \left( \tilde D_\bfZ (\bfZ) \frac{Z_1}{ \|\bfZ \|} \right) = Var (\tilde D_\bfZ (\bfZ)) Var (S_1 (\bfZ)) = \frac{1}{p} Var (\tilde D_\bfZ (\bfZ))
$$
%
as $Cov(\bfS(\bfZ)) = Cov((S_1(\bfZ), S_2(\bfZ), ..., S_p(\bfZ))^T) = I_p/p$. Now for MhD and HSD $u(\infty)=1, u(0)=0$, so (M4) and (M5) are immediate. To achieve this for PD, we only need to replace $u_{PD}(r)$ with $u_{PD}^*(r) = G^2(r) - 1/4$.

\subsection{Calculation}
(Comes right after the calculations discussion of DCM)

In contrast to the DCM, the issue of estimating $\bfmu$ to plug into the ADCM is easily handled by simultaneously solving for the location and scatter functionals ($\bfmu_{Dw}, \Sigma_{Dw}$):
%
\begin{eqnarray}
E \left[ \tilde D_\bfX (\bfx) \frac{\Sigma_{Dw}^{-1/2} (\bfx - \bfmu_{Dw})}{ \| \Sigma_{Dw}^{-1/2}(\bfx - \bfmu_{Dw}) \|} \right] &=& {\bf 0}_p \label{eqn:AffineMedian}\\
E \left[ \frac{(\tilde D_\bfX(\bfx))^2 \Sigma_{Dw}^{-1/2} (\bfx - \bfmu_{Dw}) (\bfx - \bfmu_{Dw})^T \Sigma_{Dw}^{-1/2}}{(\bfx - \bfmu_{Dw})^T \Sigma_{Dw}^{-1} (\bfx - \bfmu_{Dw})} \right] &=& Var (\tilde Z_1) I_p \label{eqn:AffineCov}
\end{eqnarray}
%
In the framework of (\ref{eqn:ADCM}), for any fixed $\Sigma_M$ there exists a unique and fixed solution of the location problem $E_{\bfZ_M} (w(\| \bfz_M \| \bfz_M) = {\bf 0}_p $ under the following condition:

\vspace{1em}
\noindent\textbf{(M6)} The function $w(r)r$ is monotone increasing for $r>0$.

\vspace{1em}
\noindent This condition is easy to verify for our choice of the weights: $w(\| \bfz_M \| ) = \tilde D_{\bfZ_M} (\bfz_M) / \| \bfz_M \|$. Uniqueness of simultaneous fixed point solutions of \ref{eqn:AffineMedian} and \ref{eqn:AffineCov} is guaranteed when $\bfX$ has a symmetric distribution \citep{HuberBook81}.

In practice it is difficult to calculate the scale multiple $Var (\tilde Z_1)$ analytically for known depth functions and an arbitrary $F$. Here we instead obtain its standardized version $\Sigma_{Dw}^* = \Sigma_{Dw} / Var(\tilde Z_1)$ (so that the determinant equals 1), alongwith $\bfmu_{Dw}$ using the following iterative algorithm:

\begin{enumerate}
\item Start from some initial estimates $(\bfmu_{Dw}^{(0)}, \Sigma_{Dw,(0)})$. Set $t=0$;

\item Calculate the standardized observations $\bfz_i^{(t)} = \Sigma_{Dw,(t)}^{-1/2} (\bfx_i - \bfmu_{Dw}^{(t)})$;

\item Update the location estimate:
%
$$
\bfmu_{Dw}^{(t+1)} = \frac{\sum_{i=1}^n \tilde D_\bfX (\bfx_i) \bfx_i / \| \bfz_i^{(t)} \| }{\sum_{i=1}^n \tilde D_\bfX (\bfx_i) / \| \bfz_i^{(t)} \|}
$$
%
\item Update the scatter estimate:
%
$$
\Sigma_{Dw}^{*(t+1)} = \frac{1}{n} \sum_{i=1}^n \frac{(\tilde D_\bfX (\bfx_i))^2 (\bfx_i - \bfmu_{Dw}^{(t+1)})(\bfx_i - \bfmu_{Dw}^{(t+1)})^T}{\| \bfz_i^{(t)} \|^2}; \quad \Sigma_{Dw}^{*(t+1)} \leftarrow \frac{\Sigma_{Dw}^{*(t+1)}}{\text{det} (\Sigma_{Dw}^{*(t+1)})^{1/p}}
$$
%
\item Continue until convergence.
\end{enumerate}

\subsection{Influence functions}
The influence function of any affine equivariant estimate of scatter can be expressed as
%
$$
IF(\bfx_0, C, F) = \alpha_C (\| \bfz_0 \| ) \frac{\bfz_0 \bfz_0^T}{\bfz_0^T \bfz_0} - \beta_C( \| \bfz_0 \| ) C
$$
%
for scalar valued functions $\alpha_C, \beta_C$ \citep{HampelBook86}. Following this, the influence function of an eigenvector $\bfgamma_{C,i}$ of $C$ is derived:
%
$$
IF(\bfx_0, \bfgamma_{C,i}, F) = \alpha_C(\| \bfz_0 \|) \sum_{k=1, k \neq i}^p \frac{\sqrt {\lambda_i \lambda_k}}{\lambda_i - \lambda_k}. \frac{z_{0i} z_{0k}}{\bfz_0^T \bfz_0} \bfgamma_k
$$
%
For Tyler's estimate of scatter, we have $\alpha_C (\| \bfz_0 \|) = p+2$. Considering a more general case, when $C=\Sigma_M$, i.e. the solution to (\ref{eqn:ADCM}), then \cite{HuberBook81} shows that
%
$$
\alpha_C (\| \bfz_0 \|) = \frac{p(p+2) u (\| \bfz_0 \|)}{E_{F_0} \left[ p u(\| \bfy \| ) + u'(\| \bfy \|) \| \bfy \| \right] }
$$
%
Setting $u( \| \bfz_0 \|) = ( \tilde D_\bfZ (\bfz_0))^2$ ensures that the influence function of eigenvectors of the ADCM is bounded as well as increaseing in magnitude with $\| \bfz_0 \|$.

\subsection{ARE calculations}

Obtaining ARE of the ADCM is, in comparison to DCM, more straightforward. The asymptotic covariance matrix of an eigenvector of the affine equivariant scatter functional $C$ is given by:
%
$$
AVar (\sqrt n  \hat\bfgamma_{C,j}) = ASV (C_{12}, F_0) \sum_{k=1, k \neq i}^p \frac{\lambda_i \lambda_k}{\lambda_i - \lambda_k}. \bfgamma_i \bfgamma_k^T
$$
%
where $ASV (C_{12}, F_0)$ is the asymptotic variance of an off-diagonal element of $C$ when the underlying distribution is $F_0$. Following \cite{croux00} this equals
%
$$
ASV (C_{12}, F_0) = E_{F_0} \left[ \alpha_c (\| \bfz \|)^2 (S_1(\bfz)S_2 (\bfz))^2 \right] = E_{F_0} \alpha_C (\| \bfz \|)^2 . E_{F_0} (S_1(\bfz)S_2 (\bfz))^2 
$$
% 
again using the fact that $\|\bfZ\|$ and $\bfS(\bfZ)$ are independent with $\bfZ \sim F_0$. When $C = Cov$, i.e. the sample covariance matrix, we have $\alpha_{Cov} (\| \bfz \|) = \| \bfz \|^2$. It now follows that
%
\begin{equation}
ARE (\hat\bfgamma_{\Sigma_M,i}, \hat\bfgamma_{Cov,i}) = \frac{E_{F_0} \alpha_{Cov} (\| \bfz \|)^2}{E_{F_0} \alpha_C (\| \bfz \|)^2} = \frac{E_{F_0} \| \bfz \|^4. \left[ E_{F_0} ( p u (\| \bfz\|) + u'( \| \bfz \|) \| \bfz \| ) \right]^2}{p^2 (p+2)^2 E_{F_0} (u(\| \bfz \|))^2}
\end{equation}
%

Table \ref{table:AREtable} considers 6 different elliptic distributions (namely, bivariate $t$ with df = 5, 6, 10, 15, 25 and bivariate normal) and summarizes ARE for first eigenvectors for ADCMs corresponding to projection depth (PD-ACM) and halfspace depth (HSD-ACM). Due to difficulty of analytically obtain the AREs, we calculate them using Monte-Carlo simulation of $10^6$ samples and subsequent numerical integration. The ADCM seems to be particularly efficient in lower dimensions for distributions with heavier tails ($t_5$ and $t_6$), while for distributions with lighter tails, the AREs increase with data dimension. At higher values of $p$ the ADCM is almost as efficient as the sample covarnace matrix when the data comes from multivariate normal distribution.

\begin{table}[t]
    \begin{tabular}{c|cccc|cccc}
    \hline
    & \multicolumn{4}{c|}{PD-ACM} & \multicolumn{4}{c}{HSD-ACM} \\\cline{2-9}
    Distribution & $p=2$  & $p=5$  & $p=10$ & $p=20$ & $p=2$  & $p=5$  & $p=10$ & $p=20$ \\ \hline
    $t_5$           & 4.73 & 3.99 & 3.46 & 3.26 & 4.18 & 3.63 & 3.36 & 3.15 \\
    $t_6$           & 2.97 & 3.28 & 2.49 & 2.36 & 2.59 & 2.45 & 2.37 & 2.32 \\
    $t_{10}$          & 1.45 & 1.47 & 1.49 & 1.52 & 1.30 & 1.37 & 1.43 & 1.49 \\
    $t_{15}$          & 1.15 & 1.19 & 1.23 & 1.27 & 1.01 & 1.10 & 1.17 & 1.24 \\
    $t_{25}$          & 0.97 & 1.02 & 1.07 & 1.11 & 0.85 & 0.94 & 1.02 & 1.08 \\
    MVN          & 0.77 & 0.84 & 0.89 & 0.93 & 0.68 & 0.77 & 0.84 & 0.91 \\ \hline
    \end{tabular}
    \caption{Table of AREs of the ADCM for different choices of $p$ and data-generating distributions, and two choices of depth functions}
    \label{table:AREtable}
\end{table}

\section{The robust location problem}
Consider the general situation of estimation or testing for the location parameter of an elliptical distribution using weighted sign vectors. For now the only condition we impose on these weights, say $w(.)$, is that they need to be scalar-valued affine equivariant and square-integrable functions of the data, or in other words functions of the norm of the standardized random variable $\bfZ$. In that sense $w(\bfX)$ can be equivalently written as $f(r)$, with $r = \| \bfZ \|$. The simplest use of weighted signs here would be to construct a robust alternative to the Hotelling's $T^2$ test using their sample mean vector and covariance matrix. Formally, this means testing for $H_0: \bfmu = {\bf 0}_p$ vs. $H_1:\bfmu \neq {\bf 0}_p$  based on the test statistic:
%
$$ T_{n,w} = n \bar\bfX_w^T ( Cov (X_w))^{-1} \bar\bfX_w $$
%
with $\bar\bfX_w = \sum_{i=1}^n \bfX_{w,i}/n$ and $\bfX_{w,i} = w(\bfX_i ) \bfS (\bfX_i)$ for $i=1,2,...,n$. However, the following holds true for this weighted sign test:
%
\begin{Proposition}\label{proposition:SignTest}
Consider $n$ random variables $Z = (\bfZ_1,...,\bfZ_n)^T$ distributed independently and identically as $\mathcal{E}( \bfmu, kI_p, G); k \in \mathbb R$, and the class of hypothesis tests defined above. Then, given any $\alpha \in (0,1)$, local power at $\bfmu \neq {\bf 0}_p$ for the level-$\alpha$ test  based on $T_{n,w}$ is maximum when $w(\bfZ_1) = c$, a constant independent of $\bfZ_1$.
\end{Proposition}
%
\noindent This essentially means that power-wise the (unweighted) spatial sign test \citep{OjaBook10} is optimal in the given class of hypothesis tests when the data comes from a spherically symmetric distribution. Our simulations show that this empirically holds for non-spherical but elliptic distributions as well.

\subsection{The weighted spatial median}

Our weight functions are affine equivariant functions of the data, i.e. they are not affected by the population location parameter $\bfmu$. This ensures that there exists a unique solution of the following of optimization problem:
%
$$
\bfmu_w = \text{arg}\min_{\bfmu_0 \in \mathbb{R}^p} E ( w(\bfX) | \bfX - \bfmu_0 |)
$$
%
 This can be seen as a generalization of the Fermat-Weber location problem (which has the spatial median \citep{brown83, Chaudhuri96} as the solution) using data-dependent weights. We call its solution, $\bfmu_w$, the \textit{weighted spatial median} of $F$. In a sample setup it is estimated by iteratively solving the equation $\sum_{i=1}^n w(\bfX_i) \bfS (\bfX_i - \hat\bfmu_w)/n = {\bf 0}_p$.

The following theorem shows that the sample weighted spatial median $\hat\bfmu_w$ is a $\sqrt n$-consistent estimator of $\bfmu_w$, and gives its asymptotic distribution:

\begin{Theorem}
Let $A_w, B_w$ be two matrices, dependent on the weight function $w$ such that
%
$$
A_w = E \left[ \frac{w( \bfepsilon ) }{\| \bfepsilon \|} \left( 1 - \frac{\bfepsilon \bfepsilon^T}{\| \bfepsilon \|^2} \right) \right]; \quad B_w = E \left[ \frac{(w( \bfepsilon ))^2 \bfepsilon \bfepsilon^T}{\| \bfepsilon \|^2} \right]
$$
%
where $\bfepsilon \sim \mathcal E({\bf 0}_p, \Sigma, G)$. Then
%
\begin{equation}
\sqrt n (\hat\bfmu_w - \bfmu_w) \leadsto N_p ({\bf 0}_p, A_w^{-1} B_w A_w^{-1})
\end{equation}
\end{Theorem}
%
This theorem generalizes equivalent results for the spatial median, and can be proved using the same steps to obtain those results \citep{OjaBook10}. Setting $w(\bfepsilon)=1$ above yields the asymptotic covariance matrix for the spatial median. Following this, the asymptotic relative efficiency (ARE) of $\bfmu_w$ corresponding to some non-uniform weight function with respect to the spatial median, say $\bfmu_s$ will be:
%
$$
ARE( \bfmu_w, \bfmu_s) = \left[ \frac{\text{det} (A^{-1} B A^{-1})}{\text{det} (A_w^{-1} B_w A_w^{-1})} \right]^{1/p}
$$
%
with $A = E [ 1/ \| \bfepsilon \| ( I_p - \bfepsilon \bfepsilon^T/ \| \bfepsilon \|^2 ) ]$ and $B = E [ \bfepsilon \bfepsilon^T/ \| \bfepsilon \|^2 ]$. This is further simplified under spherical symmetry:

\begin{Corollary}
For the spherical distribution $\mathcal{E}(\bfmu, kI_p, G); k \in \mathbb R, \bfmu \in \mathbb R^p$, we have
%
$$
ARE( \bfmu_w, \bfmu_s) = \frac{ \left[ E \left( \frac{f(r)}{r} \right) \right]^2}{Ef^2(r) \left[ E \left( \frac{1}{r} \right) \right]^2 }
$$
\end{Corollary}

\subsection{A high-dimensional test of location}

It is possible to take an alternative approach to the location testing problem by using the covariance-type U-statistic $C_{n,w} = \sum_{i=1}^n \sum_{j=1}^{i-1} \bfX_{w,i}^T \bfX_{w,j}$. This class of test statistics are especially attractive since they are readily generalized to cover high-dimensional situations, i.e. when $p > n$. The Chen and Qin (CQ) high-dimensional test of location for multivariate normal $\bfX_i$ \citep{ChenQin10} is a special case of this test that uses the statistic $C_n = \sum_{i=1}^n \sum_{j=1}^{i-1} \bfX_i^T \bfX_j$, and a recent paper (\citep{WangPengLi15}, from here on referred to as WPL test) shows that one can improve upon the power of the CQ test for non-gaussian elliptical distributions by using spatial signs $\bfS(\bfX_i)$ in place of the actual variables.

Given these, and some mild regularity conditions, the following holds for our generalized test statistic $C_{n,w}$ under $H_0$ as $n,p \rightarrow \infty$:
%
\begin{equation}\label{eqn:hdtest1}
\frac{C_{n,w}}{\sqrt{\frac{n(n-1)}{2} \text{Tr}(B_w^2)}} \leadsto N(0,1)
\end{equation}
%
and under contiguous alternatives $H_1: \bfmu = \bfmu_0$,
%
\begin{equation}\label{eqn:hdtest2}
\frac{C_{n,w} - \frac{n(n-1)}{2} \bfmu_0^T A_w^2 \bfmu_0 (1 + o(1)) }{\sqrt{\frac{n(n-1)}{2} \text{Tr}(B_w^2)}} \leadsto N(0,1)
\end{equation}
%
we provide the details behind deriving these two results in the supplementary material, which involve modified regularity conditions and sketches of proofs along the lines of \cite{WangPengLi15}.

Following this, the ARE of this test statistic with respect to its unweighted version, i.e. the WPL statistic, is expressed as:
%
$$
ARE(C_{n,w}, \text{WPL}; \bfmu_0) = \frac{\bfmu_0^T A_w^2 \bfmu_0}{\bfmu_0^T A^2 \bfmu_0} \sqrt\frac{\text{Tr}(B^2)}{\text{Tr}(B_w^2)} (1 + o(1))
$$
%
when $\Sigma = kI_p$, this again simplifies to $E^2(f(r)/r)/[E f^2(r). E^2(1/r)]$.

\subsubsection{Robust estimation of eigenvalues, and a plug-in estimator of $\Sigma$}

As we have seen in subsection 3.1, eigenvalues of the DCM are not same as the population eigenvalues, whereas the ADCM only gives back standardized eigenvalues. However, it is possible to robustly estimate the original eigenvalues by working with the individual columns of the robust score matrix. We do this using the following steps:

\begin{enumerate}
\item Randomly divide the sample indices $\{1,2,...,n\}$ into $k$ disjoint groups $\{G_1,...,G_k \}$ of size $\lfloor n/k \rfloor$ each;

\item Assume the data is centered. Transform the data matrix: $S = \hat\Gamma^T_D X$;

\item Calculate coordinate-wise variances for each group of indices $G_j$:
%
$$
\hat\lambda_{i,j} = \frac{1}{|G_j|} \sum_{l \in G_j} (s_{li} - \bar s_{G_j,i})^2; \quad i = 1,...,p; j = 1,...,k
$$
where $\bar\bfs_{G_j} = (\bar s_{G_j,1}, ..., \bar s_{G_j,p})^T$ is the vector of column-wise means of $S_{G_j}$, the submatrix od $S$ with row indices in $G_j$.
%
\item Obtain estimates of eigenvalues by taking coordinate-wise medians of these variances:
%
$$
\hat \lambda_i = \text{median} (\hat\lambda_{i,1}, ... , \hat\lambda_{i,k} ); \quad i = 1,...,p
$$
%
\end{enumerate}
%
The number of subgroups used to calculate this median-of-small-variances estimator can be determined following \citep{Minsker15}. After this, we construct a consistent plug-in estimator of the population covariance matrix $\Sigma$:

\begin{Theorem}\label{Thm:pluginSigma}
Consider the estimates $\hat\lambda_i$ obtained from the above algorithm, and the matrix of eigenvectors $\hat\Gamma_D$ estimated using the sample DCM. Define $\hat\Sigma = \hat\Gamma_D \hat\Lambda \hat\Gamma_D^T; \hat\Lambda = \text{diag}(\hat\lambda_1, ..., \hat\lambda_p)$. Then as $n \rightarrow \infty$,
%
$$ \| \hat\Sigma - \Sigma \|_F \stackrel{P}{\rightarrow} 0 $$
%
$\|.\|_F$ being the Frobenius norm.
\end{Theorem}

{\colrbf (put in 1 or 2 sentences?)}

\begin{proof}[Proof of Proposition \ref{proposition:SignTest}]
Under contiguous alternatives $H_0: \bfmu = \bfmu_0$, the weighted sign test statistic $T_{n,w}$ has mean $E (w(\bfZ) \bfS (\bfZ))$. For spherically symmetric $\bfZ$, $w(\bfZ)$ depends on $\bfZ$ only through its norm. Since $\| \bfZ \|$ and $\bfS(\bfZ)$ are independent, we get $E (w(\bfZ) \bfS (\bfZ)) = E w(\bfZ). E \bfS (\bfZ)$. The same kind of decomposition holds for $Cov(w(\bfZ) \bfS(\bfZ))$.

We can now simplify the approximate local power $\beta_{n,w}$ of the level-$\alpha$ ($0 < \alpha < 1$) test based on $T_{n,w}$:
%
\begin{eqnarray*}
\beta_{n,w} &=& K_p \left( \chi^2_{p,\alpha} + n (E (w(\bfZ) \bfS (\bfZ))^T \right.\\
&& \left. [ E (w^2(\bfZ) \bfS (\bfZ) \bfS (\bfZ)^T) ]^{-1} (E (w(\bfZ) \bfS (\bfZ)) \right)\\
&=& K_p \left( \chi^2_{p,\alpha} + \frac{E^2 w(\bfZ)}{Ew^2(\bfZ)}. E\bfS(\bfZ)^T [Cov(\bfS(\bfZ)]^{-1} E\bfS(\bfZ) \right)
\end{eqnarray*}
%
where $K_p$ and $\chi^2_{p,\alpha}$ are distribution function and upper-$\alpha$ cutoff of a $\chi^2_p$ distribution, respectively. Since $E^2 w(\bfZ) \leq Ew(\bfZ)$, $\beta_{n,w}$ the largest possible value of $\beta_{n,w}$ is $K_p ( \chi^2_{p,\alpha} + E\bfS(\bfZ)^T [Cov(\bfS(\bfZ)]^{-1} E\bfS(\bfZ) )$, the approximate power of the unweighted sign test statistic. Equality is of course achieved when $w(\bfZ)$ is a constant independent of $\bfZ$.
\end{proof}

\begin{proof}[Proof of Theorem \ref{Thm:pluginSigma}]
We are going to prove the following:
%
\begin{enumerate}
\item $\| \hat\Gamma_D - \Gamma \|_F \stackrel{P}{\rightarrow} 0$, and

\item $\| \hat\Lambda - \Lambda \|_F \stackrel{P}{\rightarrow} 0$
\end{enumerate}
%
as $n \rightarrow \infty$. For (1), we notice $\sqrt n vec(\hat\Gamma_D - \Gamma)$ asymptotically has a (singular) multivariate normal distribution following Corollary \ref{Corollary:eigendist}, so that $\| \hat\Gamma_D - \Gamma \|_F = O_P(1/\sqrt n)$ using Prokhorov's theorem.

It is now enough to prove convergence in probability of the individual eigenvalue estimates $\hat\lambda_i; i = 1,...,p$. For this, define estimates $\tilde\lambda_i$ as median-of-small-variances estimator of the \textit{true} score vectors $\Gamma^T X$. For this we have
%
\begin{equation}\label{eqn:PluginSigmaProof1}
| \tilde\lambda_i - \lambda_i | \stackrel{P}{\rightarrow} 0
\end{equation}
%
using Theorem 3.1 of \cite{Minsker15}, with $\mu = \lambda_i$. Now $ \hat\lambda_i = \text{med}_j (Var( X_{G_j}^T \hat\bfgamma_{D,i} ))$ and $\tilde\lambda_i = \text{med}_j (Var( X_{G_j}^T \bfgamma_i )) $, so that
%
\begin{eqnarray*}
| \hat\lambda_i - \tilde\lambda_i | &\leq & \text{med}_j \left[ Var( X_{G_j}^T ( \hat\bfgamma_{D,i} - \bfgamma_i) ) \right]
\\ &\leq & \| \hat\bfgamma_{D,i} - \bfgamma_i \|^2 \text{med}_j  \left[ \text{Tr} (Cov ( X_{G_j})) \right]
\end{eqnarray*}
%
using Cauchy-Schwarz inequality. Combining the facts $ \| \hat\bfgamma_{D,i} - \bfgamma_i \| = O_P(1/\sqrt n)$ and $ \text{med}_j  [ \text{Tr} (Cov ( X_{G_j})) ] \stackrel{P}{\rightarrow} \text{Tr}(\Sigma)$ \citep{Minsker15} with (\ref{eqn:PluginSigmaProof1}), we get the needed.

\end{proof}

\begin{proof}[Sketch of proofs for statements regarding $C_{n,w}$]

A first step to obtain asymptotic normality for the high-dimensional location test statistic $C_{n,w}$ is obtaining an equivalent result of Lemma 2.1 in \cite{WangPengLi15}:

\begin{Lemma}\label{Lemma:HDlemma21} Under the conditions

\noindent\textbf{(C1)}$\text{Tr}(\Sigma^4) = o(\text{Tr}^2(\Sigma^2)) $,

\noindent\textbf{(C2)}$\text{Tr}^4(\Sigma) / \text{Tr}^2(\Sigma^2) \exp[ - \text{Tr}^2(\Sigma) / 128p \lambda^2_{\max}(\Sigma) ] = o(1)$
\vspace{1em}

\noindent when $H_0$ is true we have
%
\begin{eqnarray}
E[ (\bfepsilon_{w1}^T \bfepsilon_{w2})^4 ] &=& O(1) E^2[ (\bfepsilon_{w1}^T \bfepsilon_{w2})^2 ]\\
E[ (\bfepsilon_{w1}^T B_w \bfepsilon_{w1})^2 ] &=& O(1) E^2[ (\bfepsilon_{w1}^T B_w \bfepsilon_{w1})^2 ]\\
E[ (\bfepsilon_{w1}^T B_w \bfepsilon_{w2})^2 ] &=& o(1) E^2[ (\bfepsilon_{w1}^T B_w \bfepsilon_{w1})^2 ]
\end{eqnarray}
%
with $\bfepsilon \sim \mathcal E({\bf 0}_p, \Lambda, G)$ and $\bfepsilon_w = w(\bfepsilon) \bfS(\bfepsilon)$.
\end{Lemma}
%
A proof of this lemma is derived using results in section 3 of \cite{ElKaroui09}, noticing that any-scalar valued 1-Lipschitz function of $\bfepsilon_w$ is a $M_w$-Lipschitz function of $\bfS(\bfepsilon)$, with $M_w = \sup_\bfepsilon w(\bfepsilon)$. Same steps as in the proof of Theorem 2.2 in \cite{WangPengLi15} follow now, using the lemma above in place of Lemma 2.1 therein, to establish asymptotic normality of $C_{n,w}$ under $H_0$.

To derive the asymptotic distribution under contiguous alternatives we need the conditions (C3)-(C6) in \cite{WangPengLi15}, as well as slightly modified versions of Lemmas A.4 and A.5:

\begin{Lemma}
Given that condition (C3) holds, we have $\lambda_{\max} (B_w) \leq 2 \frac{\lambda_{\max}}{\text{Tr} (\Sigma)} (1+o(1))$.
\end{Lemma}

\begin{Lemma}
Define $D_w = E \left[ \frac{w^2(\bfepsilon)}{\| \bfepsilon \|^2} (I_p - \bfS(\bfepsilon) \bfS(\bfepsilon)^T )\right] $. Then $\lambda_{\max} (A_w) \leq E( w(\bfepsilon)/\| \bfepsilon \|)$ and $\lambda_{\max} (D_w) \leq E( w(\bfepsilon)/\| \bfepsilon \|)^2$. Further, if (C3) and (C4) hold then $\lambda_{\min} (A_w) \geq E( w(\bfepsilon)/\| \bfepsilon \|)(1+o(1))/\sqrt 3$.
\end{Lemma}
%
The proof now exactly follows steps in the proof of theorem 2.3 in \cite{WangPengLi15}, replacing vector signs by weighted signs, using the fact that $w(\bfepsilon)$ is bounded above by $M_w$ while applying conditions (C5)-(C6) and lemmas A.1, A.2, A.3, and finally using the above two lemmas in place of lemmas A.4 and A.5 respectively.

\end{proof}

\bibliographystyle{plainnat}
\bibliography{scatterbib}

\end{document}

### 2018-03-20 MS-new/Signed-peripherality-draft.tex
first commit in shubhobm

\documentclass[11pt,letterpaper]{article}
\pdfoutput=1

\usepackage{mycommands,amssymb,amsmath,amsthm,color,pagesize,outlines,cite,subfigure,epsfig}
\usepackage[small]{caption}
\usepackage{hyperref} % for linking references
\hypersetup{colorlinks = true, citecolor = blue, urlcolor = blue}

\usepackage{stackrel}

\usepackage[round]{natbib}

% for algorithm
%\usepackage[noend]{algpseudocode}
%\usepackage{algorithm}

% DON'T change margins - should be 1 inch all around.
\addtolength{\evensidemargin}{-.5in}
\addtolength{\oddsidemargin}{-.5in}
\addtolength{\textwidth}{0.9in}
\addtolength{\textheight}{0.9in}
\addtolength{\topmargin}{-.4in}

%% measurements for 1 inch margin
%\addtolength{\oddsidemargin}{-.875in}
%\addtolength{\evensidemargin}{-.875in}
%\addtolength{\textwidth}{1.75in}
%\addtolength{\topmargin}{-.875in}
%\addtolength{\textheight}{1.75in}

%\pagestyle{myheadings}
%\markboth{}{\underline{{\bf Notes: (do not circulate)} \hspace{4.5cm} {\sc  Ansu Chatterjee} \hspace{0.25cm}}}

\DeclareMathOperator*{\ve}{vec}
\DeclareMathOperator*{\diag}{diag }
\DeclareMathOperator*{\supp}{supp }
\DeclareMathOperator*{\Tr}{Tr}
\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\Th}{^{\text{th}}}

\makeatletter
\newcommand{\opnorm}{\@ifstar\@opnorms\@opnorm}
\newcommand{\@opnorms}[1]{%
  \left|\mkern-1.5mu\left|\mkern-1.5mu\left|
   #1
  \right|\mkern-1.5mu\right|\mkern-1.5mu\right|
}
\newcommand{\@opnorm}[2][]{%
  \mathopen{#1|\mkern-1.5mu#1|\mkern-1.5mu#1|}
  #2
  \mathclose{#1|\mkern-1.5mu#1|\mkern-1.5mu#1|}
}
\makeatother

%% Appendix theorem counter
\usepackage{chngcntr}
\usepackage{apptools}
\AtAppendix{\counterwithin{Theorem}{section}}
\numberwithin{equation}{section}

\begin{document}

\newtheorem{Theorem}{Theorem}[section]
\newtheorem{Lemma}[Theorem]{Lemma}
\newtheorem{Corollary}[Theorem]{Corollary}
\newtheorem{Proposition}[Theorem]{Proposition}
\newtheorem{Conjecture}[Theorem]{Conjecture}
\theoremstyle{definition} \newtheorem{Definition}[Theorem]{Definition}

\title{Signed Peripherality Functions for Multivariate Statistical Inference}
\date{}
\author{Subhabrata Majumdar, Snigdhansu Chatterjee}
\maketitle

Abstract:
{(\colrbf will change)}Analyzing principal components for multivariate data from its spatial sign covariance matrix (SCM) has been proposed as a computationally simple and robust alternative to normal PCA, but it suffers from poor efficiency properties and is actually inadmissible with respect to the maximum likelihood estimator. Here we use data depth-based spatial ranks in place of spatial signs to obtain the orthogonally equivariant Depth Covariance Matrix (DCM) and use its eigenvector estimates for PCA. We derive asymptotic properties of the sample DCM and influence functions of its eigenvectors. The shapes of these influence functions indicate robustness of estimated principal components, and good efficiency properties compared to the SCM. Finite sample simulation studies show that principal components of the sample DCM are robust with respect to deviations from normality, as well as are more efficient than the SCM and its affine equivariant version, Tyler's shape matrix. Through two real data examples, we also show the effectiveness of DCM-based PCA in analyzing high-dimensional data and outlier detection, and compare it with other methods of robust PCA.
\vspace{.5cm}

Keywords:
Multivariate ranking, data depth, dimension reduction, principal components analysis, robust statistics, functional data

\newpage
\input{1_Introduction}
\input{2_Location}
\input{3_Scale}
\input{4_SDR}
\input{5_Functional}
\input{6_Conclusion}

\newpage
\input{7_Appendix}

\newpage
\input{misc}

\bibliographystyle{apalike}
\bibliography{scatterbib}

\end{document}

### 2018-03-20 MS-new/SignedDepth_08_07_16_1.tex
first commit in shubhobm

\documentclass[12pt,letterpaper]{article}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{authblk}
\usepackage{bibentry}
\usepackage{color}
\usepackage{epsfig}
\usepackage{fullpage}
\usepackage{graphics}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{lmodern}
\usepackage{pdflscape}
\usepackage{pdfpages}
\usepackage{relsize}
\usepackage{scalerel}
\usepackage{setspace}
\usepackage{soul}
\usepackage{slantsc}
\usepackage{stackengine}
\usepackage{subfigure}
\usepackage{subfiles}
% \usepackage{tikz}
\usepackage{verbatim}
% \usepackage{amsmath,amssymb,amsthm}
% \usepackage{rotating}
\usepackage{wrapfig}
%\usepackage{bibentry}

\usepackage{natbib}

\newcommand{\bfa}{{\mathbf {a}}}
\newcommand{\bfb}{{\mathbf {b}}}
\newcommand{\bfc}{{\mathbf {c}}}
\newcommand{\bfd}{{\mathbf {d}}}
\newcommand{\bfe}{{\mathbf {e}}}
\newcommand{\bff}{{\mathbf {f}}}
\newcommand{\bfg}{{\mathbf {g}}}
\newcommand{\bfh}{{\mathbf {h}}}
\newcommand{\bfi}{{\mathbf {i}}}
\newcommand{\bfj}{{\mathbf {j}}}
\newcommand{\bfm}{{\mathbf {m}}}
\newcommand{\bfn}{{\mathbf {n}}}
\newcommand{\bfp}{{\mathbf {p}}}
\newcommand{\bfr}{{\mathbf {r}}}
\newcommand{\bfs}{{\mathbf {s}}}
\newcommand{\bft}{{\mathbf {t}}}
\newcommand{\bfu}{{\mathbf {u}}}
\newcommand{\bfv}{{\mathbf {v}}}
\newcommand{\bfw}{{\mathbf {w}}}
\newcommand{\bfx}{{\mathbf {x}}}
\newcommand{\bfy}{{\mathbf {y}}}
\newcommand{\bfz}{{\mathbf {z}}}

\newcommand{\bfA}{{\mathbf {A}}}
\newcommand{\bfB}{{\mathbf {B}}}
\newcommand{\bfC}{{\mathbf {C}}}
\newcommand{\bfD}{{\mathbf {D}}}
\newcommand{\bfE}{{\mathbf {E}}}
\newcommand{\bfF}{{\mathbf {F}}}
\newcommand{\bfG}{{\mathbf {G}}}
\newcommand{\bfH}{{\mathbf {H}}}
\newcommand{\bfI}{{\mathbf {I}}}
\newcommand{\bfJ}{{\mathbf {J}}}
\newcommand{\bfK}{{\mathbf {K}}}
\newcommand{\bfL}{{\mathbf {L}}}
\newcommand{\bfM}{{\mathbf {M}}}
\newcommand{\bfP}{{\mathbf {P}}}
\newcommand{\bfQ}{{\mathbf {Q}}}
\newcommand{\bfR}{{\mathbf {R}}}
\newcommand{\bfS}{{\mathbf {S}}}
\newcommand{\bfT}{{\mathbf {T}}}
\newcommand{\bfU}{{\mathbf {U}}}
\newcommand{\bfV}{{\mathbf {V}}}
\newcommand{\bfW}{{\mathbf {W}}}
\newcommand{\bfY}{{\mathbf {Y}}}
\newcommand{\bfX}{{\mathbf {X}}}
\newcommand{\bfZ}{{\mathbf {Z}}}

\newcommand{\bfalpha}{{\boldsymbol{\alpha}}}
\newcommand{\bfbeta}{{\boldsymbol{\beta}}}
\newcommand{\bfgamma}{{\boldsymbol{\gamma}}}
\newcommand{\bfdelta}{{\boldsymbol{\delta}}}
\newcommand{\bfepsilon}{{\boldsymbol{\epsilon}}}
\newcommand{\bfeta}{{\boldsymbol{\eta}}}
\newcommand{\bflambda}{{\boldsymbol{\lambda}}}
\newcommand{\bfmu}{{\boldsymbol{\mu}}}
\newcommand{\bfnu}{{\boldsymbol{\nu}}}
\newcommand{\bfomega}{{\boldsymbol{\omega}}}
\newcommand{\bfpi}{{\boldsymbol{\pi}}}
\newcommand{\bfpsi}{{\boldsymbol{\psi}}}
\newcommand{\bfsigma}{{\boldsymbol{\sigma}}}
\newcommand{\bftheta}{{\boldsymbol{\theta}}}
\newcommand{\bfxi}{{\boldsymbol{\xi}}}

\newcommand{\bfLambda}{{\boldsymbol{\Lambda}}}
\newcommand{\bfPi}{{\boldsymbol{\Pi}}}
\newcommand{\bfSigma}{{\boldsymbol{\Sigma}}}
\newcommand{\bfTau}{{\boldsymbol{T}}}
\newcommand{\bfTheta}{{\boldsymbol{\Theta}}}

\newcommand{\BE}{\mathbb{E}}
\newcommand{\BF}{\mathbb{F}}
\newcommand{\BG}{\mathbb{G}}
\newcommand{\BI}{\mathbb{I}}
\newcommand{\BR}{\mathbb{R}}
\newcommand{\BV}{\mathbb{V}}

\newcommand{\cA}{\mathcal{A}}
\newcommand{\cB}{\mathcal{B}}
\newcommand{\cC}{\mathcal{C}}
\newcommand{\cD}{\mathcal{D}}
\newcommand{\cH}{\mathcal{H}}
\newcommand{\cI}{\mathcal{I}}
\newcommand{\cM}{\mathcal{M}}
\newcommand{\cX}{\mathcal{X}}

\def\baq#1\eaq{\begin{align}#1\end{align}}

\def\ban#1\ean{\begin{align*}#1\end{align*}}

\def\bredbf#1\eredbf{{\color{red}{\bf ???? #1 ????}}}

\newtheorem{Theorem}{Theorem}[section]
\newtheorem{Proposition}{Proposition}[section]
\newtheorem{Corollary}{Corollary}[section]
\newtheorem{Definition}{Definition}[section]
\newtheorem{Algorithm}{Algorithm}[section]
\newtheorem{Claim}{Claim}[section]

%\voffset=0.5in

   \newtheoremstyle{Example}{\topsep}{\topsep}%
     {}%         Body font
     {}%         Indent amount (empty = no indent, \parindent = para indent)
     {\bfseries}% Thm head font
     {:}%        Punctuation after thm head
    {0.9mm}%     Space after thm head (\newline = linebreak)
     {\thmname{#1}\thmnumber{ #2}\thmnote{(\it #3)}}%         Thm head spec

%	\AtEndEnvironment{Example}{\null\hfill\qed}%
   \theoremstyle{Example}
   \newtheorem{Example}{Example}[section]
	\AtEndEnvironment{Example}{\null\hfill\qed}%

\renewcommand{\baselinestretch}{1.1}

%
%\pagestyle{myheadings}
%\markboth{}{\underline{{\bf Notes: (do not circulate)} \hspace{4.5cm} {\sc  Ansu Chatterjee} \hspace{0.25cm}}}

\begin{document}
\bibliographystyle{plain}

\makeatletter
\def\@oddfoot{[\jobname (\today)]\hfil\thepage}
\makeatother

\title{On Combinations of Sign and Peripherality Transformations for Robust Analysis
of Hilbert-valued data}

%\title{Robust methods  based on the kernel signed peripherality 
%transformations}
\author{SM, SC}

\maketitle

\section{Introduction}

\bredbf
I will write this section once the rest of the work is complete
\eredbf

The scope of Hilbert-valued data is considerable, and encompasses 
the univariate and multivariate finite-dimensional observations traditionally 
studied in Statistics, as well  as certain kinds of functional data. For 
$\BR^{p}$-valued data, the classical approach is to model the joint distribution 
of the observations using a probability distribution known up to finite dimensional
parameters. If the correct probability distribution is used, there are often 
theoretical optimality guarantees. However in practice, the correct distribution is 
rarely, if ever, known; there may be aberrant observations that do not follow the 
pattern of the bulk of the data but whose influence on parameter estimates and 
eventual inference can be considerable; computational practicability and costs 
and complexity of patterns in the data may limit choices of statistical methods 
to adopt. The analysis of functional data is in a developmental stage, 
but the above comments on practical issues are applicable for such data also.

One way of circumventing the practical issues outlined above is to use 
{\it robust} techniques of data analysis, where theoretical optimality under 
restrictive idealized conditions is not of interest. Instead, efforts are made to 
make the resulting estimation and inference insensitive to  technical assumptions, 
outliers in the data, and computationally feasible. Naturally, subject to these 
robustness guarantees, the goal is to use the most efficient techniques possible.
The following very simple example recapitulates some very well known facts, but 
serves to illustrate the main drive of this paper.

\begin{Example}[Testing for a location parameter]
\label{Example:TestingLocation1d}

Suppose we have real valued observations $Y_{1}, \ldots, Y_{n}$, which from the 
domain of study that gave rise to these data, are known to be distributed around 
an unknown parameter $\mu \in \BR$, and the scientific question of interest lies in 
evaluating  whether the hypothesis $\mu = \mu_{0}$ for some given constant 
$\mu_{0}$ is tenable or not.

Under the assumption that the observations $Y_{1}, \ldots, Y_{n}$ are 
independent, identically distributed (i.i.d. hereafter) as $N (\mu, \sigma^{2})$, the 
Gaussian distribution with mean $\mu$ and variance $\sigma^{2}$, the optimal 
procedure is to use the $t$-test based on the statistic 
\ban 
T_{n} = n^{1/2} (\bar{Y}_{n} - \mu_{0})/S_{n-1}
\ean
and the Student's $t$-distribution. Here 
$\bar{Y}_{n} = n^{-1} \sum_{i=1}^{n} Y_{i}$ and 
$S_{n- 1}^{2} = (n -1)^{-1} \sum_{i=1}^{n} (Y_{i} - \bar{Y}_{n})^{2}$. 
However, note that the assumptions of the data being  independent, or identically 
distributed, or following the Gaussian distribution, or having the same variance for 
all observations, are rarely justified from the domain of study, and are merely choices of 
convenience. Also, one or more outlying observations among 
$Y_{1}, \ldots, Y_{n}$ can have extreme effect on either or both of 
$\bar{Y}_{n}$ and $S_{n- 1}^{2}$, and result in a numeric value that  completely 
misrepresents the nature of the data and misleading inference relating to the scientific query.

Alternatives to the above is to use the {\it sign}, and possibly also the 
{\it rank} of each observation. Let $\cI_{A}$ be the indicator of  $A$, 
that is, $\cI_{A} = 1$ if $A$ is true and is zero otherwise.
Define the following:
\ban 
(a) \text{ Sign function } & S (y; \nu) 
= | y - \nu |^{-1} (y - \nu) \cI_{\{ y \ne \nu \}}, \\
(b) \text{ Rank function } & R (y; Y_{1}, \ldots, Y_{n}) 
= \sum_{i=1}^{n} \cI_{ \{ y \leq Y_{i} \}}.
\ean
Then $S_{i} = S (Y_{i}; \mu_{0})$ indicates whether the $i^{th}$ observation is 
greater than $\mu_{0}$ or not, and $R_{i} = R (Y_{i}; Y_{1}, \ldots, Y_{n})$ is 
the rank that the $i^{th}$ observation takes among the entire data when sorted 
in an ascending order.

The {\it sign test statistic} corresponding to the above location testing problem
is given by $S = \sum_{i = 1}^{n} S_{i}$ and under the very general assumption 
that the $Y_{i}$'s are independent with distribution function $F_{i}$, and all the 
$F_{i}$'s have a common median $\mu_{0}$, the null distribution of 
$S$ is Binomial $(n, 0.5)$. This testing procedure is also indeed optimal in a 
very broad framework, see 
\bredbf
Need the appropriate reference from hajek, also need the conditions from there 
\eredbf

However, in many situations some additional information is known beyond the 
extremely relaxed conditions required by the sign test, and the Wilcoxon 
signed-rank test,  is found to be considerably more efficient than the sign test. 
These are well known results from several decades back, see 
\bredbf
Standard Hollander and Wolfe type refernce
\eredbf
for details.

\end{Example}

Example~\ref{Example:TestingLocation1d} motivates the present paper: which is a 
study on combinations of the equivalents of the sign function and rank function 
in Hilbert spaces, that leads to robust statistical procedures of considerable efficiency 
in a wide variety of problems. Very interestingly, we find that for location 
parameters, using in conjunction with the sign function a weight function that 
assigns {\it more} mass to observations closer to the center, results in   robust  
and considerably efficient estimators and test statistics. On the other hand, for 
scale or dispersion parameters, in conjunction with the sign function using a weight 
function that assigns {\it less} mass to observations closer to the center, 
results in  similar properties.

Notice that the robust and potentially optimal procedures outlined in 
Example~\ref{Example:TestingLocation1d}  above are based on transformations of the 
original data that preserved the structures of interest. In the rest of this paper we 
study equivalent transformations on general Hilbert spaces, and use the transformed data 
for ($i$) robust location estimation, ($ii$) testing for a location parameter in 
high dimensions and Hilbert spaces, ($iii$) robust dispersion estimation, ($iv$) 
robust principal component analysis (RPCA), ($v$) RPCA in dimension reduction and 
learning, ($vi$) robust analysis of functional data.

Given the considerable breadth of these topics, we present algorithmic details, some 
illustrative examples, and a selection of theoretical results. Considerably deeper studies 
in any of the above topics is feasible, however we postpone deep-dives into any 
specific application to future papers in order to make the main methodological drivers 
of this paper more easily understandable.

In Section~\ref{Section:SP} we present the {\it sign function} and the 
{\it peripherality function} for Hilbert spaces. The former is well known, and variants of 
the latter are also well known  in the literature. One major contribution of this 
paper is in the proposal of combining the two in different ways to achieve 
simultaneous robustness and efficiency targets. Then on the following sections we 
present details on the six applications listed above.

\section{The sign and peripherality functions}
\label{Section:SP}

We consider data $X_{1}, \ldots, X_{n}$ from some subset $\cX$ of 
a real separable Hilbert $\cH$.

We consider two functions defined below. First, we consider the 
{\it sign function} $S : \cH \times \cH \rightarrow \cH$, defined as 
\ban
S (x; \mu_{x}) = || x - \mu_{x} ||^{-1} (x - \mu_{x}) {\cI}_{ \{ x \ne \mu_{x} \}}. 
\ean
This sign function is defined with respect to the {\it location parameter} 
$\mu_{x} \in \cH$, and the norm $|| \cdot ||$ used above is the norm of the 
underlying Hilbert space. This is a direct  generalization of the 
real-valued case of the indicator of whether the point $x$ is to the right, 
left or at $\mu_{x}$, described in Example~\ref{Example:TestingLocation1d}. 
This function has been used many times in statistics, see
\bredbf insert several references. \eredbf

We next describe the {\it peripherality function}, for which some mathematical 
preliminaries are necessary for easier exposition. Let $(\Omega, \cA, \alpha)$ 
be a probability space, and let $\cB$ be the Borel $\sigma$-algebra generated 
by the norm topology of $\cH$. A $\cH$-valued random variable is a mapping 
$X :  \Omega \rightarrow \cH$ such that for every $B \in \cB$, $X^{-1} (B) \in \cA$. 
It is easy to see that $\alpha_{x} = \alpha ( X^{-1} (\cdot ) )$ is a probability 
measure on the measurable space $(\cH, \cB)$. Mathematical details about 
such probability measures on Hilbert spaces are available from a number of 
places, including
\bredbf
BLSP notes (my primary reference), Gross, Segal, and what not.
\eredbf

Let $\cM$ be a set of probability measures on $\cH$. 
%When $\cH$ 
%is infinite-dimensional, we further impose the conditions that for any $\nu \in \cM$
%\ban 
%\int_{\cH} || x || \nu (d x) < \infty, \hspace{1 cm} 
%\int_{\cH} || x ||^{2} \nu (d x) < \infty.
%\ean
A {\it peripherality function} 
$ P : \cH \times \cM \rightarrow \BR$,  is a function that satisfies the following 
condition:\\
{\it For every probability measure $F \in \cM$, there exists a constant $\mu_{F} \in \cH$ 
such that for every $t \in [ 0, 1]$ and every $x \in \cH$}
\ban 
P \Bigl( \mu_{F} ; F \Bigr) \leq P \Bigl( \mu_{F} + t ( x - \mu_{F} ); F \Bigr). 
\ean

That is, for every fixed $F$, the peripherality function achieves a minimum at 
$\mu_{F}$, and is non-decreasing in every direction away from $\mu_{F}$. If 
we impose the practical restriction that $\inf_{x} P ( x ; F )$ is finite and 
bounded below, then we may as well impose without loss of generality 
$P ( \mu_{F} ; F ) = 0$ and consequently $P ( x ; F ) \geq 0$ for all $x \in \cH$ 
and  $F \in \cM$. In many cases of interest, $P ( \cdot; \cdot)$ is 
uniformly bounded above as well.

The peripherality function quantifies whether the point $x$ is near or far from $\mu_{F}$. 
We will impose additional conditions on this function 
as we proceed, but it can be seem immediately that any distance measure between 
$x$ and $\mu_{F}$ satisfies the bare minimum requirement mentioned above.

In this paper, we demonstrate certain interesting applications arising from 
composing the sign function and the peripherality function together, to form the 
{\it signed-peripherality function} $\kappa (\cdot)$. We define this function 
with three parameters $\mu_{x} \in \cH$, $F \in \cM$ and  
$\mu_{y} \in \cH$,  argument $x \in \cH$ and range $\cH$. More precisely,
we use two functions $\kappa_{s} : \cH \rightarrow \cH$, 
$\kappa_{p} : \cH \rightarrow \cH$ that are respectively 
composed with the sign transformation and the peripherality function, and 
then multiplied together to obtain the function
$\kappa : \cH \times \cH \times \cM \times \cH \times \cH \rightarrow \cH$ 
defined as 
\ban 
\kappa (x; \mu_{x}, F, \mu_{y} ) = k_{s} (S (x; \mu_{x})) k_{p} (P (x; F)) + \mu_{y}. 
\ean
Within this very generic framework, we will explore two simple choices. We consider 
$\kappa_{s} (x) = x$, thus this is fixed to be the identity transformation. The two 
alternatives we consider for $\kappa_{p}$ are 
$\kappa_{p} (x) = x$ and $\kappa_{p} (x) = \exp (- x)$, thus one is linearly 
increasing with $x$ while the other is exponentially decreasing.

Notice that if we consider $\mu_{y} = \mu_{F} = \mu_{x}$,  
$\kappa_{s} (x) = \kappa_{p} (x) = x$, and take the very 
simple peripherality  function $P( x; F) = || x - \mu_{F} ||$, we have 
$\kappa (x; \mu_{x}, F, \mu_{y} ) \equiv x$ for all choices of parameters 
$\mu_{x}, F, \mu_{y}$.  Consequently, under this choice of parameters for the 
$\kappa$-transformation, analyzing a dataset $\{ X_{1}, \ldots, X_{n} \}$ and 
its $\kappa$-transformed version 
$\{ Y_{i} = \kappa (X_{i}; \ldots), \ i = 1, \ldots, n \}$ are equivalent. However,
in this paper we illustrate how other choices of the peripherality function 
lead to interesting robustness results. We have deliberately set the location 
parameters $\mu_{x}, \mu_{F}, \mu_{y}$ to be potentially non-identical, this 
additional flexibility has some advantage for robust data analysis. In many 
applications, the value of these three parameters may be identical, which leads 
to no conflict in our framework.

A whole class of peripherality functions can be defined from 
 {\it data - depth},  which are center-outward ranking of multivariate data. 
 Data-depths have been extensively used in statistics also, see 
 \bredbf multiple references. \eredbf
 Peripherality functions can be defined as some inverse ranking based 
 on data depth, and the concept of {\it outlyingness} associated with data depth 
 is essentially same as what we use in this paper. We use the term 
 {\it peripherality} to keep track of the difference in application 
 contexts and technical assumptions. As an additional objective of this paper, 
 we discuss  some properties and uses of  data-depth in real, separable Hilbert spaces.

 {\bf old material:}{\it
 In this paper, we consider a few illustrative cases of the use of the 
 $\kappa$-transformation. Suppose the data at hand is $X_{1}, \ldots, X_{n}$, 
 and we define $Y_{i} = \kappa (X_{i}; \mu_{X}, F, \mu_{Y})$ for some 
choice of parameters $\mu_{X}, F, \mu_{Y}$. For interpretability and 
convenience, we assume that $\BE S ( X_{i}; \mu_{X}) P ( X_{i}; F) = 0$, thus 
$\BE Y_{i} = \mu_{Y}$. We thus have 
\ban 
\BV Y_{i} 
& = \BE P ( X_{i}; F)^{2} S ( X_{i}; \mu_{X}) S ( X_{i}; \mu_{X})^{T} \\
& = \BE P ( X_{i}; F)^{2} || X_{i} - \mu_{X} ||^{-2} 
( X_{i} - \mu_{X} ) (X_{i} - \mu_{X})^{T}.
\ean
}

\bredbf Need to include (a) Biman-PC idea for affine equivariance for $p \ll n$, 
(b) kernel versions as an example of generalization. (c) anything else? \eredbf

\section{The robust location problem}

%\bredbf
%This section and the section following this needs to be merged and made sensible and 
%publication-worthy. 
%\eredbf

\subsection{General approach}

Here are things we need to do:
\begin{enumerate}

\item Propose robust location estimation in  a general Hilbert space $\cH$, based on 
$\kappa_{s} (x) = x$ and $\kappa_{p} (x) = \exp (-x)$. I am using $\exp (-x)$ and not 
$1/x$ (on which you have done some simulations successfully I think) so that we do 
not have unboundedness issues.

\item Suggest that this may be a better location estimate than the spatial median 
that is obtained by just minimizing the sign function.

\item Show whatever theoretical results we have. Make these completely error-free, 
so no handwaving or loose, non-crisp arguments.

\item Do the infinite dimensional case also. Our strongest point in this paper is being 
able to handle robustness in infinite dimensions. There may not be any useful 
or usable definition of invariance or equivariance in infinite dimensions. So separate 
the results for the $p \ll n$ case and the high-dimensional case, if necessary.

\item Show simulation results.

\item Do one running data analysis in infinite dimensions. Working with extreme 
precipitation or temperatures is a good idea, there is a potentially a need for robust  
location estimation there.

\item Let us finish one section first, then move to another section.
\end{enumerate}

\subsection{The following are concrete suggestions:}

\begin{enumerate}

\item 
%\bredbf 
Describe what is being observed, ie, the main aspects of the data. For example, are 
you assuming iid data throughout?
%\eredbf

\item 
%\bredbf
After you have described the data, define the parameter you are interested in. 
The population mean, population median, 
the population equivalent of the minimizer of the weighted sign function are not all 
same. However, each of them can be a candidate for a {\it location parameter}. Don't skip 
the mathematical details, include everything.
%\eredbf

\item 
%\bredbf 
Then propose your estimator for the parameter of your choice. 
%\eredbf

\item 
%\bredbf
Now explore properties of your proposed estimator. Simulate data and show that 
your estimator is better than the (sample) mean in terms of robustness, and 
better than the (sample) median in terms of efficiency. The following steps 
describe what you might simulate.
%Use curves as data, so 
%we are justified in using the term ``Hilbert-valued''. 
%\eredbf

\item Use the el Nino data as a template. Do your robust PCA, and extract the first 
5 or so PCs with their loadings $\beta_{1}, \beta_{2}, \ldots, \beta_{5}$. This will form
the foundation for the simulation. For the time index of the data, make it $t \in [0, 1)$
to avoid technical difficulties. That is, consider June as $t = 0$, July as $t = 1/12$ and 
so on. This simulation will also form the spine of the paper for each application (we will use this simulated data for all the sections), so do this carefully. Use {\tt set.seed}, so we can reproduce results.

\item
We will generate $n$ curves indexed by $i = 1, \ldots, n$, 
all of which will be sampled at time points 
%$t_{i k}$, $k =1, \ldots, T_{i}$. Scale the total 
%time to be between $[0, 1]$, so that there are no technical difficulties. You may take 
%$T_{1} = \ldots = T_{n} = T$ for convenience, and in fact even take 
$t_{1}, \ldots, t_{T}$. That is, the observation times for all the curves are 
same. You can take $T = 12$ and $t_{j} = (j -1)/12$.

\item 
For simulation, first generate $b_{i j} \sim N ( \beta_{j}, V_{j})$ for $j = 1, \ldots, 5$, 
and define the simulated signal for the $i^{th}$ curve as  
\ban 
\xi_{i}  (t) = \sum_{j = 1}^{5} b_{i j} PC_{j} (t), \ i=1, \ldots, n. 
\ean
Use $V_{2}$ very large, so that in different signals there is considerable variability 
in the signal.

\item
Add a iid high-variance noise, say $t_{2}$ or something to each observed data point 
$t_{i k}$, $k =1, \ldots, T_{i}$, $i =1, \ldots, n$. Thus, the final simulated data is 
\ban 
Y_{i}  ( t_{i k} ) = \xi (t _{i k}) + \varepsilon (t_{i k}).
\ean

\item While this is supposed to be functional data, all we have really is a 
$n \times T$  table. Get the $T$-dimensional sample mean (minimizer of squared 
Euclidean norm), and median (ie, 
the minimizer of the Euclidean norm,  ie, Haldane's median, ie, the quantity that 
solves $\sum S(Y_{i} ; \theta) = 0$.) Also get your proposed weighted median.

\item Show that the weighted median and original median are robust, and the weighted 
median is closer than the median to the "population mean" 
\ban 
\sum_{j = 1}^{5} \beta_{j} PC_{j} (t), t = 1, \ldots, T.
\ean

\item Remember that although we are calling this FDA, this is really 12-dim data 
analysis. 
\end{enumerate}

\subsection{Subho's write-up}

Consider the general situation of estimating or testing for the location parameter of 
an elliptical distribution using weighted sign vectors. 
\bredbf
What is an elliptical distribution? In any scientific writing, for any technical term 
you must (a) either define it if it is brand new, (b) give the formula with proper 
citations if somebody has already defined it (in this case, there should be a definition 
in Fang's book, maybe in several other places), (c) prove every claim that you are making, 
or provide a reference from a trustworthy source.
\eredbf
For now the only condition 
we impose on these weights, say $w( \cdot)$, is that they need to be scalar-valued 
affine equivariant and square-integrable functions of the data, or in other words 
functions of the norm of the standardized random variable $\bfZ$.
\bredbf 
I am not sure if in FDA context, "affine equivariance" is defined. Find out. If not, then 
what you have above is a good definition. 
\eredbf
 In that sense $w(\bfX)$ can be equivalently written as $f(r)$, with $r = \| \bfZ \|$. 
 \bredbf 
 Are we always working with square integrable functions of the data? (to begin with, what 
 do you mean by that? Do you mean that the data is iid random variables all of which 
 have finite second moments? What is a standardized random variable? 
 \eredbf

 The simplest use of weighted signs here would be to construct a robust alternative to the 
 Hotelling's $T^2$ test \bredbf reference \eredbf using their sample mean vector and 
 covariance matrix. \bredbf what sort of robust alternative? provide details? always 
 provide 100\% exact mathematicalstatements \eredbf 
 Formally, 
 this means testing for $H_0: \bfmu = {\bf 0}_p$ vs. $H_1:\bfmu \neq {\bf 0}_p$  based 
 on the test statistic: \bredbf are you testing for the mean? Or a different parameter? 
 If it is the latter, then it's not the same test. Requires discussion and clarification \eredbf
%
$$ T_{n,w} = n \bar\bfX_w^T ( Cov (X_w))^{-1} \bar\bfX_w $$
%
with $\bar\bfX_w = \sum_{i=1}^n \bfX_{w,i}/n$ 
and $\bfX_{w,i} = w(\bfX_i ) \bfS (\bfX_i)$ for $i=1,2,...,n$. 
However, the following holds true for this weighted sign test:
%
\begin{Proposition}
Consider $n$ random variables $Z = (\bfZ_1,...,\bfZ_n)^T$ distributed independently and 
identically as $\mathcal{E}( \bfmu, kI_p, G); k \in \mathbb R$, and the class of hypothesis tests defined above. Then, given any $\alpha \in (0,1)$, local power 
at $\bfmu \neq {\bf 0}_p$ for the level-$\alpha$ test  based on $T_{n,w}$ is maximum when $w(\bfZ_1) = c$, a constant independent of $\bfZ_1$.
\end{Proposition}
%
\noindent This essentially means that power-wise the (unweighted) spatial sign test \citep{OjaBook10} is optimal in the given class of hypothesis tests when the data comes from a spherically symmetric distribution. Our simulations show that this empirically holds for non-spherical but elliptic distributions as well.

\subsection{The weighted spatial median}

Our weight functions are affine equivariant functions of the data, i.e. they are not affected by the population location parameter $\bfmu$. This ensures that there exists a unique solution of the following of optimization problem:
%
$$
\bfmu_w = \text{arg}\min_{\bfmu_0 \in \mathbb{R}^p} E ( w(\bfX) | \bfX - \bfmu_0 |)
$$
%
 This can be seen as a generalization of the Fermat-Weber location problem (which has the spatial median \citep{brown83, Chaudhuri96} as the solution) using data-dependent weights. We call its solution, $\bfmu_w$, the \textit{weighted spatial median} of $F$. In a sample setup it is estimated by iteratively solving the equation $\sum_{i=1}^n w(\bfX_i) \bfS (\bfX_i - \hat\bfmu_w)/n = {\bf 0}_p$.

The following theorem shows that the sample weighted spatial median $\hat\bfmu_w$ is a $\sqrt n$-consistent estimator of $\bfmu_w$, and gives its asymptotic distribution:

\begin{Theorem}
Let $A_w, B_w$ be two matrices, dependent on the weight function $w$ such that
%
$$
A_w = E \left[ \frac{w( \bfepsilon ) }{\| \bfepsilon \|} \left( 1 - \frac{\bfepsilon \bfepsilon^T}{\| \bfepsilon \|^2} \right) \right]; \quad B_w = E \left[ \frac{(w( \bfepsilon ))^2 \bfepsilon \bfepsilon^T}{\| \bfepsilon \|^2} \right]
$$
%
where $\bfepsilon \sim \mathcal E({\bf 0}_p, \Sigma, G)$. Then
%
\begin{equation}
\sqrt n (\hat\bfmu_w - \bfmu_w) \leadsto N_p ({\bf 0}_p, A_w^{-1} B_w A_w^{-1})
\end{equation}
\end{Theorem}
%

We provide a sketch of its proof in the supplementary material, which generalizes equivalent results for the spatial median \citep{OjaBook10}. Setting $w(\bfepsilon)=1$ above yields the asymptotic covariance matrix for the spatial median. Following this, the asymptotic relative efficiency (ARE) of $\bfmu_w$ corresponding to some non-uniform weight function with respect to the spatial median, say $\bfmu_s$ will be:
%
$$
ARE( \bfmu_w, \bfmu_s) = \left[ \frac{\text{det} (A^{-1} B A^{-1})}{\text{det} (A_w^{-1} B_w A_w^{-1})} \right]^{1/p}
$$
%
with $A = E [ 1/ \| \bfepsilon \| ( I_p - \bfepsilon \bfepsilon^T/ \| \bfepsilon \|^2 ) ]$ and $B = E [ \bfepsilon \bfepsilon^T/ \| \bfepsilon \|^2 ]$. This is further simplified under spherical symmetry:

\begin{Corollary}
For the spherical distribution $\mathcal{E}(\bfmu, kI_p, G); k \in \mathbb R, \bfmu \in \mathbb R^p$, we have
%
$$
ARE( \bfmu_w, \bfmu_s) = \frac{ \left[ E \left( \frac{f(r)}{r} \right) \right]^2}{Ef^2(r) \left[ E \left( \frac{1}{r} \right) \right]^2 }
$$
\end{Corollary}

\section{A high-dimensional test of location}

It is possible to take an alternative approach to the location testing problem by using the covariance-type U-statistic $C_{n,w} = \sum_{i=1}^n \sum_{j=1}^{i-1} \bfX_{w,i}^T \bfX_{w,j}$. This class of test statistics are especially attractive since they are readily generalized to cover high-dimensional situations, i.e. when $p > n$. The Chen and Qin (CQ) high-dimensional test of location for multivariate normal $\bfX_i$ \citep{ChenQin10} is a special case of this test that uses the statistic $C_n = \sum_{i=1}^n \sum_{j=1}^{i-1} \bfX_i^T \bfX_j$, and a recent paper (\citep{WangPengLi15}, from here on referred to as WPL test) shows that one can improve upon the power of the CQ test for non-gaussian elliptical distributions by using spatial signs $\bfS(\bfX_i)$ in place of the actual variables.

Given these, and some mild regularity conditions, the following holds for our generalized test statistic $C_{n,w}$ under $H_0$ as $n,p \rightarrow \infty$:
%
\begin{equation}\label{eqn:hdtest1}
\frac{C_{n,w}}{\sqrt{\frac{n(n-1)}{2} \text{Tr}(B_w^2)}} \leadsto N(0,1)
\end{equation}
%
and under contiguous alternatives $H_1: \bfmu = \bfmu_0$,
%
\begin{equation}\label{eqn:hdtest2}
\frac{C_{n,w} - \frac{n(n-1)}{2} \bfmu_0^T A_w^2 \bfmu_0 (1 + o(1)) }{\sqrt{\frac{n(n-1)}{2} \text{Tr}(B_w^2)}} \leadsto N(0,1)
\end{equation}
%
we provide the details behind deriving these two results in the supplementary material, which involve modified regularity conditions and sketches of proofs along the lines of \cite{WangPengLi15}.

Following this, the ARE of this test statistic with respect to its unweighted version, i.e. the WPL statistic, is expressed as:
%
$$
ARE(C_{n,w}, \text{WPL}; \bfmu_0) = \frac{\bfmu_0^T A_w^2 \bfmu_0}{\bfmu_0^T A^2 \bfmu_0} \sqrt\frac{\text{Tr}(B^2)}{\text{Tr}(B_w^2)} (1 + o(1))
$$
%
when $\Sigma = kI_p$, this again simplifies to $E^2(f(r)/r)/[E f^2(r). E^2(1/r)]$.

{\color{red}\bf (need to write the sketch in supplementary material) }

\section{SC: (older material) Testing for a location parameter}

Suppose $W \in \{ 0, 1 \}$, $Z \in \BR^{p}$ and $U \in \BR^{p}$ 
are independent  random variables, with 
$W$ having a Bernoulli distribution with parameter $\theta$, 
and each 
element of $U$ is an independent standard Cauchy random variable. 
The random vector $Z$ follows a mean-zero, variance matrix $\Sigma$ Normal distribution 
$Z \sim N_{p} (0, \Sigma)$. Our choices of $\Sigma$ in the details 
below include 
cases where $Cov (Z_{i}, Z_{j}) = \rho^{ | i - j|}$ for some $\rho \in [0, 1)$
which includes as special case the identity matrix $\BI_{p}$ corresponding to 
$\rho = 0$, and where $Cov (Z_{i}, Z_{j}) = \rho$.

We define $X = \mu + W Z + (1 - W) U$, and let the observed data be 
independent, identically distributed copies $X_{1}, \ldots, X_{n}$ copies of $X$. 
Note that the conditional distribution of $(X | W = 0)$ does not have finite moments.
Suppose our goal is to conduct inference on $\mu$, in particular, to test the hypothesis 
that $\mu = 0 \in \BR^{p}$. 
The sample mean and variance from the observed data $X_{1}, \ldots, X_{n}$, 
denoted respectively by $\bar{X} = n^{-1} \sum_{i = 1}^{n} X_{i}$ and
$S_{X} = (n - 1)^{-1} \sum_{i = 1}^{n} ( X_{i} - \bar{X} )( X_{i} - \bar{X} )^{T}$. 
These are 
well-defined quantities, even though their expectations may not exist.
Assume $p < n$, and thus $S_{x}$ is invertible.

One option for inference on $\mu$ is to ignore the heavy-tailed component of 
the data, and to use Hotteling's $T^{2}$ statistic given by 
$T^{2} = n (\bar{X} - \mu_{0})^{T} S_{X}^{-1} (\bar{X} - \mu_{0})$.

Other, more robust options, is to use the sign function exclusively, 
or any variety of data-depth functions exclusively. 
\bredbf suggest 2 or 3 depth functions used earlier for one-sample mean 
testing, provide references. List details on how these methods would be implemented,
just do what these references do
 \eredbf

Another alternative is to use the $\kappa$-transformation proposed in this paper. 
We begin with a robust estimator of $\mu$, for example the co-ordinatewise median, 
to use as $\mu_{X}$ and $\mu_{F}$. As $F$, we use the $p$-dimensional Normal 
distribution with mean $\mu_{F}$ and identity covariance matrix. One simple
peripherality function is $ || x - mu_{F} ||/ (1 + || x - mu_{F} ||)$, which 
is bounded above and below and achieves a minima at $\mu_{F}$. We take $\mu_{Y}$ 
to be $\mu$ also, and we may again use the co-ordinatewise median or a different 
statistic as its estimator like simple sample mean of $Y_{i} = \kappa (X_{i})$.
(Use the sample mean: we want to sell the idea that after the kappa transformation 
all standard classical methods like sample moments can be used).

We should be able to show that 
\begin{enumerate}

\item Classical methods like Hotteling is a disaster because of outliers.

\item Sign and depth-based methods lack power, which becomes quite bad when $\rho$ 
is considerably away from zero.

\end{enumerate}

\end{document}

\section{Testing for equality of two location parameters}

You know how to develop this. Do both the two sample and paired sample case.

Show simulation results like above.

\section{Develop a robust estimator of variance}
Simply do sample variance of the transformed variables $Y_{i} = \kappa (X_{i})$.

Show simulation results like above.

\section{Outlier detection}

Expand and generalize what you have in the paper already, where I think this is a small 
example. Refer to a standard method for multivariate outlier detection, and show that 
such a method used on $Y_{i} = \kappa (X_{i})$ works. I will send you some papers for 
referencing in this part.

\section{Robust principal component analysis}

This will be one of the bigger and 
 major sections of the paper, essentially copied and pasted
 from the previous version. Don't do anything here as of now.

\section{Robust Hawkins-regression}

Consider the $p + 1$ dimensional data $\{ 
(\mathbf{X}_{i} \ Y_{i})^{T} \in \BR^{p +1}, \ i =1, \ldots, n \}$. 
Do the robust PCA on this, and get all the eigenvectors. The typical eigenvector looks 
like $( \mathbf{\gamma} \ \gamma_{0} ) \in \BR^{p +1}$. Under the condition that the 
joint distribution of $(\mathbf{X} \ Y)^{T}$ is absolutely continuous, we have 
$\gamma_{0} \ne 0$ almost surely. We implement the following for any estimated 
eigenvector where $|\gamma_{0} | > \epsilon$ for some fixed $\epsilon > 0$: 
multiply the eigenvector by  $-\gamma_{0}^{-1}$, thus consider 
$( -\gamma_{0}^{-1} \mathbf{\gamma} \ -1 ) \in \BR^{p +1}$, which is a 
"Hawkins-regression". The  variance of this linear 
combination of variables is given by the corresponding eigenvalue times 
$\gamma_{0}^{-2}$, which may be small or large in the $p + 1$ eigenvectors, so the order 
in which eigenvalues/vectors appear in PCA may not be maintained here.

Also look up what Hawkins had originally proposed, and implement those.

Do a simple simulation, building on the simulation you have for the previous 
section.

\section{Robust inference with functional data}

This section is to show something beyond the $p \ll n$ setting. Both robust PCA 
and location testing are important problems for functional data. Abhirup can 
take charge of this part once we have everything else settled.

The main idea here is to use any decent location estimator to start with (some 
version of median is fine). Then we may test if the functional location for resting 
and active state are identical or not.

Also do functional PCA robust version, and then maybe project the data on the first few
principal components and then do the 2 sample (or paired sampel) testing again.

\section{An example with images}
\end{document}

### 2018-03-20 MS-new/misc.tex
first commit in shubhobm

\section{Introduction}

{\colrbf (needs rewriting)}

In multivariate analysis, the study of principal components is important since it provides a small number of uncorrelated variables from a potentially larger number of variables, so that these new components explain most of the underlying variability in the original data. In case of multivariate normal distribution, the sample covariance matrix provides the most asymptotically efficient estimates of eigenvectors/ principal components, but it is extremely sensitive to outliers as well as relaxations of the normality assumption. To address this issue, several robust estimators of the population covariance or correlation matrix have been proposed which can be used for Principal Components Analysis (PCA). They can be roughly put into these categories: robust, high breakdown point estimators that are computation-intensive \citep{rousseeuw85, maronna76}; M-estimators that are calculated by simple iterative algorithms but do not necessarily possess high breakdown point \citep{huber77, tyler87}; and symmetrised estomators that are highly efficient and robust to deviations from normality, but sensitive to outliers and computationally demanding \citep{dumbgen98, sirkia07}.

When principal components are of interest, one can also estimate the population eigenvectors by analyzing the spatial sign of a multivariate vector: the vector divided by its magnitude, instead of the original data. The covariance matrix of these sign vectors, namely Sign Covariance Matrix (SCM) has the same set of eigenvectors as the covariance matrix of the original population, thus the multivariate sign transformation yields computationally simple and high-breakdown estimates of principal components \citep{locantore99, visuri00}. Although the SCM is not affine equivariant, its orthogonal equivariance suffices for the purpose of PCA. However, the resulting estimates are not very efficient, and are in fact asymptotically inadmissible \citep{magyar14}, in the sense that there is an estimator (Tyler's M-estimate of scatter, to be precise) that has uniformly lower asymptotic risk than the SCM.

The nonparametric concept of data-depth had first been proposed by \cite{tukey75} when he introduced the halfspace depth. Given a dataset, the depth of a given point in the sample space measures how far inside the data cloud the point exists. An overview of statistical depth functions can be found in \citep{zuo00}. Depth-based methods have recently been popular for robust nonparametric classification \citep{jornsten04, ghosh05, dutta12, sguera14}. In parametric estimation, depth-weighted means \citep{ZuoCuiHe04} and covariance matrices \citep{ZuoCui05} provide high-breakdown point as well as efficient estimators, although they do involve choice of a suitable weight function and tuning parameters. In this paper we study the covariance matrix of the multivariate rank vector that is obtained from the data-depth of a point and its spatial sign, paying special attention to its eigenvectors. Specifically, we develop a robust version of principal components analysis for elliptically symmetric distributions based on the eigenvectors of this covariance matrix, and compare it with normal PCA and spherical PCA, i.e. PCA based on eigenvectors of the SCM.

Given a vector $\bfx \in \mathbb{R}^p$, its spatial sign is defined as the vector valued function \citep{MottonenOja95}:
%
$$ \bfS(\bfx) = \begin{cases} \bfx\| \bfx \|^{-1} \quad \mbox{if }\bfx \neq \bf0\\
\bf0 \quad \mbox{if }\bfx = \bf0 \end{cases} $$
%
When $\bfx$ is a random vector that follows an elliptic distribution $|\Sigma|^{-1/2} f((\bfx - \bfmu)^T \Sigma^{-1} (\bfx - \bfmu))$, with a mean vector $\bfmu$ and covariance matrix $\Sigma$, the sign vectors $\bfS(\bfx - \bfmu)$ reside on the surface of a $p$-dimensional unit ball centered at $\bfmu$. Denote by $\Sigma_S(\bfX) = E\bfS (\bfX - \bfmu)\bfS (\bfX - \bfmu)^T$ the covariance matrix of spatial signs, or the \textit{Sign Covariance Matrix} (SCM). The transformation $\bfx \mapsto \bfS(\bfx - \bfmu)$ keeps eigenvectors of population covariance matrix unchanged, and eigenvectors of the sample SCM $ \hat \Sigma_S = \sum_{i=1}^n \bfS (\bfx_i - \bfmu)\bfS (\bfx_i - \bfmu)^T/n $ are $\sqrt n$-consistent estimators of their population counterparts \citep{taskinen12}.

The sign transformation is rotation equivariant, i.e. $ \bfS(P (\bfx - \bfmu)) = P(\bfx - \bfmu)/\| P (\bfx - \bfmu)\| = P(\bfx - \bfmu)/\|\bfx - \bfmu\| = P \bfS(\bfx - \bfmu)$ for any orthogonal matrix $P$, and as a result the SCM is rotation equivariant too, in the sense that $\Sigma_S(P\bfX) = P \Sigma_S(\bfX) P^T$. This is not necessarily true in general if $P$ is replaced by any non-singular matrix. An affine equivariant version of the sample SCM is obtained as the solution $\hat \Sigma_T$ of the following equation:
%
$$ \hat \Sigma_T(\bfX) = \frac{p}{n} \sum_{i=1}^n \frac{(\bfx - \bfmu)(\bfx - \bfmu)^T}{(\bfx - \bfmu)^T \hat\Sigma_T(\bfX)^{-1} (\bfx - \bfmu)} $$
%
which turns out to be Tyler's M-estimator of scatter \citep{tyler87}. In this context, one should note that for scatter matrices, affine equivariance will mean any affine transformation on the original random variable $\bfX \mapsto \bfX^* = A\bfX + \bfb$ ($A$ non-singular, $\bfb \in \mathbb{R}^p$) being carried over to the covariance matrix estimate upto a scalar multiple: $\hat\Sigma_T(\bfX^*) = k. A \hat\Sigma_T(\bfX) A^T$ for some $k>0$.

For any multivariate distribution $F = F_\bfX$ belonging to a set of distributions $\mathcal F$, the depth of a point $\bfx \in \mathbb{R}^p$, say $D(\bfx, F_\bfX)$ is any real-valued function that provides a 'center outward ordering' of $\bfx$ with respect to $F$ \citep{zuo00}. \cite{liu90} outlines the desirable properties of a statistical depth function:

\vspace{1em}
\noindent\textbf{(D1)} \textit{Affine invariance}: $D(A\bfx + \bfb, F_{A\bfX+\bfb}) = D(\bfx, F_\bfX)$;

\noindent\textbf{(D2)} \textit{Maximality at center}: $D(\bftheta, F_\bfX) = \sup_{\bfx\in \mathbb{R}^p} D(\bfx, F_\bfX)$ for $F_\bfX$ having center of symmetry $\bftheta$. This point is called the \textit{deepest point} of the distribution.;

\noindent\textbf{(D3)} \textit{Monotonicity with respect to deepest point}: $D(\bfx; F_\bfX) \leq D(\bftheta + a(\bfx - \bftheta), F_\bfX)$, $\bftheta$ being deepest point of $F_\bfX$.;

\noindent\textbf{(D4)} \textit{Vanishing at infinity}: $D(\bfx; F_\bfX) \rightarrow 0$ as $\|\bfx\| \rightarrow \infty $.
\vspace{1em}

In (D2) the types of symmetry considered can be central symmetry, angular symmetry and halfspace symmetry. Also for multimodal probability distributions, i.e. distributions with multiple local maxima in their probability density functions, properties (D2) and (D3) are actually restrictive towards the formulation of a reasonable depth function that captures the shape of the data cloud. In our derivations that follow, we replace these two by a weaker condition:

\vspace{1em}
\noindent\textbf{(D2*)} \textit{Existence of a maximal point}: The maximum depth over all distributions $F$ and points $\bfx$ is bounded above, i.e. $ \sup_{F_\bfX \in \mathcal F} \sup_{\bfx\in \mathbb{R}^p} D(\bfx, F_\bfX) < \infty $. We denote this point by $M_D(F_\bfX)$.
\vspace{1em}

We will be using the following 3 measures of data-depth to obtain our DCMs and compare their performances:

\begin{itemize}
\item \textbf{Halfspace depth} (HD) \citep{tukey75} is defined as the minimum probability of all halfspaces containing a point. In our notations,

$$ HD(\bfx, F)  = \inf_{\bfu \in \mathbb{R}^p; \bfu \neq \bf0} P(\bfu^T \bfX \geq \bfu^T \bfx) $$

\item \textbf{Mahalanobis depth} (MhD) \citep{LiuPareliusSingh99} is based on the Mahalanobis distance of $\bfx$ to $\bfmu$ with respect to $\Sigma$: $d_\Sigma(\bfx, \bfmu) = \sqrt{(\bfx - \bfmu)^T \Sigma^{-1} (\bfx - \bfmu)}$. It is defined as
%
$$ MhD(\bfX, F) = \frac{1}{1 + d^2_\Sigma (\bfx - \bfmu)} $$
%
note here that $d_\Sigma(\bfx,\bfmu)$ can be seen as a valid htped function of $\bfx$ with respect to $F$.

\item \textbf{Projection depth} (PD) \citep{zuo03} is another depth function based on an outlyingness function. Here that function is
%
$$ O(\bfx, F) = \sup_{\| \bfu \| = 1} \frac{| \bfu^T\bfx - m(\bfu^T\bfX)|}{s(\bfu^T\bfX)} $$
%
where $m$ and $s$ are some univariate measures location and scale, respectively. Given this the depth at $\bfx$ is defined as $PD(\bfx, F) = 1/(1+O(\bfx, F))$.
\end{itemize}

Computation-wise, MhD is easy to calculate since the sample mean and covariance matrix are generally used as estimates of $\mu$ and $\Sigma$, respectively. However this makes MhD less robust with respect to outliers. PD is generally approximated by taking maximum over a number of random projections. There have been several approaches for calculating HD. A recent unpublished paper \citep{rainerArxiv} provides a general algorithm that computes exact HD in $O(n^{p-1}\log n)$ time. In this paper, we shall use inbuilt functions in the R package \texttt{fda.usc} for calculating the above depth functions.

### 2018-03-20 MS/Depth-scatter-summary.tex
first commit in shubhobm

\documentclass[fleqn,11pt]{article}
\usepackage{mycommands,amssymb,amsmath,amsthm,color,pagesize,outlines,cite,caption}
\usepackage[pdftex]{graphicx}
\usepackage[round]{natbib}
\addtolength{\evensidemargin}{-.5in}
\addtolength{\oddsidemargin}{-.5in}
\addtolength{\textwidth}{0.9in}
\addtolength{\textheight}{0.9in}
\addtolength{\topmargin}{-.4in}

\usepackage{hyperref} % for linking references 
\usepackage{setspace}
\doublespacing

%\DeclareMathOperator*{\vec}{vec}
\DeclareMathOperator*{\diag}{diag}
\DeclareMathOperator*{\Tr}{Tr}

\begin{document}

\newtheorem{Theorem}{Theorem}[section]
\newtheorem{Lemma}[Theorem]{Lemma}
\newtheorem{Corollary}[Theorem]{Corollary}
\theoremstyle{definition} \newtheorem{Definition}[Theorem]{Definition}

\title{Robust estimation of principal components from depth-based multivariate rank covariance matrix}
\date{}
\author{Subhabrata Majumdar}
\maketitle

Abstract:
Analyzing principal components for multivariate data from its spatial sign covariance matrix (SCM) has been proposed as a computationally simple and robust alternative to normal PCA, but it suffers from poor efficiency properties and is actually inadmissible with respect to the maximum likelihood estimator. Here we use data depth-based spatial ranks in place of spatial signs to obtain the orthogonally equivariant Depth Covariance Matrix (DCM) and use its eigenvector estimates for PCA. We derive asymptotic properties of the sample DCM and influence functions of its eigenvectors. The shapes of these influence functions indicate robustness of estimated principal components, and good efficiency properties compared to the SCM. Finite sample simulation studies show that principal components of the sample DCM are robust with respect to deviations from normality, as well as are more efficient than the SCM and its affine equivariant version, Tyler's shape matrix. Through two real data examples, we also show the effectiveness of DCM-based PCA in analyzing high-dimensional data and outlier detection, and compare it with other methods of robust PCA.
\vspace{.5cm}

Keywords:
Data depth; Principal components analysis; Robustness; Sign covariance matrix; Multivariate ranking

\newpage
\section{Introduction}
In multivariate analysis, the study of principal components is important since it provides a small number of uncorrelated variables from a potentially larger number of variables, so that these new components explain most of the underlying variability in the original data. In case of multivariate normal distribution, the sample covariance matrix provides the most asymptotically efficient estimates of eigenvectors/ principal components, but it is extremely sensitive to outliers as well as relaxations of the normality assumption. To address this issue, several robust estimators of the population covariance or correlation matrix have been proposed which can be used for Principal Components Analysis (PCA). They can be roughly put into these categories: robust, high breakdown point estimators that are computation-intensive \citep{rousseeuw85, maronna76}; M-estimators that are calculated by simple iterative algorithms but do not necessarily possess high breakdown point \citep{huber77, tyler87}; and symmetrised estomators that are highly efficient and robust to deviations from normality, but sensitive to outliers and computationally demanding \citep{dumbgen98, sirkia07}.

When principal components are of interest, one can also estimate the population eigenvectors by analyzing the spatial sign of a multivariate vector: the vector divided by its magnitude, instead of the original data. The covariance matrix of these sign vectors, namely Sign Covariance Matrix (SCM) has the same set of eigenvectors as the covariance matrix of the original population, thus the multivariate sign transformation yields computationally simple and high-breakdown estimates of principal components \citep{locantore99, visuri00}. Although the SCM is not affine equivariant, its orthogonal equivariance suffices for the purpose of PCA. However, the resulting estimates are not very efficient, and are in fact asymptotically inadmissible \citep{magyar14}, in the sense that there is an estimator (Tyler's M-estimate of scatter, to be precise) that has uniformly lower asymptotic risk than the SCM.

The nonparametric concept of data-depth had first been proposed by \cite{tukey75} when he introduced the halfspace depth. Given a dataset, the depth of a given point in the sample space measures how far inside the data cloud the point exists. An overview of statistical depth functions can be found in \citep{zuo00}. Depth-based methods have recently been popular for robust nonparametric classification \citep{jornsten04, ghosh05, dutta12, sguera14}. In parametric estimation, depth-weighted means \citep{ZuoCuiHe04} and covariance matrices \citep{ZuoCui05} provide high-breakdown point as well as efficient estimators, although they do involve choice of a suitable weight function and tuning parameters. In this paper we study the covariance matrix of the multivariate rank vector that is obtained from the data-depth of a point and its spatial sign, paying special attention to its eigenvectors. Specifically, we develop a robust version of principal components analysis for elliptically symmetric distributions based on the eigenvectors of this covariance matrix, and compare it with normal PCA and spherical PCA, i.e. PCA based on eigenvectors of the SCM.

The chapter is arranged in the following fashion. Section \ref{section:sec2} provides preliminary theoretical concepts required for developments in the subsequent sections. Section \ref{section:dcmSection} introduces the Depth Covariance Matrix (DCM) and states some basic results related to this. Section \ref{section:sec4} provides asymptotic results regarding the sample DCM, calculated using data depths with respect to the empirical distribution function, as well as its eigenvectors and eigenvalues. Section \ref{section:simSection} focuses solely on principal component estimation using the sample DCM. We obtain influence functions and asymptotic efficiencies for eigenvectors of the DCM. We also compare their finite sample efficiencies for several multinormal and multivariate $t$-distributions with those of the SCM, Tyler's scatter matrix and its depth-weighted version through a simulation study. Section \ref{section:sec6} presents two applications of the methods we develop on real data. Finally, we wrap up our discussion in Section \ref{section:sec7} by giving a summary of our findings and providing some potential future areas of research. Appendices \ref{section:appA} and \ref{section:appB} contain all technical details and proofs of the results we derive.

\section{Preliminaries}\label{section:sec2}
\subsection{Spatial signs and sign covariance matrix}
Given a vector $\bfx \in \mathbb{R}^p$, its spatial sign is defined as the vector valued function \citep{MottonenOja95}:
%
$$ \bfS(\bfx) = \begin{cases} \bfx\| \bfx \|^{-1} \quad \mbox{if }\bfx \neq \bf0\\
\bf0 \quad \mbox{if }\bfx = \bf0 \end{cases} $$
%
When $\bfx$ is a random vector that follows an elliptic distribution $|\Sigma|^{-1/2} f((\bfx - \bfmu)^T \Sigma^{-1} (\bfx - \bfmu))$, with a mean vector $\bfmu$ and covariance matrix $\Sigma$, the sign vectors $\bfS(\bfx - \bfmu)$ reside on the surface of a $p$-dimensional unit ball centered at $\bfmu$. Denote by $\Sigma_S(\bfX) = E\bfS (\bfX - \bfmu)\bfS (\bfX - \bfmu)^T$ the covariance matrix of spatial signs, or the \textit{Sign Covariance Matrix} (SCM). The transformation $\bfx \mapsto \bfS(\bfx - \bfmu)$ keeps eigenvectors of population covariance matrix unchanged, and eigenvectors of the sample SCM $ \hat \Sigma_S = \sum_{i=1}^n \bfS (\bfx_i - \bfmu)\bfS (\bfx_i - \bfmu)^T/n $ are $\sqrt n$-consistent estimators of their population counterparts \citep{taskinen12}.

The sign transformation is rotation equivariant, i.e. $ \bfS(P (\bfx - \bfmu)) = P(\bfx - \bfmu)/\| P (\bfx - \bfmu)\| = P(\bfx - \bfmu)/\|\bfx - \bfmu\| = P \bfS(\bfx - \bfmu)$ for any orthogonal matrix $P$, and as a result the SCM is rotation equivariant too, in the sense that $\Sigma_S(P\bfX) = P \Sigma_S(\bfX) P^T$. This is not necessarily true in general if $P$ is replaced by any non-singular matrix. An affine equivariant version of the sample SCM is obtained as the solution $\hat \Sigma_T$ of the following equation:
%
$$ \hat \Sigma_T(\bfX) = \frac{p}{n} \sum_{i=1}^n \frac{(\bfx - \bfmu)(\bfx - \bfmu)^T}{(\bfx - \bfmu)^T \hat\Sigma_T(\bfX)^{-1} (\bfx - \bfmu)} $$
%
which turns out to be Tyler's M-estimator of scatter \citep{tyler87}. In this context, one should note that for scatter matrices, affine equivariance will mean any affine transformation on the original random variable $\bfX \mapsto \bfX^* = A\bfX + \bfb$ ($A$ non-singular, $\bfb \in \mathbb{R}^p$) being carried over to the covariance matrix estimate upto a scalar multiple: $\hat\Sigma_T(\bfX^*) = k. A \hat\Sigma_T(\bfX) A^T$ for some $k>0$.

\subsection{Data depth and outlyingness}
For any multivariate distribution $F = F_\bfX$ belonging to a set of distributions $\mathcal F$, the depth of a point $\bfx \in \mathbb{R}^p$, say $D(\bfx, F_\bfX)$ is any real-valued function that provides a 'center outward ordering' of $\bfx$ with respect to $F$ \citep{zuo00}. \cite{liu90} outlines the desirable properties of a statistical depth function:

\vspace{1em}
\noindent\textbf{(D1)} \textit{Affine invariance}: $D(A\bfx + \bfb, F_{A\bfX+\bfb}) = D(\bfx, F_\bfX)$;

\noindent\textbf{(D2)} \textit{Maximality at center}: $D(\bftheta, F_\bfX) = \sup_{\bfx\in \mathbb{R}^p} D(\bfx, F_\bfX)$ for $F_\bfX$ having center of symmetry $\bftheta$. This point is called the \textit{deepest point} of the distribution.;

\noindent\textbf{(D3)} \textit{Monotonicity with respect to deepest point}: $D(\bfx; F_\bfX) \leq D(\bftheta + a(\bfx - \bftheta), F_\bfX)$, $\bftheta$ being deepest point of $F_\bfX$.;

\noindent\textbf{(D4)} \textit{Vanishing at infinity}: $D(\bfx; F_\bfX) \rightarrow 0$ as $\|\bfx\| \rightarrow \infty $.
\vspace{1em}

In (D2) the types of symmetry considered can be central symmetry, angular symmetry and halfspace symmetry. Also for multimodal probability distributions, i.e. distributions with multiple local maxima in their probability density functions, properties (D2) and (D3) are actually restrictive towards the formulation of a reasonable depth function that captures the shape of the data cloud. In our derivations that follow, we replace these two by a weaker condition:

\vspace{1em}
\noindent\textbf{(D2*)} \textit{Existence of a maximal point}: The maximum depth over all distributions $F$ and points $\bfx$ is bounded above, i.e. $ \sup_{F_\bfX \in \mathcal F} \sup_{\bfx\in \mathbb{R}^p} D(\bfx, F_\bfX) < \infty $. We denote this point by $M_D(F_\bfX)$.
\vspace{1em}

A real-valued function measuring the outlyingness of a point with respect to the data cloud can be seen as the opposite of what data depth does. Indeed, such functions have been used to define several depth functions, for example simplicial depth, projection depth and $L_p$-depth. Keeping with the spirit of the utility of these functions we name them `htped': literally the reverse of `depth', and give a general definition of such functions as a transformation on any depth function:

\begin{Definition}
Given a random variable $\bfX$ following a probability distribution $F$, and a depth function $D(.,.)$, we define Htped of a point $\bfx$ as: $\tilde D(\bfx, F) = h(d_\bfx)$ as any function of the data depth $D(\bfx, F) = d_\bfx$ so that $h(d_\bfx)$ is bounded, monotonically decreasing in $d_\bfx$ and $\sup_\bfx \tilde D(\bfx, F) < \infty$.
\end{Definition}

For a fixed depth function, there are several choices of a corresponding htped. We develop our theory assuming a general htped function, but for the plots and simulations, fix our htped as $\tilde D(\bfx, F) = M_D(F) - D(\bfx, F)$, i.e. simply subtract the depth of a point from the maximum possible depth over all points in sample space.

We will be using the following 3 measures of data-depth to obtain our DCMs and compare their performances:

\begin{itemize}
\item \textbf{Halfspace depth} (HD) \citep{tukey75} is defined as the minimum probability of all halfspaces containing a point. In our notations,

$$ HD(\bfx, F)  = \inf_{\bfu \in \mathbb{R}^p; \bfu \neq \bf0} P(\bfu^T \bfX \geq \bfu^T \bfx) $$

\item \textbf{Mahalanobis depth} (MhD) \citep{LiuPareliusSingh99} is based on the Mahalanobis distance of $\bfx$ to $\bfmu$ with respect to $\Sigma$: $d_\Sigma(\bfx, \bfmu) = \sqrt{(\bfx - \bfmu)^T \Sigma^{-1} (\bfx - \bfmu)}$. It is defined as
%
$$ MhD(\bfX, F) = \frac{1}{1 + d^2_\Sigma (\bfx - \bfmu)} $$
%
note here that $d_\Sigma(\bfx,\bfmu)$ can be seen as a valid htped function of $\bfx$ with respect to $F$.

\item \textbf{Projection depth} (PD) \citep{zuo03} is another depth function based on an outlyingness function. Here that function is
%
$$ O(\bfx, F) = \sup_{\| \bfu \| = 1} \frac{| \bfu^T\bfx - m(\bfu^T\bfX)|}{s(\bfu^T\bfX)} $$
%
where $m$ and $s$ are some univariate measures location and scale, respectively. Given this the depth at $\bfx$ is defined as $PD(\bfx, F) = 1/(1+O(\bfx, F))$.
\end{itemize}

Computation-wise, MhD is easy to calculate since the sample mean and covariance matrix are generally used as estimates of $\mu$ and $\Sigma$, respectively. However this makes MhD less robust with respect to outliers. PD is generally approximated by taking maximum over a number of random projections. There have been several approaches for calculating HD. A recent unpublished paper \citep{rainerArxiv} provides a general algorithm that computes exact HD in $O(n^{p-1}\log n)$ time. In this paper, we shall use inbuilt functions in the R package \texttt{fda.usc} for calculating the above depth functions.

\section{Depth-based rank covariance matrix} \label{section:dcmSection}

Consider a vector-valued random variable $\bfX \in \mathbb{R}^p$ . Data depth is as much a property of the random variable as it is of the underlying distribution, so for ease of notation while working with transformed random variables, from now on we shall be using $D_\bfX(\bfx) = D(\bfx, F)$ to denote the depth of a point $\bfx$. Now, given a depth function $D_{\bfX}(\bfx)$ (equivalently, an htped function $\tilde D_\bfX(\bfx) = \tilde D(\bfx, F)$), transform the original random variable as: $\tilde \bfx = \tilde D_\bfX(\bfx) \bfS(\bfx - \bfmu)$, $\bfS(.)$ being the spatial sign functional. The transformed random variable $\tilde \bfX$ can be seen as the multivariate rank corresponding to $\bfX$ (e.g. \cite{serfling2006}). The notion of multivariate ranks goes back to \cite{PuriSenBook}, where they take the vector consisting of marginal univariate ranks as multivariate rank vector. Subsequent definitions of multivariate ranks were proposed by \cite{MottonenOja95,HallinPaindaveine02} and \cite{Chernozhukov14}. Compared to these formulations, our definition of multivariate ranks works for any general depth function, and provides an intuitive extension to any spatial sign-based methodology.

Figure \ref{fig:rankplot} gives an idea of how the multivariate rank vector $\tilde \bfX$ is distributed when $\bfX$ has a bivariate normal distribution. Compared to the spatial sign, which are distributed on the surface of $p$-dimensional unit ball centered at $\bfmu$, these spatial ranks have the same direction as original data and reside \textit{inside} the $p$-dimensional ball around $\bfmu$ that has radius $M_D(F)$ (which, for the case of halfspace depth, equals 0.5).

\begin{figure}[t]
	\captionsetup{singlelinecheck=off}
	\centering
		\includegraphics[height=6cm]{../Codes/ranks}
	\caption{(Left) 1000 points randomly drawn from $\mathcal N_2\left((0,0)^T, \left(\protect\begin{smallmatrix} 5 & -4 \\ -4 & 5 \protect\end{smallmatrix}\right)\right) $ and (Right) their multivariate ranks based on halfspace depth}
	\label{fig:rankplot}
\end{figure}

Now consider the spectral decomposition for the covariance matrix of $F$: $\Sigma = \Gamma\Lambda\Gamma^T$, $\Gamma$ being orthogonal and $\Lambda$ diagonal with positive diagonal elements. Also normalize the original random variable as $\bfz = \Gamma^T\Lambda^{-1/2} (\bfx - \bfmu)$. In this setup, we can represent the transformed random variable as
%
\begin{eqnarray}
\tilde \bfx &=& \tilde D_{\bfX} (\bfx) \bfS(\bfX - \bfmu) \notag \\
&=& \tilde D_{\Gamma\Lambda^{1/2}\bfZ + \bfmu} (\Gamma\Lambda^{1/2} \bfz + \bfmu). \bfS(\Gamma\Lambda^{1/2} \bfz) \notag \\
&=& \Gamma \tilde D_{\bfZ}(\bfz) \bfS(\Lambda^{1/2}\bfz) \notag \\
&=& \Gamma \Lambda^{1/2} \tilde D_{\bfZ}(\bfz) \bfS(\bfz) \frac{\| \bfz \|}{\|\Lambda^{1/2} \bfz\|}
\label{equation:rankdecomp}
\end{eqnarray}
%
%Because of affine (thus rotational) invariance of a depth function, the depth (htped) value at $\bfz$ does not depend on the direction of $\bfz$, i.e. $\tilde D_{\bfZ}(\bfz)$ and $\bfS(\bfz)$ are independent. Furthermore,
%$$ Cov \left(\bfS (\bfz), \frac{\| \bfz \|}{\|\Lambda^{1/2} \bfz\|} \right) = E \left(\bfS (\bfz). \frac{\| \bfz \|}{\|\Lambda^{1/2} \bfz\|} \right) - E \bfS (\bfz) E \left(\frac{\| \bfz \|}{\|\Lambda^{1/2} \bfz\|} \right) = E \left( \frac{\bfz}{\|\Lambda^{1/2} \bfz\|} \right) = \bf0$$
%both $\bfS (\bfz)$ and $\bfz / \| \Lambda^{1/2}\bfz \|$ are odd functions of $\bfz$, which has a circularly symmetric distribution, hence each of them has expectation $\bf0$. Consequently, we obtain an expression for the covariance matrix of $\tilde \bfX$:

$\tilde D_\bfZ(\bfz)$ is an even function in $\bfz$ because of affine invariance, as is $\| \bfz \| / \|\Lambda^{1/2} \bfz \|$. Since $\bfS(\bfz)$ is odd in $\bfz$ for circularly symmetric $\bfz$, it follows that $E(\tilde \bfX) = \bf0$, and consequently we obtain an expression for the covariance matrix of $\tilde \bfX$:

\begin{Theorem} \label{Theorem:covform}
Let the random variable $\bfX \in \mathbb{R}^p$ follow an elliptical distribution with center $\bfmu$ and covariance matrix $\Sigma = \Gamma\Lambda\Gamma^T$, its spectral decomposition. Then, given a depth function $D_\bfX(.)$ the covariance matrix of the transformed random variable $\tilde\bfX$ is
\begin{equation} \label{equation:covformEq1}
Cov(\tilde \bfX) = \Gamma \Lambda_{D,S} \Gamma^T,\quad\mbox{with}\quad \Lambda_{D,S} = \mathbb E_\bfz \left[ (\tilde D_\bfZ(\bfz))^2 \frac{\Lambda^{1/2} \bfz \bfz^T \Lambda^{1/2}}{\bfz^T \Lambda \bfz} \right]
\end{equation}
where $\bfz = (z_1,...,z_p)^T \sim N({\bf 0}, I_p)$, so that $\Lambda_{D,S}$ a diagonal matrix with diagonal entries
%
$$ \lambda_{D,S,i} = \mathbb E_\bfZ \left[ \frac{(\tilde D_\bfZ(\bfz))^2 \lambda_i z_i^2}{\sum_{j=1}^p \lambda_j z_j^2} \right] $$
\end{Theorem}

The matrix of eigenvectors of the covariance matrix, $\Gamma$, remains unchanged in the transformation $\bfX \rightarrow \tilde \bfX$. As a result, the multivariate rank vectors can be used for robust principal component analysis, which will be outlined in the following sections. However, as one can see in the above expression, the diagonal entries of $\Lambda_{D,S}$ do not change if a scale change is done on all entries of $\Lambda$, meaning the $\Lambda_{D,S}$ matrices corresponding to $F$ and $cF$ for some $c \neq 0$ will be same. This is the reason for lack of affine equavariance of the DCM. Following the case of multivariate sign covariance matrices \citep{taskinen12} one can get back the shape components, i.e. original \textit{standardized} eigenvalues $\Lambda^*$ from $\Lambda_{D,S}$ by an iterative algorithm:

\begin{enumerate}
\item Set $k=0$, and start with an initial value $\Lambda^{*(0)}$.

\item Calculate the next iterate
%
$$ \Lambda^{*(k+1)} = \left[ \mathbb E_\bfz \left( \frac{(\tilde D_\bfZ(\bfz))^2 \bfz \bfz^T}{\bfz^T \Lambda^{*(k)} \bfz} \right) \right]^{-1} \Lambda_{D,S} $$
and standardize its eigenvalues:
%
$$ \Lambda^{*(k+1)} = \frac{\Lambda^{*(k+1)}}{\text{det} (\Lambda^{*(k+1)})^{1/p}} $$
%
\item Stop if convergence criterion is satisfied. Otherwise set $k \rightarrow k+1$ ad go to step 2.
\end{enumerate}

Unlike sign covariance matrices and symmetrized sign covariance matrices \citep{dumbgen98}, however, attempting to derive an affine equivariant counterpart (as opposed to only orthogonal equivariance) of the DCM through an iterative approach analogous to \cite{tyler87} will not result in anything new. This is because Tyler's scatter matrix $\Sigma_T$ is defined as the implicit solution to the following equation:
\begin{equation} \label{equation:tylerEq}
\Sigma_T = \mathbb E\left[ \frac{(\bfx - \bfmu) (\bfx - \bfmu)^T}{(\bfx - \bfmu)^T \Sigma_T^{-1} (\bfx - \bfmu)} \right]
\end{equation}
and simply replacing $\bfx$ by its multivariate rank counterpart $\tilde\bfx$ will not change the estimate $\Sigma_T$ as $\bfx$ and $\tilde \bfx$ have the same directions. Instead we consider a depth-weighted version of Tyler's scatter matrix (i.e. weights $(\tilde D_\bfX(\bfx))^2$ in right side of (\ref{equation:tylerEq})) in the simulations in Section \ref{section:simSection}. The simulations show that it has slightly better finite-sample efficiency than $\Sigma_T$ but has same asymptotic performance. We conjecture that its concentration properties can be obtained by taking an approach similar to \cite{soloveychik14}.

\section{Asymptotic results}\label{section:sec4}
\subsection{The sample DCM}
Let us now consider $n$ iid random draws from our elliptic distribution $F$, say $\bfX_1,...,\bfX_n$. For ease of notation, denote $SS(\bfx; \bfmu) = \bfS(\bfx - \bfmu) \bfS(\bfx - \bfmu)^T$. Then, given the depth function and known location center $\bfmu$, one can show that the vectorized form of $\sqrt n$-times the sample DCM: $\sum_{i=1}^n (\tilde D_\bfX(\bfx_i))^2SS(\bfx_i; \bfmu) /\sqrt{n}$  has an asymptotic multivariate normal distribution with mean $\sqrt n.vec(E[( (\tilde D_\bfX (\bfX))^2 SS(\bfx; \bfmu)])$ and a certain covariance matrix by straightforward application of the central limit theorem (CLT). But in practice the population depth function $D_\bfX(\bfx) = D(\bfx, F)$ is estimated by the depth function based on the empirical distribution function, $F_n$. Denote this sample depth by $D^n_\bfX (\bfx) = D(\bfx, F_n)$. Here we make the following assumption regarding its relation to $D_\bfX(\bfx)$:

\vspace{1em}
\noindent\textbf{(D5)} \textit{Uniform convergence}: $\sup_{\bfx \in \mathbb R^p} | D^n_\bfX (\bfx) - D_\bfX (\bfx) | \rightarrow 0$ as $n \rightarrow \infty $.
\vspace{1em}

The assumption that empirical depths converge uniformly at all points $\bfx$ to their population versions holds under very mild conditions for several well known depth functions: for example projection depth \citep{zuo03} and simplicial depth \citep{Dumbgen92}. One also needs to replace the known location parameter $\bfmu$ by some estimator $\hat\bfmu_n$. Examples of robust estimators of location that are relevant here include the spatial median \citep{haldane48,brown83}, Oja median \citep{oja83}, projection median \citep{zuo03} etc. Now, given $D^n_\bfX(.)$ and $\hat \bfmu_n$, to plug them into the sample DCM and still go through with the CLT we need the following result:

\begin{Lemma} \label{Lemma:lemma1}
Consider a random variable $\bfX \in \mathbb{R}^p$ having a continuous and symmetric distribution with location center $\bfmu$ such that $E\|\bfx - \bfmu \|^{-3/2} < \infty$. Given $n$ random samples from this distribution, suppose $\hat\bfmu_n$ is an estimator of $\bfmu$ so that $\sqrt n (\hat\bfmu_n - \bfmu) = O_P(1) $. Then with the above notations, and given the assumption (D5) we have
%
$$ \sqrt n \left[
\frac{1}{n} \sum_{i=1}^n (\tilde D^n_\bfX (\bfx_i))^2 SS(\bfx_i; \hat\bfmu_n) -
\frac{1}{n} \sum_{i=1}^n (\tilde D_\bfX (\bfx_i))^2 SS(\bfx_i; \bfmu) \right]
\stackrel{P}{\rightarrow} 0 $$
\end{Lemma}

We are now in a position to state the result for consistency of the sample DCM:

\begin{Theorem} \label{Theorem:rootn}
Consider $n$ iid samples from the distribution in Lemma \ref{Lemma:lemma1}. Then, given a depth function $D_\bfX(.)$ and an estimate of center $\hat\bfmu_n$ so that $\sqrt n(\hat \bfmu_n - \bfmu) = O_P(1)$,
%
$$ \sqrt n \left[ vec\left\{ \frac{1}{n} \sum_{i=1}^n (\tilde D^n_\bfX (\bfx_i))^2 SS(\bfx_i; \hat\bfmu_n) \right\} - E \left[ vec\left\{ (\tilde D_\bfX (\bfx))^2 SS(\bfx; \bfmu) \right\} \right] \right]
\stackrel{D}{\rightarrow}
N_{p^2} ({\bf 0}, V_{D,S}(F)) $$
$$ \text{with } V_{D,S}(F) = Var \left[vec \left\{ (\tilde D_\bfX (\bfx))^2 SS(\bfx; \bfmu) \right\} \right] $$
\end{Theorem}

In case $F$ is elliptical, an elaborate form of the covariance matrix $V_{D,S}(F)$ explicitly specifying each of its elements (more directly those of its $\Gamma^T$-rotated version) can be obtained, which is given in Appendix \ref{section:appA}. This form is useful when deriving limiting distributions of eigenvectors and eigenvalues of the sample DCM.

\subsection{Eigenvectors and eigenvalues} Since we are mainly interested in using the DCM for a robust version of principal components analysis, from now on we assume that the eigenvalues of $\Sigma$ are distinct: $\lambda_1 > \lambda_2 > ... > \lambda_p$ to obtain asymptotic distributions of principal components. In the case of eigenvalues with larger than 1 multiplicities, the limiting distributions of eigenprojection matrices can be obtained analogous to those of the sign covariance matrix \citep{magyar14}.

\paragraph{}We now derive the asymptotic joint distributions of eigenvectors and eigenvalues of the sample DCM. The following result allows us to get these, provided we know the limiting distribution of the sample DCM itself:

\begin{Theorem} \label{Theorem:decomp} \citep{taskinen12}
Let $F_\Lambda$ be an elliptical distribution with a diagonal covariance matrix $\Lambda$, and $\hat C$ be any positive definite symmetric $p \times p$ matrix such that at $F_\Lambda$ the limiting distribution of $\sqrt n vec(\hat C - \Lambda)$ is a $p^2$-variate (singular) normal distribution with mean zero. Write the spectral decomposition of $\hat C$ as $\hat C = \hat P \hat\Lambda \hat P^T$. Then the limiting distributions of $\sqrt n vec(\hat P - I_p)$ and $\sqrt n vec(\hat\Lambda - \Lambda)$ are multivariate (singular) normal and
%
\begin{equation} \label{equation:decompEq}
\sqrt n vec (\hat C - \Lambda)  = \left[ (\Lambda \otimes I_p) - (I_p \otimes \Lambda) \right] \sqrt n vec (\hat P - I_p) + \sqrt n vec (\hat\Lambda - \Lambda) + o_P(1)
\end{equation}
\end{Theorem}

The first matrix picks only off-diagonal elements of the LHS and the second one only diagonal elements. We shall now use this as well as the form of the asymptotic covariance matrix of the vec of sample DCM, i.e. $V_{D,S}(F)$ to obtain limiting variance and covariances of eigenvalues and eigenvectors.

\begin{Corollary} \label{Corollary:eigendist}
Consider the sample DCM $ \hat S^D(F) = \sum_{i=1}^n (\tilde D^n_\bfX (\bfx_i))^2 SS(\bfx_i; {\bf \hat\bfmu_n})/n $ and its spectral decomposition $\hat S^D(F) = \hat\Gamma_D \hat\Lambda_D \hat\Gamma_D^T $. Then the matrices $G = \sqrt n (\hat\Gamma_D - \Gamma) $ and $L = \sqrt n (\hat\Lambda_D - \Lambda_{D,S}) $ have independent distributions. The random variable $vec(G)$ asymptotically has a $p^2$-variate normal distribution with mean ${\bf 0}_{p^2}$, and the asymptotic variance and covariance of different columns of $G = (\bfg_1,...,\bfg_p)$ are as follows:
%
\begin{equation} \label{equation:DevEq}
AVar(\bfg_i) = \sum_{k=1; k \neq i}^p \frac{1}{(\lambda_{D,s,k} - \lambda_{D,S,i})^2} E \left[ \frac{(\tilde D_\bfZ (\bfz))^4 \lambda_i \lambda_k z_i^2 z_k^2}{(\bfz^T \Lambda \bfz)^2} \right] \bfgamma_k \bfgamma_k^T
\end{equation}
%
\begin{equation}
ACov(\bfg_i, \bfg_j) = - \frac{1}{(\lambda_{D,s,i} - \lambda_{D,S,j})^2} E \left[ \frac{(\tilde D_\bfZ (\bfz))^4 \lambda_i \lambda_j z_i^2 z_j^2}{(\bfz^T \Lambda \bfz)^2} \right] \bfgamma_j \bfgamma_i^T; \quad i \neq j
\end{equation}
%
where $\Gamma = (\bfgamma_1,...,\bfgamma_p)$. The vector consisting of diagonal elements of $L$, say $\bfl = (\l_1,...,\l_p)^T$ asymptotically has a $p$-variate normal distribution with mean ${\bf 0}_p$ and variance-covariance elements:
%
\begin{eqnarray}
AVar(l_i) &=& E \left[ \frac{(\tilde D_\bfZ (\bfz))^4 \lambda_i^2 z_i^4}{(\bfz^T \Lambda \bfz)^2} \right] - \lambda_{D,S,i}^2\\
ACov(l_i, l_j) &=& E \left[ \frac{(\tilde D_\bfZ (\bfz))^4 \lambda_i \lambda_j z_i^2 z_j^2}{(\bfz^T \Lambda \bfz)^2} \right] - \lambda_{D,S,i} \lambda_{D,S,j}; \quad i \neq j
\end{eqnarray}
%
\end{Corollary}

\section{Robustness and efficiency properties} \label{section:simSection}
In this section, we first obtain the influence functions of the DCM as well as its eigenvectors and eigenvalues, which are essential to understand how much influence a sample point, especially an infinitesimal contamination, has on any functional on the distribution \citep{hampel}. We also derive the asymptotic efficiencies of individual principal components with respect to those of the original covariance matrix and sign covariance matrix. Unlike affine equivariant estimators of shape, the Asymptotic Relative Efficiency (ARE) of eigenvectors (with respect to any other affine equivariant estimator) can not be simplified as a ratio of two scalar quantities dependent on only the distribution of $\| \bfz \|$ (e.g. \cite{taskinen12,ollilia03}). Finite sample efficiency of the DCM estimates with respect to infinitesimal contamination and heavy-tailed distributions shall also be demonstrated by a simulation study.

\subsection{Influence functions}
Given any probability distribution $F$, the influence function of any point $\bfx_0$ in the sample space $\mathcal{X}$ for some functional $T(F)$ on the distribution is defined as
%
$$ IF(\bfx_0; T,F) = \lim_{\epsilon \rightarrow 0} \frac{1}{\epsilon} (T(F_\epsilon) - T(F)) $$
%
where $F_\epsilon$ is $F$ with an additional mass of $\epsilon$ at $\bfx_0$, i.e. $F_\epsilon = (1-\epsilon)F + \epsilon \Delta_{\bfx_0}$; $\Delta_{\bfx_0}$ being the distribution with point mass at $\bfx_0$. When $T(F) = E_F g$ for some $F$-integrable function $g$, $IF(\bfx_0; T,F) = g(\bfx_0) - T(F)$. It now follows that for the DCM,
%
$$ IF(\bfx_0; Cov(\tilde \bfX), F) = (\tilde D_\bfX(\bfx_0))^2 SS(\bfx_0; \bfmu) - Cov(\tilde \bfX) $$

Following \cite{croux00}, we now get the influence function of the $i^\text{th}$ column of $\hat\Gamma_D = (\hat\bfgamma_{D,1},...,\hat\bfgamma_{D,p}); i = 1,...,p$:
%
\begin{eqnarray}
IF(\bfx_0; \hat\bfgamma_{D,i}, F) &=& \sum_{k=1; k \neq i}^p \frac{1}{\lambda_{D,S,i} - \lambda_{D,S,k}} \left\{ \bfgamma^T_k IF(\bfx_0; Cov(\tilde \bfX), \bfgamma_i) \right\} \bfgamma_k \notag \\
&=& \sum_{k=1; k \neq i}^p \frac{1}{\lambda_{D,S,i} - \lambda_{D,S,k}} \left\{ \bfgamma^T_k (\tilde D_\bfX(\bfx_0))^2 SS(\bfx_0; \bfmu)\bfgamma_i - \lambda_{D,S,i}\bfgamma_k^T\bfgamma_i \right\} \bfgamma_k \notag \\
&=& \sum_{k=1; k \neq i}^p \frac{\sqrt{\lambda_i \lambda_k} z_{0i} z_{0k}}{\lambda_{D,S,i} - \lambda_{D,S,k}}. \frac{(\tilde D_\bfZ(\bfz_0))^2 }{\bfz_0^T \Lambda \bfz_0} \bfgamma_k
\end{eqnarray}
%
where $\Gamma^T \Lambda^{-1/2} (\bfx_0 - \bfmu) = \bfz_0 = (z_{01},...,z_{0p})^T$. Clearly this influence function will be bounded, which indicates good robustness properties of principal components. Moreover, since the htped function takes small values for points close to the center of the distribution, it does not suffer from the inlier effect that is typical of the SCM and Tyler's shape matrix. The influence function for the $i^\text{th}$ eigenvector estimates of these two matrices (say $\hat\bfgamma_{S,i}$ and $\hat\bfgamma_{T,i}$, respectively) are as follows:
%
\begin{eqnarray*}
\quad IF(\bfx_0; \hat \bfgamma_{S,i}, F) &=& \sum_{k=1; k \neq i}^p \frac{\sqrt{\lambda_i \lambda_k}}{\lambda_{S,i} - \lambda_{S,k}}. \frac{z_{0i} z_{0k}}{\bfz_0^T \Lambda \bfz_0} \bfgamma_k, \text{ with } \lambda_{S,i} = E_\bfZ \left( \frac{\lambda_i z_i^2}{\sum_{j=1}^p \lambda_j z_j^2} \right) \quad \\
IF(\bfx_0; \hat \bfgamma_{T,i}, F) &=& (p+2) \sum_{k=1; k \neq i}^p \frac{\sqrt{\lambda_i \lambda_k}}{\lambda_i - \lambda_k}. \frac{z_{0i} z_{0k}}{\bfz_0^T \bfz_0} \bfgamma_k \quad 
\end{eqnarray*}
%
for $i = 1,2$. In Figure \ref{fig:IFnorm} we consider first eigenvectors of different scatter estimates for the $\mathcal{N}_2((0,0)^T, \diag(2,1))$ and plot norms of these influence functions for different values of $\bfx_0$. The plots for SCM and Tyler's shape matrix demonstrate the 'inlier effect', i.e. points close to symmetry center and the center itself having high influence. The influence function for the sample covariance matrix is obtained by replacing $(p+2)$ by $\| \bfz_0 \|^2$ in the expression of $IF(\bfx_0; \hat \bfgamma_{T,i}, F)$ above, hence is unbounded and the corresponding eigenvector estimators are not robust. In comparison, all three DCMs considered here have a bounded influence function as well as small values of the influence function at 'deep' points.

\begin{figure}[]
	\centering
		\includegraphics[width=12cm]{../Codes/IFnorm.png}
	\caption{Plot of the norm of influence function for first eigenvector of (a) sample covariance matrix, (b) SCM, (c) Tyler's scatter matrix and DCMs for (d) Halfspace depth, (e) Mahalanobis depth, (f) Projection depth for a bivariate normal distribution with $\bfmu = {\bf 0}, \Sigma = \diag(2,1)$}
	\label{fig:IFnorm}
\end{figure}

\subsection{Asymptotic and finite-sample efficiencies}
Suppose $\hat\Sigma$ is a $\sqrt n$-consistent estimator of the population covariance matrix $\Sigma$, which permits a spectral decomposition $ \hat\Sigma = \hat\Gamma \hat\Lambda \hat\Gamma^T $, where $\hat\Gamma = (\hat\bfgamma_1,...,\hat\bfgamma_p)$. Then the asymptotic variance of the eigenvectors are (see Theorem 13.5.1 in \cite{anderson})
%
\begin{equation} \label{equation:covevEq}
AVar(\sqrt n\hat \bfgamma_i) = \sum_{k=1; k \neq i}^p \frac{\lambda_i \lambda_k}{(\lambda_i - \lambda_k)^2} \bfgamma_k \bfgamma_k^T
\end{equation}
%
The asymptotic relative efficiencies of eigenvectors from the sample DCM with respect to the sample covariance matrix can now be derived using (\ref{equation:covevEq}) above and (\ref{equation:DevEq}) from Corollary \ref{Corollary:eigendist}:
%
\begin{eqnarray*}
ARE(\hat\bfgamma^D_i, \hat\bfgamma_i; F) &=& \frac{\Tr( AVar(\sqrt n\hat \bfgamma_i))}{\Tr( AVar(\sqrt n\hat \bfgamma^D_i))}\\
&=& \left[\sum_{k=1; k \neq i}^p \frac{\lambda_i \lambda_k}{(\lambda_i - \lambda_k)^2} \right] \left[ \sum_{k=1; k \neq i}^p \frac{\lambda_i \lambda_k }{(\lambda_{D,s,i} - \lambda_{D,S,k})^2} E \left( \frac{(\tilde D_\bfZ (\bfz))^4 z_i^2 z_k^2}{(\bfz^T \Lambda \bfz)^2} \right) \right]^{-1}
\end{eqnarray*}

For 2 dimensions, this expression can be somewhat simplified. Suppose the two eigenvalues are $\lambda$ and $\rho\lambda$. In that case the eigenvalues of the DCM are
%
$$ \lambda_{D,S,1} = E \left( \frac{(\tilde D_\bfZ(\bfz))^2 z_1^2}{z_1^2 + \rho z_2^2} \right), \quad
\lambda_{D,S,2} = E \left( \frac{(\tilde D_\bfZ(\bfz))^2 \rho z_2^2}{z_1^2 + \rho z_2^2} \right) $$
and by simple algebra we get
%
$$ ARE(\hat\bfgamma^D_1, \hat\bfgamma_1; F) = ARE(\hat\bfgamma^D_2, \hat\bfgamma_2; F) = \frac{1}{(1-\rho)^2} \frac{\left[ E \left( \frac{(\tilde D_\bfZ(\bfz))^2 (z_1^2 - \rho z_2^2)}{(z_1^2 + \rho z_2^2)} \right) \right]^2 }{E \left( \frac{(\tilde D_\bfZ(\bfz))^4 z_1^2z_2^2}{(z_1^2 + \rho z_2^2)^2}\right)} $$

For $\rho=0.5$, Table \ref{table:AREtable} below considers 6 different elliptic distributions (namely, bivariate $t$ with df = $5,6,10,15,25$ and bivariate normal), and summarizes the ARE for first eigenvector of the SCM, Tyler's scatter matrix and DCM for 3 choices of depth function (HSD-CM, MhD-CM, PD-CM: columns 3-5), as well as their depth-weighted versions mentioned at the end of section \ref{section:dcmSection} (HSD-wCM, MhD-wCM, PD-wCM: columns 6-8). The SCM and Tyler's M-estimator perform better than the sample covariance matrix only for a bivariate $t$-distribution with df = 5. Estimates based on depth-based covariance matrices have much better performances for all distributions, and continue to be competitive of the sample covariance matrix estimates as the base distribution approaches normality, especially those based on projection depth. Interestingly, depth-weighted versions seem to have better performances than their corresponding DCMs, more so for heavy-tailed distributions.

\begin{table}
\begin{footnotesize}
    \begin{tabular}{c|cc|ccc|ccc}
     \hline
                       & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
    Bivariate $t_5$    & 1.46 & 1.50  & 1.97   & 1.54   & 1.99  & 2.09    & 1.57    & 2.11   \\
    Bivariate $t_6$    & 0.97 & 1.00  & 1.37   & 1.12   & 1.40  & 1.45    & 1.19    & 1.49   \\
    Bivariate $t_{10}$ & 0.65 & 0.67  & 0.96   & 0.88   & 1.02  & 1.02    & 0.94    & 1.10   \\
    Bivariate $t_{15}$ & 0.57 & 0.59  & 0.87   & 0.82   & 0.94  & 0.92    & 0.87    & 1.00   \\
    Bivariate $t_{25}$ & 0.54 & 0.55  & 0.79   & 0.75   & 0.88  & 0.85    & 0.81    & 0.95   \\
    BVN   & 0.49 & 0.50  & 0.73   & 0.71   & 0.82  & 0.77    & 0.75    & 0.88   \\ \hline
    \end{tabular}
\end{footnotesize}
\caption{Asymptotic efficiencies relative to sample covariance matrix for $p=2$}
\label{table:AREtable}
\end{table}

We now obtain finite sample efficiencies of the three DCMs as well as their depth-weighted affine equivariant counterparts by a simulation study, and compare them with the same from the SCM and Tyler's scatter matrix. We consider the same 6 elliptical distributions considered in ARE calculations above, and from every distribution draw 10000 samples each for sample sizes $n = 20, 50, 100, 300, 500$. All distributions are centered at ${\bf 0}_p$, and have covariance matrix $\Sigma = \diag(p,p-1,...1)$. We consider 3 choices of $p$: 2, 3 and 4.

We use the concept of principal angles \citep{miao92} to find out error estimates for the first eigenvector of a scatter matrix. In our case, the first eigenvector will be
%
$$ \bfgamma_1 = (1,\overbrace{0,...,0}^{p-1})^T $$
%
For an estimate of the eigenvector, say $\hat\bfgamma_1$, error in prediction is measured by the smallest angle between the two lines, i.e. $ \cos^{-1} | \bfgamma_1^T \hat\bfgamma_1 | $. A smaller absolute value of this angle is equivalent to better prediction. We repeat this 10000 times and calculate the \textbf{Mean Squared Prediction Angle}:
%
$$ MSPA(\hat \bfgamma_1) = \frac{1}{10000} \sum_{m=1}^{10000} \left( \cos^{-1} \left|\bfgamma_1^T \hat\bfgamma^{(m)}_1 \right| \right)^2 $$
%
Finally, the finite sample efficiency of some eigenvector estimate $\hat\bfgamma^E_1$ relative to that obtained from the sample covariance matrix, say $\hat\bfgamma^{Cov}_1$ is obtained as:
$$ FSE(\hat\bfgamma^E_1, \hat\bfgamma^{Cov}_1) = \frac{MSPA(\hat\bfgamma^{Cov}_1)}{MSPA(\hat\bfgamma^E_1)} $$

Tables \ref{table:FSEtable2}, \ref{table:FSEtable3} and \ref{table:FSEtable4} give FSE values for $p=2,3,4$, respectively. In general, all the efficiencies increase as the dimension $p$ goes up. DCM-based estimators (columns 3-5 in each table) outperform SCM and Tyler's scatter matrix, and among the 3 depths considered, projection depth seems to give the best results. Its finite sample performances are better than Tyler's and Huber's M-estimators of scatter as well as their symmetrized counterparts (see Table 4 in \cite{sirkia07}, and quite close to the affine equivariant spatial sign covariance matrix (see Table 2 in \cite{ollilia03}) For $p=2$, $n=300, 500$ the first 5 columns of Table \ref{table:FSEtable2} approximate the asymptotic efficiencies in Table \ref{table:AREtable} well, except for the multivariate $t$-distribution with df = 5. Finally, the depth-weighted iterated versions of these 3 SCMs (columns 6-8 in each table) seem to further better the performance of their corresponding orthogonal equivariant counterparts.

\begin{table}
\begin{footnotesize}
    \begin{tabular}{c|cc|ccc|ccc}
    \hline
    $F$ = Bivariate $t_5$    & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
    $n$=20                   & 0.80 & 0.83  & 0.95   & 0.95   & 0.89  & 1.00    & 0.96    & 0.89   \\
    $n$=50                   & 0.86 & 0.90  & 1.25   & 1.10   & 1.21  & 1.32    & 1.13    & 1.25   \\
    $n$=100                  & 1.02 & 1.04  & 1.58   & 1.20   & 1.54  & 1.67    & 1.24    & 1.63   \\
    $n$=300                  & 1.24 & 1.28  & 1.81   & 1.36   & 1.82  & 1.93    & 1.44    & 1.95   \\
    $n$=500                  & 1.25 & 1.29  & 1.80   & 1.33   & 1.84  & 1.91    & 1.39    & 1.97   \\ \hline
    $F$ = Bivariate $t_6$    & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
    $n$=20                   & 0.77 & 0.79  & 0.92   & 0.92   & 0.86  & 0.96    & 0.92    & 0.85   \\
    $n$=50                   & 0.76 & 0.78  & 1.11   & 1.00   & 1.08  & 1.17    & 1.03    & 1.13   \\
    $n$=100                  & 0.78 & 0.79  & 1.27   & 1.06   & 1.33  & 1.35    & 1.11    & 1.41   \\
    $n$=300                  & 0.88 & 0.91  & 1.29   & 1.09   & 1.35  & 1.38    & 1.15    & 1.45   \\
    $n$=500                  & 0.93 & 0.96  & 1.37   & 1.13   & 1.40  & 1.44    & 1.19    & 1.48   \\ \hline
    $F$ = Bivariate $t_{10}$ & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
    $n$=20                   & 0.70 & 0.72  & 0.83   & 0.84   & 0.77  & 0.89    & 0.87    & 0.79   \\
    $n$=50                   & 0.58 & 0.60  & 0.90   & 0.84   & 0.86  & 0.95    & 0.88    & 0.91   \\
    $n$=100                  & 0.57 & 0.59  & 0.92   & 0.87   & 0.97  & 0.98    & 0.90    & 1.03   \\
    $n$=300                  & 0.62 & 0.64  & 0.93   & 0.85   & 0.99  & 0.99    & 0.91    & 1.06   \\
    $n$=500                  & 0.62 & 0.65  & 0.93   & 0.86   & 1.00  & 1.00    & 0.92    & 1.08   \\ \hline
    $F$ = Bivariate $t_{15}$ & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
    $n$=20                   & 0.63 & 0.66  & 0.76   & 0.78   & 0.72  & 0.81    & 0.81    & 0.73   \\
    $n$=50                   & 0.52 & 0.52  & 0.79   & 0.75   & 0.80  & 0.84    & 0.79    & 0.85   \\
    $n$=100                  & 0.51 & 0.52  & 0.83   & 0.77   & 0.88  & 0.88    & 0.81    & 0.94   \\
    $n$=300                  & 0.55 & 0.56  & 0.84   & 0.79   & 0.91  & 0.89    & 0.84    & 0.98   \\
    $n$=500                  & 0.56 & 0.59  & 0.85   & 0.80   & 0.93  & 0.91    & 0.86    & 0.99   \\ \hline
    $F$ = Bivariate $t_{25}$ & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
    $n$=20                   & 0.63 & 0.65  & 0.77   & 0.79   & 0.74  & 0.80    & 0.81    & 0.74   \\
    $n$=50                   & 0.49 & 0.50  & 0.73   & 0.71   & 0.76  & 0.78    & 0.75    & 0.80   \\
    $n$=100                  & 0.45 & 0.46  & 0.73   & 0.69   & 0.81  & 0.78    & 0.73    & 0.87   \\
    $n$=300                  & 0.51 & 0.52  & 0.78   & 0.75   & 0.87  & 0.83    & 0.79    & 0.94   \\
    $n$=500                  & 0.53 & 0.55  & 0.79   & 0.75   & 0.87  & 0.84    & 0.80    & 0.94   \\ \hline
    $F$ = BVN                & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
    $n$=20                   & 0.56 & 0.60  & 0.69   & 0.71   & 0.67  & 0.73    & 0.74    & 0.68   \\
    $n$=50                   & 0.42 & 0.43  & 0.66   & 0.66   & 0.70  & 0.71    & 0.69    & 0.75   \\
    $n$=100                  & 0.42 & 0.43  & 0.69   & 0.66   & 0.77  & 0.74    & 0.71    & 0.83   \\
    $n$=300                  & 0.47 & 0.49  & 0.71   & 0.69   & 0.82  & 0.76    & 0.73    & 0.88   \\
    $n$=500                  & 0.48 & 0.50  & 0.73   & 0.71   & 0.83  & 0.78    & 0.76    & 0.89   \\ \hline
    \end{tabular}
\end{footnotesize}
\caption{Finite sample efficiencies of several scatter matrices: $p=2$}
\label{table:FSEtable2}
\end{table}

\begin{table}
\begin{footnotesize}
   \begin{tabular}{c|cc|ccc|ccc}
    \hline
    3-variate $t_5$    & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
    $n$=20             & 0.96 & 0.97  & 1.06   & 1.03   & 0.99  & 1.07    & 1.06    & 0.97   \\
    $n$=50             & 1.07 & 1.08  & 1.28   & 1.20   & 1.18  & 1.33    & 1.23    & 1.20   \\
    $n$=100            & 1.12 & 1.15  & 1.49   & 1.31   & 1.40  & 1.57    & 1.38    & 1.48   \\
    $n$=300            & 1.49 & 1.54  & 2.09   & 1.82   & 2.07  & 2.19    & 1.93    & 2.18   \\
    $n$=500            & 1.60 & 1.66  & 2.18   & 1.87   & 2.21  & 2.27    & 1.95    & 2.30   \\ \hline
    3-variate $t_6$    & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
    $n$=20             & 0.90 & 0.92  & 1.00   & 0.99   & 0.95  & 1.02    & 1.01    & 0.94   \\
    $n$=50             & 0.95 & 0.96  & 1.16   & 1.09   & 1.09  & 1.21    & 1.14    & 1.11   \\
    $n$=100            & 0.98 & 0.99  & 1.32   & 1.22   & 1.25  & 1.38    & 1.27    & 1.29   \\
    $n$=300            & 1.10 & 1.14  & 1.57   & 1.40   & 1.58  & 1.62    & 1.47    & 1.64   \\
    $n$=500            & 1.17 & 1.20  & 1.57   & 1.43   & 1.60  & 1.63    & 1.51    & 1.67   \\ \hline
    3-variate $t_{10}$ & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
    $n$=20             & 0.87 & 0.88  & 0.95   & 0.94   & 0.90  & 0.97    & 0.98    & 0.89   \\
    $n$=50             & 0.77 & 0.79  & 0.96   & 0.92   & 0.94  & 0.99    & 0.96    & 0.95   \\
    $n$=100            & 0.75 & 0.76  & 1.02   & 0.95   & 1.01  & 1.06    & 1.00    & 1.05   \\
    $n$=300            & 0.73 & 0.75  & 1.03   & 0.98   & 1.10  & 1.08    & 1.03    & 1.15   \\
    $n$=500            & 0.73 & 0.76  & 1.02   & 0.98   & 1.09  & 1.06    & 1.02    & 1.14   \\ \hline
    3-variate $t_{15}$ & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
    $n$=20             & 0.84 & 0.86  & 0.92   & 0.92   & 0.89  & 0.94    & 0.94    & 0.87   \\
    $n$=50             & 0.75 & 0.76  & 0.92   & 0.90   & 0.90  & 0.96    & 0.94    & 0.93   \\
    $n$=100            & 0.66 & 0.67  & 0.91   & 0.87   & 0.95  & 0.96    & 0.92    & 1.00   \\
    $n$=300            & 0.61 & 0.64  & 0.90   & 0.87   & 1.00  & 0.93    & 0.91    & 1.04   \\
    $n$=500            & 0.65 & 0.67  & 0.89   & 0.87   & 0.99  & 0.93    & 0.91    & 1.03   \\ \hline
    3-variate $t_{25}$ & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
    $n$=20             & 0.78 & 0.79  & 0.87   & 0.89   & 0.87  & 0.89    & 0.92    & 0.86   \\
    $n$=50             & 0.70 & 0.71  & 0.88   & 0.86   & 0.88  & 0.91    & 0.90    & 0.90   \\
    $n$=100            & 0.61 & 0.63  & 0.86   & 0.83   & 0.89  & 0.90    & 0.88    & 0.94   \\
    $n$=300            & 0.58 & 0.59  & 0.83   & 0.80   & 0.92  & 0.87    & 0.85    & 0.98   \\
    $n$=500            & 0.62 & 0.64  & 0.83   & 0.82   & 0.94  & 0.88    & 0.87    & 0.99   \\ \hline
    3-variate Normal   & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
    $n$=20             & 0.76 & 0.78  & 0.85   & 0.87   & 0.84  & 0.87    & 0.90    & 0.83   \\
    $n$=50             & 0.66 & 0.67  & 0.82   & 0.81   & 0.84  & 0.86    & 0.86    & 0.86   \\
    $n$=100            & 0.56 & 0.58  & 0.77   & 0.75   & 0.83  & 0.82    & 0.79    & 0.87   \\
    $n$=300            & 0.53 & 0.55  & 0.75   & 0.74   & 0.85  & 0.79    & 0.78    & 0.90   \\
    $n$=500            & 0.56 & 0.58  & 0.76   & 0.76   & 0.87  & 0.80    & 0.80    & 0.92   \\ \hline
    \end{tabular}
\end{footnotesize}
\caption{Finite sample efficiencies of several scatter matrices: $p=3$}
\label{table:FSEtable3}
\end{table}

\begin{table}
\begin{footnotesize}
    \begin{tabular}{c|cc|ccc|ccc}
    \hline
    4-variate $t_5$    & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
    $n$=20             & 1.04 & 1.02  & 1.10   & 1.07   & 1.02  & 1.09    & 1.07    & 0.98   \\
    $n$=50             & 1.08 & 1.08  & 1.16   & 1.16   & 1.13  & 1.19    & 1.19    & 1.13   \\
    $n$=100            & 1.31 & 1.31  & 1.42   & 1.38   & 1.36  & 1.46    & 1.44    & 1.36   \\
    $n$=300            & 1.46 & 1.54  & 1.81   & 1.76   & 1.95  & 1.88    & 1.88    & 1.95   \\
    $n$=500            & 1.92 & 1.93  & 2.23   & 2.03   & 2.31  & 2.35    & 2.19    & 2.39   \\ \hline
    4-variate $t_6$    & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
    $n$=20             & 1.00 & 1.05  & 1.03   & 1.05   & 1.00  & 1.04    & 1.04    & 0.95   \\
    $n$=50             & 1.03 & 1.01  & 1.13   & 1.12   & 1.11  & 1.19    & 1.17    & 1.10   \\
    $n$=100            & 1.08 & 1.12  & 1.25   & 1.23   & 1.27  & 1.24    & 1.25    & 1.22   \\
    $n$=300            & 1.34 & 1.36  & 1.64   & 1.52   & 1.60  & 1.67    & 1.61    & 1.68   \\
    $n$=500            & 1.26 & 1.34  & 1.55   & 1.49   & 1.60  & 1.65    & 1.61    & 1.69   \\ \hline
    4-variate $t_{10}$ & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
    $n$=20             & 0.90 & 0.89  & 0.95   & 0.98   & 0.98  & 0.96    & 1.01    & 0.95   \\
    $n$=50             & 0.90 & 0.91  & 1.01   & 0.98   & 0.98  & 1.03    & 1.04    & 0.99   \\
    $n$=100            & 0.87 & 0.87  & 0.93   & 0.95   & 1.01  & 0.99    & 1.01    & 1.05   \\
    $n$=300            & 0.87 & 0.87  & 1.09   & 1.09   & 1.17  & 1.14    & 1.16    & 1.23   \\
    $n$=500            & 0.88 & 0.92  & 1.10   & 1.10   & 1.23  & 1.19    & 1.22    & 1.29   \\ \hline
    4-variate $t_{15}$ & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
    $n$=20             & 0.92 & 0.90  & 0.94   & 0.94   & 0.96  & 0.95    & 0.97    & 0.89   \\
    $n$=50             & 0.82 & 0.83  & 0.88   & 0.91   & 0.93  & 0.88    & 0.93    & 0.93   \\
    $n$=100            & 0.84 & 0.87  & 0.92   & 0.95   & 1.00  & 0.93    & 0.96    & 1.00   \\
    $n$=300            & 0.73 & 0.75  & 0.96   & 0.99   & 1.10  & 1.00    & 1.06    & 1.12   \\
    $n$=500            & 0.73 & 0.76  & 0.95   & 0.96   & 1.06  & 0.94    & 0.97    & 1.06   \\ \hline
    4-variate $t_{25}$ & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
    $n$=20             & 0.89 & 0.92  & 0.92   & 0.92   & 0.90  & 0.96    & 0.95    & 0.89   \\
    $n$=50             & 0.82 & 0.84  & 0.89   & 0.90   & 0.91  & 0.93    & 0.96    & 0.92   \\
    $n$=100            & 0.77 & 0.76  & 0.90   & 0.90   & 0.96  & 0.94    & 0.98    & 1.04   \\
    $n$=300            & 0.73 & 0.77  & 0.93   & 0.91   & 0.98  & 1.00    & 0.98    & 1.03   \\
    $n$=500            & 0.67 & 0.71  & 0.83   & 0.83   & 0.96  & 0.88    & 0.90    & 1.00   \\ \hline
    4-variate Normal   & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
    $n$=20             & 0.82 & 0.84  & 0.87   & 0.90   & 0.91  & 0.89    & 0.93    & 0.89   \\
    $n$=50             & 0.80 & 0.81  & 0.87   & 0.88   & 0.88  & 0.88    & 0.92    & 0.88   \\
    $n$=100            & 0.68 & 0.71  & 0.80   & 0.85   & 0.91  & 0.82    & 0.86    & 0.92   \\
    $n$=300            & 0.61 & 0.63  & 0.82   & 0.85   & 0.93  & 0.86    & 0.91    & 0.96   \\
    $n$=500            & 0.60 & 0.64  & 0.77   & 0.80   & 0.90  & 0.82    & 0.86    & 0.96   \\ \hline
    \end{tabular}
\end{footnotesize}
\caption{Finite sample efficiencies of several scatter matrices: $p=4$}
\label{table:FSEtable4}
\end{table}

\section{Examples in real data analysis}\label{section:sec6}
%\subsection{Communities and crime data}
%This data is from the UCI machine learning repository [], and consists information on 101 demographic and socio-economic variables (like population, racial percentages, percentage of people living in urbal areas etc.)  in 1994 community areas in the United States. The dataset is a combination of data from the 1990 US Census, 1990 US Law Enforcement Management and Administrative Statistics survey and 1995 FBI Uniform Crime Reporting data.
%
%With the goal of building a model for the total number of violent crimes per 100K population from others, we initially do normal and depth-based PCA on the other variables. While doing the depth-based PCA, we use projection depth as our chosen depth function. After obtaining the PCA models, we take the first $k$ PCs in each case and build linear models for both the methods. This is repeated for $k = 1,2,...,100$ and the $R^2$ values on principal components regression models of the two types are plotted in Figure \ref{fig:rsqplot}. For building linear regression models, we keep all the predictors unchanged, while go for an inverse cubic transformation on the response variable. We do this since boxcox transformations on all of the models we consider suggest optimal power transformations of values close to --3.
%
%From the screeplots in \ref{fig:screeplot} we see that both the methods explain similar amounts of variances in the leading few PCs. As for the model performances, linear regressions based on depth-PCA have slightly higher $R^2$ values when the top few (upto 10) principal components are used. At around 20 PCs the two models have same $R^2$ values and the normal PC-regression models perform slightly better after that.
%
%\begin{figure}[t]
%	\captionsetup{singlelinecheck=off}
%	\centering
%		\includegraphics[height=5cm]{../Codes/crime_screeplots.png}
%	\caption{(Left) Screeplots for two types of PCA on communities data}
%	\label{fig:screeplot}
%\end{figure}
%
%\begin{figure}[t]
%	\captionsetup{singlelinecheck=off}
%	\centering
%		\includegraphics[height=7cm]{../Codes/crime_Rsq_plot.png}
%	\caption{(Left) Change of $R^2$ values for normal and depth-based principal components regression models on communities data}
%	\label{fig:rsqplot}
%\end{figure}

\subsection{Bus data}
This dataset is available in the R package \texttt{rrcov}, and consists of data on images of 218 buses. The 18 variables here correspond to several features related to these images. Here we extend upon the analysis in \cite{maronna06}, pp. 213 to compare the classical PCA and 3 different methods of robust PCA (including that using SCM) with our DCM-based method. Similar to the original analysis, we set aside variable 9 and scale the other variables by dividing with their respective median absolute deviations (MAD). This is done because all the variables had much larger standard deviations compared to their MADs, and variable 9 had MAD = 0.

For the sake of uniformity, we use projection depth as our fixed depth function while doing depth-based PCA in our data analysis examples. We compare the outputs of classical (CPCA) and depth-based PCA (DPCA) with the following 3 robust methods: Spherical PCA, i.e. PCA based on the SCM (SPCA), PCs obtained by the ROBPCA algorithm \citep{hubert05}, and the Minimum Covariance Determinant (MCD) estimator \citep{Rousseeuw84leastmedian} (MPCA). Table \ref{table:bus_table1} gives the proportions of variability that are left unexplained after the top $q$ $(= 1,...,6)$ components are taken into account in each of the 5 methods. The first PC in classical PCA seems to explain a much higher proportion of variability in original data than robust methods. However, as noted in \cite{maronna06} and \cite{hubert05}, this is a result of the classical variances being inflated due to outliers in the direction of the first principal axis. Among the robust methods, the proportions of unexplained variances are highest for DCM-based PCA for all values of $q$.

Table \ref{table:bus_table2} demonstrates why robust methods actually give a better representation of the underlying data structure than classical PCA here. Each of its column lists different quantiles of the squared orthogonal distance for a sample point from the hyperplane formed by top 3 PCs estimated by the corresponding method. For PCA based on projection-DCM, the estimated principal component subspaces are closer to the data than CPCA for more than 90\% of samples, and the distance only becomes larger for higher quantiles. This means that for CPCA, estimated basis vectors of the hyperspace get pulled by extreme outlying points, while the influence of these outliers is very low for DPCA. SPCA and ROBPCA perform very closely in this respect, the percentage of points that have less squared distance than CPCA being between 80\% and 90\% for both of them. This percentage is only 50\% for MPCA, which suggests that the corresponding 3-dimensional subspace estimated by MCD is possibly not an accurate representation of the truth.

\begin{table}[t]
\centering
    \begin{tabular}{c|ccccc}
    \hline
    \begin{large} $q$ \end{large} & \multicolumn{5}{c}{Method of PCA}         \\ \cline{2-6}
    ~                   & CPCA     & SPCA & ROBPCA & MPCA & DPCA \\\hline 
    1                   & 0.188         & 0.549     & 0.410  & 0.514     & 0.662     \\
    2                   & 0.084         & 0.272     & 0.214  & 0.337     & 0.359     \\
    3                   & 0.044         & 0.182     & 0.121  & 0.227     & 0.237     \\
    4                   & 0.026         & 0.135     & 0.083  & 0.154     & 0.173     \\
    5                   & 0.018         & 0.099     & 0.054  & 0.098     & 0.115     \\
    6                   & 0.012         & 0.069     & 0.036  & 0.070     & 0.084     \\ \hline
    \end{tabular}
    \caption{Unexplained proportions of variability by PCA models with $q$ components for bus data}
    \label{table:bus_table1}
\end{table}

\begin{table}[t]
\centering
    \begin{tabular}{c|ccccc}
    \hline
    Quantile & \multicolumn{5}{c}{Method of PCA}         \\ \cline{2-6}
    ~                   & CPCA     & SPCA & ROBPCA & MPCA & DPCA \\\hline 
    10\%      & 1.9       & 1.2       & 1.2    & 1.0       & 1.2       \\
    20\%      & 2.3       & 1.6       & 1.6    & 1.3       & 1.6       \\
    30\%      & 2.8       & 1.8       & 1.8    & 1.7       & 1.9       \\
    40\%      & 3.2       & 2.2       & 2.1    & 2.1       & 2.3       \\
    50\%      & 3.7       & 2.6       & 2.5    & 3.1       & 2.6       \\
    60\%      & 4.4       & 3.1       & 3.0    & 5.9       & 3.2       \\
    70\%      & 5.4       & 3.8       & 3.9    & 25.1      & 3.9       \\
    80\%      & 6.5       & 5.2       & 4.8    & 86.1      & 4.8       \\
    90\%      & 8.2       & 9.0       & 10.9   & 298.2     & 6.9      \\
    Max       & 24        & 1037      & 1055   & 1037      & 980      \\\hline
    \end{tabular}
    \caption{Quantiles to squared distance from 3-principal component hyperplanes for bus data}
    \label{table:bus_table2}
\end{table}

\subsection{Octane data}
We now apply our method to a high-dimensional dataset and demonstrate its effectiveness in outlier detection. Due to \cite{esbensen94}, this dataset consists of 226 variables and 39 observations. Each observation is a gasoline sample with a certain octane number, and have their NIR absorbance spectra measured in 2 nm intervals between 1100 - 1550 nm. There are 6 outliers here: compounds 25, 26 and 36-39, which contain alcohol. Proportions of \textit{explained} variability by PCs obtained by the two methods are given in Figure \ref{fig:screeplot}. Once again, the first PC in CPCA explains a much larger proportion of variance than DPCA. Second and third PCs obtained by DPCA explain higher proportions of variability than the corresponding components in CPCA.

In both methods, the first two PCs explains a large amount (98\% for CPCA, 89\% for DPCA) of underlying variability. But in DPCA, these PCs are more effective in detecting outliers, which we demonstrate in Figure \ref{fig:distplot}. For any method of PCA with $k$ components on a dataset of $n$ observations and $p$ variables, the \textbf{score distance} (SD) and \textbf{orthogonal distance} (OD) for $i^\text{th}$ observation ($i=1,2,...,n$) are defined as:
$$ SD_i = \sqrt{ \sum_{j=1}^k \frac{s^2_{ij}}{\lambda_j}}; \quad OD_i = \| \bfx_i - P\bfs_i^T \| $$
where $S = (\bfs_1, \ldots ,\bfs_n)^T$ is the $n\times k$ scoring matrix, $P$ the $p\times k$ loading matrix, and $\lambda_1,\ldots ,\lambda_k$ are eigenvalues obtained from the PCA, and $\bfx_1,\ldots,\bfx_n$ are the $n$ observation vectors. We only consider the first 2 PCs here, so $k$ is set to 2. From a practical standpoint, $SD_i$ can be interpreted as a weighted norm of the projection of the $i^\text{th}$ point on the hyperplane formed by first $k$ principal components, and $OD_i$ the orthogonal distance of point $i$ from that hyperplane. For outlier detection, following \cite{hubert05} we set the upper cutoff values for score distances at $\sqrt{\chi^2_{2,.975}}$ and orthogonal distances at $[\text{median}(OD^{2/3}) + \text{MAD}(OD^{2/3})\Phi^{-1}(0.975)]^{3/2}$, where $\Phi(.)$ is the standard normal cumulative distribution function. These cutoffs are marked by red lines in the diagnostic plots in figure \ref{fig:distplot}. In the figure we see that CPCA detects only 1 of the 6 outliers (point 26, left panel). Compared to this the diagnostic plot corresponding to DPCA in the right panel correctly detects all 6 outlying points. All of them have larger score distances than the score cutoff value, while points 25, 26 and 38 have higher-than-cutoff orthogonal distances as well. Interestingly, the arrangement of outlying points here is similar to that in the diagnostic plot corresponding to ROBPCA, which can be found in figure 5(b) of \cite{hubert05}.

\begin{figure}[t]
	\centering
		\includegraphics[height=6cm]{../Codes/octane_screeplot.pdf}
	\caption{Explained variance proportions for two types of PCA on octane data}
	\label{fig:screeplot}
\end{figure}
\begin{figure}[t]
	\centering
		\includegraphics[height=6.5cm]{../Codes/octane_distanceplot.pdf}
	\caption{Distance plots for two types of PCA on octane data}
	\label{fig:distplot}
\end{figure}

\section{Conclusion}\label{section:sec7}

In the above sections we introduce a covariance matrix based on depth-based multivariate ranks that keeps the eigenvectors of the actual population unchanged for elliptical distributions. We provide asymptotic results for the sample DCM, its eigenvalues and eigenvectors. Bounded influence functions as well as simulation studies suggest that the eigenvector estimates obtained from the DCM are highly robust, yet do not lose much in terms of efficiency. Thus it provides a plausible alternative to existing approaches of robust PCA that are based on estimation of covariance matrices (for example SCM, Tyler's scatter matrix, D\"{u}mbgen's symmetrized shape matrix).

An immediate extension of this would be to study the depth-weighted iterated scatter matrices, i.e. matrices $\Sigma_{Dw}$ that are solution to the following type of equations:

$$ \Sigma_{Dw} = E \left[ \frac{(\tilde D_\bfX(\bfx))^2 (\bfx - \bfmu) (\bfx - \bfmu)^T}{(\bfx - \bfmu)^T \Sigma_{Dw}^{-1} (\bfx - \bfmu)} \right] $$
as their eigenvector estimates seem to have better efficiency than those obtained from the corresponding DCMs. Unlike the DCM, these matrices will possess the affine equivariance property. It is possible to develop tests for central and elliptic symmetry based on the decomposition of the multivariate rank vector in equation \ref{equation:rankdecomp}. The result in Theorem \ref{Theorem:covform} is based on the fact that $E(\tilde \bfX) = \bf0$, and it holds for any centrally symmetric underlying distribution. Moreover, the depth of a point in the standardized scale (i.e. $\bfz$-scale) does not depend on the direction of $\bfz$. This is not possible without circular symmetry of $\bfz$, so any test of independence between $D_\bfZ (\bfz)$ and $\bfS (\bfz)$ can be seen as a test of ellipticity for the original random variable $\bfX$. Finally the applicability of this procedure in high-dimensional and functional data remains to be explored.

\appendix
\section*{Appendix}
\numberwithin{equation}{section}
\section{\textbf{Form of $V_{D,S}(F)$}}\label{section:appA}

First observe that for $F$ having covariance matrix $\Sigma = \Gamma\Lambda\Gamma^T$,
%
$$ V_{D,S}(F)  = (\Gamma \otimes \Gamma) V_{D,S}(F_\Lambda) (\Gamma \otimes \Gamma)^T$$
%
where $F_\Lambda$ has the same elliptic distribution as $F$, but with covariance matrix $\Lambda$. Now,
%
\begin{eqnarray*}
V_{D,S} (F_\Lambda) &=& E \left[ vec \left\{ \frac{(\tilde D_\bfZ (\bfz))^2 \Lambda^{1/2} \bfz\bfz^T \Lambda^{1/2}}{\bfz^T\Lambda\bfz} - \Lambda_{D,S} \right\} vec^T \left\{ \frac{(\tilde D_\bfZ (\bfz))^2 \Lambda^{1/2} \bfz\bfz^T \Lambda^{1/2}}{\bfz^T\Lambda\bfz} - \Lambda_{D,S} \right\} \right]\\
&=& E \left[ vec \left\{ (\tilde D_\bfZ (\bfz))^2 SS(\Lambda^{1/2}\bfz; \bf0) \right\} vec^T \left\{ (\tilde D_\bfZ (\bfz))^2 SS(\Lambda^{1/2}\bfz; \bf0) \right\} \right]\\
&& - \quad vec(\Lambda_{D,S}) vec^T(\Lambda_{D,S})
\end{eqnarray*}

The matrix $vec(\Lambda_{D,S}) vec^T(\Lambda_{D,S})$ consists of elements $\lambda_i\lambda_j$ at $(i,j)^\text{th}$ position of the $(i,j)^\text{th}$ block, and 0 otherwise. These positions correspond to variance and covariance components of on-diagonal elements. For the expectation matrix, all its elements are of the form $E[\sqrt{\lambda_a \lambda_b \lambda_c \lambda_d} z_a z_b z_c z_d . (\tilde D_\bfZ (\bfz))^4 / (\bfz^T \Lambda \bfz)^2]$, with $1 \leq a,b,c,d \leq p$. Since $(\tilde D_\bfZ (\bfz))^4 / (\bfz^T \Lambda \bfz)^2$ is even in $\bfz$, which has a circularly symmetric distribution, all such expectations will be 0 unless $a=b=c=d$, or they are pairwise equal. Following a similar derivation for spatial sign covariance matrices in \cite{magyar14}, we collect the non-zero elements and write the matrix of expectations:
%
$$ (I_{p^2} + K_{p,p}) \left\{ \sum_{a=1}^p \sum_{b=1}^p \gamma^D_{ab} (\bfe_a \bfe_a^T \otimes  \bfe_b \bfe_b^T) - \sum_{a=1}^p \gamma^D_{aa} (\bfe_a \bfe_a^T \otimes  \bfe_a \bfe_a^T) \right\} + \sum_{a=1}^p \sum_{b=1}^p \gamma^D_{ab} (\bfe_a \bfe_b^T \otimes  \bfe_a \bfe_b^T) $$
%
where $I_k = (\bfe_1,...,\bfe_k), K_{m,n} = \sum_{i=1}^m \sum_{j=1}^n J_{ij} \otimes J_{ij}^T$ with $J_{ij}$ the $m \times n$ matrix having 1 as $(i,j)^\text{th}$ element and 0 elsewhere, and $\gamma^D_{mn} = E[ \lambda_m \lambda_n z_m^2 z_n ^2 . (\tilde D_\bfZ (\bfz))^4 / (\bfz^T \Lambda \bfz)^2]; 1 \leq m,n \leq p$.

\paragraph{}Putting everything together, denote $\hat S^D(F_\Lambda) = \sum_{i=1}^n (\tilde D^n_\bfZ (\bfz_i))^2 SS(\Lambda^{1/2}\bfz_i; \hat \bfmu_n)/n $. Then the different types of elements in the matrix $V_{D,S}(F_\Lambda)$ are as given below ($1 \leq a,b,c,d \leq p$):

\begin{itemize}
\item Variance of on-diagonal elements
%
$$ AVar( \sqrt n \hat S^D_{aa} (F_\Lambda)) = E \left[ \frac{(\tilde D_\bfZ (\bfz))^4 \lambda_a^2 z_a^4}{(\bfz^T \Lambda \bfz)^2} \right] - \lambda_{D,S,a}^2 $$

\item Variance of off-diagonal elements ($a \neq b$)
%
$$ AVar( \sqrt n \hat S^D_{ab} (F_\Lambda)) = E \left[ \frac{(\tilde D_\bfZ (\bfz))^4 \lambda_a \lambda_b z_a^2 z_b^2}{(\bfz^T \Lambda \bfz)^2} \right] $$

\item Covariance of two on-diagonal elements ($a \neq b$)
%
$$ ACov(\sqrt n \hat S^D_{aa} (F_\Lambda), \sqrt n \hat S^D_{bb} (F_\Lambda))
= E \left[ \frac{(\tilde D_\bfZ (\bfz))^4 \lambda_a \lambda_b z_a^2 z_b^2}{(\bfz^T \Lambda \bfz)^2} \right] - \lambda_{D,S,a} \lambda_{D,S,b} $$

\item Covariance of two off-diagonal elements ($a \neq b \neq c \neq d$)
%
$$ ACov(\sqrt n \hat S^D_{ab} (F_\Lambda), \sqrt n \hat S^D_{cd} (F_\Lambda)) = 0 $$

\item Covariance of one off-diagonal and one on-diagonal element ($a \neq b \neq c$)
%
$$ ACov(\sqrt n \hat S^D_{ab} (F_\Lambda), \sqrt n \hat S^D_{cc} (F_\Lambda)) = 0 $$
\end{itemize}

\section{Proofs}\label{section:appB}

\begin{proof}[Proof of Theorem  \ref{Theorem:covform}]
The proof follows directly from writing out the expression of $Cov ( \tilde \bfX)$:
%
\begin{eqnarray*}
Cov(\tilde\bfX) &=& E(\tilde\bfX \tilde\bfX^T) - E(\tilde\bfX) E(\tilde\bfX)^T\\
&=& \Gamma . E \left[ (\tilde D_\bfZ(\bfz))^2 \frac{\|\bfz\|^2}{\| \Lambda^{1/2}\bfz\|} \Lambda^{1/2} \bfS(\bfz) \bfS(\bfz)^T \Lambda^{1/2} \right] \Gamma^T - {\bf 0}_p {\bf 0}_p^T\\
&=& \Gamma .E \left[ (\tilde D_\bfZ(\bfz))^2 \frac{\Lambda^{1/2} \bfz \bfz^T \Lambda^{1/2}}{\bfz^T \Lambda \bfz} \right] \Gamma^T
\end{eqnarray*}
%
\end{proof}

\begin{proof}[Proof of Lemma \ref{Lemma:lemma1}]
For two positive definite matrices $A,B$, we denote by $A>B$ that $A-B$ is positive definite. Also, denote
%
$$ S_n = \sqrt n \left[ \frac{1}{n} \sum_{i=1}^n \left| (\tilde D^{n} _\bfX (\bfx_i))^2  - (\tilde D_\bfX (\bfx_i))^2 \right| SS(\bfx_i; \hat\bfmu_n) \right] $$
%
%Consider now the quantity $\bft^T S_n \bft$, where $\bft \in \mathbb{R}^p$. Now applying Cauchy-Schwarz inequality we shall have
%%
%\begin{eqnarray}\label{eqn:AppEqn1}
%\frac{(\bft^T S_n \bft)^2}{n} & = & \left[ \frac{1}{n} \sum_{i=1}^n \left| (\tilde D^{n} _\bfX (\bfx_i))^2  - (\tilde D_\bfX (\bfx_i))^2 \right|^2  \bft^T SS(\bfx_i; \hat\bfmu_n) \bft \right]^2 \notag\\
%& \leq & \left[ \frac{1}{n} \sum_{i=1}^n \left| (\tilde D^{n} _\bfX (\bfx_i))^2  - (\tilde D_\bfX (\bfx_i))^2 \right|^2 \right] \left[ \frac{1}{n} \left( \sqrt n.\frac{1}{n} \sum_{i=1}^n  SS(\bfx, \hat\bfmu_n) \right) \right]
%\end{eqnarray}
%%
%with $\hat S_n = \sum_{i=1}^n SS(\bfx_i, \hat\bfmu_n)/ \sqrt n$.
Now due to the assumption of uniform convergence, given $\epsilon>0$ we can find $N \in \mathbb{N}$ such that
%
\begin{equation}
\label{equation:lemma1eq}
| (\tilde D^{n_1}_\bfX(\bfx_i))^2 - (\tilde D_\bfX(\bfx_i))^2 | < \epsilon
\end{equation}
%
for all $n_1 \geq N; i = 1,2,...,n_1$. This implies
%
\begin{eqnarray}
\label{eqn:lemma1eq2}
S_{n_1} &< & \epsilon \sqrt{n_1} \left[ \frac{1}{n_1} \sum_{i=1}^{n_1} SS(\bfx_i; \hat\bfmu_{n_1}) \right]\notag\\
&=& \epsilon \sqrt{n_1} \left[ \frac{1}{n_1} \sum_{i=1}^{n_1} \left\{ SS(\bfx_i; \hat\bfmu_{n_1}) - SS(\bfx_i; \bfmu) \right\} + \frac{1}{n_1} \sum_{i=1}^{n_1} SS(\bfx_i; \bfmu) \right]
\end{eqnarray}

We now construct a sequence of positive definite matrices $\{A_k (B_k+C_k) : k \in \mathbb N\} $ so that
%
$$ A_k = \frac{1}{k}, \quad B_k = \sqrt{N_k} \left[ \frac{1}{N_k} \sum_{i=1}^{N_k} \left\{ SS(\bfx_i; \hat\bfmu_{N_k}) - SS(\bfx_i; \bfmu) \right\} \right]$$
$$\quad C_k = \sqrt{N_k} \left[ \frac{1}{N_k} \sum_{i=1}^{N_k} SS(\bfx_i; \bfmu) \right] $$
%
where $N_k \in \mathbb N$ gives the relation (\ref{equation:lemma1eq}) in place of $N$ when we take $\epsilon = 1/k$. Under conditions $ E\|\bfx - \bfmu\|^{-3/2} < \infty $ and $\sqrt n (\hat\bfmu_n - \bfmu) = O_P(1)$, the sample SCM with unknown location parameter $\hat\bfmu_n$ has the same asymptotic distribution as the SCM with known location $\bfmu$ \citep{durre14}, hence $B_k = o_P(1)$, thus $A_k (B_k+C_k) \stackrel{P}{\rightarrow} 0$.

Now (\ref{eqn:lemma1eq2}) implies that for any $\epsilon_1 > 0$, $S_{N_k} > \epsilon_1 \Rightarrow A_k (B_k + C_k) > \epsilon_1$, which means $ P(S_{N_k} > \epsilon_1) < P(A_k (B_k + C_k) > \epsilon_1)$. Hence the subsequence $\{S_{N_k}\} \stackrel{P}{\rightarrow} 0$. Since the main sequence $\{S_k\}$ is bounded below by 0, this implies $\{S_k\} \stackrel{P}{\rightarrow} 0$. Finally, we have that
%
\begin{eqnarray}
\sqrt n \left[
\frac{1}{n} \sum_{i=1}^n (\tilde D^n_\bfX (\bfx_i))^2 SS(\bfx_i; \hat\bfmu_n) -
\frac{1}{n} \sum_{i=1}^n (\tilde D_\bfX (\bfx_i))^2 SS(\bfx_i; \bfmu) \right] &\leq & \hspace{1em} \notag\\
S_n +  \sqrt{n} \left[ \frac{1}{n} \sum_{i=1}^{n} \left\{ SS(\bfx_i; \hat\bfmu_{n}) - SS(\bfx_i; \bfmu) \right\} \right] &&
\end{eqnarray}
%
Since the second summand on the right hand side is $o_P(1)$ due to \cite{durre14} as mentioned before, we have the needed.
\end{proof}

\begin{proof}[Proof of Theorem \ref{Theorem:rootn}]
The quantity in the statement of the theorem can be broken down as:
%
\begin{eqnarray*}
\sqrt n \left[ vec\left\{ \frac{1}{n} \sum_{i=1}^n (\tilde D^n_\bfX (\bfx_i))^2 SS(\bfx_i; \hat\bfmu_n) \right\} - vec\left\{ \frac{1}{n} \sum_{i=1}^n (\tilde D_\bfX (\bfx_i))^2 SS(\bfx_i; \bfmu) \right\} \right] +\\
\sqrt n \left[ vec\left\{ \frac{1}{n} \sum_{i=1}^n (\tilde D_\bfX (\bfx_i))^2 SS(\bfx_i; \bfmu) \right\} - E \left[ vec\left\{ (\tilde D_\bfX (\bfx))^2 SS(\bfx; \bfmu) \right\} \right] \right]
\end{eqnarray*}
%
The first part goes to 0 in probability by Lemma \ref{Lemma:lemma1}, and applying Slutsky's theorem we get the required convergence.
\end{proof}

\begin{proof}[Proof of Theorem \ref{Theorem:decomp}]
See \cite{taskinen12}
\end{proof}

\begin{proof}[Proof of Corollary \ref{Corollary:eigendist}]
In spirit, this corollary is similar to Theorem 13.5.1 in \cite{anderson}, and indeed, \cite{taskinen12} used this theorem to prove Theorem \ref{Theorem:decomp}. Due to the decomposition (\ref{equation:decompEq}) we have, for the distribution $F_\Lambda$, the following relation between any off-diagonal element of $\hat S^D(F_\Lambda)$ and the corresponding element in the estimate of eigenvectors $\hat\Gamma_D (F_\Lambda)$:

$$ \sqrt n \hat\gamma_{D,ij} (F_\Lambda) = \sqrt n \frac{\hat S^D_{ij} (F_\Lambda)}{\lambda_{D,S,i} - \lambda_{D,S,j}}; \quad i \neq j$$

So that for eigenvector estimates of the original $F$ we have

\begin{equation} \label{equation:app1}
\sqrt n (\hat\bfgamma_{D,i} - \bfgamma_i) = \sqrt n \Gamma (\hat \bfgamma_{D,i}(F_\Lambda) - \bfe_i ) = \sqrt n \left[ \sum_{k=1; k \neq i}^p \hat \gamma_{D,ik}(F_\Lambda)\bfgamma_k + (\hat \gamma_{D,ii}(F_\Lambda) - 1)\bfgamma_i \right]
\end{equation}

$\sqrt n (\hat \gamma_{D,ii}(F_\Lambda) - 1) =  o_P(1)$ and $ACov(\sqrt n \hat S^D_{ik}(F_\Lambda), \sqrt n \hat S^D_{il}(F_\Lambda)) = 0$ for $k \neq l$, so the above equation implies

$$ AVar(\bfg_i) = AVar (\sqrt n (\hat\bfgamma_{D,i} - \bfgamma_i)) = \sum_{k=1; k \neq i}^p \frac{AVar(\sqrt n \hat S^D_{ik}(F_\Lambda))}{(\lambda_{D,s,i} - \lambda_{D,S,k})^2} \bfgamma_k \bfgamma_k^T $$

For the covariance terms, from (\ref{equation:app1}) we get, for $i \neq j$,

\begin{eqnarray*}
ACov(\bfg_i, \bfg_j) &=& ACov (\sqrt n (\hat\bfgamma_{D,i} - \bfgamma_i), \sqrt n (\hat\bfgamma_{D,j} - \bfgamma_j))\\
&=& ACov \left( \sum_{k=1; k \neq i}^p \sqrt n \hat \gamma_{D,ik}(F_\Lambda)\bfgamma_k, \sum_{k=1; k \neq j}^p \sqrt n \hat \gamma_{D,jk}(F_\Lambda)\bfgamma_k \right)\\
&=& ACov \left( \sqrt n \hat \gamma_{D,ij}(F_\Lambda)\bfgamma_j, \sqrt n \hat \gamma_{D,ji}(F_\Lambda)\bfgamma_i \right)\\
&=& - \frac{AVar(\sqrt n \hat S^D_{ij}(\Lambda))}{(\lambda_{D,s,i} - \lambda_{D,S,j})^2} \bfgamma_j \bfgamma_i^T
\end{eqnarray*}

The exact forms given in the statement of the corollary now follows from the  Form of $V_{D,S}$ in Appendix \ref{section:appA}.

\paragraph{}For the on-diagonal elements of $\hat S^D(F_\Lambda)$ Theorem \ref{Theorem:decomp} gives us $ \sqrt n \hat\lambda_{D,s,i} (F_\Lambda) = \sqrt n \hat S^D_{ii}(F_\Lambda)$ for $i = 1,...,p$. Hence

\begin{eqnarray*}
AVar(l_i) &=& AVar(\sqrt n \hat\lambda_{D,s,i} - \sqrt n \lambda_{D,S,i})\\
&=& AVar(\sqrt n \hat\lambda_{D,s,i} (F_\Lambda) - \sqrt n \lambda_{D,S,i}(F_\Lambda))\\
&=& AVar(\sqrt n S^D_{ii}(F_\Lambda))
\end{eqnarray*}

A similar derivation gives the expression for $AVar(l_i,l_j); i \neq j$. Finally, since the asymptotic covariance between an on-diagonal and an off-diagonal element of $\hat S^D(F_\Lambda)$, it follows that the elements of $G$ and diagonal elements of $L$ are independent.
\end{proof}

\bibliographystyle{plainnat}
\bibliography{scatterbib}

\end{document}

### 2018-03-20 MS/JSMtalk/JSMtalk_depth-scatter.tex
first commit in shubhobm

\documentclass[handout,10pt]{beamer}
\usepackage{SexySlides,fancyvrb,outlines,pbox}
\usepackage[round]{natbib}
\usepackage{hyperref} % link references

\definecolor{UniBlue}{RGB}{83,121,170}
\setbeamercolor{title}{fg=UniBlue}
\setbeamercolor{frametitle}{fg=UniBlue}
\newcommand{\coluit}{\color{UniBlue}\it}
\newcommand{\colubf}{\color{UniBlue}\bf}

\DeclareMathOperator*{\diag}{diag}
\DeclareMathOperator*{\Tr}{Tr}
\DeclareMathOperator*{\argmin}{argmin}

     \setbeamertemplate{footline}
        {
      \leavevmode%
      \hbox{%
      \begin{beamercolorbox}[wd=.333333\paperwidth,ht=2.25ex,dp=1ex,center]{author in head/foot}%
        \usebeamerfont{author in head/foot}\insertshortauthor~~
        %(\insertshortinstitute)
      \end{beamercolorbox}%
      \begin{beamercolorbox}[wd=.333333\paperwidth,ht=2.25ex,dp=1ex,center]{title in head/foot}%
        \usebeamerfont{title in head/foot}\insertshorttitle
      \end{beamercolorbox}%
      \begin{beamercolorbox}[wd=.333333\paperwidth,ht=2.25ex,dp=1ex,right]{date in head/foot}%
        \usebeamerfont{date in head/foot}\insertshortdate{}\hspace*{2em}

    %#turning the next line into a comment, erases the frame numbers
        %\insertframenumber{} / \inserttotalframenumber\hspace*{2ex}

      \end{beamercolorbox}}}%

%\def\logo{%
%{\includegraphics[height=1cm]{goldy1.png}}
%}
%%
%\setbeamertemplate{footline}
%{%
%	\hspace*{.05cm}\logo
%  \begin{beamercolorbox}[sep=1em,wd=10cm,rightskip=0.5cm]
%  {footlinecolor,author in head/foot}
%%    \usebeamercolor{UniBlue}
%    \vspace{0.1cm}
%    \insertshortdate \hfill \insertshorttitle
%    \newline
%    \insertshortauthor   - \insertshortinstitute
%    \hfill
%    \hfill \insertframenumber/\inserttotalframenumber
%  \end{beamercolorbox}
%  \vspace*{0.05cm}
%}

%% smart verbatim
\fvset{framesep=1cm,fontfamily=courier,fontsize=\scriptsize,framerule=.3mm,numbersep=1mm,commandchars=\\\{\}}

\title[Depth PCA]
{\Large  
Robust estimation of \\principal components from \\depth-based multivariate rank covariance matrix}

\author[Subho Majumdar]{Subho Majumdar\\ Snigdhansu Chatterjee}
\institute[]{University of Minnesota, School of Statistics\\
\vspace{.5cm}
\includegraphics[height=.5cm]{UMNlogo}}

\date {}

\date [August 9, 2015]

%%%%%%%List Outline in the beginning of each section.
%\AtBeginSection[] {
%   \begin{frame}
%       \frametitle{Outline}
%       \tableofcontents[currentsection]
%   \end{frame}
%}

%-------------------------------------------------------------------
\begin{document}

%\begin{frame}
\frame{ \titlepage}
%\end{frame}

\frame{\frametitle{Table of contents}\tableofcontents}

%---------------------------------------------------

\begin{frame}
\frametitle{Summary}
\begin{itemize}
\item Introduction: what is data depth?
\vspace{.5cm}
\item Multivariate ranks based on data depth
\vspace{.5cm}
\item The Depth Covariance Matrix (DCM): overview of results
\vspace{.5cm}
\item Performance: simulations and real data analysis
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{What is depth?}
\textbf{Example}: 500 points from $\mathcal{N}_2 ((0,0)^T, \diag (2,1))$
\begin{figure}\begin{center}
   \includegraphics[height=6cm]{depthplot}
   \label{fig:fig1}
\end{center}\end{figure}
\colbbf{A scalar measure of how much inside a point is with respect to a data cloud}
\end{frame}

\begin{frame}
\frametitle{Formal definition}
For any multivariate distribution $F = F_\bfX$, the depth of a point $\bfx \in \mathbb{R}^p$, say $D(\bfx, F_\bfX)$ is any real-valued function that provides a `center outward ordering' of $\bfx$ with respect to $F$ \citep{zuo00}.

\vspace{.5cm}
\begin{block}{Desirable properties \citep{liu90}}
(P1) {\colbit Affine invariance}: $D(A\bfx + \bfb, F_{A\bfX+\bfb}) = D(\bfx, F_\bfX)$
\vspace{.2cm}

(P2) {\colbit Maximality at center}: $D(\bftheta, F_\bfX) = \sup_{\bfx\in \mathbb{R}^p} D(\bfx, F_\bfX)$ for $F_\bfX$ with center of symmetry $\bftheta$, the \textit{deepest point} of $F_\bfX$.
\vspace{.2cm}

(P3) {\colbit Monotonicity w.r.t. deepest point}: $D(\bfx; F_\bfX) \leq D(\bftheta + a(\bfx - \bftheta), F_\bfX)$
\vspace{.5cm}

(P4) {\colbit Vanishing at infinity}: $D(\bfx; F_\bfX) \rightarrow \bf0$ as $\|\bfx\| \rightarrow \infty $.
\end{block}
\end{frame}

\begin{frame}
\frametitle{Examples}
\begin{itemize}
\item \textbf{Halfspace depth} (HD) \citep{tukey75} is the minimum probability of all halfspaces containing a point.
$$ HD(\bfx, F)  = \inf_{\bfu \in \mathbb{R}^p; \bfu \neq \bf0} P(\bfu^T \bfX \geq \bfu^T \bfx) $$

\item \textbf{Projection depth} (PD) \citep{zuo03} is based on an outlyingness function:
$$ O(\bfx, F) = \sup_{\| \bfu \| = 1} \frac{| \bfu^T\bfx - m(\bfu^T\bfX)|}{s(\bfu^T\bfX)}; \quad PD(\bfx, F) = \frac{1}{1+O(\bfx, F)} $$
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Utility of data depth}
{\colbbf Robustness}

\begin{itemize}
\item \textbf{Classification}
\vspace{.2cm}

\item Depth-weighted means and covariance matrices
\vspace{.2cm}

\item What we're going to do:\\Define multivariate rank vectors based on data depth, do PCA on them
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Spatial signs \citep{locantore99}}
$$ \bfS(\bfx) = \begin{cases} \bfx\| \bfx \|^{-1} \quad \mbox{if }\bfx \neq \bf0\\
\bf0 \quad \mbox{if }\bfx = \bf0 \end{cases} $$

\begin{itemize}
\item Say $\bfx$ follows an elliptic distribution with mean $\bfmu$, covariance matrix $\Sigma$.
\item Sign covariance matrix (SCM): $\Sigma_S(\bfX) = E\bfS (\bfX - \bfmu)\bfS (\bfX - \bfmu)^T$
\item SCM has same eigenvectors as $\Sigma$. PCA using SCM is robust, but not efficient.
\end{itemize}

\begin{figure}\begin{center}
   \includegraphics[height=5cm]{signs}
   \label{fig:fig2}
\end{center}\end{figure}
\end{frame}

\begin{frame}
\frametitle{Spatial ranks}

\begin{itemize}
\item Fix a depth function $D(\bfx, F) = D_\bfX(\bfx)$. Define $ \tilde D_\bfX(\bfx) = \sup_{\bfx\in \mathbb{R}^p} D_\bfX(\bfx) - D_\bfX(\bfx) $

\item Transform the original observation: $\tilde \bfx = \tilde D_\bfX(\bfx) \bfS(\bfx - \bfmu)$. This is the {\colbit Spatial Rank} of $\bfx$.

\item Depth Covariance Matrix (DCM) = $Cov(\tilde \bfX)$. Has more information than spatial signs, so more efficient.
\end{itemize}

\begin{figure}\begin{center}
   \includegraphics[height=5cm]{ranks}
   \label{fig:fig3}
\end{center}\end{figure}
\end{frame}

\begin{frame}
\frametitle{Form of DCM}
\begin{theorem}[1]
Let the random variable $\bfX \in \mathbb{R}^p$ follow an elliptical distribution with center $\bfmu$ and covariance matrix $\Sigma = \Gamma\Lambda\Gamma^T$, its spectral decomposition. Then, given a depth function $D_\bfX(.)$ the covariance matrix of the transformed random variable $\tilde\bfX$ is
\begin{equation}
Cov(\tilde \bfX) = \Gamma \Lambda_{D,S} \Gamma^T,\quad\mbox{with}\quad \Lambda_{D,S} = E \left[ (\tilde D_\bfZ(\bfz))^2 \frac{\Lambda^{1/2} \bfz \bfz^T \Lambda^{1/2}}{\bfz^T \Lambda \bfz} \right]
\end{equation}

where $\bfz = (z_1,...,z_p)^T \sim N({\bf 0}, I_p)$ and $\Lambda_{D,S}$ a diagonal matrix with diagonal entries
$$ \lambda_{D,S,i} = E_\bfZ \left[ \frac{(\tilde D_\bfZ(\bfz))^2 \lambda_i z_i^2}{\sum_{j=1}^p \lambda_j z_j^2} \right] $$
\end{theorem}

\vspace{.5cm}
{\colb \textbf{TL; DR:} Population eigenvectors are invariant under the spatial rank transformation.}
\end{frame}

\begin{frame}
\frametitle{Other results}
\begin{itemize}
\item Asymptotic distribution of sample DCM, form of its asymptotic variance
\vspace{.2cm}

\item Asymptotic joint distribution of eigenvectors and eigenvalues of sample DCM
\vspace{.2cm}

\item Form and shape of influence function: a measure of robustness
\vspace{.2cm}

\item Asymptotic efficiency relative to sample covariance matrix
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Simulation}
\begin{itemize}
\item 6 elliptical distributions: $p$-variate normal and $t$- distributions with df = 5, 6, 10, 15, 25.
\vspace{.2cm}

\item All distributions centered at ${\bf 0}_p$, and have covariance matrix $\Sigma = \diag(p,p-1,...1)$. 
\vspace{.2cm}

\item 3 choices of $p$: 2, 3 and 4.
\vspace{.2cm}

\item 10000 samples each for sample sizes $n = 20, 50, 100, 300, 500$
\vspace{.2cm}

\item For estimates $\hat\bfgamma_1$ of the first eigenvector $\hat\bfgamma_1$, prediction error is measured by the average smallest angle between the two lines, i.e. \textbf{Mean Squared Prediction Angle}:
$$ MSPA(\hat \bfgamma_1) = \frac{1}{10000} \sum_{m=1}^{10000} \left( \cos^{-1} \left|\bfgamma_1^T \hat\bfgamma^{(m)}_1 \right| \right)^2 $$

Finite sample efficiency of some eigenvector estimate $\hat\bfgamma^E_1$ relative to that obtained from the sample covariance matrix, say $\hat\bfgamma^{Cov}_1$ is:
$$ FSE(\hat\bfgamma^E_1, \hat\bfgamma^{Cov}_1) = \frac{MSPA(\hat\bfgamma^{Cov}_1)}{MSPA(\hat\bfgamma^E_1)} $$
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Table of FSE for $p=2$}

(HSD = Halfspace depth, MhD = Mahalanobis depth, PD = Projection depth)
\begin{table}
\begin{footnotesize}
   \begin{tabular}{c|cccc}
    \hline
    $F$ = Bivariate $t_5$      & SCM  & HSD-CM & MhD-CM & PD-CM \\ \hline
    $n$=20                        & 0.80 & 0.95   & 0.95   & 0.89  \\
    $n$=50                        & 0.86 & 1.25   & 1.10   & 1.21  \\
    $n$=100                       & 1.02 & 1.58   & 1.20   & 1.54  \\
    $n$=300                       & 1.24 & 1.81   & 1.36   & 1.82  \\
    $n$=500                       & 1.25 & 1.80   & 1.33   & 1.84  \\ \hline
    $F$ = Bivariate $t_6$      & SCM  & HSD-CM & MhD-CM & PD-CM \\ \hline
    $n$=20                        & 0.77 & 0.92   & 0.92   & 0.86  \\
    $n$=50                        & 0.76 & 1.11   & 1.00   & 1.08  \\
    $n$=100                       & 0.78 & 1.27   & 1.06   & 1.33  \\
    $n$=300                       & 0.88 & 1.29   & 1.09   & 1.35  \\
    $n$=500                       & 0.93 & 1.37   & 1.13   & 1.40  \\ \hline
    $F$ = Bivariate $t_{10}$ & SCM  & HSD-CM & MhD-CM & PD-CM \\ \hline
    $n$=20                        & 0.70 & 0.83   & 0.84   & 0.77  \\
    $n$=50                        & 0.58 & 0.90   & 0.84   & 0.86  \\
    $n$=100                       & 0.57 & 0.92   & 0.87   & 0.97  \\
    $n$=300                       & 0.62 & 0.93   & 0.85   & 0.99  \\
    $n$=500                       & 0.62 & 0.93   & 0.86   & 1.00  \\ \hline
    \end{tabular}
\end{footnotesize}
\label{table:FSEtable1}
\end{table}
\end{frame}

\begin{frame}
\frametitle{Table of FSE for $p=2$}
(HSD = Halfspace depth, MhD = Mahalanobis depth, PD = Projection depth)
\begin{table}
\begin{footnotesize}
   \begin{tabular}{c|cccc}
    \hline
    $F$ = Bivariate $t_{15}$ & SCM  & HSD-CM & MhD-CM & PD-CM \\ \hline
    $n$=20                        & 0.63 & 0.76   & 0.78   & 0.72  \\
    $n$=50                        & 0.52 & 0.79   & 0.75   & 0.80  \\
    $n$=100                       & 0.51 & 0.83   & 0.77   & 0.88  \\
    $n$=300                       & 0.55 & 0.84   & 0.79   & 0.91  \\
    $n$=500                       & 0.56 & 0.85   & 0.80   & 0.93  \\ \hline
    $F$ = Bivariate $t_{25}$ & SCM  & HSD-CM & MhD-CM & PD-CM \\ \hline
    $n$=20                        & 0.63 & 0.77   & 0.79   & 0.74  \\
    $n$=50                        & 0.49 & 0.73   & 0.71   & 0.76  \\
    $n$=100                       & 0.45 & 0.73   & 0.69   & 0.81  \\
    $n$=300                       & 0.51 & 0.78   & 0.75   & 0.87  \\
    $n$=500                       & 0.53 & 0.79   & 0.75   & 0.87  \\ \hline
    $F$ = BVN                     & SCM  & HSD-CM & MhD-CM & PD-CM \\ \hline
    $n$=20                        & 0.56 & 0.69   & 0.71   & 0.67  \\
    $n$=50                        & 0.42 & 0.66   & 0.66   & 0.70  \\
    $n$=100                       & 0.42 & 0.69   & 0.66   & 0.77  \\
    $n$=300                       & 0.47 & 0.71   & 0.69   & 0.82  \\
    $n$=500                       & 0.48 & 0.73   & 0.71   & 0.83  \\ \hline
    \end{tabular}
\end{footnotesize}
\label{table:FSEtable2}
\end{table}
\end{frame}

\begin{frame}
\frametitle{Data analysis: Bus data}
\begin{itemize}
\item Features extracted from images of 213 buses: 18 variables
\vspace{.2cm}

\item Methods compared:\\
\vspace{.2cm}
Classical PCA (CPCA)\\
SCM PCA (SPCA)\\
ROBPCA \citep{hubert05}\\
PCA based on MCD (MPCA)\\
PCA based on projection-DCM (DPCA)
\vspace{.2cm}
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Score distance (SD) and orthogonal distance (OD)}
$$ SD_i = \sqrt{ \sum_{j=1}^k \frac{s^2_{ij}}{\lambda_j}}; \quad OD_i = \| \bfx_i - P\bfs_i^T \| $$

\begin{footnotesize}
where $S_{n\times k} = (\bfs_1, \ldots ,\bfs_n)^T$ is the scoring matrix, $P_{p\times k}$ loading matrix, $\lambda_1,\ldots ,\lambda_k$ are eigenvalues obtained from the PCA, and $\bfx_1,\ldots,\bfx_n$ are the observation vectors.
\end{footnotesize}

\begin{figure}[h]
	\centering
		\includegraphics[height=5.5cm]{ScoreOrtho}
	\label{fig:ScoreOrthoPlot}
\end{figure}
\end{frame}

\begin{frame}
\frametitle{Bus data: comparison tables}

\begin{footnotesize}
\begin{table}[t]
\centering
    \begin{tabular}{c|ccccc}
    \hline
    Quantile & \multicolumn{5}{c}{Method of PCA}         \\ \cline{2-6}
    ~                   & CPCA     & SPCA & ROBPCA & MPCA & DPCA \\\hline 
    10\%      & 1.9       & {\colb 1.2}       & {\colm 1.2}    & {\colr 1.0}       & {\colubf 1.2}       \\
    20\%      & 2.3       & {\colb 1.6}       & {\colm 1.6}    & {\colr 1.3}       & {\colubf 1.6}       \\
    30\%      & 2.8       & {\colb 1.8}       & {\colm 1.8}    & {\colr 1.7}       & {\colubf 1.9}       \\
    40\%      & 3.2       & {\colb 2.2}       & {\colm 2.1}    & {\colr 2.1}       & {\colubf 2.3}       \\
    50\%      & 3.7       & {\colb 2.6}       & {\colm 2.5}    & {\colr 3.1}       & {\colubf 2.6}       \\
    60\%      & 4.4       & {\colb 3.1}       & {\colm 3.0}    & 5.9       & {\colubf 3.2}       \\
    70\%      & 5.4       & {\colb 3.8}       & {\colm 3.9}    & 25.1      & {\colubf 3.9}       \\
    80\%      & 6.5       & {\colb 5.2}       & {\colm 4.8}    & 86.1      & {\colubf 4.8}       \\
    90\%      & 8.2       & 9.0       & 10.9   & 298.2     & {\colubf 6.9}      \\
    Max       & 24        & 1037      & 1055   & 1037      & 980      \\\hline
    \end{tabular}
    \label{table:bus_table2}
\end{table}
\end{footnotesize}

\begin{itemize}
\item Table lists quantiles of the squared orthogonal distance for a sample point from the hyperplane formed by top 3 PCs,
\vspace{.2cm}
\item For DPCA, more than 90\% of points have a smaller orthogonal distance than CPCA
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Data analysis: Octane data}
\begin{itemize}
\item 226 variables and 39 observations. Each observation is a gasoline sample with a certain octane number, and have their NIR absorbance spectra measured in 2 nm intervals between 1100 - 1550 nm.
\vspace{.2cm}
\item 6 outliers: compounds 25, 26 and 36-39, which contain alcohol.
\end{itemize}

\begin{figure}[h]
	\centering
		\includegraphics[height=6cm]{octane_distanceplot.pdf}
	\label{fig:distplot}
\end{figure}
\end{frame}

\begin{frame}
\frametitle{Extensions: Robust kernel PCA}

\begin{footnotesize}
\begin{itemize}
\item 20 points from each person. Noise added to one image from each person.
\item Columns due to kernel CPCA, SPCA and DPCA, respectively. Rows due to top 2, 4, 6, 8 or 10 PCs considered.
\end{itemize}
\end{footnotesize}

\begin{figure}[h]
	\centering
		\includegraphics[width=2cm]{yale1.png}
		\hspace{.2cm}
		\includegraphics[width=3cm]{yaleB01recon.png}
		\hspace{.2cm}
		\includegraphics[width=3cm]{yaleB02recon.png}
		\hspace{.2cm}
		\includegraphics[width=3cm]{yaleB28recon.png}
	\label{fig:kdpca}
\end{figure}
\end{frame}

\begin{frame}
\frametitle{Extensions: future work}
\begin{itemize}
\item Explore properties of a depth-weighted M-estimator of scale matrix:
$$ \Sigma_{Dw} = E \left[ \frac{(\tilde D_\bfX(\bfx))^2 (\bfx - \bfmu) (\bfx - \bfmu)^T}{(\bfx - \bfmu)^T \Sigma_{Dw}^{-1} (\bfx - \bfmu)} \right] $$
\vspace{.5cm}

\item Leverage the idea of depth based ranks: robust non-parametric testing

\item Extending to high-dimensional and functional data
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Acknowledgements}
\begin{itemize}
\item NSF grants \# IIS-1029711, \# SES-0851705;
\vspace{.2cm}
\item NASA grant \#-1502546;
\vspace{.2cm}
\item The Institute on the Environment (IonE), and College of Liberal Arts (CLA) - University of Minnesota;
\vspace{.2cm}
\item Abhirup Mallik;
\vspace{.2cm}
\item My team in Santander Consumer USA;
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{References}
\bibliographystyle{plainnat}
\bibliography{scatterbib}
\end{frame}

\begin{frame}
\centering\huge
\textcolor{UniBlue}{\textbf{THANK YOU!}}
\end{frame}

\end{document}

### 2018-03-20 MS/SJS/Appendix.tex
first commit in shubhobm

--- 2018-03-20 MS/Depth-scatter-summary.tex
@@
-\documentclass[fleqn,11pt]{article}
-\usepackage{mycommands,amssymb,amsmath,amsthm,color,pagesize,outlines,cite,caption}
-\usepackage[pdftex]{graphicx}
-\usepackage[round]{natbib}
-\addtolength{\evensidemargin}{-.5in}
-\addtolength{\oddsidemargin}{-.5in}
-\addtolength{\textwidth}{0.9in}
-\addtolength{\textheight}{0.9in}
-\addtolength{\topmargin}{-.4in}
+\section*{Appendix A: \textbf{Form of $V_{D,S}(F)$}}
+First observe that for $F$ having covariance matrix $\Sigma = \Gamma\Lambda\Gamma^T$,
 
-\usepackage{hyperref} % for linking references 
-\usepackage{setspace}
-\doublespacing
-
-%\DeclareMathOperator*{\vec}{vec}
-\DeclareMathOperator*{\diag}{diag}
-\DeclareMathOperator*{\Tr}{Tr}
-
-\begin{document}
-
-\newtheorem{Theorem}{Theorem}[section]
-\newtheorem{Lemma}[Theorem]{Lemma}
-\newtheorem{Corollary}[Theorem]{Corollary}
-\theoremstyle{definition} \newtheorem{Definition}[Theorem]{Definition}
-
-\title{Robust estimation of principal components from depth-based multivariate rank covariance matrix}
-\date{}
-\author{Subhabrata Majumdar}
-\maketitle
-
-Abstract:
-Analyzing principal components for multivariate data from its spatial sign covariance matrix (SCM) has been proposed as a computationally simple and robust alternative to normal PCA, but it suffers from poor efficiency properties and is actually inadmissible with respect to the maximum likelihood estimator.
-Here we use data depth-based spatial ranks in place of spatial signs to obtain the orthogonally equivariant Depth Covariance Matrix (DCM) and use its eigenvector estimates for PCA.
-We derive asymptotic properties of the sample DCM and influence functions of its eigenvectors.
-The shapes of these influence functions indicate robustness of estimated principal components, and good efficiency properties compared to the SCM.
-Finite sample simulation studies show that principal components of the sample DCM are robust with respect to deviations from normality, as well as are more efficient than the SCM and its affine equivariant version, Tyler's shape matrix.
-Through two real data examples, we also show the effectiveness of DCM-based PCA in analyzing high-dimensional data and outlier detection, and compare it with other methods of robust PCA.
-\vspace{.5cm}
-
-Keywords:
-Data depth; Principal components analysis; Robustness; Sign covariance matrix; Multivariate ranking
-
-\newpage
-\section{Introduction}
-In multivariate analysis, the study of principal components is important since it provides a small number of uncorrelated variables from a potentially larger number of variables, so that these new components explain most of the underlying variability in the original data.
-In case of multivariate normal distribution, the sample covariance matrix provides the most asymptotically efficient estimates of eigenvectors/ principal components, but it is extremely sensitive to outliers as well as relaxations of the normality assumption.
-To address this issue, several robust estimators of the population covariance or correlation matrix have been proposed which can be used for Principal Components Analysis (PCA).
-They can be roughly put into these categories: robust, high breakdown point estimators that are computation-intensive \citep{rousseeuw85, maronna76}; M-estimators that are calculated by simple iterative algorithms but do not necessarily possess high breakdown point \citep{huber77, tyler87}; and symmetrised estomators that are highly efficient and robust to deviations from normality, but sensitive to outliers and computationally demanding \citep{dumbgen98, sirkia07}.
-
-When principal components are of interest, one can also estimate the population eigenvectors by analyzing the spatial sign of a multivariate vector: the vector divided by its magnitude, instead of the original data.
-The covariance matrix of these sign vectors, namely Sign Covariance Matrix (SCM) has the same set of eigenvectors as the covariance matrix of the original population, thus the multivariate sign transformation yields computationally simple and high-breakdown estimates of principal components \citep{locantore99, visuri00}.
-Although the SCM is not affine equivariant, its orthogonal equivariance suffices for the purpose of PCA.
-However, the resulting estimates are not very efficient, and are in fact asymptotically inadmissible \citep{magyar14}, in the sense that there is an estimator (Tyler's M-estimate of scatter, to be precise) that has uniformly lower asymptotic risk than the SCM.
-
-The nonparametric concept of data-depth had first been proposed by \cite{tukey75} when he introduced the halfspace depth.
-Given a dataset, the depth of a given point in the sample space measures how far inside the data cloud the point exists.
-An overview of statistical depth functions can be found in \citep{zuo00}.
-Depth-based methods have recently been popular for robust nonparametric classification \citep{jornsten04, ghosh05, dutta12, sguera14}.
-In parametric estimation, depth-weighted means \citep{ZuoCuiHe04} and covariance matrices \citep{ZuoCui05} provide high-breakdown point as well as efficient estimators, although they do involve choice of a suitable weight function and tuning parameters.
-In this paper we study the covariance matrix of the multivariate rank vector that is obtained from the data-depth of a point and its spatial sign, paying special attention to its eigenvectors.
-Specifically, we develop a robust version of principal components analysis for elliptically symmetric distributions based on the eigenvectors of this covariance matrix, and compare it with normal PCA and spherical PCA, i.e.
-PCA based on eigenvectors of the SCM.
-
-The chapter is arranged in the following fashion.
-Section \ref{section:sec2} provides preliminary theoretical concepts required for developments in the subsequent sections.
-Section \ref{section:dcmSection} introduces the Depth Covariance Matrix (DCM) and states some basic results related to this.
-Section \ref{section:sec4} provides asymptotic results regarding the sample DCM, calculated using data depths with respect to the empirical distribution function, as well as its eigenvectors and eigenvalues.
-Section \ref{section:simSection} focuses solely on principal component estimation using the sample DCM.
-We obtain influence functions and asymptotic efficiencies for eigenvectors of the DCM.
-We also compare their finite sample efficiencies for several multinormal and multivariate $t$-distributions with those of the SCM, Tyler's scatter matrix and its depth-weighted version through a simulation study.
-Section \ref{section:sec6} presents two applications of the methods we develop on real data.
-Finally, we wrap up our discussion in Section \ref{section:sec7} by giving a summary of our findings and providing some potential future areas of research.
-Appendices \ref{section:appA} and \ref{section:appB} contain all technical details and proofs of the results we derive.
-
-\section{Preliminaries}\label{section:sec2}
-\subsection{Spatial signs and sign covariance matrix}
-Given a vector $\bfx \in \mathbb{R}^p$, its spatial sign is defined as the vector valued function \citep{MottonenOja95}:
-%
-$$ \bfS(\bfx) = \begin{cases} \bfx\| \bfx \|^{-1} \quad \mbox{if }\bfx \neq \bf0\\
-\bf0 \quad \mbox{if }\bfx = \bf0 \end{cases} $$
-%
-When $\bfx$ is a random vector that follows an elliptic distribution $|\Sigma|^{-1/2} f((\bfx - \bfmu)^T \Sigma^{-1} (\bfx - \bfmu))$, with a mean vector $\bfmu$ and covariance matrix $\Sigma$, the sign vectors $\bfS(\bfx - \bfmu)$ reside on the surface of a $p$-dimensional unit ball centered at $\bfmu$.
-Denote by $\Sigma_S(\bfX) = E\bfS (\bfX - \bfmu)\bfS (\bfX - \bfmu)^T$ the covariance matrix of spatial signs, or the \textit{Sign Covariance Matrix} (SCM).
-The transformation $\bfx \mapsto \bfS(\bfx - \bfmu)$ keeps eigenvectors of population covariance matrix unchanged, and eigenvectors of the sample SCM $ \hat \Sigma_S = \sum_{i=1}^n \bfS (\bfx_i - \bfmu)\bfS (\bfx_i - \bfmu)^T/n $ are $\sqrt n$-consistent estimators of their population counterparts \citep{taskinen12}.
-
-The sign transformation is rotation equivariant, i.e.
-$ \bfS(P (\bfx - \bfmu)) = P(\bfx - \bfmu)/\| P (\bfx - \bfmu)\| = P(\bfx - \bfmu)/\|\bfx - \bfmu\| = P \bfS(\bfx - \bfmu)$ for any orthogonal matrix $P$, and as a result the SCM is rotation equivariant too, in the sense that $\Sigma_S(P\bfX) = P \Sigma_S(\bfX) P^T$.
-This is not necessarily true in general if $P$ is replaced by any non-singular matrix.
-An affine equivariant version of the sample SCM is obtained as the solution $\hat \Sigma_T$ of the following equation:
-%
-$$ \hat \Sigma_T(\bfX) = \frac{p}{n} \sum_{i=1}^n \frac{(\bfx - \bfmu)(\bfx - \bfmu)^T}{(\bfx - \bfmu)^T \hat\Sigma_T(\bfX)^{-1} (\bfx - \bfmu)} $$
-%
-which turns out to be Tyler's M-estimator of scatter \citep{tyler87}.
-In this context, one should note that for scatter matrices, affine equivariance will mean any affine transformation on the original random variable $\bfX \mapsto \bfX^* = A\bfX + \bfb$ ($A$ non-singular, $\bfb \in \mathbb{R}^p$) being carried over to the covariance matrix estimate upto a scalar multiple: $\hat\Sigma_T(\bfX^*) = k.
-A \hat\Sigma_T(\bfX) A^T$ for some $k>0$.
-
-\subsection{Data depth and outlyingness}
-For any multivariate distribution $F = F_\bfX$ belonging to a set of distributions $\mathcal F$, the depth of a point $\bfx \in \mathbb{R}^p$, say $D(\bfx, F_\bfX)$ is any real-valued function that provides a 'center outward ordering' of $\bfx$ with respect to $F$ \citep{zuo00}.
-\cite{liu90} outlines the desirable properties of a statistical depth function:
-
-\vspace{1em}
-\noindent\textbf{(D1)} \textit{Affine invariance}: $D(A\bfx + \bfb, F_{A\bfX+\bfb}) = D(\bfx, F_\bfX)$;
-
-\noindent\textbf{(D2)} \textit{Maximality at center}: $D(\bftheta, F_\bfX) = \sup_{\bfx\in \mathbb{R}^p} D(\bfx, F_\bfX)$ for $F_\bfX$ having center of symmetry $\bftheta$.
-This point is called the \textit{deepest point} of the distribution.;
-
-\noindent\textbf{(D3)} \textit{Monotonicity with respect to deepest point}: $D(\bfx; F_\bfX) \leq D(\bftheta + a(\bfx - \bftheta), F_\bfX)$, $\bftheta$ being deepest point of $F_\bfX$.;
-
-\noindent\textbf{(D4)} \textit{Vanishing at infinity}: $D(\bfx; F_\bfX) \rightarrow 0$ as $\|\bfx\| \rightarrow \infty $.
-\vspace{1em}
-
-In (D2) the types of symmetry considered can be central symmetry, angular symmetry and halfspace symmetry.
-Also for multimodal probability distributions, i.e.
-distributions with multiple local maxima in their probability density functions, properties (D2) and (D3) are actually restrictive towards the formulation of a reasonable depth function that captures the shape of the data cloud.
-In our derivations that follow, we replace these two by a weaker condition:
-
-\vspace{1em}
-\noindent\textbf{(D2*)} \textit{Existence of a maximal point}: The maximum depth over all distributions $F$ and points $\bfx$ is bounded above, i.e.
-$ \sup_{F_\bfX \in \mathcal F} \sup_{\bfx\in \mathbb{R}^p} D(\bfx, F_\bfX) < \infty $.
-We denote this point by $M_D(F_\bfX)$.
-\vspace{1em}
-
-A real-valued function measuring the outlyingness of a point with respect to the data cloud can be seen as the opposite of what data depth does.
-Indeed, such functions have been used to define several depth functions, for example simplicial depth, projection depth and $L_p$-depth.
-Keeping with the spirit of the utility of these functions we name them `htped': literally the reverse of `depth', and give a general definition of such functions as a transformation on any depth function:
-
-\begin{Definition}
-Given a random variable $\bfX$ following a probability distribution $F$, and a depth function $D(.,.)$, we define Htped of a point $\bfx$ as: $\tilde D(\bfx, F) = h(d_\bfx)$ as any function of the data depth $D(\bfx, F) = d_\bfx$ so that $h(d_\bfx)$ is bounded, monotonically decreasing in $d_\bfx$ and $\sup_\bfx \tilde D(\bfx, F) < \infty$.
-\end{Definition}
-
-For a fixed depth function, there are several choices of a corresponding htped.
-We develop our theory assuming a general htped function, but for the plots and simulations, fix our htped as $\tilde D(\bfx, F) = M_D(F) - D(\bfx, F)$, i.e.
-simply subtract the depth of a point from the maximum possible depth over all points in sample space.
-
-We will be using the following 3 measures of data-depth to obtain our DCMs and compare their performances:
-
-\begin{itemize}
-\item \textbf{Halfspace depth} (HD) \citep{tukey75} is defined as the minimum probability of all halfspaces containing a point. In our notations,
-
-$$ HD(\bfx, F)  = \inf_{\bfu \in \mathbb{R}^p; \bfu \neq \bf0} P(\bfu^T \bfX \geq \bfu^T \bfx) $$
-
-\item \textbf{Mahalanobis depth} (MhD) \citep{LiuPareliusSingh99} is based on the Mahalanobis distance of $\bfx$ to $\bfmu$ with respect to $\Sigma$: $d_\Sigma(\bfx, \bfmu) = \sqrt{(\bfx - \bfmu)^T \Sigma^{-1} (\bfx - \bfmu)}$.
-It is defined as
-%
-$$ MhD(\bfX, F) = \frac{1}{1 + d^2_\Sigma (\bfx - \bfmu)} $$
-%
-note here that $d_\Sigma(\bfx,\bfmu)$ can be seen as a valid htped function of $\bfx$ with respect to $F$.
-
-\item \textbf{Projection depth} (PD) \citep{zuo03} is another depth function based on an outlyingness function. Here that function is
-%
-$$ O(\bfx, F) = \sup_{\| \bfu \| = 1} \frac{| \bfu^T\bfx - m(\bfu^T\bfX)|}{s(\bfu^T\bfX)} $$
-%
-where $m$ and $s$ are some univariate measures location and scale, respectively. Given this the depth at $\bfx$ is defined as $PD(\bfx, F) = 1/(1+O(\bfx, F))$.
-\end{itemize}
-
-Computation-wise, MhD is easy to calculate since the sample mean and covariance matrix are generally used as estimates of $\mu$ and $\Sigma$, respectively.
-However this makes MhD less robust with respect to outliers.
-PD is generally approximated by taking maximum over a number of random projections.
-There have been several approaches for calculating HD.
-A recent unpublished paper \citep{rainerArxiv} provides a general algorithm that computes exact HD in $O(n^{p-1}\log n)$ time.
-In this paper, we shall use inbuilt functions in the R package \texttt{fda.usc} for calculating the above depth functions.
-
-\section{Depth-based rank covariance matrix} \label{section:dcmSection}
-
-Consider a vector-valued random variable $\bfX \in \mathbb{R}^p$ .
-Data depth is as much a property of the random variable as it is of the underlying distribution, so for ease of notation while working with transformed random variables, from now on we shall be using $D_\bfX(\bfx) = D(\bfx, F)$ to denote the depth of a point $\bfx$.
-Now, given a depth function $D_{\bfX}(\bfx)$ (equivalently, an htped function $\tilde D_\bfX(\bfx) = \tilde D(\bfx, F)$), transform the original random variable as: $\tilde \bfx = \tilde D_\bfX(\bfx) \bfS(\bfx - \bfmu)$, $\bfS(.)$ being the spatial sign functional.
-The transformed random variable $\tilde \bfX$ can be seen as the multivariate rank corresponding to $\bfX$ (e.g.
-\cite{serfling2006}).
-The notion of multivariate ranks goes back to \cite{PuriSenBook}, where they take the vector consisting of marginal univariate ranks as multivariate rank vector.
-Subsequent definitions of multivariate ranks were proposed by \cite{MottonenOja95,HallinPaindaveine02} and \cite{Chernozhukov14}.
-Compared to these formulations, our definition of multivariate ranks works for any general depth function, and provides an intuitive extension to any spatial sign-based methodology.
-
-Figure \ref{fig:rankplot} gives an idea of how the multivariate rank vector $\tilde \bfX$ is distributed when $\bfX$ has a bivariate normal distribution.
-Compared to the spatial sign, which are distributed on the surface of $p$-dimensional unit ball centered at $\bfmu$, these spatial ranks have the same direction as original data and reside \textit{inside} the $p$-dimensional ball around $\bfmu$ that has radius $M_D(F)$ (which, for the case of halfspace depth, equals 0.5).
-
-\begin{figure}[t]
-	\captionsetup{singlelinecheck=off}
-	\centering
-		\includegraphics[height=6cm]{../Codes/ranks}
-	\caption{(Left) 1000 points randomly drawn from $\mathcal N_2\left((0,0)^T, \left(\protect\begin{smallmatrix} 5 & -4 \\ -4 & 5 \protect\end{smallmatrix}\right)\right) $ and (Right) their multivariate ranks based on halfspace depth}
-	\label{fig:rankplot}
-\end{figure}
-
-Now consider the spectral decomposition for the covariance matrix of $F$: $\Sigma = \Gamma\Lambda\Gamma^T$, $\Gamma$ being orthogonal and $\Lambda$ diagonal with positive diagonal elements.
-Also normalize the original random variable as $\bfz = \Gamma^T\Lambda^{-1/2} (\bfx - \bfmu)$.
-In this setup, we can represent the transformed random variable as
-%
-\begin{eqnarray}
-\tilde \bfx &=& \tilde D_{\bfX} (\bfx) \bfS(\bfX - \bfmu) \notag \\
-&=& \tilde D_{\Gamma\Lambda^{1/2}\bfZ + \bfmu} (\Gamma\Lambda^{1/2} \bfz + \bfmu). \bfS(\Gamma\Lambda^{1/2} \bfz) \notag \\
-&=& \Gamma \tilde D_{\bfZ}(\bfz) \bfS(\Lambda^{1/2}\bfz) \notag \\
-&=& \Gamma \Lambda^{1/2} \tilde D_{\bfZ}(\bfz) \bfS(\bfz) \frac{\| \bfz \|}{\|\Lambda^{1/2} \bfz\|}
-\label{equation:rankdecomp}
-\end{eqnarray}
-%
-%Because of affine (thus rotational) invariance of a depth function, the depth (htped) value at $\bfz$ does not depend on the direction of $\bfz$, i.e.
-$\tilde D_{\bfZ}(\bfz)$ and $\bfS(\bfz)$ are independent.
-Furthermore,
-%$$ Cov \left(\bfS (\bfz), \frac{\| \bfz \|}{\|\Lambda^{1/2} \bfz\|} \right) = E \left(\bfS (\bfz).
-\frac{\| \bfz \|}{\|\Lambda^{1/2} \bfz\|} \right) - E \bfS (\bfz) E \left(\frac{\| \bfz \|}{\|\Lambda^{1/2} \bfz\|} \right) = E \left( \frac{\bfz}{\|\Lambda^{1/2} \bfz\|} \right) = \bf0$$
-%both $\bfS (\bfz)$ and $\bfz / \| \Lambda^{1/2}\bfz \|$ are odd functions of $\bfz$, which has a circularly symmetric distribution, hence each of them has expectation $\bf0$.
-Consequently, we obtain an expression for the covariance matrix of $\tilde \bfX$:
-
-$\tilde D_\bfZ(\bfz)$ is an even function in $\bfz$ because of affine invariance, as is $\| \bfz \| / \|\Lambda^{1/2} \bfz \|$.
-Since $\bfS(\bfz)$ is odd in $\bfz$ for circularly symmetric $\bfz$, it follows that $E(\tilde \bfX) = \bf0$, and consequently we obtain an expression for the covariance matrix of $\tilde \bfX$:
-
-\begin{Theorem} \label{Theorem:covform}
-Let the random variable $\bfX \in \mathbb{R}^p$ follow an elliptical distribution with center $\bfmu$ and covariance matrix $\Sigma = \Gamma\Lambda\Gamma^T$, its spectral decomposition.
-Then, given a depth function $D_\bfX(.)$ the covariance matrix of the transformed random variable $\tilde\bfX$ is
-\begin{equation} \label{equation:covformEq1}
-Cov(\tilde \bfX) = \Gamma \Lambda_{D,S} \Gamma^T,\quad\mbox{with}\quad \Lambda_{D,S} = \mathbb E_\bfz \left[ (\tilde D_\bfZ(\bfz))^2 \frac{\Lambda^{1/2} \bfz \bfz^T \Lambda^{1/2}}{\bfz^T \Lambda \bfz} \right]
-\end{equation}
-where $\bfz = (z_1,...,z_p)^T \sim N({\bf 0}, I_p)$, so that $\Lambda_{D,S}$ a diagonal matrix with diagonal entries
-%
-$$ \lambda_{D,S,i} = \mathbb E_\bfZ \left[ \frac{(\tilde D_\bfZ(\bfz))^2 \lambda_i z_i^2}{\sum_{j=1}^p \lambda_j z_j^2} \right] $$
-\end{Theorem}
-
-The matrix of eigenvectors of the covariance matrix, $\Gamma$, remains unchanged in the transformation $\bfX \rightarrow \tilde \bfX$.
-As a result, the multivariate rank vectors can be used for robust principal component analysis, which will be outlined in the following sections.
-However, as one can see in the above expression, the diagonal entries of $\Lambda_{D,S}$ do not change if a scale change is done on all entries of $\Lambda$, meaning the $\Lambda_{D,S}$ matrices corresponding to $F$ and $cF$ for some $c \neq 0$ will be same.
-This is the reason for lack of affine equavariance of the DCM.
-Following the case of multivariate sign covariance matrices \citep{taskinen12} one can get back the shape components, i.e.
-original \textit{standardized} eigenvalues $\Lambda^*$ from $\Lambda_{D,S}$ by an iterative algorithm:
-
-\begin{enumerate}
-\item Set $k=0$, and start with an initial value $\Lambda^{*(0)}$.
-
-\item Calculate the next iterate
-%
-$$ \Lambda^{*(k+1)} = \left[ \mathbb E_\bfz \left( \frac{(\tilde D_\bfZ(\bfz))^2 \bfz \bfz^T}{\bfz^T \Lambda^{*(k)} \bfz} \right) \right]^{-1} \Lambda_{D,S} $$
-and standardize its eigenvalues:
-%
-$$ \Lambda^{*(k+1)} = \frac{\Lambda^{*(k+1)}}{\text{det} (\Lambda^{*(k+1)})^{1/p}} $$
-%
-\item Stop if convergence criterion is satisfied. Otherwise set $k \rightarrow k+1$ ad go to step 2.
-\end{enumerate}
-
-Unlike sign covariance matrices and symmetrized sign covariance matrices \citep{dumbgen98}, however, attempting to derive an affine equivariant counterpart (as opposed to only orthogonal equivariance) of the DCM through an iterative approach analogous to \cite{tyler87} will not result in anything new.
-This is because Tyler's scatter matrix $\Sigma_T$ is defined as the implicit solution to the following equation:
-\begin{equation} \label{equation:tylerEq}
-\Sigma_T = \mathbb E\left[ \frac{(\bfx - \bfmu) (\bfx - \bfmu)^T}{(\bfx - \bfmu)^T \Sigma_T^{-1} (\bfx - \bfmu)} \right]
-\end{equation}
-and simply replacing $\bfx$ by its multivariate rank counterpart $\tilde\bfx$ will not change the estimate $\Sigma_T$ as $\bfx$ and $\tilde \bfx$ have the same directions.
-Instead we consider a depth-weighted version of Tyler's scatter matrix (i.e.
-weights $(\tilde D_\bfX(\bfx))^2$ in right side of (\ref{equation:tylerEq})) in the simulations in Section \ref{section:simSection}.
-The simulations show that it has slightly better finite-sample efficiency than $\Sigma_T$ but has same asymptotic performance.
-We conjecture that its concentration properties can be obtained by taking an approach similar to \cite{soloveychik14}.
-
-\section{Asymptotic results}\label{section:sec4}
-\subsection{The sample DCM}
-Let us now consider $n$ iid random draws from our elliptic distribution $F$, say $\bfX_1,...,\bfX_n$.
-For ease of notation, denote $SS(\bfx; \bfmu) = \bfS(\bfx - \bfmu) \bfS(\bfx - \bfmu)^T$.
-Then, given the depth function and known location center $\bfmu$, one can show that the vectorized form of $\sqrt n$-times the sample DCM: $\sum_{i=1}^n (\tilde D_\bfX(\bfx_i))^2SS(\bfx_i; \bfmu) /\sqrt{n}$  has an asymptotic multivariate normal distribution with mean $\sqrt n.vec(E[( (\tilde D_\bfX (\bfX))^2 SS(\bfx; \bfmu)])$ and a certain covariance matrix by straightforward application of the central limit theorem (CLT).
-But in practice the population depth function $D_\bfX(\bfx) = D(\bfx, F)$ is estimated by the depth function based on the empirical distribution function, $F_n$.
-Denote this sample depth by $D^n_\bfX (\bfx) = D(\bfx, F_n)$.
-Here we make the following assumption regarding its relation to $D_\bfX(\bfx)$:
-
-\vspace{1em}
-\noindent\textbf{(D5)} \textit{Uniform convergence}: $\sup_{\bfx \in \mathbb R^p} | D^n_\bfX (\bfx) - D_\bfX (\bfx) | \rightarrow 0$ as $n \rightarrow \infty $.
-\vspace{1em}
-
-The assumption that empirical depths converge uniformly at all points $\bfx$ to their population versions holds under very mild conditions for several well known depth functions: for example projection depth \citep{zuo03} and simplicial depth \citep{Dumbgen92}.
-One also needs to replace the known location parameter $\bfmu$ by some estimator $\hat\bfmu_n$.
-Examples of robust estimators of location that are relevant here include the spatial median \citep{haldane48,brown83}, Oja median \citep{oja83}, projection median \citep{zuo03} etc.
-Now, given $D^n_\bfX(.)$ and $\hat \bfmu_n$, to plug them into the sample DCM and still go through with the CLT we need the following result:
-
-\begin{Lemma} \label{Lemma:lemma1}
-Consider a random variable $\bfX \in \mathbb{R}^p$ having a continuous and symmetric distribution with location center $\bfmu$ such that $E\|\bfx - \bfmu \|^{-3/2} < \infty$.
-Given $n$ random samples from this distribution, suppose $\hat\bfmu_n$ is an estimator of $\bfmu$ so that $\sqrt n (\hat\bfmu_n - \bfmu) = O_P(1) $.
-Then with the above notations, and given the assumption (D5) we have
-%
-$$ \sqrt n \left[
-\frac{1}{n} \sum_{i=1}^n (\tilde D^n_\bfX (\bfx_i))^2 SS(\bfx_i; \hat\bfmu_n) -
-\frac{1}{n} \sum_{i=1}^n (\tilde D_\bfX (\bfx_i))^2 SS(\bfx_i; \bfmu) \right]
-\stackrel{P}{\rightarrow} 0 $$
-\end{Lemma}
-
-We are now in a position to state the result for consistency of the sample DCM:
-
-\begin{Theorem} \label{Theorem:rootn}
-Consider $n$ iid samples from the distribution in Lemma \ref{Lemma:lemma1}.
-Then, given a depth function $D_\bfX(.)$ and an estimate of center $\hat\bfmu_n$ so that $\sqrt n(\hat \bfmu_n - \bfmu) = O_P(1)$,
-%
-$$ \sqrt n \left[ vec\left\{ \frac{1}{n} \sum_{i=1}^n (\tilde D^n_\bfX (\bfx_i))^2 SS(\bfx_i; \hat\bfmu_n) \right\} - E \left[ vec\left\{ (\tilde D_\bfX (\bfx))^2 SS(\bfx; \bfmu) \right\} \right] \right]
-\stackrel{D}{\rightarrow}
-N_{p^2} ({\bf 0}, V_{D,S}(F)) $$
-$$ \text{with } V_{D,S}(F) = Var \left[vec \left\{ (\tilde D_\bfX (\bfx))^2 SS(\bfx; \bfmu) \right\} \right] $$
-\end{Theorem}
-
-In case $F$ is elliptical, an elaborate form of the covariance matrix $V_{D,S}(F)$ explicitly specifying each of its elements (more directly those of its $\Gamma^T$-rotated version) can be obtained, which is given in Appendix \ref{section:appA}.
-This form is useful when deriving limiting distributions of eigenvectors and eigenvalues of the sample DCM.
-
-\subsection{Eigenvectors and eigenvalues} Since we are mainly interested in using the DCM for a robust version of principal components analysis, from now on we assume that the eigenvalues of $\Sigma$ are distinct: $\lambda_1 > \lambda_2 > ...
-> \lambda_p$ to obtain asymptotic distributions of principal components.
-In the case of eigenvalues with larger than 1 multiplicities, the limiting distributions of eigenprojection matrices can be obtained analogous to those of the sign covariance matrix \citep{magyar14}.
-
-\paragraph{}We now derive the asymptotic joint distributions of eigenvectors and eigenvalues of the sample DCM.
-The following result allows us to get these, provided we know the limiting distribution of the sample DCM itself:
-
-\begin{Theorem} \label{Theorem:decomp} \citep{taskinen12}
-Let $F_\Lambda$ be an elliptical distribution with a diagonal covariance matrix $\Lambda$, and $\hat C$ be any positive definite symmetric $p \times p$ matrix such that at $F_\Lambda$ the limiting distribution of $\sqrt n vec(\hat C - \Lambda)$ is a $p^2$-variate (singular) normal distribution with mean zero.
-Write the spectral decomposition of $\hat C$ as $\hat C = \hat P \hat\Lambda \hat P^T$.
-Then the limiting distributions of $\sqrt n vec(\hat P - I_p)$ and $\sqrt n vec(\hat\Lambda - \Lambda)$ are multivariate (singular) normal and
-%
-\begin{equation} \label{equation:decompEq}
-\sqrt n vec (\hat C - \Lambda)  = \left[ (\Lambda \otimes I_p) - (I_p \otimes \Lambda) \right] \sqrt n vec (\hat P - I_p) + \sqrt n vec (\hat\Lambda - \Lambda) + o_P(1)
-\end{equation}
-\end{Theorem}
-
-The first matrix picks only off-diagonal elements of the LHS and the second one only diagonal elements.
-We shall now use this as well as the form of the asymptotic covariance matrix of the vec of sample DCM, i.e.
-$V_{D,S}(F)$ to obtain limiting variance and covariances of eigenvalues and eigenvectors.
-
-\begin{Corollary} \label{Corollary:eigendist}
-Consider the sample DCM $ \hat S^D(F) = \sum_{i=1}^n (\tilde D^n_\bfX (\bfx_i))^2 SS(\bfx_i; {\bf \hat\bfmu_n})/n $ and its spectral decomposition $\hat S^D(F) = \hat\Gamma_D \hat\Lambda_D \hat\Gamma_D^T $.
-Then the matrices $G = \sqrt n (\hat\Gamma_D - \Gamma) $ and $L = \sqrt n (\hat\Lambda_D - \Lambda_{D,S}) $ have independent distributions.
-The random variable $vec(G)$ asymptotically has a $p^2$-variate normal distribution with mean ${\bf 0}_{p^2}$, and the asymptotic variance and covariance of different columns of $G = (\bfg_1,...,\bfg_p)$ are as follows:
-%
-\begin{equation} \label{equation:DevEq}
-AVar(\bfg_i) = \sum_{k=1; k \neq i}^p \frac{1}{(\lambda_{D,s,k} - \lambda_{D,S,i})^2} E \left[ \frac{(\tilde D_\bfZ (\bfz))^4 \lambda_i \lambda_k z_i^2 z_k^2}{(\bfz^T \Lambda \bfz)^2} \right] \bfgamma_k \bfgamma_k^T
-\end{equation}
-%
-\begin{equation}
-ACov(\bfg_i, \bfg_j) = - \frac{1}{(\lambda_{D,s,i} - \lambda_{D,S,j})^2} E \left[ \frac{(\tilde D_\bfZ (\bfz))^4 \lambda_i \lambda_j z_i^2 z_j^2}{(\bfz^T \Lambda \bfz)^2} \right] \bfgamma_j \bfgamma_i^T; \quad i \neq j
-\end{equation}
-%
-where $\Gamma = (\bfgamma_1,...,\bfgamma_p)$.
-The vector consisting of diagonal elements of $L$, say $\bfl = (\l_1,...,\l_p)^T$ asymptotically has a $p$-variate normal distribution with mean ${\bf 0}_p$ and variance-covariance elements:
-%
-\begin{eqnarray}
-AVar(l_i) &=& E \left[ \frac{(\tilde D_\bfZ (\bfz))^4 \lambda_i^2 z_i^4}{(\bfz^T \Lambda \bfz)^2} \right] - \lambda_{D,S,i}^2\\
-ACov(l_i, l_j) &=& E \left[ \frac{(\tilde D_\bfZ (\bfz))^4 \lambda_i \lambda_j z_i^2 z_j^2}{(\bfz^T \Lambda \bfz)^2} \right] - \lambda_{D,S,i} \lambda_{D,S,j}; \quad i \neq j
-\end{eqnarray}
-%
-\end{Corollary}
-
-\section{Robustness and efficiency properties} \label{section:simSection}
-In this section, we first obtain the influence functions of the DCM as well as its eigenvectors and eigenvalues, which are essential to understand how much influence a sample point, especially an infinitesimal contamination, has on any functional on the distribution \citep{hampel}.
-We also derive the asymptotic efficiencies of individual principal components with respect to those of the original covariance matrix and sign covariance matrix.
-Unlike affine equivariant estimators of shape, the Asymptotic Relative Efficiency (ARE) of eigenvectors (with respect to any other affine equivariant estimator) can not be simplified as a ratio of two scalar quantities dependent on only the distribution of $\| \bfz \|$ (e.g.
-\cite{taskinen12,ollilia03}).
-Finite sample efficiency of the DCM estimates with respect to infinitesimal contamination and heavy-tailed distributions shall also be demonstrated by a simulation study.
-
-\subsection{Influence functions}
-Given any probability distribution $F$, the influence function of any point $\bfx_0$ in the sample space $\mathcal{X}$ for some functional $T(F)$ on the distribution is defined as
-%
-$$ IF(\bfx_0; T,F) = \lim_{\epsilon \rightarrow 0} \frac{1}{\epsilon} (T(F_\epsilon) - T(F)) $$
-%
-where $F_\epsilon$ is $F$ with an additional mass of $\epsilon$ at $\bfx_0$, i.e.
-$F_\epsilon = (1-\epsilon)F + \epsilon \Delta_{\bfx_0}$; $\Delta_{\bfx_0}$ being the distribution with point mass at $\bfx_0$.
-When $T(F) = E_F g$ for some $F$-integrable function $g$, $IF(\bfx_0; T,F) = g(\bfx_0) - T(F)$.
-It now follows that for the DCM,
-%
-$$ IF(\bfx_0; Cov(\tilde \bfX), F) = (\tilde D_\bfX(\bfx_0))^2 SS(\bfx_0; \bfmu) - Cov(\tilde \bfX) $$
-
-Following \cite{croux00}, we now get the influence function of the $i^\text{th}$ column of $\hat\Gamma_D = (\hat\bfgamma_{D,1},...,\hat\bfgamma_{D,p}); i = 1,...,p$:
-%
-\begin{eqnarray}
-IF(\bfx_0; \hat\bfgamma_{D,i}, F) &=& \sum_{k=1; k \neq i}^p \frac{1}{\lambda_{D,S,i} - \lambda_{D,S,k}} \left\{ \bfgamma^T_k IF(\bfx_0; Cov(\tilde \bfX), \bfgamma_i) \right\} \bfgamma_k \notag \\
-&=& \sum_{k=1; k \neq i}^p \frac{1}{\lambda_{D,S,i} - \lambda_{D,S,k}} \left\{ \bfgamma^T_k (\tilde D_\bfX(\bfx_0))^2 SS(\bfx_0; \bfmu)\bfgamma_i - \lambda_{D,S,i}\bfgamma_k^T\bfgamma_i \right\} \bfgamma_k \notag \\
-&=& \sum_{k=1; k \neq i}^p \frac{\sqrt{\lambda_i \lambda_k} z_{0i} z_{0k}}{\lambda_{D,S,i} - \lambda_{D,S,k}}. \frac{(\tilde D_\bfZ(\bfz_0))^2 }{\bfz_0^T \Lambda \bfz_0} \bfgamma_k
-\end{eqnarray}
-%
-where $\Gamma^T \Lambda^{-1/2} (\bfx_0 - \bfmu) = \bfz_0 = (z_{01},...,z_{0p})^T$.
-Clearly this influence function will be bounded, which indicates good robustness properties of principal components.
-Moreover, since the htped function takes small values for points close to the center of the distribution, it does not suffer from the inlier effect that is typical of the SCM and Tyler's shape matrix.
-The influence function for the $i^\text{th}$ eigenvector estimates of these two matrices (say $\hat\bfgamma_{S,i}$ and $\hat\bfgamma_{T,i}$, respectively) are as follows:
-%
+$$ V_{D,S}(F)  = (\Gamma \otimes \Gamma) V_{D,S}(F_\Lambda) (\Gamma \otimes \Gamma)^T$$
+where $F_\Lambda$ has the same elliptic distribution as $F$, but with covariance matrix $\Lambda$. Now,
 \begin{eqnarray*}
-\quad IF(\bfx_0; \hat \bfgamma_{S,i}, F) &=& \sum_{k=1; k \neq i}^p \frac{\sqrt{\lambda_i \lambda_k}}{\lambda_{S,i} - \lambda_{S,k}}.
-\frac{z_{0i} z_{0k}}{\bfz_0^T \Lambda \bfz_0} \bfgamma_k, \text{ with } \lambda_{S,i} = E_\bfZ \left( \frac{\lambda_i z_i^2}{\sum_{j=1}^p \lambda_j z_j^2} \right) \quad \\
-IF(\bfx_0; \hat \bfgamma_{T,i}, F) &=& (p+2) \sum_{k=1; k \neq i}^p \frac{\sqrt{\lambda_i \lambda_k}}{\lambda_i - \lambda_k}. \frac{z_{0i} z_{0k}}{\bfz_0^T \bfz_0} \bfgamma_k \quad 
-\end{eqnarray*}
-%
-for $i = 1,2$.
-In Figure \ref{fig:IFnorm} we consider first eigenvectors of different scatter estimates for the $\mathcal{N}_2((0,0)^T, \diag(2,1))$ and plot norms of these influence functions for different values of $\bfx_0$.
-The plots for SCM and Tyler's shape matrix demonstrate the 'inlier effect', i.e.
-points close to symmetry center and the center itself having high influence.
-The influence function for the sample covariance matrix is obtained by replacing $(p+2)$ by $\| \bfz_0 \|^2$ in the expression of $IF(\bfx_0; \hat \bfgamma_{T,i}, F)$ above, hence is unbounded and the corresponding eigenvector estimators are not robust.
-In comparison, all three DCMs considered here have a bounded influence function as well as small values of the influence function at 'deep' points.
-
-\begin{figure}[]
-	\centering
-		\includegraphics[width=12cm]{../Codes/IFnorm.png}
-	\caption{Plot of the norm of influence function for first eigenvector of (a) sample covariance matrix, (b) SCM, (c) Tyler's scatter matrix and DCMs for (d) Halfspace depth, (e) Mahalanobis depth, (f) Projection depth for a bivariate normal distribution with $\bfmu = {\bf 0}, \Sigma = \diag(2,1)$}
-	\label{fig:IFnorm}
-\end{figure}
-
-\subsection{Asymptotic and finite-sample efficiencies}
-Suppose $\hat\Sigma$ is a $\sqrt n$-consistent estimator of the population covariance matrix $\Sigma$, which permits a spectral decomposition $ \hat\Sigma = \hat\Gamma \hat\Lambda \hat\Gamma^T $, where $\hat\Gamma = (\hat\bfgamma_1,...,\hat\bfgamma_p)$.
-Then the asymptotic variance of the eigenvectors are (see Theorem 13.5.1 in \cite{anderson})
-%
-\begin{equation} \label{equation:covevEq}
-AVar(\sqrt n\hat \bfgamma_i) = \sum_{k=1; k \neq i}^p \frac{\lambda_i \lambda_k}{(\lambda_i - \lambda_k)^2} \bfgamma_k \bfgamma_k^T
-\end{equation}
-%
-The asymptotic relative efficiencies of eigenvectors from the sample DCM with respect to the sample covariance matrix can now be derived using (\ref{equation:covevEq}) above and (\ref{equation:DevEq}) from Corollary \ref{Corollary:eigendist}:
-%
-\begin{eqnarray*}
-ARE(\hat\bfgamma^D_i, \hat\bfgamma_i; F) &=& \frac{\Tr( AVar(\sqrt n\hat \bfgamma_i))}{\Tr( AVar(\sqrt n\hat \bfgamma^D_i))}\\
-&=& \left[\sum_{k=1; k \neq i}^p \frac{\lambda_i \lambda_k}{(\lambda_i - \lambda_k)^2} \right] \left[ \sum_{k=1; k \neq i}^p \frac{\lambda_i \lambda_k }{(\lambda_{D,s,i} - \lambda_{D,S,k})^2} E \left( \frac{(\tilde D_\bfZ (\bfz))^4 z_i^2 z_k^2}{(\bfz^T \Lambda \bfz)^2} \right) \right]^{-1}
+V_{D,S} (F_\Lambda) &=& E \left[ \text{vec} \left\{ \frac{(\tilde D_\bfZ (\bfz))^2 \Lambda^{1/2} \bfz\bfz^T \Lambda^{1/2}}{\bfz^T\Lambda\bfz} - \Lambda_{D,S} \right\} \text{vec}^T \left\{ \frac{(\tilde D_\bfZ (\bfz))^2 \Lambda^{1/2} \bfz\bfz^T \Lambda^{1/2}}{\bfz^T\Lambda\bfz} - \Lambda_{D,S} \right\} \right]\\
+&=& E \left[ \text{vec} \left\{ (\tilde D_\bfZ (\bfz))^2 SS(\Lambda^{1/2}\bfz; \bf0) \right\} \text{vec}^T \left\{ (\tilde D_\bfZ (\bfz))^2 SS(\Lambda^{1/2}\bfz; \bf0) \right\} \right]\\
+&& - \quad \text{vec}(\Lambda_{D,S}) \text{vec}^T(\Lambda_{D,S})
 \end{eqnarray*}
 
-For 2 dimensions, this expression can be somewhat simplified. Suppose the two eigenvalues are $\lambda$ and $\rho\lambda$. In that case the eigenvalues of the DCM are
-%
-$$ \lambda_{D,S,1} = E \left( \frac{(\tilde D_\bfZ(\bfz))^2 z_1^2}{z_1^2 + \rho z_2^2} \right), \quad
-\lambda_{D,S,2} = E \left( \frac{(\tilde D_\bfZ(\bfz))^2 \rho z_2^2}{z_1^2 + \rho z_2^2} \right) $$
-and by simple algebra we get
-%
-$$ ARE(\hat\bfgamma^D_1, \hat\bfgamma_1; F) = ARE(\hat\bfgamma^D_2, \hat\bfgamma_2; F) = \frac{1}{(1-\rho)^2} \frac{\left[ E \left( \frac{(\tilde D_\bfZ(\bfz))^2 (z_1^2 - \rho z_2^2)}{(z_1^2 + \rho z_2^2)} \right) \right]^2 }{E \left( \frac{(\tilde D_\bfZ(\bfz))^4 z_1^2z_2^2}{(z_1^2 + \rho z_2^2)^2}\right)} $$
-
-For $\rho=0.5$, Table \ref{table:AREtable} below considers 6 different elliptic distributions (namely, bivariate $t$ with df = $5,6,10,15,25$ and bivariate normal), and summarizes the ARE for first eigenvector of the SCM, Tyler's scatter matrix and DCM for 3 choices of depth function (HSD-CM, MhD-CM, PD-CM: columns 3-5), as well as their depth-weighted versions mentioned at the end of section \ref{section:dcmSection} (HSD-wCM, MhD-wCM, PD-wCM: columns 6-8).
-The SCM and Tyler's M-estimator perform better than the sample covariance matrix only for a bivariate $t$-distribution with df = 5.
-Estimates based on depth-based covariance matrices have much better performances for all distributions, and continue to be competitive of the sample covariance matrix estimates as the base distribution approaches normality, especially those based on projection depth.
-Interestingly, depth-weighted versions seem to have better performances than their corresponding DCMs, more so for heavy-tailed distributions.
-
-\begin{table}
-\begin{footnotesize}
-    \begin{tabular}{c|cc|ccc|ccc}
-     \hline
-                       & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
-    Bivariate $t_5$    & 1.46 & 1.50  & 1.97   & 1.54   & 1.99  & 2.09    & 1.57    & 2.11   \\
-    Bivariate $t_6$    & 0.97 & 1.00  & 1.37   & 1.12   & 1.40  & 1.45    & 1.19    & 1.49   \\
-    Bivariate $t_{10}$ & 0.65 & 0.67  & 0.96   & 0.88   & 1.02  & 1.02    & 0.94    & 1.10   \\
-    Bivariate $t_{15}$ & 0.57 & 0.59  & 0.87   & 0.82   & 0.94  & 0.92    & 0.87    & 1.00   \\
-    Bivariate $t_{25}$ & 0.54 & 0.55  & 0.79   & 0.75   & 0.88  & 0.85    & 0.81    & 0.95   \\
-    BVN   & 0.49 & 0.50  & 0.73   & 0.71   & 0.82  & 0.77    & 0.75    & 0.88   \\ \hline
-    \end{tabular}
-\end{footnotesize}
-\caption{Asymptotic efficiencies relative to sample covariance matrix for $p=2$}
-\label{table:AREtable}
-\end{table}
-
-We now obtain finite sample efficiencies of the three DCMs as well as their depth-weighted affine equivariant counterparts by a simulation study, and compare them with the same from the SCM and Tyler's scatter matrix.
-We consider the same 6 elliptical distributions considered in ARE calculations above, and from every distribution draw 10000 samples each for sample sizes $n = 20, 50, 100, 300, 500$.
-All distributions are centered at ${\bf 0}_p$, and have covariance matrix $\Sigma = \diag(p,p-1,...1)$.
-We consider 3 choices of $p$: 2, 3 and 4.
-
-We use the concept of principal angles \citep{miao92} to find out error estimates for the first eigenvector of a scatter matrix. In our case, the first eigenvector will be
-%
-$$ \bfgamma_1 = (1,\overbrace{0,...,0}^{p-1})^T $$
-%
-For an estimate of the eigenvector, say $\hat\bfgamma_1$, error in prediction is measured by the smallest angle between the two lines, i.e.
-$ \cos^{-1} | \bfgamma_1^T \hat\bfgamma_1 | $.
-A smaller absolute value of this angle is equivalent to better prediction.
-We repeat this 10000 times and calculate the \textbf{Mean Squared Prediction Angle}:
-%
-$$ MSPA(\hat \bfgamma_1) = \frac{1}{10000} \sum_{m=1}^{10000} \left( \cos^{-1} \left|\bfgamma_1^T \hat\bfgamma^{(m)}_1 \right| \right)^2 $$
-%
-Finally, the finite sample efficiency of some eigenvector estimate $\hat\bfgamma^E_1$ relative to that obtained from the sample covariance matrix, say $\hat\bfgamma^{Cov}_1$ is obtained as:
-$$ FSE(\hat\bfgamma^E_1, \hat\bfgamma^{Cov}_1) = \frac{MSPA(\hat\bfgamma^{Cov}_1)}{MSPA(\hat\bfgamma^E_1)} $$
-
-Tables \ref{table:FSEtable2}, \ref{table:FSEtable3} and \ref{table:FSEtable4} give FSE values for $p=2,3,4$, respectively.
-In general, all the efficiencies increase as the dimension $p$ goes up.
-DCM-based estimators (columns 3-5 in each table) outperform SCM and Tyler's scatter matrix, and among the 3 depths considered, projection depth seems to give the best results.
-Its finite sample performances are better than Tyler's and Huber's M-estimators of scatter as well as their symmetrized counterparts (see Table 4 in \cite{sirkia07}, and quite close to the affine equivariant spatial sign covariance matrix (see Table 2 in \cite{ollilia03}) For $p=2$, $n=300, 500$ the first 5 columns of Table \ref{table:FSEtable2} approximate the asymptotic efficiencies in Table \ref{table:AREtable} well, except for the multivariate $t$-distribution with df = 5.
-Finally, the depth-weighted iterated versions of these 3 SCMs (columns 6-8 in each table) seem to further better the performance of their corresponding orthogonal equivariant counterparts.
-
-\begin{table}
-\begin{footnotesize}
-    \begin{tabular}{c|cc|ccc|ccc}
-    \hline
-    $F$ = Bivariate $t_5$    & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
-    $n$=20                   & 0.80 & 0.83  & 0.95   & 0.95   & 0.89  & 1.00    & 0.96    & 0.89   \\
-    $n$=50                   & 0.86 & 0.90  & 1.25   & 1.10   & 1.21  & 1.32    & 1.13    & 1.25   \\
-    $n$=100                  & 1.02 & 1.04  & 1.58   & 1.20   & 1.54  & 1.67    & 1.24    & 1.63   \\
-    $n$=300                  & 1.24 & 1.28  & 1.81   & 1.36   & 1.82  & 1.93    & 1.44    & 1.95   \\
-    $n$=500                  & 1.25 & 1.29  & 1.80   & 1.33   & 1.84  & 1.91    & 1.39    & 1.97   \\ \hline
-    $F$ = Bivariate $t_6$    & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
-    $n$=20                   & 0.77 & 0.79  & 0.92   & 0.92   & 0.86  & 0.96    & 0.92    & 0.85   \\
-    $n$=50                   & 0.76 & 0.78  & 1.11   & 1.00   & 1.08  & 1.17    & 1.03    & 1.13   \\
-    $n$=100                  & 0.78 & 0.79  & 1.27   & 1.06   & 1.33  & 1.35    & 1.11    & 1.41   \\
-    $n$=300                  & 0.88 & 0.91  & 1.29   & 1.09   & 1.35  & 1.38    & 1.15    & 1.45   \\
-    $n$=500                  & 0.93 & 0.96  & 1.37   & 1.13   & 1.40  & 1.44    & 1.19    & 1.48   \\ \hline
-    $F$ = Bivariate $t_{10}$ & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
-    $n$=20                   & 0.70 & 0.72  & 0.83   & 0.84   & 0.77  & 0.89    & 0.87    & 0.79   \\
-    $n$=50                   & 0.58 & 0.60  & 0.90   & 0.84   & 0.86  & 0.95    & 0.88    & 0.91   \\
-    $n$=100                  & 0.57 & 0.59  & 0.92   & 0.87   & 0.97  & 0.98    & 0.90    & 1.03   \\
-    $n$=300                  & 0.62 & 0.64  & 0.93   & 0.85   & 0.99  & 0.99    & 0.91    & 1.06   \\
-    $n$=500                  & 0.62 & 0.65  & 0.93   & 0.86   & 1.00  & 1.00    & 0.92    & 1.08   \\ \hline
-    $F$ = Bivariate $t_{15}$ & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
-    $n$=20                   & 0.63 & 0.66  & 0.76   & 0.78   & 0.72  & 0.81    & 0.81    & 0.73   \\
-    $n$=50                   & 0.52 & 0.52  & 0.79   & 0.75   & 0.80  & 0.84    & 0.79    & 0.85   \\
-    $n$=100                  & 0.51 & 0.52  & 0.83   & 0.77   & 0.88  & 0.88    & 0.81    & 0.94   \\
-    $n$=300                  & 0.55 & 0.56  & 0.84   & 0.79   & 0.91  & 0.89    & 0.84    & 0.98   \\
-    $n$=500                  & 0.56 & 0.59  & 0.85   & 0.80   & 0.93  & 0.91    & 0.86    & 0.99   \\ \hline
-    $F$ = Bivariate $t_{25}$ & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
-    $n$=20                   & 0.63 & 0.65  & 0.77   & 0.79   & 0.74  & 0.80    & 0.81    & 0.74   \\
-    $n$=50                   & 0.49 & 0.50  & 0.73   & 0.71   & 0.76  & 0.78    & 0.75    & 0.80   \\
-    $n$=100                  & 0.45 & 0.46  & 0.73   & 0.69   & 0.81  & 0.78    & 0.73    & 0.87   \\
-    $n$=300                  & 0.51 & 0.52  & 0.78   & 0.75   & 0.87  & 0.83    & 0.79    & 0.94   \\
-    $n$=500                  & 0.53 & 0.55  & 0.79   & 0.75   & 0.87  & 0.84    & 0.80    & 0.94   \\ \hline
-    $F$ = BVN                & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
-    $n$=20                   & 0.56 & 0.60  & 0.69   & 0.71   & 0.67  & 0.73    & 0.74    & 0.68   \\
-    $n$=50                   & 0.42 & 0.43  & 0.66   & 0.66   & 0.70  & 0.71    & 0.69    & 0.75   \\
-    $n$=100                  & 0.42 & 0.43  & 0.69   & 0.66   & 0.77  & 0.74    & 0.71    & 0.83   \\
-    $n$=300                  & 0.47 & 0.49  & 0.71   & 0.69   & 0.82  & 0.76    & 0.73    & 0.88   \\
-    $n$=500                  & 0.48 & 0.50  & 0.73   & 0.71   & 0.83  & 0.78    & 0.76    & 0.89   \\ \hline
-    \end{tabular}
-\end{footnotesize}
-\caption{Finite sample efficiencies of several scatter matrices: $p=2$}
-\label{table:FSEtable2}
-\end{table}
-
-\begin{table}
-\begin{footnotesize}
-   \begin{tabular}{c|cc|ccc|ccc}
-    \hline
-    3-variate $t_5$    & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
-    $n$=20             & 0.96 & 0.97  & 1.06   & 1.03   & 0.99  & 1.07    & 1.06    & 0.97   \\
-    $n$=50             & 1.07 & 1.08  & 1.28   & 1.20   & 1.18  & 1.33    & 1.23    & 1.20   \\
-    $n$=100            & 1.12 & 1.15  & 1.49   & 1.31   & 1.40  & 1.57    & 1.38    & 1.48   \\
-    $n$=300            & 1.49 & 1.54  & 2.09   & 1.82   & 2.07  & 2.19    & 1.93    & 2.18   \\
-    $n$=500            & 1.60 & 1.66  & 2.18   & 1.87   & 2.21  & 2.27    & 1.95    & 2.30   \\ \hline
-    3-variate $t_6$    & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
-    $n$=20             & 0.90 & 0.92  & 1.00   & 0.99   & 0.95  & 1.02    & 1.01    & 0.94   \\
-    $n$=50             & 0.95 & 0.96  & 1.16   & 1.09   & 1.09  & 1.21    & 1.14    & 1.11   \\
-    $n$=100            & 0.98 & 0.99  & 1.32   & 1.22   & 1.25  & 1.38    & 1.27    & 1.29   \\
-    $n$=300            & 1.10 & 1.14  & 1.57   & 1.40   & 1.58  & 1.62    & 1.47    & 1.64   \\
-    $n$=500            & 1.17 & 1.20  & 1.57   & 1.43   & 1.60  & 1.63    & 1.51    & 1.67   \\ \hline
-    3-variate $t_{10}$ & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
-    $n$=20             & 0.87 & 0.88  & 0.95   & 0.94   & 0.90  & 0.97    & 0.98    & 0.89   \\
-    $n$=50             & 0.77 & 0.79  & 0.96   & 0.92   & 0.94  & 0.99    & 0.96    & 0.95   \\
-    $n$=100            & 0.75 & 0.76  & 1.02   & 0.95   & 1.01  & 1.06    & 1.00    & 1.05   \\
-    $n$=300            & 0.73 & 0.75  & 1.03   & 0.98   & 1.10  & 1.08    & 1.03    & 1.15   \\
-    $n$=500            & 0.73 & 0.76  & 1.02   & 0.98   & 1.09  & 1.06    & 1.02    & 1.14   \\ \hline
-    3-variate $t_{15}$ & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
-    $n$=20             & 0.84 & 0.86  & 0.92   & 0.92   & 0.89  & 0.94    & 0.94    & 0.87   \\
-    $n$=50             & 0.75 & 0.76  & 0.92   & 0.90   & 0.90  & 0.96    & 0.94    & 0.93   \\
-    $n$=100            & 0.66 & 0.67  & 0.91   & 0.87   & 0.95  & 0.96    & 0.92    & 1.00   \\
-    $n$=300            & 0.61 & 0.64  & 0.90   & 0.87   & 1.00  & 0.93    & 0.91    & 1.04   \\
-    $n$=500            & 0.65 & 0.67  & 0.89   & 0.87   & 0.99  & 0.93    & 0.91    & 1.03   \\ \hline
-    3-variate $t_{25}$ & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
-    $n$=20             & 0.78 & 0.79  & 0.87   & 0.89   & 0.87  & 0.89    & 0.92    & 0.86   \\
-    $n$=50             & 0.70 & 0.71  & 0.88   & 0.86   & 0.88  & 0.91    & 0.90    & 0.90   \\
-    $n$=100            & 0.61 & 0.63  & 0.86   & 0.83   & 0.89  & 0.90    & 0.88    & 0.94   \\
-    $n$=300            & 0.58 & 0.59  & 0.83   & 0.80   & 0.92  & 0.87    & 0.85    & 0.98   \\
-    $n$=500            & 0.62 & 0.64  & 0.83   & 0.82   & 0.94  & 0.88    & 0.87    & 0.99   \\ \hline
-    3-variate Normal   & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
-    $n$=20             & 0.76 & 0.78  & 0.85   & 0.87   & 0.84  & 0.87    & 0.90    & 0.83   \\
-    $n$=50             & 0.66 & 0.67  & 0.82   & 0.81   & 0.84  & 0.86    & 0.86    & 0.86   \\
-    $n$=100            & 0.56 & 0.58  & 0.77   & 0.75   & 0.83  & 0.82    & 0.79    & 0.87   \\
-    $n$=300            & 0.53 & 0.55  & 0.75   & 0.74   & 0.85  & 0.79    & 0.78    & 0.90   \\
-    $n$=500            & 0.56 & 0.58  & 0.76   & 0.76   & 0.87  & 0.80    & 0.80    & 0.92   \\ \hline
-    \end{tabular}
-\end{footnotesize}
-\caption{Finite sample efficiencies of several scatter matrices: $p=3$}
-\label{table:FSEtable3}
-\end{table}
-
-\begin{table}
-\begin{footnotesize}
-    \begin{tabular}{c|cc|ccc|ccc}
-    \hline
-    4-variate $t_5$    & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
-    $n$=20             & 1.04 & 1.02  & 1.10   & 1.07   & 1.02  & 1.09    & 1.07    & 0.98   \\
-    $n$=50             & 1.08 & 1.08  & 1.16   & 1.16   & 1.13  & 1.19    & 1.19    & 1.13   \\
-    $n$=100            & 1.31 & 1.31  & 1.42   & 1.38   & 1.36  & 1.46    & 1.44    & 1.36   \\
-    $n$=300            & 1.46 & 1.54  & 1.81   & 1.76   & 1.95  & 1.88    & 1.88    & 1.95   \\
-    $n$=500            & 1.92 & 1.93  & 2.23   & 2.03   & 2.31  & 2.35    & 2.19    & 2.39   \\ \hline
-    4-variate $t_6$    & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
-    $n$=20             & 1.00 & 1.05  & 1.03   & 1.05   & 1.00  & 1.04    & 1.04    & 0.95   \\
-    $n$=50             & 1.03 & 1.01  & 1.13   & 1.12   & 1.11  & 1.19    & 1.17    & 1.10   \\
-    $n$=100            & 1.08 & 1.12  & 1.25   & 1.23   & 1.27  & 1.24    & 1.25    & 1.22   \\
-    $n$=300            & 1.34 & 1.36  & 1.64   & 1.52   & 1.60  & 1.67    & 1.61    & 1.68   \\
-    $n$=500            & 1.26 & 1.34  & 1.55   & 1.49   & 1.60  & 1.65    & 1.61    & 1.69   \\ \hline
-    4-variate $t_{10}$ & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
-    $n$=20             & 0.90 & 0.89  & 0.95   & 0.98   & 0.98  & 0.96    & 1.01    & 0.95   \\
-    $n$=50             & 0.90 & 0.91  & 1.01   & 0.98   & 0.98  & 1.03    & 1.04    & 0.99   \\
-    $n$=100            & 0.87 & 0.87  & 0.93   & 0.95   & 1.01  & 0.99    & 1.01    & 1.05   \\
-    $n$=300            & 0.87 & 0.87  & 1.09   & 1.09   & 1.17  & 1.14    & 1.16    & 1.23   \\
-    $n$=500            & 0.88 & 0.92  & 1.10   & 1.10   & 1.23  & 1.19    & 1.22    & 1.29   \\ \hline
-    4-variate $t_{15}$ & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
-    $n$=20             & 0.92 & 0.90  & 0.94   & 0.94   & 0.96  & 0.95    & 0.97    & 0.89   \\
-    $n$=50             & 0.82 & 0.83  & 0.88   & 0.91   & 0.93  & 0.88    & 0.93    & 0.93   \\
-    $n$=100            & 0.84 & 0.87  & 0.92   & 0.95   & 1.00  & 0.93    & 0.96    & 1.00   \\
-    $n$=300            & 0.73 & 0.75  & 0.96   & 0.99   & 1.10  & 1.00    & 1.06    & 1.12   \\
-    $n$=500            & 0.73 & 0.76  & 0.95   & 0.96   & 1.06  & 0.94    & 0.97    & 1.06   \\ \hline
-    4-variate $t_{25}$ & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
-    $n$=20             & 0.89 & 0.92  & 0.92   & 0.92   & 0.90  & 0.96    & 0.95    & 0.89   \\
-    $n$=50             & 0.82 & 0.84  & 0.89   & 0.90   & 0.91  & 0.93    & 0.96    & 0.92   \\
-    $n$=100            & 0.77 & 0.76  & 0.90   & 0.90   & 0.96  & 0.94    & 0.98    & 1.04   \\
-    $n$=300            & 0.73 & 0.77  & 0.93   & 0.91   & 0.98  & 1.00    & 0.98    & 1.03   \\
-    $n$=500            & 0.67 & 0.71  & 0.83   & 0.83   & 0.96  & 0.88    & 0.90    & 1.00   \\ \hline
-    4-variate Normal   & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
-    $n$=20             & 0.82 & 0.84  & 0.87   & 0.90   & 0.91  & 0.89    & 0.93    & 0.89   \\
-    $n$=50             & 0.80 & 0.81  & 0.87   & 0.88   & 0.88  & 0.88    & 0.92    & 0.88   \\
-    $n$=100            & 0.68 & 0.71  & 0.80   & 0.85   & 0.91  & 0.82    & 0.86    & 0.92   \\
-    $n$=300            & 0.61 & 0.63  & 0.82   & 0.85   & 0.93  & 0.86    & 0.91    & 0.96   \\
-    $n$=500            & 0.60 & 0.64  & 0.77   & 0.80   & 0.90  & 0.82    & 0.86    & 0.96   \\ \hline
-    \end{tabular}
-\end{footnotesize}
-\caption{Finite sample efficiencies of several scatter matrices: $p=4$}
-\label{table:FSEtable4}
-\end{table}
-
-\section{Examples in real data analysis}\label{section:sec6}
-%\subsection{Communities and crime data}
-%This data is from the UCI machine learning repository [], and consists information on 101 demographic and socio-economic variables (like population, racial percentages, percentage of people living in urbal areas etc.)  in 1994 community areas in the United States.
-The dataset is a combination of data from the 1990 US Census, 1990 US Law Enforcement Management and Administrative Statistics survey and 1995 FBI Uniform Crime Reporting data.
-%
-%With the goal of building a model for the total number of violent crimes per 100K population from others, we initially do normal and depth-based PCA on the other variables.
-While doing the depth-based PCA, we use projection depth as our chosen depth function.
-After obtaining the PCA models, we take the first $k$ PCs in each case and build linear models for both the methods.
-This is repeated for $k = 1,2,...,100$ and the $R^2$ values on principal components regression models of the two types are plotted in Figure \ref{fig:rsqplot}.
-For building linear regression models, we keep all the predictors unchanged, while go for an inverse cubic transformation on the response variable.
-We do this since boxcox transformations on all of the models we consider suggest optimal power transformations of values close to --3.
-%
-%From the screeplots in \ref{fig:screeplot} we see that both the methods explain similar amounts of variances in the leading few PCs.
-As for the model performances, linear regressions based on depth-PCA have slightly higher $R^2$ values when the top few (upto 10) principal components are used.
-At around 20 PCs the two models have same $R^2$ values and the normal PC-regression models perform slightly better after that.
-%
-%\begin{figure}[t]
-%	\captionsetup{singlelinecheck=off}
-%	\centering
-%		\includegraphics[height=5cm]{../Codes/crime_screeplots.png}
-%	\caption{(Left) Screeplots for two types of PCA on communities data}
-%	\label{fig:screeplot}
-%\end{figure}
-%
-%\begin{figure}[t]
-%	\captionsetup{singlelinecheck=off}
-%	\centering
-%		\includegraphics[height=7cm]{../Codes/crime_Rsq_plot.png}
-%	\caption{(Left) Change of $R^2$ values for normal and depth-based principal components regression models on communities data}
-%	\label{fig:rsqplot}
-%\end{figure}
-
-\subsection{Bus data}
-This dataset is available in the R package \texttt{rrcov}, and consists of data on images of 218 buses.
-The 18 variables here correspond to several features related to these images.
-Here we extend upon the analysis in \cite{maronna06}, pp.
-213 to compare the classical PCA and 3 different methods of robust PCA (including that using SCM) with our DCM-based method.
-Similar to the original analysis, we set aside variable 9 and scale the other variables by dividing with their respective median absolute deviations (MAD).
-This is done because all the variables had much larger standard deviations compared to their MADs, and variable 9 had MAD = 0.
-
-For the sake of uniformity, we use projection depth as our fixed depth function while doing depth-based PCA in our data analysis examples.
-We compare the outputs of classical (CPCA) and depth-based PCA (DPCA) with the following 3 robust methods: Spherical PCA, i.e.
-PCA based on the SCM (SPCA), PCs obtained by the ROBPCA algorithm \citep{hubert05}, and the Minimum Covariance Determinant (MCD) estimator \citep{Rousseeuw84leastmedian} (MPCA).
-Table \ref{table:bus_table1} gives the proportions of variability that are left unexplained after the top $q$ $(= 1,...,6)$ components are taken into account in each of the 5 methods.
-The first PC in classical PCA seems to explain a much higher proportion of variability in original data than robust methods.
-However, as noted in \cite{maronna06} and \cite{hubert05}, this is a result of the classical variances being inflated due to outliers in the direction of the first principal axis.
-Among the robust methods, the proportions of unexplained variances are highest for DCM-based PCA for all values of $q$.
-
-Table \ref{table:bus_table2} demonstrates why robust methods actually give a better representation of the underlying data structure than classical PCA here.
-Each of its column lists different quantiles of the squared orthogonal distance for a sample point from the hyperplane formed by top 3 PCs estimated by the corresponding method.
-For PCA based on projection-DCM, the estimated principal component subspaces are closer to the data than CPCA for more than 90\% of samples, and the distance only becomes larger for higher quantiles.
-This means that for CPCA, estimated basis vectors of the hyperspace get pulled by extreme outlying points, while the influence of these outliers is very low for DPCA.
-SPCA and ROBPCA perform very closely in this respect, the percentage of points that have less squared distance than CPCA being between 80\% and 90\% for both of them.
-This percentage is only 50\% for MPCA, which suggests that the corresponding 3-dimensional subspace estimated by MCD is possibly not an accurate representation of the truth.
-
-\begin{table}[t]
-\centering
-    \begin{tabular}{c|ccccc}
-    \hline
-    \begin{large} $q$ \end{large} & \multicolumn{5}{c}{Method of PCA}         \\ \cline{2-6}
-    ~                   & CPCA     & SPCA & ROBPCA & MPCA & DPCA \\\hline 
-    1                   & 0.188         & 0.549     & 0.410  & 0.514     & 0.662     \\
-    2                   & 0.084         & 0.272     & 0.214  & 0.337     & 0.359     \\
-    3                   & 0.044         & 0.182     & 0.121  & 0.227     & 0.237     \\
-    4                   & 0.026         & 0.135     & 0.083  & 0.154     & 0.173     \\
-    5                   & 0.018         & 0.099     & 0.054  & 0.098     & 0.115     \\
-    6                   & 0.012         & 0.069     & 0.036  & 0.070     & 0.084     \\ \hline
-    \end{tabular}
-    \caption{Unexplained proportions of variability by PCA models with $q$ components for bus data}
-    \label{table:bus_table1}
-\end{table}
-
-\begin{table}[t]
-\centering
-    \begin{tabular}{c|ccccc}
-    \hline
-    Quantile & \multicolumn{5}{c}{Method of PCA}         \\ \cline{2-6}
-    ~                   & CPCA     & SPCA & ROBPCA & MPCA & DPCA \\\hline 
-    10\%      & 1.9       & 1.2       & 1.2    & 1.0       & 1.2       \\
-    20\%      & 2.3       & 1.6       & 1.6    & 1.3       & 1.6       \\
-    30\%      & 2.8       & 1.8       & 1.8    & 1.7       & 1.9       \\
-    40\%      & 3.2       & 2.2       & 2.1    & 2.1       & 2.3       \\
-    50\%      & 3.7       & 2.6       & 2.5    & 3.1       & 2.6       \\
-    60\%      & 4.4       & 3.1       & 3.0    & 5.9       & 3.2       \\
-    70\%      & 5.4       & 3.8       & 3.9    & 25.1      & 3.9       \\
-    80\%      & 6.5       & 5.2       & 4.8    & 86.1      & 4.8       \\
-    90\%      & 8.2       & 9.0       & 10.9   & 298.2     & 6.9      \\
-    Max       & 24        & 1037      & 1055   & 1037      & 980      \\\hline
-    \end{tabular}
-    \caption{Quantiles to squared distance from 3-principal component hyperplanes for bus data}
-    \label{table:bus_table2}
-\end{table}
-
-\subsection{Octane data}
-We now apply our method to a high-dimensional dataset and demonstrate its effectiveness in outlier detection.
-Due to \cite{esbensen94}, this dataset consists of 226 variables and 39 observations.
-Each observation is a gasoline sample with a certain octane number, and have their NIR absorbance spectra measured in 2 nm intervals between 1100 - 1550 nm.
-There are 6 outliers here: compounds 25, 26 and 36-39, which contain alcohol.
-Proportions of \textit{explained} variability by PCs obtained by the two methods are given in Figure \ref{fig:screeplot}.
-Once again, the first PC in CPCA explains a much larger proportion of variance than DPCA.
-Second and third PCs obtained by DPCA explain higher proportions of variability than the corresponding components in CPCA.
-
-In both methods, the first two PCs explains a large amount (98\% for CPCA, 89\% for DPCA) of underlying variability.
-But in DPCA, these PCs are more effective in detecting outliers, which we demonstrate in Figure \ref{fig:distplot}.
-For any method of PCA with $k$ components on a dataset of $n$ observations and $p$ variables, the \textbf{score distance} (SD) and \textbf{orthogonal distance} (OD) for $i^\text{th}$ observation ($i=1,2,...,n$) are defined as:
-$$ SD_i = \sqrt{ \sum_{j=1}^k \frac{s^2_{ij}}{\lambda_j}}; \quad OD_i = \| \bfx_i - P\bfs_i^T \| $$
-where $S = (\bfs_1, \ldots ,\bfs_n)^T$ is the $n\times k$ scoring matrix, $P$ the $p\times k$ loading matrix, and $\lambda_1,\ldots ,\lambda_k$ are eigenvalues obtained from the PCA, and $\bfx_1,\ldots,\bfx_n$ are the $n$ observation vectors.
-We only consider the first 2 PCs here, so $k$ is set to 2.
-From a practical standpoint, $SD_i$ can be interpreted as a weighted norm of the projection of the $i^\text{th}$ point on the hyperplane formed by first $k$ principal components, and $OD_i$ the orthogonal distance of point $i$ from that hyperplane.
-For outlier detection, following \cite{hubert05} we set the upper cutoff values for score distances at $\sqrt{\chi^2_{2,.975}}$ and orthogonal distances at $[\text{median}(OD^{2/3}) + \text{MAD}(OD^{2/3})\Phi^{-1}(0.975)]^{3/2}$, where $\Phi(.)$ is the standard normal cumulative distribution function.
-These cutoffs are marked by red lines in the diagnostic plots in figure \ref{fig:distplot}.
-In the figure we see that CPCA detects only 1 of the 6 outliers (point 26, left panel).
-Compared to this the diagnostic plot corresponding to DPCA in the right panel correctly detects all 6 outlying points.
-All of them have larger score distances than the score cutoff value, while points 25, 26 and 38 have higher-than-cutoff orthogonal distances as well.
-Interestingly, the arrangement of outlying points here is similar to that in the diagnostic plot corresponding to ROBPCA, which can be found in figure 5(b) of \cite{hubert05}.
-
-\begin{figure}[t]
-	\centering
-		\includegraphics[height=6cm]{../Codes/octane_screeplot.pdf}
-	\caption{Explained variance proportions for two types of PCA on octane data}
-	\label{fig:screeplot}
-\end{figure}
-\begin{figure}[t]
-	\centering
-		\includegraphics[height=6.5cm]{../Codes/octane_distanceplot.pdf}
-	\caption{Distance plots for two types of PCA on octane data}
-	\label{fig:distplot}
-\end{figure}
-
-\section{Conclusion}\label{section:sec7}
-
-In the above sections we introduce a covariance matrix based on depth-based multivariate ranks that keeps the eigenvectors of the actual population unchanged for elliptical distributions.
-We provide asymptotic results for the sample DCM, its eigenvalues and eigenvectors.
-Bounded influence functions as well as simulation studies suggest that the eigenvector estimates obtained from the DCM are highly robust, yet do not lose much in terms of efficiency.
-Thus it provides a plausible alternative to existing approaches of robust PCA that are based on estimation of covariance matrices (for example SCM, Tyler's scatter matrix, D\"{u}mbgen's symmetrized shape matrix).
-
-An immediate extension of this would be to study the depth-weighted iterated scatter matrices, i.e. matrices $\Sigma_{Dw}$ that are solution to the following type of equations:
-
-$$ \Sigma_{Dw} = E \left[ \frac{(\tilde D_\bfX(\bfx))^2 (\bfx - \bfmu) (\bfx - \bfmu)^T}{(\bfx - \bfmu)^T \Sigma_{Dw}^{-1} (\bfx - \bfmu)} \right] $$
-as their eigenvector estimates seem to have better efficiency than those obtained from the corresponding DCMs.
-Unlike the DCM, these matrices will possess the affine equivariance property.
-It is possible to develop tests for central and elliptic symmetry based on the decomposition of the multivariate rank vector in equation \ref{equation:rankdecomp}.
-The result in Theorem \ref{Theorem:covform} is based on the fact that $E(\tilde \bfX) = \bf0$, and it holds for any centrally symmetric underlying distribution.
-Moreover, the depth of a point in the standardized scale (i.e.
-$\bfz$-scale) does not depend on the direction of $\bfz$.
-This is not possible without circular symmetry of $\bfz$, so any test of independence between $D_\bfZ (\bfz)$ and $\bfS (\bfz)$ can be seen as a test of ellipticity for the original random variable $\bfX$.
-Finally the applicability of this procedure in high-dimensional and functional data remains to be explored.
-
-\appendix
-\section*{Appendix}
-\numberwithin{equation}{section}
-\section{\textbf{Form of $V_{D,S}(F)$}}\label{section:appA}
-
-First observe that for $F$ having covariance matrix $\Sigma = \Gamma\Lambda\Gamma^T$,
-%
-$$ V_{D,S}(F)  = (\Gamma \otimes \Gamma) V_{D,S}(F_\Lambda) (\Gamma \otimes \Gamma)^T$$
-%
-where $F_\Lambda$ has the same elliptic distribution as $F$, but with covariance matrix $\Lambda$. Now,
-%
-\begin{eqnarray*}
-V_{D,S} (F_\Lambda) &=& E \left[ vec \left\{ \frac{(\tilde D_\bfZ (\bfz))^2 \Lambda^{1/2} \bfz\bfz^T \Lambda^{1/2}}{\bfz^T\Lambda\bfz} - \Lambda_{D,S} \right\} vec^T \left\{ \frac{(\tilde D_\bfZ (\bfz))^2 \Lambda^{1/2} \bfz\bfz^T \Lambda^{1/2}}{\bfz^T\Lambda\bfz} - \Lambda_{D,S} \right\} \right]\\
-&=& E \left[ vec \left\{ (\tilde D_\bfZ (\bfz))^2 SS(\Lambda^{1/2}\bfz; \bf0) \right\} vec^T \left\{ (\tilde D_\bfZ (\bfz))^2 SS(\Lambda^{1/2}\bfz; \bf0) \right\} \right]\\
-&& - \quad vec(\Lambda_{D,S}) vec^T(\Lambda_{D,S})
-\end{eqnarray*}
-
-The matrix $vec(\Lambda_{D,S}) vec^T(\Lambda_{D,S})$ consists of elements $\lambda_i\lambda_j$ at $(i,j)^\text{th}$ position of the $(i,j)^\text{th}$ block, and 0 otherwise.
+The matrix $\text{vec}(\Lambda_{D,S}) \text{vec}^T(\Lambda_{D,S})$ consists of elements $\lambda_i\lambda_j$ at $(i,j)^\text{th}$ position of the $(i,j)^\text{th}$ $p \times p$ block, for $1 \leq i,j \leq p$, and 0 otherwise.
 These positions correspond to variance and covariance components of on-diagonal elements.
@@
 Following a similar derivation for spatial sign covariance matrices in \cite{magyar14}, we collect the non-zero elements and write the matrix of expectations:
-%
+
 $$ (I_{p^2} + K_{p,p}) \left\{ \sum_{a=1}^p \sum_{b=1}^p \gamma^D_{ab} (\bfe_a \bfe_a^T \otimes  \bfe_b \bfe_b^T) - \sum_{a=1}^p \gamma^D_{aa} (\bfe_a \bfe_a^T \otimes  \bfe_a \bfe_a^T) \right\} + \sum_{a=1}^p \sum_{b=1}^p \gamma^D_{ab} (\bfe_a \bfe_b^T \otimes  \bfe_a \bfe_b^T) $$
-%
 where $I_k = (\bfe_1,...,\bfe_k), K_{m,n} = \sum_{i=1}^m \sum_{j=1}^n J_{ij} \otimes J_{ij}^T$ with $J_{ij}$ the $m \times n$ matrix having 1 as $(i,j)^\text{th}$ element and 0 elsewhere, and $\gamma^D_{mn} = E[ \lambda_m \lambda_n z_m^2 z_n ^2 .
@@
 \item Variance of on-diagonal elements
-%
+
 $$ AVar( \sqrt n \hat S^D_{aa} (F_\Lambda)) = E \left[ \frac{(\tilde D_\bfZ (\bfz))^4 \lambda_a^2 z_a^4}{(\bfz^T \Lambda \bfz)^2} \right] - \lambda_{D,S,a}^2 $$
@@
 \item Variance of off-diagonal elements ($a \neq b$)
-%
+
 $$ AVar( \sqrt n \hat S^D_{ab} (F_\Lambda)) = E \left[ \frac{(\tilde D_\bfZ (\bfz))^4 \lambda_a \lambda_b z_a^2 z_b^2}{(\bfz^T \Lambda \bfz)^2} \right] $$
@@
 \item Covariance of two on-diagonal elements ($a \neq b$)
-%
+
 $$ ACov(\sqrt n \hat S^D_{aa} (F_\Lambda), \sqrt n \hat S^D_{bb} (F_\Lambda))
@@
 \item Covariance of two off-diagonal elements ($a \neq b \neq c \neq d$)
-%
+
 $$ ACov(\sqrt n \hat S^D_{ab} (F_\Lambda), \sqrt n \hat S^D_{cd} (F_\Lambda)) = 0 $$
@@
 \item Covariance of one off-diagonal and one on-diagonal element ($a \neq b \neq c$)
-%
+
 $$ ACov(\sqrt n \hat S^D_{ab} (F_\Lambda), \sqrt n \hat S^D_{cc} (F_\Lambda)) = 0 $$
@@
 
-\section{Proofs}\label{section:appB}
-
+\section*{Appendix B: Proofs}
 \begin{proof}[Proof of Theorem  \ref{Theorem:covform}]
 The proof follows directly from writing out the expression of $Cov ( \tilde \bfX)$:
-%
+
 \begin{eqnarray*}
@@
 \end{eqnarray*}
-%
 \end{proof}
@@
 For two positive definite matrices $A,B$, we denote by $A>B$ that $A-B$ is positive definite. Also, denote
-%
+
 $$ S_n = \sqrt n \left[ \frac{1}{n} \sum_{i=1}^n \left| (\tilde D^{n} _\bfX (\bfx_i))^2  - (\tilde D_\bfX (\bfx_i))^2 \right| SS(\bfx_i; \hat\bfmu_n) \right] $$
-%
-%Consider now the quantity $\bft^T S_n \bft$, where $\bft \in \mathbb{R}^p$. Now applying Cauchy-Schwarz inequality we shall have
-%%
-%\begin{eqnarray}\label{eqn:AppEqn1}
-%\frac{(\bft^T S_n \bft)^2}{n} & = & \left[ \frac{1}{n} \sum_{i=1}^n \left| (\tilde D^{n} _\bfX (\bfx_i))^2  - (\tilde D_\bfX (\bfx_i))^2 \right|^2  \bft^T SS(\bfx_i; \hat\bfmu_n) \bft \right]^2 \notag\\
-%& \leq & \left[ \frac{1}{n} \sum_{i=1}^n \left| (\tilde D^{n} _\bfX (\bfx_i))^2  - (\tilde D_\bfX (\bfx_i))^2 \right|^2 \right] \left[ \frac{1}{n} \left( \sqrt n.\frac{1}{n} \sum_{i=1}^n  SS(\bfx, \hat\bfmu_n) \right) \right]
-%\end{eqnarray}
-%%
-%with $\hat S_n = \sum_{i=1}^n SS(\bfx_i, \hat\bfmu_n)/ \sqrt n$.
-Now due to the assumption of uniform convergence, given $\epsilon>0$ we can find $N \in \mathbb{N}$ such that
-%
+Now, convergence in probability of $D^n_\bfX(.)$ to $D_\bfX(.)$ (hence $(\tilde D^n_\bfX(.))^2$ to $(\tilde D_\bfX(.))^2$) implies that given $\epsilon, \delta > 0$ there exists $N \in \mathbb{N}$ so that
+
+$$ P \left[ |(\tilde D^{n_1}_\bfX(\bfx))^2 - (\tilde D_\bfX(\bfx))^2| > \epsilon \right] < \delta $$
+for all $n_1 \geq N$.
+Now if $M$ is the largest value the square of a depth function can take, then $|(\tilde D^{n_1}_\bfX(\bfx))^2 - (\tilde D_\bfX(\bfx))^2| < \epsilon$ with probability $1-\delta$, and $< M$ with probability $\delta$.
+Thus we have
+
 \begin{equation}
 \label{equation:lemma1eq}
-| (\tilde D^{n_1}_\bfX(\bfx_i))^2 - (\tilde D_\bfX(\bfx_i))^2 | < \epsilon
+\tilde | D^{n_1}_\bfX(\bfx))^2 - (\tilde D_\bfX(\bfx))^2 | < \min \{ \epsilon, M \}
 \end{equation}
-%
-for all $n_1 \geq N; i = 1,2,...,n_1$. This implies
-%
-\begin{eqnarray}
-\label{eqn:lemma1eq2}
-S_{n_1} &< & \epsilon \sqrt{n_1} \left[ \frac{1}{n_1} \sum_{i=1}^{n_1} SS(\bfx_i; \hat\bfmu_{n_1}) \right]\notag\\
-&=& \epsilon \sqrt{n_1} \left[ \frac{1}{n_1} \sum_{i=1}^{n_1} \left\{ SS(\bfx_i; \hat\bfmu_{n_1}) - SS(\bfx_i; \bfmu) \right\} + \frac{1}{n_1} \sum_{i=1}^{n_1} SS(\bfx_i; \bfmu) \right]
-\end{eqnarray}
+with probability 1. Consequently for all such $n_1$, with probability 1 we shall have
+$$ S_{n_1} \quad < \quad \min \{ \epsilon, M \} . \sqrt n_1 \left[ \frac{1}{n_1} \sum_{i=1}^{n_1} SS(\bfx_i; \hat\bfmu_{n_1}) \right] $$
 
 We now construct a sequence of positive definite matrices $\{A_k (B_k+C_k) : k \in \mathbb N\} $ so that
-%
-$$ A_k = \frac{1}{k}, \quad B_k = \sqrt{N_k} \left[ \frac{1}{N_k} \sum_{i=1}^{N_k} \left\{ SS(\bfx_i; \hat\bfmu_{N_k}) - SS(\bfx_i; \bfmu) \right\} \right]$$
-$$\quad C_k = \sqrt{N_k} \left[ \frac{1}{N_k} \sum_{i=1}^{N_k} SS(\bfx_i; \bfmu) \right] $$
-%
-where $N_k \in \mathbb N$ gives the relation (\ref{equation:lemma1eq}) in place of $N$ when we take $\epsilon = 1/k$.
-Under conditions $ E\|\bfx - \bfmu\|^{-3/2} < \infty $ and $\sqrt n (\hat\bfmu_n - \bfmu) = O_P(1)$, the sample SCM with unknown location parameter $\hat\bfmu_n$ has the same asymptotic distribution as the SCM with known location $\bfmu$ \citep{durre14}, hence $B_k = o_P(1)$, thus $A_k (B_k+C_k) \stackrel{P}{\rightarrow} 0$.
 
-Now (\ref{eqn:lemma1eq2}) implies that for any $\epsilon_1 > 0$, $S_{N_k} > \epsilon_1 \Rightarrow A_k (B_k + C_k) > \epsilon_1$, which means $ P(S_{N_k} > \epsilon_1) < P(A_k (B_k + C_k) > \epsilon_1)$.
-Hence the subsequence $\{S_{N_k}\} \stackrel{P}{\rightarrow} 0$.
-Since the main sequence $\{S_k\}$ is bounded below by 0, this implies $\{S_k\} \stackrel{P}{\rightarrow} 0$.
-Finally, we have that
-%
-\begin{eqnarray}
-\sqrt n \left[
-\frac{1}{n} \sum_{i=1}^n (\tilde D^n_\bfX (\bfx_i))^2 SS(\bfx_i; \hat\bfmu_n) -
-\frac{1}{n} \sum_{i=1}^n (\tilde D_\bfX (\bfx_i))^2 SS(\bfx_i; \bfmu) \right] &\leq & \hspace{1em} \notag\\
-S_n +  \sqrt{n} \left[ \frac{1}{n} \sum_{i=1}^{n} \left\{ SS(\bfx_i; \hat\bfmu_{n}) - SS(\bfx_i; \bfmu) \right\} \right] &&
-\end{eqnarray}
-%
-Since the second summand on the right hand side is $o_P(1)$ due to \cite{durre14} as mentioned before, we have the needed.
+$$ A_k = \frac{M}{k}, \quad B_k = \sqrt N_k \left[ \frac{1}{N_k} \sum_{i=1}^{N_k} \left\{ SS(\bfx_i; \hat\bfmu_{N_k}) - SS(\bfx_i; \bfmu) \right\} \right] $$
+$$ \quad C_k = \sqrt N_k \left[ \frac{1}{N_k} \sum_{i=1}^{N_k} SS(\bfx_i; \bfmu) \right] $$
+where $N_k \in \mathbb N$ gives the relation (\ref{equation:lemma1eq}) in place of $N$ when we take $\epsilon = \delta  =1/k$.
+Under conditions $ E\|\bfx - \bfmu\|^{-3/2} < \infty $ and $\sqrt n (\hat\bfmu_n - \bfmu) = O_P(1)$, the sample sign covariance matrix with unknown location parameter $\hat\bfmu_n$ has the same asymptotic distribution as the same with known location $\bfmu$ \citep{durre14}, hence $B_k \stackrel{P}{\rightarrow} 0$.
+Now by Slutsky's theorem, $A_k (B_k+C_k) \stackrel{P}{\rightarrow} 0$.
+Finally, for any $\epsilon_1 > 0$, $ P(S_{N_k} > \epsilon_1) < P(A_k (B_k + C_k) > \epsilon_1)$, hence the subsequence $\{S_{N_k}\} \stackrel{P}{\rightarrow} 0$.
+Since the main sequence $\{S_k\}$ is bounded below by 0, we have the needed.
 \end{proof}
@@
 The quantity in the statement of the theorem can be broken down as:
-%
 \begin{eqnarray*}
-\sqrt n \left[ vec\left\{ \frac{1}{n} \sum_{i=1}^n (\tilde D^n_\bfX (\bfx_i))^2 SS(\bfx_i; \hat\bfmu_n) \right\} - vec\left\{ \frac{1}{n} \sum_{i=1}^n (\tilde D_\bfX (\bfx_i))^2 SS(\bfx_i; \bfmu) \right\} \right] +\\
-\sqrt n \left[ vec\left\{ \frac{1}{n} \sum_{i=1}^n (\tilde D_\bfX (\bfx_i))^2 SS(\bfx_i; \bfmu) \right\} - E \left[ vec\left\{ (\tilde D_\bfX (\bfx))^2 SS(\bfx; \bfmu) \right\} \right] \right]
+\sqrt n \left[ \text{vec}\left\{ \frac{1}{n} \sum_{i=1}^n (\tilde D^n_\bfX (\bfx_i))^2 SS(\bfx_i; \hat\bfmu_n) \right\} - \text{vec}\left\{ \frac{1}{n} \sum_{i=1}^n (\tilde D_\bfX (\bfx_i))^2 SS(\bfx_i; \bfmu) \right\} \right] +\\
+\sqrt n \left[ \text{vec}\left\{ \frac{1}{n} \sum_{i=1}^n (\tilde D_\bfX (\bfx_i))^2 SS(\bfx_i; \bfmu) \right\} - E \left[ \text{vec}\left\{ (\tilde D_\bfX (\bfx))^2 SS(\bfx; \bfmu) \right\} \right] \right]
 \end{eqnarray*}
-%
+
 The first part goes to 0 in probability by Lemma \ref{Lemma:lemma1}, and applying Slutsky's theorem we get the required convergence.
@@
 \begin{proof}[Proof of Corollary \ref{Corollary:eigendist}]
-In spirit, this corollary is similar to Theorem 13.5.1 in \cite{anderson}, and indeed, \cite{taskinen12} used this theorem to prove Theorem \ref{Theorem:decomp}.
+In spirit, this corollary is similar to Theorem 13.5.1 in \cite{anderson}, and indeed, \cite{taskinen12} used it to prove Theorem \ref{Theorem:decomp}.
 Due to the decomposition (\ref{equation:decompEq}) we have, for the distribution $F_\Lambda$, the following relation between any off-diagonal element of $\hat S^D(F_\Lambda)$ and the corresponding element in the estimate of eigenvectors $\hat\Gamma_D (F_\Lambda)$:
@@
 \begin{equation} \label{equation:app1}
-\sqrt n (\hat\bfgamma_{D,i} - \bfgamma_i) = \sqrt n \Gamma (\hat \bfgamma_{D,i}(F_\Lambda) - \bfe_i ) = \sqrt n \left[ \sum_{k=1; k \neq i}^p \hat \gamma_{D,ik}(F_\Lambda)\bfgamma_k + (\hat \gamma_{D,ii}(F_\Lambda) - 1)\bfgamma_i \right]
+\sqrt n (\hat\bfgamma_{D,i} - \bfgamma_i) = \sqrt n \Gamma (\hat \bfgamma_{D,i}(F_\Lambda) - \bfe_i ) = \sqrt n \left[ \sum_{k=1; k \neq i}^p \hat \gamma_{D,ik}(F_\Lambda)\bfgamma_k + (\hat \gamma_{D,ii}(F_\Lambda) - 1)\bfgamma_i \right] \tag{A1}
 \end{equation}
@@
 
-The exact forms given in the statement of the corollary now follows from the  Form of $V_{D,S}$ in Appendix \ref{section:appA}.
+The exact forms given in the statement of the corollary now follows from the  Form of $V_{D,S}$ in Appendix A.
 
@@
 \end{proof}
-
-\bibliographystyle{plainnat}
-\bibliography{scatterbib}
-
-\end{document}

### 2018-03-20 MS/SJS/Depth-scatter-summary-SJS.tex
first commit in shubhobm

--- 2018-03-20 MS/Depth-scatter-summary.tex
@@
 
-%\DeclareMathOperator*{\vec}{vec}
 \DeclareMathOperator*{\diag}{diag}
@@
 \date{}
-\author{Subhabrata Majumdar}
+\author{Subhabrata Majumdar, Snigdhansu Chatterjee\\
+\textit{University of Minnesota, Twin cities}}
 \maketitle
+\vspace{.5cm}
 
-Abstract:
-Analyzing principal components for multivariate data from its spatial sign covariance matrix (SCM) has been proposed as a computationally simple and robust alternative to normal PCA, but it suffers from poor efficiency properties and is actually inadmissible with respect to the maximum likelihood estimator.
-Here we use data depth-based spatial ranks in place of spatial signs to obtain the orthogonally equivariant Depth Covariance Matrix (DCM) and use its eigenvector estimates for PCA.
+\textit{Running headline}: Robust PCA using data depth
+\vspace{.5cm}
+
+\textit{Keywords}: Data depth; Multivariate ranking; Principal component analysis; Robustness; Robust PCA; Sign covariance matrix
+
+\vspace{.5cm}
+
+\textit{Abstract}:
+We use data depth-based spatial rank vectors to obtain the orthogonally equivariant Depth Covariance Matrix (DCM) and use its eigenvector estimates for principal component analysis (PCA).
 We derive asymptotic properties of the sample DCM and influence functions of its eigenvectors.
-The shapes of these influence functions indicate robustness of estimated principal components, and good efficiency properties compared to the SCM.
+The shapes of these influence functions indicate robustness and better efficiency properties of estimated principal components compared to Sign Covariance Matrix (SCM), the covariance matrix of spatial sign vectors \citep{locantore99}.
 Finite sample simulation studies show that principal components of the sample DCM are robust with respect to deviations from normality, as well as are more efficient than the SCM and its affine equivariant version, Tyler's shape matrix.
@@
 \vspace{.5cm}
-
-Keywords:
-Data depth; Principal components analysis; Robustness; Sign covariance matrix; Multivariate ranking
 
@@
 In case of multivariate normal distribution, the sample covariance matrix provides the most asymptotically efficient estimates of eigenvectors/ principal components, but it is extremely sensitive to outliers as well as relaxations of the normality assumption.
-To address this issue, several robust estimators of the population covariance or correlation matrix have been proposed which can be used for Principal Components Analysis (PCA).
+To address this issue, several robust estimators of the population covariance or correlation matrix have been proposed which can be used for Principal Component Analysis (PCA).
 They can be roughly put into these categories: robust, high breakdown point estimators that are computation-intensive \citep{rousseeuw85, maronna76}; M-estimators that are calculated by simple iterative algorithms but do not necessarily possess high breakdown point \citep{huber77, tyler87}; and symmetrised estomators that are highly efficient and robust to deviations from normality, but sensitive to outliers and computationally demanding \citep{dumbgen98, sirkia07}.
 
-When principal components are of interest, one can also estimate the population eigenvectors by analyzing the spatial sign of a multivariate vector: the vector divided by its magnitude, instead of the original data.
+When principal components are of interest, one can also estimate the population eigenvectors by analyzing the \textit{spatial sign} of a multivariate vector: the vector divided by its magnitude, instead of the original data.
 The covariance matrix of these sign vectors, namely Sign Covariance Matrix (SCM) has the same set of eigenvectors as the covariance matrix of the original population, thus the multivariate sign transformation yields computationally simple and high-breakdown estimates of principal components \citep{locantore99, visuri00}.
@@
 Given a dataset, the depth of a given point in the sample space measures how far inside the data cloud the point exists.
-An overview of statistical depth functions can be found in \citep{zuo00}.
+An overview of statistical depth functions can be found in \cite{zuo00}.
 Depth-based methods have recently been popular for robust nonparametric classification \citep{jornsten04, ghosh05, dutta12, sguera14}.
@@
 In this paper we study the covariance matrix of the multivariate rank vector that is obtained from the data-depth of a point and its spatial sign, paying special attention to its eigenvectors.
-Specifically, we develop a robust version of principal components analysis for elliptically symmetric distributions based on the eigenvectors of this covariance matrix, and compare it with normal PCA and spherical PCA, i.e.
+Specifically, we develop a robust version of principal component analysis for elliptically symmetric distributions based on the eigenvectors of this covariance matrix, and compare it with classical PCA and spherical PCA, i.e.
 PCA based on eigenvectors of the SCM.
 
-The chapter is arranged in the following fashion.
-Section \ref{section:sec2} provides preliminary theoretical concepts required for developments in the subsequent sections.
-Section \ref{section:dcmSection} introduces the Depth Covariance Matrix (DCM) and states some basic results related to this.
-Section \ref{section:sec4} provides asymptotic results regarding the sample DCM, calculated using data depths with respect to the empirical distribution function, as well as its eigenvectors and eigenvalues.
-Section \ref{section:simSection} focuses solely on principal component estimation using the sample DCM.
+The paper is arranged in the following fashion.
+Section 2 provides preliminary theoretical concepts required for developments in the subsequent sections.
+Section 3 introduces the Depth Covariance Matrix (DCM) and states some basic results related to this.
+Section 4 provides asymptotic results regarding the sample DCM, calculated using data depths with respect to the empirical distribution function, as well as its eigenvectors and eigenvalues.
+Section 5 focuses solely on principal component estimation using the sample DCM.
 We obtain influence functions and asymptotic efficiencies for eigenvectors of the DCM.
 We also compare their finite sample efficiencies for several multinormal and multivariate $t$-distributions with those of the SCM, Tyler's scatter matrix and its depth-weighted version through a simulation study.
-Section \ref{section:sec6} presents two applications of the methods we develop on real data.
-Finally, we wrap up our discussion in Section \ref{section:sec7} by giving a summary of our findings and providing some potential future areas of research.
-Appendices \ref{section:appA} and \ref{section:appB} contain all technical details and proofs of the results we derive.
+Section 6 presents two applications of the methods we develop on real data.
+Finally, we wrap up our discussion in Section 7 by giving a summary of our findings and providing some potential future areas of research.
+Proofs of all the results we derive are given in Appendix B.
 
-\section{Preliminaries}\label{section:sec2}
+\section{Preliminaries}
 \subsection{Spatial signs and sign covariance matrix}
-Given a vector $\bfx \in \mathbb{R}^p$, its spatial sign is defined as the vector valued function \citep{MottonenOja95}:
-%
+Given a vector $\bfx \in \mathbb{R}^p$, its spatial sign is defined as the vector valued function \citep{locantore99}:
+
 $$ \bfS(\bfx) = \begin{cases} \bfx\| \bfx \|^{-1} \quad \mbox{if }\bfx \neq \bf0\\
 \bf0 \quad \mbox{if }\bfx = \bf0 \end{cases} $$
-%
+
 When $\bfx$ is a random vector that follows an elliptic distribution $|\Sigma|^{-1/2} f((\bfx - \bfmu)^T \Sigma^{-1} (\bfx - \bfmu))$, with a mean vector $\bfmu$ and covariance matrix $\Sigma$, the sign vectors $\bfS(\bfx - \bfmu)$ reside on the surface of a $p$-dimensional unit ball centered at $\bfmu$.
@@
 An affine equivariant version of the sample SCM is obtained as the solution $\hat \Sigma_T$ of the following equation:
-%
-$$ \hat \Sigma_T(\bfX) = \frac{p}{n} \sum_{i=1}^n \frac{(\bfx - \bfmu)(\bfx - \bfmu)^T}{(\bfx - \bfmu)^T \hat\Sigma_T(\bfX)^{-1} (\bfx - \bfmu)} $$
-%
+
+$$ \hat \Sigma_T(\bfX) = \frac{p}{n} \sum_{i=1}^n \frac{(\bfx_i - \bfmu)(\bfx_i - \bfmu)^T}{(\bfx_i - \bfmu)^T \hat\Sigma_T(\bfX)^{-1} (\bfx_i - \bfmu)} $$
 which turns out to be Tyler's M-estimator of scatter \citep{tyler87}.
@@
 \subsection{Data depth and outlyingness}
-For any multivariate distribution $F = F_\bfX$ belonging to a set of distributions $\mathcal F$, the depth of a point $\bfx \in \mathbb{R}^p$, say $D(\bfx, F_\bfX)$ is any real-valued function that provides a 'center outward ordering' of $\bfx$ with respect to $F$ \citep{zuo00}.
+For any multivariate distribution $F = F_\bfX$, the depth of a point $\bfx \in \mathbb{R}^p$, say $D(\bfx, F_\bfX)$ is any real-valued function that provides a 'center outward ordering' of $\bfx$ with respect to $F$ \citep{zuo00}.
 \cite{liu90} outlines the desirable properties of a statistical depth function:
 
-\vspace{1em}
-\noindent\textbf{(D1)} \textit{Affine invariance}: $D(A\bfx + \bfb, F_{A\bfX+\bfb}) = D(\bfx, F_\bfX)$;
+\noindent
+(P1) Affine invariance: $D(A\bfx + \bfb, F_{A\bfX+\bfb}) = D(\bfx, F_\bfX)$ for any non-singular matrix $A \in \mathbb{R}^{p \times p}, \bfb \in \mathbb{R}^p $;\\
+(P2) Maximality at center: $D(\bftheta, F_\bfX) = \sup_{\bfx\in \mathbb{R}^p} D(\bfx, F_\bfX)$ for $F_\bfX$ having center of symmetry $\bftheta$.
+This point is called the \textit{deepest point} of the distribution;\\
+(P3) Monotonicity with respect to deepest point: $D(\bfx; F_\bfX) \leq D(\bftheta + a(\bfx - \bftheta), F_\bfX)$, $\bftheta$ being deepest point of $F_\bfX$, for any $\bftheta \in \mathbb{R}^p $;\\
+(P4) Vanishing at infinity: $D(\bfx; F_\bfX) \rightarrow \bf0$ as $\|\bfx\| \rightarrow \infty $.
 
-\noindent\textbf{(D2)} \textit{Maximality at center}: $D(\bftheta, F_\bfX) = \sup_{\bfx\in \mathbb{R}^p} D(\bfx, F_\bfX)$ for $F_\bfX$ having center of symmetry $\bftheta$.
-This point is called the \textit{deepest point} of the distribution.;
-
-\noindent\textbf{(D3)} \textit{Monotonicity with respect to deepest point}: $D(\bfx; F_\bfX) \leq D(\bftheta + a(\bfx - \bftheta), F_\bfX)$, $\bftheta$ being deepest point of $F_\bfX$.;
-
-\noindent\textbf{(D4)} \textit{Vanishing at infinity}: $D(\bfx; F_\bfX) \rightarrow 0$ as $\|\bfx\| \rightarrow \infty $.
-\vspace{1em}
-
-In (D2) the types of symmetry considered can be central symmetry, angular symmetry and halfspace symmetry.
+In (P2) the types of symmetry considered can be central symmetry, angular symmetry and halfspace symmetry.
 Also for multimodal probability distributions, i.e.
-distributions with multiple local maxima in their probability density functions, properties (D2) and (D3) are actually restrictive towards the formulation of a reasonable depth function that captures the shape of the data cloud.
-In our derivations that follow, we replace these two by a weaker condition:
-
-\vspace{1em}
-\noindent\textbf{(D2*)} \textit{Existence of a maximal point}: The maximum depth over all distributions $F$ and points $\bfx$ is bounded above, i.e.
-$ \sup_{F_\bfX \in \mathcal F} \sup_{\bfx\in \mathbb{R}^p} D(\bfx, F_\bfX) < \infty $.
-We denote this point by $M_D(F_\bfX)$.
-\vspace{1em}
+distributions with multiple local maxima in their probability density functions, properties (P2) and (P3) are actually restrictive towards the formulation of a reasonable depth function that captures the shape of the data cloud.
+In our derivations that follow, we replace these two by a slightly weaker condition: (P2*) The \textit{existence} of a maximal point, i.e.
+$ \sup_{\bfx\in \mathbb{R}^p} D(\bfx, F_\bfX) < \infty $.
+We denote this point by $M_D(F)$.
 
 A real-valued function measuring the outlyingness of a point with respect to the data cloud can be seen as the opposite of what data depth does.
-Indeed, such functions have been used to define several depth functions, for example simplicial depth, projection depth and $L_p$-depth.
-Keeping with the spirit of the utility of these functions we name them `htped': literally the reverse of `depth', and give a general definition of such functions as a transformation on any depth function:
+Indeed, such functions have been used to define several depth functions, for example simplicial volume depth, projection depth and $L_p$-depth.
+Here we give a general definition of such functions as a transformation on any depth function:
 
 \begin{Definition}
-Given a random variable $\bfX$ following a probability distribution $F$, and a depth function $D(.,.)$, we define Htped of a point $\bfx$ as: $\tilde D(\bfx, F) = h(d_\bfx)$ as any function of the data depth $D(\bfx, F) = d_\bfx$ so that $h(d_\bfx)$ is bounded, monotonically decreasing in $d_\bfx$ and $\sup_\bfx \tilde D(\bfx, F) < \infty$.
+Given a random variable $\bfX$ following a probability distribution $F$, and a depth function $D(.,.)$, we define \textit{Htped of a point} $\bfx$ as: $\tilde D(\bfx, F) = h(d_\bfx)$ as any function of the data depth $D(\bfx, F) = d_\bfx$ so that $h(d_\bfx)$ is bounded, monotonically decreasing in $d_\bfx$ and $\sup_\bfx \tilde D(\bfx, F) < \infty$.
 \end{Definition}
@@
 It is defined as
-%
+
 $$ MhD(\bfX, F) = \frac{1}{1 + d^2_\Sigma (\bfx - \bfmu)} $$
-%
-note here that $d_\Sigma(\bfx,\bfmu)$ can be seen as a valid htped function of $\bfx$ with respect to $F$.
+Note here that $d_\Sigma(\bfx,\bfmu)$ can be seen as a valid htped function of $\bfx$ with respect to $F$.
 
 \item \textbf{Projection depth} (PD) \citep{zuo03} is another depth function based on an outlyingness function. Here that function is
-%
-$$ O(\bfx, F) = \sup_{\| \bfu \| = 1} \frac{| \bfu^T\bfx - m(\bfu^T\bfX)|}{s(\bfu^T\bfX)} $$
-%
+
+$$ O(\bfx, F) = \sup_{\bfu \in \mathbb{R}^p; \| \bfu \| = 1} \frac{| \bfu^T\bfx - m(\bfu^T\bfX)|}{s(\bfu^T\bfX)} $$
 where $m$ and $s$ are some univariate measures location and scale, respectively. Given this the depth at $\bfx$ is defined as $PD(\bfx, F) = 1/(1+O(\bfx, F))$.
@@
 
-Consider a vector-valued random variable $\bfX \in \mathbb{R}^p$ .
+Consider a vector-valued random variable $\bfX \in \mathbb{R}^p$.
 Data depth is as much a property of the random variable as it is of the underlying distribution, so for ease of notation while working with transformed random variables, from now on we shall be using $D_\bfX(\bfx) = D(\bfx, F)$ to denote the depth of a point $\bfx$.
@@
 \cite{serfling2006}).
-The notion of multivariate ranks goes back to \cite{PuriSenBook}, where they take the vector consisting of marginal univariate ranks as multivariate rank vector.
-Subsequent definitions of multivariate ranks were proposed by \cite{MottonenOja95,HallinPaindaveine02} and \cite{Chernozhukov14}.
-Compared to these formulations, our definition of multivariate ranks works for any general depth function, and provides an intuitive extension to any spatial sign-based methodology.
-
-Figure \ref{fig:rankplot} gives an idea of how the multivariate rank vector $\tilde \bfX$ is distributed when $\bfX$ has a bivariate normal distribution.
+Figure \ref{fig:rankplot} gives an idea of how $\tilde \bfX$ is distributed when $\bfX$ has a bivariate normal distribution.
 Compared to the spatial sign, which are distributed on the surface of $p$-dimensional unit ball centered at $\bfmu$, these spatial ranks have the same direction as original data and reside \textit{inside} the $p$-dimensional ball around $\bfmu$ that has radius $M_D(F)$ (which, for the case of halfspace depth, equals 0.5).
 
-\begin{figure}[t]
-	\captionsetup{singlelinecheck=off}
-	\centering
-		\includegraphics[height=6cm]{../Codes/ranks}
-	\caption{(Left) 1000 points randomly drawn from $\mathcal N_2\left((0,0)^T, \left(\protect\begin{smallmatrix} 5 & -4 \\ -4 & 5 \protect\end{smallmatrix}\right)\right) $ and (Right) their multivariate ranks based on halfspace depth}
-	\label{fig:rankplot}
-\end{figure}
+(Insert Figure \ref{fig:rankplot} here)
 
@@
 In this setup, we can represent the transformed random variable as
-%
+
 \begin{eqnarray}
@@
 \end{eqnarray}
-%
 %Because of affine (thus rotational) invariance of a depth function, the depth (htped) value at $\bfz$ does not depend on the direction of $\bfz$, i.e.
@@
 Let the random variable $\bfX \in \mathbb{R}^p$ follow an elliptical distribution with center $\bfmu$ and covariance matrix $\Sigma = \Gamma\Lambda\Gamma^T$, its spectral decomposition.
-Then, given a depth function $D_\bfX(.)$ the covariance matrix of the transformed random variable $\tilde\bfX$ is
+Then, given a depth function $D$ the covariance matrix of the transformed random variable $\tilde\bfX$ is
 \begin{equation} \label{equation:covformEq1}
-Cov(\tilde \bfX) = \Gamma \Lambda_{D,S} \Gamma^T,\quad\mbox{with}\quad \Lambda_{D,S} = \mathbb E_\bfz \left[ (\tilde D_\bfZ(\bfz))^2 \frac{\Lambda^{1/2} \bfz \bfz^T \Lambda^{1/2}}{\bfz^T \Lambda \bfz} \right]
+Cov(\tilde \bfX) = \Gamma \Lambda_{D,S} \Gamma^T,\quad\mbox{with}\quad \Lambda_{D,S} = E \left[ (\tilde D_\bfZ(\bfz))^2 \frac{\Lambda^{1/2} \bfz \bfz^T \Lambda^{1/2}}{\bfz^T \Lambda \bfz} \right]
 \end{equation}
-where $\bfz = (z_1,...,z_p)^T \sim N({\bf 0}, I_p)$, so that $\Lambda_{D,S}$ a diagonal matrix with diagonal entries
-%
-$$ \lambda_{D,S,i} = \mathbb E_\bfZ \left[ \frac{(\tilde D_\bfZ(\bfz))^2 \lambda_i z_i^2}{\sum_{j=1}^p \lambda_j z_j^2} \right] $$
+where $\bfz = (z_1,...,z_p)^T \sim N({\bf 0}, I_p)$ and $\Lambda_{D,S}$ a diagonal matrix with diagonal entries
+
+$$ \lambda_{D,S,i} = E_\bfZ \left[ \frac{(\tilde D_\bfZ(\bfz))^2 \lambda_i z_i^2}{\sum_{j=1}^p \lambda_j z_j^2} \right] $$
 \end{Theorem}
@@
 However, as one can see in the above expression, the diagonal entries of $\Lambda_{D,S}$ do not change if a scale change is done on all entries of $\Lambda$, meaning the $\Lambda_{D,S}$ matrices corresponding to $F$ and $cF$ for some $c \neq 0$ will be same.
-This is the reason for lack of affine equavariance of the DCM.
+This is the reason for lack of affine equivariance of the DCM.
 Following the case of multivariate sign covariance matrices \citep{taskinen12} one can get back the shape components, i.e.
@@
 \item Calculate the next iterate
-%
-$$ \Lambda^{*(k+1)} = \left[ \mathbb E_\bfz \left( \frac{(\tilde D_\bfZ(\bfz))^2 \bfz \bfz^T}{\bfz^T \Lambda^{*(k)} \bfz} \right) \right]^{-1} \Lambda_{D,S} $$
+
+$$ \Lambda^{*(k+1)} = \left[ E\left( \frac{(\tilde D_\bfZ(\bfz))^2 \bfz \bfz^T}{\bfz^T \Lambda^{*(k)} \bfz} \right) \right]^{-1} \Lambda_{D,S} $$
 and standardize its eigenvalues:
-%
-$$ \Lambda^{*(k+1)} = \frac{\Lambda^{*(k+1)}}{\text{det} (\Lambda^{*(k+1)})^{1/p}} $$
-%
+
+$$ \Lambda^{*(k+1)} = \frac{\Lambda^{*(k+1)}}{det(\Lambda^{*(k+1)})^{1/p}} $$
 \item Stop if convergence criterion is satisfied. Otherwise set $k \rightarrow k+1$ ad go to step 2.
@@
 This is because Tyler's scatter matrix $\Sigma_T$ is defined as the implicit solution to the following equation:
+
 \begin{equation} \label{equation:tylerEq}
-\Sigma_T = \mathbb E\left[ \frac{(\bfx - \bfmu) (\bfx - \bfmu)^T}{(\bfx - \bfmu)^T \Sigma_T^{-1} (\bfx - \bfmu)} \right]
+\Sigma_T = E_F \left[ \frac{(\bfX - \bfmu) (\bfX - \bfmu)^T}{(\bfX - \bfmu)^T \Sigma_T^{-1} (\bfX - \bfmu)} \right]
 \end{equation}
@@
 weights $(\tilde D_\bfX(\bfx))^2$ in right side of (\ref{equation:tylerEq})) in the simulations in Section \ref{section:simSection}.
-The simulations show that it has slightly better finite-sample efficiency than $\Sigma_T$ but has same asymptotic performance.
+The simulations show that its estimated eigenvectors have slightly better finite-sample efficiencies than those of $Cov( \tilde \bfX) = S^D(F)$, say.
 We conjecture that its concentration properties can be obtained by taking an approach similar to \cite{soloveychik14}.
 
-\section{Asymptotic results}\label{section:sec4}
+\section{Asymptotic results}
 \subsection{The sample DCM}
@@
 For ease of notation, denote $SS(\bfx; \bfmu) = \bfS(\bfx - \bfmu) \bfS(\bfx - \bfmu)^T$.
-Then, given the depth function and known location center $\bfmu$, one can show that the vectorized form of $\sqrt n$-times the sample DCM: $\sum_{i=1}^n (\tilde D_\bfX(\bfx_i))^2SS(\bfx_i; \bfmu) /\sqrt{n}$  has an asymptotic multivariate normal distribution with mean $\sqrt n.vec(E[( (\tilde D_\bfX (\bfX))^2 SS(\bfx; \bfmu)])$ and a certain covariance matrix by straightforward application of the central limit theorem (CLT).
+Then, given the depth function $D$ and known location center $\bfmu$, one can show that the vectorized form of $\sqrt n$-times the sample DCM: $\sum_{i=1}^n (\tilde D_\bfX(\bfx_i))^2SS(\bfx_i; \bfmu) /\sqrt{n}$  has an asymptotic multivariate normal distribution with mean $\sqrt n.\text{vec}(E[( (\tilde D_\bfX (\bfX))^2 SS(\bfx; \bfmu)])$ and a certain covariance matrix by straightforward application of CLT.
 But in practice the population depth function $D_\bfX(\bfx) = D(\bfx, F)$ is estimated by the depth function based on the empirical distribution function, $F_n$.
 Denote this sample depth by $D^n_\bfX (\bfx) = D(\bfx, F_n)$.
-Here we make the following assumption regarding its relation to $D_\bfX(\bfx)$:
-
-\vspace{1em}
-\noindent\textbf{(D5)} \textit{Uniform convergence}: $\sup_{\bfx \in \mathbb R^p} | D^n_\bfX (\bfx) - D_\bfX (\bfx) | \rightarrow 0$ as $n \rightarrow \infty $.
-\vspace{1em}
-
-The assumption that empirical depths converge uniformly at all points $\bfx$ to their population versions holds under very mild conditions for several well known depth functions: for example projection depth \citep{zuo03} and simplicial depth \citep{Dumbgen92}.
 One also needs to replace the known location parameter $\bfmu$ by some estimator $\hat\bfmu_n$.
@@
 Given $n$ random samples from this distribution, suppose $\hat\bfmu_n$ is an estimator of $\bfmu$ so that $\sqrt n (\hat\bfmu_n - \bfmu) = O_P(1) $.
-Then with the above notations, and given the assumption (D5) we have
-%
+Then with the above notations, and given that for any $\bfx \in \mathbb{R}^p$, $D^n_\bfX (\bfx) \stackrel{P}{\rightarrow} D_\bfX (\bfx)$,
+
 $$ \sqrt n \left[
@@
 
-We are now in a position to state the result for consistency of the sample DCM:
+Given this lemma, we can now state the result for consistency of the sample DCM:
 
@@
 Then, given a depth function $D_\bfX(.)$ and an estimate of center $\hat\bfmu_n$ so that $\sqrt n(\hat \bfmu_n - \bfmu) = O_P(1)$,
-%
-$$ \sqrt n \left[ vec\left\{ \frac{1}{n} \sum_{i=1}^n (\tilde D^n_\bfX (\bfx_i))^2 SS(\bfx_i; \hat\bfmu_n) \right\} - E \left[ vec\left\{ (\tilde D_\bfX (\bfx))^2 SS(\bfx; \bfmu) \right\} \right] \right]
+
+$$ \sqrt n \left[ \text{vec} \left\{ \frac{1}{n} \sum_{i=1}^n (\tilde D^n_\bfX (\bfx_i))^2 SS(\bfx_i; \hat\bfmu_n) \right\} - E \left[ \text{vec} \left\{ (\tilde D_\bfX (\bfx))^2 SS(\bfx; \bfmu) \right\} \right] \right]
 \stackrel{D}{\rightarrow}
 N_{p^2} ({\bf 0}, V_{D,S}(F)) $$
-$$ \text{with } V_{D,S}(F) = Var \left[vec \left\{ (\tilde D_\bfX (\bfx))^2 SS(\bfx; \bfmu) \right\} \right] $$
+$$ \text{with } V_{D,S}(F) = Var \left[ \text{vec}  \left\{ (\tilde D_\bfX (\bfx))^2 SS(\bfx; \bfmu) \right\} \right] $$
 \end{Theorem}
 
-In case $F$ is elliptical, an elaborate form of the covariance matrix $V_{D,S}(F)$ explicitly specifying each of its elements (more directly those of its $\Gamma^T$-rotated version) can be obtained, which is given in Appendix \ref{section:appA}.
+In case $F$ is elliptical, an elaborate form of the covariance matrix $V_{D,S}(F)$ explicitly specifying each of its elements (more directly those of its $\Gamma^T$-rotated version) can be obtained, which is given in Appendix A.
 This form is useful when deriving limiting distributions of eigenvectors and eigenvalues of the sample DCM.
@@
 Write the spectral decomposition of $\hat C$ as $\hat C = \hat P \hat\Lambda \hat P^T$.
-Then the limiting distributions of $\sqrt n vec(\hat P - I_p)$ and $\sqrt n vec(\hat\Lambda - \Lambda)$ are multivariate (singular) normal and
-%
+Then the limiting distributions of $\sqrt n \text{vec}(\hat P - I_p)$ and $\sqrt n \text{vec} (\hat\Lambda - \Lambda)$ are multivariate (singular) normal and
+
 \begin{equation} \label{equation:decompEq}
@@
 
-The first matrix picks only off-diagonal elements of the LHS and the second one only diagonal elements.
-We shall now use this as well as the form of the asymptotic covariance matrix of the vec of sample DCM, i.e.
+The first summand matrix picks only off-diagonal elements of the LHS and the second one only diagonal elements.
+We shall now use this as well as the form of the asymptotic covariance matrix of the vectorized sample DCM, i.e.
 $V_{D,S}(F)$ to obtain limiting variance and covariances of eigenvalues and eigenvectors.
@@
 The random variable $vec(G)$ asymptotically has a $p^2$-variate normal distribution with mean ${\bf 0}_{p^2}$, and the asymptotic variance and covariance of different columns of $G = (\bfg_1,...,\bfg_p)$ are as follows:
-%
+
 \begin{equation} \label{equation:DevEq}
@@
 \end{equation}
-%
 \begin{equation}
@@
 \end{equation}
-%
 where $\Gamma = (\bfgamma_1,...,\bfgamma_p)$.
 The vector consisting of diagonal elements of $L$, say $\bfl = (\l_1,...,\l_p)^T$ asymptotically has a $p$-variate normal distribution with mean ${\bf 0}_p$ and variance-covariance elements:
-%
+
 \begin{eqnarray}
@@
 \end{eqnarray}
-%
 \end{Corollary}
@@
 \cite{taskinen12,ollilia03}).
-Finite sample efficiency of the DCM estimates with respect to infinitesimal contamination and heavy-tailed distributions shall also be demonstrated by a simulation study.
+Finite sample efficiency of the DCM estimates with respect to heavy-tailed distributions shall also be demonstrated by a simulation study.
 
@@
 Given any probability distribution $F$, the influence function of any point $\bfx_0$ in the sample space $\mathcal{X}$ for some functional $T(F)$ on the distribution is defined as
-%
+
 $$ IF(\bfx_0; T,F) = \lim_{\epsilon \rightarrow 0} \frac{1}{\epsilon} (T(F_\epsilon) - T(F)) $$
-%
 where $F_\epsilon$ is $F$ with an additional mass of $\epsilon$ at $\bfx_0$, i.e.
@@
 It now follows that for the DCM,
-%
+
 $$ IF(\bfx_0; Cov(\tilde \bfX), F) = (\tilde D_\bfX(\bfx_0))^2 SS(\bfx_0; \bfmu) - Cov(\tilde \bfX) $$
@@
 Following \cite{croux00}, we now get the influence function of the $i^\text{th}$ column of $\hat\Gamma_D = (\hat\bfgamma_{D,1},...,\hat\bfgamma_{D,p}); i = 1,...,p$:
-%
 \begin{eqnarray}
@@
 \end{eqnarray}
-%
 where $\Gamma^T \Lambda^{-1/2} (\bfx_0 - \bfmu) = \bfz_0 = (z_{01},...,z_{0p})^T$.
 Clearly this influence function will be bounded, which indicates good robustness properties of principal components.
-Moreover, since the htped function takes small values for points close to the center of the distribution, it does not suffer from the inlier effect that is typical of the SCM and Tyler's shape matrix.
+Moreover, since the htped function takes small values for points close to the center of the distribution, it does not suffer from the `inlier effect', i.e.
+points close to symmetry center and the center itself having high influence, that is typical of the SCM and Tyler's shape matrix.
 The influence function for the $i^\text{th}$ eigenvector estimates of these two matrices (say $\hat\bfgamma_{S,i}$ and $\hat\bfgamma_{T,i}$, respectively) are as follows:
-%
 \begin{eqnarray*}
@@
 \end{eqnarray*}
-%
 for $i = 1,2$.
 In Figure \ref{fig:IFnorm} we consider first eigenvectors of different scatter estimates for the $\mathcal{N}_2((0,0)^T, \diag(2,1))$ and plot norms of these influence functions for different values of $\bfx_0$.
-The plots for SCM and Tyler's shape matrix demonstrate the 'inlier effect', i.e.
-points close to symmetry center and the center itself having high influence.
+The plots for SCM and Tyler's shape matrix demonstrate the inlier effect.
 The influence function for the sample covariance matrix is obtained by replacing $(p+2)$ by $\| \bfz_0 \|^2$ in the expression of $IF(\bfx_0; \hat \bfgamma_{T,i}, F)$ above, hence is unbounded and the corresponding eigenvector estimators are not robust.
-In comparison, all three DCMs considered here have a bounded influence function as well as small values of the influence function at 'deep' points.
+In comparison, all three DCMs considered here have a bounded influence function as well as small values of the influence function at `deep' points.
 
-\begin{figure}[]
-	\centering
-		\includegraphics[width=12cm]{../Codes/IFnorm.png}
-	\caption{Plot of the norm of influence function for first eigenvector of (a) sample covariance matrix, (b) SCM, (c) Tyler's scatter matrix and DCMs for (d) Halfspace depth, (e) Mahalanobis depth, (f) Projection depth for a bivariate normal distribution with $\bfmu = {\bf 0}, \Sigma = \diag(2,1)$}
-	\label{fig:IFnorm}
-\end{figure}
+(Insert Figure \ref{fig:IFnorm} here)
 
@@
 Then the asymptotic variance of the eigenvectors are (see Theorem 13.5.1 in \cite{anderson})
-%
+
 \begin{equation} \label{equation:covevEq}
@@
 \end{equation}
-%
-The asymptotic relative efficiencies of eigenvectors from the sample DCM with respect to the sample covariance matrix can now be derived using (\ref{equation:covevEq}) above and (\ref{equation:DevEq}) from Corollary \ref{Corollary:eigendist}:
-%
+the asymptotic relative efficiencies of eigenvectors from the sample DCM with respect to the sample covariance matrix can now be derived using (\ref{equation:covevEq}) above and (\ref{equation:DevEq}) from Corollary \ref{Corollary:eigendist}:
+
 \begin{eqnarray*}
@@
 For 2 dimensions, this expression can be somewhat simplified. Suppose the two eigenvalues are $\lambda$ and $\rho\lambda$. In that case the eigenvalues of the DCM are
-%
+
 $$ \lambda_{D,S,1} = E \left( \frac{(\tilde D_\bfZ(\bfz))^2 z_1^2}{z_1^2 + \rho z_2^2} \right), \quad
@@
 and by simple algebra we get
-%
+
 $$ ARE(\hat\bfgamma^D_1, \hat\bfgamma_1; F) = ARE(\hat\bfgamma^D_2, \hat\bfgamma_2; F) = \frac{1}{(1-\rho)^2} \frac{\left[ E \left( \frac{(\tilde D_\bfZ(\bfz))^2 (z_1^2 - \rho z_2^2)}{(z_1^2 + \rho z_2^2)} \right) \right]^2 }{E \left( \frac{(\tilde D_\bfZ(\bfz))^4 z_1^2z_2^2}{(z_1^2 + \rho z_2^2)^2}\right)} $$
@@
 
-\begin{table}
-\begin{footnotesize}
-    \begin{tabular}{c|cc|ccc|ccc}
-     \hline
-                       & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
-    Bivariate $t_5$    & 1.46 & 1.50  & 1.97   & 1.54   & 1.99  & 2.09    & 1.57    & 2.11   \\
-    Bivariate $t_6$    & 0.97 & 1.00  & 1.37   & 1.12   & 1.40  & 1.45    & 1.19    & 1.49   \\
-    Bivariate $t_{10}$ & 0.65 & 0.67  & 0.96   & 0.88   & 1.02  & 1.02    & 0.94    & 1.10   \\
-    Bivariate $t_{15}$ & 0.57 & 0.59  & 0.87   & 0.82   & 0.94  & 0.92    & 0.87    & 1.00   \\
-    Bivariate $t_{25}$ & 0.54 & 0.55  & 0.79   & 0.75   & 0.88  & 0.85    & 0.81    & 0.95   \\
-    BVN   & 0.49 & 0.50  & 0.73   & 0.71   & 0.82  & 0.77    & 0.75    & 0.88   \\ \hline
-    \end{tabular}
-\end{footnotesize}
-\caption{Asymptotic efficiencies relative to sample covariance matrix for $p=2$}
-\label{table:AREtable}
-\end{table}
+(Insert Table \ref{table:AREtable} here)
 
-We now obtain finite sample efficiencies of the three DCMs as well as their depth-weighted affine equivariant counterparts by a simulation study, and compare them with the same from the SCM and Tyler's scatter matrix.
+Now we obtain finite sample efficiencies of the three DCMs as well as their depth-weighted affine equivariant counterparts by a simulation study, and compare them with the same from the SCM and Tyler's scatter matrix.
 We consider the same 6 elliptical distributions considered in ARE calculations above, and from every distribution draw 10000 samples each for sample sizes $n = 20, 50, 100, 300, 500$.
@@
 We use the concept of principal angles \citep{miao92} to find out error estimates for the first eigenvector of a scatter matrix. In our case, the first eigenvector will be
-%
 $$ \bfgamma_1 = (1,\overbrace{0,...,0}^{p-1})^T $$
-%
 For an estimate of the eigenvector, say $\hat\bfgamma_1$, error in prediction is measured by the smallest angle between the two lines, i.e.
@@
 We repeat this 10000 times and calculate the \textbf{Mean Squared Prediction Angle}:
-%
 $$ MSPA(\hat \bfgamma_1) = \frac{1}{10000} \sum_{m=1}^{10000} \left( \cos^{-1} \left|\bfgamma_1^T \hat\bfgamma^{(m)}_1 \right| \right)^2 $$
-%
+
 Finally, the finite sample efficiency of some eigenvector estimate $\hat\bfgamma^E_1$ relative to that obtained from the sample covariance matrix, say $\hat\bfgamma^{Cov}_1$ is obtained as:
@@
 Tables \ref{table:FSEtable2}, \ref{table:FSEtable3} and \ref{table:FSEtable4} give FSE values for $p=2,3,4$, respectively.
-In general, all the efficiencies increase as the dimension $p$ goes up.
-DCM-based estimators (columns 3-5 in each table) outperform SCM and Tyler's scatter matrix, and among the 3 depths considered, projection depth seems to give the best results.
+In general, all efficiencies increase as the dimension $p$ goes up.
+DCM-based estimators (columns 3-5 in each table) outperform SCM and Tyler's scatter matrix, and among the 3 depths considered, projection depth seems to give best results.
 Its finite sample performances are better than Tyler's and Huber's M-estimators of scatter as well as their symmetrized counterparts (see Table 4 in \cite{sirkia07}, and quite close to the affine equivariant spatial sign covariance matrix (see Table 2 in \cite{ollilia03}) For $p=2$, $n=300, 500$ the first 5 columns of Table \ref{table:FSEtable2} approximate the asymptotic efficiencies in Table \ref{table:AREtable} well, except for the multivariate $t$-distribution with df = 5.
@@
 
-\begin{table}
-\begin{footnotesize}
-    \begin{tabular}{c|cc|ccc|ccc}
-    \hline
-    $F$ = Bivariate $t_5$    & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
-    $n$=20                   & 0.80 & 0.83  & 0.95   & 0.95   & 0.89  & 1.00    & 0.96    & 0.89   \\
-    $n$=50                   & 0.86 & 0.90  & 1.25   & 1.10   & 1.21  & 1.32    & 1.13    & 1.25   \\
-    $n$=100                  & 1.02 & 1.04  & 1.58   & 1.20   & 1.54  & 1.67    & 1.24    & 1.63   \\
-    $n$=300                  & 1.24 & 1.28  & 1.81   & 1.36   & 1.82  & 1.93    & 1.44    & 1.95   \\
-    $n$=500                  & 1.25 & 1.29  & 1.80   & 1.33   & 1.84  & 1.91    & 1.39    & 1.97   \\ \hline
-    $F$ = Bivariate $t_6$    & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
-    $n$=20                   & 0.77 & 0.79  & 0.92   & 0.92   & 0.86  & 0.96    & 0.92    & 0.85   \\
-    $n$=50                   & 0.76 & 0.78  & 1.11   & 1.00   & 1.08  & 1.17    & 1.03    & 1.13   \\
-    $n$=100                  & 0.78 & 0.79  & 1.27   & 1.06   & 1.33  & 1.35    & 1.11    & 1.41   \\
-    $n$=300                  & 0.88 & 0.91  & 1.29   & 1.09   & 1.35  & 1.38    & 1.15    & 1.45   \\
-    $n$=500                  & 0.93 & 0.96  & 1.37   & 1.13   & 1.40  & 1.44    & 1.19    & 1.48   \\ \hline
-    $F$ = Bivariate $t_{10}$ & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
-    $n$=20                   & 0.70 & 0.72  & 0.83   & 0.84   & 0.77  & 0.89    & 0.87    & 0.79   \\
-    $n$=50                   & 0.58 & 0.60  & 0.90   & 0.84   & 0.86  & 0.95    & 0.88    & 0.91   \\
-    $n$=100                  & 0.57 & 0.59  & 0.92   & 0.87   & 0.97  & 0.98    & 0.90    & 1.03   \\
-    $n$=300                  & 0.62 & 0.64  & 0.93   & 0.85   & 0.99  & 0.99    & 0.91    & 1.06   \\
-    $n$=500                  & 0.62 & 0.65  & 0.93   & 0.86   & 1.00  & 1.00    & 0.92    & 1.08   \\ \hline
-    $F$ = Bivariate $t_{15}$ & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
-    $n$=20                   & 0.63 & 0.66  & 0.76   & 0.78   & 0.72  & 0.81    & 0.81    & 0.73   \\
-    $n$=50                   & 0.52 & 0.52  & 0.79   & 0.75   & 0.80  & 0.84    & 0.79    & 0.85   \\
-    $n$=100                  & 0.51 & 0.52  & 0.83   & 0.77   & 0.88  & 0.88    & 0.81    & 0.94   \\
-    $n$=300                  & 0.55 & 0.56  & 0.84   & 0.79   & 0.91  & 0.89    & 0.84    & 0.98   \\
-    $n$=500                  & 0.56 & 0.59  & 0.85   & 0.80   & 0.93  & 0.91    & 0.86    & 0.99   \\ \hline
-    $F$ = Bivariate $t_{25}$ & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
-    $n$=20                   & 0.63 & 0.65  & 0.77   & 0.79   & 0.74  & 0.80    & 0.81    & 0.74   \\
-    $n$=50                   & 0.49 & 0.50  & 0.73   & 0.71   & 0.76  & 0.78    & 0.75    & 0.80   \\
-    $n$=100                  & 0.45 & 0.46  & 0.73   & 0.69   & 0.81  & 0.78    & 0.73    & 0.87   \\
-    $n$=300                  & 0.51 & 0.52  & 0.78   & 0.75   & 0.87  & 0.83    & 0.79    & 0.94   \\
-    $n$=500                  & 0.53 & 0.55  & 0.79   & 0.75   & 0.87  & 0.84    & 0.80    & 0.94   \\ \hline
-    $F$ = BVN                & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
-    $n$=20                   & 0.56 & 0.60  & 0.69   & 0.71   & 0.67  & 0.73    & 0.74    & 0.68   \\
-    $n$=50                   & 0.42 & 0.43  & 0.66   & 0.66   & 0.70  & 0.71    & 0.69    & 0.75   \\
-    $n$=100                  & 0.42 & 0.43  & 0.69   & 0.66   & 0.77  & 0.74    & 0.71    & 0.83   \\
-    $n$=300                  & 0.47 & 0.49  & 0.71   & 0.69   & 0.82  & 0.76    & 0.73    & 0.88   \\
-    $n$=500                  & 0.48 & 0.50  & 0.73   & 0.71   & 0.83  & 0.78    & 0.76    & 0.89   \\ \hline
-    \end{tabular}
-\end{footnotesize}
-\caption{Finite sample efficiencies of several scatter matrices: $p=2$}
-\label{table:FSEtable2}
-\end{table}
+(Insert Tables \ref{table:FSEtable2}, \ref{table:FSEtable3}, \ref{table:FSEtable4} here)
 
-\begin{table}
-\begin{footnotesize}
-   \begin{tabular}{c|cc|ccc|ccc}
-    \hline
-    3-variate $t_5$    & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
-    $n$=20             & 0.96 & 0.97  & 1.06   & 1.03   & 0.99  & 1.07    & 1.06    & 0.97   \\
-    $n$=50             & 1.07 & 1.08  & 1.28   & 1.20   & 1.18  & 1.33    & 1.23    & 1.20   \\
-    $n$=100            & 1.12 & 1.15  & 1.49   & 1.31   & 1.40  & 1.57    & 1.38    & 1.48   \\
-    $n$=300            & 1.49 & 1.54  & 2.09   & 1.82   & 2.07  & 2.19    & 1.93    & 2.18   \\
-    $n$=500            & 1.60 & 1.66  & 2.18   & 1.87   & 2.21  & 2.27    & 1.95    & 2.30   \\ \hline
-    3-variate $t_6$    & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
-    $n$=20             & 0.90 & 0.92  & 1.00   & 0.99   & 0.95  & 1.02    & 1.01    & 0.94   \\
-    $n$=50             & 0.95 & 0.96  & 1.16   & 1.09   & 1.09  & 1.21    & 1.14    & 1.11   \\
-    $n$=100            & 0.98 & 0.99  & 1.32   & 1.22   & 1.25  & 1.38    & 1.27    & 1.29   \\
-    $n$=300            & 1.10 & 1.14  & 1.57   & 1.40   & 1.58  & 1.62    & 1.47    & 1.64   \\
-    $n$=500            & 1.17 & 1.20  & 1.57   & 1.43   & 1.60  & 1.63    & 1.51    & 1.67   \\ \hline
-    3-variate $t_{10}$ & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
-    $n$=20             & 0.87 & 0.88  & 0.95   & 0.94   & 0.90  & 0.97    & 0.98    & 0.89   \\
-    $n$=50             & 0.77 & 0.79  & 0.96   & 0.92   & 0.94  & 0.99    & 0.96    & 0.95   \\
-    $n$=100            & 0.75 & 0.76  & 1.02   & 0.95   & 1.01  & 1.06    & 1.00    & 1.05   \\
-    $n$=300            & 0.73 & 0.75  & 1.03   & 0.98   & 1.10  & 1.08    & 1.03    & 1.15   \\
-    $n$=500            & 0.73 & 0.76  & 1.02   & 0.98   & 1.09  & 1.06    & 1.02    & 1.14   \\ \hline
-    3-variate $t_{15}$ & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
-    $n$=20             & 0.84 & 0.86  & 0.92   & 0.92   & 0.89  & 0.94    & 0.94    & 0.87   \\
-    $n$=50             & 0.75 & 0.76  & 0.92   & 0.90   & 0.90  & 0.96    & 0.94    & 0.93   \\
-    $n$=100            & 0.66 & 0.67  & 0.91   & 0.87   & 0.95  & 0.96    & 0.92    & 1.00   \\
-    $n$=300            & 0.61 & 0.64  & 0.90   & 0.87   & 1.00  & 0.93    & 0.91    & 1.04   \\
-    $n$=500            & 0.65 & 0.67  & 0.89   & 0.87   & 0.99  & 0.93    & 0.91    & 1.03   \\ \hline
-    3-variate $t_{25}$ & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
-    $n$=20             & 0.78 & 0.79  & 0.87   & 0.89   & 0.87  & 0.89    & 0.92    & 0.86   \\
-    $n$=50             & 0.70 & 0.71  & 0.88   & 0.86   & 0.88  & 0.91    & 0.90    & 0.90   \\
-    $n$=100            & 0.61 & 0.63  & 0.86   & 0.83   & 0.89  & 0.90    & 0.88    & 0.94   \\
-    $n$=300            & 0.58 & 0.59  & 0.83   & 0.80   & 0.92  & 0.87    & 0.85    & 0.98   \\
-    $n$=500            & 0.62 & 0.64  & 0.83   & 0.82   & 0.94  & 0.88    & 0.87    & 0.99   \\ \hline
-    3-variate Normal   & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
-    $n$=20             & 0.76 & 0.78  & 0.85   & 0.87   & 0.84  & 0.87    & 0.90    & 0.83   \\
-    $n$=50             & 0.66 & 0.67  & 0.82   & 0.81   & 0.84  & 0.86    & 0.86    & 0.86   \\
-    $n$=100            & 0.56 & 0.58  & 0.77   & 0.75   & 0.83  & 0.82    & 0.79    & 0.87   \\
-    $n$=300            & 0.53 & 0.55  & 0.75   & 0.74   & 0.85  & 0.79    & 0.78    & 0.90   \\
-    $n$=500            & 0.56 & 0.58  & 0.76   & 0.76   & 0.87  & 0.80    & 0.80    & 0.92   \\ \hline
-    \end{tabular}
-\end{footnotesize}
-\caption{Finite sample efficiencies of several scatter matrices: $p=3$}
-\label{table:FSEtable3}
-\end{table}
-
-\begin{table}
-\begin{footnotesize}
-    \begin{tabular}{c|cc|ccc|ccc}
-    \hline
-    4-variate $t_5$    & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
-    $n$=20             & 1.04 & 1.02  & 1.10   & 1.07   & 1.02  & 1.09    & 1.07    & 0.98   \\
-    $n$=50             & 1.08 & 1.08  & 1.16   & 1.16   & 1.13  & 1.19    & 1.19    & 1.13   \\
-    $n$=100            & 1.31 & 1.31  & 1.42   & 1.38   & 1.36  & 1.46    & 1.44    & 1.36   \\
-    $n$=300            & 1.46 & 1.54  & 1.81   & 1.76   & 1.95  & 1.88    & 1.88    & 1.95   \\
-    $n$=500            & 1.92 & 1.93  & 2.23   & 2.03   & 2.31  & 2.35    & 2.19    & 2.39   \\ \hline
-    4-variate $t_6$    & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
-    $n$=20             & 1.00 & 1.05  & 1.03   & 1.05   & 1.00  & 1.04    & 1.04    & 0.95   \\
-    $n$=50             & 1.03 & 1.01  & 1.13   & 1.12   & 1.11  & 1.19    & 1.17    & 1.10   \\
-    $n$=100            & 1.08 & 1.12  & 1.25   & 1.23   & 1.27  & 1.24    & 1.25    & 1.22   \\
-    $n$=300            & 1.34 & 1.36  & 1.64   & 1.52   & 1.60  & 1.67    & 1.61    & 1.68   \\
-    $n$=500            & 1.26 & 1.34  & 1.55   & 1.49   & 1.60  & 1.65    & 1.61    & 1.69   \\ \hline
-    4-variate $t_{10}$ & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
-    $n$=20             & 0.90 & 0.89  & 0.95   & 0.98   & 0.98  & 0.96    & 1.01    & 0.95   \\
-    $n$=50             & 0.90 & 0.91  & 1.01   & 0.98   & 0.98  & 1.03    & 1.04    & 0.99   \\
-    $n$=100            & 0.87 & 0.87  & 0.93   & 0.95   & 1.01  & 0.99    & 1.01    & 1.05   \\
-    $n$=300            & 0.87 & 0.87  & 1.09   & 1.09   & 1.17  & 1.14    & 1.16    & 1.23   \\
-    $n$=500            & 0.88 & 0.92  & 1.10   & 1.10   & 1.23  & 1.19    & 1.22    & 1.29   \\ \hline
-    4-variate $t_{15}$ & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
-    $n$=20             & 0.92 & 0.90  & 0.94   & 0.94   & 0.96  & 0.95    & 0.97    & 0.89   \\
-    $n$=50             & 0.82 & 0.83  & 0.88   & 0.91   & 0.93  & 0.88    & 0.93    & 0.93   \\
-    $n$=100            & 0.84 & 0.87  & 0.92   & 0.95   & 1.00  & 0.93    & 0.96    & 1.00   \\
-    $n$=300            & 0.73 & 0.75  & 0.96   & 0.99   & 1.10  & 1.00    & 1.06    & 1.12   \\
-    $n$=500            & 0.73 & 0.76  & 0.95   & 0.96   & 1.06  & 0.94    & 0.97    & 1.06   \\ \hline
-    4-variate $t_{25}$ & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
-    $n$=20             & 0.89 & 0.92  & 0.92   & 0.92   & 0.90  & 0.96    & 0.95    & 0.89   \\
-    $n$=50             & 0.82 & 0.84  & 0.89   & 0.90   & 0.91  & 0.93    & 0.96    & 0.92   \\
-    $n$=100            & 0.77 & 0.76  & 0.90   & 0.90   & 0.96  & 0.94    & 0.98    & 1.04   \\
-    $n$=300            & 0.73 & 0.77  & 0.93   & 0.91   & 0.98  & 1.00    & 0.98    & 1.03   \\
-    $n$=500            & 0.67 & 0.71  & 0.83   & 0.83   & 0.96  & 0.88    & 0.90    & 1.00   \\ \hline
-    4-variate Normal   & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
-    $n$=20             & 0.82 & 0.84  & 0.87   & 0.90   & 0.91  & 0.89    & 0.93    & 0.89   \\
-    $n$=50             & 0.80 & 0.81  & 0.87   & 0.88   & 0.88  & 0.88    & 0.92    & 0.88   \\
-    $n$=100            & 0.68 & 0.71  & 0.80   & 0.85   & 0.91  & 0.82    & 0.86    & 0.92   \\
-    $n$=300            & 0.61 & 0.63  & 0.82   & 0.85   & 0.93  & 0.86    & 0.91    & 0.96   \\
-    $n$=500            & 0.60 & 0.64  & 0.77   & 0.80   & 0.90  & 0.82    & 0.86    & 0.96   \\ \hline
-    \end{tabular}
-\end{footnotesize}
-\caption{Finite sample efficiencies of several scatter matrices: $p=4$}
-\label{table:FSEtable4}
-\end{table}
-
-\section{Examples in real data analysis}\label{section:sec6}
+\section{Examples in real data analysis}
 %\subsection{Communities and crime data}
@@
 %	\centering
-%		\includegraphics[height=5cm]{../Codes/crime_screeplots.png}
+%		\includegraphics[height=5cm]{crime_screeplots.png}
 %	\caption{(Left) Screeplots for two types of PCA on communities data}
@@
 %	\centering
-%		\includegraphics[height=7cm]{../Codes/crime_Rsq_plot.png}
+%		\includegraphics[height=7cm]{crime_Rsq_plot.png}
 %	\caption{(Left) Change of $R^2$ values for normal and depth-based principal components regression models on communities data}
@@
 Similar to the original analysis, we set aside variable 9 and scale the other variables by dividing with their respective median absolute deviations (MAD).
-This is done because all the variables had much larger standard deviations compared to their MADs, and variable 9 had MAD = 0.
+This is done because all variables had much larger standard deviations compared to their MADs, and variable 9 had MAD = 0.
 
@@
 PCA based on the SCM (SPCA), PCs obtained by the ROBPCA algorithm \citep{hubert05}, and the Minimum Covariance Determinant (MCD) estimator \citep{Rousseeuw84leastmedian} (MPCA).
-Table \ref{table:bus_table1} gives the proportions of variability that are left unexplained after the top $q$ $(= 1,...,6)$ components are taken into account in each of the 5 methods.
+Table \ref{table:bus_table1} gives proportions of total variability that are left unexplained after the top $q$ $(= 1,...,6)$ components are taken into account in each of the 5 methods.
 The first PC in classical PCA seems to explain a much higher proportion of variability in original data than robust methods.
@@
 
+(Insert Tables \ref{table:bus_table1}, \ref{table:bus_table2} here)
+
 Table \ref{table:bus_table2} demonstrates why robust methods actually give a better representation of the underlying data structure than classical PCA here.
 Each of its column lists different quantiles of the squared orthogonal distance for a sample point from the hyperplane formed by top 3 PCs estimated by the corresponding method.
-For PCA based on projection-DCM, the estimated principal component subspaces are closer to the data than CPCA for more than 90\% of samples, and the distance only becomes larger for higher quantiles.
+For PCA based on projection-DCM, the estimated principal component subspaces are closer to the data than CPCA for more than 90\% of samples, and the distance only becomes larger for very high quantiles.
 This means that for CPCA, estimated basis vectors of the hyperspace get pulled by extreme outlying points, while the influence of these outliers is very low for DPCA.
@@
 This percentage is only 50\% for MPCA, which suggests that the corresponding 3-dimensional subspace estimated by MCD is possibly not an accurate representation of the truth.
-
-\begin{table}[t]
-\centering
-    \begin{tabular}{c|ccccc}
-    \hline
-    \begin{large} $q$ \end{large} & \multicolumn{5}{c}{Method of PCA}         \\ \cline{2-6}
-    ~                   & CPCA     & SPCA & ROBPCA & MPCA & DPCA \\\hline 
-    1                   & 0.188         & 0.549     & 0.410  & 0.514     & 0.662     \\
-    2                   & 0.084         & 0.272     & 0.214  & 0.337     & 0.359     \\
-    3                   & 0.044         & 0.182     & 0.121  & 0.227     & 0.237     \\
-    4                   & 0.026         & 0.135     & 0.083  & 0.154     & 0.173     \\
-    5                   & 0.018         & 0.099     & 0.054  & 0.098     & 0.115     \\
-    6                   & 0.012         & 0.069     & 0.036  & 0.070     & 0.084     \\ \hline
-    \end{tabular}
-    \caption{Unexplained proportions of variability by PCA models with $q$ components for bus data}
-    \label{table:bus_table1}
-\end{table}
-
-\begin{table}[t]
-\centering
-    \begin{tabular}{c|ccccc}
-    \hline
-    Quantile & \multicolumn{5}{c}{Method of PCA}         \\ \cline{2-6}
-    ~                   & CPCA     & SPCA & ROBPCA & MPCA & DPCA \\\hline 
-    10\%      & 1.9       & 1.2       & 1.2    & 1.0       & 1.2       \\
-    20\%      & 2.3       & 1.6       & 1.6    & 1.3       & 1.6       \\
-    30\%      & 2.8       & 1.8       & 1.8    & 1.7       & 1.9       \\
-    40\%      & 3.2       & 2.2       & 2.1    & 2.1       & 2.3       \\
-    50\%      & 3.7       & 2.6       & 2.5    & 3.1       & 2.6       \\
-    60\%      & 4.4       & 3.1       & 3.0    & 5.9       & 3.2       \\
-    70\%      & 5.4       & 3.8       & 3.9    & 25.1      & 3.9       \\
-    80\%      & 6.5       & 5.2       & 4.8    & 86.1      & 4.8       \\
-    90\%      & 8.2       & 9.0       & 10.9   & 298.2     & 6.9      \\
-    Max       & 24        & 1037      & 1055   & 1037      & 980      \\\hline
-    \end{tabular}
-    \caption{Quantiles to squared distance from 3-principal component hyperplanes for bus data}
-    \label{table:bus_table2}
-\end{table}
 
@@
 
-In both methods, the first two PCs explains a large amount (98\% for CPCA, 89\% for DPCA) of underlying variability.
+In both methods, the first two PCs explain a large amount (98\% for CPCA, 89\% for DPCA) of underlying variability.
 But in DPCA, these PCs are more effective in detecting outliers, which we demonstrate in Figure \ref{fig:distplot}.
 For any method of PCA with $k$ components on a dataset of $n$ observations and $p$ variables, the \textbf{score distance} (SD) and \textbf{orthogonal distance} (OD) for $i^\text{th}$ observation ($i=1,2,...,n$) are defined as:
+
 $$ SD_i = \sqrt{ \sum_{j=1}^k \frac{s^2_{ij}}{\lambda_j}}; \quad OD_i = \| \bfx_i - P\bfs_i^T \| $$
@@
 We only consider the first 2 PCs here, so $k$ is set to 2.
-From a practical standpoint, $SD_i$ can be interpreted as a weighted norm of the projection of the $i^\text{th}$ point on the hyperplane formed by first $k$ principal components, and $OD_i$ the orthogonal distance of point $i$ from that hyperplane.
+From a practical standpoint, $SD_i$ can be interpreted as magnitude of the standardized projection of $i^\text{th}$ point on the hyperplane formed by first $k$ principal components, and $OD_i$ the orthogonal distance of point $i$ from that hyperplane.
 For outlier detection, following \cite{hubert05} we set the upper cutoff values for score distances at $\sqrt{\chi^2_{2,.975}}$ and orthogonal distances at $[\text{median}(OD^{2/3}) + \text{MAD}(OD^{2/3})\Phi^{-1}(0.975)]^{3/2}$, where $\Phi(.)$ is the standard normal cumulative distribution function.
@@
 
-\begin{figure}[t]
-	\centering
-		\includegraphics[height=6cm]{../Codes/octane_screeplot.pdf}
-	\caption{Explained variance proportions for two types of PCA on octane data}
-	\label{fig:screeplot}
-\end{figure}
-\begin{figure}[t]
-	\centering
-		\includegraphics[height=6.5cm]{../Codes/octane_distanceplot.pdf}
-	\caption{Distance plots for two types of PCA on octane data}
-	\label{fig:distplot}
-\end{figure}
+(Insert Figures \ref{fig:screeplot}, \ref{fig:distplot} here)
 
-\section{Conclusion}\label{section:sec7}
-
+\section{Conclusion}
 In the above sections we introduce a covariance matrix based on depth-based multivariate ranks that keeps the eigenvectors of the actual population unchanged for elliptical distributions.
@@
 
-$$ \Sigma_{Dw} = E \left[ \frac{(\tilde D_\bfX(\bfx))^2 (\bfx - \bfmu) (\bfx - \bfmu)^T}{(\bfx - \bfmu)^T \Sigma_{Dw}^{-1} (\bfx - \bfmu)} \right] $$
+$$ \Sigma_{Dw} = E_F \left[ \frac{(\tilde D_\bfX(\bfX))^2 (\bfX - \bfmu) (\bfX - \bfmu)^T}{(\bfX - \bfmu)^T \Sigma_{Dw}^{-1} (\bfX - \bfmu)} \right] $$
 as their eigenvector estimates seem to have better efficiency than those obtained from the corresponding DCMs.
@@
 
-\appendix
-\section*{Appendix}
-\numberwithin{equation}{section}
-\section{\textbf{Form of $V_{D,S}(F)$}}\label{section:appA}
+\section*{Acknowledgement}
+This research is supported by the U.S. National Science Foundation grant IIS--1029711.
 
-First observe that for $F$ having covariance matrix $\Sigma = \Gamma\Lambda\Gamma^T$,
-%
-$$ V_{D,S}(F)  = (\Gamma \otimes \Gamma) V_{D,S}(F_\Lambda) (\Gamma \otimes \Gamma)^T$$
-%
-where $F_\Lambda$ has the same elliptic distribution as $F$, but with covariance matrix $\Lambda$. Now,
-%
-\begin{eqnarray*}
-V_{D,S} (F_\Lambda) &=& E \left[ vec \left\{ \frac{(\tilde D_\bfZ (\bfz))^2 \Lambda^{1/2} \bfz\bfz^T \Lambda^{1/2}}{\bfz^T\Lambda\bfz} - \Lambda_{D,S} \right\} vec^T \left\{ \frac{(\tilde D_\bfZ (\bfz))^2 \Lambda^{1/2} \bfz\bfz^T \Lambda^{1/2}}{\bfz^T\Lambda\bfz} - \Lambda_{D,S} \right\} \right]\\
-&=& E \left[ vec \left\{ (\tilde D_\bfZ (\bfz))^2 SS(\Lambda^{1/2}\bfz; \bf0) \right\} vec^T \left\{ (\tilde D_\bfZ (\bfz))^2 SS(\Lambda^{1/2}\bfz; \bf0) \right\} \right]\\
-&& - \quad vec(\Lambda_{D,S}) vec^T(\Lambda_{D,S})
-\end{eqnarray*}
-
-The matrix $vec(\Lambda_{D,S}) vec^T(\Lambda_{D,S})$ consists of elements $\lambda_i\lambda_j$ at $(i,j)^\text{th}$ position of the $(i,j)^\text{th}$ block, and 0 otherwise.
-These positions correspond to variance and covariance components of on-diagonal elements.
-For the expectation matrix, all its elements are of the form $E[\sqrt{\lambda_a \lambda_b \lambda_c \lambda_d} z_a z_b z_c z_d .
-(\tilde D_\bfZ (\bfz))^4 / (\bfz^T \Lambda \bfz)^2]$, with $1 \leq a,b,c,d \leq p$.
-Since $(\tilde D_\bfZ (\bfz))^4 / (\bfz^T \Lambda \bfz)^2$ is even in $\bfz$, which has a circularly symmetric distribution, all such expectations will be 0 unless $a=b=c=d$, or they are pairwise equal.
-Following a similar derivation for spatial sign covariance matrices in \cite{magyar14}, we collect the non-zero elements and write the matrix of expectations:
-%
-$$ (I_{p^2} + K_{p,p}) \left\{ \sum_{a=1}^p \sum_{b=1}^p \gamma^D_{ab} (\bfe_a \bfe_a^T \otimes  \bfe_b \bfe_b^T) - \sum_{a=1}^p \gamma^D_{aa} (\bfe_a \bfe_a^T \otimes  \bfe_a \bfe_a^T) \right\} + \sum_{a=1}^p \sum_{b=1}^p \gamma^D_{ab} (\bfe_a \bfe_b^T \otimes  \bfe_a \bfe_b^T) $$
-%
-where $I_k = (\bfe_1,...,\bfe_k), K_{m,n} = \sum_{i=1}^m \sum_{j=1}^n J_{ij} \otimes J_{ij}^T$ with $J_{ij}$ the $m \times n$ matrix having 1 as $(i,j)^\text{th}$ element and 0 elsewhere, and $\gamma^D_{mn} = E[ \lambda_m \lambda_n z_m^2 z_n ^2 .
-(\tilde D_\bfZ (\bfz))^4 / (\bfz^T \Lambda \bfz)^2]; 1 \leq m,n \leq p$.
-
-\paragraph{}Putting everything together, denote $\hat S^D(F_\Lambda) = \sum_{i=1}^n (\tilde D^n_\bfZ (\bfz_i))^2 SS(\Lambda^{1/2}\bfz_i; \hat \bfmu_n)/n $.
-Then the different types of elements in the matrix $V_{D,S}(F_\Lambda)$ are as given below ($1 \leq a,b,c,d \leq p$):
-
-\begin{itemize}
-\item Variance of on-diagonal elements
-%
-$$ AVar( \sqrt n \hat S^D_{aa} (F_\Lambda)) = E \left[ \frac{(\tilde D_\bfZ (\bfz))^4 \lambda_a^2 z_a^4}{(\bfz^T \Lambda \bfz)^2} \right] - \lambda_{D,S,a}^2 $$
-
-\item Variance of off-diagonal elements ($a \neq b$)
-%
-$$ AVar( \sqrt n \hat S^D_{ab} (F_\Lambda)) = E \left[ \frac{(\tilde D_\bfZ (\bfz))^4 \lambda_a \lambda_b z_a^2 z_b^2}{(\bfz^T \Lambda \bfz)^2} \right] $$
-
-\item Covariance of two on-diagonal elements ($a \neq b$)
-%
-$$ ACov(\sqrt n \hat S^D_{aa} (F_\Lambda), \sqrt n \hat S^D_{bb} (F_\Lambda))
-= E \left[ \frac{(\tilde D_\bfZ (\bfz))^4 \lambda_a \lambda_b z_a^2 z_b^2}{(\bfz^T \Lambda \bfz)^2} \right] - \lambda_{D,S,a} \lambda_{D,S,b} $$
-
-\item Covariance of two off-diagonal elements ($a \neq b \neq c \neq d$)
-%
-$$ ACov(\sqrt n \hat S^D_{ab} (F_\Lambda), \sqrt n \hat S^D_{cd} (F_\Lambda)) = 0 $$
-
-\item Covariance of one off-diagonal and one on-diagonal element ($a \neq b \neq c$)
-%
-$$ ACov(\sqrt n \hat S^D_{ab} (F_\Lambda), \sqrt n \hat S^D_{cc} (F_\Lambda)) = 0 $$
-\end{itemize}
-
-\section{Proofs}\label{section:appB}
-
-\begin{proof}[Proof of Theorem  \ref{Theorem:covform}]
-The proof follows directly from writing out the expression of $Cov ( \tilde \bfX)$:
-%
-\begin{eqnarray*}
-Cov(\tilde\bfX) &=& E(\tilde\bfX \tilde\bfX^T) - E(\tilde\bfX) E(\tilde\bfX)^T\\
-&=& \Gamma . E \left[ (\tilde D_\bfZ(\bfz))^2 \frac{\|\bfz\|^2}{\| \Lambda^{1/2}\bfz\|} \Lambda^{1/2} \bfS(\bfz) \bfS(\bfz)^T \Lambda^{1/2} \right] \Gamma^T - {\bf 0}_p {\bf 0}_p^T\\
-&=& \Gamma .E \left[ (\tilde D_\bfZ(\bfz))^2 \frac{\Lambda^{1/2} \bfz \bfz^T \Lambda^{1/2}}{\bfz^T \Lambda \bfz} \right] \Gamma^T
-\end{eqnarray*}
-%
-\end{proof}
-
-\begin{proof}[Proof of Lemma \ref{Lemma:lemma1}]
-For two positive definite matrices $A,B$, we denote by $A>B$ that $A-B$ is positive definite. Also, denote
-%
-$$ S_n = \sqrt n \left[ \frac{1}{n} \sum_{i=1}^n \left| (\tilde D^{n} _\bfX (\bfx_i))^2  - (\tilde D_\bfX (\bfx_i))^2 \right| SS(\bfx_i; \hat\bfmu_n) \right] $$
-%
-%Consider now the quantity $\bft^T S_n \bft$, where $\bft \in \mathbb{R}^p$. Now applying Cauchy-Schwarz inequality we shall have
-%%
-%\begin{eqnarray}\label{eqn:AppEqn1}
-%\frac{(\bft^T S_n \bft)^2}{n} & = & \left[ \frac{1}{n} \sum_{i=1}^n \left| (\tilde D^{n} _\bfX (\bfx_i))^2  - (\tilde D_\bfX (\bfx_i))^2 \right|^2  \bft^T SS(\bfx_i; \hat\bfmu_n) \bft \right]^2 \notag\\
-%& \leq & \left[ \frac{1}{n} \sum_{i=1}^n \left| (\tilde D^{n} _\bfX (\bfx_i))^2  - (\tilde D_\bfX (\bfx_i))^2 \right|^2 \right] \left[ \frac{1}{n} \left( \sqrt n.\frac{1}{n} \sum_{i=1}^n  SS(\bfx, \hat\bfmu_n) \right) \right]
-%\end{eqnarray}
-%%
-%with $\hat S_n = \sum_{i=1}^n SS(\bfx_i, \hat\bfmu_n)/ \sqrt n$.
-Now due to the assumption of uniform convergence, given $\epsilon>0$ we can find $N \in \mathbb{N}$ such that
-%
-\begin{equation}
-\label{equation:lemma1eq}
-| (\tilde D^{n_1}_\bfX(\bfx_i))^2 - (\tilde D_\bfX(\bfx_i))^2 | < \epsilon
-\end{equation}
-%
-for all $n_1 \geq N; i = 1,2,...,n_1$. This implies
-%
-\begin{eqnarray}
-\label{eqn:lemma1eq2}
-S_{n_1} &< & \epsilon \sqrt{n_1} \left[ \frac{1}{n_1} \sum_{i=1}^{n_1} SS(\bfx_i; \hat\bfmu_{n_1}) \right]\notag\\
-&=& \epsilon \sqrt{n_1} \left[ \frac{1}{n_1} \sum_{i=1}^{n_1} \left\{ SS(\bfx_i; \hat\bfmu_{n_1}) - SS(\bfx_i; \bfmu) \right\} + \frac{1}{n_1} \sum_{i=1}^{n_1} SS(\bfx_i; \bfmu) \right]
-\end{eqnarray}
-
-We now construct a sequence of positive definite matrices $\{A_k (B_k+C_k) : k \in \mathbb N\} $ so that
-%
-$$ A_k = \frac{1}{k}, \quad B_k = \sqrt{N_k} \left[ \frac{1}{N_k} \sum_{i=1}^{N_k} \left\{ SS(\bfx_i; \hat\bfmu_{N_k}) - SS(\bfx_i; \bfmu) \right\} \right]$$
-$$\quad C_k = \sqrt{N_k} \left[ \frac{1}{N_k} \sum_{i=1}^{N_k} SS(\bfx_i; \bfmu) \right] $$
-%
-where $N_k \in \mathbb N$ gives the relation (\ref{equation:lemma1eq}) in place of $N$ when we take $\epsilon = 1/k$.
-Under conditions $ E\|\bfx - \bfmu\|^{-3/2} < \infty $ and $\sqrt n (\hat\bfmu_n - \bfmu) = O_P(1)$, the sample SCM with unknown location parameter $\hat\bfmu_n$ has the same asymptotic distribution as the SCM with known location $\bfmu$ \citep{durre14}, hence $B_k = o_P(1)$, thus $A_k (B_k+C_k) \stackrel{P}{\rightarrow} 0$.
-
-Now (\ref{eqn:lemma1eq2}) implies that for any $\epsilon_1 > 0$, $S_{N_k} > \epsilon_1 \Rightarrow A_k (B_k + C_k) > \epsilon_1$, which means $ P(S_{N_k} > \epsilon_1) < P(A_k (B_k + C_k) > \epsilon_1)$.
-Hence the subsequence $\{S_{N_k}\} \stackrel{P}{\rightarrow} 0$.
-Since the main sequence $\{S_k\}$ is bounded below by 0, this implies $\{S_k\} \stackrel{P}{\rightarrow} 0$.
-Finally, we have that
-%
-\begin{eqnarray}
-\sqrt n \left[
-\frac{1}{n} \sum_{i=1}^n (\tilde D^n_\bfX (\bfx_i))^2 SS(\bfx_i; \hat\bfmu_n) -
-\frac{1}{n} \sum_{i=1}^n (\tilde D_\bfX (\bfx_i))^2 SS(\bfx_i; \bfmu) \right] &\leq & \hspace{1em} \notag\\
-S_n +  \sqrt{n} \left[ \frac{1}{n} \sum_{i=1}^{n} \left\{ SS(\bfx_i; \hat\bfmu_{n}) - SS(\bfx_i; \bfmu) \right\} \right] &&
-\end{eqnarray}
-%
-Since the second summand on the right hand side is $o_P(1)$ due to \cite{durre14} as mentioned before, we have the needed.
-\end{proof}
-
-\begin{proof}[Proof of Theorem \ref{Theorem:rootn}]
-The quantity in the statement of the theorem can be broken down as:
-%
-\begin{eqnarray*}
-\sqrt n \left[ vec\left\{ \frac{1}{n} \sum_{i=1}^n (\tilde D^n_\bfX (\bfx_i))^2 SS(\bfx_i; \hat\bfmu_n) \right\} - vec\left\{ \frac{1}{n} \sum_{i=1}^n (\tilde D_\bfX (\bfx_i))^2 SS(\bfx_i; \bfmu) \right\} \right] +\\
-\sqrt n \left[ vec\left\{ \frac{1}{n} \sum_{i=1}^n (\tilde D_\bfX (\bfx_i))^2 SS(\bfx_i; \bfmu) \right\} - E \left[ vec\left\{ (\tilde D_\bfX (\bfx))^2 SS(\bfx; \bfmu) \right\} \right] \right]
-\end{eqnarray*}
-%
-The first part goes to 0 in probability by Lemma \ref{Lemma:lemma1}, and applying Slutsky's theorem we get the required convergence.
-\end{proof}
-
-\begin{proof}[Proof of Theorem \ref{Theorem:decomp}]
-See \cite{taskinen12}
-\end{proof}
-
-\begin{proof}[Proof of Corollary \ref{Corollary:eigendist}]
-In spirit, this corollary is similar to Theorem 13.5.1 in \cite{anderson}, and indeed, \cite{taskinen12} used this theorem to prove Theorem \ref{Theorem:decomp}.
-Due to the decomposition (\ref{equation:decompEq}) we have, for the distribution $F_\Lambda$, the following relation between any off-diagonal element of $\hat S^D(F_\Lambda)$ and the corresponding element in the estimate of eigenvectors $\hat\Gamma_D (F_\Lambda)$:
-
-$$ \sqrt n \hat\gamma_{D,ij} (F_\Lambda) = \sqrt n \frac{\hat S^D_{ij} (F_\Lambda)}{\lambda_{D,S,i} - \lambda_{D,S,j}}; \quad i \neq j$$
-
-So that for eigenvector estimates of the original $F$ we have
-
-\begin{equation} \label{equation:app1}
-\sqrt n (\hat\bfgamma_{D,i} - \bfgamma_i) = \sqrt n \Gamma (\hat \bfgamma_{D,i}(F_\Lambda) - \bfe_i ) = \sqrt n \left[ \sum_{k=1; k \neq i}^p \hat \gamma_{D,ik}(F_\Lambda)\bfgamma_k + (\hat \gamma_{D,ii}(F_\Lambda) - 1)\bfgamma_i \right]
-\end{equation}
-
-$\sqrt n (\hat \gamma_{D,ii}(F_\Lambda) - 1) =  o_P(1)$ and $ACov(\sqrt n \hat S^D_{ik}(F_\Lambda), \sqrt n \hat S^D_{il}(F_\Lambda)) = 0$ for $k \neq l$, so the above equation implies
-
-$$ AVar(\bfg_i) = AVar (\sqrt n (\hat\bfgamma_{D,i} - \bfgamma_i)) = \sum_{k=1; k \neq i}^p \frac{AVar(\sqrt n \hat S^D_{ik}(F_\Lambda))}{(\lambda_{D,s,i} - \lambda_{D,S,k})^2} \bfgamma_k \bfgamma_k^T $$
-
-For the covariance terms, from (\ref{equation:app1}) we get, for $i \neq j$,
-
-\begin{eqnarray*}
-ACov(\bfg_i, \bfg_j) &=& ACov (\sqrt n (\hat\bfgamma_{D,i} - \bfgamma_i), \sqrt n (\hat\bfgamma_{D,j} - \bfgamma_j))\\
-&=& ACov \left( \sum_{k=1; k \neq i}^p \sqrt n \hat \gamma_{D,ik}(F_\Lambda)\bfgamma_k, \sum_{k=1; k \neq j}^p \sqrt n \hat \gamma_{D,jk}(F_\Lambda)\bfgamma_k \right)\\
-&=& ACov \left( \sqrt n \hat \gamma_{D,ij}(F_\Lambda)\bfgamma_j, \sqrt n \hat \gamma_{D,ji}(F_\Lambda)\bfgamma_i \right)\\
-&=& - \frac{AVar(\sqrt n \hat S^D_{ij}(\Lambda))}{(\lambda_{D,s,i} - \lambda_{D,S,j})^2} \bfgamma_j \bfgamma_i^T
-\end{eqnarray*}
-
-The exact forms given in the statement of the corollary now follows from the  Form of $V_{D,S}$ in Appendix \ref{section:appA}.
-
-\paragraph{}For the on-diagonal elements of $\hat S^D(F_\Lambda)$ Theorem \ref{Theorem:decomp} gives us $ \sqrt n \hat\lambda_{D,s,i} (F_\Lambda) = \sqrt n \hat S^D_{ii}(F_\Lambda)$ for $i = 1,...,p$.
-Hence
-
-\begin{eqnarray*}
-AVar(l_i) &=& AVar(\sqrt n \hat\lambda_{D,s,i} - \sqrt n \lambda_{D,S,i})\\
-&=& AVar(\sqrt n \hat\lambda_{D,s,i} (F_\Lambda) - \sqrt n \lambda_{D,S,i}(F_\Lambda))\\
-&=& AVar(\sqrt n S^D_{ii}(F_\Lambda))
-\end{eqnarray*}
-
-A similar derivation gives the expression for $AVar(l_i,l_j); i \neq j$.
-Finally, since the asymptotic covariance between an on-diagonal and an off-diagonal element of $\hat S^D(F_\Lambda)$, it follows that the elements of $G$ and diagonal elements of $L$ are independent.
-\end{proof}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%% END OF PAPER %%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%% END OF BIBLIOGRAPHY %%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\clearpage
+\input{TablesAndFigures}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%% END OF TABLES/FIGS %%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\clearpage
+\textbf{Corresponding author's contact information}
+
+\textit{Address}
+
+Subhabrata Majumdar
+
+University of Minnesota School of Statistics,
+
+Ford hall,
+
+224, Church Street,
+
+Minneapolis, MN 55455.
+
+\textit{e-mail}
+
+\href{mailto:majum010@umn.edu}{majum010@umn.edu}
+
+\textit{Phone}
+
++1 (612) -- 806 9996
+
+\clearpage
+\input{Appendix}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%% END OF APPENDIX %%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \end{document}

### 2018-03-20 MS/Sinica/SS-template - Copy.tex
first commit in shubhobm

--- 2018-03-20 MS/Depth-scatter-summary.tex
@@
-\documentclass[fleqn,11pt]{article}
-\usepackage{mycommands,amssymb,amsmath,amsthm,color,pagesize,outlines,cite,caption}
-\usepackage[pdftex]{graphicx}
-\usepackage[round]{natbib}
-\addtolength{\evensidemargin}{-.5in}
-\addtolength{\oddsidemargin}{-.5in}
-\addtolength{\textwidth}{0.9in}
-\addtolength{\textheight}{0.9in}
-\addtolength{\topmargin}{-.4in}
+\documentclass[10pt]{book}
+\usepackage[sectionbib]{natbib}
+\usepackage{array,epsfig,fancyheadings,rotating,caption}
+\usepackage{hyperref}
+\usepackage{mycommands}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-\usepackage{hyperref} % for linking references 
-\usepackage{setspace}
-\doublespacing
+\textwidth=31.9pc
+\textheight=46.5pc
+\oddsidemargin=1pc
+\evensidemargin=1pc
+\headsep=15pt
+%\headheight=.2cm
+\topmargin=.6cm
+\parindent=1.7pc
+\parskip=0pt
 
-%\DeclareMathOperator*{\vec}{vec}
-\DeclareMathOperator*{\diag}{diag}
-\DeclareMathOperator*{\Tr}{Tr}
+\usepackage{amsmath}
+\usepackage{amssymb}
+\usepackage{amsfonts}
+\usepackage{multirow}
+\usepackage{amsthm}
+
+\setcounter{page}{1}
+\pagestyle{fancy}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\pagestyle{fancy}
+\def\n{\noindent}
+\lhead[\fancyplain{} \leftmark]{}
+\chead[]{}
+\rhead[]{\fancyplain{}\rightmark}
+\cfoot{}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 \theoremstyle{definition} \newtheorem{Definition}[Theorem]{Definition}
+%\newtheorem{proof}{Proof}
+\newtheorem{example}{Example}
+\newtheorem{remark}{Remark}
 
-\title{Robust estimation of principal components from depth-based multivariate rank covariance matrix}
-\date{}
-\author{Subhabrata Majumdar}
-\maketitle
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-Abstract:
+%\renewcommand{\baselinestretch}{1.2}
+
+\markright{ \hbox{\footnotesize\rm Statistica Sinica
+%{\footnotesize\bf 24} (201?), 000-000
+}\hfill\\[-13pt]
+\hbox{\footnotesize\rm
+%\href{http://dx.doi.org/10.5705/ss.20??.???}{doi:http://dx.doi.org/10.5705/ss.20??.???}
+}\hfill }
+
+\markboth{\hfill{\footnotesize\rm FIRSTNAME1 LASTNAME1 AND FIRSTNAME2 LASTNAME2} \hfill}
+{\hfill {\footnotesize\rm FILL IN A SHORT RUNNING TITLE} \hfill}
+
+\renewcommand{\thefootnote}{}
+$\ $\par
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\fontsize{10.95}{14pt plus.8pt minus .6pt}\selectfont
+\vspace{0.8pc}
+\centerline{\large\bf Robust estimation of principal components}
+\vspace{2pt}
+\centerline{\large\bf from depth-based multivariate rank covariance matrix}
+\vspace{.4cm}
+\centerline{Author(s)}
+\vspace{.4cm}
+\centerline{\it Affiliation(s)}
+\vspace{.55cm}
+\fontsize{9}{11.5pt plus.8pt minus .6pt}\selectfont
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{quotation}
+\noindent {\it Abstract:}
 Analyzing principal components for multivariate data from its spatial sign covariance matrix (SCM) has been proposed as a computationally simple and robust alternative to normal PCA, but it suffers from poor efficiency properties and is actually inadmissible with respect to the maximum likelihood estimator.
@@
 Through two real data examples, we also show the effectiveness of DCM-based PCA in analyzing high-dimensional data and outlier detection, and compare it with other methods of robust PCA.
-\vspace{.5cm}
+\par
 
-Keywords:
+\vspace{9pt}
+\noindent {\it Key words and phrases:}
 Data depth; Principal components analysis; Robustness; Sign covariance matrix; Multivariate ranking
+\par
+\end{quotation}\par
 
-\newpage
-\section{Introduction}
+\def\thefigure{\arabic{figure}}
+\def\thetable{\arabic{table}}
+
+\fontsize{10.95}{14pt plus.8pt minus .6pt}\selectfont
+
+\setcounter{chapter}{1}
+\setcounter{equation}{0} %-1
+\noindent {\bf 1. Introduction}
+
 In multivariate analysis, the study of principal components is important since it provides a small number of uncorrelated variables from a potentially larger number of variables, so that these new components explain most of the underlying variability in the original data.
@@
 
-The chapter is arranged in the following fashion.
-Section \ref{section:sec2} provides preliminary theoretical concepts required for developments in the subsequent sections.
-Section \ref{section:dcmSection} introduces the Depth Covariance Matrix (DCM) and states some basic results related to this.
-Section \ref{section:sec4} provides asymptotic results regarding the sample DCM, calculated using data depths with respect to the empirical distribution function, as well as its eigenvectors and eigenvalues.
-Section \ref{section:simSection} focuses solely on principal component estimation using the sample DCM.
+The paper is arranged in the following fashion.
+Section 2 provides preliminary theoretical concepts required for developments in the subsequent sections.
+Section 3 introduces the Depth Covariance Matrix (DCM) and states some basic results related to this.
+Section 4 provides asymptotic results regarding the sample DCM, calculated using data depths with respect to the empirical distribution function, as well as its eigenvectors and eigenvalues.
+Section 5 focuses solely on principal component estimation using the sample DCM.
 We obtain influence functions and asymptotic efficiencies for eigenvectors of the DCM.
 We also compare their finite sample efficiencies for several multinormal and multivariate $t$-distributions with those of the SCM, Tyler's scatter matrix and its depth-weighted version through a simulation study.
-Section \ref{section:sec6} presents two applications of the methods we develop on real data.
-Finally, we wrap up our discussion in Section \ref{section:sec7} by giving a summary of our findings and providing some potential future areas of research.
-Appendices \ref{section:appA} and \ref{section:appB} contain all technical details and proofs of the results we derive.
+Section 6 presents two applications of the methods we develop on real data.
+Finally, we wrap up our discussion in Section 7 by giving a summary of our findings and providing some potential future areas of research.
+Proofs of all the results we derive are given in the appendix.
+\par
 
-\section{Preliminaries}\label{section:sec2}
-\subsection{Spatial signs and sign covariance matrix}
-Given a vector $\bfx \in \mathbb{R}^p$, its spatial sign is defined as the vector valued function \citep{MottonenOja95}:
+\vspace{1em}
+\setcounter{chapter}{2}
+\setcounter{equation}{0} %-1
+\noindent {\bf 2. Preliminaries}
+
+Given a vector $\bfx \in \mathbb{R}^p$, its spatial sign is defined as the vector valued function \citep{locantore99}:
 %
@@
 
-\subsection{Data depth and outlyingness}
-For any multivariate distribution $F = F_\bfX$ belonging to a set of distributions $\mathcal F$, the depth of a point $\bfx \in \mathbb{R}^p$, say $D(\bfx, F_\bfX)$ is any real-valued function that provides a 'center outward ordering' of $\bfx$ with respect to $F$ \citep{zuo00}.
+\vspace{.5em}
+\noindent {\bf 2.1 Data depth and outlyingness}
+
+For any multivariate distribution $F = F_\bfX$, the depth of a point $\bfx \in \mathbb{R}^p$, say $D(\bfx, F_\bfX)$ is any real-valued function that provides a 'center outward ordering' of $\bfx$ with respect to $F$ \citep{zuo00}.
 \cite{liu90} outlines the desirable properties of a statistical depth function:
 
-\vspace{1em}
-\noindent\textbf{(D1)} \textit{Affine invariance}: $D(A\bfx + \bfb, F_{A\bfX+\bfb}) = D(\bfx, F_\bfX)$;
+\noindent
+(P1) Affine invariance: $D(A\bfx + \bfb, F_{A\bfX+\bfb}) = D(\bfx, F_\bfX)$\\
+(P2) Maximality at center: $D(\bftheta, F_\bfX) = \sup_{\bfx\in \mathbb{R}^p} D(\bfx, F_\bfX)$ for $F_\bfX$ having center of symmetry $\bftheta$.
+This point is called the \textit{deepest point} of the distribution.\\
+(P3) Monotonicity with respect to deepest point: $D(\bfx; F_\bfX) \leq D(\bftheta + a(\bfx - \bftheta), F_\bfX)$, $\bftheta$ being deepest point of $F_\bfX$.\\
+(P4) Vanishing at infinity: $D(\bfx; F_\bfX) \rightarrow \bf0$ as $\|\bfx\| \rightarrow \infty $.
 
-\noindent\textbf{(D2)} \textit{Maximality at center}: $D(\bftheta, F_\bfX) = \sup_{\bfx\in \mathbb{R}^p} D(\bfx, F_\bfX)$ for $F_\bfX$ having center of symmetry $\bftheta$.
-This point is called the \textit{deepest point} of the distribution.;
-
-\noindent\textbf{(D3)} \textit{Monotonicity with respect to deepest point}: $D(\bfx; F_\bfX) \leq D(\bftheta + a(\bfx - \bftheta), F_\bfX)$, $\bftheta$ being deepest point of $F_\bfX$.;
-
-\noindent\textbf{(D4)} \textit{Vanishing at infinity}: $D(\bfx; F_\bfX) \rightarrow 0$ as $\|\bfx\| \rightarrow \infty $.
-\vspace{1em}
-
-In (D2) the types of symmetry considered can be central symmetry, angular symmetry and halfspace symmetry.
+In (P2) the types of symmetry considered can be central symmetry, angular symmetry and halfspace symmetry.
 Also for multimodal probability distributions, i.e.
-distributions with multiple local maxima in their probability density functions, properties (D2) and (D3) are actually restrictive towards the formulation of a reasonable depth function that captures the shape of the data cloud.
-In our derivations that follow, we replace these two by a weaker condition:
-
-\vspace{1em}
-\noindent\textbf{(D2*)} \textit{Existence of a maximal point}: The maximum depth over all distributions $F$ and points $\bfx$ is bounded above, i.e.
-$ \sup_{F_\bfX \in \mathcal F} \sup_{\bfx\in \mathbb{R}^p} D(\bfx, F_\bfX) < \infty $.
-We denote this point by $M_D(F_\bfX)$.
-\vspace{1em}
+distributions with multiple local maxima in their probability density functions, properties (P2) and (P3) are actually restrictive towards the formulation of a reasonable depth function that captures the shape of the data cloud.
+In our derivations that follow, we replace these two by a slightly weaker condition: (P2*) The \textit{existence} of a maximal point, i.e.
+$ \sup_{\bfx\in \mathbb{R}^p} D(\bfx, F_\bfX) < \infty $.
+We denote this point by $M_D(F)$.
 
 A real-valued function measuring the outlyingness of a point with respect to the data cloud can be seen as the opposite of what data depth does.
-Indeed, such functions have been used to define several depth functions, for example simplicial depth, projection depth and $L_p$-depth.
-Keeping with the spirit of the utility of these functions we name them `htped': literally the reverse of `depth', and give a general definition of such functions as a transformation on any depth function:
+Indeed, such functions have been used to define several depth functions, for example simplicial volume depth, projection depth and $L_p$-depth.
+Here we give a general definition of such functions as a transformation on any depth function:
 
@@
 It is defined as
-%
+
 $$ MhD(\bfX, F) = \frac{1}{1 + d^2_\Sigma (\bfx - \bfmu)} $$
-%
+
 note here that $d_\Sigma(\bfx,\bfmu)$ can be seen as a valid htped function of $\bfx$ with respect to $F$.
@@
 \item \textbf{Projection depth} (PD) \citep{zuo03} is another depth function based on an outlyingness function. Here that function is
-%
+
 $$ O(\bfx, F) = \sup_{\| \bfu \| = 1} \frac{| \bfu^T\bfx - m(\bfu^T\bfX)|}{s(\bfu^T\bfX)} $$
-%
+
 where $m$ and $s$ are some univariate measures location and scale, respectively. Given this the depth at $\bfx$ is defined as $PD(\bfx, F) = 1/(1+O(\bfx, F))$.
@@
 
-\section{Depth-based rank covariance matrix} \label{section:dcmSection}
+\vspace{1em}
+\setcounter{chapter}{3}
+\setcounter{equation}{0} %-1
+\noindent {\bf 3. Depth-based rank covariance matrix}\vspace{1em}
 
-Consider a vector-valued random variable $\bfX \in \mathbb{R}^p$ .
+Consider a vector-valued random variable $\bfX \in \mathbb{R}^p$.
 Data depth is as much a property of the random variable as it is of the underlying distribution, so for ease of notation while working with transformed random variables, from now on we shall be using $D_\bfX(\bfx) = D(\bfx, F)$ to denote the depth of a point $\bfx$.
@@
 \cite{serfling2006}).
-The notion of multivariate ranks goes back to \cite{PuriSenBook}, where they take the vector consisting of marginal univariate ranks as multivariate rank vector.
-Subsequent definitions of multivariate ranks were proposed by \cite{MottonenOja95,HallinPaindaveine02} and \cite{Chernozhukov14}.
-Compared to these formulations, our definition of multivariate ranks works for any general depth function, and provides an intuitive extension to any spatial sign-based methodology.
-
-Figure \ref{fig:rankplot} gives an idea of how the multivariate rank vector $\tilde \bfX$ is distributed when $\bfX$ has a bivariate normal distribution.
+Figure \ref{fig:rankplot} gives an idea of how $\tilde \bfX$ is distributed when $\bfX$ has a bivariate normal distribution.
 Compared to the spatial sign, which are distributed on the surface of $p$-dimensional unit ball centered at $\bfmu$, these spatial ranks have the same direction as original data and reside \textit{inside} the $p$-dimensional ball around $\bfmu$ that has radius $M_D(F)$ (which, for the case of halfspace depth, equals 0.5).
@@
 	\centering
-		\includegraphics[height=6cm]{../Codes/ranks}
+		\includegraphics[height=6cm]{ranks}
 	\caption{(Left) 1000 points randomly drawn from $\mathcal N_2\left((0,0)^T, \left(\protect\begin{smallmatrix} 5 & -4 \\ -4 & 5 \protect\end{smallmatrix}\right)\right) $ and (Right) their multivariate ranks based on halfspace depth}
@@
 This is because Tyler's scatter matrix $\Sigma_T$ is defined as the implicit solution to the following equation:
+%
 \begin{equation} \label{equation:tylerEq}
@@
 \end{equation}
+%
 and simply replacing $\bfx$ by its multivariate rank counterpart $\tilde\bfx$ will not change the estimate $\Sigma_T$ as $\bfx$ and $\tilde \bfx$ have the same directions.
@@
 We conjecture that its concentration properties can be obtained by taking an approach similar to \cite{soloveychik14}.
+%\begin{figure}[h!]
+%\includegraphics [angle=-90, scale=0.45]{d:/sinicas/simuh3.eps}\par
+%\centerline{\epsfig{file=d:/sinicas/simuh3.eps,angle=-90,width=4.5in}}\par
+%\centerline{\epsfig{file=d:/sinicas/simuh4.eps,width=4.5in}}\par
 
-\section{Asymptotic results}\label{section:sec4}
-\subsection{The sample DCM}
-Let us now consider $n$ iid random draws from our elliptic distribution $F$, say $\bfX_1,...,\bfX_n$.
-For ease of notation, denote $SS(\bfx; \bfmu) = \bfS(\bfx - \bfmu) \bfS(\bfx - \bfmu)^T$.
-Then, given the depth function and known location center $\bfmu$, one can show that the vectorized form of $\sqrt n$-times the sample DCM: $\sum_{i=1}^n (\tilde D_\bfX(\bfx_i))^2SS(\bfx_i; \bfmu) /\sqrt{n}$  has an asymptotic multivariate normal distribution with mean $\sqrt n.vec(E[( (\tilde D_\bfX (\bfX))^2 SS(\bfx; \bfmu)])$ and a certain covariance matrix by straightforward application of the central limit theorem (CLT).
-But in practice the population depth function $D_\bfX(\bfx) = D(\bfx, F)$ is estimated by the depth function based on the empirical distribution function, $F_n$.
-Denote this sample depth by $D^n_\bfX (\bfx) = D(\bfx, F_n)$.
-Here we make the following assumption regarding its relation to $D_\bfX(\bfx)$:
+%\caption{Caption of the figure.}
+%\end{figure}
 
-\vspace{1em}
-\noindent\textbf{(D5)} \textit{Uniform convergence}: $\sup_{\bfx \in \mathbb R^p} | D^n_\bfX (\bfx) - D_\bfX (\bfx) | \rightarrow 0$ as $n \rightarrow \infty $.
-\vspace{1em}
+\begin{equation}\label{2.1}
+\mbox {The 1st display equation of the second section.}
+\end{equation}
+\begin{equation}\label{2.2}
+\mbox {The 2nd display equation of the second section.}
+\end{equation}
 
-The assumption that empirical depths converge uniformly at all points $\bfx$ to their population versions holds under very mild conditions for several well known depth functions: for example projection depth \citep{zuo03} and simplicial depth \citep{Dumbgen92}.
-One also needs to replace the known location parameter $\bfmu$ by some estimator $\hat\bfmu_n$.
-Examples of robust estimators of location that are relevant here include the spatial median \citep{haldane48,brown83}, Oja median \citep{oja83}, projection median \citep{zuo03} etc.
-Now, given $D^n_\bfX(.)$ and $\hat \bfmu_n$, to plug them into the sample DCM and still go through with the CLT we need the following result:
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\newpage
+\lhead[\footnotesize\thepage\fancyplain{}\leftmark]{}\rhead[]{\fancyplain{}\rightmark\footnotesize\thepage}%Put this line in Page 2
 
-\begin{Lemma} \label{Lemma:lemma1}
-Consider a random variable $\bfX \in \mathbb{R}^p$ having a continuous and symmetric distribution with location center $\bfmu$ such that $E\|\bfx - \bfmu \|^{-3/2} < \infty$.
-Given $n$ random samples from this distribution, suppose $\hat\bfmu_n$ is an estimator of $\bfmu$ so that $\sqrt n (\hat\bfmu_n - \bfmu) = O_P(1) $.
-Then with the above notations, and given the assumption (D5) we have
-%
-$$ \sqrt n \left[
-\frac{1}{n} \sum_{i=1}^n (\tilde D^n_\bfX (\bfx_i))^2 SS(\bfx_i; \hat\bfmu_n) -
-\frac{1}{n} \sum_{i=1}^n (\tilde D_\bfX (\bfx_i))^2 SS(\bfx_i; \bfmu) \right]
-\stackrel{P}{\rightarrow} 0 $$
-\end{Lemma}
+\setcounter{chapter}{3}
+\setcounter{equation}{0} %-1
+\noindent {\bf 3. The Third Section}
 
-We are now in a position to state the result for consistency of the sample DCM:
+Contents of the third section.
 
-\begin{Theorem} \label{Theorem:rootn}
-Consider $n$ iid samples from the distribution in Lemma \ref{Lemma:lemma1}.
-Then, given a depth function $D_\bfX(.)$ and an estimate of center $\hat\bfmu_n$ so that $\sqrt n(\hat \bfmu_n - \bfmu) = O_P(1)$,
-%
-$$ \sqrt n \left[ vec\left\{ \frac{1}{n} \sum_{i=1}^n (\tilde D^n_\bfX (\bfx_i))^2 SS(\bfx_i; \hat\bfmu_n) \right\} - E \left[ vec\left\{ (\tilde D_\bfX (\bfx))^2 SS(\bfx; \bfmu) \right\} \right] \right]
-\stackrel{D}{\rightarrow}
-N_{p^2} ({\bf 0}, V_{D,S}(F)) $$
-$$ \text{with } V_{D,S}(F) = Var \left[vec \left\{ (\tilde D_\bfX (\bfx))^2 SS(\bfx; \bfmu) \right\} \right] $$
-\end{Theorem}
+Contents of the third section.
 
-In case $F$ is elliptical, an elaborate form of the covariance matrix $V_{D,S}(F)$ explicitly specifying each of its elements (more directly those of its $\Gamma^T$-rotated version) can be obtained, which is given in Appendix \ref{section:appA}.
-This form is useful when deriving limiting distributions of eigenvectors and eigenvalues of the sample DCM.
+Contents of the third section.
 
-\subsection{Eigenvectors and eigenvalues} Since we are mainly interested in using the DCM for a robust version of principal components analysis, from now on we assume that the eigenvalues of $\Sigma$ are distinct: $\lambda_1 > \lambda_2 > ...
-> \lambda_p$ to obtain asymptotic distributions of principal components.
-In the case of eigenvalues with larger than 1 multiplicities, the limiting distributions of eigenprojection matrices can be obtained analogous to those of the sign covariance matrix \citep{magyar14}.
+Contents of the third section.
 
-\paragraph{}We now derive the asymptotic joint distributions of eigenvectors and eigenvalues of the sample DCM.
-The following result allows us to get these, provided we know the limiting distribution of the sample DCM itself:
-
-\begin{Theorem} \label{Theorem:decomp} \citep{taskinen12}
-Let $F_\Lambda$ be an elliptical distribution with a diagonal covariance matrix $\Lambda$, and $\hat C$ be any positive definite symmetric $p \times p$ matrix such that at $F_\Lambda$ the limiting distribution of $\sqrt n vec(\hat C - \Lambda)$ is a $p^2$-variate (singular) normal distribution with mean zero.
-Write the spectral decomposition of $\hat C$ as $\hat C = \hat P \hat\Lambda \hat P^T$.
-Then the limiting distributions of $\sqrt n vec(\hat P - I_p)$ and $\sqrt n vec(\hat\Lambda - \Lambda)$ are multivariate (singular) normal and
-%
-\begin{equation} \label{equation:decompEq}
-\sqrt n vec (\hat C - \Lambda)  = \left[ (\Lambda \otimes I_p) - (I_p \otimes \Lambda) \right] \sqrt n vec (\hat P - I_p) + \sqrt n vec (\hat\Lambda - \Lambda) + o_P(1)
+Contents of the third section.
+\begin{equation}\label{3.1}
+\mbox {The 1st display equation of the third section.}
 \end{equation}
-\end{Theorem}
-
-The first matrix picks only off-diagonal elements of the LHS and the second one only diagonal elements.
-We shall now use this as well as the form of the asymptotic covariance matrix of the vec of sample DCM, i.e.
-$V_{D,S}(F)$ to obtain limiting variance and covariances of eigenvalues and eigenvectors.
-
-\begin{Corollary} \label{Corollary:eigendist}
-Consider the sample DCM $ \hat S^D(F) = \sum_{i=1}^n (\tilde D^n_\bfX (\bfx_i))^2 SS(\bfx_i; {\bf \hat\bfmu_n})/n $ and its spectral decomposition $\hat S^D(F) = \hat\Gamma_D \hat\Lambda_D \hat\Gamma_D^T $.
-Then the matrices $G = \sqrt n (\hat\Gamma_D - \Gamma) $ and $L = \sqrt n (\hat\Lambda_D - \Lambda_{D,S}) $ have independent distributions.
-The random variable $vec(G)$ asymptotically has a $p^2$-variate normal distribution with mean ${\bf 0}_{p^2}$, and the asymptotic variance and covariance of different columns of $G = (\bfg_1,...,\bfg_p)$ are as follows:
-%
-\begin{equation} \label{equation:DevEq}
-AVar(\bfg_i) = \sum_{k=1; k \neq i}^p \frac{1}{(\lambda_{D,s,k} - \lambda_{D,S,i})^2} E \left[ \frac{(\tilde D_\bfZ (\bfz))^4 \lambda_i \lambda_k z_i^2 z_k^2}{(\bfz^T \Lambda \bfz)^2} \right] \bfgamma_k \bfgamma_k^T
+\begin{equation}\label{3.2}
+\mbox {The 2nd display equation of the third section.}
 \end{equation}
-%
-\begin{equation}
-ACov(\bfg_i, \bfg_j) = - \frac{1}{(\lambda_{D,s,i} - \lambda_{D,S,j})^2} E \left[ \frac{(\tilde D_\bfZ (\bfz))^4 \lambda_i \lambda_j z_i^2 z_j^2}{(\bfz^T \Lambda \bfz)^2} \right] \bfgamma_j \bfgamma_i^T; \quad i \neq j
-\end{equation}
-%
-where $\Gamma = (\bfgamma_1,...,\bfgamma_p)$.
-The vector consisting of diagonal elements of $L$, say $\bfl = (\l_1,...,\l_p)^T$ asymptotically has a $p$-variate normal distribution with mean ${\bf 0}_p$ and variance-covariance elements:
-%
-\begin{eqnarray}
-AVar(l_i) &=& E \left[ \frac{(\tilde D_\bfZ (\bfz))^4 \lambda_i^2 z_i^4}{(\bfz^T \Lambda \bfz)^2} \right] - \lambda_{D,S,i}^2\\
-ACov(l_i, l_j) &=& E \left[ \frac{(\tilde D_\bfZ (\bfz))^4 \lambda_i \lambda_j z_i^2 z_j^2}{(\bfz^T \Lambda \bfz)^2} \right] - \lambda_{D,S,i} \lambda_{D,S,j}; \quad i \neq j
-\end{eqnarray}
-%
-\end{Corollary}
-
-\section{Robustness and efficiency properties} \label{section:simSection}
-In this section, we first obtain the influence functions of the DCM as well as its eigenvectors and eigenvalues, which are essential to understand how much influence a sample point, especially an infinitesimal contamination, has on any functional on the distribution \citep{hampel}.
-We also derive the asymptotic efficiencies of individual principal components with respect to those of the original covariance matrix and sign covariance matrix.
-Unlike affine equivariant estimators of shape, the Asymptotic Relative Efficiency (ARE) of eigenvectors (with respect to any other affine equivariant estimator) can not be simplified as a ratio of two scalar quantities dependent on only the distribution of $\| \bfz \|$ (e.g.
-\cite{taskinen12,ollilia03}).
-Finite sample efficiency of the DCM estimates with respect to infinitesimal contamination and heavy-tailed distributions shall also be demonstrated by a simulation study.
-
-\subsection{Influence functions}
-Given any probability distribution $F$, the influence function of any point $\bfx_0$ in the sample space $\mathcal{X}$ for some functional $T(F)$ on the distribution is defined as
-%
-$$ IF(\bfx_0; T,F) = \lim_{\epsilon \rightarrow 0} \frac{1}{\epsilon} (T(F_\epsilon) - T(F)) $$
-%
-where $F_\epsilon$ is $F$ with an additional mass of $\epsilon$ at $\bfx_0$, i.e.
-$F_\epsilon = (1-\epsilon)F + \epsilon \Delta_{\bfx_0}$; $\Delta_{\bfx_0}$ being the distribution with point mass at $\bfx_0$.
-When $T(F) = E_F g$ for some $F$-integrable function $g$, $IF(\bfx_0; T,F) = g(\bfx_0) - T(F)$.
-It now follows that for the DCM,
-%
-$$ IF(\bfx_0; Cov(\tilde \bfX), F) = (\tilde D_\bfX(\bfx_0))^2 SS(\bfx_0; \bfmu) - Cov(\tilde \bfX) $$
-
-Following \cite{croux00}, we now get the influence function of the $i^\text{th}$ column of $\hat\Gamma_D = (\hat\bfgamma_{D,1},...,\hat\bfgamma_{D,p}); i = 1,...,p$:
-%
-\begin{eqnarray}
-IF(\bfx_0; \hat\bfgamma_{D,i}, F) &=& \sum_{k=1; k \neq i}^p \frac{1}{\lambda_{D,S,i} - \lambda_{D,S,k}} \left\{ \bfgamma^T_k IF(\bfx_0; Cov(\tilde \bfX), \bfgamma_i) \right\} \bfgamma_k \notag \\
-&=& \sum_{k=1; k \neq i}^p \frac{1}{\lambda_{D,S,i} - \lambda_{D,S,k}} \left\{ \bfgamma^T_k (\tilde D_\bfX(\bfx_0))^2 SS(\bfx_0; \bfmu)\bfgamma_i - \lambda_{D,S,i}\bfgamma_k^T\bfgamma_i \right\} \bfgamma_k \notag \\
-&=& \sum_{k=1; k \neq i}^p \frac{\sqrt{\lambda_i \lambda_k} z_{0i} z_{0k}}{\lambda_{D,S,i} - \lambda_{D,S,k}}. \frac{(\tilde D_\bfZ(\bfz_0))^2 }{\bfz_0^T \Lambda \bfz_0} \bfgamma_k
-\end{eqnarray}
-%
-where $\Gamma^T \Lambda^{-1/2} (\bfx_0 - \bfmu) = \bfz_0 = (z_{01},...,z_{0p})^T$.
-Clearly this influence function will be bounded, which indicates good robustness properties of principal components.
-Moreover, since the htped function takes small values for points close to the center of the distribution, it does not suffer from the inlier effect that is typical of the SCM and Tyler's shape matrix.
-The influence function for the $i^\text{th}$ eigenvector estimates of these two matrices (say $\hat\bfgamma_{S,i}$ and $\hat\bfgamma_{T,i}$, respectively) are as follows:
-%
-\begin{eqnarray*}
-\quad IF(\bfx_0; \hat \bfgamma_{S,i}, F) &=& \sum_{k=1; k \neq i}^p \frac{\sqrt{\lambda_i \lambda_k}}{\lambda_{S,i} - \lambda_{S,k}}.
-\frac{z_{0i} z_{0k}}{\bfz_0^T \Lambda \bfz_0} \bfgamma_k, \text{ with } \lambda_{S,i} = E_\bfZ \left( \frac{\lambda_i z_i^2}{\sum_{j=1}^p \lambda_j z_j^2} \right) \quad \\
-IF(\bfx_0; \hat \bfgamma_{T,i}, F) &=& (p+2) \sum_{k=1; k \neq i}^p \frac{\sqrt{\lambda_i \lambda_k}}{\lambda_i - \lambda_k}. \frac{z_{0i} z_{0k}}{\bfz_0^T \bfz_0} \bfgamma_k \quad 
-\end{eqnarray*}
-%
-for $i = 1,2$.
-In Figure \ref{fig:IFnorm} we consider first eigenvectors of different scatter estimates for the $\mathcal{N}_2((0,0)^T, \diag(2,1))$ and plot norms of these influence functions for different values of $\bfx_0$.
-The plots for SCM and Tyler's shape matrix demonstrate the 'inlier effect', i.e.
-points close to symmetry center and the center itself having high influence.
-The influence function for the sample covariance matrix is obtained by replacing $(p+2)$ by $\| \bfz_0 \|^2$ in the expression of $IF(\bfx_0; \hat \bfgamma_{T,i}, F)$ above, hence is unbounded and the corresponding eigenvector estimators are not robust.
-In comparison, all three DCMs considered here have a bounded influence function as well as small values of the influence function at 'deep' points.
-
-\begin{figure}[]
-	\centering
-		\includegraphics[width=12cm]{../Codes/IFnorm.png}
-	\caption{Plot of the norm of influence function for first eigenvector of (a) sample covariance matrix, (b) SCM, (c) Tyler's scatter matrix and DCMs for (d) Halfspace depth, (e) Mahalanobis depth, (f) Projection depth for a bivariate normal distribution with $\bfmu = {\bf 0}, \Sigma = \diag(2,1)$}
-	\label{fig:IFnorm}
-\end{figure}
-
-\subsection{Asymptotic and finite-sample efficiencies}
-Suppose $\hat\Sigma$ is a $\sqrt n$-consistent estimator of the population covariance matrix $\Sigma$, which permits a spectral decomposition $ \hat\Sigma = \hat\Gamma \hat\Lambda \hat\Gamma^T $, where $\hat\Gamma = (\hat\bfgamma_1,...,\hat\bfgamma_p)$.
-Then the asymptotic variance of the eigenvectors are (see Theorem 13.5.1 in \cite{anderson})
-%
-\begin{equation} \label{equation:covevEq}
-AVar(\sqrt n\hat \bfgamma_i) = \sum_{k=1; k \neq i}^p \frac{\lambda_i \lambda_k}{(\lambda_i - \lambda_k)^2} \bfgamma_k \bfgamma_k^T
-\end{equation}
-%
-The asymptotic relative efficiencies of eigenvectors from the sample DCM with respect to the sample covariance matrix can now be derived using (\ref{equation:covevEq}) above and (\ref{equation:DevEq}) from Corollary \ref{Corollary:eigendist}:
-%
-\begin{eqnarray*}
-ARE(\hat\bfgamma^D_i, \hat\bfgamma_i; F) &=& \frac{\Tr( AVar(\sqrt n\hat \bfgamma_i))}{\Tr( AVar(\sqrt n\hat \bfgamma^D_i))}\\
-&=& \left[\sum_{k=1; k \neq i}^p \frac{\lambda_i \lambda_k}{(\lambda_i - \lambda_k)^2} \right] \left[ \sum_{k=1; k \neq i}^p \frac{\lambda_i \lambda_k }{(\lambda_{D,s,i} - \lambda_{D,S,k})^2} E \left( \frac{(\tilde D_\bfZ (\bfz))^4 z_i^2 z_k^2}{(\bfz^T \Lambda \bfz)^2} \right) \right]^{-1}
-\end{eqnarray*}
-
-For 2 dimensions, this expression can be somewhat simplified. Suppose the two eigenvalues are $\lambda$ and $\rho\lambda$. In that case the eigenvalues of the DCM are
-%
-$$ \lambda_{D,S,1} = E \left( \frac{(\tilde D_\bfZ(\bfz))^2 z_1^2}{z_1^2 + \rho z_2^2} \right), \quad
-\lambda_{D,S,2} = E \left( \frac{(\tilde D_\bfZ(\bfz))^2 \rho z_2^2}{z_1^2 + \rho z_2^2} \right) $$
-and by simple algebra we get
-%
-$$ ARE(\hat\bfgamma^D_1, \hat\bfgamma_1; F) = ARE(\hat\bfgamma^D_2, \hat\bfgamma_2; F) = \frac{1}{(1-\rho)^2} \frac{\left[ E \left( \frac{(\tilde D_\bfZ(\bfz))^2 (z_1^2 - \rho z_2^2)}{(z_1^2 + \rho z_2^2)} \right) \right]^2 }{E \left( \frac{(\tilde D_\bfZ(\bfz))^4 z_1^2z_2^2}{(z_1^2 + \rho z_2^2)^2}\right)} $$
-
-For $\rho=0.5$, Table \ref{table:AREtable} below considers 6 different elliptic distributions (namely, bivariate $t$ with df = $5,6,10,15,25$ and bivariate normal), and summarizes the ARE for first eigenvector of the SCM, Tyler's scatter matrix and DCM for 3 choices of depth function (HSD-CM, MhD-CM, PD-CM: columns 3-5), as well as their depth-weighted versions mentioned at the end of section \ref{section:dcmSection} (HSD-wCM, MhD-wCM, PD-wCM: columns 6-8).
-The SCM and Tyler's M-estimator perform better than the sample covariance matrix only for a bivariate $t$-distribution with df = 5.
-Estimates based on depth-based covariance matrices have much better performances for all distributions, and continue to be competitive of the sample covariance matrix estimates as the base distribution approaches normality, especially those based on projection depth.
-Interestingly, depth-weighted versions seem to have better performances than their corresponding DCMs, more so for heavy-tailed distributions.
-
+\newpage
 \begin{table}
-\begin{footnotesize}
-    \begin{tabular}{c|cc|ccc|ccc}
-     \hline
-                       & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
-    Bivariate $t_5$    & 1.46 & 1.50  & 1.97   & 1.54   & 1.99  & 2.09    & 1.57    & 2.11   \\
-    Bivariate $t_6$    & 0.97 & 1.00  & 1.37   & 1.12   & 1.40  & 1.45    & 1.19    & 1.49   \\
-    Bivariate $t_{10}$ & 0.65 & 0.67  & 0.96   & 0.88   & 1.02  & 1.02    & 0.94    & 1.10   \\
-    Bivariate $t_{15}$ & 0.57 & 0.59  & 0.87   & 0.82   & 0.94  & 0.92    & 0.87    & 1.00   \\
-    Bivariate $t_{25}$ & 0.54 & 0.55  & 0.79   & 0.75   & 0.88  & 0.85    & 0.81    & 0.95   \\
-    BVN   & 0.49 & 0.50  & 0.73   & 0.71   & 0.82  & 0.77    & 0.75    & 0.88   \\ \hline
-    \end{tabular}
-\end{footnotesize}
-\caption{Asymptotic efficiencies relative to sample covariance matrix for $p=2$}
-\label{table:AREtable}
+\caption{Caption of the table.}
+\label{tab:simulation}\par
+\vskip .2cm
+\centerline{\tabcolsep=5truept\begin{tabular}{|rcrrrrrrrrr|} \hline
+\multicolumn{2}{|c}{Bandwidth}
+         & \multicolumn{3}{c}{$h=3$}
+         & \multicolumn{3}{c}{$h=4$}
+         & \multicolumn{3}{c|}{$h=5$} \\ \hline
+         &&&&&&&&&&\\[-11pt]
+\multicolumn{2}{|c}{Estimates}
+          & \multicolumn{1}{c}{$\hat N_H^{LC}$} & \multicolumn{1}{c}{$\hat N_{\bar H}^{LC}$} & \multicolumn{1}{c}{$\hat N_{\bar H}^{LL}$}
+          & \multicolumn{1}{c}{$\hat N_H^{LC}$} & \multicolumn{1}{c}{$\hat N_{\bar H}^{LC}$} & \multicolumn{1}{c}{$\hat N_{\bar H}^{LL}$}
+          & \multicolumn{1}{c}{$\hat N_H^{LC}$} & \multicolumn{1}{c}{$\hat N_{\bar H}^{LC}$} & \multicolumn{1}{c|}{$\hat N_{\bar H}^{LL}$} \\[3pt] \hline
+$beta(10,10)$ & BIAS  &-22.5&-14.8&14.0&-13.3&-6.9&12.5&-8.2&-4.7&11.5 \\
+$\bar{p}=0.500$ & S.E. &13.8&14.9&12.1&12.6&14.6&11.7&15.1&19.3&15.5 \\
+$cv=0.218$ & RMSE &26.4&21.0&18.5&18.3&16.2&17.1&17.2&19.9&19.3
+\\ \hline
+$beta(5,5)$ & BIAS &-32.2&-19.9&5.4&-21.9&-11.8&4.9&-15.6&-8.4&5.1 \\
+$\bar{p}=0.500$ & S.E. &15.8&16.2&12.3&14.3&19.8&12.9&16.4&19.8&14.6 \\
+$cv=0.302$ & RMSE &35.9&25.7&13.4&26.1&15.9&11.9&22.6&21.5&15.4
+\\ \hline
+$beta(4,8)$ & BIAS &-53.7&-29.1&-10.8&-42.0&-19.3&-8.4&-34.4&-13.9&-7.6 \\
+$\bar{p}=0.333$ & S.E. &20.8&19.4&18.1&18.5&18.8&15.6&19.2&20.6&16.4 \\
+$cv=0.392$ & RMSE &57.6&34.9&21.1&45.9&26.9&17.8&39.4&24.9&18.1
+\\ \hline
+$beta(3,5)$ & BIAS &-57.4&-32.4&-15.5&-45.6&-22.8&-13.1&-37.4&-17.1&-11.4 \\
+$\bar{p}=0.375$ & S.E. &21.2&19.9&17.1&18.9&18.8&15.0&19.6&21.6&15.6 \\
+$cv=0.430$ & RMSE &61.2&38.1&23.1&49.4&29.5&19.9&42.3&27.5&19.3
+\\ \hline
+\end{tabular}}
 \end{table}
 
-We now obtain finite sample efficiencies of the three DCMs as well as their depth-weighted affine equivariant counterparts by a simulation study, and compare them with the same from the SCM and Tyler's scatter matrix.
-We consider the same 6 elliptical distributions considered in ARE calculations above, and from every distribution draw 10000 samples each for sample sizes $n = 20, 50, 100, 300, 500$.
-All distributions are centered at ${\bf 0}_p$, and have covariance matrix $\Sigma = \diag(p,p-1,...1)$.
-We consider 3 choices of $p$: 2, 3 and 4.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\vskip 14pt
+\noindent {\large\bf Supplementary Materials}
 
-We use the concept of principal angles \citep{miao92} to find out error estimates for the first eigenvector of a scatter matrix. In our case, the first eigenvector will be
-%
-$$ \bfgamma_1 = (1,\overbrace{0,...,0}^{p-1})^T $$
-%
-For an estimate of the eigenvector, say $\hat\bfgamma_1$, error in prediction is measured by the smallest angle between the two lines, i.e.
-$ \cos^{-1} | \bfgamma_1^T \hat\bfgamma_1 | $.
-A smaller absolute value of this angle is equivalent to better prediction.
-We repeat this 10000 times and calculate the \textbf{Mean Squared Prediction Angle}:
-%
-$$ MSPA(\hat \bfgamma_1) = \frac{1}{10000} \sum_{m=1}^{10000} \left( \cos^{-1} \left|\bfgamma_1^T \hat\bfgamma^{(m)}_1 \right| \right)^2 $$
-%
-Finally, the finite sample efficiency of some eigenvector estimate $\hat\bfgamma^E_1$ relative to that obtained from the sample covariance matrix, say $\hat\bfgamma^{Cov}_1$ is obtained as:
-$$ FSE(\hat\bfgamma^E_1, \hat\bfgamma^{Cov}_1) = \frac{MSPA(\hat\bfgamma^{Cov}_1)}{MSPA(\hat\bfgamma^E_1)} $$
+Contain
+the brief description of the online supplementary materials.
+\par
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\vskip 14pt
+\noindent {\large\bf Acknowledgements}
 
-Tables \ref{table:FSEtable2}, \ref{table:FSEtable3} and \ref{table:FSEtable4} give FSE values for $p=2,3,4$, respectively.
-In general, all the efficiencies increase as the dimension $p$ goes up.
-DCM-based estimators (columns 3-5 in each table) outperform SCM and Tyler's scatter matrix, and among the 3 depths considered, projection depth seems to give the best results.
-Its finite sample performances are better than Tyler's and Huber's M-estimators of scatter as well as their symmetrized counterparts (see Table 4 in \cite{sirkia07}, and quite close to the affine equivariant spatial sign covariance matrix (see Table 2 in \cite{ollilia03}) For $p=2$, $n=300, 500$ the first 5 columns of Table \ref{table:FSEtable2} approximate the asymptotic efficiencies in Table \ref{table:AREtable} well, except for the multivariate $t$-distribution with df = 5.
-Finally, the depth-weighted iterated versions of these 3 SCMs (columns 6-8 in each table) seem to further better the performance of their corresponding orthogonal equivariant counterparts.
+Write the acknowledgements here.
+\par
 
-\begin{table}
-\begin{footnotesize}
-    \begin{tabular}{c|cc|ccc|ccc}
-    \hline
-    $F$ = Bivariate $t_5$    & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
-    $n$=20                   & 0.80 & 0.83  & 0.95   & 0.95   & 0.89  & 1.00    & 0.96    & 0.89   \\
-    $n$=50                   & 0.86 & 0.90  & 1.25   & 1.10   & 1.21  & 1.32    & 1.13    & 1.25   \\
-    $n$=100                  & 1.02 & 1.04  & 1.58   & 1.20   & 1.54  & 1.67    & 1.24    & 1.63   \\
-    $n$=300                  & 1.24 & 1.28  & 1.81   & 1.36   & 1.82  & 1.93    & 1.44    & 1.95   \\
-    $n$=500                  & 1.25 & 1.29  & 1.80   & 1.33   & 1.84  & 1.91    & 1.39    & 1.97   \\ \hline
-    $F$ = Bivariate $t_6$    & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
-    $n$=20                   & 0.77 & 0.79  & 0.92   & 0.92   & 0.86  & 0.96    & 0.92    & 0.85   \\
-    $n$=50                   & 0.76 & 0.78  & 1.11   & 1.00   & 1.08  & 1.17    & 1.03    & 1.13   \\
-    $n$=100                  & 0.78 & 0.79  & 1.27   & 1.06   & 1.33  & 1.35    & 1.11    & 1.41   \\
-    $n$=300                  & 0.88 & 0.91  & 1.29   & 1.09   & 1.35  & 1.38    & 1.15    & 1.45   \\
-    $n$=500                  & 0.93 & 0.96  & 1.37   & 1.13   & 1.40  & 1.44    & 1.19    & 1.48   \\ \hline
-    $F$ = Bivariate $t_{10}$ & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
-    $n$=20                   & 0.70 & 0.72  & 0.83   & 0.84   & 0.77  & 0.89    & 0.87    & 0.79   \\
-    $n$=50                   & 0.58 & 0.60  & 0.90   & 0.84   & 0.86  & 0.95    & 0.88    & 0.91   \\
-    $n$=100                  & 0.57 & 0.59  & 0.92   & 0.87   & 0.97  & 0.98    & 0.90    & 1.03   \\
-    $n$=300                  & 0.62 & 0.64  & 0.93   & 0.85   & 0.99  & 0.99    & 0.91    & 1.06   \\
-    $n$=500                  & 0.62 & 0.65  & 0.93   & 0.86   & 1.00  & 1.00    & 0.92    & 1.08   \\ \hline
-    $F$ = Bivariate $t_{15}$ & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
-    $n$=20                   & 0.63 & 0.66  & 0.76   & 0.78   & 0.72  & 0.81    & 0.81    & 0.73   \\
-    $n$=50                   & 0.52 & 0.52  & 0.79   & 0.75   & 0.80  & 0.84    & 0.79    & 0.85   \\
-    $n$=100                  & 0.51 & 0.52  & 0.83   & 0.77   & 0.88  & 0.88    & 0.81    & 0.94   \\
-    $n$=300                  & 0.55 & 0.56  & 0.84   & 0.79   & 0.91  & 0.89    & 0.84    & 0.98   \\
-    $n$=500                  & 0.56 & 0.59  & 0.85   & 0.80   & 0.93  & 0.91    & 0.86    & 0.99   \\ \hline
-    $F$ = Bivariate $t_{25}$ & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
-    $n$=20                   & 0.63 & 0.65  & 0.77   & 0.79   & 0.74  & 0.80    & 0.81    & 0.74   \\
-    $n$=50                   & 0.49 & 0.50  & 0.73   & 0.71   & 0.76  & 0.78    & 0.75    & 0.80   \\
-    $n$=100                  & 0.45 & 0.46  & 0.73   & 0.69   & 0.81  & 0.78    & 0.73    & 0.87   \\
-    $n$=300                  & 0.51 & 0.52  & 0.78   & 0.75   & 0.87  & 0.83    & 0.79    & 0.94   \\
-    $n$=500                  & 0.53 & 0.55  & 0.79   & 0.75   & 0.87  & 0.84    & 0.80    & 0.94   \\ \hline
-    $F$ = BVN                & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
-    $n$=20                   & 0.56 & 0.60  & 0.69   & 0.71   & 0.67  & 0.73    & 0.74    & 0.68   \\
-    $n$=50                   & 0.42 & 0.43  & 0.66   & 0.66   & 0.70  & 0.71    & 0.69    & 0.75   \\
-    $n$=100                  & 0.42 & 0.43  & 0.69   & 0.66   & 0.77  & 0.74    & 0.71    & 0.83   \\
-    $n$=300                  & 0.47 & 0.49  & 0.71   & 0.69   & 0.82  & 0.76    & 0.73    & 0.88   \\
-    $n$=500                  & 0.48 & 0.50  & 0.73   & 0.71   & 0.83  & 0.78    & 0.76    & 0.89   \\ \hline
-    \end{tabular}
-\end{footnotesize}
-\caption{Finite sample efficiencies of several scatter matrices: $p=2$}
-\label{table:FSEtable2}
-\end{table}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\markboth{\hfill{\footnotesize\rm FIRSTNAME1 LASTNAME1 AND FIRSTNAME2 LASTNAME2} \hfill}
+{\hfill {\footnotesize\rm FILL IN A SHORT RUNNING TITLE} \hfill}
 
-\begin{table}
-\begin{footnotesize}
-   \begin{tabular}{c|cc|ccc|ccc}
-    \hline
-    3-variate $t_5$    & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
-    $n$=20             & 0.96 & 0.97  & 1.06   & 1.03   & 0.99  & 1.07    & 1.06    & 0.97   \\
-    $n$=50             & 1.07 & 1.08  & 1.28   & 1.20   & 1.18  & 1.33    & 1.23    & 1.20   \\
-    $n$=100            & 1.12 & 1.15  & 1.49   & 1.31   & 1.40  & 1.57    & 1.38    & 1.48   \\
-    $n$=300            & 1.49 & 1.54  & 2.09   & 1.82   & 2.07  & 2.19    & 1.93    & 2.18   \\
-    $n$=500            & 1.60 & 1.66  & 2.18   & 1.87   & 2.21  & 2.27    & 1.95    & 2.30   \\ \hline
-    3-variate $t_6$    & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
-    $n$=20             & 0.90 & 0.92  & 1.00   & 0.99   & 0.95  & 1.02    & 1.01    & 0.94   \\
-    $n$=50             & 0.95 & 0.96  & 1.16   & 1.09   & 1.09  & 1.21    & 1.14    & 1.11   \\
-    $n$=100            & 0.98 & 0.99  & 1.32   & 1.22   & 1.25  & 1.38    & 1.27    & 1.29   \\
-    $n$=300            & 1.10 & 1.14  & 1.57   & 1.40   & 1.58  & 1.62    & 1.47    & 1.64   \\
-    $n$=500            & 1.17 & 1.20  & 1.57   & 1.43   & 1.60  & 1.63    & 1.51    & 1.67   \\ \hline
-    3-variate $t_{10}$ & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
-    $n$=20             & 0.87 & 0.88  & 0.95   & 0.94   & 0.90  & 0.97    & 0.98    & 0.89   \\
-    $n$=50             & 0.77 & 0.79  & 0.96   & 0.92   & 0.94  & 0.99    & 0.96    & 0.95   \\
-    $n$=100            & 0.75 & 0.76  & 1.02   & 0.95   & 1.01  & 1.06    & 1.00    & 1.05   \\
-    $n$=300            & 0.73 & 0.75  & 1.03   & 0.98   & 1.10  & 1.08    & 1.03    & 1.15   \\
-    $n$=500            & 0.73 & 0.76  & 1.02   & 0.98   & 1.09  & 1.06    & 1.02    & 1.14   \\ \hline
-    3-variate $t_{15}$ & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
-    $n$=20             & 0.84 & 0.86  & 0.92   & 0.92   & 0.89  & 0.94    & 0.94    & 0.87   \\
-    $n$=50             & 0.75 & 0.76  & 0.92   & 0.90   & 0.90  & 0.96    & 0.94    & 0.93   \\
-    $n$=100            & 0.66 & 0.67  & 0.91   & 0.87   & 0.95  & 0.96    & 0.92    & 1.00   \\
-    $n$=300            & 0.61 & 0.64  & 0.90   & 0.87   & 1.00  & 0.93    & 0.91    & 1.04   \\
-    $n$=500            & 0.65 & 0.67  & 0.89   & 0.87   & 0.99  & 0.93    & 0.91    & 1.03   \\ \hline
-    3-variate $t_{25}$ & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
-    $n$=20             & 0.78 & 0.79  & 0.87   & 0.89   & 0.87  & 0.89    & 0.92    & 0.86   \\
-    $n$=50             & 0.70 & 0.71  & 0.88   & 0.86   & 0.88  & 0.91    & 0.90    & 0.90   \\
-    $n$=100            & 0.61 & 0.63  & 0.86   & 0.83   & 0.89  & 0.90    & 0.88    & 0.94   \\
-    $n$=300            & 0.58 & 0.59  & 0.83   & 0.80   & 0.92  & 0.87    & 0.85    & 0.98   \\
-    $n$=500            & 0.62 & 0.64  & 0.83   & 0.82   & 0.94  & 0.88    & 0.87    & 0.99   \\ \hline
-    3-variate Normal   & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
-    $n$=20             & 0.76 & 0.78  & 0.85   & 0.87   & 0.84  & 0.87    & 0.90    & 0.83   \\
-    $n$=50             & 0.66 & 0.67  & 0.82   & 0.81   & 0.84  & 0.86    & 0.86    & 0.86   \\
-    $n$=100            & 0.56 & 0.58  & 0.77   & 0.75   & 0.83  & 0.82    & 0.79    & 0.87   \\
-    $n$=300            & 0.53 & 0.55  & 0.75   & 0.74   & 0.85  & 0.79    & 0.78    & 0.90   \\
-    $n$=500            & 0.56 & 0.58  & 0.76   & 0.76   & 0.87  & 0.80    & 0.80    & 0.92   \\ \hline
-    \end{tabular}
-\end{footnotesize}
-\caption{Finite sample efficiencies of several scatter matrices: $p=3$}
-\label{table:FSEtable3}
-\end{table}
-
-\begin{table}
-\begin{footnotesize}
-    \begin{tabular}{c|cc|ccc|ccc}
-    \hline
-    4-variate $t_5$    & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
-    $n$=20             & 1.04 & 1.02  & 1.10   & 1.07   & 1.02  & 1.09    & 1.07    & 0.98   \\
-    $n$=50             & 1.08 & 1.08  & 1.16   & 1.16   & 1.13  & 1.19    & 1.19    & 1.13   \\
-    $n$=100            & 1.31 & 1.31  & 1.42   & 1.38   & 1.36  & 1.46    & 1.44    & 1.36   \\
-    $n$=300            & 1.46 & 1.54  & 1.81   & 1.76   & 1.95  & 1.88    & 1.88    & 1.95   \\
-    $n$=500            & 1.92 & 1.93  & 2.23   & 2.03   & 2.31  & 2.35    & 2.19    & 2.39   \\ \hline
-    4-variate $t_6$    & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
-    $n$=20             & 1.00 & 1.05  & 1.03   & 1.05   & 1.00  & 1.04    & 1.04    & 0.95   \\
-    $n$=50             & 1.03 & 1.01  & 1.13   & 1.12   & 1.11  & 1.19    & 1.17    & 1.10   \\
-    $n$=100            & 1.08 & 1.12  & 1.25   & 1.23   & 1.27  & 1.24    & 1.25    & 1.22   \\
-    $n$=300            & 1.34 & 1.36  & 1.64   & 1.52   & 1.60  & 1.67    & 1.61    & 1.68   \\
-    $n$=500            & 1.26 & 1.34  & 1.55   & 1.49   & 1.60  & 1.65    & 1.61    & 1.69   \\ \hline
-    4-variate $t_{10}$ & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
-    $n$=20             & 0.90 & 0.89  & 0.95   & 0.98   & 0.98  & 0.96    & 1.01    & 0.95   \\
-    $n$=50             & 0.90 & 0.91  & 1.01   & 0.98   & 0.98  & 1.03    & 1.04    & 0.99   \\
-    $n$=100            & 0.87 & 0.87  & 0.93   & 0.95   & 1.01  & 0.99    & 1.01    & 1.05   \\
-    $n$=300            & 0.87 & 0.87  & 1.09   & 1.09   & 1.17  & 1.14    & 1.16    & 1.23   \\
-    $n$=500            & 0.88 & 0.92  & 1.10   & 1.10   & 1.23  & 1.19    & 1.22    & 1.29   \\ \hline
-    4-variate $t_{15}$ & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
-    $n$=20             & 0.92 & 0.90  & 0.94   & 0.94   & 0.96  & 0.95    & 0.97    & 0.89   \\
-    $n$=50             & 0.82 & 0.83  & 0.88   & 0.91   & 0.93  & 0.88    & 0.93    & 0.93   \\
-    $n$=100            & 0.84 & 0.87  & 0.92   & 0.95   & 1.00  & 0.93    & 0.96    & 1.00   \\
-    $n$=300            & 0.73 & 0.75  & 0.96   & 0.99   & 1.10  & 1.00    & 1.06    & 1.12   \\
-    $n$=500            & 0.73 & 0.76  & 0.95   & 0.96   & 1.06  & 0.94    & 0.97    & 1.06   \\ \hline
-    4-variate $t_{25}$ & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
-    $n$=20             & 0.89 & 0.92  & 0.92   & 0.92   & 0.90  & 0.96    & 0.95    & 0.89   \\
-    $n$=50             & 0.82 & 0.84  & 0.89   & 0.90   & 0.91  & 0.93    & 0.96    & 0.92   \\
-    $n$=100            & 0.77 & 0.76  & 0.90   & 0.90   & 0.96  & 0.94    & 0.98    & 1.04   \\
-    $n$=300            & 0.73 & 0.77  & 0.93   & 0.91   & 0.98  & 1.00    & 0.98    & 1.03   \\
-    $n$=500            & 0.67 & 0.71  & 0.83   & 0.83   & 0.96  & 0.88    & 0.90    & 1.00   \\ \hline
-    4-variate Normal   & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
-    $n$=20             & 0.82 & 0.84  & 0.87   & 0.90   & 0.91  & 0.89    & 0.93    & 0.89   \\
-    $n$=50             & 0.80 & 0.81  & 0.87   & 0.88   & 0.88  & 0.88    & 0.92    & 0.88   \\
-    $n$=100            & 0.68 & 0.71  & 0.80   & 0.85   & 0.91  & 0.82    & 0.86    & 0.92   \\
-    $n$=300            & 0.61 & 0.63  & 0.82   & 0.85   & 0.93  & 0.86    & 0.91    & 0.96   \\
-    $n$=500            & 0.60 & 0.64  & 0.77   & 0.80   & 0.90  & 0.82    & 0.86    & 0.96   \\ \hline
-    \end{tabular}
-\end{footnotesize}
-\caption{Finite sample efficiencies of several scatter matrices: $p=4$}
-\label{table:FSEtable4}
-\end{table}
-
-\section{Examples in real data analysis}\label{section:sec6}
-%\subsection{Communities and crime data}
-%This data is from the UCI machine learning repository [], and consists information on 101 demographic and socio-economic variables (like population, racial percentages, percentage of people living in urbal areas etc.)  in 1994 community areas in the United States.
-The dataset is a combination of data from the 1990 US Census, 1990 US Law Enforcement Management and Administrative Statistics survey and 1995 FBI Uniform Crime Reporting data.
-%
-%With the goal of building a model for the total number of violent crimes per 100K population from others, we initially do normal and depth-based PCA on the other variables.
-While doing the depth-based PCA, we use projection depth as our chosen depth function.
-After obtaining the PCA models, we take the first $k$ PCs in each case and build linear models for both the methods.
-This is repeated for $k = 1,2,...,100$ and the $R^2$ values on principal components regression models of the two types are plotted in Figure \ref{fig:rsqplot}.
-For building linear regression models, we keep all the predictors unchanged, while go for an inverse cubic transformation on the response variable.
-We do this since boxcox transformations on all of the models we consider suggest optimal power transformations of values close to --3.
-%
-%From the screeplots in \ref{fig:screeplot} we see that both the methods explain similar amounts of variances in the leading few PCs.
-As for the model performances, linear regressions based on depth-PCA have slightly higher $R^2$ values when the top few (upto 10) principal components are used.
-At around 20 PCs the two models have same $R^2$ values and the normal PC-regression models perform slightly better after that.
-%
-%\begin{figure}[t]
-%	\captionsetup{singlelinecheck=off}
-%	\centering
-%		\includegraphics[height=5cm]{../Codes/crime_screeplots.png}
-%	\caption{(Left) Screeplots for two types of PCA on communities data}
-%	\label{fig:screeplot}
-%\end{figure}
-%
-%\begin{figure}[t]
-%	\captionsetup{singlelinecheck=off}
-%	\centering
-%		\includegraphics[height=7cm]{../Codes/crime_Rsq_plot.png}
-%	\caption{(Left) Change of $R^2$ values for normal and depth-based principal components regression models on communities data}
-%	\label{fig:rsqplot}
-%\end{figure}
-
-\subsection{Bus data}
-This dataset is available in the R package \texttt{rrcov}, and consists of data on images of 218 buses.
-The 18 variables here correspond to several features related to these images.
-Here we extend upon the analysis in \cite{maronna06}, pp.
-213 to compare the classical PCA and 3 different methods of robust PCA (including that using SCM) with our DCM-based method.
-Similar to the original analysis, we set aside variable 9 and scale the other variables by dividing with their respective median absolute deviations (MAD).
-This is done because all the variables had much larger standard deviations compared to their MADs, and variable 9 had MAD = 0.
-
-For the sake of uniformity, we use projection depth as our fixed depth function while doing depth-based PCA in our data analysis examples.
-We compare the outputs of classical (CPCA) and depth-based PCA (DPCA) with the following 3 robust methods: Spherical PCA, i.e.
-PCA based on the SCM (SPCA), PCs obtained by the ROBPCA algorithm \citep{hubert05}, and the Minimum Covariance Determinant (MCD) estimator \citep{Rousseeuw84leastmedian} (MPCA).
-Table \ref{table:bus_table1} gives the proportions of variability that are left unexplained after the top $q$ $(= 1,...,6)$ components are taken into account in each of the 5 methods.
-The first PC in classical PCA seems to explain a much higher proportion of variability in original data than robust methods.
-However, as noted in \cite{maronna06} and \cite{hubert05}, this is a result of the classical variances being inflated due to outliers in the direction of the first principal axis.
-Among the robust methods, the proportions of unexplained variances are highest for DCM-based PCA for all values of $q$.
-
-Table \ref{table:bus_table2} demonstrates why robust methods actually give a better representation of the underlying data structure than classical PCA here.
-Each of its column lists different quantiles of the squared orthogonal distance for a sample point from the hyperplane formed by top 3 PCs estimated by the corresponding method.
-For PCA based on projection-DCM, the estimated principal component subspaces are closer to the data than CPCA for more than 90\% of samples, and the distance only becomes larger for higher quantiles.
-This means that for CPCA, estimated basis vectors of the hyperspace get pulled by extreme outlying points, while the influence of these outliers is very low for DPCA.
-SPCA and ROBPCA perform very closely in this respect, the percentage of points that have less squared distance than CPCA being between 80\% and 90\% for both of them.
-This percentage is only 50\% for MPCA, which suggests that the corresponding 3-dimensional subspace estimated by MCD is possibly not an accurate representation of the truth.
-
-\begin{table}[t]
-\centering
-    \begin{tabular}{c|ccccc}
-    \hline
-    \begin{large} $q$ \end{large} & \multicolumn{5}{c}{Method of PCA}         \\ \cline{2-6}
-    ~                   & CPCA     & SPCA & ROBPCA & MPCA & DPCA \\\hline 
-    1                   & 0.188         & 0.549     & 0.410  & 0.514     & 0.662     \\
-    2                   & 0.084         & 0.272     & 0.214  & 0.337     & 0.359     \\
-    3                   & 0.044         & 0.182     & 0.121  & 0.227     & 0.237     \\
-    4                   & 0.026         & 0.135     & 0.083  & 0.154     & 0.173     \\
-    5                   & 0.018         & 0.099     & 0.054  & 0.098     & 0.115     \\
-    6                   & 0.012         & 0.069     & 0.036  & 0.070     & 0.084     \\ \hline
-    \end{tabular}
-    \caption{Unexplained proportions of variability by PCA models with $q$ components for bus data}
-    \label{table:bus_table1}
-\end{table}
-
-\begin{table}[t]
-\centering
-    \begin{tabular}{c|ccccc}
-    \hline
-    Quantile & \multicolumn{5}{c}{Method of PCA}         \\ \cline{2-6}
-    ~                   & CPCA     & SPCA & ROBPCA & MPCA & DPCA \\\hline 
-    10\%      & 1.9       & 1.2       & 1.2    & 1.0       & 1.2       \\
-    20\%      & 2.3       & 1.6       & 1.6    & 1.3       & 1.6       \\
-    30\%      & 2.8       & 1.8       & 1.8    & 1.7       & 1.9       \\
-    40\%      & 3.2       & 2.2       & 2.1    & 2.1       & 2.3       \\
-    50\%      & 3.7       & 2.6       & 2.5    & 3.1       & 2.6       \\
-    60\%      & 4.4       & 3.1       & 3.0    & 5.9       & 3.2       \\
-    70\%      & 5.4       & 3.8       & 3.9    & 25.1      & 3.9       \\
-    80\%      & 6.5       & 5.2       & 4.8    & 86.1      & 4.8       \\
-    90\%      & 8.2       & 9.0       & 10.9   & 298.2     & 6.9      \\
-    Max       & 24        & 1037      & 1055   & 1037      & 980      \\\hline
-    \end{tabular}
-    \caption{Quantiles to squared distance from 3-principal component hyperplanes for bus data}
-    \label{table:bus_table2}
-\end{table}
-
-\subsection{Octane data}
-We now apply our method to a high-dimensional dataset and demonstrate its effectiveness in outlier detection.
-Due to \cite{esbensen94}, this dataset consists of 226 variables and 39 observations.
-Each observation is a gasoline sample with a certain octane number, and have their NIR absorbance spectra measured in 2 nm intervals between 1100 - 1550 nm.
-There are 6 outliers here: compounds 25, 26 and 36-39, which contain alcohol.
-Proportions of \textit{explained} variability by PCs obtained by the two methods are given in Figure \ref{fig:screeplot}.
-Once again, the first PC in CPCA explains a much larger proportion of variance than DPCA.
-Second and third PCs obtained by DPCA explain higher proportions of variability than the corresponding components in CPCA.
-
-In both methods, the first two PCs explains a large amount (98\% for CPCA, 89\% for DPCA) of underlying variability.
-But in DPCA, these PCs are more effective in detecting outliers, which we demonstrate in Figure \ref{fig:distplot}.
-For any method of PCA with $k$ components on a dataset of $n$ observations and $p$ variables, the \textbf{score distance} (SD) and \textbf{orthogonal distance} (OD) for $i^\text{th}$ observation ($i=1,2,...,n$) are defined as:
-$$ SD_i = \sqrt{ \sum_{j=1}^k \frac{s^2_{ij}}{\lambda_j}}; \quad OD_i = \| \bfx_i - P\bfs_i^T \| $$
-where $S = (\bfs_1, \ldots ,\bfs_n)^T$ is the $n\times k$ scoring matrix, $P$ the $p\times k$ loading matrix, and $\lambda_1,\ldots ,\lambda_k$ are eigenvalues obtained from the PCA, and $\bfx_1,\ldots,\bfx_n$ are the $n$ observation vectors.
-We only consider the first 2 PCs here, so $k$ is set to 2.
-From a practical standpoint, $SD_i$ can be interpreted as a weighted norm of the projection of the $i^\text{th}$ point on the hyperplane formed by first $k$ principal components, and $OD_i$ the orthogonal distance of point $i$ from that hyperplane.
-For outlier detection, following \cite{hubert05} we set the upper cutoff values for score distances at $\sqrt{\chi^2_{2,.975}}$ and orthogonal distances at $[\text{median}(OD^{2/3}) + \text{MAD}(OD^{2/3})\Phi^{-1}(0.975)]^{3/2}$, where $\Phi(.)$ is the standard normal cumulative distribution function.
-These cutoffs are marked by red lines in the diagnostic plots in figure \ref{fig:distplot}.
-In the figure we see that CPCA detects only 1 of the 6 outliers (point 26, left panel).
-Compared to this the diagnostic plot corresponding to DPCA in the right panel correctly detects all 6 outlying points.
-All of them have larger score distances than the score cutoff value, while points 25, 26 and 38 have higher-than-cutoff orthogonal distances as well.
-Interestingly, the arrangement of outlying points here is similar to that in the diagnostic plot corresponding to ROBPCA, which can be found in figure 5(b) of \cite{hubert05}.
-
-\begin{figure}[t]
-	\centering
-		\includegraphics[height=6cm]{../Codes/octane_screeplot.pdf}
-	\caption{Explained variance proportions for two types of PCA on octane data}
-	\label{fig:screeplot}
-\end{figure}
-\begin{figure}[t]
-	\centering
-		\includegraphics[height=6.5cm]{../Codes/octane_distanceplot.pdf}
-	\caption{Distance plots for two types of PCA on octane data}
-	\label{fig:distplot}
-\end{figure}
-
-\section{Conclusion}\label{section:sec7}
-
-In the above sections we introduce a covariance matrix based on depth-based multivariate ranks that keeps the eigenvectors of the actual population unchanged for elliptical distributions.
-We provide asymptotic results for the sample DCM, its eigenvalues and eigenvectors.
-Bounded influence functions as well as simulation studies suggest that the eigenvector estimates obtained from the DCM are highly robust, yet do not lose much in terms of efficiency.
-Thus it provides a plausible alternative to existing approaches of robust PCA that are based on estimation of covariance matrices (for example SCM, Tyler's scatter matrix, D\"{u}mbgen's symmetrized shape matrix).
-
-An immediate extension of this would be to study the depth-weighted iterated scatter matrices, i.e. matrices $\Sigma_{Dw}$ that are solution to the following type of equations:
-
-$$ \Sigma_{Dw} = E \left[ \frac{(\tilde D_\bfX(\bfx))^2 (\bfx - \bfmu) (\bfx - \bfmu)^T}{(\bfx - \bfmu)^T \Sigma_{Dw}^{-1} (\bfx - \bfmu)} \right] $$
-as their eigenvector estimates seem to have better efficiency than those obtained from the corresponding DCMs.
-Unlike the DCM, these matrices will possess the affine equivariance property.
-It is possible to develop tests for central and elliptic symmetry based on the decomposition of the multivariate rank vector in equation \ref{equation:rankdecomp}.
-The result in Theorem \ref{Theorem:covform} is based on the fact that $E(\tilde \bfX) = \bf0$, and it holds for any centrally symmetric underlying distribution.
-Moreover, the depth of a point in the standardized scale (i.e.
-$\bfz$-scale) does not depend on the direction of $\bfz$.
-This is not possible without circular symmetry of $\bfz$, so any test of independence between $D_\bfZ (\bfz)$ and $\bfS (\bfz)$ can be seen as a test of ellipticity for the original random variable $\bfX$.
-Finally the applicability of this procedure in high-dimensional and functional data remains to be explored.
-
-\appendix
-\section*{Appendix}
-\numberwithin{equation}{section}
-\section{\textbf{Form of $V_{D,S}(F)$}}\label{section:appA}
-
-First observe that for $F$ having covariance matrix $\Sigma = \Gamma\Lambda\Gamma^T$,
-%
-$$ V_{D,S}(F)  = (\Gamma \otimes \Gamma) V_{D,S}(F_\Lambda) (\Gamma \otimes \Gamma)^T$$
-%
-where $F_\Lambda$ has the same elliptic distribution as $F$, but with covariance matrix $\Lambda$. Now,
-%
-\begin{eqnarray*}
-V_{D,S} (F_\Lambda) &=& E \left[ vec \left\{ \frac{(\tilde D_\bfZ (\bfz))^2 \Lambda^{1/2} \bfz\bfz^T \Lambda^{1/2}}{\bfz^T\Lambda\bfz} - \Lambda_{D,S} \right\} vec^T \left\{ \frac{(\tilde D_\bfZ (\bfz))^2 \Lambda^{1/2} \bfz\bfz^T \Lambda^{1/2}}{\bfz^T\Lambda\bfz} - \Lambda_{D,S} \right\} \right]\\
-&=& E \left[ vec \left\{ (\tilde D_\bfZ (\bfz))^2 SS(\Lambda^{1/2}\bfz; \bf0) \right\} vec^T \left\{ (\tilde D_\bfZ (\bfz))^2 SS(\Lambda^{1/2}\bfz; \bf0) \right\} \right]\\
-&& - \quad vec(\Lambda_{D,S}) vec^T(\Lambda_{D,S})
-\end{eqnarray*}
-
-The matrix $vec(\Lambda_{D,S}) vec^T(\Lambda_{D,S})$ consists of elements $\lambda_i\lambda_j$ at $(i,j)^\text{th}$ position of the $(i,j)^\text{th}$ block, and 0 otherwise.
-These positions correspond to variance and covariance components of on-diagonal elements.
-For the expectation matrix, all its elements are of the form $E[\sqrt{\lambda_a \lambda_b \lambda_c \lambda_d} z_a z_b z_c z_d .
-(\tilde D_\bfZ (\bfz))^4 / (\bfz^T \Lambda \bfz)^2]$, with $1 \leq a,b,c,d \leq p$.
-Since $(\tilde D_\bfZ (\bfz))^4 / (\bfz^T \Lambda \bfz)^2$ is even in $\bfz$, which has a circularly symmetric distribution, all such expectations will be 0 unless $a=b=c=d$, or they are pairwise equal.
-Following a similar derivation for spatial sign covariance matrices in \cite{magyar14}, we collect the non-zero elements and write the matrix of expectations:
-%
-$$ (I_{p^2} + K_{p,p}) \left\{ \sum_{a=1}^p \sum_{b=1}^p \gamma^D_{ab} (\bfe_a \bfe_a^T \otimes  \bfe_b \bfe_b^T) - \sum_{a=1}^p \gamma^D_{aa} (\bfe_a \bfe_a^T \otimes  \bfe_a \bfe_a^T) \right\} + \sum_{a=1}^p \sum_{b=1}^p \gamma^D_{ab} (\bfe_a \bfe_b^T \otimes  \bfe_a \bfe_b^T) $$
-%
-where $I_k = (\bfe_1,...,\bfe_k), K_{m,n} = \sum_{i=1}^m \sum_{j=1}^n J_{ij} \otimes J_{ij}^T$ with $J_{ij}$ the $m \times n$ matrix having 1 as $(i,j)^\text{th}$ element and 0 elsewhere, and $\gamma^D_{mn} = E[ \lambda_m \lambda_n z_m^2 z_n ^2 .
-(\tilde D_\bfZ (\bfz))^4 / (\bfz^T \Lambda \bfz)^2]; 1 \leq m,n \leq p$.
-
-\paragraph{}Putting everything together, denote $\hat S^D(F_\Lambda) = \sum_{i=1}^n (\tilde D^n_\bfZ (\bfz_i))^2 SS(\Lambda^{1/2}\bfz_i; \hat \bfmu_n)/n $.
-Then the different types of elements in the matrix $V_{D,S}(F_\Lambda)$ are as given below ($1 \leq a,b,c,d \leq p$):
-
-\begin{itemize}
-\item Variance of on-diagonal elements
-%
-$$ AVar( \sqrt n \hat S^D_{aa} (F_\Lambda)) = E \left[ \frac{(\tilde D_\bfZ (\bfz))^4 \lambda_a^2 z_a^4}{(\bfz^T \Lambda \bfz)^2} \right] - \lambda_{D,S,a}^2 $$
-
-\item Variance of off-diagonal elements ($a \neq b$)
-%
-$$ AVar( \sqrt n \hat S^D_{ab} (F_\Lambda)) = E \left[ \frac{(\tilde D_\bfZ (\bfz))^4 \lambda_a \lambda_b z_a^2 z_b^2}{(\bfz^T \Lambda \bfz)^2} \right] $$
-
-\item Covariance of two on-diagonal elements ($a \neq b$)
-%
-$$ ACov(\sqrt n \hat S^D_{aa} (F_\Lambda), \sqrt n \hat S^D_{bb} (F_\Lambda))
-= E \left[ \frac{(\tilde D_\bfZ (\bfz))^4 \lambda_a \lambda_b z_a^2 z_b^2}{(\bfz^T \Lambda \bfz)^2} \right] - \lambda_{D,S,a} \lambda_{D,S,b} $$
-
-\item Covariance of two off-diagonal elements ($a \neq b \neq c \neq d$)
-%
-$$ ACov(\sqrt n \hat S^D_{ab} (F_\Lambda), \sqrt n \hat S^D_{cd} (F_\Lambda)) = 0 $$
-
-\item Covariance of one off-diagonal and one on-diagonal element ($a \neq b \neq c$)
-%
-$$ ACov(\sqrt n \hat S^D_{ab} (F_\Lambda), \sqrt n \hat S^D_{cc} (F_\Lambda)) = 0 $$
-\end{itemize}
-
-\section{Proofs}\label{section:appB}
-
-\begin{proof}[Proof of Theorem  \ref{Theorem:covform}]
-The proof follows directly from writing out the expression of $Cov ( \tilde \bfX)$:
-%
-\begin{eqnarray*}
-Cov(\tilde\bfX) &=& E(\tilde\bfX \tilde\bfX^T) - E(\tilde\bfX) E(\tilde\bfX)^T\\
-&=& \Gamma . E \left[ (\tilde D_\bfZ(\bfz))^2 \frac{\|\bfz\|^2}{\| \Lambda^{1/2}\bfz\|} \Lambda^{1/2} \bfS(\bfz) \bfS(\bfz)^T \Lambda^{1/2} \right] \Gamma^T - {\bf 0}_p {\bf 0}_p^T\\
-&=& \Gamma .E \left[ (\tilde D_\bfZ(\bfz))^2 \frac{\Lambda^{1/2} \bfz \bfz^T \Lambda^{1/2}}{\bfz^T \Lambda \bfz} \right] \Gamma^T
-\end{eqnarray*}
-%
-\end{proof}
-
-\begin{proof}[Proof of Lemma \ref{Lemma:lemma1}]
-For two positive definite matrices $A,B$, we denote by $A>B$ that $A-B$ is positive definite. Also, denote
-%
-$$ S_n = \sqrt n \left[ \frac{1}{n} \sum_{i=1}^n \left| (\tilde D^{n} _\bfX (\bfx_i))^2  - (\tilde D_\bfX (\bfx_i))^2 \right| SS(\bfx_i; \hat\bfmu_n) \right] $$
-%
-%Consider now the quantity $\bft^T S_n \bft$, where $\bft \in \mathbb{R}^p$. Now applying Cauchy-Schwarz inequality we shall have
-%%
-%\begin{eqnarray}\label{eqn:AppEqn1}
-%\frac{(\bft^T S_n \bft)^2}{n} & = & \left[ \frac{1}{n} \sum_{i=1}^n \left| (\tilde D^{n} _\bfX (\bfx_i))^2  - (\tilde D_\bfX (\bfx_i))^2 \right|^2  \bft^T SS(\bfx_i; \hat\bfmu_n) \bft \right]^2 \notag\\
-%& \leq & \left[ \frac{1}{n} \sum_{i=1}^n \left| (\tilde D^{n} _\bfX (\bfx_i))^2  - (\tilde D_\bfX (\bfx_i))^2 \right|^2 \right] \left[ \frac{1}{n} \left( \sqrt n.\frac{1}{n} \sum_{i=1}^n  SS(\bfx, \hat\bfmu_n) \right) \right]
-%\end{eqnarray}
-%%
-%with $\hat S_n = \sum_{i=1}^n SS(\bfx_i, \hat\bfmu_n)/ \sqrt n$.
-Now due to the assumption of uniform convergence, given $\epsilon>0$ we can find $N \in \mathbb{N}$ such that
-%
-\begin{equation}
-\label{equation:lemma1eq}
-| (\tilde D^{n_1}_\bfX(\bfx_i))^2 - (\tilde D_\bfX(\bfx_i))^2 | < \epsilon
-\end{equation}
-%
-for all $n_1 \geq N; i = 1,2,...,n_1$. This implies
-%
-\begin{eqnarray}
-\label{eqn:lemma1eq2}
-S_{n_1} &< & \epsilon \sqrt{n_1} \left[ \frac{1}{n_1} \sum_{i=1}^{n_1} SS(\bfx_i; \hat\bfmu_{n_1}) \right]\notag\\
-&=& \epsilon \sqrt{n_1} \left[ \frac{1}{n_1} \sum_{i=1}^{n_1} \left\{ SS(\bfx_i; \hat\bfmu_{n_1}) - SS(\bfx_i; \bfmu) \right\} + \frac{1}{n_1} \sum_{i=1}^{n_1} SS(\bfx_i; \bfmu) \right]
-\end{eqnarray}
-
-We now construct a sequence of positive definite matrices $\{A_k (B_k+C_k) : k \in \mathbb N\} $ so that
-%
-$$ A_k = \frac{1}{k}, \quad B_k = \sqrt{N_k} \left[ \frac{1}{N_k} \sum_{i=1}^{N_k} \left\{ SS(\bfx_i; \hat\bfmu_{N_k}) - SS(\bfx_i; \bfmu) \right\} \right]$$
-$$\quad C_k = \sqrt{N_k} \left[ \frac{1}{N_k} \sum_{i=1}^{N_k} SS(\bfx_i; \bfmu) \right] $$
-%
-where $N_k \in \mathbb N$ gives the relation (\ref{equation:lemma1eq}) in place of $N$ when we take $\epsilon = 1/k$.
-Under conditions $ E\|\bfx - \bfmu\|^{-3/2} < \infty $ and $\sqrt n (\hat\bfmu_n - \bfmu) = O_P(1)$, the sample SCM with unknown location parameter $\hat\bfmu_n$ has the same asymptotic distribution as the SCM with known location $\bfmu$ \citep{durre14}, hence $B_k = o_P(1)$, thus $A_k (B_k+C_k) \stackrel{P}{\rightarrow} 0$.
-
-Now (\ref{eqn:lemma1eq2}) implies that for any $\epsilon_1 > 0$, $S_{N_k} > \epsilon_1 \Rightarrow A_k (B_k + C_k) > \epsilon_1$, which means $ P(S_{N_k} > \epsilon_1) < P(A_k (B_k + C_k) > \epsilon_1)$.
-Hence the subsequence $\{S_{N_k}\} \stackrel{P}{\rightarrow} 0$.
-Since the main sequence $\{S_k\}$ is bounded below by 0, this implies $\{S_k\} \stackrel{P}{\rightarrow} 0$.
-Finally, we have that
-%
-\begin{eqnarray}
-\sqrt n \left[
-\frac{1}{n} \sum_{i=1}^n (\tilde D^n_\bfX (\bfx_i))^2 SS(\bfx_i; \hat\bfmu_n) -
-\frac{1}{n} \sum_{i=1}^n (\tilde D_\bfX (\bfx_i))^2 SS(\bfx_i; \bfmu) \right] &\leq & \hspace{1em} \notag\\
-S_n +  \sqrt{n} \left[ \frac{1}{n} \sum_{i=1}^{n} \left\{ SS(\bfx_i; \hat\bfmu_{n}) - SS(\bfx_i; \bfmu) \right\} \right] &&
-\end{eqnarray}
-%
-Since the second summand on the right hand side is $o_P(1)$ due to \cite{durre14} as mentioned before, we have the needed.
-\end{proof}
-
-\begin{proof}[Proof of Theorem \ref{Theorem:rootn}]
-The quantity in the statement of the theorem can be broken down as:
-%
-\begin{eqnarray*}
-\sqrt n \left[ vec\left\{ \frac{1}{n} \sum_{i=1}^n (\tilde D^n_\bfX (\bfx_i))^2 SS(\bfx_i; \hat\bfmu_n) \right\} - vec\left\{ \frac{1}{n} \sum_{i=1}^n (\tilde D_\bfX (\bfx_i))^2 SS(\bfx_i; \bfmu) \right\} \right] +\\
-\sqrt n \left[ vec\left\{ \frac{1}{n} \sum_{i=1}^n (\tilde D_\bfX (\bfx_i))^2 SS(\bfx_i; \bfmu) \right\} - E \left[ vec\left\{ (\tilde D_\bfX (\bfx))^2 SS(\bfx; \bfmu) \right\} \right] \right]
-\end{eqnarray*}
-%
-The first part goes to 0 in probability by Lemma \ref{Lemma:lemma1}, and applying Slutsky's theorem we get the required convergence.
-\end{proof}
-
-\begin{proof}[Proof of Theorem \ref{Theorem:decomp}]
-See \cite{taskinen12}
-\end{proof}
-
-\begin{proof}[Proof of Corollary \ref{Corollary:eigendist}]
-In spirit, this corollary is similar to Theorem 13.5.1 in \cite{anderson}, and indeed, \cite{taskinen12} used this theorem to prove Theorem \ref{Theorem:decomp}.
-Due to the decomposition (\ref{equation:decompEq}) we have, for the distribution $F_\Lambda$, the following relation between any off-diagonal element of $\hat S^D(F_\Lambda)$ and the corresponding element in the estimate of eigenvectors $\hat\Gamma_D (F_\Lambda)$:
-
-$$ \sqrt n \hat\gamma_{D,ij} (F_\Lambda) = \sqrt n \frac{\hat S^D_{ij} (F_\Lambda)}{\lambda_{D,S,i} - \lambda_{D,S,j}}; \quad i \neq j$$
-
-So that for eigenvector estimates of the original $F$ we have
-
-\begin{equation} \label{equation:app1}
-\sqrt n (\hat\bfgamma_{D,i} - \bfgamma_i) = \sqrt n \Gamma (\hat \bfgamma_{D,i}(F_\Lambda) - \bfe_i ) = \sqrt n \left[ \sum_{k=1; k \neq i}^p \hat \gamma_{D,ik}(F_\Lambda)\bfgamma_k + (\hat \gamma_{D,ii}(F_\Lambda) - 1)\bfgamma_i \right]
-\end{equation}
-
-$\sqrt n (\hat \gamma_{D,ii}(F_\Lambda) - 1) =  o_P(1)$ and $ACov(\sqrt n \hat S^D_{ik}(F_\Lambda), \sqrt n \hat S^D_{il}(F_\Lambda)) = 0$ for $k \neq l$, so the above equation implies
-
-$$ AVar(\bfg_i) = AVar (\sqrt n (\hat\bfgamma_{D,i} - \bfgamma_i)) = \sum_{k=1; k \neq i}^p \frac{AVar(\sqrt n \hat S^D_{ik}(F_\Lambda))}{(\lambda_{D,s,i} - \lambda_{D,S,k})^2} \bfgamma_k \bfgamma_k^T $$
-
-For the covariance terms, from (\ref{equation:app1}) we get, for $i \neq j$,
-
-\begin{eqnarray*}
-ACov(\bfg_i, \bfg_j) &=& ACov (\sqrt n (\hat\bfgamma_{D,i} - \bfgamma_i), \sqrt n (\hat\bfgamma_{D,j} - \bfgamma_j))\\
-&=& ACov \left( \sum_{k=1; k \neq i}^p \sqrt n \hat \gamma_{D,ik}(F_\Lambda)\bfgamma_k, \sum_{k=1; k \neq j}^p \sqrt n \hat \gamma_{D,jk}(F_\Lambda)\bfgamma_k \right)\\
-&=& ACov \left( \sqrt n \hat \gamma_{D,ij}(F_\Lambda)\bfgamma_j, \sqrt n \hat \gamma_{D,ji}(F_\Lambda)\bfgamma_i \right)\\
-&=& - \frac{AVar(\sqrt n \hat S^D_{ij}(\Lambda))}{(\lambda_{D,s,i} - \lambda_{D,S,j})^2} \bfgamma_j \bfgamma_i^T
-\end{eqnarray*}
-
-The exact forms given in the statement of the corollary now follows from the  Form of $V_{D,S}$ in Appendix \ref{section:appA}.
-
-\paragraph{}For the on-diagonal elements of $\hat S^D(F_\Lambda)$ Theorem \ref{Theorem:decomp} gives us $ \sqrt n \hat\lambda_{D,s,i} (F_\Lambda) = \sqrt n \hat S^D_{ii}(F_\Lambda)$ for $i = 1,...,p$.
-Hence
-
-\begin{eqnarray*}
-AVar(l_i) &=& AVar(\sqrt n \hat\lambda_{D,s,i} - \sqrt n \lambda_{D,S,i})\\
-&=& AVar(\sqrt n \hat\lambda_{D,s,i} (F_\Lambda) - \sqrt n \lambda_{D,S,i}(F_\Lambda))\\
-&=& AVar(\sqrt n S^D_{ii}(F_\Lambda))
-\end{eqnarray*}
-
-A similar derivation gives the expression for $AVar(l_i,l_j); i \neq j$.
-Finally, since the asymptotic covariance between an on-diagonal and an off-diagonal element of $\hat S^D(F_\Lambda)$, it follows that the elements of $G$ and diagonal elements of $L$ are independent.
-\end{proof}
+\bibhang=1.7pc
+\bibsep=2pt
+\fontsize{9}{14pt plus.8pt minus .6pt}\selectfont
+\renewcommand\bibname{\large \bf References}
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\vskip .65cm
+\noindent
+first author affiliation
+\vskip 2pt
+\noindent
+E-mail: (first author email)
+\vskip 2pt
+
+\noindent
+second author affiliation
+\vskip 2pt
+\noindent
+E-mail: (second author email)
+% \vskip .3cm
+%\centerline{(Received ???? 20??; accepted ???? 20??)}\par
 \end{document}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\end{document}

### 2018-03-20 MS/arXiv/Depth-scatter-summary.tex
first commit in shubhobm

--- 2018-03-20 MS/Depth-scatter-summary.tex
@@
 \date{}
-\author{Subhabrata Majumdar}
+\author{Subhabrata Majumdar\\
+University of Minnesota, Twin Cities\\
+\vspace{1em}
+Technical Report}
 \maketitle
@@
 Compared to the spatial sign, which are distributed on the surface of $p$-dimensional unit ball centered at $\bfmu$, these spatial ranks have the same direction as original data and reside \textit{inside} the $p$-dimensional ball around $\bfmu$ that has radius $M_D(F)$ (which, for the case of halfspace depth, equals 0.5).
+Any outlying samples situated far away from the data cloud (represented by red points in the figure) are mapped close to the boundary of the $p$-dimensional ball after the rank transformation.
 
@@
 As a result, the multivariate rank vectors can be used for robust principal component analysis, which will be outlined in the following sections.
-However, as one can see in the above expression, the diagonal entries of $\Lambda_{D,S}$ do not change if a scale change is done on all entries of $\Lambda$, meaning the $\Lambda_{D,S}$ matrices corresponding to $F$ and $cF$ for some $c \neq 0$ will be same.
+However, as one can see in the above expression, the diagonal entries of $\Lambda_{D,S}$ are not same as those of $\Lambda$, i.e.
+the actual eigenvalues.
 This is the reason for lack of affine equavariance of the DCM.
@@
 	\centering
-		\includegraphics[width=12cm]{../Codes/IFnorm.png}
+		\includegraphics[width=12cm]{IFnorm.png}
 	\caption{Plot of the norm of influence function for first eigenvector of (a) sample covariance matrix, (b) SCM, (c) Tyler's scatter matrix and DCMs for (d) Halfspace depth, (e) Mahalanobis depth, (f) Projection depth for a bivariate normal distribution with $\bfmu = {\bf 0}, \Sigma = \diag(2,1)$}
@@
 	\centering
-		\includegraphics[height=6cm]{../Codes/octane_screeplot.pdf}
+		\includegraphics[height=6cm]{octane_screeplot}
 	\caption{Explained variance proportions for two types of PCA on octane data}
@@
 	\centering
-		\includegraphics[height=6.5cm]{../Codes/octane_distanceplot.pdf}
+		\includegraphics[height=6.5cm]{octane_distanceplot}
 	\caption{Distance plots for two types of PCA on octane data}
@@
 \bibliographystyle{plainnat}
-\bibliography{scatterbib}
+\bibliography{Depth-scatter-summary}
 

### 2018-03-20 Codes/Analyze_crime.R

@@ -1,0 +1,69 @@
+## Comm_analyze: analysis of communities data
+rm(list=ls())
+setwd("C:/Study/My projects/Depth-scatter/Codes")
+source('misc_functions.R')
+
+##########
+# Load packages
+##########
+library(fda.usc)
+library(rrcov)
+
+##########
+# Load data
+##########
+commdata = read.csv("../Data/communities.data.txt", header=F)
+NAcols = c(102:118, 122:125, 127) # columns with most NA entries
+commdata.X = commdata[,-c(1:5, NAcols)]
+
+# convert all columns into numeric
+for(i in 1:ncol(commdata.X)){
+  if(class(commdata.X[,i]) != "numeric"){
+    commdata.X[,i] = as.numeric(paste(commdata.X[,i]))
+  }
+}
+
+Y = commdata.X[,101]+1
+commdata.X = data.frame(scale(commdata.X[,-101]))
+Y = Y[complete.cases(commdata.X)]
+commdata.X = commdata.X[complete.cases(commdata.X),]
+
+##########
+# Implementation
+##########
+
+## wil do vanilla and rank PCA, then
+## principal components regression on increasing number of PCs
+
+## vanilla PCA
+pcamod = PcaClassic(commdata.X)
+scores = pcamod@scores
+
+# rank PCA
+pca.rank = PcaRank(commdata.X)
+scores.rank = pca.rank@scores
+
+par(mfrow=c(1,2))
+barplot(pcamod@eigenvalues[1:10]/sum(pcamod@eigenvalues),
+        ylim=c(0,.4), main="Normal PCA")
+barplot(pca.rank@eigenvalues[1:10]/sum(pca.rank@eigenvalues),
+        ylim=c(0,.4), main="(Projection-) Depth PCA")
+par(mfrow=c(1,1))
+
+n = nrow(commdata.X)
+p = ncol(commdata.X)
+rsq.mat = matrix(0, nrow=p, ncol=2)
+for(npc in 1:p){
+  # PC regression on vanilla PCA scores
+  lm.PC = lm(1/Y^3~scores[,1:npc]) # inverse cube transformation chosen by boxcox
+  
+  # PC-regression on rank PCA scores
+  lm.PCrank = lm(1/Y^3~scores.rank[,1:npc])
+  
[…]

### 2018-03-20 Codes/Analyze_elnino_functional.R

@@ -1,0 +1,98 @@
+setwd("C:/Study/My projects/Depth-scatter/Codes")
+rm(list=ls());
+source('misc_functions.R')
+library(rrcov)
+library(fda.usc)
+library(splines)
+library(pracma)
+library(robustbase)
+
+npfda.elnino <- read.table(
+  "C:/Study/My projects/Depth-scatter/Data/npfda-elnino.dat", quote="\"")
+
+# rain = read.csv("C:/Study/My projects/Climate-indian monsoon/data/rain_1973_2013_test.csv")
+# rainsmall = aggregate(PRCP ~ year+STATION_NAME, data=rain, FUN=median)
+# rainwide = reshape(rainsmall, timevar="year", idvar="STATION_NAME", direction="wide")
+
+# colvec = rep(grey(.5), n)
+# colvec[c(6,25,26,36:39)] = "black"
+# plot(as.numeric(Octane.X[1,]), type='l', col=colvec[1])
+# for(i in 2:n){
+#   lines(as.numeric(Octane.X[i,]), col=colvec[i])
+# }
+
+mydata = npfda.elnino
+# mydata = Octane.X
+n = nrow(mydata)
+p = ncol(mydata)
+
+plot(as.numeric(mydata[1,]), col=grey(.6), type='l',
+     ylim=(c(min(mydata), max(mydata)+.1)))
+for(i in 2:n){
+  lines(as.numeric(mydata[i,]), col=grey(.6))
+}
+
+# take a B-spline basis and orthonormalize it
+B = bs(1:p, knots=seq(0,p-1,by=2), degree=3)
+B1 = gramSchmidt(B)$Q
+
+# transform data... diff between two bins is 1
+Xt = as.matrix(mydata[,-1]) %*% B1[-1,]
+
+# do depth PCA
+source('misc_functions.R')
+pcarank = PcaRank(Xt, k=2, proj=1e2)
+Xthat = matrix(spatial.median(Xt, delta=1e-5)$mu, nrow=n, ncol=ncol(B1), byrow=T) + 
+  pcarank@scores %*% t(pcarank@loadings)
+Xhat = Xthat %*% t(B1)
+Xhat[,1] = as.numeric(mydata[,1])
+
+sdrank = pcarank@sd
+odrank = pcarank@od
+csdrank = pcarank@cutoff.sd
+codrank = pcarank@cutoff.od
+indices = 1:n
[…]

### 2018-03-20 Codes/Analyze_hbk.R

@@ -1,0 +1,84 @@
+## Analyze_octane: analysis of octane data
+rm(list=ls())
+setwd("C:/Study/My projects/Depth-scatter/Codes")
+source('misc_functions.R')
+
+## Octane data
+library(ellipse)
+library(rrcov)
+library(fda.usc)
+set.seed(04112015)
+
+## Analyze bus data
+data(bus)
+bus1 <- bus[, -9]
+madbus <- apply(bus1, 2, mad)
+bus2 <- sweep(bus1, 2, madbus, "/", check.margin = FALSE)
+# bus2 = scale(bus2)
+
+system.time(pca <- PcaClassic(bus2))
+system.time(rpca <- PcaLocantore(bus2))
+system.time(pcaHubert <- PcaHubert(bus2, k=17, kmax=17, mcd=FALSE))
+system.time(pcamcd <- PcaCov(bus2, cov.control=CovControlMcd()))
+#pcaogk <- PcaCov(bus2, cov.control=CovControlOgk())
+system.time(pcarank <- PcaRank(bus2))
+
+ev <- getEigenvalues(pca)
+evrob <- getEigenvalues(rpca)
+evhub <- getEigenvalues(pcaHubert)
+evmcd <- getEigenvalues(pcamcd)
+#evogk <- getEigenvalues(pcaogk)
+evrank = getEigenvalues(pcarank)
+
+uvar <- matrix(nrow=6, ncol=6)
+svar <- sum(ev)
+svarrob <- sum(evrob)
+svarhub <- sum(evhub)
+svarmcd <- sum(evmcd)
+#svarogk <- sum(evogk)
+svarrank = sum(evrank)
+
+for(i in 1:6){
+  uvar[i,1] <- i
+  uvar[i,2] <- round((svar - sum(ev[1:i]))/svar, 3)
+  uvar[i,3] <- round((svarrob - sum(evrob[1:i]))/svarrob, 3)
+  uvar[i,4] <- round((svarhub - sum(evhub[1:i]))/svarhub, 3)
+  uvar[i,5] <- round((svarmcd - sum(evmcd[1:i]))/svarmcd, 3)
+#  uvar[i,6] <- round((svarogk - sum(evogk[1:i]))/svarogk, 3)
+  uvar[i,6] <- round((svarrank - sum(evrank[1:i]))/svarrank, 3)
+}
+uvar <- as.data.frame(uvar)
+names(uvar) <- c("q", "Classical","Spherical", "Hubert", "MCD", "Depth")
[…]

### 2018-03-20 Codes/Analyze_octane.R

@@ -1,0 +1,112 @@
+## Analyze_octane: analysis of octane data
+rm(list=ls())
+setwd("C:/Study/My projects/Depth-scatter/Codes")
+source('misc_functions.R')
+
+## Octane data
+require(ellipse)
+require(ChemoSpec)
+require(rrcov)
+require(fda.usc)
+
+Octane <- read.csv("../Data/Octane.csv")
+Octane.X = Octane[,-c(1,2)]
+n = nrow(Octane.X)
+p = ncol(Octane.X)
+
+distanceplot = function(data.X, npc, ...){
+  # vanila PCA
+  pcamod = PcaClassic(Octane.X, k=2)
+  
+  sd = pcamod@sd
+  od = pcamod@od
+  csd = pcamod@cutoff.sd
+  cod = pcamod@cutoff.od
+  indices = 1:n
+  which.ind = which(sd > csd | od > cod)
+  
+  ## distance-distance plots
+  par(mfrow=c(1,2))
+  
+  plot(sd, od,
+       main="Classical PCA", xlab="Score distance", ylab="Orthogonal distance", ...)
+  abline(v=csd, col="red")
+  abline(h=cod, col="red")
+  if(length(which.ind>0)){
+    text(sd[which.ind], od[which.ind], indices[which.ind], pos=4, cex=.7)
+  }
+  
+  # rank PCA
+  pcarank = PcaRank(Octane.X, k=2, proj=2000)
+  
+  sdrank = pcarank@sd
+  odrank = pcarank@od
+  csdrank = pcarank@cutoff.sd
+  codrank = pcarank@cutoff.od
+  indices = 1:n
+  which.ind = which(sdrank > csdrank | odrank > codrank)
+  
+  ## distance-distance plots
+  plot(sdrank, odrank,
+       main="Depth PCA", xlab="Score distance", ylab="Orthogonal distance", ...)
+  abline(v=csdrank, col="red")
+  abline(h=codrank, col="red")
+  if(length(which.ind>0)){
+    text(sdrank[which.ind], odrank[which.ind], indices[which.ind], pos=4, cex=.7)
+  }  
+  par(mfrow=c(1,1))  
+}
+
+scoreplot = function(data.X, npc){
+  svd.oct = svd(data.X)
+  P.oct = svd.oct$v[,1:npc]
+  scores.oct = as.matrix(data.X) %*% P.oct
+  
[…]

### 2018-03-20 Codes/Analyze_octane_functional.R

@@ -1,0 +1,85 @@
+setwd("C:/Study/My projects/Depth-scatter/Codes")
+rm(list=ls());
+source('misc_functions.R')
+library(rrcov)
+library(fda.usc)
+library(splines)
+library(pracma)
+library(robustbase)
+
+Octane <- read.csv("../Data/Octane.csv")
+Octane.X = Octane[,-c(1,2)]
+n = nrow(Octane.X)
+p = ncol(Octane.X)
+
+mydata = Octane.X
+n = nrow(mydata)
+p = ncol(mydata)
+
+plot(as.numeric(mydata[1,]), col=grey(.6), type='l',
+     ylim=(c(min(mydata), max(mydata)+.1)))
+for(i in 2:n){
+  lines(as.numeric(mydata[i,]), col=grey(.6))
+}
+
+# take a B-spline basis and orthonormalize it
+B = bs(1:p, knots=seq(0,p-1,by=2), degree=3)
+B1 = gramSchmidt(B)$Q
+
+# transform data... diff between two bins is 1
+Xt = as.matrix(mydata[,-1]) %*% B1[-1,]
+
+# do depth PCA
+source('misc_functions.R')
+pcarank = PcaRank(Xt, k=1, proj=1e2)
+Xthat = matrix(spatial.median(Xt, delta=1e-5)$mu, nrow=n, ncol=ncol(B1), byrow=T) + 
+  pcarank@scores %*% t(pcarank@loadings)
+Xhat = Xthat %*% t(B1)
+Xhat[,1] = as.numeric(mydata[,1])
+
+sdrank = pcarank@sd
+odrank = pcarank@od
+csdrank = pcarank@cutoff.sd
+codrank = pcarank@cutoff.od
+indices = 1:n
+which.ind = which(sdrank > csdrank & odrank > codrank)
+
+## distance-distance plots
+pdf('Octane_functional1.pdf',width=4, height=4)
+plot(as.numeric(mydata[1,]), col=grey(.6), type='l',
+     ylab="Absorbance", xlab="Wavelength (in nm)",
+     ylim=(c(min(mydata), max(mydata)+.1)))
+for(i in 2:n){
+  lines(as.numeric(mydata[i,]), col=grey(.6))
+}
+for(i in which.ind){
+  lines(as.numeric(mydata[i,]), col="black")
+}
+dev.off()
+
+pdf('Octane_functional2.pdf',width=4, height=4)
[…]

### 2018-03-20 Codes/Analyze_spartina.R

@@ -1,0 +1,50 @@
+## Comm_analyze: analysis of communities data
+rm(list=ls())
+setwd("C:/Study/My projects/Depth-scatter/Codes")
+commdata = read.table("../Data/spartina.txt", header=T)
+NAcols = c(7,8) # columns with most NA entries
+commdata.X = commdata[,-NAcols]
+
+Y = commdata.X[,1]
+commdata.X = data.frame(scale(commdata.X[,-1]))
+Y = Y[complete.cases(commdata.X)]
+commdata.X = commdata.X[complete.cases(commdata.X),]
+
+## wil do vanilla and rank PCA, then
+## principal components regression on increasing number of PCs
+
+## vanilla PCA
+pcamod = princomp(commdata.X)
+scores = pcamod$scores
+
+## get ranks
+n = nrow(commdata.X)
+p = ncol(commdata.X)
+norms = sqrt(commdata.X^2 %*% rep(1,p))
+signs = commdata.X / (norms %*% rep(1,p))
+
+# calculate depth
+require(fda.usc)
+depths = mdepth.RP(commdata.X, commdata.X)$dep
+depths = max(depths) - depths
+commdata.rank = scale(signs * depths)
+
+# rank PCA
+pca.rank = princomp(commdata.rank)
+scores.rank = pca.rank$scores
+
+rsq.mat = matrix(0, nrow=p, ncol=2)
+for(npc in 1:p){
+  # PC regression on vanilla PCA scores
+  lm.PC = lm(sqrt(Y)~scores[,1:npc]) # inverse cube transformation chosen by boxcox
+  
+  # PC-regression on rank PCA scores
+  lm.PCrank = lm(sqrt(Y)~scores.rank[,1:npc])
+  
+  rsq.mat[npc,] = c(summary(lm.PC)$r.squared, summary(lm.PCrank)$r.squared)
+}
+
+plot(1:p, rsq.mat[,1], type='l', ylim=c(0.2,.8), lwd=2,
+     xlab="no. of PCs", ylab="R^2")
+lines(1:p, rsq.mat[,2], type='l', lty=2, lwd=2)
+legend("bottomright", c("with normal PCs", "with depth-PCs"), lty=c(1,2), lwd=2)

### 2018-03-20 Codes/Sim1.R

@@ -1,0 +1,180 @@
+## PQDSim: Initial simulations of Projection quantile depth and comparisions with projection depth
+## v4: Multivariate rank-based PCA simulations
+
+## Functions
+## function to generate from multivariate normal
+my.mvrnorm = function(n, mu, Sigma){
+  p = length(mu)
+  # compute square root of covariance matrix
+  eo=eigen(Sigma, symmetric=TRUE)
+  sigma.sqrt=eo$vec%*%diag(eo$val^0.5)%*%t(eo$vec)
+  
+  # generate random normals from runif by box-muller transform
+  rnorm.vec = sqrt(-2*log(runif(n*p)))*cos(2*pi*runif(n*p))
+  
+  # generate sample matrix
+  sample.matrix = matrix(rep(mu, n), nrow=n, byrow=T) +
+    matrix(rnorm.vec, nrow=n, ncol=p)%*%sigma.sqrt
+  return(sample.matrix)
+}
+
+ones = function(m,n){
+  matrix(1, nrow=m, ncol=n)
+}
+
+## function to calculate weighted projection quantile depth
+EPQD1 = function(X, grid, nu=1e3){
+  
+  p = ncol(X)
+  b = apply(X, 2, median)
+  X0 = X - ones(nrow(X),1) %*% b
+  grid0 = grid - ones(nrow(grid),1) %*% b
+  
+  ## get matrix of weighted PQDs for all points
+  npt = dim(grid)[1]
+  Fuxu.mat = matrix(0, nrow=npt, ncol=nu)
+  
+  # loop over nu pts on unit circle then take max
+  for(iu in 1:nu){
+    u = as.matrix(rnorm(p)); u = u/sqrt(sum(u^2))
+    uecdf = ecdf(X0%*%u)
+    Fuxu.mat[,iu] = uecdf(grid0%*%u)
+  }
+  EPQD.vec = 1/(1+apply(abs(Fuxu.mat-.5), 1, max))
+  
+  return(cbind(grid,EPQD.vec))
+  
+}
+
+wEPQD1 = function(X, grid, sig, nu=1e3){
+  
+  p = ncol(X)
+  b = apply(X, 2, median)
+  X0 = X - ones(nrow(X),1) %*% b
[…]

### 2018-03-20 Codes/Sim_ARE.R

@@ -1,0 +1,93 @@
+## Sim_efficiency: Finite sample efficiency for depth-based scatter estimator
+## comparison with sign covariance matrix (SCM)
+
+set.seed(03092016)
+df.list = c(5,6,10,15,25,Inf)
+p.list = c(2,5,10,20)
+
+ARE.mat1 = matrix(0, nrow=length(p.list), ncol=length(df.list))
+for(i in 1:length(p.list)){
+  for(j in 1:length(df.list)){
+    pi = p.list[i]
+    dfj = df.list[j]
+    
+    # ARE for PD
+    X = matrix(rt(1e6*pi, df=dfj), ncol=pi)
+    z = sqrt(rowSums(X^2))
+    c = qnorm(.75)
+    uz = z^2 / (c+z)^2
+    upz = 2*c*z / (c+z)^3
+    numerat = mean(pi*uz + upz*z)^2
+    denom = mean(uz^2)
+    ARE.mat1[i,j] = numerat/((pi)^2*denom)
+  }
+}
+
+ARE.mat2 = matrix(0, nrow=length(p.list), ncol=length(df.list))
+for(i in 1:length(p.list)){
+  for(j in 1:length(df.list)){
+    pi = p.list[i]
+    dfj = df.list[j]
+    
+    # ARE for HSD
+    X = matrix(rt(1e6*pi, df=dfj), ncol=pi)
+    z = sqrt(rowSums(X^2))
+    c = qnorm(.75)
+    Fz = pt(z, df=dfj)
+    uz = Fz^2
+    upz = 2*Fz * dt(z, df=dfj)
+    numerat = mean(z^4) * mean(pi*uz + upz*z)^2
+    denom = mean(uz^2)
+    ARE.mat2[i,j] = numerat/((pi^2+2*pi)^2*denom)
+  }
+}
+
+cbind(t(ARE.mat1), t(ARE.mat2))
+
+library(parallel)
+library(doSNOW)
+
+# Functions
+ARE.norm = function(rho, depth, ns=1e4){
+  require(fda.usc)
+  Z = matrix(rnorm(2*ns), ncol=2)
+  
+  # get depth values
[…]

### 2018-03-20 Codes/Sim_ARE_Linux.R

@@ -1,0 +1,200 @@
+## Sim_efficiency: Finite sample efficiency for depth-based scatter estimator
+## comparison with sign covariance matrix (SCM)
+
+#setwd("C:/Study/My projects/Depth-scatter/Codes")
+rm(list=ls());
+source('misc_functions.R')
+library(parallel)
+
+## Functions
+
+## simulate for normal dist
+FSE.norm = function(n, p, iter=1e3, ncores=detectCores()){
+  set.seed(12182014)
+  v = c(rep(0,p-1), 1)
+  lam = 1:p
+  Sigma = diag(lam)
+  
+  MSE.mat = matrix(0, nrow=length(n), ncol=8)
+  for(i in 1:length(n)){
+    
+    # function to compute stuff 1000 times for a given n
+    loopfun = function(j){
+      source('misc_functions.R')
+      require(fastM)
+      require(fda.usc)
+      iv = rep(0,9)
+      
+      # get sample and construct sign matrix
+      iX = matrix(rnorm(p*n[i]), ncol=p) %*% sqrt(Sigma)
+      iXnorm = sqrt(iX^2 %*% rep(1,p))
+      iS = iX / (iXnorm %*% rep(1,p))
+      
+      # PCA on original sample
+      iP = princomp(iX)
+      iv[1] = abs(sum(v * iP$loadings[,1]))
+      
+      # PCA on SCM
+      iPsign = princomp(iS)
+      iv[2] = abs(sum(v * iPsign$loadings[,1]))
+      
+      # PCA on Tyler's cov matrix
+      T = TYLERshape(iX)$Sigma
+      iv[3] = abs(sum(v * eigen(T)$vectors[,1]))
+      
+      # PCA on DCM and depth-weighted tyler's scatter
+      # Tukey's depth
+      idep = mdepth.HS(iX,iX)$dep
+      #idep = EPQD(iX,iX)[,p+1]
+      idep = max(idep) - idep
+      iXd = iS * idep
+      iPdepth = princomp(iXd)
+      iv[4] = abs(sum(v * iPdepth$loadings[,1]))
+      
+      Td = TylerSig(iX, weight=idep)
+      iv[5] = abs(sum(v * eigen(Td)$vectors[,1]))
+      
+      # Mahalanobis depth
+      idep = mdepth.MhD(iX,iX)$dep
[…]

### 2018-03-20 Codes/Sim_FSE.R

@@ -1,0 +1,258 @@
+## Sim_efficiency: Finite sample efficiency for depth-based scatter estimator
+## comparison with sign covariance matrix (SCM)
+
+setwd("C:/Study/My projects/Depth-scatter/Codes")
+rm(list=ls());
+source('misc_functions.R')
+library(parallel)
+library(doSNOW)
+
+## Functions
+
+## simulate for normal dist
+FSE.norm = function(n, p, iter=1e3, ncores=detectCores()){
+  set.seed(12182014)
+  v = c(rep(0,p-1), 1)
+  lam = 1:p
+  Sigma = diag(lam)
+  
+  MSE.mat = matrix(0, nrow=length(n), ncol=8)
+  for(i in 1:length(n)){
+    
+    # function to compute stuff 1000 times for a given n
+    loopfun = function(j){
+      source('misc_functions.R')
+      require(fastM)
+      require(fda.usc)
+      iv = rep(0,9)
+      
+      # get sample and construct sign matrix
+      iX = matrix(rnorm(p*n[i]), ncol=p) %*% sqrt(Sigma)
+      iXnorm = sqrt(iX^2 %*% rep(1,p))
+      iS = iX / (iXnorm %*% rep(1,p))
+      
+      # PCA on original sample
+      iP = princomp(iX)
+      iv[1] = abs(sum(v * iP$loadings[,1]))
+      
+      # PCA on SCM
+      iPsign = princomp(iS)
+      iv[2] = abs(sum(v * iPsign$loadings[,1]))
+      
+      # PCA on Tyler's cov matrix
+      T = TYLERshape(iX)$Sigma
+      iv[3] = abs(sum(v * eigen(T)$vectors[,1]))
+      
+      # PCA on DCM and depth-weighted tyler's scatter
+      # Tukey's depth
+      idep = mdepth.HS(iX,iX)$dep
+      #idep = EPQD(iX,iX)[,p+1]
+      idep = max(idep) - idep
+      #idep=1
+      iXd = iS * idep
+      iPdepth = princomp(iXd)
+      iv[4] = abs(sum(v * iPdepth$loadings[,1]))
+      
+      Td = TylerSig(iX, weight=idep)
+      iv[5] = abs(sum(v * eigen(Td)$vectors[,1]))
+      
[…]

### 2018-03-20 Codes/Sim_FSE_Linux.R

@@ -1,0 +1,248 @@
+## Sim_efficiency: Finite sample efficiency for depth-based scatter estimator
+## comparison with sign covariance matrix (SCM)
+
+#setwd("C:/Study/My projects/Depth-scatter/Codes")
+rm(list=ls());
+source('misc_functions.R')
+library(parallel)
+
+## Functions
+
+## simulate for normal dist
+FSE.norm = function(n, p, iter=1e3, ncores=detectCores()){
+  set.seed(12182014)
+  v = c(rep(0,p-1), 1)
+  lam = 1:p
+  Sigma = diag(lam)
+  
+  MSE.mat = matrix(0, nrow=length(n), ncol=8)
+  for(i in 1:length(n)){
+    
+    # function to compute stuff 1000 times for a given n
+    loopfun = function(j){
+      source('misc_functions.R')
+      require(fastM)
+      require(fda.usc)
+      iv = rep(0,9)
+      
+      # get sample and construct sign matrix
+      iX = matrix(rnorm(p*n[i]), ncol=p) %*% sqrt(Sigma)
+      iXnorm = sqrt(iX^2 %*% rep(1,p))
+      iS = iX / (iXnorm %*% rep(1,p))
+      
+      # PCA on original sample
+      iP = princomp(iX)
+      iv[1] = abs(sum(v * iP$loadings[,1]))
+      
+      # PCA on SCM
+      iPsign = princomp(iS)
+      iv[2] = abs(sum(v * iPsign$loadings[,1]))
+      
+      # PCA on Tyler's cov matrix
+      T = TYLERshape(iX)$Sigma
+      iv[3] = abs(sum(v * eigen(T)$vectors[,1]))
+      
+      # PCA on DCM and depth-weighted tyler's scatter
+      # Tukey's depth
+      idep = mdepth.HS(iX,iX)$dep
+      #idep = EPQD(iX,iX)[,p+1]
+      idep = max(idep) - idep
+      iXd = iS * idep
+      iPdepth = princomp(iXd)
+      iv[4] = abs(sum(v * iPdepth$loadings[,1]))
+      
+      Td = TylerSig(iX, weight=idep)
+      iv[5] = abs(sum(v * eigen(Td)$vectors[,1]))
+      
+      # Mahalanobis depth
+      idep = mdepth.MhD(iX,iX)$dep
[…]

### 2018-03-20 Codes/Sim_FSE_Linux2.R

@@ -1,0 +1,214 @@
+## Sim_efficiency: Finite sample efficiency for depth-based scatter estimator
+## comparison with sign covariance matrix (SCM)
+
+#setwd("C:/Study/My projects/Depth-scatter/Codes")
+rm(list=ls());
+source('misc_functions.R')
+library(parallel)
+
+## Functions
+
+## simulate for normal dist
+FSE.norm = function(n, p, iter=1e3, ncores=detectCores()){
+  set.seed(12182014)
+  v = c(rep(0,p-1), 1)
+  lam = 1:p
+  Sigma = diag(lam)
+  
+  MSE.mat = matrix(0, nrow=length(n), ncol=8)
+  for(i in 1:length(n)){
+    
+    # function to compute stuff 1000 times for a given n
+    loopfun = function(j){
+      source('misc_functions.R')
+      require(fastM)
+      require(fda.usc)
+      iv = rep(0,9)
+      
+      # get sample and construct sign matrix
+      iX = matrix(rnorm(p*n[i]), ncol=p) %*% sqrt(Sigma)
+      iXnorm = sqrt(iX^2 %*% rep(1,p))
+      iS = iX / (iXnorm %*% rep(1,p))
+      
+      # PCA on original sample
+      iP = princomp(iX)
+      iv[1] = abs(sum(v * iP$loadings[,1]))
+      
+      # PCA on SCM
+      iPsign = princomp(iS)
+      iv[2] = abs(sum(v * iPsign$loadings[,1]))
+      
+      # PCA on Tyler's cov matrix
+      T = TYLERshape(iX)$Sigma
+      iv[3] = abs(sum(v * eigen(T)$vectors[,1]))
+      
+      # PCA on DCM and depth-weighted tyler's scatter
+      # Tukey's depth
+      idep = mdepth.HS(iX,iX)$dep
+      #idep = EPQD(iX,iX)[,p+1]
+      idep = max(idep) - idep
+      iXd = iS * idep
+      iPdepth = princomp(iXd)
+      iv[4] = abs(sum(v * iPdepth$loadings[,1]))
+      
+      Td = TylerSig(iX, weight=idep)
+      iv[5] = abs(sum(v * eigen(Td)$vectors[,1]))
+      
+      # Mahalanobis depth
+      idep = mdepth.MhD(iX,iX)$dep
[…]

### 2018-03-20 Codes/Sim_FSE_Linux_Depth.R

@@ -1,0 +1,215 @@
+## Sim_efficiency: Finite sample efficiency for depth-based scatter estimator
+## comparison with sign covariance matrix (SCM)
+
+#setwd("C:/Study/My projects/Depth-scatter/Codes")
+rm(list=ls());
+source('misc_functions.R')
+library(parallel)
+
+## Functions
+
+## simulate for normal dist
+FSE.norm = function(n, p, iter=1e3, ncores=detectCores()){
+  set.seed(12182014)
+  v = c(rep(0,p-1), 1)
+  lam = 1:p
+  Sigma = diag(lam)
+  
+  MSE.mat = matrix(0, nrow=length(n), ncol=8)
+  for(i in 1:length(n)){
+    
+    # function to compute stuff 1000 times for a given n
+    loopfun = function(j){
+      source('misc_functions.R')
+      require(fastM)
+      require(fda.usc)
+      iv = rep(0,9)
+      
+      # get sample and construct sign matrix
+      iX = matrix(rnorm(p*n[i]), ncol=p) %*% sqrt(Sigma)
+      iXnorm = sqrt(iX^2 %*% rep(1,p))
+      iS = iX / (iXnorm %*% rep(1,p))
+      
+      # PCA on original sample
+      iP = princomp(iX)
+      iv[1] = abs(sum(v * iP$loadings[,1]))
+      
+      # PCA on SCM
+      iPsign = princomp(iS)
+      iv[2] = abs(sum(v * iPsign$loadings[,1]))
+      
+      # PCA on Tyler's cov matrix
+      T = TYLERshape(iX)$Sigma
+      iv[3] = abs(sum(v * eigen(T)$vectors[,1]))
+      
+      # PCA on DCM and depth-weighted tyler's scatter
+      # Tukey's depth
+      idep = mdepth.HS(iX,iX)$dep
+      #idep = EPQD(iX,iX)[,p+1]
+      idep = max(idep) - idep
+      iXd = iS * idep
+      iPdepth = princomp(iXd)
+      iv[4] = abs(sum(v * iPdepth$loadings[,1]))
+      
+      Td = TylerSig(iX, weight=idep)
+      iv[5] = abs(sum(v * eigen(Td)$vectors[,1]))
+      
+      # Mahalanobis depth
+      idep = mdepth.MhD(iX,iX)$dep
[…]

### 2018-03-20 Codes/Sim_influenceplot.R

@@ -1,0 +1,158 @@
+## Sim_influenceplot: Plots to compare influence functions for DCM and SCM
+
+setwd("C:/Study/My projects/Depth-scatter/Codes")
+rm(list=ls());
+source('misc_functions.R')
+
+## Functions
+# DCM plots for different types of depth
+plot.IFnorm = function(X, grid, depth, ...){
+  require(fda.usc)
+  
+  # get depth values
+  if(depth=='HS'){
+    DX = mdepth.HS(X,X)$dep
+  }
+  else if(depth=='MhD'){
+    DX = mdepth.MhD(X,X)$dep
+  }
+  else {
+    DX = mdepth.RP(X,X)$dep
+  }
+    
+  # get eigenvalues of DCM
+  DX = max(DX) - DX
+  lamDS = colMeans((DX^2/sum.lam.Zsq) * lam.Zsq)
+  
+  # get htped at grid points
+  if(depth=='HS'){
+    Dgrid = mdepth.HS(grid,X)$dep
+  }
+  else if(depth=='MhD'){
+    Dgrid = mdepth.MhD(grid,X)$dep
+  }
+  else {
+    Dgrid = mdepth.RP(grid,X)$dep
+  }
+  Dgrid = max(Dgrid) - Dgrid
+  
+  # get norms of influence fns for eigenvectors
+  mult = sqrt(lam[1]*lam[2])/(lamDS[1] - lamDS[2])
+  IFnorm.D = abs(mult * xygrid[,1] * xygrid[,2] * Dgrid^2 / diag(xygrid %*% Sig %*% t(xygrid)))
+  
+  # plot result
+  persp(pts, pts, matrix(IFnorm.D, nrow=lengrid, byrow=T), ...)
+}
+
+## Scatterplot of data and D-rank
+require(fda.usc)
+n = 1e3
+set.seed(120214)
+Gamma = matrix(c(1,-1,1,1), nrow=2)/sqrt(2)
+sig = Gamma %*% diag(c(9,1)) %*% t(Gamma)
+X = my.mvrnorm(n, mu=c(0,0), Sig=2*sig)
+X = rbind(X, matrix(c(-5,-9, -7,-9, 9,9), ncol=2, byrow=T))
+uX = X / sqrt(rowSums(X^2))
+dX = mdepth.HS(X,X)$dep
+Xrank = uX * (max(dX) - dX)
+
+pdf('signs.pdf', width=7, height=4)
+par(mfrow=c(1,2))
[…]

### 2018-03-20 Codes/Sim_tylereff.R

@@ -1,0 +1,24 @@
+## Sim_influenceplot: Plots to compare influence functions for DCM and SCM
+
+setwd("C:/Study/My projects/Depth-scatter/Codes")
+rm(list=ls());
+source('misc_functions.R')
+library(parallel)
+library(doSNOW)
+
+## setup 1: Sigma = diag(1,1)
+set.seed(02032015)
+
+n = 50
+Sig = diag(c(2,1))
+simiter = 100
+err = matrix(0, nrow=simiter, ncol=2)
+
+for(i in 1:simiter){
+  iX = matrix(rnorm(2*n), ncol=2) %*% sqrt(Sig)
+  
+  err[i,1] = norm(Sig - TylerSigma(iX), type="F")
+  err[i,2] = norm(Sig - TylerSigma(iX, depth=T), type="F")
+}
+
+colSums(err)/simiter

### 2018-03-20 Codes/Simulate_are_of_wsm.R

@@ -1,0 +1,55 @@
+## calculate asymptotic relative efficiency of weighted spatial median
+setwd("C:/Study/My projects/Depth-scatter/Codes")
+rm(list=ls());
+source('misc_functions.R')
+
+ARE.wsm = function(p, dist, df=NULL, rho=0){
+  # covariance matrix
+  Sigma = diag(p)
+  for(i in 2:p){
+    for(j in 1:(i-1)){
+      Sigma[i,j] = rho^abs(i-j)
+    }
+  }
+  Sigma = Sigma + t(Sigma) - diag(p)
+  
+  # generate random entries
+  if(dist=="norm"){
+    e.mat = my.mvrnorm(1e4, mu=rep(0,p), Sigma=Sigma)
+  } else{
+    e.mat = my.mvrt(1e4, df=df, mu=rep(0,p), Sigma=Sigma)
+  }
+  A.list = list()
+  B.list = list()
+  Aw.list = list()
+  Bw.list = list()
+  
+  for(i in 1:1e4){
+    z = e.mat[i,]
+    normz = sqrt(sum(z^2))
+    ztz = z %*% t(z)
+    wz = 1/(normz)
+    A.list[[i]] = (diag(p) - ztz/normz^2) / normz
+    B.list[[i]] = ztz / normz^2
+    Aw.list[[i]] = (diag(p) - ztz/normz^2) * wz / normz
+    Bw.list[[i]] = wz^2 * ztz / normz^2
+  }
+  
+  # calculate quantities
+  A = apply(simplify2array(A.list), 1:2, mean)
+  B = apply(simplify2array(B.list), 1:2, mean)
+  Aw = apply(simplify2array(Aw.list), 1:2, mean)
+  Bw = apply(simplify2array(Bw.list), 1:2, mean)
+  
+  (det(solve(A) %*% B %*% solve(A)) / det(solve(Aw) %*% Bw %*% solve(Aw)))^(1/p)
+}
+
+set.seed(8202016)
+c(ARE.wsm(5,"norm", 0),ARE.wsm(5,"t",df=3, 0),
+  ARE.wsm(5,"t", df=5, 0),ARE.wsm(5,"t", df=10, 0),ARE.wsm(5,"t", df=20, 0))
[…]

### 2018-03-20 Codes/Simulate_elnino_functional.R

@@ -1,0 +1,83 @@
+setwd("C:/Study/My projects/Depth-scatter/Codes")
+rm(list=ls());
+source('misc_functions.R')
+library(rrcov)
+library(fda.usc)
+library(splines)
+library(pracma)
+library(robustbase)
+
+npfda.elnino <- read.table(
+  "C:/Study/My projects/Depth-scatter/Data/npfda-elnino.dat", quote="\"")
+mydata = npfda.elnino
+# mydata = Octane.X
+n = nrow(mydata)
+p = ncol(mydata)
+
+# take a B-spline basis and orthonormalize it
+B = bs(1:p, knots=seq(0,p-1,by=2), degree=3)
+B1 = gramSchmidt(B)$Q
+
+# transform data... diff between two bins is 1
+Xt = as.matrix(mydata[,-1]) %*% B1[-1,]
+muhat = spatial.median(Xt, delta=1e-5)$mu
+
+set.seed(08162016)
+source('misc_functions.R')
+ncomp = 2
+
+nrep = 1e3
+ndata = 1e2
+out.mat = matrix(0, nrep, 3)
+
+## iterate nrep times
+pb = txtProgressBar(0, nrep)
+for(rep in 1:nrep){
+  pcarank = PcaRank(Xt, k=ncomp, proj=1e2)
+  mu = muhat + colMeans(pcarank@scores %*% t(pcarank@loadings))
+
+  # generate random observations
+  V = c(1,1,1,1,10)
+  nbasis = ncol(B)
+
+  ## add noise to loadings
+  B.mat = matrix(0, nrow=ndata, ncol=nbasis)
+  for(i in 1:ndata){
+    B.mat.j = matrix(0, nrow=nbasis, ncol=ncomp)
+    for(j in 1:ncomp){
+      B.mat.j[,j] = my.mvrnorm(n=1, mu=pcarank@loadings[,j], Sigma=diag(rep(V[j],nbasis)))
+    }
+    B.mat[i,] = muhat + colMeans(pcarank@scores %*% t(B.mat.j))
+  }
+  
+  ## add white noise to each element
+  B.mat = B.mat + matrix(rnorm(ndata*nbasis, 0, 1e-1), ndata, nbasis)
+  
+  ## add comtamination
+  B.mat[2:6,2:6] = B.mat[2:6,2:6] + 1e2
+  
[…]

### 2018-03-20 Codes/comm_analyze.R

@@ -1,0 +1,66 @@
+## Comm_analyze: analysis of communities data
+rm(list=ls())
+setwd("C:/Study/My projects/Depth-scatter/Codes")
+commdata = read.csv("../Data/communities.data.txt", header=F)
+NAcols = c(102:118, 122:125, 127) # columns with most NA entries
+commdata.X = commdata[,-c(1:5, NAcols)]
+
+# convert all columns into numeric
+for(i in 1:ncol(commdata.X)){
+  if(class(commdata.X[,i]) != "numeric"){
+    commdata.X[,i] = as.numeric(paste(commdata.X[,i]))
+  }
+}
+
+Y = commdata.X[,101]+1
+commdata.X = data.frame(scale(commdata.X[,-101]))
+Y = Y[complete.cases(commdata.X)]
+commdata.X = commdata.X[complete.cases(commdata.X),]
+
+## vanilla PCA
+pcamod = princomp(commdata.X)
+plot(pcamod)
+scores = pcamod$scores
+pairs(scores[,1:3], pch=19, cex=.5)
+
+# PC-regression
+X.PC = as.matrix(commdata.X) %*% pcamod$loadings[,1:5]
+# best transformation: boxcox
+boxcox(Y~X.PC, seq(-5,5,.1))
+lm.PC = lm(1/Y^3~X.PC)
+summary(lm.PC)
+
+par(mfrow=c(2,2))
+plot(lm.PC)
+par(mfrow=c(1,1))
+
+## rank PCA
+n = nrow(commdata.X)
+p = ncol(commdata.X)
+norms = sqrt(commdata.X^2 %*% rep(1,p))
+signs = commdata.X / (norms %*% rep(1,p))
+
+# calculate depth
+require(fda.usc)
+depths = mdepth.RP(commdata.X, commdata.X)$dep
+depths = max(depths) - depths
+commdata.rank = signs * depths
+
+pca.rank = princomp(commdata.rank)
+plot(pca.rank)
+
+scores.rank = pca.rank$scores
+pairs(scores.rank[,1:3], pch=19, cex=.5)
+
+# PC-regression
+X.PCrank = as.matrix(commdata.rank) %*% pca.rank$loadings[,1:5]
+
+# best transformation: boxcox
+boxcox(Y~X.PCrank, seq(-5,5,.1))
+
+lm.PCrank = lm(1/Y^3~X.scores.rank[,1:5])
[…]

### 2018-03-20 Codes/depthplot.R

@@ -1,0 +1,23 @@
+library(plot3D)
+library(fda.usc)
+library(scales)
+
+X = matrix(rnorm(1e3), ncol=2) %*% sqrt(diag(c(1,1/2)))
+
+# make grid of points
+pts = seq(-3, 3, by=.2)
+lengrid = length(pts)
+xcoord = rep(pts, rep(lengrid,lengrid))
+ycoord = rep(pts, lengrid)
+xygrid = cbind(xcoord,ycoord)
+rm(xcoord,ycoord)
+
+pdf('depthplot.pdf', width=6, height=5)
+p = persp3D(pts, pts, matrix(mdepth.RP(xygrid,X)$dep, nrow=lengrid, byrow=T),
+      xlab="x1", ylab="x2", zlab="Depth", zlim=c(-1,1),
+      col=alpha("lightblue", .2),expand = 0.5,shade = 0.2,
+      theta=30, phi=10, border=alpha("black", .2), contour=TRUE)
+
+points3D(X[,1], X[,2], rep(-1,nrow(X)),
+         pch=19, cex=.5, pch=.3, col='red', add=TRUE)
+dev.off()

### 2018-03-20 Codes/depthtesting.R

@@ -1,0 +1,90 @@
+## Sim_influenceplot: Plots to compare influence functions for DCM and SCM
+
+setwd("C:/Study/My projects/Depth-scatter/Codes")
+rm(list=ls());
+source('misc_functions.R')
+
+library(fda.usc)
+library(WCQ)
+library(MethylCapSig)
+
+level.vec = rep(0,3)
+mu = .25
+nrep = 1e2
+n = 20
+p = 1e3
+rho = 0.8
+Sigma = diag(rep(1,p))
+for(i in 1:p){
+  for(j in 1:p){
+    Sigma[i,j] = rho^abs(i-j)
+  }
+}
+eo = eigen(Sigma)
+Sigma.sqrt = eo$vectors %*% diag(sqrt(eo$values))
+
+level.vec = rep(0,3)
+## Crossprod hiigh-dimensional test
+pb = txtProgressBar(0,nrep)
+for(rep in 1:nrep){
+  
+  # generate data
+  #set.seed(1)
+  X1 = matrix(rnorm(n*p), ncol=p) %*% t(Sigma.sqrt)
+  X2 = 3 * matrix(rnorm(n*p), ncol=p) %*% t(Sigma.sqrt)
+  X = mu + .9*X1 + .1*X2
+#   uX = X / sqrt(rowSums(X^2))
+#   dX = mdepth.TD(X,X)$dep
+#   Xrank = uX * exp(-dX)
+#   cqtest(X)
+#   cqtest(uX)
+#   cqtest(Xrank)
+  
+  # Chen-Qin test
+  level.vec[1] = level.vec[1] + (cqtest(X)[2] < 0.05)
+  
+  # Sign-based test
+  uX = X / sqrt(rowSums(X^2))
+  level.vec[2] = level.vec[2] + (cqtest(uX)[2] < 0.05)
+  
+  # Depth-rank based test
+  dX = mdepth.TD(X,X)$dep
+  Xrank = uX * (max(dX)-dX)
+  #Xrank = uX * dX
+  level.vec[3] = level.vec[3] + (cqtest(Xrank)[2] < 0.05)
+  setTxtProgressBar(pb,rep)
+}
+close(pb)
+
+level.vec = level.vec/nrep
+level.vec 
+
+n=1e3
+p=10
+mu=0
+rho = 0.8
+Sigma = diag(rep(1,p))
[…]

### 2018-03-20 Codes/depthtesting_empirical.R

@@ -1,0 +1,124 @@
+## Sim_influenceplot: Plots to compare influence functions for DCM and SCM
+
+setwd("C:/Study/My projects/Depth-scatter/Codes")
+rm(list=ls());
+source('misc_functions.R')
+
+library(fda.usc)
+
+get.power = function(n,p,nrep,mu,cov,rho=0.5){
+  
+  ## construct output matrix
+  out.mat = matrix(0, nrow=length(n)*length(p), ncol=6)
+  out.mat[,1] = rep(p,rep(length(n),length(p)))
+  out.mat[,2] = rep(n, length(p))
+  
+  ## get rows of output matrix, each by nrep simulations
+  loopfun = function(j){
+    is.reject = rep(0,4)
+    
+    # generate data
+    X1 = my.mvrnorm(ni, mu=rep(0,pi), Sig=Sigma)
+    #X2 = my.mvrnorm(ni, mu=rep(mu,pi), Sig=9*Sigma)
+    X2 = matrix(rcauchy(pi*ni), ncol=pi)
+    ind = rbinom(ni, 1, 0.5)
+    X = mu + ind*X1 + (1-ind)*X2
+    
+    # Hotelling Tsq
+    Xbar = apply(X, 2, mean)
+    T2 = ni * t(Xbar) %*% solve(cov(X)) %*% Xbar
+    is.reject[1] = (1 - pchisq(T2, pi) < 0.05)
+    
+    ## Sign-based test
+    uX = X / sqrt(rowSums(X^2))
+    uXbar = apply(uX, 2, mean)
+    uT2 = ni * t(uXbar) %*% solve(cov(uX)) %*% uXbar
+    is.reject[2] = (sum(uDist > as.numeric(uT2))/1e4 < 0.05)
+    
+    ## Depth-rank based test
+    dX = mdepth.RP(X,X)$dep
+#   Xc = X - apply(X,2,median)
+#    uXc = Xc / sqrt(rowSums(Xc^2))
+    rX = uX * (max(dX)-dX)
+    rXbar = apply(rX, 2, mean)
+    rT2 = ni * t(rXbar) %*% solve(cov(rX)) %*% rXbar
+    is.reject[3] = (sum(rDist > as.numeric(rT2))/1e4 < 0.05)
+
+    ## Depth-based test
+    Xd = uX * dX
+    dXbar = apply(Xd, 2, mean)
[…]

### 2018-03-20 Codes/depthtesting_highdim.R

@@ -1,0 +1,98 @@
+## Sim_influenceplot: Plots to compare influence functions for DCM and SCM
+
+setwd("C:/Study/My projects/Depth-scatter/Codes")
+rm(list=ls());
+source('misc_functions.R')
+
+library(fda.usc)
+library(MethylCapSig)
+library(parallel)
+
+get.power = function(n,p,nrep,mu,cov,rho=0.5){
+  
+  ## construct output matrix
+  out.mat = matrix(0, nrow=length(n)*length(p), ncol=5)
+  out.mat[,1] = rep(p,rep(length(n),length(p)))
+  out.mat[,2] = rep(n, length(p))
+  
+  ## get rows of output matrix, each by nrep simulations
+  loopfun = function(j){
+    
+    ## Get null distributions
+    is.reject = rep(0,3)
+    
+    # generate data
+    X1 = matrix(rnorm(ni*pi), ncol=pi) %*% t(Sigma.sqrt)
+    X2 = 3 * matrix(rnorm(ni*pi), ncol=pi) %*% t(Sigma.sqrt)
+    ind = rbinom(ni, 1, 0.5)
+    X = mu + ind*X1 + (1-ind)*X2
+    
+    # Chen-Qin test
+    is.reject[1] = (cqtest(X)[2] < 0.05)
+    
+    # Sign-based test
+    uX = X / sqrt(rowSums(X^2))
+    is.reject[2] = (cqtest(uX)[2] < 0.05)
+    
+    # Depth-rank based test
+    dX = mdepth.TD(X,X)$dep
+    Xrank = uX * (max(dX)-dX)
+    #Xrank = uX * dX
+    is.reject[3] = (cqtest(Xrank)[2] < 0.05)
+    
+    is.reject
+  }
+  
+  for(irep in 1:nrow(out.mat)){
+    ni = out.mat[irep,2]
+    pi = out.mat[irep,1]
+    Sigma = diag(rep(1,pi))
+    if(cov=="AR1"){
+      for(i in 2:pi){
+        for(j in 1:i-1){
+          Sigma[i,j] = rho^abs(i-j)
+          Sigma[j,i] = Sigma[i,j]
+        }
+      }
+    }
+    else if(cov=="compound"){
+      for(i in 2:pi){
+        for(j in 1:i-1){
+          Sigma[i,j] = rho
+          Sigma[j,i] = Sigma[i,j]
+        }
[…]

### 2018-03-20 Codes/robustSDR.R

@@ -1,0 +1,183 @@
+setwd("C:/Study/My projects/Depth-scatter/Codes")
+rm(list=ls());
+source('misc_functions.R')
+library(rrcov)
+library(fda.usc)
+library(ldr)
+
+n = 80
+V = matrix(0, ncol=2, nrow=n)
+for(i in 1:n){
+  ri = sample(1:4, 1)
+  if(ri==1){
+    V[i,] = c(-1,runif(1,-1,1))
+  }
+  else if(ri==2){
+    V[i,] = c(runif(1,-1,1), 1)
+  }
+  else if(ri==3){
+    V[i,] = c(1,runif(1,-1,1))
+  }
+  else{
+    V[i,] = c(runif(1,-1,1), -1)
+  }
+}
+
+plot(V, pch=19, cex=.3)
+
+p = 1e2
+d = 2
+X = V %*% matrix(rnorm(d*p), nrow=d) + matrix(rnorm(n*p), ncol=p)
+
+X1 = X
+X1[1:5,1] = X1[1:5,1] + 1e5
+
+par(mfrow=c(1,2))
+z = PcaLocantore(t(X1), k=2)
+plot(z@loadings, cex=.5, pch=19)
+
+z = PcaRank(t(X1), k=2)
+plot(z@loadings, cex=.5, pch=19)
+par(mfrow=c(1,1))
+
+# solver function:
+rsir = function(X,y,d,nslices){
+  X = as.matrix(X)
+  n = nrow(X)
+  p = ncol(X)
+
+  sy = ldr.slices(y, nslices=nslices)$slice.indicator
+  uy = unique(sy)
+  luy = length(uy)
+  
+  # get unique mean levels
+  u.mu = matrix(0, ncol=p, nrow=as.numeric(luy))
+  for(i in 1:length(uy)){
+#    u.mu[i,] = apply(X[which(sy == uy[i]),], 2, median)
+    u.mu[i,] = spatial.median(X[which(sy == uy[i]),], delta=1e-5)$mu
+    
+  }
+  Xbar = spatial.median(X, delta=1e-5)$mu
+  u.mu = u.mu - matrix(Xbar, ncol=p, nrow=luy, byrow=T)
+  
+  # get Gamma
+  pcamod = PcaRank(X)
+  Gamma = pcamod@loadings[,1:d]
+  
+  # Get signal part of X
+  muhat = X
+  for(i in 1:n){
+    muhat[i,] = u.mu[which(uy == sy[i]),]
[…]

### 2018-03-20 Codes/sim_depthreg.R

@@ -1,0 +1,50 @@
+rm(list=ls())
+
+## Function to generate multivariate normal observations
+my.mvrnorm = function(n, mu, Sigma){
+  p = length(mu)
+  # compute square root of covariance matrix
+  eo=eigen(Sigma, symmetric=TRUE)
+  sigma.sqrt=eo$vec%*%diag(eo$val^0.5)%*%t(eo$vec)
+  # generate random normals from runif by box-muller transform
+  rnorm.vec = sqrt(-2*log(runif(n*p)))*cos(2*pi*runif(n*p))
+  # generate sample matrix
+  sample.matrix = matrix(rep(mu, n), nrow=n, byrow=T) +
+    matrix(rnorm.vec, nrow=n, ncol=p)%*%sigma.sqrt
+  return(sample.matrix)
+}
+
+## simulation setup
+n = 1e3; p = 4
+v.star = 1
+beta.star = 1:4
+Sigma = diag(p)
+
+X = my.mvrnorm(n=n, mu=rep(0,p), Sigma=Sigma)
+y = my.mvrnorm(n=1, mu=rep(0,n)+X%*%beta.star, Sigma=v.star*diag(n))
+
+npure = 600
+y[(npure+1):n] = y[(npure+1):n] + sample(60:109, (n-npure), replace=T)
+
+beta.mat = matrix(0, nrow=n, ncol=p+1)
+idep = rep(1,n)
+
+iter=1; maxit=100
+for(i in 1:n){
+  ilm = lm(t(y)~X, weights=idep)
+  beta.mat[i,] = ilm$coef
+  ires = residuals(ilm)
+  iPhi = pnorm(ires)
+  idep = iPhi*(1-iPhi)
+}
+
+par(mfrow=c(2,2))
+for(i in 2:5){
+  plot(1:n, beta.mat[,i], type="l")
+}
+par(mfrow=c(1,1))
+
+col.vec = c(rep("green", npure), rep("red", n-npure))
+plot(idep, col=col.vec, pch=19, cex=.5)
+
+plot(ilm$res~ilm$fit, col=col.vec, pch=19)

### 2018-03-23 MS-new/1_Introduction.tex
main paper v1 done, proofs and intro remain

@@
 
-Consider a point $\bfx$ from some $\cX \subseteq \BR^p$, and the spatial sign function $\bfS : \cX \times \BR^p \rightarrow \BR^p$, defined as
+Consider a point $\bfx$ from some $\cX \subseteq \BR^p$, and the spatial sign function $\bfS : \cX \times \BR^p \mapsto \BR^p$, defined as
 %
@@
 \begin{Definition}\label{defn:peripherality}
-For a set of probability measures $\cM$ taking values in $\BR^p$, a {\it peripherality function} $ P : \BR^p \times \cM \rightarrow \BR^+ \cup \{ 0\}$,  is a function that satisfies the following condition:\\
+For a set of probability measures $\cM$ taking values in $\BR^p$, a {\it peripherality function} $ P : \BR^p \times \cM \mapsto \BR^+ \cup \{ 0\}$,  is a function that satisfies the following condition:\\
 
@@
 Firstly, as evident in Figure~\ref{fig:rankplot}, our rank transformation preserves the general shape of the data.
-In fact, if the map $\| \bfx \| \mapsto P(\bfx, \BF)$ is one-one (given a fixed $\BF$), then it is possible to get back $\bfx$ from $\bfR (\bfx; \bfmu_x, \BF)$.
+In fact, if the map $\| \bfx \| \rightarrow P(\bfx, \BF)$ is one-one (given a fixed $\BF$), then it is possible to get back $\bfx$ from $\bfR (\bfx; \bfmu_x, \BF)$.
 It also provides an intuitive extension to any spatial sign-based methodology.

### 2018-03-23 MS-new/3_Scale.tex
main paper v1 done, proofs and intro remain

@@
 \label{section:dcmSection}
-We elaborate on the problem estimating the covariance matrix $\Sigma$ and its eigenvectors and eigenvalues using signed peripherality functions in this section.
-In addition to conditions (P) and (A1), we assume the following conditions on these functions in this section:
+We focus on the estimation of scatter functionals of $\BF$ using peripherality-weighted sign vectors in this section.
+To this end, in addition to conditions (P) and (A1), we assume the following conditions on the peripherality functions:
 
 \vspace{1em}
-\noindent\textbf{(B1)} The following holds:
+\noindent\textbf{(B1)} The following holds for any $\bfx \in \BR^p$ and $t \in (0,1)$:
+%
 $$
@@
 %
-for any $\bfx \in \BR^p$ and $t \in (0,1)$.
 
@@
 Given an inverse depth function $D^-_{\bfX}(\bfx)$ we transform the original random variable as: $\tilde \bfX = D^-_\bfX(\bfx) \bfS(\bfx - \bfmu)$.
-We attempt to use these vector as the proxy of original data for improved estimation of the components of the population covariance matrix $\Sigma$ in this section.
+We attempt to use the transformed data matrix $\tilde \BX = (\tilde \bfx_1, \ldots, \tilde \bfx_n)^T$ as proxy of the original data matrix $\BX$ for improved estimation of the components of the population covariance matrix $\Sigma$ in this section.
 To this end, in Section~\ref{subsec:dcm} we give some results characterizing the population covariance matrix of these vectors, i.e.
 $\BV \tilde \bfX$, and its affine equivariant counterpart.
+{\colrbf details of 3.2 and rest}
 
@@
 \label{subsec:dcm}
-Consider the spectral decomposition of $\Sigma$: $\Sigma = \Gamma\Lambda\Gamma^T$, $\Gamma$ being orthogonal and $\Lambda$ diagonal with positive diagonal elements $\lambda_1, \ldots, \lambda_p$.
+Consider the spectral decomposition of $\Sigma$: $\Sigma = \Gamma\Lambda\Gamma^T$, $\Gamma$ being orthogonal and $\Lambda$ diagonal with positive diagonal elements $\lambda_1 \geq \ldots \geq \lambda_p$.
 Also normalize the original random variable as $\bfZ = \Gamma^T\Lambda^{-1/2} (\bfX - \bfmu)$.
@@
 \begin{eqnarray}
-\tilde \bfX &=& D^-_{\bfX} (\bfX) \bfS(\bfx - \bfmu) \notag \\
+\tilde \bfX &=& D^-_{\bfX} (\bfX) \bfS(\bfX - \bfmu) \notag \\
 &=& D^-_{\Gamma\Lambda^{1/2}\bfZ + \bfmu} (\Gamma\Lambda^{1/2} \bfZ + \bfmu). \bfS(\Gamma\Lambda^{1/2} \bfZ) \notag \\
@@
 Since the sign function $\bfS(\cdot)$ is odd in its argument, it follows that $\BE \tilde \bfX = \bf0$.
-Consequently, we obtain an expression for $\BV \tilde \bfX$, which we call the {\it Depth Covariance Matrix} (DCM):
+Consequently, we obtain an expression for $\tilde \Sigma := \BV \tilde \bfX$, which we call the {\it Depth Covariance Matrix} (DCM).
 
@@
 \begin{equation} \label{equation:covformEq1}
-\BV \tilde \bfX) = \Gamma \Lambda_{D} \Gamma^T,\quad\mbox{with}\quad \Lambda_{D} = \mathbb E_\bfZ \left[ (D^-_\bfZ(\bfz))^2 \frac{\Lambda^{1/2} \bfz \bfz^T \Lambda^{1/2}}{\bfz^T \Lambda \bfz} \right],
+\tilde \Sigma = \Gamma \Lambda_{D} \Gamma^T,\quad\mbox{with}\quad \Lambda_{D} = \mathbb E_\bfZ \left[ (D^-_\bfZ(\bfz))^2 \frac{\Lambda^{1/2} \bfz \bfz^T \Lambda^{1/2}}{\bfz^T \Lambda \bfz} \right],
 \end{equation}
-where $\bfZ = (Z_1,...,Z_p)^T \sim N({\bf 0}, \bfI_p)$, so that $\Lambda_{D}$ a diagonal matrix with diagonal entries
+where $\bfZ = (Z_1,...,Z_p)^T \sim N({\bf 0}, \BI_p)$, so that $\Lambda_{D}$ a diagonal matrix with diagonal entries
 %
@@
 The matrix of eigenvectors $\Gamma$ remains unchanged in the transformation $\bfX \rightarrow \tilde \bfX$.
-As a result, the multivariate rank vectors can be used for robust principal component analysis, which we are going to discuss shortly.
-However, as one can see in the above expression, the diagonal entries of $\Lambda_{D}$ do not change if a scale change is done on all entries of $\Lambda$, meaning the $\Lambda_{D}$ matrices corresponding to $\BF$ and $c \BF$ for some $c \neq 0$ will be same.
-This is the reason the DCM is not equivariant under affine transformations.
+Thus the multivariate rank vectors can be used for robust principal component analysis (which we discuss shortly).
+However, as seen in \eqref{equation:covformEq1}, the diagonal entries of $\Lambda_{D}$ do not change if a scale change is done on all entries of $\Lambda$, meaning the $\Lambda_{D}$ matrices corresponding to $\BF$ and $c \BF$ for some $c \neq 0$ are same.
+Because of this reason, the DCM is not equivariant under affine transformations.
 
-We need to follow the general framework of M-estimation with data-dependent weights \citep{HuberBook81} to construct an affine equivariant counterpart of the DCM.
+We follow the general framework of M-estimation with data-dependent weights \citep{HuberBook81} to construct an affine equivariant counterpart of the DCM.
 Specifically, we implicitly define the Affine-equivariant Depth Covariance Matrix (ADCM) as
@@
 $$
-\Sigma^{(k+1)}_{Dw} = \frac{1}{\BV \tilde Z_1 } \BE_\bfX \left[ \frac{(D^-_\bfX(\bfx))^2 (\Sigma^{(k)}_{Dw})^{1/2} (\bfx - \bfmu) (\bfx - \bfmu)^T (\Sigma^{(k)}_{Dw})^{1/2}}{(\bfx - \bfmu)^T (\Sigma^{(k)}_{Dw})^{-1} (\bfx - \bfmu)} \right].
+\Sigma^{(k+1)}_{Dw} = \frac{1}{\BV \tilde Z_1 } \BE_\bfX \left[ \frac{(D^-_\bfX(\bfx))^2 (\Sigma^{(k)}_{Dw})^{1/2} (\bfx - \bfmu) (\bfx - \bfmu)^T (\Sigma^{(k)}_{Da})^{1/2}}{(\bfx - \bfmu)^T (\Sigma^{(k)}_{Dw})^{-1} (\bfx - \bfmu)} \right].
 $$
@@
 
-To ensure existence and uniqueness of this estimator, let us consider the class of scatter estimators $\Sigma_M$ that are obtained as solutions of the following equation:
+To ensure existence and uniqueness of this estimator, we consider the class of scatter estimators $\Sigma_M$ that are obtained as solutions of the following equation:
 %
 \begin{equation}
-E_{\bfZ_M} \left[ u( \| \bfz_M \| )  \frac{\bfz_M \bfz_M^T}{\| \bfz_M \|^2}  - v( \| \bfz_M \| ) I_p \right] = 0
+E_{\bfZ_M} \left[ u( \| \bfz_M \| )  \frac{\bfz_M \bfz_M^T}{\| \bfz_M \|^2}  - v( \| \bfz_M \| ) \BI_p \right] = 0
 \end{equation}
@@
 \vspace{1em}
-\noindent\textbf{(M1)} The function $u(r)/r^2$ is monotone decreasing, and $u(r)>0$ for $r>0$;
+\noindent\textbf{(C1)} The function $u(r)/r^2$ is monotone decreasing, and $u(r)>0$ for $r>0$;
 
-\noindent\textbf{(M2)}  The function $v(r)$ is monotone decreasing, and $v(r)>0$ for $r>0$;
+\noindent\textbf{(C2)}  The function $v(r)$ is monotone decreasing, and $v(r)>0$ for $r>0$;
 
-\noindent\textbf{(M3)} Both $u(r)$ and $v(r)$ are bounded and continuous;
+\noindent\textbf{(C3)} Both $u(r)$ and $v(r)$ are bounded and continuous;
 
-\noindent\textbf{(M4)} $u(0) / v(0) < p$;
+\noindent\textbf{(C4)} $u(0) / v(0) < p$;
 
-\noindent\textbf{(M5)} For any hyperplane in the sample space $\mathcal X$, (i) $P(H) = E_\bfX 1_{\bfx \in H} < 1 - p v(\infty) / u(\infty)$ and (ii) $P(H) \leq 1/p$.
+\noindent\textbf{(C5)} For any hyperplane in the sample space $\mathcal X$, (i) $P(H) = \BE_\bfX \{ \BI{\bfx \in H} \} < 1 - p v(\infty) / u(\infty)$ and (ii) $P(H) \leq 1/p$.
 %
@@
 \vspace{1em}
-\noindent In our case we take $v(r) = Var(\tilde Z_1)$, i.e.
-a constant, thus (M2) and (M3) are trivially satisfied.
-As for $u$, we notice that most well-known depth functions can be expressed as simple functions of the norm of the standardized random variable.
-For example, $PD_\bfZ (\bfz) = (1 - G(\| \bfz \|); MhD_\bfZ (\bfz) = (1+\| \bfz \|^2)^{-1}; HSD_\bfZ (\bfz) = (1+\| \bfz \|)^{-1}$ etc., so that we can take as $u$ square of the corresponding peripherality functions:
+\noindent Putting things into context, in our case we have $v(r) = \BV\tilde Z_1, u(r) = (D^-_\bfX(\bfx))^2 = (D^-_\bfZ(\bfz))^2$.
+Since $v(r)$ is a constant, (C2) and (C3) are trivially satisfied.
+As for $u$, most well-known depth functions can be expressed as simple functions of the norm of the standardized random variable.
+For example, for Halfspace Depth (HSD) we have $D_\bfZ (\bfz) = (1 - G(\| \bfz \|)$, for Mahalanobis Depth (MhD) we have $D_\bfZ (\bfz) = (1+\| \bfz \|^2)^{-1}$ and for Projection Depth (PD) we have $D_\bfZ (\bfz) = (1+\| \bfz \|//MAD(G))^{-1}$, where $G$ is the cumulative distribution function of $g$, and MAD is median absolute deviation.
+Combined with the choice of inverse transformation, we get
 % Var(Z1) breaks into two independent parts: depth and sign. So can check m4 and M5 here itself.
 $$
-u_{PD} (r) = G^2 (r); \quad u_{MhD}(r)  = \frac{r^4}{(1 + r^2)^2}; \quad u_{HSD}(r)  = \frac{r^2}{(1 + r/G^{-1}(0.75))^2}
+u_{HSD} (r) = G^2 (r); \quad u_{MhD}(r)  = \frac{r^4}{(1 + r^2)^2}; \quad u_{PD}(r)  = \frac{r^2}{(1 + r/MAD(G))^2}.
 $$
 %
-
-It is easy to verify that the above choices of $u$ satisfy (M1) and (M3).
-To check (M4) and (M5), first notice that $\bfZ$ has a spherically symmetric distribution, so that its norm and sign are independent.
-Since $D_\bfZ(\bfz)$ depends only on $\| \bfz \|$, we have
+It is easy to verify that the above choices of $u$ satisfy (C1) and (C3).
+To check (C4) and (C5), notice that $\bfZ$ has a spherically symmetric distribution, so that its euclidean norm and spatial sign are independent.
+Since $D_\bfZ(\bfz)$ depends only on $\| \bfz \|$, we now have
 %
 $$
-Var (\tilde Z_1) = Var \left( D^-_\bfZ (\bfZ) \frac{Z_1}{ \|\bfZ \|} \right) = Var (D^-_\bfZ (\bfZ)) Var (S_1 (\bfZ)) = \frac{1}{p} Var (D^-_\bfZ (\bfZ))
+\BV \tilde Z_1 = \BV \left( D^-_\bfZ (\bfZ) \frac{Z_1}{ \|\bfZ \|} \right) = \BV (D^-_\bfZ (\bfZ)) \BV (S_1 (\bfZ)) = \frac{1}{p} \BV (D^-_\bfZ (\bfZ)),
 $$
 %
-as $Cov(\bfS(\bfZ)) = Cov((S_1(\bfZ), S_2(\bfZ), ..., S_p(\bfZ))^T) = I_p/p$.
-Now for MhD and HSD $u(\infty)=1, u(0)=0$, so (M4) and (M5) are immediate.
-To achieve this for PD, we only need to replace $u_{PD}(r)$ with $u_{PD}^*(r) = G^2(r) - 1/4$.
+as $\BV(\bfS(\bfZ)) = \BV((S_1(\bfZ), S_2(\bfZ), ..., S_p(\bfZ))^T) = \BI_p/p$.
+Now for MhD and PD $u(\infty)=1, u(0)=0$, so (C4) and (C5) are immediate.
+To achieve this for HSD, we only need to replace $u_{HSD}(r)$ with $u_{HSD*}(r) = G^2(r) - 1/4$.
 
 \subsection{Calculating the sample DCM and ADCM}
-Let us now consider $n$ iid random draws from our elliptic distribution $F$, say $\bfX_1,...,\bfX_n$.
-For ease of notation, denote $SS(\bfx; \bfmu) = \bfS(\bfx - \bfmu) \bfS(\bfx - \bfmu)^T$.
-Then, given the depth function and known location center $\bfmu$, one can show that the vectorized form of $\sqrt n$-times the sample DCM: $\sum_{i=1}^n (D^-_\bfX(\bfx_i))^2SS(\bfx_i; \bfmu) /\sqrt{n}$  has an asymptotic multivariate normal distribution with mean $\sqrt n.vec(E[( (D^-_\bfX (\bfX))^2 SS(\bfx; \bfmu)])$ and a certain covariance matrix by straightforward application of the central limit theorem (CLT).
-But in practice the population depth function $D_\bfX(\bfx) = D(\bfx, F)$ is estimated by the depth function based on the empirical distribution function, $F_n$.
-Denote this sample depth by $D^n_\bfX (\bfx) = D(\bfx, F_n)$.
-Here we make the following assumption regarding how it approximates $D_\bfX(\bfx)$:
+Let us denote $\BS(\bfx; \bfmu) = \bfS(\bfx - \bfmu) \bfS(\bfx - \bfmu)^T$.
+Then, given the depth function and {\it known} location center $\bfmu$, one can show that the vectorized form of $\sqrt n$-times the sample DCM, i.e.
+$n^{-1/2} \sum_{i=1}^n (D^-_\bfX(\bfx_i))^2 \BS (\bfx_i; \bfmu)$  has an asymptotic multivariate normal distribution with mean $\sqrt n.
+\ve( \BE [( (D^-_\bfX (\bfX))^2 \BS(\bfx; \bfmu)])$ and some covariance matrix by straightforward application of the central limit theorem (CLT).
+But in practice the depth at any point $\bfx$ is estimated by the sample depth, i.e.
+depth calculated using empirical distribution function in place of $\BF$.
+We also need to replace the known location parameter $\bfmu$ by some estimator $\hat\bfmu_n$.
+
+Denote this sample depth by $D^n_\bfX (\bfx)$, and the inverse depth by $D^{n-}_\bfX (\bfx)$. Here we make the following assumption regarding the sample depths:
 
 \vspace{1em}
-\noindent\textbf{(D5)} \textit{Uniform convergence}: $\sup_{\bfx \in \mathbb R^p} | D^n_\bfX (\bfx) - D_\bfX (\bfx) | \rightarrow 0$ as $n \rightarrow \infty $.
+\noindent\textbf{(D1)} \textit{Uniform convergence}: $\sup_{\bfx \in \mathbb R^p} | D^n_\bfX (\bfx) - D_\bfX (\bfx) | \rightarrow 0$ as $n \rightarrow \infty $.
 \vspace{1em}
 
-The assumption that empirical depths converge uniformly at all points $\bfx$ to their population versions holds under very mild conditions for several well known depth functions: for example projection depth \citep{zuo03} and simplicial depth \citep{Dumbgen92}.
-One also needs to replace the known location parameter $\bfmu$ by some estimator $\hat\bfmu_n$.
-Examples of robust estimators of location that are relevant here include the spatial median \citep{haldane48,brown83}, Oja median \citep{oja83}, projection median \citep{zuo03} etc.
-Now, given $D^n_\bfX(.)$ and $\hat \bfmu_n$, to plug them into the sample DCM and still go through with the CLT we need the following result:
+\noindent The above holds under very mild conditions for several depth functions, e.g.
+projection depth \citep{zuo03} and simplicial depth \citep{Dumbgen92}.
+For $\hat \bfmu_n$ we use a robust estimate of location, examples of which include the spatial median \citep{haldane48,brown83}, Oja median \citep{oja83} and projection median \citep{zuo03}.
+
+To plug in the above estimates to the sample DCM and go through with the CLT, we need the following result.
 
 \begin{Lemma} \label{Lemma:lemma1}
-Consider a random variable $\bfX \in \mathbb{R}^p$ having a continuous and symmetric distribution with location center $\bfmu$ such that $E\|\bfx - \bfmu \|^{-3/2} < \infty$.
-Given $n$ random samples from this distribution, suppose $\hat\bfmu_n$ is an estimator of $\bfmu$ so that $\sqrt n (\hat\bfmu_n - \bfmu) = O_P(1) $.
-Then with the above notations, and given the assumption (D5) we have
+Consider a random variable $\bfX \in \mathbb{R}^p$ having a continuous and symmetric distribution with location center $\bfmu$ such that $\BE \|\bfx - \bfmu \|^{-3/2} < \infty$.
+For a size-$n$ random sample from this distribution, suppose $\hat\bfmu_n$ is an estimator of $\bfmu$ so that $\hat\bfmu_n - \bfmu = O_P(n^{-1/2}) $.
+Then, given assumption (D1) we have
 %
-$$ \sqrt n \left[
-\frac{1}{n} \sum_{i=1}^n (D^{-n}_\bfX (\bfx_i))^2 SS(\bfx_i; \hat\bfmu_n) -
-\frac{1}{n} \sum_{i=1}^n (D^-_\bfX (\bfx_i))^2 SS(\bfx_i; \bfmu) \right]
-\stackrel{P}{\rightarrow} 0 $$
+$$
+\frac{1}{n} \sum_{i=1}^n (D^{n-}_\bfX (\bfx_i))^2 \BS(\bfx_i; \hat\bfmu_n) = \frac{1}{n} \sum_{i=1}^n (D^-_\bfX (\bfx_i))^2 \BS(\bfx_i; \bfmu)
++ \BR_n,
+$$
+%
+where $\| \BR_n \|_\infty = o_P(n^{-1/2})$.
 \end{Lemma}
 
-Following this, we are now in a position to state the result for consistency of the sample DCM:
+\noindent We are now in a position to state the result for consistency of the sample DCM:
 
 \begin{Theorem} \label{Theorem:rootn}
-Consider $n$ iid samples from the distribution in Lemma \ref{Lemma:lemma1}.
+Consider a size-$n$ random sample from the distribution in Lemma \ref{Lemma:lemma1}.
 Then, given a depth function $D_\bfX(.)$ and an estimate of center $\hat\bfmu_n$ so that $\sqrt n(\hat \bfmu_n - \bfmu) = O_P(1)$,
 %
-$$ \sqrt n \left[ vec\left\{ \frac{1}{n} \sum_{i=1}^n (D^{-n}_\bfX (\bfx_i))^2 SS(\bfx_i; \hat\bfmu_n) \right\} - E \left[ vec\left\{ (D^-_\bfX (\bfx))^2 SS(\bfx; \bfmu) \right\} \right] \right]
-\stackrel{D}{\rightarrow}
-N_{p^2} ({\bf 0}, V_{D,S}(F)) $$
-$$ \text{with } V_{D,S}(F) = Var \left[vec \left\{ (D^-_\bfX (\bfx))^2 SS(\bfx; \bfmu) \right\} \right] $$
+$$ \ve \left\{ \frac{1}{n} \sum_{i=1}^n (D^{n-}_\bfX (\bfx_i))^2 \BS(\bfx_i; \hat\bfmu_n) \right\} -
+\BE [ \ve \left\{ (D^-_\bfX (\bfx))^2 \BS(\bfx; \bfmu) \right\} ] \rightsquigarrow
+\cN_{p^2} ({\bf 0}, \BV_D(\BF)) + \bfR_n,
+$$
+%
+with $\BV_D(\BF) = \BV [\ve \{ (D^-_\bfX (\bfx))^2 \BS(\bfx; \bfmu) \} ] $ and $\| \bfR_n \|_\infty = o_P(n^{-1/2})$.
 \end{Theorem}
 
-\noindent In case $F$ is elliptical, an elaborate form of the covariance matrix $V_{D,S}(F)$ explicitly specifying each of its elements (more directly those of its $\Gamma^T$-rotated version) can be obtained, which is given in Appendix \ref{section:appA}.
+\noindent When $\BF$ is elliptical, an elaborate form of the covariance matrix $\BV_D(\BF)$ explicitly specifying each of its elements (more directly those of its $\Gamma^T$-rotated version) can be obtained (see Appendix \ref{section:appA}).
 This form is useful when deriving limiting distributions of eigenvectors and eigenvalues of the sample DCM.
 
-In contrast to the DCM, the issue of estimating $\bfmu$ to plug into the ADCM is easily handled by simultaneously solving for the location and scatter functionals ($\bfmu_{Dw}, \Sigma_{Dw}$):
+For ADCM, we simultaneously estimate its sample version and the mean vector $\bfmu$ by solving for the location and scatter functionals ($\bfmu_{Dw}, \Sigma_{Dw}$):
 %
 \begin{eqnarray}
-E \left[ \frac{\Sigma_{Dw}^{-1/2} (\bfx - \bfmu_{Dw})}{ \| \Sigma_{Dw}^{-1/2}(\bfx - \bfmu_{Dw}) \|} \right] &=& {\bf 0}_p \label{eqn:AffineMedian}\\
-E \left[ \frac{(D^-_\bfX(\bfx))^2 \Sigma_{Dw}^{-1/2} (\bfx - \bfmu_{Dw}) (\bfx - \bfmu_{Dw})^T \Sigma_{Dw}^{-1/2}}{(\bfx - \bfmu_{Dw})^T \Sigma_{Dw}^{-1} (\bfx - \bfmu_{Dw})} \right] &=& Var (\tilde Z_1) I_p \label{eqn:AffineCov}
+\BE \left[ \frac{\Sigma_{Dw}^{-1/2} (\bfx - \bfmu_{Dw})}{ \| \Sigma_{Dw}^{-1/2}(\bfx - \bfmu_{Dw}) \|} \right] &=& {\bf 0}_p, \label{eqn:AffineMedian}\\
+\frac{1}{\BV \tilde Z_1}
+\BE \left[ \frac{(D^-_\bfX(\bfx))^2 \Sigma_{Dw}^{-1/2} (\bfx - \bfmu_{Dw}) (\bfx - \bfmu_{Dw})^T \Sigma_{Dw}^{-1/2}}{(\bfx - \bfmu_{Dw})^T \Sigma_{Dw}^{-1} (\bfx - \bfmu_{Dw})} \right] &=& \BI_p.
+\label{eqn:AffineCov}
 \end{eqnarray}
 %
-In the framework of (\ref{eqn:ADCM}), for any fixed $\Sigma_M$ there exists a unique and fixed solution of the location problem $E_{\bfZ_M} (w(\| \bfz_M \| \bfz_M) = {\bf 0}_p $ under the following condition:
+In the M-estimation framework of \cite{HuberBook81}, for any fixed $\Sigma_M$ there exists a unique and fixed solution of the general location problem $\BE_{\bfZ_M} (w(\| \bfz_M \| \bfz_M) = {\bf 0}_p $ under the following condition:
 
 \vspace{1em}
-\noindent\textbf{(M6)} The function $w(r)r$ is monotone increasing for $r>0$.
+\noindent\textbf{(D2)} The function $w(r)r$ is monotone increasing for $r>0$.
 
 \vspace{1em}
-\noindent This condition is easy to verify for our choice of the weights: $w(\| \bfz_M \| ) = D^-_{\bfZ_M} (\bfz_M) / \| \bfz_M \|$.
-Uniqueness of simultaneous fixed point solutions of \ref{eqn:AffineMedian} and \ref{eqn:AffineCov} is guaranteed when $\bfX$ has a symmetric distribution \citep{HuberBook81}.
+\noindent This is easy to verify for our choice of the weights: $w(\| \bfz_M \| ) = D^-_{\bfZ_M} (\bfz_M) / \| \bfz_M \|$.
+Uniqueness of simultaneous fixed point solutions of \eqref{eqn:AffineMedian} and \eqref{eqn:AffineCov} is guaranteed when $\bfX$ has a symmetric distribution \citep{HuberBook81}, which we also satisfy since $\bfX \sim \BF$, an elliptical distribution,
 
-In practice it is difficult to calculate the scale multiple $Var (\tilde Z_1)$ analytically for known depth functions and an arbitrary $F$.
-Here we instead obtain its standardized version $\Sigma_{Dw}^* = \Sigma_{Dw} / Var(\tilde Z_1)$ (so that the determinant equals 1), alongwith $\bfmu_{Dw}$ using the following iterative algorithm:
+In practice, it is difficult to calculate the scale multiple $\BV \tilde Z_1$ analytically for known depth functions and an arbitrary $\BF$.
+We bypass this by instead obtaining a standardized version of the scatter functional: $\Sigma_{Dw}^* = \Sigma_{Dw} / \BV \tilde Z_1$ (and $\bfmu_{Dw}$) using the following iterative algorithm:
 
 \begin{enumerate}
-\item Start from some initial estimates $(\bfmu_{Dw}^{(0)}, \Sigma_{Dw,(0)})$. Set $t=0$;
+\item Start from some initial estimates $(\bfmu_{Dw}^{(0)}, \Sigma_{Dw}^{(0)}$. Set $t=0$;
 
-\item Calculate the standardized observations $\bfz_i^{(t)} = \Sigma_{Dw,(t)}^{-1/2} (\bfx_i - \bfmu_{Dw}^{(t)})$;
+\item Calculate the standardized observations $\bfz_i^{(t)} = (\Sigma_{Dw}^{(t)})^{-1/2} (\bfx_i - \bfmu_{Dw}^{(t)})$;
 
@@
 $$
-\bfmu_{Dw}^{(t+1)} = \frac{\sum_{i=1}^n \tilde \bfx_i / \| \bfz_i^{(t)} \| }{\sum_{i=1}^n 1 / \| \bfz_i^{(t)} \|}
+\bfmu_{Dw}^{(t+1)} = \frac{\sum_{i=1}^n \tilde \bfx_i / \| \bfz_i^{(t)} \| }{\sum_{i=1}^n 1 / \| \bfz_i^{(t)} \|};
 $$
@@
 $$
-\Sigma_{Dw}^{*(t+1)} = \frac{1}{n} \sum_{i=1}^n \frac{(D^{-n}_\bfX (\bfx_i))^2 (\bfx_i - \bfmu_{Dw}^{(t+1)})(\bfx_i - \bfmu_{Dw}^{(t+1)})^T}{\| \bfz_i^{(t)} \|^2}; \quad \Sigma_{Dw}^{*(t+1)} \leftarrow \frac{\Sigma_{Dw}^{*(t+1)}}{\text{det} (\Sigma_{Dw}^{*(t+1)})^{1/p}}
+\Sigma_{Dw}^{*(t+1)} = \frac{1}{n} \sum_{i=1}^n \frac{(D^{n-}_\bfX (\bfx_i))^2 (\bfx_i - \bfmu_{Dw}^{(t+1)})(\bfx_i - \bfmu_{Dw}^{(t+1)})^T}{\| \bfz_i^{(t)} \|^2}; \quad \Sigma_{Dw}^{*(t+1)} \leftarrow \frac{\Sigma_{Dw}^{*(t+1)}}{\text{det} (\Sigma_{Dw}^{*(t+1)})^{1/p}}.
 $$
@@
 
-Since we are mainly interested in using the DCM for robust principal components analysis, from now on we assume that the eigenvalues of $\Sigma$ are distinct: $\lambda_1 > \lambda_2 > ...
-> \lambda_p$ to obtain asymptotic distributions of its eigenvectors.
-In case any of the eigenvalues have multiplicity larger than 1, limiting distributions of the corresponding eigenprojection matrices can be obtained analogous to those of the sign covariance matrix \citep{magyar14}.
+We are mainly interested in using the DCM for robust principal component analysis (PCA).
+We assume that the eigenvalues of $\Sigma$ are distinct: $\lambda_1 > \lambda_2 > ...
+> \lambda_p$, for ease of obtaining asymptotic distributions of eigenvectors of the DCM (Appendix \ref{section:appB}).
+Limiting distributions for the case of non-unique eigenvalues can be obtained following \cite{magyar14}.
 
 \subsubsection{Influence functions}
-We start with deriving the influence functions for eigenvectors of the DCM and ADCM.
-This will help in demonstrating the robustness of their estimates, as well as deriving the asymptotic distributions of their sample counterparts.
-Influence functions of the DCM as well as its eigenvectors and eigenvalues, which are essential to understand how much influence a sample point, especially an infinitesimal contamination, has on any functional on the distribution \citep{HampelBook86}.
-Given any probability distribution $F$, the influence function of any point $\bfx_0$ in the sample space $\mathcal{X}$ for some functional $T(F)$ on the distribution is defined as
+To demonstrate the robustness of eigenvector estimates of the DCM and ADCM, we derive their influence functions.
+Influence functions quantify how much influence a sample point, especially an infinitesimal contamination, has on any functional of a probability distribution \citep{HampelBook86}.
+Given any probability distribution $\BH \in \cM$, the influence function of any point $\bfx_0 \in \mathcal{X}$ for some functional $T(\BH)$ on the distribution is defined as
 %
-$$ IF(\bfx_0; T,F) = \lim_{\epsilon \rightarrow 0} \frac{1}{\epsilon} (T(F_\epsilon) - T(F)) $$
+$$
+IF(\bfx_0; T,\BH) =
+\lim_{\epsilon \rightarrow 0} \frac{1}{\epsilon} (T(\BH_\epsilon) - T(\BH))
+$$
 %
-where $F_\epsilon$ is $F$ with an additional mass of $\epsilon$ at $\bfx_0$, i.e.
-$F_\epsilon = (1-\epsilon)F + \epsilon \Delta_{\bfx_0}$; $\Delta_{\bfx_0}$ being the distribution with point mass at $\bfx_0$.
-When $T(F) = E_F g$ for some $F$-integrable function $g$, $IF(\bfx_0; T,F) = g(\bfx_0) - T(F)$.
+where $\BH_\epsilon$ is $\BH$ with an additional mass of $\epsilon$ at $\bfx_0$, i.e.
+$\BH_\epsilon = (1-\epsilon)\BH + \epsilon \Delta_{\bfx_0}$; $\Delta_{\bfx_0}$ being the distribution with point mass at $\bfx_0$.
+When $T(\BH) = E_\BH f$ for some $\BH$-integrable function $f$, $IF(\bfx_0; T,\BH) = f(\bfx_0) - T(\BH)$.
+
 It now follows that for the DCM,
 %
-$$ IF(\bfx_0; Cov(\tilde \bfX), F) = (D^-_\bfX(\bfx_0))^2 SS(\bfx_0; \bfmu) - Cov(\tilde \bfX) $$
-
-Following \cite{croux00}, we now get the influence function of the $i^\text{th}$ eigenvector of $Cov(\tilde\bfX)$, say $\bfgamma_D = (\bfgamma_{D,1},...,\bfgamma_{D,p}); i = 1,...,p$:
+$$
+IF(\bfx_0; \tilde \Sigma, \BF) =
+(D^-_\bfX(\bfx_0))^2 \BS(\bfx_0; \bfmu) - \tilde \Sigma.
+$$
+%
+Following \cite{croux00}, we get the influence function of the $i^\text{th}$ eigenvector of $\tilde \Sigma$, say $\bfgamma_D = (\gamma_{D,1},...,\gamma_{D,p})^T$ for $1 \leq i \leq p$:
 %
 \begin{eqnarray}
-IF(\bfx_0; \bfgamma_{D,i}, F) &=& \sum_{k=1; k \neq i}^p \frac{1}{\lambda_{D,S,i} - \lambda_{D,S,k}} \left\{ \bfgamma^T_k IF(\bfx_0; Cov(\tilde \bfX), \bfgamma_i) \right\} \bfgamma_k \notag \\
-&=& \sum_{k=1; k \neq i}^p \frac{1}{\lambda_{D,S,i} - \lambda_{D,S,k}} \left\{ \bfgamma^T_k (D^-_\bfX(\bfx_0))^2 SS(\bfx_0; \bfmu)\bfgamma_i - \lambda_{D,S,i}\bfgamma_k^T\bfgamma_i \right\} \bfgamma_k \notag \\
-&=& \sum_{k=1; k \neq i}^p \frac{\sqrt{\lambda_i \lambda_k} z_{0i} z_{0k}}{\lambda_{D,S,i} - \lambda_{D,S,k}}. \frac{(D^-_\bfZ(\bfz_0))^2 }{\bfz_0^T \Lambda \bfz_0} \bfgamma_k
+IF(\bfx_0; \bfgamma_{D,i}, \BF) &=&
+\sum_{k=1; k \neq i}^p \frac{1}{\lambda_{D,i} - \lambda_{D,k}} \left\{ \bfgamma^T_k IF(\bfx_0; \tilde \Sigma, \bfgamma_i) \right\} \bfgamma_k \notag \\
+&=& \sum_{k=1; k \neq i}^p \frac{1}{\lambda_{D,i} - \lambda_{D,k}}
+\left\{ \bfgamma^T_k (D^-_\bfX(\bfx_0))^2 \BS(\bfx_0; \bfmu)\bfgamma_i - \lambda_{D,i}\bfgamma_k^T\bfgamma_i \right\} \bfgamma_k \notag \\
+&=& \sum_{k=1; k \neq i}^p \frac{\sqrt{\lambda_i \lambda_k} z_{0i} z_{0k}}{\lambda_{D,i} - \lambda_{D,k}}. \frac{(D^-_\bfZ(\bfz_0))^2 }{\bfz_0^T \Lambda \bfz_0} \bfgamma_k \notag\\
+&=& \sum_{k=1; k \neq i}^p \frac{(D^-_\bfZ(\bfz_0))^2 \BS_{ik}(\Lambda^{1/2} \bfz_0; {\bf 0})}{\lambda_{D,i} - \lambda_{D,k}} \bfgamma_k,
 \end{eqnarray}
 %
-where $\Gamma^T \Lambda^{-1/2} (\bfx_0 - \bfmu) = \bfz_0 = (z_{01},...,z_{0p})^T$. Clearly this influence function will be bounded, which indicates good robustness properties of principal components.
-
-For the ADCM, we first notice that the influence function of any affine equivariant estimate of scatter can be expressed as
-%
-$$
-IF(\bfx_0, C, F) = \alpha_C (\| \bfz_0 \| ) \frac{\bfz_0 \bfz_0^T}{\bfz_0^T \bfz_0} - \beta_C( \| \bfz_0 \| ) C
-$$
-%
-for scalar valued functions $\alpha_C, \beta_C$ \citep{HampelBook86}. Following this, the influence function of an eigenvector $\bfgamma_{C,i}$ of $C$ is derived:
-%
-$$
-IF(\bfx_0, \bfgamma_{C,i}, F) = \alpha_C(\| \bfz_0 \|) \sum_{k=1, k \neq i}^p \frac{\sqrt {\lambda_i \lambda_k}}{\lambda_i - \lambda_k}. \frac{z_{0i} z_{0k}}{\bfz_0^T \bfz_0} \bfgamma_k
-$$
-%
-When $C=\Sigma_M$, i.e. the solution to (\ref{eqn:ADCM}), then \cite{HuberBook81} shows that
-%
-$$
-\alpha_C (\| \bfz_0 \|) = \frac{p(p+2) u (\| \bfz_0 \|)}{E_{F_0} \left[ p u(\| \bfy \| ) + u'(\| \bfy \|) \| \bfy \| \right] }
-$$
-%
-Setting $u( \| \bfz_0 \|) = ( D^-_\bfZ (\bfz_0))^2$ ensures that the influence function of eigenvectors of the ADCM is bounded as well as increasing in magnitude with $\| \bfz_0 \|$.
+where $\Gamma^T \Lambda^{-1/2} (\bfx_0 - \bfmu) = \bfz_0 = (z_{01},...,z_{0p})^T$.
+Clearly this influence function is bounded, indicating good robustness properties of the principal component estimates.
 
@@
 
-In Figure \ref{fig:IFnorm} we consider first eigenvectors of our scatter estimates, as well as teo well-known robust estimates of scatter: the Sign Covariance Matrix (SCM) and Tyler's shape matrix, for the $\mathcal{N}_2((0,0)^T, \diag(2,1))$ and plot norms of these influence functions for different values of $\bfx_0$.
+In Figure \ref{fig:IFnorm} we consider first eigenvectors of the DCM and two other well-known robust estimates of scatter: the Sign Covariance Matrix (SCM) and Tyler's shape matrix \citep{tyler87}.
+We set $\BF \equiv \mathcal{N}_2({\bf 0}, \diag(2,1))$ and plot norms of the eigenvector influence functions for different values of $\bfx_0$.
 Influence function for the $i^\text{th}$ eigenvectors of these two matrices (say $\bfgamma_{S,i}$ and $\bfgamma_{T,i}$, respectively) are as follows:
 %
-\begin{eqnarray*}
-\quad IF(\bfx_0; \bfgamma_{S,i}, F) &=& \sum_{k=1; k \neq i}^p \frac{\sqrt{\lambda_i \lambda_k}}{\lambda_{S,i} - \lambda_{S,k}}.
-\frac{z_{0i} z_{0k}}{\bfz_0^T \Lambda \bfz_0} \bfgamma_k, \text{ with } \lambda_{S,i} = E_\bfZ \left( \frac{\lambda_i z_i^2}{\sum_{j=1}^p \lambda_j z_j^2} \right) \quad \\
-IF(\bfx_0; \bfgamma_{T,i}, F) &=& (p+2) \sum_{k=1; k \neq i}^p \frac{\sqrt{\lambda_i \lambda_k}}{\lambda_i - \lambda_k}. \frac{z_{0i} z_{0k}}{\bfz_0^T \bfz_0} \bfgamma_k \quad 
-\end{eqnarray*}
+\begin{eqnarray}
+\quad IF(\bfx_0; \bfgamma_{S,i}, \BF) &=&
+\sum_{k=1; k \neq i}^p \frac{\BS_{ik}(\Lambda^{1/2} \bfz_0, {\bf 0})}{\lambda_{S,i} - \lambda_{S,k}} \bfgamma_k; \quad
+\lambda_{S,i} = \BE_\bfZ \left( \frac{\lambda_i z_i^2}{\sum_{j=1}^p \lambda_j z_j^2} \right),\\
+IF(\bfx_0; \bfgamma_{T,i}, \BF) &=& (p+2) \sum_{k=1; k \neq i}^p \frac{\sqrt{\lambda_i \lambda_k}}{\lambda_i - \lambda_k}\BS_{ik}(\bfz_0; {\bf 0}) \bfgamma_k. \label{eqn:IFeqnTyler}
+\end{eqnarray}
 %
-Their corresponding plots demonstrate the 'inlier effect', i.e.
-points close to symmetry center and the center itself having high influence, which results in loss of efficiency.
-The influence function for the sample covariance matrix is obtained by replacing $(p+2)$ by $\| \bfz_0 \|^2$ in the expression of $IF(\bfx_0; \bfgamma_{T,i}, F)$ above, hence is unbounded and the corresponding eigenvector estimators are not robust.
-In comparison, all three DCMs considered here have a bounded influence function as well as small values of the influence function at 'deep' points.
+Their corresponding plots (panels (b) and (c) in Figure~\ref{fig:IFnorm}) demonstrate an `inlier effect', i.e.
+points close to symmetry center and the center itself having high influence: which results in loss of efficiency.
+The influence function for eigenvector estimates of the sample covariance matrix is obtained by replacing $(p+2)$ by $\| \bfz_0 \|^2$ in \eqref{eqn:IFeqnTyler}, hence is unbounded and makes the corresponding estimates non-robust.
+In comparison, all three DCMs considered have bounded influence functions {\it and} small values of the influence function at `deep' points.
+
+For the ADCM, we first notice that the influence function of any affine equivariant estimate of scatter can be expressed as
+%
+$$
+IF(\bfx_0, C, \BF) = \alpha_C (\| \bfz_0 \| ) \BS(\bfz_0; {\bf 0}) - \beta_C( \| \bfz_0 \| ) C
+$$
+%
+for scalar valued functions $\alpha_C, \beta_C$ \citep{HampelBook86}. Following this, the influence function of an eigenvector $\bfgamma_{C,i}$ of $C$ is derived:
+%
+$$
+IF(\bfx_0, \bfgamma_{C,i}, \BF) = \alpha_C(\| \bfz_0 \|) \sum_{k=1, k \neq i}^p \frac{\sqrt {\lambda_i \lambda_k}}{\lambda_i - \lambda_k}. \BS_{ik}(\bfz_0; {\bf 0}) \bfgamma_k.
+$$
+%
+When $C=\Sigma_M$, i.e. the solution to (\ref{eqn:ADCM}), \cite{HuberBook81} shows that
+%
+$$
+\alpha_C (\| \bfz_0 \|) = \frac{p(p+2) u (\| \bfz_0 \|)}{\BE_{\bfZ} \left[ p u(\| \bfz \| ) + u'(\| \bfz \|) \| \bfz \| \right] }.
+$$
+%
+In our case $u( \| \bfz_0 \|) = ( D^-_\bfZ (\bfz_0))^2$, thus the influence function of eigenvectors of the ADCM is a bounded increasing function of $\| \bfz_0 \|$.
 
@@
 \cite{taskinen12,ollilia03}).
-Suppose $\hat C$ is a $\sqrt n$-consistent estimator of a scatter functional $C$. Then the asymptotic variance of its eigenvectors are \cite{anderson}
+The asymptotic variance of the $i\Th$ eigenvector of the sample covariance matrix, say $\hat \bfgamma_i$, is \citep{anderson}:
 %
 \begin{equation} \label{equation:covevEq}
-AVar(\sqrt n\hat \bfgamma_{c,i}) = \sum_{k=1; k \neq i}^p \frac{\lambda_i \lambda_k}{(\lambda_i - \lambda_k)^2} \bfgamma_k \bfgamma_k^T
+A\BV( \sqrt n\hat \bfgamma_{i}) = \sum_{k=1; k \neq i}^p \frac{\lambda_i \lambda_k}{(\lambda_i - \lambda_k)^2} \bfgamma_k \bfgamma_k^T; \quad
+1 \leq i \leq p.
 \end{equation}
 %
-The asymptotic relative efficiencies of eigenvectors from the sample DCM with respect to the sample covariance matrix can now be derived using (\ref{equation:covevEq}) above and (\ref{equation:DevEq}) from Corollary \ref{Corollary:eigendist}:
+Asymptotic relative efficiencies of eigenvectors from the sample DCM with respect to the sample covariance matrix can now be derived using (\ref{equation:covevEq}) and (\ref{equation:DevEq}) from Corollary \ref{Corollary:eigendist} from Appendix \ref{section:appB}:
 %
 \begin{eqnarray*}
-ARE(\hat\bfgamma^D_i, \hat\bfgamma_i; F) &=& \frac{\Tr( AVar(\sqrt n\hat \bfgamma_i))}{\Tr( AVar(\sqrt n\hat \bfgamma^D_i))}\\
-&=& \left[\sum_{k=1; k \neq i}^p \frac{\lambda_i \lambda_k}{(\lambda_i - \lambda_k)^2} \right] \left[ \sum_{k=1; k \neq i}^p \frac{\lambda_i \lambda_k }{(\lambda_{D,s,i} - \lambda_{D,S,k})^2} E \left( \frac{(D^-_\bfZ (\bfz))^4 z_i^2 z_k^2}{(\bfz^T \Lambda \bfz)^2} \right) \right]^{-1}
+ARE(\hat\bfgamma_{D,i}, \hat\bfgamma_i; \BF) &=& \frac{\Tr( A\BV ( \sqrt n\hat \bfgamma_i))}{\Tr( A\BV(\sqrt n\hat \bfgamma_{D,i}))}\\
+&=& \left[\sum_{k=1; k \neq i}^p \frac{\lambda_i \lambda_k}{(\lambda_i - \lambda_k)^2} \right] \left[ \sum_{k=1; k \neq i}^p
+\frac{\BE [ (D^-_\bfZ (\bfz))^4 (\BS_{ik} (\Lambda^{1/2} \bfz; {\bf 0}))^2 ]}{(\lambda_{D,i} - \lambda_{D,k})^2} \right]^{-1}.
 \end{eqnarray*}
@@
 $$
-AVar (\sqrt n  \hat\bfgamma_{C,j}) = ASV (C_{12}, F_0) \sum_{k=1, k \neq i}^p \frac{\lambda_i \lambda_k}{\lambda_i - \lambda_k}. \bfgamma_i \bfgamma_k^T
+A\BV (\sqrt n  \hat\bfgamma_{C,j}) = A\BV (C_{12}, \BF_0) \sum_{k=1, k \neq i}^p \frac{\lambda_i \lambda_k}{\lambda_i - \lambda_k}. \bfgamma_i \bfgamma_k^T,
 $$
 %
-where $ASV (C_{12}, F_0)$ is the asymptotic variance of an off-diagonal element of $C$ when the underlying distribution is $F_0$. Following \cite{croux00} this equals
+where $A\BV (C_{12}, \BF_0)$ is the asymptotic variance of an off-diagonal element of $C$ when the underlying distribution is $\BF_0 \equiv \cE({\bf 0}, \BI_p, g)$.
+Following \cite{croux00} this equals
 %
 $$
-ASV (C_{12}, F_0) = E_{F_0} \left[ \alpha_c (\| \bfz \|)^2 (S_1(\bfz)S_2 (\bfz))^2 \right] = E_{F_0} \alpha_C (\| \bfz \|)^2 . E_{F_0} (S_1(\bfz)S_2 (\bfz))^2 
+A\BV (C_{12}, \BF_0) = \BE_{\bfZ} \left[ (\alpha_C (\| \bfz \|) \BS_{12} (\bfz; {\bf 0}))^2 \right] = \BE_{\bfZ} \alpha_C (\| \bfz \|)^2 . \BE_{\bfZ} (\BS_{12}(\bfz; {\bf 0}))^2,
 $$
 % 
-again using the fact that $\|\bfZ\|$ and $\bfS(\bfZ)$ are independent with $\bfZ \sim F_0$. It now follows that
+using the fact that $\|\bfZ\|$ and $\bfS(\bfZ)$ are independent with $\bfZ \sim \BF_0$. It now follows that
 %
 \begin{equation}
-ARE (\hat\bfgamma_{\Sigma_M,i}, \hat\bfgamma_{Cov,i}; F) = \frac{E_{F_0} \alpha_{Cov} (\| \bfz \|)^2}{E_{F_0} \alpha_C (\| \bfz \|)^2} = \frac{E_{F_0} \| \bfz \|^4.
-\left[ E_{F_0} ( p u \| \bfz\| + u'( \| \bfz \|) \| \bfz \| ) \right]^2}{E_{F_0} (u(\| \bfz \|))^2}
+ARE (\hat\bfgamma_{\Sigma_M,i}, \hat\bfgamma_{i}; \BF) =
+\frac{1}{A\BV (C_{12}, \BF_0)} = \frac{\left[ \BE_{\bfZ} ( p u \| \bfz\| + u'( \| \bfz \|) \| \bfz \| ) \right]^2}
+{p^2 (p+2)^2 \BE_\bfZ (u (\| \bfz \|)^2 \BE_{\bfZ} (\BS_{12}(\bfz; {\bf 0}))^2}.
 \end{equation}
@@
 
-Table \ref{table:AREtable} considers 6 different elliptic distributions (namely, bivariate $t$ with df = 5, 6, 10, 15, 25 and bivariate normal) and summarizes ARE for first eigenvectors for ADCMs corresponding to projection depth (PD-ACM) and halfspace depth (HSD-ACM).
-Due to difficulty of analytically obtain the AREs, we calculate them using Monte-Carlo simulation of $10^6$ samples and subsequent numerical integration.
+Table \ref{table:AREtable} considers 6 different elliptic distributions (namely, $p$-variate $t$ with df = 5, 6, 10, 15, 25 and multivariate normal) and summarizes ARE of the first eigenvectors for ADCMs corresponding to projection depth (PD-ACM) and halfspace depth (HSD-ACM).
+Due to difficulty in analytically obtaining the AREs, we calculate them using Monte-Carlo simulation of $10^6$ samples and subsequent numerical integration.
 The ADCM seems to be particularly efficient in lower dimensions for distributions with heavier tails ($t_5$ and $t_6$), while for distributions with lighter tails, the AREs increase with data dimension.
@@
 \centering
+\begin{footnotesize}
 \begin{tabular}{c|cccc|cccc}
@@
 \end{tabular}
+\end{footnotesize}
 \caption{Table of AREs of the ADCM for different choices of $p$ and data-generating distributions, and two choices of depth functions}
@@
 
-We now obtain finite sample efficiencies of the three DCMs as well as their depth-weighted affine equivariant counterparts by a simulation study, and compare them with the same from the SCM and Tyler's scatter matrix.
+We also obtain finite sample efficiencies of the three DCMs and ADCMs by a simulation study for $p=4$, and compare them with the same from the SCM and Tyler's scatter matrix.
 We consider the same 6 elliptical distributions considered in ARE calculations above, and from every distribution draw 10000 samples each for sample sizes $n = 20, 50, 100, 300, 500$.
-All distributions are centered at ${\bf 0}_p$, and have covariance matrix $\Sigma = \diag(p,p-1,...1)$.
-We consider 3 choices of $p$: 2, 3 and 4.
+All distributions are centered at ${\bf 0}_p$, and have covariance matrix $\Sigma = \diag(4,3,2,1)$.
 
-We use the concept of principal angles \citep{miao92} to find out error estimates for the first eigenvector of a scatter matrix. In our case, the first eigenvector will be
+We use the concept of principal angles \citep{miao92} to find out error estimates for the first eigenvector of a scatter matrix. In our case, the first eigenvector is
 %
-$$ \bfgamma_1 = (1,\overbrace{0,...,0}^{p-1})^T $$
+$$
+\bfgamma_1 = (1,\overbrace{0,...,0}^{p-1})^T.
+$$
 %
-For an estimate of the eigenvector, say $\hat\bfgamma_1$, error in prediction is measured by the smallest angle between the two lines, i.e.
-$ \cos^{-1} | \hat\bfgamma_1^T \hat\bfgamma_1 | $.
-A smaller absolute value of this angle is equivalent to better prediction.
+We measure the prediction error for an eigenvector estimate by some method, say $\hat\bfgamma_{E,1}$, by the smallest angle between the true and predicted vectors, i.e.
+$ \cos^{-1} | \hat\bfgamma_{E,1}^T \hat\bfgamma_1 | $.
+A small absolute value of this angle means to better prediction.
 We repeat this 10000 times and calculate the \textbf{Mean Squared Prediction Angle}:
 %
-$$ MSPA(\hat \bfgamma_1) = \frac{1}{10000} \sum_{m=1}^{10000} \left( \cos^{-1} \left|\bfgamma_1^T \hat\bfgamma^{(m)}_1 \right| \right)^2 $$
+$$
+MSPA(\hat \bfgamma_{E,1}) =
+\frac{1}{10000} \sum_{m=1}^{10000} \left( \cos^{-1} \left|\bfgamma_1^T \hat\bfgamma^{(m)}_{E,1} \right| \right)^2.
+$$
 %
-Finally, the finite sample efficiency of some eigenvector estimate $\hat\bfgamma^E_1$ relative to that obtained from the sample covariance matrix, say $\hat\bfgamma^{Cov}_1$ is obtained as:
-$$ FSE(\hat\bfgamma^E_1, \hat\bfgamma^{Cov}_1) = \frac{MSPA(\hat\bfgamma^{Cov}_1)}{MSPA(\hat\bfgamma^E_1)} $$
+The finite sample efficiency of this eigenvector estimate relative to that from the sample covariance matrix, i.e. $\hat\bfgamma_1$ is obtained as:
+$$ FSE(\hat\bfgamma_{E,1}, \hat\bfgamma_1) = \frac{MSPA(\hat\bfgamma_1)}{MSPA(\hat\bfgamma_{E,1})}.$$
 
-Tables \ref{table:FSEtable2}, \ref{table:FSEtable3} and \ref{table:FSEtable4} give FSE values for $p=2,3,4$, respectively.
-In general, all the efficiencies increase as the dimension $p$ goes up.
-DCM-based estimators (columns 3-5 in each table) outperform SCM and Tyler's scatter matrix, and among the 3 depths considered, projection depth seems to give the best results.
-Its finite sample performances are better than Tyler's and Huber's M-estimators of scatter as well as their symmetrized counterparts (see Table 4 in \cite{sirkia07}, and quite close to the affine equivariant spatial sign covariance matrix (see Table 2 in \cite{ollilia03}).
-The depth-weighted iterated versions of these 3 SCMs (columns 6-8 in each table) seem to further better the performance of their corresponding orthogonal equivariant counterparts.
+As seen in Table~\ref{table:FSEtable4} for $p = 4$, DCM- and ADCM-based estimators (columns 3-5) outperform SCM and Tyler's M-estimate of scatter.
+Among the 3 depth functions considered, projection depth gives the best results.
+Its finite sample performances are better than Tyler's and Huber's M-estimators of scatter, as well as their symmetrized counterparts that are much more computationally intensive (see Table 4 in \cite{sirkia07}).
+The affine equivariant versions of all DCMs (columns 6-8) further improve their performance.
 
-\begin{table}[b]
-\begin{footnotesize}
-    \begin{tabular}{c|cc|ccc|ccc}
-    \hline
-    $F$ = Bivariate $t_5$    & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
-    $n$=20                   & 0.80 & 0.83  & 0.95   & 0.95   & 0.89  & 1.00    & 0.96    & 0.89   \\
-    $n$=50                   & 0.86 & 0.90  & 1.25   & 1.10   & 1.21  & 1.32    & 1.13    & 1.25   \\
-    $n$=100                  & 1.02 & 1.04  & 1.58   & 1.20   & 1.54  & 1.67    & 1.24    & 1.63   \\
-    $n$=300                  & 1.24 & 1.28  & 1.81   & 1.36   & 1.82  & 1.93    & 1.44    & 1.95   \\
-    $n$=500                  & 1.25 & 1.29  & 1.80   & 1.33   & 1.84  & 1.91    & 1.39    & 1.97   \\ \hline
-    $F$ = Bivariate $t_6$    & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
-    $n$=20                   & 0.77 & 0.79  & 0.92   & 0.92   & 0.86  & 0.96    & 0.92    & 0.85   \\
-    $n$=50                   & 0.76 & 0.78  & 1.11   & 1.00   & 1.08  & 1.17    & 1.03    & 1.13   \\
-    $n$=100                  & 0.78 & 0.79  & 1.27   & 1.06   & 1.33  & 1.35    & 1.11    & 1.41   \\
-    $n$=300                  & 0.88 & 0.91  & 1.29   & 1.09   & 1.35  & 1.38    & 1.15    & 1.45   \\
-    $n$=500                  & 0.93 & 0.96  & 1.37   & 1.13   & 1.40  & 1.44    & 1.19    & 1.48   \\ \hline
-    $F$ = Bivariate $t_{10}$ & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
-    $n$=20                   & 0.70 & 0.72  & 0.83   & 0.84   & 0.77  & 0.89    & 0.87    & 0.79   \\
-    $n$=50                   & 0.58 & 0.60  & 0.90   & 0.84   & 0.86  & 0.95    & 0.88    & 0.91   \\
-    $n$=100                  & 0.57 & 0.59  & 0.92   & 0.87   & 0.97  & 0.98    & 0.90    & 1.03   \\
-    $n$=300                  & 0.62 & 0.64  & 0.93   & 0.85   & 0.99  & 0.99    & 0.91    & 1.06   \\
-    $n$=500                  & 0.62 & 0.65  & 0.93   & 0.86   & 1.00  & 1.00    & 0.92    & 1.08   \\ \hline
-    $F$ = Bivariate $t_{15}$ & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
-    $n$=20                   & 0.63 & 0.66  & 0.76   & 0.78   & 0.72  & 0.81    & 0.81    & 0.73   \\
-    $n$=50                   & 0.52 & 0.52  & 0.79   & 0.75   & 0.80  & 0.84    & 0.79    & 0.85   \\
-    $n$=100                  & 0.51 & 0.52  & 0.83   & 0.77   & 0.88  & 0.88    & 0.81    & 0.94   \\
-    $n$=300                  & 0.55 & 0.56  & 0.84   & 0.79   & 0.91  & 0.89    & 0.84    & 0.98   \\
-    $n$=500                  & 0.56 & 0.59  & 0.85   & 0.80   & 0.93  & 0.91    & 0.86    & 0.99   \\ \hline
-    $F$ = Bivariate $t_{25}$ & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
-    $n$=20                   & 0.63 & 0.65  & 0.77   & 0.79   & 0.74  & 0.80    & 0.81    & 0.74   \\
-    $n$=50                   & 0.49 & 0.50  & 0.73   & 0.71   & 0.76  & 0.78    & 0.75    & 0.80   \\
-    $n$=100                  & 0.45 & 0.46  & 0.73   & 0.69   & 0.81  & 0.78    & 0.73    & 0.87   \\
-    $n$=300                  & 0.51 & 0.52  & 0.78   & 0.75   & 0.87  & 0.83    & 0.79    & 0.94   \\
-    $n$=500                  & 0.53 & 0.55  & 0.79   & 0.75   & 0.87  & 0.84    & 0.80    & 0.94   \\ \hline
-    $F$ = BVN                & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
-    $n$=20                   & 0.56 & 0.60  & 0.69   & 0.71   & 0.67  & 0.73    & 0.74    & 0.68   \\
-    $n$=50                   & 0.42 & 0.43  & 0.66   & 0.66   & 0.70  & 0.71    & 0.69    & 0.75   \\
-    $n$=100                  & 0.42 & 0.43  & 0.69   & 0.66   & 0.77  & 0.74    & 0.71    & 0.83   \\
-    $n$=300                  & 0.47 & 0.49  & 0.71   & 0.69   & 0.82  & 0.76    & 0.73    & 0.88   \\
-    $n$=500                  & 0.48 & 0.50  & 0.73   & 0.71   & 0.83  & 0.78    & 0.76    & 0.89   \\ \hline
-    \end{tabular}
-\end{footnotesize}
-\caption{Finite sample efficiencies of several scatter matrices: $p=2$}
-\label{table:FSEtable2}
-\end{table}
-
-\begin{table}[b]
-\begin{footnotesize}
-   \begin{tabular}{c|cc|ccc|ccc}
-    \hline
-    3-variate $t_5$    & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
-    $n$=20             & 0.96 & 0.97  & 1.06   & 1.03   & 0.99  & 1.07    & 1.06    & 0.97   \\
-    $n$=50             & 1.07 & 1.08  & 1.28   & 1.20   & 1.18  & 1.33    & 1.23    & 1.20   \\
-    $n$=100            & 1.12 & 1.15  & 1.49   & 1.31   & 1.40  & 1.57    & 1.38    & 1.48   \\
-    $n$=300            & 1.49 & 1.54  & 2.09   & 1.82   & 2.07  & 2.19    & 1.93    & 2.18   \\
-    $n$=500            & 1.60 & 1.66  & 2.18   & 1.87   & 2.21  & 2.27    & 1.95    & 2.30   \\ \hline
-    3-variate $t_6$    & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
-    $n$=20             & 0.90 & 0.92  & 1.00   & 0.99   & 0.95  & 1.02    & 1.01    & 0.94   \\
-    $n$=50             & 0.95 & 0.96  & 1.16   & 1.09   & 1.09  & 1.21    & 1.14    & 1.11   \\
-    $n$=100            & 0.98 & 0.99  & 1.32   & 1.22   & 1.25  & 1.38    & 1.27    & 1.29   \\
-    $n$=300            & 1.10 & 1.14  & 1.57   & 1.40   & 1.58  & 1.62    & 1.47    & 1.64   \\
-    $n$=500            & 1.17 & 1.20  & 1.57   & 1.43   & 1.60  & 1.63    & 1.51    & 1.67   \\ \hline
-    3-variate $t_{10}$ & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
-    $n$=20             & 0.87 & 0.88  & 0.95   & 0.94   & 0.90  & 0.97    & 0.98    & 0.89   \\
-    $n$=50             & 0.77 & 0.79  & 0.96   & 0.92   & 0.94  & 0.99    & 0.96    & 0.95   \\
-    $n$=100            & 0.75 & 0.76  & 1.02   & 0.95   & 1.01  & 1.06    & 1.00    & 1.05   \\
-    $n$=300            & 0.73 & 0.75  & 1.03   & 0.98   & 1.10  & 1.08    & 1.03    & 1.15   \\
-    $n$=500            & 0.73 & 0.76  & 1.02   & 0.98   & 1.09  & 1.06    & 1.02    & 1.14   \\ \hline
-    3-variate $t_{15}$ & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
-    $n$=20             & 0.84 & 0.86  & 0.92   & 0.92   & 0.89  & 0.94    & 0.94    & 0.87   \\
-    $n$=50             & 0.75 & 0.76  & 0.92   & 0.90   & 0.90  & 0.96    & 0.94    & 0.93   \\
-    $n$=100            & 0.66 & 0.67  & 0.91   & 0.87   & 0.95  & 0.96    & 0.92    & 1.00   \\
-    $n$=300            & 0.61 & 0.64  & 0.90   & 0.87   & 1.00  & 0.93    & 0.91    & 1.04   \\
-    $n$=500            & 0.65 & 0.67  & 0.89   & 0.87   & 0.99  & 0.93    & 0.91    & 1.03   \\ \hline
-    3-variate $t_{25}$ & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
-    $n$=20             & 0.78 & 0.79  & 0.87   & 0.89   & 0.87  & 0.89    & 0.92    & 0.86   \\
-    $n$=50             & 0.70 & 0.71  & 0.88   & 0.86   & 0.88  & 0.91    & 0.90    & 0.90   \\
-    $n$=100            & 0.61 & 0.63  & 0.86   & 0.83   & 0.89  & 0.90    & 0.88    & 0.94   \\
-    $n$=300            & 0.58 & 0.59  & 0.83   & 0.80   & 0.92  & 0.87    & 0.85    & 0.98   \\
-    $n$=500            & 0.62 & 0.64  & 0.83   & 0.82   & 0.94  & 0.88    & 0.87    & 0.99   \\ \hline
-    3-variate Normal   & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
-    $n$=20             & 0.76 & 0.78  & 0.85   & 0.87   & 0.84  & 0.87    & 0.90    & 0.83   \\
-    $n$=50             & 0.66 & 0.67  & 0.82   & 0.81   & 0.84  & 0.86    & 0.86    & 0.86   \\
-    $n$=100            & 0.56 & 0.58  & 0.77   & 0.75   & 0.83  & 0.82    & 0.79    & 0.87   \\
-    $n$=300            & 0.53 & 0.55  & 0.75   & 0.74   & 0.85  & 0.79    & 0.78    & 0.90   \\
-    $n$=500            & 0.56 & 0.58  & 0.76   & 0.76   & 0.87  & 0.80    & 0.80    & 0.92   \\ \hline
-    \end{tabular}
-\end{footnotesize}
-\caption{Finite sample efficiencies of several scatter matrices: $p=3$}
-\label{table:FSEtable3}
-\end{table}
-
-\begin{table}[b]
+\begin{table}[t]
 \begin{footnotesize}
@@
 
-As we have seen in theorem \ref{Theorem:covform}, eigenvalues of the DCM are not same as the population eigenvalues, whereas the ADCM only gives back standardized eigenvalues.
+As seen in Theorem~\ref{Theorem:covform}, eigenvalues of the DCM are not same as the population eigenvalues, whereas the ADCM only gives back standardized eigenvalues.
 However, it is possible to robustly estimate the original eigenvalues by working with the individual columns of the robust score matrix.
-We do this using the following steps:
+We do so using the following steps:
 
@@
 
-\item Assume the data is centered. Transform the data matrix: $S = \hat\Gamma^T_D X$;
+\item Assume the data is centered. Transform the data matrix: $\BS = \hat\Gamma^T_D \BX$;
 
@@
 $$
-where $\bar\bfs_{G_j} = (\bar s_{G_j,1}, ..., \bar s_{G_j,p})^T$ is the vector of column-wise means of $S_{G_j}$, the submatrix od $S$ with row indices in $G_j$.
+where $\bar\bfs_{G_j} = (\bar s_{G_j,1}, ..., \bar s_{G_j,p})^T$ is the vector of column-wise means of $\BS_{G_j}$, the submatrix of $\BS$ with row indices in $G_j$.
 %
@@
 %
-The number of subgroups used to calculate this median-of-small-variances estimator can be determined following \citep{Minsker15}.
+The number of subgroups used to calculate this median-of-small-variances estimator can be determined following \cite{Minsker15}.
 After this, we construct a consistent plug-in estimator of the population covariance matrix $\Sigma$:
@@
 Consider the estimates $\hat\lambda_i$ obtained from the above algorithm, and the matrix of eigenvectors $\hat\Gamma_D$ estimated using the sample DCM.
-Define $\hat\Sigma = \hat\Gamma_D \hat\Lambda \hat\Gamma_D^T; \hat\Lambda = \text{diag}(\hat\lambda_1, ..., \hat\lambda_p)$.
+Define $\hat\Sigma = \hat\Gamma_D \hat\Lambda \hat\Gamma_D^T; \hat\Lambda = \diag(\hat\lambda_1, ..., \hat\lambda_p)$.
 Then as $n \rightarrow \infty$,
 %
-$$ \| \hat\Sigma - \Sigma \|_F \stackrel{P}{\rightarrow} 0 $$
+$$
+\| \hat\Sigma - \Sigma \|_F \stackrel{P}{\rightarrow} 0.
+$$
 %
-$\|.\|_F$ being the Frobenius norm.
 \end{Theorem}

### 2018-03-23 MS-new/4_SDR.tex
main paper v1 done, proofs and intro remain

@@
 
-In the presence of a vector of univariate responses, say $\bfY = (Y_1,Y_2,...,Y_n)^T$, there is substantial literature devoted to utilizing the subspace generated by the basis of $Cov(\bfX)$ in modelling $E(Y|\bfX)$.
+In the presence of a vector of univariate responses, say $\bfy = (y_1,\ldots, y_n)^T$, each $y_i$ being i.i.d.
+relalizations of a univariate random variable $Y$ that takes values in $\cY \subseteq \BR$, there is substantial literature devoted to utilizing the subspace generated by the basis of $\Sigma = \BV \bfX$ in modelling $\BE(Y|\bfX)$.
 This ranges from the simple Principal Components Regression (PCR) to Partial Least Squares (PLS) and Envelope methods \citep{Cook10}.
-Here we concentrate on robust inference using Sufficient Dimension Reduction (SDR) \citep{AdragniCook09}, mainly because it provides a general framework for reducing dimensionality of data directly using top eigenvectors of the covariance matrix of $X$ (albeit in a different manner than PCR) or an appropriate affine transformation of it.
+In this section, we concentrate on robust inference using Sufficient Dimension Reduction (SDR) \citep{AdragniCook09}, mainly because it provides a general framework for reducing dimensionality of data directly using top eigenvectors of $\Sigma$ (albeit in a different manner than PCR) or an appropriate affine transformation of it.
 
-SDR attempts to find out a linear transformation $R$ on $\bfX$ such that $E(Y|\bfX) = E(Y|R(\bfX))$.
-Assuming that $R(\bfX)$ takes values in $\mathbb R^d, d \leq \min(n,p)$, this can be achieved through an inverse regression model:
+SDR attempts to find out a linear transformation $\bfR$ on $\bfX$ such that $\BE(Y|\bfX) = \BE(Y| \BR(\bfX))$.
+Assuming that $\bfR(\bfX)$ takes values in $\mathbb R^d, d \leq \min(n,p)$, this can be achieved through an inverse regression model:
 %
 \begin{equation}
-\bfX_y = \bar \bfmu + \Gamma \bfv_y + \bfepsilon
+\bfX_y = \bfmu + \Gamma_d \bfv_y + \bfepsilon,
 \end{equation}
 %
-where $\bfX_y = \bfX|Y=y, \bar\bfmu = E\bfX$, $\Gamma$ is a $p \times d$ semi-orthogonal basis for $\mathcal S_\Gamma$, the spanning subspace of $\{ E \bfX_y - \bar\bfmu | y \in S _Y \}$ ($S_y$ is sample space of $Y$) and $\bfv_y = (\Gamma^T \Gamma)^{-1} \Gamma^T (E \bfX_y - \bar\bfmu) \in \mathbb R^d$.
-The random error term $\bfepsilon$ follows a multivariate normal distribution with mean ${\bf 0}_p$ and covariance matrix $\Delta$.
+where $\bfX_y = \bfX|Y=y$, $\Gamma_d \in \BR^{p \times d}$ is a semi-orthogonal basis for $\cS_\Gamma$, the spanning subspace of $\{ \BE \bfX_y - \bfmu | y \in \cY \}$, $\bfv_y = (\Gamma_d^T \Gamma_d)^{-1} \Gamma_d^T (\BE \bfX_y - \bfmu) \in \mathbb R^d$, and $\bfepsilon \sim \cN_p ({\bf 0}, \Delta)$ for some positive-definite matix $\Delta$.
 This formulation is straightforward to implement when $Y$ is categorical, while for continuous responses, the vector $\bfy$ is divided into a number of slices.
 
-Under this model the minimal sufficient transformation is $R(\bfX) = \Gamma^T \Delta^{-1} \bfX$.
-The simplest case of this model is when $\Delta = \sigma^2 I_p$, for which the maximum likelihood estimator of $ R(\bfX)$ turns out to be the first $d$ PCs of $Cov(\bfX)$.
-Taking $\hat E\bfX_y = \bar\bfX_y$ and $\hat{\bar\bfmu} = \bar\bfX$, one can now estimate $\sigma^2$ as: $\hat\sigma^2 = \sum_{i=1}^p s_{ii}/p$, where $s_{ii}$ is the $i^\text{th}$ diagonal element of $\hat{Cov}_Y( \bfX_Y - \bar\bfX - \hat\Gamma \hat\bfv_Y)$.
+Under this model the minimal sufficient transformation is $\bfR(\bfX) = \Gamma_d^T \Delta^{-1} \bfX$ \citep{AdragniCook09}.
+The simplest case of this model is when $\Delta = \sigma^2 \BI_p$, for which the maximum likelihood estimator of $ \bfR(\bfX)$ turns out to be the first $d$ PCs of $\Sigma$.
+Taking $\hat \bfmu_y = \sum_{i=1}^n \bfx_i \BI \{y_i = y\}/n$ and $\hat \bfmu = \sum_{i=1}^n \bfx_i /n$, one can now estimate $\sigma^2$ as: $\hat\sigma^2 = \sum_{i=1}^p s_i /p$, where $s_i$ is the $i^\text{th}$ diagonal element of $\BC_y^T \BC_y/n$, with
+%
+$$
+\BC_y = (\bfc_{y1}, \ldots, \bfc_{yn_y})^T; \quad
+n_y = \sum_{i=1}^n \BI \{ y_i = y \},
+\bfc_{yi} = \bfx_{yi} - \hat \bfmu - \hat\Gamma_d (\hat \Gamma_d^T \hat \Gamma_d)^{-1} \hat \Gamma_d^T (\hat \bfmu_y - \hat \bfmu ).
+$$
+%
 Following this, predictions for a new observation $\bfx$ is obtained as a weighted sum of the responses:
@@
 $$
-\hat E(Y|\bfX=\bfx) = \frac{\sum_{i=1}^n w_i Y_i}{\sum_{i=1}^n w_i}; \quad w_i = \exp \left[ -\frac{1}{\hat\sigma^2}  \| \hat\Gamma^T (\bfx - \bfX_i) \|^2 \right]
+\hat \BE(Y|\bfX=\bfx) = \frac{\sum_{i=1}^n w_i y_i}{\sum_{i=1}^n w_i}; \quad w_i = \exp \left[ -\frac{1}{\hat\sigma^2}  \| \hat\Gamma_d^T (\bfx - \bfx_i) \|^2 \right].
 $$
@@
 
-We formulate a robust version of the above procedure by estimating the quantities $\Gamma, \bar\bfmu, \bfmu_y, \sigma^2$ by robust methods. Specifically, we take:
+We formulate a robust version of the above procedure by estimating the quantities $\Gamma_d, \bfmu, \bfmu_y, \sigma^2$ by robust methods. Specifically, we take:
 %
 \begin{itemize}
-\item $\tilde \Gamma = $ first $d$ eigenvectors of the sample DCM;
+\item $\tilde \Gamma_d = $ first $d$ eigenvectors of the sample DCM;
 %
-\item $\tilde{\bar\bfmu} = $ spatial median of the rows of $X$;
+\item $\tilde \bfmu = $ spatial median of the rows of $\BX$;
 %
-\item $\tilde \bfmu_y = $ spatial median of the rows of $(X|Y=y)$, for all $y \in S_Y$;
+\item $\tilde \bfmu_y = $ spatial median of the rows of $\BX_y$, for each $y \in \cY$;
 %
-\item $\tilde\sigma^2 = \sum_{i=1}^p [\widehat{\text{MAD}}_Y (X_{Y,i} - \tilde{\bar\mu}_i - \tilde\bfgamma_i^T \tilde\bfv_Y)]^2/p$, with $\tilde\Gamma = (\tilde\bfgamma_1, ..., \tilde\bfgamma_p)^T$.
+\item $\tilde\sigma^2 = \sum_{i=1}^p \tilde s_i/p$, where $\tilde s_i$ is the $i^\text{th}$ diagonal element of $\tilde \BC_y^T \tilde \BC_y/n$, $\tilde \BC_y$ being the matrix composed of rows $\bfx_{yi} - \tilde \bfmu - \tilde \Gamma_d (\tilde \Gamma_d^T \tilde \Gamma_d)^{-1} \tilde \Gamma_d^T (\tilde \bfmu_y - \tilde \bfmu )$ for $i \in \{ 1, \ldots, n \}$ such that $y_i = y$.
 \end{itemize}
 %
-The following simulation study using the same setup as in \citep{AdragniCook09} compares the performance of our robust SDR with the original method with or without the presence of bad leverage points in the covariate matrix $X$.
-For a fixed dimension $p$, we take $n=200, d=1$, generate the responses $Y$ as independent standard normal, and the predictors as $\bfX_Y = \bfgamma^* v_Y^* + \bfepsilon$, with $\bfgamma^*_{p\times 1} = (1,...,1)^T, v_Y = Y + Y^2 + Y^3$ and $Var(\bfepsilon) = 25 I_p$.
-We measure performance of both SDR models by their mean squared prediction error on another set of 200 observations $(Y^*, \bfX^*)$ generated similarly, and taking the average of these errors on 100 such training-test pair of datasets.
-Finally we repeat the whole setup for different choices of $p = 5,10,25,50,75,100,125,150$.
+We compare the performance of our robust SDR with the original method of \cite{AdragniCook09} with or without the presence of bad leverage points in $\Sigma$ using a simulation study.
+For a given value of $p$, we take $n=200, d=1$, generate the responses $y_1, \ldots, y_n$ as independent standard normal, and the predictors as $\bfX_y = {\bf 1} (y + y^2 + y^3) + \bfepsilon$, with ${\bf 1} \in \BR^p$ consisting of all 1's, and $\BV(\bfepsilon) = 25 \BI_p$.
+We measure performances of the SDR models by their mean squared prediction error on another set of 200 observations $(\bfy^*, \BX^*)$ generated similarly, and taking the average of these errors on 100 such training-test pairs of datasets.
+Finally we repeat the full setup for different choices of $p = 5,10,25,50,75,100,125,150$.
 
@@
 
-Panel (a) of figure \ref{fig:SDRfig} compares prediction errors using robust and maximum likelihood SDR estimates when $X$ contains no outliers, and the two methods are virtually indistinguishable.
-We now introduce outliers in each of the 100 datasets by adding 100 to first $p/5$ coordinates of the first 10 observations in $X$, and repeat the analysis.
-Panel (b) of the figure shows that although our robust method performs slightly worse than the case when there were no outliers, it remains more accurate in predicting our of sample observations for all values of $p$.
+Panel (a) of figure \ref{fig:SDRfig} compares prediction errors using robust and maximum likelihood SDR estimates when $\BX$ contains no outliers: here the two methods are virtually indistinguishable.
+We now introduce outliers in each of the 100 datasets by adding 100 to first $p/5$ coordinates of the first 10 observations in $\BX$, and repeat the analysis.
+Panel (b) of the figure shows that the robust SDR method remains more accurate in predicting out of sample observations for all values of $p$ than standard SDR.

### 2018-03-23 MS-new/5_Functional.tex
main paper v1 done, proofs and intro remain

@@
 \section{Robust inference with functional data}
-
-{\colrbf (Some technical notations)}
-
-We use the approach of \cite{BoenteBarrera15} for performing robust PCA on functional data.
-Given data on $n$ functions, say $f_1, f_2, ..., f_n \in L^2[0,1]$, each observed at a set of common design points $\{ t_1, ..., t_m \} $, we model each function as a linear combination of $p$ mutually orthogonal B-spline basis functions $\delta_1, ..., \delta_p$.
+\label{section:fpcaSection}
+Detection of anomalous observations is of importance in real-life problems involving functional data analysis, and functional PCA is a widely used tool in this setting.
+In this section we utilize robust principal components from the DCM for this purpose.
+We use the approach of \cite{BoenteBarrera15} for performing robust PCA on functional data using the estimated PCs from the DCM.
+Here we have a data matrix $\BH$, that stores the values of a set of $n$ curves, say $ \cF = \{ f_1, \ldots , f_n  \} \in L^2[0,1]$, each observed at a set of common design points $\{ t_1, ..., t_m \} $.
+We model each of these functions as a linear combination of $p$ mutually orthogonal B-spline basis functions $\cD = \{ \delta_1, ..., \delta_p \}$.
 Following this, we map data for each of the functions onto the coordinate system formed by the spline basis:
@@
 \begin{equation}
-\tilde x_{ij} = \sum_{l=2}^m f_i(t_l) \delta_j(t_l) (t_l - t_{l-1}); \quad 1 \leq i \leq n, 1 \leq j \leq p
+T( \BH; \cF, \cD)_{ij} = \sum_{l=2}^m f_i(t_l) \delta_j(t_l) (t_l - t_{l-1}); \quad 1 \leq i \leq n, 1 \leq j \leq p.
 \end{equation}
 %
-We now do depth-based PCA on the transformed $n \times p$ data matrix $\tilde X$, and obtain the rank-$q$ approximation ($q \leq p$) of the $i^\text{th}$ observation using the robust $p \times q$ loading matrix $\tilde P$ and robust $q \times 1$ score vector $\tilde\bfs_i$:
+We now do depth-based PCA on the transformed $n \times p$ data matrix $T(\BH; \cF, \cD) \equiv T(\BH)$, and obtain the rank-$q$ approximation ($q \leq p$) of the $i\Th$ observation using the robust $p \times q$ loading matrix $\tilde \bfP$ and robust $q \times 1$ score vector $\tilde\bfs_i$:
 %
-$$ \widehat{\tilde\bfx_i} = \tilde\bfmu + \tilde P \tilde \bfs_i $$
+$$
+\widehat T(\BH)_i = \tilde \bfmu + \tilde \bfP \tilde \bfs_i,
+$$
 %
-with $\tilde\bfmu$ being the spatial median of $\tilde X$.
-Then we transform this approximation back to the original coordinates: $\hat f_i (t_l) = \sum_{j=1}^p \widehat{ \tilde x}_{ij} \delta_j (t_l)$.
+with $\tilde \bfmu$ being the spatial median of $T(\BH)$. Then we transform this approximation back to the original coordinates: $\hat f_i (t_l) = \sum_{j=1}^p \widehat T(\BH)_{ij} \delta_j (t_l)$.
 
-Detection of anomalous observations is of importance in real-life problems involving functional data analysis.
-We now demonstrate the utility of our robust method for detecting functional outliers through two data examples.
+We demonstrate the utility of our robust method for detecting functional outliers through two data examples.
+For any method of PCA with $k$ components on a dataset of $n$ observations and $p$ variables, the \textit{score distance} (SD) and \textit{orthogonal distance} (OD) for $i^\text{th}$ observation ($i=1,2,...,n$) are defined as:
+%
+$$
+SD_i = \sqrt{ \sum_{j=1}^k \frac{s^2_{ij}}{\hat \lambda_j}}; \quad OD_i = \| \bfx_i - \bfP\bfs_i^T \|,
+$$
+%
+where $\bfs_1, \ldots ,\bfs_n$ are the score vectors, $\bfP \in \BR^{p\times k}$ the loading matrix, and $\hat \lambda_1,\ldots ,\hat \lambda_k$ are eigenvalues obtained from the PCA.
+From a practical standpoint, $SD_i$ can be interpreted as a weighted norm of the projection of the $i^\text{th}$ point on the hyperplane formed by first $k$ principal components, and $OD_i$ the orthogonal distance of point $i$ from that hyperplane.
+For outlier detection, following \cite{hubert05} we set the upper cutoff values for score distances at $(\chi^2_{2,.975})^{1/2}$ and orthogonal distances at $[\text{median}(OD^{2/3}) + \text{MAD}(OD^{2/3})\Phi^{-1}(0.975)]^{3/2}$, where $\Phi(.)$ is the standard normal cumulative distribution function.
 
-\textbf{(SD and OD definition, cutoffs... from previous manuscript)
-}
-
-\begin{figure}[t]
+\begin{figure}
 %\captionsetup{justification=centering, font=footnotesize}
 \begin{center}
-\subfigure[]{\epsfxsize=.32\linewidth\epsfbox{../Codes/Elnino_functional1}}
-\subfigure[]{\epsfxsize=.32\linewidth\epsfbox{../Codes/Elnino_functional2}}
-\subfigure[]{\epsfxsize=.32\linewidth\epsfbox{../Codes/Elnino_functional3}}\\
-\vspace{-1em}
-\subfigure[]{\epsfxsize=.32\linewidth\epsfbox{../Codes/Octane_functional1}}
-\subfigure[]{\epsfxsize=.32\linewidth\epsfbox{../Codes/Octane_functional2}}
-\subfigure[]{\epsfxsize=.32\linewidth\epsfbox{../Codes/Octane_functional3}}
+\subfigure[]{\epsfxsize=.35\linewidth\epsfbox{../Codes/Elnino_functional1}}
+\subfigure[]{\epsfxsize=.35\linewidth\epsfbox{../Codes/Octane_functional1}}\\
+
+\subfigure[]{\epsfxsize=.35\linewidth\epsfbox{../Codes/Elnino_functional2}}
+\subfigure[]{\epsfxsize=.35\linewidth\epsfbox{../Codes/Octane_functional2}}\\
+
+\subfigure[]{\epsfxsize=.35\linewidth\epsfbox{../Codes/Elnino_functional3}}
+\subfigure[]{\epsfxsize=.35\linewidth\epsfbox{../Codes/Octane_functional3}}\\
 %\subfigure[]{\epsfxsize=0.35\linewidth \epsfbox{../Codes/SDRcomparison_out}}
-\caption{Actual sample curves, their spline approximations and diagnostic plots respectively for El-Ni\~no (a-c) and Octane (d-f) datasets}
+\caption{Actual sample curves, their spline approximations and diagnostic plots respectively for El-Ni\~no (a,c,e) and Octane (b,d,f) datasets}
 \label{fig:fPCAfig}
@@
 
-We first look into the El-Ni\~no data, which is part of a larger dataset on potential factors behind El-Ni\~no oscillations in the tropical pacific available in \url{http://www.cpc.ncep.noaa.gov/data/indices/}.
-This records monthly average Sea Surface Temperatures from June 1970 to May 2004, and the yearly oscillations follow more or less the same pattern (see panel a of figure \ref{fig:fPCAfig}).
-Using a cubic spline basis with knots at alternate months starting in June gives a close approximation of the yearly time series data (panel b), and performing depth-based PCA with $q=1$ results in two points having their SD and OD larger than cutoff (panel c).
-These points correspond to the time periods June 1982 to May 1983 and June 1997 to May 1998 are marked by black curves in panels a and b), and pinpoint the two seasons with strongest El-Ni\~no events.
+We consider the El-Ni\~no data, which is part of a larger dataset on potential factors behind El-Ni\~no oscillations in the tropical pacific available in \url{http://www.cpc.ncep.noaa.gov/data/indices}, as the first test case for outlier detection using our robust functional PCA.
+This records monthly average Sea Surface Temperatures from June 1970 to May 2004, and the yearly oscillations follow more or less the same pattern (see panel a of Figure~\ref{fig:fPCAfig}).
+Using a cubic spline basis with knots at alternate months starting in June gives a close approximation of the yearly time series data (panel c), and performing depth-based PCA with $q=1$ results in two points having their SD and OD larger than cutoff (panel e).
+These points correspond to the time periods June 1982 to May 1983 and June 1997 to May 1998 are marked by black curves in panels a and c, and pinpoint the two seasons with strongest El-Ni\~no events.
 
@@
 There are 6 outliers here: compounds 25, 26 and 36-39, which contain alcohol.
-We use the same basis structure as the one in El-Ni\~no data here, and again the top robust PC turns out to be sufficient in identifying all 6 outliers (panels d, e and f of figure \ref{fig:fPCAfig}).
+We use the same basis structure as the one in El-Ni\~no data here, and again the top robust PC turns out to be sufficient in identifying all 6 outliers (panels b, d and f of Figure~\ref{fig:fPCAfig}).

### 2018-03-23 MS-new/6_Conclusion.tex
main paper v1 done, proofs and intro remain

@@
-\section{Conclusion}\label{section:sec7}
-
-In the above sections we introduce a covariance matrix based on depth-based multivariate ranks that keeps the eigenvectors of the actual population unchanged for elliptical distributions.
+%\section{Conclusion}\label{section:sec7}
+%
+%In the above sections we introduce a covariance matrix based on depth-based multivariate ranks that keeps the eigenvectors of the actual population unchanged for elliptical distributions.
 We provide asymptotic results for the sample DCM, its eigenvalues and eigenvectors.
@@
 
-{\colrbf (some text)}
+\section{Conclusion}\label{section:sec7}
+\label{section:Conclusion}
+In the above sections we elaborate on a proposed transformation based on the idea of combining sign functions in an inner product space and certain transformations of general peripherality functions defined using probability measures on the same space.
+Based on the conditions we impose in course of the chapter, we essentially end up using data depths as scalar multiples of the spatial sign in estimation and testing problems for the location parameter of an elliptical distribution in $\BR^p$, and using inverse depth functions for robust estimation of different components of its covariance matrix.
+As demonstrated by several simulation studies and data examples, in all these situations the use of this composite transformation vector brings about efficiency gains, as well as favorable robustness properties in terms of bounded influence functions and deviations from Gaussianity.
+
+Regarding the multivariate rank transformation we propose, to be noted is the fact that the mapping $\bfX \rightarrow \tilde \bfX$ is in fact one-to-one for elliptical distributions.
+Thus such rank vectors can possibly be used for inference based on transformation-retransformation type techniques (e.g.
+\cite{ChakrabortyChaudhuri96,ChakrabortyChaudhuriOja98}).
+We defer this to future research.
+Finally, while these rank vectors have excellent intuitive appeal in preserving the shape of a multivariate data cloud, it would be interesting to study the properties of transformations similar to \eqref{eqn:rank} in general Hilbert spaces, as well as explore their applications in different data-analytic domains.

### 2018-03-23 MS-new/7_Appendix.tex
main paper v1 done, proofs and intro remain

@@
 \numberwithin{equation}{section}
-\section{\textbf{Form of $V_{D,S}(F)$}}\label{section:appA}
+\section{\textbf{Form of $\BV_D(\BF)$}}
+\label{section:appA}
+First observe that for $\BF$ having covariance matrix $\Sigma = \Gamma\Lambda\Gamma^T$, we have
+%
+$$
+\BV_D(\BF)  = (\Gamma \otimes \Gamma) \BV_D (\BF_\Lambda) (\Gamma \otimes \Gamma)^T,
+$$
+%
+where $\BF_\Lambda$ has the same elliptic distribution as $\BF$, but with covariance matrix $\Lambda$. Now,
+%
+\begin{align*}
+\BV_D (\BF_\Lambda) &= \BE \left[ \ve \left\{ \frac{(D^-_\bfZ (\bfz))^2 \Lambda^{1/2} \bfz\bfz^T \Lambda^{1/2}}{\bfz^T\Lambda\bfz} - \Lambda_D \right\} {\ve}^T \left\{ \frac{(D^-_\bfZ (\bfz))^2 \Lambda^{1/2} \bfz\bfz^T \Lambda^{1/2}}{\bfz^T\Lambda\bfz} - \Lambda_{D} \right\} \right]\\
+&= \BE \left[ \ve \left\{ (D^-_\bfZ (\bfz))^2 \BS (\Lambda^{1/2}\bfz; \bf0) \right\} {\ve}^T \left\{ (D^-_\bfZ (\bfz))^2 \BS (\Lambda^{1/2}\bfz; \bf0) \right\} \right]
+- \ve(\Lambda_{D}) {\ve}^T(\Lambda_{D})
+\end{align*}
 
-First observe that for $F$ having covariance matrix $\Sigma = \Gamma\Lambda\Gamma^T$,
-%
-$$ V_{D,S}(F)  = (\Gamma \otimes \Gamma) V_{D,S}(F_\Lambda) (\Gamma \otimes \Gamma)^T$$
-%
-where $F_\Lambda$ has the same elliptic distribution as $F$, but with covariance matrix $\Lambda$. Now,
-%
-\begin{eqnarray*}
-V_{D,S} (F_\Lambda) &=& E \left[ vec \left\{ \frac{(\tilde D_\bfZ (\bfz))^2 \Lambda^{1/2} \bfz\bfz^T \Lambda^{1/2}}{\bfz^T\Lambda\bfz} - \Lambda_{D,S} \right\} vec^T \left\{ \frac{(\tilde D_\bfZ (\bfz))^2 \Lambda^{1/2} \bfz\bfz^T \Lambda^{1/2}}{\bfz^T\Lambda\bfz} - \Lambda_{D,S} \right\} \right]\\
-&=& E \left[ vec \left\{ (\tilde D_\bfZ (\bfz))^2 SS(\Lambda^{1/2}\bfz; \bf0) \right\} vec^T \left\{ (\tilde D_\bfZ (\bfz))^2 SS(\Lambda^{1/2}\bfz; \bf0) \right\} \right]\\
-&& - \quad vec(\Lambda_{D,S}) vec^T(\Lambda_{D,S})
-\end{eqnarray*}
-
-The matrix $vec(\Lambda_{D,S}) vec^T(\Lambda_{D,S})$ consists of elements $\lambda_i\lambda_j$ at $(i,j)^\text{th}$ position of the $(i,j)^\text{th}$ block, and 0 otherwise.
+The matrix $\ve (\Lambda_{D}) {\ve}^T(\Lambda_{D})$ consists of elements $\lambda_{D,i} \lambda_{D,j}$ at $(i,j)^\text{th}$ position of the $(i,j)^\text{th}$ block, and 0 otherwise.
 These positions correspond to variance and covariance components of on-diagonal elements.
-For the expectation matrix, all its elements are of the form $E[\sqrt{\lambda_a \lambda_b \lambda_c \lambda_d} z_a z_b z_c z_d .
-(\tilde D_\bfZ (\bfz))^4 / (\bfz^T \Lambda \bfz)^2]$, with $1 \leq a,b,c,d \leq p$.
-Since $(\tilde D_\bfZ (\bfz))^4 / (\bfz^T \Lambda \bfz)^2$ is even in $\bfz$, which has a circularly symmetric distribution, all such expectations will be 0 unless $a=b=c=d$, or they are pairwise equal.
+For the expectation matrix, all its elements are of the form $ \BE [\sqrt{\lambda_a \lambda_b \lambda_c \lambda_d} z_a z_b z_c z_d .
+(D^-_\bfZ (\bfz))^4 / (\bfz^T \Lambda \bfz)^2]$, with $1 \leq a,b,c,d \leq p$.
+Since $(D^-_\bfZ (\bfz))^4 / (\bfz^T \Lambda \bfz)^2$ is even in $\bfz$, which has a sperically symmetric distribution, all such expectations will be 0 unless $a = b = c = d$, or they are pairwise equal.
 Following a similar derivation for spatial sign covariance matrices in \cite{magyar14}, we collect the non-zero elements and write the matrix of expectations:
 %
-$$ (I_{p^2} + K_{p,p}) \left\{ \sum_{a=1}^p \sum_{b=1}^p \gamma^D_{ab} (\bfe_a \bfe_a^T \otimes  \bfe_b \bfe_b^T) - \sum_{a=1}^p \gamma^D_{aa} (\bfe_a \bfe_a^T \otimes  \bfe_a \bfe_a^T) \right\} + \sum_{a=1}^p \sum_{b=1}^p \gamma^D_{ab} (\bfe_a \bfe_b^T \otimes  \bfe_a \bfe_b^T) $$
+$$
+(\BI_{p^2} + \BK_{p,p}) \left\{ \sum_{a=1}^p \sum_{b=1}^p d_{ab} (\bfe_a \bfe_a^T \otimes  \bfe_b \bfe_b^T) - \sum_{a=1}^p d_{aa} (\bfe_a \bfe_a^T \otimes  \bfe_a \bfe_a^T) \right\} + \sum_{a=1}^p \sum_{b=1}^p d_{ab} (\bfe_a \bfe_b^T \otimes  \bfe_a \bfe_b^T) $$
 %
-where $I_k = (\bfe_1,...,\bfe_k), K_{m,n} = \sum_{i=1}^m \sum_{j=1}^n J_{ij} \otimes J_{ij}^T$ with $J_{ij}$ the $m \times n$ matrix having 1 as $(i,j)^\text{th}$ element and 0 elsewhere, and $\gamma^D_{mn} = E[ \lambda_m \lambda_n z_m^2 z_n ^2 .
-(\tilde D_\bfZ (\bfz))^4 / (\bfz^T \Lambda \bfz)^2]; 1 \leq m,n \leq p$.
+where $\BI_k = (\bfe_1,...,\bfe_k), \BK_{m,n} = \sum_{i=1}^m \sum_{j=1}^n \BJ_{ij} \otimes \BJ_{ij}^T$ with $\BJ_{ij}$ the $m \times n$ matrix having 1 as $(i,j)^\text{th}$ element and 0 elsewhere, and $d_{mn} = \BE [ (D^-_\bfZ (\bfz))^4 (\BS_{mn}(\bfz; {\bf 0}))^2]; 1 \leq m,n \leq p$.
 
-\paragraph{}Putting everything together, denote $\hat S^D(F_\Lambda) = \sum_{i=1}^n (\tilde D^n_\bfZ (\bfz_i))^2 SS(\Lambda^{1/2}\bfz_i; \hat \bfmu_n)/n $.
-Then the different types of elements in the matrix $V_{D,S}(F_\Lambda)$ are as given below ($1 \leq a,b,c,d \leq p$):
+\paragraph{}Putting everything together, denote $ \tilde \BS(\BF_\Lambda) = \sum_{i=1}^n (\tilde D^{n-}_\bfZ (\bfz_i))^2 \BS (\Lambda^{1/2}\bfz_i; \hat \bfmu_n)/n $.
+Then the different types of elements in the matrix $\BV_D(F_\Lambda)$ are as given below ($1 \leq a,b,c,d \leq p$):
 
@@
 %
-$$ AVar( \sqrt n \hat S^D_{aa} (F_\Lambda)) = E \left[ \frac{(\tilde D_\bfZ (\bfz))^4 \lambda_a^2 z_a^4}{(\bfz^T \Lambda \bfz)^2} \right] - \lambda_{D,S,a}^2 $$
+$$
+A\BV( \sqrt n \tilde \BS_{aa}(\BF_\Lambda)) = \BE \left[ (D^-_\bfZ (\bfz))^4 (\BS_{aa} (\Lambda^{1/2} \bfz; {\bf 0}))^2 \right] - \lambda_{D,a}^2
+$$
 
@@
 %
-$$ AVar( \sqrt n \hat S^D_{ab} (F_\Lambda)) = E \left[ \frac{(\tilde D_\bfZ (\bfz))^4 \lambda_a \lambda_b z_a^2 z_b^2}{(\bfz^T \Lambda \bfz)^2} \right] $$
+$$
+A\BV( \sqrt n \tilde \BS_{ab}(\BF_\Lambda)) = \BE \left[ (D^-_\bfZ (\bfz))^4 (\BS_{ab} (\Lambda^{1/2} \bfz; {\bf 0}))^2 \right]
+$$
 
@@
 %
-$$ ACov(\sqrt n \hat S^D_{aa} (F_\Lambda), \sqrt n \hat S^D_{bb} (F_\Lambda))
-= E \left[ \frac{(\tilde D_\bfZ (\bfz))^4 \lambda_a \lambda_b z_a^2 z_b^2}{(\bfz^T \Lambda \bfz)^2} \right] - \lambda_{D,S,a} \lambda_{D,S,b} $$
+$$
+A\BC( \sqrt n \tilde \BS_{aa}(\BF_\Lambda), \sqrt n \tilde \BS_{bb}(\BF_\Lambda)) =
+\BE \left[ (D^-_\bfZ (\bfz))^4 (\BS_{ab} (\Lambda^{1/2} \bfz; {\bf 0}))^2 \right] - \lambda_{D,a} \lambda_{D,b}
+$$
 
@@
 %
-$$ ACov(\sqrt n \hat S^D_{ab} (F_\Lambda), \sqrt n \hat S^D_{cd} (F_\Lambda)) = 0 $$
+$$
+A\BC( \sqrt n \tilde \BS_{aa}(\BF_\Lambda), \sqrt n \tilde \BS_{bb}(\BF_\Lambda)) = 0
+$$
 
@@
 %
-$$ ACov(\sqrt n \hat S^D_{ab} (F_\Lambda), \sqrt n \hat S^D_{cc} (F_\Lambda)) = 0 $$
+$$
+A\BC( \sqrt n \tilde \BS_{ab}(\BF_\Lambda), \sqrt n \tilde \BS_{cc}(\BF_\Lambda)) = 0
+$$
+%
 \end{itemize}
@@
 
-\begin{Theorem} \label{Theorem:decomp} \citep{taskinen12}
-Let $F_\Lambda$ be an elliptical distribution with a diagonal covariance matrix $\Lambda$, and $\hat C$ be any positive definite symmetric $p \times p$ matrix such that at $F_\Lambda$ the limiting distribution of $\sqrt n vec(\hat C - \Lambda)$ is a $p^2$-variate (singular) normal distribution with mean zero.
-Write the spectral decomposition of $\hat C$ as $\hat C = \hat P \hat\Lambda \hat P^T$.
-Then the limiting distributions of $\sqrt n vec(\hat P - I_p)$ and $\sqrt n vec(\hat\Lambda - \Lambda)$ are multivariate (singular) normal and
+\begin{Theorem}
+\label{Theorem:decomp} \citep{taskinen12}
+Let $\BF_\Lambda$ be an elliptical distribution with a diagonal covariance matrix $\Lambda$, and $\hat \BC$ be any positive definite symmetric $p \times p$ matrix such that at $\BF_\Lambda$ the limiting distribution of $\sqrt n \ve (\hat \BC - \Lambda)$ is a $p^2$-variate (singular) normal distribution with mean zero.
+Write the spectral decomposition of $\hat \BC$ as $\hat \BC = \hat \BP \hat \BL \hat \BP^T$.
+Then the limiting distributions of $\sqrt n vec(\hat \BP - \BI_p)$ and $\sqrt n vec(\hat\BL - \Lambda)$ are multivariate (singular) normal and
 %
 \begin{equation} \label{equation:decompEq}
-\sqrt n vec (\hat C - \Lambda)  = \left[ (\Lambda \otimes I_p) - (I_p \otimes \Lambda) \right] \sqrt n vec (\hat P - I_p) + \sqrt n vec (\hat\Lambda - \Lambda) + o_P(1)
+\ve (\hat \BC - \Lambda) =
+\left[ (\Lambda \otimes \BI_p) - (\BI_p \otimes \Lambda) \right]
+\ve (\hat \BP - \BI_p) + \ve (\hat\Lambda - \BL) + o_P(n^{-1/2})
 \end{equation}
@@
 The first matrix picks only off-diagonal elements of the LHS and the second one only diagonal elements.
-We shall now use this as well as the form of the asymptotic covariance matrix of the vec of sample DCM, i.e.
-$V_{D,S}(F)$ to obtain limiting variance and covariances of eigenvalues and eigenvectors.
+We now use the above result and the form of $\BV_D(\BF)$ derived in Appendix~\ref{section:appA} to obtain limiting variance and covariances of eigenvalues and eigenvectors.
 
 \begin{Corollary} \label{Corollary:eigendist}
-Consider the sample DCM $ \hat S^D(F) = \sum_{i=1}^n (\tilde D^n_\bfX (\bfx_i))^2 SS(\bfx_i; {\bf \hat\bfmu_n})/n $ and its spectral decomposition $\hat S^D(F) = \hat\Gamma_D \hat\Lambda_D \hat\Gamma_D^T $.
-Then the matrices $G = \sqrt n (\hat\Gamma_D - \Gamma) $ and $L = \sqrt n (\hat\Lambda_D - \Lambda_{D,S}) $ have independent distributions.
-The random variable $vec(G)$ asymptotically has a $p^2$-variate normal distribution with mean ${\bf 0}_{p^2}$, and the asymptotic variance and covariance of different columns of $G = (\bfg_1,...,\bfg_p)$ are as follows:
+Consider the sample DCM $ \tilde \BS = \sum_{i=1}^n (D^{n-}_\bfX (\bfx_i))^2 \BS (\bfx_i; \hat\bfmu_n)/n $ and its spectral decomposition $\tilde \BS = \hat\Gamma_D \hat\Lambda_D \hat\Gamma_D^T $.
+Then the matrices $\BG_D = \sqrt n (\hat\Gamma_D - \Gamma) $ and $\BL_D = \sqrt n (\hat\Lambda_D - \Lambda_{D}) $ have independent distributions.
+The random variable $\ve(G)$ asymptotically has a $p^2$-variate normal distribution with mean ${\bf 0}_{p^2}$, and the asymptotic variance and covariance of different columns of $\BG_D = (\bfg_1,...,\bfg_p)$ are as follows:
 %
 \begin{equation} \label{equation:DevEq}
-AVar(\bfg_i) = \sum_{k=1; k \neq i}^p \frac{1}{(\lambda_{D,s,k} - \lambda_{D,S,i})^2} E \left[ \frac{(\tilde D_\bfZ (\bfz))^4 \lambda_i \lambda_k z_i^2 z_k^2}{(\bfz^T \Lambda \bfz)^2} \right] \bfgamma_k \bfgamma_k^T
+A\BV(\bfg_i) = \sum_{k=1; k \neq i}^p \frac{\BE [ (D^-_\bfZ (\bfz))^4 (\BS_{ik}( \Lambda^{1/2} \bfz; {\bf 0}))^2 ]}
+{(\lambda_{D,i} - \lambda_{D,k})^2} \bfgamma_k \bfgamma_k^T
 \end{equation}
@@
 \begin{equation}
-ACov(\bfg_i, \bfg_j) = - \frac{1}{(\lambda_{D,s,i} - \lambda_{D,S,j})^2} E \left[ \frac{(\tilde D_\bfZ (\bfz))^4 \lambda_i \lambda_j z_i^2 z_j^2}{(\bfz^T \Lambda \bfz)^2} \right] \bfgamma_j \bfgamma_i^T; \quad i \neq j
+A\BC( \bfg_i, \bfg_j) = - \frac{\BE [ (D^-_\bfZ (\bfz))^4 (\BS_{ij}( \Lambda^{1/2} \bfz; {\bf 0}))^2 ]}
+{(\lambda_{D,i} - \lambda_{D,j})^2} \bfgamma_i \bfgamma_j^T; \quad i \neq j
 \end{equation}
 %
-where $\Gamma = (\bfgamma_1,...,\bfgamma_p)$.
-The vector consisting of diagonal elements of $L$, say $\bfl = (\l_1,...,\l_p)^T$ asymptotically has a $p$-variate normal distribution with mean ${\bf 0}_p$ and variance-covariance elements:
+The vector consisting of diagonal elements of $\BL_D$, say $\mathbf{\ell} = (\l_1,...,\l_p)^T$ asymptotically has a $p$-variate normal distribution with mean ${\bf 0}_p$ and variance-covariance elements:
 %
 \begin{eqnarray}
-AVar(l_i) &=& E \left[ \frac{(\tilde D_\bfZ (\bfz))^4 \lambda_i^2 z_i^4}{(\bfz^T \Lambda \bfz)^2} \right] - \lambda_{D,S,i}^2\\
-ACov(l_i, l_j) &=& E \left[ \frac{(\tilde D_\bfZ (\bfz))^4 \lambda_i \lambda_j z_i^2 z_j^2}{(\bfz^T \Lambda \bfz)^2} \right] - \lambda_{D,S,i} \lambda_{D,S,j}; \quad i \neq j
+A\BV(l_i) &=&\BE [ (D^-_\bfZ (\bfz))^4 (\BS_{ii}( \Lambda^{1/2} \bfz; {\bf 0}))^2 ] - \lambda_{D,i}^2,\\
+A\BC(l_i, l_j) &=& \BE [ (D^-_\bfZ (\bfz))^4 (\BS_{ij}( \Lambda^{1/2} \bfz; {\bf 0}))^2 ] - \lambda_{D,i} \lambda_{D,j}; \quad i \neq j.
 \end{eqnarray}
@@
 
-\begin{proof}[Proof of Corollary \ref{Corollary:eigendist}]
-In spirit, this corollary is similar to Theorem 13.5.1 in \cite{anderson}.
-Due to the decomposition (\ref{equation:decompEq}) we have, for the distribution $F_\Lambda$, the following relation between any off-diagonal element of $\hat S^D(F_\Lambda)$ and the corresponding element in the estimate of eigenvectors $\hat\Gamma_D (F_\Lambda)$:
-
-$$ \sqrt n \hat\gamma_{D,ij} (F_\Lambda) = \sqrt n \frac{\hat S^D_{ij} (F_\Lambda)}{\lambda_{D,S,i} - \lambda_{D,S,j}}; \quad i \neq j$$
-
-So that for eigenvector estimates of the original $F$ we have
-
-\begin{equation} \label{equation:app1}
-\sqrt n (\hat\bfgamma_{D,i} - \bfgamma_i) = \sqrt n \Gamma (\hat \bfgamma_{D,i}(F_\Lambda) - \bfe_i ) = \sqrt n \left[ \sum_{k=1; k \neq i}^p \hat \gamma_{D,ik}(F_\Lambda)\bfgamma_k + (\hat \gamma_{D,ii}(F_\Lambda) - 1)\bfgamma_i \right]
-\end{equation}
-
-$\sqrt n (\hat \gamma_{D,ii}(F_\Lambda) - 1) =  o_P(1)$ and $ACov(\sqrt n \hat S^D_{ik}(F_\Lambda), \sqrt n \hat S^D_{il}(F_\Lambda)) = 0$ for $k \neq l$, so the above equation implies
-
-$$ AVar(\bfg_i) = AVar (\sqrt n (\hat\bfgamma_{D,i} - \bfgamma_i)) = \sum_{k=1; k \neq i}^p \frac{AVar(\sqrt n \hat S^D_{ik}(F_\Lambda))}{(\lambda_{D,s,i} - \lambda_{D,S,k})^2} \bfgamma_k \bfgamma_k^T $$
-
-For the covariance terms, from (\ref{equation:app1}) we get, for $i \neq j$,
-
-\begin{eqnarray*}
-ACov(\bfg_i, \bfg_j) &=& ACov (\sqrt n (\hat\bfgamma_{D,i} - \bfgamma_i), \sqrt n (\hat\bfgamma_{D,j} - \bfgamma_j))\\
-&=& ACov \left( \sum_{k=1; k \neq i}^p \sqrt n \hat \gamma_{D,ik}(F_\Lambda)\bfgamma_k, \sum_{k=1; k \neq j}^p \sqrt n \hat \gamma_{D,jk}(F_\Lambda)\bfgamma_k \right)\\
-&=& ACov \left( \sqrt n \hat \gamma_{D,ij}(F_\Lambda)\bfgamma_j, \sqrt n \hat \gamma_{D,ji}(F_\Lambda)\bfgamma_i \right)\\
-&=& - \frac{AVar(\sqrt n \hat S^D_{ij}(\Lambda))}{(\lambda_{D,s,i} - \lambda_{D,S,j})^2} \bfgamma_j \bfgamma_i^T
-\end{eqnarray*}
-
-The exact forms given in the statement of the corollary now follows from the  Form of $V_{D,S}$ in Appendix \ref{section:appA}.
-
-\paragraph{}For the on-diagonal elements of $\hat S^D(F_\Lambda)$ Theorem \ref{Theorem:decomp} gives us $ \sqrt n \hat\lambda_{D,s,i} (F_\Lambda) = \sqrt n \hat S^D_{ii}(F_\Lambda)$ for $i = 1,...,p$.
-Hence
-
-\begin{eqnarray*}
-AVar(l_i) &=& AVar(\sqrt n \hat\lambda_{D,s,i} - \sqrt n \lambda_{D,S,i})\\
-&=& AVar(\sqrt n \hat\lambda_{D,s,i} (F_\Lambda) - \sqrt n \lambda_{D,S,i}(F_\Lambda))\\
-&=& AVar(\sqrt n S^D_{ii}(F_\Lambda))
-\end{eqnarray*}
-
-A similar derivation gives the expression for $AVar(l_i,l_j); i \neq j$.
-Finally, since the asymptotic covariance between an on-diagonal and an off-diagonal element of $\hat S^D(F_\Lambda)$, it follows that the elements of $G$ and diagonal elements of $L$ are independent.
-\end{proof}
-
-\section{Proofs}\label{section:appC}
+\newpage
+\section{Proofs}
+\label{section:appC}
 
@@
 Cov(\tilde\bfX) &=& E(\tilde\bfX \tilde\bfX^T) - E(\tilde\bfX) E(\tilde\bfX)^T\\
-&=& \Gamma . E \left[ (\tilde D_\bfZ(\bfz))^2 \frac{\|\bfz\|^2}{\| \Lambda^{1/2}\bfz\|} \Lambda^{1/2} \bfS(\bfz) \bfS(\bfz)^T \Lambda^{1/2} \right] \Gamma^T - {\bf 0}_p {\bf 0}_p^T\\
-&=& \Gamma .E \left[ (\tilde D_\bfZ(\bfz))^2 \frac{\Lambda^{1/2} \bfz \bfz^T \Lambda^{1/2}}{\bfz^T \Lambda \bfz} \right] \Gamma^T
+&=& \Gamma . E \left[ (D^-_\bfZ(\bfz))^2 \frac{\|\bfz\|^2}{\| \Lambda^{1/2}\bfz\|} \Lambda^{1/2} \bfS(\bfz) \bfS(\bfz)^T \Lambda^{1/2} \right] \Gamma^T - {\bf 0}_p {\bf 0}_p^T\\
+&=& \Gamma .E \left[ (D^-_\bfZ(\bfz))^2 \frac{\Lambda^{1/2} \bfz \bfz^T \Lambda^{1/2}}{\bfz^T \Lambda \bfz} \right] \Gamma^T
 \end{eqnarray*}
@@
 %
-$$ S_n = \sqrt n \left[ \frac{1}{n} \sum_{i=1}^n \left| (\tilde D^{n} _\bfX (\bfx_i))^2  - (\tilde D_\bfX (\bfx_i))^2 \right| SS(\bfx_i; \hat\bfmu_n) \right] $$
+$$ S_n = \sqrt n \left[ \frac{1}{n} \sum_{i=1}^n \left| (\tilde D^{n} _\bfX (\bfx_i))^2  - (D^-_\bfX (\bfx_i))^2 \right| SS(\bfx_i; \hat\bfmu_n) \right] $$
 %
@@
 %\begin{eqnarray}\label{eqn:AppEqn1}
-%\frac{(\bft^T S_n \bft)^2}{n} & = & \left[ \frac{1}{n} \sum_{i=1}^n \left| (\tilde D^{n} _\bfX (\bfx_i))^2  - (\tilde D_\bfX (\bfx_i))^2 \right|^2  \bft^T SS(\bfx_i; \hat\bfmu_n) \bft \right]^2 \notag\\
-%& \leq & \left[ \frac{1}{n} \sum_{i=1}^n \left| (\tilde D^{n} _\bfX (\bfx_i))^2  - (\tilde D_\bfX (\bfx_i))^2 \right|^2 \right] \left[ \frac{1}{n} \left( \sqrt n.\frac{1}{n} \sum_{i=1}^n  SS(\bfx, \hat\bfmu_n) \right) \right]
+%\frac{(\bft^T S_n \bft)^2}{n} & = & \left[ \frac{1}{n} \sum_{i=1}^n \left| (\tilde D^{n} _\bfX (\bfx_i))^2  - (D^-_\bfX (\bfx_i))^2 \right|^2  \bft^T SS(\bfx_i; \hat\bfmu_n) \bft \right]^2 \notag\\
+%& \leq & \left[ \frac{1}{n} \sum_{i=1}^n \left| (\tilde D^{n} _\bfX (\bfx_i))^2  - (D^-_\bfX (\bfx_i))^2 \right|^2 \right] \left[ \frac{1}{n} \left( \sqrt n.\frac{1}{n} \sum_{i=1}^n  SS(\bfx, \hat\bfmu_n) \right) \right]
 %\end{eqnarray}
@@
 \label{equation:lemma1eq}
-| (\tilde D^{n_1}_\bfX(\bfx_i))^2 - (\tilde D_\bfX(\bfx_i))^2 | < \epsilon
+| (\tilde D^{n_1}_\bfX(\bfx_i))^2 - (D^-_\bfX(\bfx_i))^2 | < \epsilon
 \end{equation}
@@
 \frac{1}{n} \sum_{i=1}^n (\tilde D^n_\bfX (\bfx_i))^2 SS(\bfx_i; \hat\bfmu_n) -
-\frac{1}{n} \sum_{i=1}^n (\tilde D_\bfX (\bfx_i))^2 SS(\bfx_i; \bfmu) \right] &\leq & \hspace{1em} \notag\\
+\frac{1}{n} \sum_{i=1}^n (D^-_\bfX (\bfx_i))^2 SS(\bfx_i; \bfmu) \right] &\leq & \hspace{1em} \notag\\
 S_n +  \sqrt{n} \left[ \frac{1}{n} \sum_{i=1}^{n} \left\{ SS(\bfx_i; \hat\bfmu_{n}) - SS(\bfx_i; \bfmu) \right\} \right] &&
@@
 \begin{eqnarray*}
-\sqrt n \left[ vec\left\{ \frac{1}{n} \sum_{i=1}^n (\tilde D^n_\bfX (\bfx_i))^2 SS(\bfx_i; \hat\bfmu_n) \right\} - vec\left\{ \frac{1}{n} \sum_{i=1}^n (\tilde D_\bfX (\bfx_i))^2 SS(\bfx_i; \bfmu) \right\} \right] +\\
-\sqrt n \left[ vec\left\{ \frac{1}{n} \sum_{i=1}^n (\tilde D_\bfX (\bfx_i))^2 SS(\bfx_i; \bfmu) \right\} - E \left[ vec\left\{ (\tilde D_\bfX (\bfx))^2 SS(\bfx; \bfmu) \right\} \right] \right]
+\sqrt n \left[ vec\left\{ \frac{1}{n} \sum_{i=1}^n (\tilde D^n_\bfX (\bfx_i))^2 SS(\bfx_i; \hat\bfmu_n) \right\} - vec\left\{ \frac{1}{n} \sum_{i=1}^n (D^-_\bfX (\bfx_i))^2 SS(\bfx_i; \bfmu) \right\} \right] +\\
+\sqrt n \left[ vec\left\{ \frac{1}{n} \sum_{i=1}^n (D^-_\bfX (\bfx_i))^2 SS(\bfx_i; \bfmu) \right\} - E \left[ vec\left\{ (D^-_\bfX (\bfx))^2 SS(\bfx; \bfmu) \right\} \right] \right]
 \end{eqnarray*}
@@
 \end{proof}
+
+\begin{proof}[Proof of Corollary \ref{Corollary:eigendist}]
+In spirit, this corollary is similar to Theorem 13.5.1 in \cite{anderson}.
+Due to the decomposition (\ref{equation:decompEq}) we have, for the distribution $F_\Lambda$, the following relation between any off-diagonal element of $\hat S^D(F_\Lambda)$ and the corresponding element in the estimate of eigenvectors $\hat\Gamma_D (F_\Lambda)$:
+
+$$ \sqrt n \hat\gamma_{D,ij} (F_\Lambda) = \sqrt n \frac{\hat S^D_{ij} (F_\Lambda)}{\lambda_{D,S,i} - \lambda_{D,S,j}}; \quad i \neq j$$
+
+So that for eigenvector estimates of the original $F$ we have
+
+\begin{equation} \label{equation:app1}
+\sqrt n (\hat\bfgamma_{D,i} - \bfgamma_i) = \sqrt n \Gamma (\hat \bfgamma_{D,i}(F_\Lambda) - \bfe_i ) = \sqrt n \left[ \sum_{k=1; k \neq i}^p \hat \gamma_{D,ik}(F_\Lambda)\bfgamma_k + (\hat \gamma_{D,ii}(F_\Lambda) - 1)\bfgamma_i \right]
+\end{equation}
+
+$\sqrt n (\hat \gamma_{D,ii}(F_\Lambda) - 1) =  o_P(1)$ and $ACov(\sqrt n \hat S^D_{ik}(F_\Lambda), \sqrt n \hat S^D_{il}(F_\Lambda)) = 0$ for $k \neq l$, so the above equation implies
+
+$$ A\BV(\bfg_i) = AVar (\sqrt n (\hat\bfgamma_{D,i} - \bfgamma_i)) = \sum_{k=1; k \neq i}^p \frac{A\BV(\sqrt n \hat S^D_{ik}(F_\Lambda))}{(\lambda_{D,s,i} - \lambda_{D,S,k})^2} \bfgamma_k \bfgamma_k^T $$
+
+For the covariance terms, from (\ref{equation:app1}) we get, for $i \neq j$,
+
+\begin{eqnarray*}
+ACov(\bfg_i, \bfg_j) &=& ACov (\sqrt n (\hat\bfgamma_{D,i} - \bfgamma_i), \sqrt n (\hat\bfgamma_{D,j} - \bfgamma_j))\\
+&=& ACov \left( \sum_{k=1; k \neq i}^p \sqrt n \hat \gamma_{D,ik}(F_\Lambda)\bfgamma_k, \sum_{k=1; k \neq j}^p \sqrt n \hat \gamma_{D,jk}(F_\Lambda)\bfgamma_k \right)\\
+&=& ACov \left( \sqrt n \hat \gamma_{D,ij}(F_\Lambda)\bfgamma_j, \sqrt n \hat \gamma_{D,ji}(F_\Lambda)\bfgamma_i \right)\\
+&=& - \frac{A\BV(\sqrt n \hat S^D_{ij}(\Lambda))}{(\lambda_{D,s,i} - \lambda_{D,S,j})^2} \bfgamma_j \bfgamma_i^T
+\end{eqnarray*}
+
+The exact forms given in the statement of the corollary now follows from the  Form of $\BV_D$ in Appendix \ref{section:appA}.
+
+\paragraph{}For the on-diagonal elements of $\hat S^D(F_\Lambda)$ Theorem \ref{Theorem:decomp} gives us $ \sqrt n \hat\lambda_{D,s,i} (F_\Lambda) = \sqrt n \hat S^D_{ii}(F_\Lambda)$ for $i = 1,...,p$.
+Hence
+
+\begin{eqnarray*}
+A\BV(l_i) &=& A\BV(\sqrt n \hat\lambda_{D,s,i} - \sqrt n \lambda_{D,S,i})\\
+&=& A\BV(\sqrt n \hat\lambda_{D,s,i} (F_\Lambda) - \sqrt n \lambda_{D,S,i}(F_\Lambda))\\
+&=& A\BV(\sqrt n S^D_{ii}(F_\Lambda))
+\end{eqnarray*}
+
+A similar derivation gives the expression for $A\BV(l_i,l_j); i \neq j$.
+Finally, since the asymptotic covariance between an on-diagonal and an off-diagonal element of $\hat S^D(F_\Lambda)$, it follows that the elements of $G$ and diagonal elements of $L$ are independent.
+\end{proof}
+
+\begin{table}[b]
+\begin{footnotesize}
+    \begin{tabular}{c|cc|ccc|ccc}
+    \hline
+    $F$ = Bivariate $t_5$    & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
+    $n$=20                   & 0.80 & 0.83  & 0.95   & 0.95   & 0.89  & 1.00    & 0.96    & 0.89   \\
+    $n$=50                   & 0.86 & 0.90  & 1.25   & 1.10   & 1.21  & 1.32    & 1.13    & 1.25   \\
+    $n$=100                  & 1.02 & 1.04  & 1.58   & 1.20   & 1.54  & 1.67    & 1.24    & 1.63   \\
+    $n$=300                  & 1.24 & 1.28  & 1.81   & 1.36   & 1.82  & 1.93    & 1.44    & 1.95   \\
+    $n$=500                  & 1.25 & 1.29  & 1.80   & 1.33   & 1.84  & 1.91    & 1.39    & 1.97   \\ \hline
+    $F$ = Bivariate $t_6$    & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
+    $n$=20                   & 0.77 & 0.79  & 0.92   & 0.92   & 0.86  & 0.96    & 0.92    & 0.85   \\
+    $n$=50                   & 0.76 & 0.78  & 1.11   & 1.00   & 1.08  & 1.17    & 1.03    & 1.13   \\
+    $n$=100                  & 0.78 & 0.79  & 1.27   & 1.06   & 1.33  & 1.35    & 1.11    & 1.41   \\
+    $n$=300                  & 0.88 & 0.91  & 1.29   & 1.09   & 1.35  & 1.38    & 1.15    & 1.45   \\
+    $n$=500                  & 0.93 & 0.96  & 1.37   & 1.13   & 1.40  & 1.44    & 1.19    & 1.48   \\ \hline
+    $F$ = Bivariate $t_{10}$ & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
+    $n$=20                   & 0.70 & 0.72  & 0.83   & 0.84   & 0.77  & 0.89    & 0.87    & 0.79   \\
+    $n$=50                   & 0.58 & 0.60  & 0.90   & 0.84   & 0.86  & 0.95    & 0.88    & 0.91   \\
+    $n$=100                  & 0.57 & 0.59  & 0.92   & 0.87   & 0.97  & 0.98    & 0.90    & 1.03   \\
+    $n$=300                  & 0.62 & 0.64  & 0.93   & 0.85   & 0.99  & 0.99    & 0.91    & 1.06   \\
+    $n$=500                  & 0.62 & 0.65  & 0.93   & 0.86   & 1.00  & 1.00    & 0.92    & 1.08   \\ \hline
+    $F$ = Bivariate $t_{15}$ & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
+    $n$=20                   & 0.63 & 0.66  & 0.76   & 0.78   & 0.72  & 0.81    & 0.81    & 0.73   \\
+    $n$=50                   & 0.52 & 0.52  & 0.79   & 0.75   & 0.80  & 0.84    & 0.79    & 0.85   \\
+    $n$=100                  & 0.51 & 0.52  & 0.83   & 0.77   & 0.88  & 0.88    & 0.81    & 0.94   \\
+    $n$=300                  & 0.55 & 0.56  & 0.84   & 0.79   & 0.91  & 0.89    & 0.84    & 0.98   \\
+    $n$=500                  & 0.56 & 0.59  & 0.85   & 0.80   & 0.93  & 0.91    & 0.86    & 0.99   \\ \hline
+    $F$ = Bivariate $t_{25}$ & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
+    $n$=20                   & 0.63 & 0.65  & 0.77   & 0.79   & 0.74  & 0.80    & 0.81    & 0.74   \\
+    $n$=50                   & 0.49 & 0.50  & 0.73   & 0.71   & 0.76  & 0.78    & 0.75    & 0.80   \\
+    $n$=100                  & 0.45 & 0.46  & 0.73   & 0.69   & 0.81  & 0.78    & 0.73    & 0.87   \\
+    $n$=300                  & 0.51 & 0.52  & 0.78   & 0.75   & 0.87  & 0.83    & 0.79    & 0.94   \\
+    $n$=500                  & 0.53 & 0.55  & 0.79   & 0.75   & 0.87  & 0.84    & 0.80    & 0.94   \\ \hline
+    $F$ = BVN                & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
+    $n$=20                   & 0.56 & 0.60  & 0.69   & 0.71   & 0.67  & 0.73    & 0.74    & 0.68   \\
+    $n$=50                   & 0.42 & 0.43  & 0.66   & 0.66   & 0.70  & 0.71    & 0.69    & 0.75   \\
+    $n$=100                  & 0.42 & 0.43  & 0.69   & 0.66   & 0.77  & 0.74    & 0.71    & 0.83   \\
+    $n$=300                  & 0.47 & 0.49  & 0.71   & 0.69   & 0.82  & 0.76    & 0.73    & 0.88   \\
+    $n$=500                  & 0.48 & 0.50  & 0.73   & 0.71   & 0.83  & 0.78    & 0.76    & 0.89   \\ \hline
+    \end{tabular}
+\end{footnotesize}
+\caption{Finite sample efficiencies of several scatter matrices: $p=2$}
+\label{table:FSEtable2}
+\end{table}
+
+\begin{table}[b]
+\begin{footnotesize}
+   \begin{tabular}{c|cc|ccc|ccc}
+    \hline
+    3-variate $t_5$    & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
+    $n$=20             & 0.96 & 0.97  & 1.06   & 1.03   & 0.99  & 1.07    & 1.06    & 0.97   \\
+    $n$=50             & 1.07 & 1.08  & 1.28   & 1.20   & 1.18  & 1.33    & 1.23    & 1.20   \\
+    $n$=100            & 1.12 & 1.15  & 1.49   & 1.31   & 1.40  & 1.57    & 1.38    & 1.48   \\
+    $n$=300            & 1.49 & 1.54  & 2.09   & 1.82   & 2.07  & 2.19    & 1.93    & 2.18   \\
+    $n$=500            & 1.60 & 1.66  & 2.18   & 1.87   & 2.21  & 2.27    & 1.95    & 2.30   \\ \hline
+    3-variate $t_6$    & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
+    $n$=20             & 0.90 & 0.92  & 1.00   & 0.99   & 0.95  & 1.02    & 1.01    & 0.94   \\
+    $n$=50             & 0.95 & 0.96  & 1.16   & 1.09   & 1.09  & 1.21    & 1.14    & 1.11   \\
+    $n$=100            & 0.98 & 0.99  & 1.32   & 1.22   & 1.25  & 1.38    & 1.27    & 1.29   \\
+    $n$=300            & 1.10 & 1.14  & 1.57   & 1.40   & 1.58  & 1.62    & 1.47    & 1.64   \\
+    $n$=500            & 1.17 & 1.20  & 1.57   & 1.43   & 1.60  & 1.63    & 1.51    & 1.67   \\ \hline
+    3-variate $t_{10}$ & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
+    $n$=20             & 0.87 & 0.88  & 0.95   & 0.94   & 0.90  & 0.97    & 0.98    & 0.89   \\
+    $n$=50             & 0.77 & 0.79  & 0.96   & 0.92   & 0.94  & 0.99    & 0.96    & 0.95   \\
+    $n$=100            & 0.75 & 0.76  & 1.02   & 0.95   & 1.01  & 1.06    & 1.00    & 1.05   \\
+    $n$=300            & 0.73 & 0.75  & 1.03   & 0.98   & 1.10  & 1.08    & 1.03    & 1.15   \\
+    $n$=500            & 0.73 & 0.76  & 1.02   & 0.98   & 1.09  & 1.06    & 1.02    & 1.14   \\ \hline
+    3-variate $t_{15}$ & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
+    $n$=20             & 0.84 & 0.86  & 0.92   & 0.92   & 0.89  & 0.94    & 0.94    & 0.87   \\
+    $n$=50             & 0.75 & 0.76  & 0.92   & 0.90   & 0.90  & 0.96    & 0.94    & 0.93   \\
+    $n$=100            & 0.66 & 0.67  & 0.91   & 0.87   & 0.95  & 0.96    & 0.92    & 1.00   \\
+    $n$=300            & 0.61 & 0.64  & 0.90   & 0.87   & 1.00  & 0.93    & 0.91    & 1.04   \\
+    $n$=500            & 0.65 & 0.67  & 0.89   & 0.87   & 0.99  & 0.93    & 0.91    & 1.03   \\ \hline
+    3-variate $t_{25}$ & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
+    $n$=20             & 0.78 & 0.79  & 0.87   & 0.89   & 0.87  & 0.89    & 0.92    & 0.86   \\
+    $n$=50             & 0.70 & 0.71  & 0.88   & 0.86   & 0.88  & 0.91    & 0.90    & 0.90   \\
+    $n$=100            & 0.61 & 0.63  & 0.86   & 0.83   & 0.89  & 0.90    & 0.88    & 0.94   \\
+    $n$=300            & 0.58 & 0.59  & 0.83   & 0.80   & 0.92  & 0.87    & 0.85    & 0.98   \\
+    $n$=500            & 0.62 & 0.64  & 0.83   & 0.82   & 0.94  & 0.88    & 0.87    & 0.99   \\ \hline
+    3-variate Normal   & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
+    $n$=20             & 0.76 & 0.78  & 0.85   & 0.87   & 0.84  & 0.87    & 0.90    & 0.83   \\
+    $n$=50             & 0.66 & 0.67  & 0.82   & 0.81   & 0.84  & 0.86    & 0.86    & 0.86   \\
+    $n$=100            & 0.56 & 0.58  & 0.77   & 0.75   & 0.83  & 0.82    & 0.79    & 0.87   \\
+    $n$=300            & 0.53 & 0.55  & 0.75   & 0.74   & 0.85  & 0.79    & 0.78    & 0.90   \\
+    $n$=500            & 0.56 & 0.58  & 0.76   & 0.76   & 0.87  & 0.80    & 0.80    & 0.92   \\ \hline
+    \end{tabular}
+\end{footnotesize}
+\caption{Finite sample efficiencies of several scatter matrices: $p=3$}
+\label{table:FSEtable3}
+\end{table}

### 2018-03-23 MS-new/7_Appendix.tex
.

@@
 \begin{proof}[Proof of Proposition \ref{proposition:SignTest}]
-Under contiguous alternatives $H_0: \bfmu = \bfmu_0$, the weighted sign test statistic $T_{n,w}$ has mean $E (w(\bfZ) \bfS (\bfZ))$.
+Under contiguous alternatives $H_0: \bfmu = \bfmu_0$, the weighted sign test statistic $T_{n,w}$ has mean $\BE (w(\bfZ) \bfS (\bfZ))$.
 For spherically symmetric $\bfZ$, $w(\bfZ)$ depends on $\bfZ$ only through its norm.
-Since $\| \bfZ \|$ and $\bfS(\bfZ)$ are independent, we get $E (w(\bfZ) \bfS (\bfZ)) = E w(\bfZ).
-E \bfS (\bfZ)$.
-The same kind of decomposition holds for $Cov(w(\bfZ) \bfS(\bfZ))$.
+Since $\| \bfZ \|$ and $\bfS(\bfZ)$ are independent, we get $\BE (w(\bfZ) \bfS (\bfZ)) = \BE w(\bfZ).
+\BE \bfS (\bfZ)$.
+A similar decomposition holds for $\BV (w(\bfZ) \bfS(\bfZ))$.
 
-We can now simplify the approximate local power $\beta_{n,w}$ of the level-$\alpha$ ($0 < \alpha < 1$) test based on $T_{n,w}$:
+We can now simplify the approximate local power $\beta_{n,w}$ of a level-$\alpha$, $0 < \alpha < 1$, test based on $T_{n,w}$:
 %
-\begin{eqnarray*}
-\beta_{n,w} &=& K_p \left( \chi^2_{p,\alpha} + n (E (w(\bfZ) \bfS (\bfZ))^T \right.\\
-&& \left. [ E (w^2(\bfZ) \bfS (\bfZ) \bfS (\bfZ)^T) ]^{-1} (E (w(\bfZ) \bfS (\bfZ)) \right)\\
-&=& K_p \left( \chi^2_{p,\alpha} + \frac{E^2 w(\bfZ)}{Ew^2(\bfZ)}. E\bfS(\bfZ)^T [Cov(\bfS(\bfZ)]^{-1} E\bfS(\bfZ) \right)
-\end{eqnarray*}
+\begin{align*}
+\beta_{n,w} &= K_p \left( \chi^2_{p,\alpha} + n (\BE (w(\bfZ) \bfS (\bfZ))^T
+[ \BE (w^2(\bfZ) \bfS (\bfZ) \bfS (\bfZ)^T) ]^{-1} (\BE (w(\bfZ) \bfS (\bfZ)) \right)\\
+&= K_p \left( \chi^2_{p,\alpha} + \frac{\BE^2 w(\bfZ)}{\BE w^2(\bfZ)}. \BE\bfS(\bfZ)^T [\BV \bfS(\bfZ)]^{-1} \BE \bfS(\bfZ) \right),
+\end{align*}
 %
 where $K_p$ and $\chi^2_{p,\alpha}$ are distribution function and upper-$\alpha$ cutoff of a $\chi^2_p$ distribution, respectively.
-Since $E^2 w(\bfZ) \leq Ew(\bfZ)$, $\beta_{n,w}$ the largest possible value of $\beta_{n,w}$ is $K_p ( \chi^2_{p,\alpha} + E\bfS(\bfZ)^T [Cov(\bfS(\bfZ)]^{-1} E\bfS(\bfZ) )$, the approximate power of the unweighted sign test statistic.
-Equality is of course achieved when $w(\bfZ)$ is a constant independent of $\bfZ$.
+Since $\BE^2 w(\bfZ) \leq \BE w(\bfZ)$, the largest possible value of $\beta_{n,w}$ is $K_p ( \chi^2_{p,\alpha} + \BE \bfS(\bfZ)^T [\BV \bfS(\bfZ)]^{-1} \BE \bfS(\bfZ) )$, the approximate power of the unweighted sign test statistic.
+Equality is achieved when $w(\bfZ)$ is a constant independent of $\bfZ$.
 \end{proof}
@@
 
-\begin{table}[b]
+\begin{table}[t]
 \begin{footnotesize}

### 2018-03-30 MS-new/1_Introduction.tex
new draft sent to anshu da

@@
 This is a generalization of the real-valued case of the indicator for whether a point $x \in \BR$ is to the right, left or at a scalar $\mu_{x} \in \BR$, and was first introduced by \cite{MottonenOja95}.
-Given a data matrix $\bfX = (\bfx_{1}, \ldots, \bfx_{n})^T$, a popular approach of using spatial signs in the literature has been to take spatial signs of the data points, i.e.
-$\bfS(\bfx_i)$, and use the matrix of signs as a proxy of $\bfX$ to formulate robust versions of location and scale problems  \citep{locantore99, OjaBook10,WangPengLi15}.
+Given a data matrix $\BX = (\bfx_{1}, \ldots, \bfx_{n})^T$, a popular approach of using spatial signs in the literature has been to take spatial signs of the data points, i.e.
+$\bfS(\bfx_i)$, and use the matrix of signs as a proxy of $\BX$ to formulate robust versions of location and scale problems  \citep{locantore99, OjaBook10,WangPengLi15}.
 
@@
 As a result, spatial sign-based procedures suffer from low efficiency.
-For example, eigenvector estimates obtained from the covariance matrix of spatial sign, which is called the Sign Covariance Matrix (SCM), are asymptotically inadmissible \citep{magyar14}- in the sense that there is an estimator (namely, Tyler's M-estimate of scatter \citep{tyler87}) that has uniformly lower asymptotic risk than the SCM.
+For example, eigenvector estimates obtained from the covariance matrix of spatial signs, which is called the Sign Covariance Matrix (SCM), are asymptotically inadmissible \citep{magyar14}- in the sense that there is an estimator (namely, Tyler's M-estimate of scatter \citep{tyler87}) that has uniformly lower asymptotic risk than the SCM.
 
@@
 To utilize the magnitude information of sample points, at the same time preserving the robustness property, we propose a general class weighted spatial sign functions.
-To this end, we first propose what we call a {\it peripherality function}.
+To this end, we first define what we call a {\it peripherality function}.
 
@@
 
-The peripherality function quantifies the relative position of $\bfx$ with respect to $\bfmu_{F}$, and condition (P) formalizes a general notion of centrality.
+Peripherality functions quantify the relative position of $\bfx$ with respect to $\bfmu_{F}$, and condition (P) formalizes a general notion of centrality.
 A whole class of such functions can be defined from {\it Data Depth} functions \citep{zuo00}, which give the center-outward ranking of points in a multivariate dataset.
@@
 Peripherality functions can be defined as some inverse ranking based on data depth, and the concept of {\it outlyingness} associated with data depth is essentially same as what we use in this paper.
-However, traditional depth functions require a wider array of theoretical conditions \citep{zuo00} in addition to our condition (P), and a sizeable portion of methods we discuss do not require the use of depth functions {\it per se} to be implemented.
+However, traditional depth functions require a wide array of theoretical conditions \citep{zuo00}, and a sizeable portion of methods we discuss do not require the use of depth functions {\it per se} to be implemented.
 %We use the term {\it peripherality} to keep track of the difference in application contexts and technical assumptions.
@@
 	\centering
-		\includegraphics[height=6cm]{../Codes/ranks}
-	\caption{(Left) 1000 points randomly drawn from $\mathcal N_2\left((0,0)^T, \left(\protect\begin{smallmatrix} 5 & -4 \\ -4 & 5 \protect\end{smallmatrix}\right)\right) $ and (Right) their signed peripherality functions based on halfspace depth}
+		\includegraphics[width=\textwidth]{../Codes/signs_and_ranks}
+	\caption{(Left) 1000 points randomly drawn from $\mathcal N_2\left((0,0)^T, \left(\protect\begin{smallmatrix} 5 & -4 \\ -4 & 5 \protect\end{smallmatrix}\right)\right) $, (center) their spatial signs, and (right) signed peripherality functions based on halfspace depth.}
 	\label{fig:rankplot}
@@
 As seen in the third panel of Figure~\ref{fig:rankplot}, $\bfR (\bfx; \bfmu_x, \BF)$ maps points {\it inside} a ball of finite radius, thus limiting the influence of outlying points {\it and} preserving the magnitude information of data points.
-In this paper, we demonstrate certain interesting applications of this multivariate rank transformation in robust statistical inference.
+In this paper, we demonstrate certain interesting applications of this multivariate rank transformation in statistical inference.
 Notice that for the trivial choice $P( \bfx; \BF) = \| \bfx - \bfmu_{F} \|$ and $\bfmu_x = \bfmu_F, \kappa_P(x)=x$, we get $\bfR (\bfx; \bfmu_x, \BF) = \bfx$.
@@
 The notion of multivariate ranks goes back to \cite{PuriSenBook}, where they take the vector consisting of marginal univariate ranks as multivariate rank vector.
-Subsequent definitions of multivariate ranks were proposed by \cite{MottonenOja95,HallinPaindaveine02} and \cite{Chernozhukov14}.
+Subsequent definitions of multivariate ranks were proposed by \cite{MottonenOja95}, \cite{HallinPaindaveine02} and \cite{Chernozhukov17}.
 Compared to them, the advantages of our signed peripherality function are two-fold: interpretability and flexibility.
@@
 
-In this paper, we assume $\BF$ to be an elliptical distribution. Following \cite{FangEtal90}, elliptical distributions can be formally defined here using their characteristic function:
+We assume $\BF$ to be an elliptical distribution. Following \cite{FangEtal90}, elliptical distributions can be formally defined here using their characteristic function:
 %
@@
 
-\paragraph{Organization of paper.}
+\paragraph{Organization of paper.} We start by elaborating on the use of weighted spatial signs in the problem of estimating or testing for the location parameter $\bfmu$ of $\BF$ in Section~\ref{section:LocSection}.
+Specifically, we use the signed peripherality vectors in \eqref{eqn:rank} to propose more efficient versions of the spatial median \citep{brown83, Chaudhuri96} and the high-dimensional testing procedure of \cite{WangPengLi15}.
+In Section~\ref{section:dcmSection}, we take inverse depth functions \citep{MajumdarChatterjeeStat} as our weights, and lay out a framework to estimate the different components of the covariance matrix $\Sigma$- namely, its eigenvectors (i.e.
+principal component analysis (PCA)), eigenvalues and $\Sigma$ itself.
+The two subsequent sections are devoted to the applications of the robust PCA method in Sections~\ref{section:LocSection} and \ref{section:dcmSection}.
+In Section~\ref{section:sdrSection} we use the robust estimates of $\bfmu$ and eigenvectors of $\Sigma$ in a supervised learning problem, while in Section~\ref{section:fpcaSection} we propose a robust functional PCA based on our methodology.
+We conclude with a discussion in \ref{section:Conclusion}.
+The appendix contains auxiliary theoretical results and proofs.
 
-\paragraph{Notation.}
+\paragraph{Notation.} We denote vectors $\bfa \in \BR^A$ by bold small letters, matrices $\BA \in \BR^{A \times A}$ by blackboard bold or greek capital letters, vector-valued random variables $\bfA$ by bold capital letters and their elements by small letters.
+For the vector $\bfa$, we denote euclidean norm and $\ell_1$-norm by $\|a\|$ and $\| a\|_1$, respectively.
+We denote expectations by $\BE(\cdot)$, the variance of a scalar random variable or covariance of a vector-valued random variable by $\BV(\cdot)$, and the covariance of two scalar random variables by $\BC(\cdot)$.
+Asymptotic variances (or covariance matrices) and covariances are denoted by $A\BV(\cdot)$ and $A\BC(\cdot)$, respectively.
+Sample variances are denoted by $\BS(\cdot)$, i.e.
+$\BS(\bfa) = \bfa^T \bfa /a - (\sum_{i=1}^A a_i/a)^2$ and $\BS(\BB) = \BB^T \BB/B - \bar \bfb \bar \bfb^T$ for $\BB = (\bfb_1, \ldots, \bfb_B)^T \in \BR^{B \times B_1}$, $\bar \bfb = \sum_{i=1}^B \bfb_i/B$.

### 2018-03-30 MS-new/2_Location.tex
main paper v1 done, proofs and intro remain
new draft sent to anshu da

@@
 $$
-w(\bfA \bfx + \bfb, \bfA \BF + \bfb) = w(\bfx, \BF),
+w(\bfA \bfx + \bfb, \bfA \BF + \bfb) = w(\bfx, \BF)
 $$
@@
 $$
-T_{n,w} = n \bar\bfX_w^T ( \BV \BX_w)^{-1} \bar\bfX_w,
+T_{n,w} = n \bar\bfx_w^T ( \BS (\BX_w))^{-1} \bar\bfx_w,
 $$
 %
-({\colrbf define $\BX_w$}) with $\bar\bfX_w = \sum_{i=1}^n \bfX_{w,i}/n$ and $\bfX_{w,i} = w(\bfX_i ) \bfS (\bfX_i)$ for $i=1,2,...,n$. However, the following holds true for this weighted sign test:
+with $\bar\bfx_w = \sum_{i=1}^n \bfx_{w,i}/n, \bfx_{w,i} = w(\bfx_i ) \bfS (\bfx_i)$ for $i=1,2,...,n$, and $\BX_w = (\bfx_{w,1}, \ldots, \bfx_{w,n})^T$.
+However, the following holds true for this weighted sign test:
 %
 \begin{Proposition}\label{proposition:SignTest}
-Consider $n$ random variables $Z = (\bfZ_1,...,\bfZ_n)^T$ distributed independently and identically as $\mathcal{E}( \bfmu, k \bfI_p, g); k \in \mathbb R$, and the class of hypothesis tests defined above.
+Consider $n$ random variables $\bfZ_1,...,\bfZ_n$ distributed independently and identically as $\mathcal{E}( \bfmu, k \bfI_p, g); k \in \mathbb R$, and the class of hypothesis tests defined above.
 Then, given any $\alpha \in (0,1)$, local power at $\bfmu \neq {\bf 0}_p$ for the level-$\alpha$ test  based on $T_{n,w}$ is maximum when $w(\bfZ_1) = c$, a constant independent of $\bfZ_1$.
@@
 \begin{Theorem}
-Let $\bfA_w, \bfB_w$ be two matrices, dependent on the weight function $w$ such that
+Let $\BA_w, \BB_w$ be two matrices, dependent on the weight function $w$ such that
 %
 $$
-\bfA_w = \BE \left[ \frac{w( \bfepsilon ) }{\| \bfepsilon \|} \left( 1 - \frac{\bfepsilon \bfepsilon^T}{\| \bfepsilon \|^2} \right) \right];
+\BA_w = \BE \left[ \frac{w( \bfepsilon ) }{\| \bfepsilon \|} \left( 1 - \frac{\bfepsilon \bfepsilon^T}{\| \bfepsilon \|^2} \right) \right];
 \quad
-\bfB_w = \BE \left[ \frac{(w( \bfepsilon ))^2 \bfepsilon \bfepsilon^T}{\| \bfepsilon \|^2} \right]
+\BB_w = \BE \left[ \frac{(w( \bfepsilon ))^2 \bfepsilon \bfepsilon^T}{\| \bfepsilon \|^2} \right],
 $$
@@
 \begin{equation}
-\sqrt n (\hat\bfmu_w - \bfmu_w) \leadsto \cN_p ({\bf 0}, \bfA_w^{-1} \bfB_w \bfA_w^{-1})
+\sqrt n (\hat\bfmu_w - \bfmu_w) \leadsto \cN_p ({\bf 0}, \BA_w^{-1} \BB_w \BA_w^{-1}).
 \end{equation}
@@
 $$
-ARE( \bfmu_w, \bfmu_s) = \left[ \frac{\text{det} (\bfA^{-1} \bfB \bfA^{-1})}{\text{det} ( \bfA_w^{-1} \bfB_w \bfA_w^{-1})} \right]^{1/p}
+ARE( \bfmu_w, \bfmu_s) = \left[ \frac{\text{det} ( \BA^{-1} \BB \BA^{-1})}{\text{det} ( \BA_w^{-1} \BB_w \BA_w^{-1})} \right]^{1/p}
 $$
 %
-with $\bfA = \BE [ 1/ \| \bfepsilon \| ( I_p - \bfepsilon \bfepsilon^T/ \| \bfepsilon \|^2 ) ]$ and $\bfB = \BE [ \bfepsilon \bfepsilon^T/ \| \bfepsilon \|^2 ]$.
+with $\BA = \BE [ 1/ \| \bfepsilon \| ( \BI_p - \bfepsilon \bfepsilon^T/ \| \bfepsilon \|^2 ) ]$ and $\BB = \BE [ \bfepsilon \bfepsilon^T/ \| \bfepsilon \|^2 ]$.
 This is further simplified under spherical symmetry:
@@
 $$
-ARE( \bfmu_w, \bfmu_s) = \frac{ \left[ \BE \left( \frac{f(r)}{r} \right) \right]^2}{\BE f^2(r) \left[ \BE \left( \frac{1}{r} \right) \right]^2 }
+ARE( \bfmu_w, \bfmu_s) = \frac{ \left[ \BE \left( \frac{f(r)}{r} \right) \right]^2}{\BE f^2(r) \left[ \BE \left( \frac{1}{r} \right) \right]^2 }.
 $$
@@
 \centering
+\begin{footnotesize}
 \begin{tabular}{c|ccccc}
@@
 \end{tabular}
+\end{footnotesize}
 \caption{Table of $ARE(\bfmu_w; \bfmu_s)$ for different spherical distributions}
@@
 \begin{equation}\label{eqn:hdtest1}
-\frac{C_{n,w}}{\sqrt{\frac{n(n-1)}{2} \text{Tr}(\bfB_w^2)}} \leadsto N(0,1),
+\frac{C_{n,w}}{\sqrt{\frac{n(n-1)}{2} \text{Tr}(\BB_w^2)}} \leadsto N(0,1),
 \end{equation}
@@
 \begin{equation}\label{eqn:hdtest2}
-\frac{C_{n,w} - \frac{n(n-1)}{2} \bfmu_0^T \bfA_w^2 \bfmu_0 (1 + o(1)) }{\sqrt{\frac{n(n-1)}{2} \text{Tr}(\bfB_w^2)}} \leadsto N(0,1).
+\frac{C_{n,w} - \frac{n(n-1)}{2} \bfmu_0^T \BA_w^2 \bfmu_0 (1 + o(1)) }{\sqrt{\frac{n(n-1)}{2} \text{Tr}(\BB_w^2)}} \leadsto N(0,1).
 \end{equation}
@@
 $$
-ARE(C_{n,w}, \text{WPL}; \bfmu_0) = \frac{\bfmu_0^T \bfA_w^2 \bfmu_0}{\bfmu_0^T \bfA^2 \bfmu_0} \sqrt\frac{\text{Tr}(\bfB^2)}{\text{Tr}(\bfB_w^2)} (1 + o(1)),
+ARE(C_{n,w}, \text{WPL}; \bfmu_0) = \frac{\bfmu_0^T \BA_w^2 \bfmu_0}{\bfmu_0^T \BA^2 \bfmu_0} \sqrt\frac{\text{Tr}( \BB^2)}{\text{Tr}( \BB_w^2)} (1 + o(1)),
 $$
 %
-when $\Sigma = k \bfI_p$, this again simplifies to $\BE^2(f(r)/r)/[\BE f^2(r).
+when $\Sigma = k \BI_p$, this again simplifies to $\BE^2(f(r)/r)/[\BE f^2(r).
 \BE^2(1/r)]$.
@@
 \centering
+\begin{footnotesize}
 \begin{tabular}{cc|ccc}\hline
@@
 \end{tabular}
+\end{footnotesize}
 \caption{Table of empirical powers of level-0.05 tests for the Chen and Qin (CQ), WPL and $C_{n,w}$ statistics}

### 2018-03-30 MS-new/3_Scale.tex
new draft sent to anshu da

@@
-\section{Inverse depth and estimation of scatter}
+\section{Inverse depth and estimates of scatter}
 \label{section:dcmSection}
@@
 Given an inverse depth function $D^-_{\bfX}(\bfx)$ we transform the original random variable as: $\tilde \bfX = D^-_\bfX(\bfx) \bfS(\bfx - \bfmu)$.
-We attempt to use the transformed data matrix $\tilde \BX = (\tilde \bfx_1, \ldots, \tilde \bfx_n)^T$ as proxy of the original data matrix $\BX$ for improved estimation of the components of the population covariance matrix $\Sigma$ in this section.
+We use the transformed data matrix $\tilde \BX = (\tilde \bfx_1, \ldots, \tilde \bfx_n)^T$ as proxy of the original data matrix $\BX$ for improved estimation of the components of the population covariance matrix $\Sigma$ in this section.
 To this end, in Section~\ref{subsec:dcm} we give some results characterizing the population covariance matrix of these vectors, i.e.
 $\BV \tilde \bfX$, and its affine equivariant counterpart.
-{\colrbf details of 3.2 and rest}
+Section~\ref{subsec:dcm} gives asymptotic properties of their finite sample versions.
+In Section~\ref{subsec:robustPCA}, we use eigenvectors of these estimates for robust PCA, deriving their influence functions, as well as asymptotic and finite sample efficiencies.
+Finally in Section~\ref{subsec:plugin}, we calculate robust estimates of eigenvalues and propose a plug-in robust estimate of $\Sigma$.
 
@@
 \begin{equation}
-E_{\bfZ_M} \left[ u( \| \bfz_M \| )  \frac{\bfz_M \bfz_M^T}{\| \bfz_M \|^2}  - v( \| \bfz_M \| ) \BI_p \right] = 0
+\BE_{\bfZ_M} \left[ u( \| \bfz_M \| )  \frac{\bfz_M \bfz_M^T}{\| \bfz_M \|^2}  - v( \| \bfz_M \| ) \BI_p \right] = 0
 \end{equation}
@@
 \subsection{Calculating the sample DCM and ADCM}
+\label{subsec:sample-DCM}
 Let us denote $\BS(\bfx; \bfmu) = \bfS(\bfx - \bfmu) \bfS(\bfx - \bfmu)^T$.
@@
 \subsection{Robust PCA using eigenvectors}
-
+\label{subsec:robustPCA}
 We are mainly interested in using the DCM for robust principal component analysis (PCA).
@@
 \begin{table}[t]
-\begin{footnotesize}
+\begin{scriptsize}
     \begin{tabular}{c|cc|ccc|ccc}
     \hline
-    4-variate $t_5$    & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
+    4-variate $t_5$    & SCM  & Tyler & DCM-H & DCM-M & DCM-P & ADCM-H & ADCM-M & ADCM-P \\ \hline
     $n$=20             & 1.04 & 1.02  & 1.10   & 1.07   & 1.02  & 1.09    & 1.07    & 0.98   \\
@@
     $n$=500            & 1.92 & 1.93  & 2.23   & 2.03   & 2.31  & 2.35    & 2.19    & 2.39   \\ \hline
-    4-variate $t_6$    & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
+    4-variate $t_6$    & SCM  & Tyler & DCM-H & DCM-M & DCM-P & ADCM-H & ADCM-M & ADCM-P \\ \hline
     $n$=20             & 1.00 & 1.05  & 1.03   & 1.05   & 1.00  & 1.04    & 1.04    & 0.95   \\
@@
     $n$=500            & 1.26 & 1.34  & 1.55   & 1.49   & 1.60  & 1.65    & 1.61    & 1.69   \\ \hline
-    4-variate $t_{10}$ & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
+    4-variate $t_{10}$ & SCM  & Tyler & DCM-H & DCM-M & DCM-P & ADCM-H & ADCM-M & ADCM-P \\ \hline
     $n$=20             & 0.90 & 0.89  & 0.95   & 0.98   & 0.98  & 0.96    & 1.01    & 0.95   \\
@@
     $n$=500            & 0.88 & 0.92  & 1.10   & 1.10   & 1.23  & 1.19    & 1.22    & 1.29   \\ \hline
-    4-variate $t_{15}$ & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
+    4-variate $t_{15}$ & SCM  & Tyler & DCM-H & DCM-M & DCM-P & ADCM-H & ADCM-M & ADCM-P \\ \hline
     $n$=20             & 0.92 & 0.90  & 0.94   & 0.94   & 0.96  & 0.95    & 0.97    & 0.89   \\
@@
     $n$=500            & 0.73 & 0.76  & 0.95   & 0.96   & 1.06  & 0.94    & 0.97    & 1.06   \\ \hline
-    4-variate $t_{25}$ & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
+    4-variate $t_{25}$ & SCM  & Tyler & DCM-H & DCM-M & DCM-P & ADCM-H & ADCM-M & ADCM-P \\ \hline
     $n$=20             & 0.89 & 0.92  & 0.92   & 0.92   & 0.90  & 0.96    & 0.95    & 0.89   \\
@@
     $n$=500            & 0.67 & 0.71  & 0.83   & 0.83   & 0.96  & 0.88    & 0.90    & 1.00   \\ \hline
-    4-variate Normal   & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
+    4-variate Normal   & SCM  & Tyler & DCM-H & DCM-M & DCM-P & ADCM-H & ADCM-M & ADCM-P \\ \hline
     $n$=20             & 0.82 & 0.84  & 0.87   & 0.90   & 0.91  & 0.89    & 0.93    & 0.89   \\
@@
     \end{tabular}
-\end{footnotesize}
-\caption{Finite sample efficiencies of several scatter matrices: $p=4$}
+\end{scriptsize}
+\caption{Finite sample efficiencies of several scatter matrices: $p=4$.
+H, M or P after DCM or ADCM indicates the depth function used: H = halfspace depth, M = Mahalanobis depth, P = projection depth.}
 \label{table:FSEtable4}
@@
 \subsection{Robust estimation of eigenvalues, and a plug-in estimator of $\Sigma$}
-
+\label{subsec:plugin}
 As seen in Theorem~\ref{Theorem:covform}, eigenvalues of the DCM are not same as the population eigenvalues, whereas the ADCM only gives back standardized eigenvalues.
@@
 
-{\colrbf (put in 1 or 2 sentences?)}
+%{\colrbf (put in 1 or 2 sentences?)}

### 2018-03-30 MS-new/4_SDR.tex
new draft sent to anshu da

@@
 \section{Robust PCA and supervised models}
-
+\label{section:sdrSection}
 In the presence of a vector of univariate responses, say $\bfy = (y_1,\ldots, y_n)^T$, each $y_i$ being i.i.d.
@@
 %
-\item $\tilde \bfmu = $ spatial median of the rows of $\BX$;
+\item $\tilde \bfmu = $ weighted spatial median of the rows of $\BX$;
 %
-\item $\tilde \bfmu_y = $ spatial median of the rows of $\BX_y$, for each $y \in \cY$;
+\item $\tilde \bfmu_y = $ weighted spatial median of the rows of $\BX_y$, for each $y \in \cY$;
 %

### 2018-03-30 MS-new/7_Appendix.tex
new draft sent to anshu da

@@
 Then the matrices $\BG_D = \sqrt n (\hat\Gamma_D - \Gamma) $ and $\BL_D = \sqrt n (\hat\Lambda_D - \Lambda_{D}) $ have independent distributions.
-The random variable $\ve(G)$ asymptotically has a $p^2$-variate normal distribution with mean ${\bf 0}_{p^2}$, and the asymptotic variance and covariance of different columns of $\BG_D = (\bfg_1,...,\bfg_p)$ are as follows:
+The random variable $\ve(\BG_D)$ asymptotically has a $p^2$-variate normal distribution with mean ${\bf 0}_{p^2}$, and the asymptotic variance and covariance of different columns of $\BG_D = (\bfg_1,...,\bfg_p)$ are as follows:
 %
@@
 
-\newpage
 \section{Proofs}
@@
 
-\noindent\textbf{(C1)}$\text{Tr}(\Sigma^4) = o(\text{Tr}^2(\Sigma^2)) $,
+\noindent\textbf{(C1)}$\Tr(\Sigma^4) = o(\Tr^2(\Sigma^2)) $,
 
-\noindent\textbf{(C2)}$\text{Tr}^4(\Sigma) / \text{Tr}^2(\Sigma^2) \exp[ - \text{Tr}^2(\Sigma) / 128p \lambda^2_{\max}(\Sigma) ] = o(1)$
+\noindent\textbf{(C2)}$\Tr^4(\Sigma) / \Tr^2(\Sigma^2) \exp[ - \Tr^2(\Sigma) / 128p \lambda^2_{\max}(\Sigma) ] = o(1)$
 \vspace{1em}
@@
 \begin{eqnarray}
-E[ (\bfepsilon_{w1}^T \bfepsilon_{w2})^4 ] &=& O(1) E^2[ (\bfepsilon_{w1}^T \bfepsilon_{w2})^2 ]\\
-E[ (\bfepsilon_{w1}^T B_w \bfepsilon_{w1})^2 ] &=& O(1) E^2[ (\bfepsilon_{w1}^T B_w \bfepsilon_{w1})^2 ]\\
-E[ (\bfepsilon_{w1}^T B_w \bfepsilon_{w2})^2 ] &=& o(1) E^2[ (\bfepsilon_{w1}^T B_w \bfepsilon_{w1})^2 ]
+\BE[ (\bfepsilon_{w1}^T \bfepsilon_{w2})^4 ] &=& O(1) \BE^2[ (\bfepsilon_{w1}^T \bfepsilon_{w2})^2 ],\\
+\BE[ (\bfepsilon_{w1}^T B_w \bfepsilon_{w1})^2 ] &=& O(1) \BE^2[ (\bfepsilon_{w1}^T B_w \bfepsilon_{w1})^2 ],\\
+\BE[ (\bfepsilon_{w1}^T B_w \bfepsilon_{w2})^2 ] &=& o(1) \BE^2[ (\bfepsilon_{w1}^T B_w \bfepsilon_{w1})^2 ],
 \end{eqnarray}
 %
-with $\bfepsilon \sim \mathcal E({\bf 0}_p, \Lambda, G)$ and $\bfepsilon_w = w(\bfepsilon) \bfS(\bfepsilon)$.
+with $\bfepsilon \sim \mathcal E({\bf 0}_p, \Lambda, g)$ and $\bfepsilon_w = w(\bfepsilon) \bfS(\bfepsilon)$.
 \end{Lemma}
@@
 \begin{Lemma}
-Given that condition (C3) holds, we have $\lambda_{\max} (B_w) \leq 2 \frac{\lambda_{\max}}{\text{Tr} (\Sigma)} (1+o(1))$.
+Given that condition (C3) holds, we have $\lambda_{\max} (\BB_w) \leq 2 \frac{\lambda_{\max}}{\text{Tr} (\Sigma)} (1+o(1))$.
 \end{Lemma}
@@
 \begin{Lemma}
-Define $D_w = E \left[ \frac{w^2(\bfepsilon)}{\| \bfepsilon \|^2} (I_p - \bfS(\bfepsilon) \bfS(\bfepsilon)^T )\right] $.
-Then $\lambda_{\max} (A_w) \leq E( w(\bfepsilon)/\| \bfepsilon \|)$ and $\lambda_{\max} (D_w) \leq E( w(\bfepsilon)/\| \bfepsilon \|)^2$.
-Further, if (C3) and (C4) hold then $\lambda_{\min} (A_w) \geq E( w(\bfepsilon)/\| \bfepsilon \|)(1+o(1))/\sqrt 3$.
+Define $\BD_w = \BE \left[ \frac{w^2(\bfepsilon)}{\| \bfepsilon \|^2} (\BI_p - \bfS(\bfepsilon) \bfS(\bfepsilon)^T )\right] $.
+Then $\lambda_{\max} (\BA_w) \leq \BE( w(\bfepsilon)/\| \bfepsilon \|)$ and $\lambda_{\max} (\BD_w) \leq \BE( w(\bfepsilon)/\| \bfepsilon \|)^2$.
+Further, if (C3) and (C4) hold then $\lambda_{\min} (\BA_w) \geq \BE( w(\bfepsilon)/\| \bfepsilon \|)(1+o(1))/\sqrt 3$.
 \end{Lemma}
@@
 \begin{eqnarray*}
-Cov(\tilde\bfX) &=& E(\tilde\bfX \tilde\bfX^T) - E(\tilde\bfX) E(\tilde\bfX)^T\\
-&=& \Gamma . E \left[ (D^-_\bfZ(\bfz))^2 \frac{\|\bfz\|^2}{\| \Lambda^{1/2}\bfz\|} \Lambda^{1/2} \bfS(\bfz) \bfS(\bfz)^T \Lambda^{1/2} \right] \Gamma^T - {\bf 0}_p {\bf 0}_p^T\\
-&=& \Gamma .E \left[ (D^-_\bfZ(\bfz))^2 \frac{\Lambda^{1/2} \bfz \bfz^T \Lambda^{1/2}}{\bfz^T \Lambda \bfz} \right] \Gamma^T
+\BV \tilde\bfX &=& \BE (\tilde\bfX \tilde\bfX^T) - \BE \tilde\bfX \BE \tilde\bfX^T\\
+&=& \Gamma . \BE \left[ (D^-_\bfZ(\bfz))^2 \frac{\|\bfz\|^2}{\| \Lambda^{1/2}\bfz\|} \Lambda^{1/2} \bfS(\bfz) \bfS(\bfz)^T \Lambda^{1/2} \right] \Gamma^T - {\bf 0}_p {\bf 0}_p^T\\
+&=& \Gamma . \BE \left[ (D^-_\bfZ(\bfz))^2 \frac{\Lambda^{1/2} \bfz \bfz^T \Lambda^{1/2}}{\bfz^T \Lambda \bfz} \right] \Gamma^T
 \end{eqnarray*}
@@
 \begin{proof}[Proof of Lemma \ref{Lemma:lemma1}]
-For two positive definite matrices $A,B$, we denote by $A>B$ that $A-B$ is positive definite. Also, denote
+For two positive definite matrices $\BA, \BB$, we denote by $ \BA > \BB$ that $\BA-\BB$ is positive definite. Also, denote
 %
-$$ S_n = \sqrt n \left[ \frac{1}{n} \sum_{i=1}^n \left| (\tilde D^{n} _\bfX (\bfx_i))^2  - (D^-_\bfX (\bfx_i))^2 \right| SS(\bfx_i; \hat\bfmu_n) \right] $$
+$$
+\BS_n = \sqrt n \left[ \frac{1}{n} \sum_{i=1}^n \left| ( D^{n-} _\bfX (\bfx_i))^2  - (D^-_\bfX (\bfx_i))^2 \right| \BS( \bfx_i; \hat\bfmu_n) \right].
+$$
 %
@@
 %with $\hat S_n = \sum_{i=1}^n SS(\bfx_i, \hat\bfmu_n)/ \sqrt n$.
-Now due to the assumption of uniform convergence, given $\epsilon>0$ we can find $N \in \mathbb{N}$ such that
+Due to assumption (D1), given $\epsilon>0$ we can find $N \in \mathbb{N}$ such that
 %
@@
 \label{equation:lemma1eq}
-| (\tilde D^{n_1}_\bfX(\bfx_i))^2 - (D^-_\bfX(\bfx_i))^2 | < \epsilon
+| (D^{n_1 -}_\bfX(\bfx_i))^2 - (D^-_\bfX(\bfx_i))^2 | < \epsilon
 \end{equation}
@@
 \begin{eqnarray}
-\label{eqn:lemma1eq2}
-S_{n_1} &< & \epsilon \sqrt{n_1} \left[ \frac{1}{n_1} \sum_{i=1}^{n_1} SS(\bfx_i; \hat\bfmu_{n_1}) \right]\notag\\
-&=& \epsilon \sqrt{n_1} \left[ \frac{1}{n_1} \sum_{i=1}^{n_1} \left\{ SS(\bfx_i; \hat\bfmu_{n_1}) - SS(\bfx_i; \bfmu) \right\} + \frac{1}{n_1} \sum_{i=1}^{n_1} SS(\bfx_i; \bfmu) \right]
+\BS_{n_1} &< & \epsilon \sqrt{n_1} \left[ \frac{1}{n_1} \sum_{i=1}^{n_1} \BS( \bfx_i; \hat\bfmu_{n_1}) \right]\notag\\
+&=& \epsilon \sqrt{n_1} \left[ \frac{1}{n_1} \sum_{i=1}^{n_1} \left\{ \BS( \bfx_i; \hat\bfmu_{n_1}) - \BS( \bfx_i; \bfmu) \right\} + \frac{1}{n_1} \sum_{i=1}^{n_1} \BS( \bfx_i; \bfmu) \right]\label{eqn:lemma1eq2}
 \end{eqnarray}
 
-We now construct a sequence of positive definite matrices $\{A_k (B_k+C_k) : k \in \mathbb N\} $ so that
+We now construct a sequence of positive definite matrices $\{a_k (B_k+C_k) : k \in \mathbb N\} $ so that
 %
-$$ A_k = \frac{1}{k}, \quad B_k = \sqrt{N_k} \left[ \frac{1}{N_k} \sum_{i=1}^{N_k} \left\{ SS(\bfx_i; \hat\bfmu_{N_k}) - SS(\bfx_i; \bfmu) \right\} \right]$$
-$$\quad C_k = \sqrt{N_k} \left[ \frac{1}{N_k} \sum_{i=1}^{N_k} SS(\bfx_i; \bfmu) \right] $$
+$$
+a_k = \frac{1}{k}, \quad \BB_k = \sqrt{N_k} \left[ \frac{1}{N_k} \sum_{i=1}^{N_k} \left\{ \BS( \bfx_i; \hat\bfmu_{N_k}) - \BS(\bfx_i; \bfmu) \right\} \right],
+\quad \BC_k = \sqrt{N_k} \left[ \frac{1}{N_k} \sum_{i=1}^{N_k} \BS(\bfx_i; \bfmu) \right]
+$$
 %
 where $N_k \in \mathbb N$ gives the relation (\ref{equation:lemma1eq}) in place of $N$ when we take $\epsilon = 1/k$.
-Under conditions $ E\|\bfx - \bfmu\|^{-3/2} < \infty $ and $\sqrt n (\hat\bfmu_n - \bfmu) = O_P(1)$, the sample SCM with unknown location parameter $\hat\bfmu_n$ has the same asymptotic distribution as the SCM with known location $\bfmu$ \citep{durre14}, hence $B_k = o_P(1)$, thus $A_k (B_k+C_k) \stackrel{P}{\rightarrow} 0$.
+Under conditions $ \BE \|\bfx - \bfmu\|^{-3/2} < \infty $ and $\sqrt n (\hat\bfmu_n - \bfmu) = O_P(1)$, the sample SCM with unknown location parameter $\hat\bfmu_n$ has the same asymptotic distribution as the SCM with known location $\bfmu$ \citep{durre14}, hence $\BB_k = o_P(1)$, thus $a_k (\BB_k + \BC_k) \stackrel{P}{\rightarrow} 0$.
 
-Now (\ref{eqn:lemma1eq2}) implies that for any $\epsilon_1 > 0$, $S_{N_k} > \epsilon_1 \Rightarrow A_k (B_k + C_k) > \epsilon_1$, which means $ P(S_{N_k} > \epsilon_1) < P(A_k (B_k + C_k) > \epsilon_1)$.
-Hence the subsequence $\{S_{N_k}\} \stackrel{P}{\rightarrow} 0$.
-Since the main sequence $\{S_k\}$ is bounded below by 0, this implies $\{S_k\} \stackrel{P}{\rightarrow} 0$.
+Now \eqref{eqn:lemma1eq2} implies that for any $\epsilon_1 > 0$, $\BS_{N_k} > \epsilon_1 \Rightarrow a_k (\BB_k + \BC_k) > \epsilon_1$, which means $ P(\BS_{N_k} > \epsilon_1) < P(a_k (\BB_k + \BC_k) > \epsilon_1)$.
+Hence the subsequence $\{\BS_{N_k}\} \stackrel{P}{\rightarrow} 0$.
+Since the main sequence $\{\BS_k\}$ is bounded below by 0, this implies $\{\BS_k\} \stackrel{P}{\rightarrow} 0$.
 Finally, we have that
@@
 \sqrt n \left[
-\frac{1}{n} \sum_{i=1}^n (\tilde D^n_\bfX (\bfx_i))^2 SS(\bfx_i; \hat\bfmu_n) -
-\frac{1}{n} \sum_{i=1}^n (D^-_\bfX (\bfx_i))^2 SS(\bfx_i; \bfmu) \right] &\leq & \hspace{1em} \notag\\
-S_n +  \sqrt{n} \left[ \frac{1}{n} \sum_{i=1}^{n} \left\{ SS(\bfx_i; \hat\bfmu_{n}) - SS(\bfx_i; \bfmu) \right\} \right] &&
+\frac{1}{n} \sum_{i=1}^n ( D^{n-}_\bfX (\bfx_i))^2 \BS(\bfx_i; \hat\bfmu_n) -
+\frac{1}{n} \sum_{i=1}^n (D^-_\bfX (\bfx_i))^2 \BS(\bfx_i; \bfmu) \right] &\leq & \hspace{1em} \notag\\
+\BS_n +  \sqrt{n} \left[ \frac{1}{n} \sum_{i=1}^{n} \left\{ \BS(\bfx_i; \hat\bfmu_{n}) - \BS(\bfx_i; \bfmu) \right\} \right] &&
 \end{eqnarray}
@@
 \begin{eqnarray*}
-\sqrt n \left[ vec\left\{ \frac{1}{n} \sum_{i=1}^n (\tilde D^n_\bfX (\bfx_i))^2 SS(\bfx_i; \hat\bfmu_n) \right\} - vec\left\{ \frac{1}{n} \sum_{i=1}^n (D^-_\bfX (\bfx_i))^2 SS(\bfx_i; \bfmu) \right\} \right] +\\
-\sqrt n \left[ vec\left\{ \frac{1}{n} \sum_{i=1}^n (D^-_\bfX (\bfx_i))^2 SS(\bfx_i; \bfmu) \right\} - E \left[ vec\left\{ (D^-_\bfX (\bfx))^2 SS(\bfx; \bfmu) \right\} \right] \right]
+\sqrt n \left[ \ve \left\{ \frac{1}{n} \sum_{i=1}^n ( D^{n-}_\bfX (\bfx_i))^2 \BS(\bfx_i; \hat\bfmu_n) \right\} - \ve \left\{ \frac{1}{n} \sum_{i=1}^n (D^-_\bfX (\bfx_i))^2 \BS( \bfx_i; \bfmu) \right\} \right] +\\
+\sqrt n \left[ \ve \left\{ \frac{1}{n} \sum_{i=1}^n (D^-_\bfX (\bfx_i))^2 \BS( \bfx_i; \bfmu) \right\} - \BE \left[ \ve \left\{ (D^-_\bfX (\bfx))^2 \BS( \bfx; \bfmu) \right\} \right] \right]
 \end{eqnarray*}
@@
 
-\item $\| \hat\Lambda - \Lambda \|_F \stackrel{P}{\rightarrow} 0$
+\item $\| \hat\Lambda - \Lambda \|_F \stackrel{P}{\rightarrow} 0$,
 \end{enumerate}
@@
 as $n \rightarrow \infty$.
-For (1), we notice $\sqrt n vec(\hat\Gamma_D - \Gamma)$ asymptotically has a (singular) multivariate normal distribution following Corollary \ref{Corollary:eigendist}, so that $\| \hat\Gamma_D - \Gamma \|_F = O_P(1/\sqrt n)$ using Prokhorov's theorem.
+For (1), we notice $\sqrt n \ve ( \hat\Gamma_D - \Gamma)$ asymptotically has a (singular) multivariate normal distribution following Corollary \ref{Corollary:eigendist}, so that $\| \hat\Gamma_D - \Gamma \|_F = O_P(1/\sqrt n)$ using Prokhorov's theorem.
 
 It is now enough to prove convergence in probability of the individual eigenvalue estimates $\hat\lambda_i; i = 1,...,p$.
-For this, define estimates $\tilde\lambda_i$ as median-of-small-variances estimator of the \textit{true} score vectors $\Gamma^T X$.
+For this, define estimates $\tilde\lambda_i$ as median-of-small-variances estimator of the \textit{true} score vectors $\Gamma^T \bfX$.
 For this we have
@@
 using Theorem 3.1 of \cite{Minsker15}, with $\mu = \lambda_i$.
-Now $ \hat\lambda_i = \text{med}_j (Var( X_{G_j}^T \hat\bfgamma_{D,i} ))$ and $\tilde\lambda_i = \text{med}_j (Var( X_{G_j}^T \bfgamma_i )) $, so that
+Now $ \hat\lambda_i = \text{median}_j ( \BS ( \BX_{G_j} \hat\bfgamma_{D,i} ))$ and $\tilde\lambda_i = \text{median}_j ( \BS( \BX_{G_j} \bfgamma_i )) $, so that
 %
 \begin{eqnarray*}
-| \hat\lambda_i - \tilde\lambda_i | &\leq & \text{med}_j \left[ Var( X_{G_j}^T ( \hat\bfgamma_{D,i} - \bfgamma_i) ) \right]
-\\ &\leq & \| \hat\bfgamma_{D,i} - \bfgamma_i \|^2 \text{med}_j  \left[ \text{Tr} (Cov ( X_{G_j})) \right]
+| \hat\lambda_i - \tilde\lambda_i | &\leq & \text{median}_j \left[ \BS( \BX_{G_j} ( \hat\bfgamma_{D,i} - \bfgamma_i) ) \right]
+\\ &\leq & \| \hat\bfgamma_{D,i} - \bfgamma_i \|^2 \text{median}_j  \left[ \text{Tr} ( \BS( \BX_{G_j}) ) \right]
 \end{eqnarray*}
@@
 using Cauchy-Schwarz inequality.
-Combining the facts $ \| \hat\bfgamma_{D,i} - \bfgamma_i \| = O_P(1/\sqrt n)$ and $ \text{med}_j  [ \text{Tr} (Cov ( X_{G_j})) ] \stackrel{P}{\rightarrow} \text{Tr}(\Sigma)$ \citep{Minsker15} with (\ref{eqn:PluginSigmaProof1}), we get the needed.
+Combining the facts $ \| \hat\bfgamma_{D,i} - \bfgamma_i \| = O_P(1/\sqrt n)$ and $ \text{median}_j  [ \text{Tr} (\BS ( X_{G_j})) ] \stackrel{P}{\rightarrow} \text{Tr}(\Sigma)$ \citep{Minsker15} with (\ref{eqn:PluginSigmaProof1}), we get the needed.
 
@@
 In spirit, this corollary is similar to Theorem 13.5.1 in \cite{anderson}.
-Due to the decomposition (\ref{equation:decompEq}) we have, for the distribution $F_\Lambda$, the following relation between any off-diagonal element of $\hat S^D(F_\Lambda)$ and the corresponding element in the estimate of eigenvectors $\hat\Gamma_D (F_\Lambda)$:
+Due to the decomposition (\ref{equation:decompEq}) we have, for the distribution $F_\Lambda$, the following relation between any off-diagonal element of $\tilde \BS (\BF_\Lambda)$ and the corresponding element in the estimate of eigenvectors $\hat\Gamma_D (\BF_\Lambda)$:
 
-$$ \sqrt n \hat\gamma_{D,ij} (F_\Lambda) = \sqrt n \frac{\hat S^D_{ij} (F_\Lambda)}{\lambda_{D,S,i} - \lambda_{D,S,j}}; \quad i \neq j$$
+$$ \sqrt n \hat\gamma_{D,ij} (\BF_\Lambda) = \sqrt n \frac{\tilde \BS_{ij} (\BF_\Lambda)}{\lambda_{D,i} - \lambda_{D,j}}; \quad i \neq j$$
 
 So that for eigenvector estimates of the original $F$ we have
+%
+\begin{align}
+\sqrt n (\hat\bfgamma_{D,i} - \bfgamma_i) &= \sqrt n \Gamma (\hat \bfgamma_{D,i}(\BF_\Lambda) - \bfe_i )\notag\\
+&= \sqrt n \left[ \sum_{k=1; k \neq i}^p \hat \gamma_{D,ik}(\BF_\Lambda )\bfgamma_k + (\hat \gamma_{D,ii}(\BF_\Lambda) - 1)\bfgamma_i \right].\label{equation:app1}
+\end{align}
 
-\begin{equation} \label{equation:app1}
-\sqrt n (\hat\bfgamma_{D,i} - \bfgamma_i) = \sqrt n \Gamma (\hat \bfgamma_{D,i}(F_\Lambda) - \bfe_i ) = \sqrt n \left[ \sum_{k=1; k \neq i}^p \hat \gamma_{D,ik}(F_\Lambda)\bfgamma_k + (\hat \gamma_{D,ii}(F_\Lambda) - 1)\bfgamma_i \right]
-\end{equation}
-
-$\sqrt n (\hat \gamma_{D,ii}(F_\Lambda) - 1) =  o_P(1)$ and $ACov(\sqrt n \hat S^D_{ik}(F_\Lambda), \sqrt n \hat S^D_{il}(F_\Lambda)) = 0$ for $k \neq l$, so the above equation implies
-
-$$ A\BV(\bfg_i) = AVar (\sqrt n (\hat\bfgamma_{D,i} - \bfgamma_i)) = \sum_{k=1; k \neq i}^p \frac{A\BV(\sqrt n \hat S^D_{ik}(F_\Lambda))}{(\lambda_{D,s,i} - \lambda_{D,S,k})^2} \bfgamma_k \bfgamma_k^T $$
+By assumption we now have $\sqrt n (\hat \gamma_{D,ii}(\BF_\Lambda) - 1) =  o_P(1)$ and $A\BV( \sqrt n \tilde \BS_{ik}(\BF_\Lambda), \sqrt n \tilde \BS_{il}(\BF_\Lambda)) = 0$ for $k \neq l$, so the above equation implies
+%
+$$
+A\BV(\bfg_i) = A\BV (\sqrt n (\hat\bfgamma_{D,i} - \bfgamma_i)) =
+\sum_{k=1; k \neq i}^p \frac{A\BV(\sqrt n \tilde \BS_{ik}(\BF_\Lambda))}{(\lambda_{D,i} - \lambda_{D,k})^2} \bfgamma_k \bfgamma_k^T
+$$
 
 For the covariance terms, from (\ref{equation:app1}) we get, for $i \neq j$,
-
+%
 \begin{eqnarray*}
-ACov(\bfg_i, \bfg_j) &=& ACov (\sqrt n (\hat\bfgamma_{D,i} - \bfgamma_i), \sqrt n (\hat\bfgamma_{D,j} - \bfgamma_j))\\
-&=& ACov \left( \sum_{k=1; k \neq i}^p \sqrt n \hat \gamma_{D,ik}(F_\Lambda)\bfgamma_k, \sum_{k=1; k \neq j}^p \sqrt n \hat \gamma_{D,jk}(F_\Lambda)\bfgamma_k \right)\\
-&=& ACov \left( \sqrt n \hat \gamma_{D,ij}(F_\Lambda)\bfgamma_j, \sqrt n \hat \gamma_{D,ji}(F_\Lambda)\bfgamma_i \right)\\
-&=& - \frac{A\BV(\sqrt n \hat S^D_{ij}(\Lambda))}{(\lambda_{D,s,i} - \lambda_{D,S,j})^2} \bfgamma_j \bfgamma_i^T
+A\BV( \bfg_i, \bfg_j) &=& A\BV (\sqrt n (\hat\bfgamma_{D,i} - \bfgamma_i), \sqrt n (\hat\bfgamma_{D,j} - \bfgamma_j))\\
+&=& A\BV \left( \sum_{k=1; k \neq i}^p \sqrt n \hat \gamma_{D,ik}(\BF_\Lambda)\bfgamma_k, \sum_{k=1; k \neq j}^p \sqrt n \hat \gamma_{D,jk}(\BF_\Lambda)\bfgamma_k \right)\\
+&=& A\BV \left( \sqrt n \hat \gamma_{D,ij}(\BF_\Lambda)\bfgamma_j, \sqrt n \hat \gamma_{D,ji}(\BF_\Lambda)\bfgamma_i \right)\\
+&=& - \frac{A\BV( \sqrt n \tilde \BS_{ij}(\BF_\Lambda))}{(\lambda_{D,i} - \lambda_{D,j})^2} \bfgamma_j \bfgamma_i^T.
 \end{eqnarray*}
 
-The exact forms given in the statement of the corollary now follows from the  Form of $\BV_D$ in Appendix \ref{section:appA}.
+The exact forms given in the statement of the corollary now follows from the  Form of $\BV_D (\BF)$ in Appendix \ref{section:appA}.
 
-\paragraph{}For the on-diagonal elements of $\hat S^D(F_\Lambda)$ Theorem \ref{Theorem:decomp} gives us $ \sqrt n \hat\lambda_{D,s,i} (F_\Lambda) = \sqrt n \hat S^D_{ii}(F_\Lambda)$ for $i = 1,...,p$.
+\paragraph{}For the on-diagonal elements of $\tilde \BS(\BF_\Lambda)$, Theorem \ref{Theorem:decomp} gives us $ \sqrt n \hat\lambda_{D,i} ( \BF_\Lambda) = \sqrt n \tilde \BS_{ii}(\BF_\Lambda)$ for $i = 1,...,p$.
 Hence
-
+%
 \begin{eqnarray*}
-A\BV(l_i) &=& A\BV(\sqrt n \hat\lambda_{D,s,i} - \sqrt n \lambda_{D,S,i})\\
-&=& A\BV(\sqrt n \hat\lambda_{D,s,i} (F_\Lambda) - \sqrt n \lambda_{D,S,i}(F_\Lambda))\\
-&=& A\BV(\sqrt n S^D_{ii}(F_\Lambda))
+A\BV(l_i) &=& A\BV(\sqrt n \hat\lambda_{D,i} - \sqrt n \lambda_{D,i})\\
+&=& A\BV(\sqrt n \hat\lambda_{D,i} (\BF_\Lambda) - \sqrt n \lambda_{D,i}(\BF_\Lambda))\\
+&=& A\BV(\sqrt n \BS_{ii}(\BF_\Lambda)).
 \end{eqnarray*}
@@
 A similar derivation gives the expression for $A\BV(l_i,l_j); i \neq j$.
-Finally, since the asymptotic covariance between an on-diagonal and an off-diagonal element of $\hat S^D(F_\Lambda)$, it follows that the elements of $G$ and diagonal elements of $L$ are independent.
+Finally, since the asymptotic covariance between an on-diagonal and an off-diagonal element of $\tilde \BS( \BF_\Lambda)$, it follows that the elements of $\BG_D$ and diagonal elements of $\BL_D$ are independent.
 \end{proof}
 
+\section{Additional simulations}
+\label{sec:appD}
+Here we give tables of finite sample efficiencies of DCM and ADCMs for $p=2,3$.
+
 \begin{table}[t]
-\begin{footnotesize}
+\begin{scriptsize}
     \begin{tabular}{c|cc|ccc|ccc}
     \hline
-    $F$ = Bivariate $t_5$    & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
+    $F$ = Bivariate $t_5$    & SCM  & Tyler & DCM-H & DCM-M & DCM-P & ADCM-H & ADCM-M & ADCM-P \\ \hline
     $n$=20                   & 0.80 & 0.83  & 0.95   & 0.95   & 0.89  & 1.00    & 0.96    & 0.89   \\
@@
     $n$=500                  & 1.25 & 1.29  & 1.80   & 1.33   & 1.84  & 1.91    & 1.39    & 1.97   \\ \hline
-    $F$ = Bivariate $t_6$    & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
+    $F$ = Bivariate $t_6$    & SCM  & Tyler & DCM-H & DCM-M & DCM-P & ADCM-H & ADCM-M & ADCM-P \\ \hline
     $n$=20                   & 0.77 & 0.79  & 0.92   & 0.92   & 0.86  & 0.96    & 0.92    & 0.85   \\
@@
     $n$=500                  & 0.93 & 0.96  & 1.37   & 1.13   & 1.40  & 1.44    & 1.19    & 1.48   \\ \hline
-    $F$ = Bivariate $t_{10}$ & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
+    $F$ = Bivariate $t_{10}$ & SCM  & Tyler & DCM-H & DCM-M & DCM-P & ADCM-H & ADCM-M & ADCM-P \\ \hline
     $n$=20                   & 0.70 & 0.72  & 0.83   & 0.84   & 0.77  & 0.89    & 0.87    & 0.79   \\
@@
     $n$=500                  & 0.62 & 0.65  & 0.93   & 0.86   & 1.00  & 1.00    & 0.92    & 1.08   \\ \hline
-    $F$ = Bivariate $t_{15}$ & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
+    $F$ = Bivariate $t_{15}$ & SCM  & Tyler & DCM-H & DCM-M & DCM-P & ADCM-H & ADCM-M & ADCM-P \\ \hline
     $n$=20                   & 0.63 & 0.66  & 0.76   & 0.78   & 0.72  & 0.81    & 0.81    & 0.73   \\
@@
     $n$=500                  & 0.56 & 0.59  & 0.85   & 0.80   & 0.93  & 0.91    & 0.86    & 0.99   \\ \hline
-    $F$ = Bivariate $t_{25}$ & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
+    $F$ = Bivariate $t_{25}$ & SCM  & Tyler & DCM-H & DCM-M & DCM-P & ADCM-H & ADCM-M & ADCM-P \\ \hline
     $n$=20                   & 0.63 & 0.65  & 0.77   & 0.79   & 0.74  & 0.80    & 0.81    & 0.74   \\
@@
     $n$=500                  & 0.53 & 0.55  & 0.79   & 0.75   & 0.87  & 0.84    & 0.80    & 0.94   \\ \hline
-    $F$ = BVN                & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
+    $F$ = BVN                & SCM  & Tyler & DCM-H & DCM-M & DCM-P & ADCM-H & ADCM-M & ADCM-P \\ \hline
     $n$=20                   & 0.56 & 0.60  & 0.69   & 0.71   & 0.67  & 0.73    & 0.74    & 0.68   \\
@@
     \end{tabular}
-\end{footnotesize}
+\end{scriptsize}
 \caption{Finite sample efficiencies of several scatter matrices: $p=2$}
@@
 \begin{table}[t]
-\begin{footnotesize}
+\begin{scriptsize}
    \begin{tabular}{c|cc|ccc|ccc}
     \hline
-    3-variate $t_5$    & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
+    3-variate $t_5$    & SCM  & Tyler & DCM-H & DCM-M & DCM-P & ADCM-H & ADCM-M & ADCM-P \\ \hline
     $n$=20             & 0.96 & 0.97  & 1.06   & 1.03   & 0.99  & 1.07    & 1.06    & 0.97   \\
@@
     $n$=500            & 1.60 & 1.66  & 2.18   & 1.87   & 2.21  & 2.27    & 1.95    & 2.30   \\ \hline
-    3-variate $t_6$    & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
+    3-variate $t_6$    & SCM  & Tyler & DCM-H & DCM-M & DCM-P & ADCM-H & ADCM-M & ADCM-P \\ \hline
     $n$=20             & 0.90 & 0.92  & 1.00   & 0.99   & 0.95  & 1.02    & 1.01    & 0.94   \\
@@
     $n$=500            & 1.17 & 1.20  & 1.57   & 1.43   & 1.60  & 1.63    & 1.51    & 1.67   \\ \hline
-    3-variate $t_{10}$ & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
+    3-variate $t_{10}$ & SCM  & Tyler & DCM-H & DCM-M & DCM-P & ADCM-H & ADCM-M & ADCM-P \\ \hline
     $n$=20             & 0.87 & 0.88  & 0.95   & 0.94   & 0.90  & 0.97    & 0.98    & 0.89   \\
@@
     $n$=500            & 0.73 & 0.76  & 1.02   & 0.98   & 1.09  & 1.06    & 1.02    & 1.14   \\ \hline
-    3-variate $t_{15}$ & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
+    3-variate $t_{15}$ & SCM  & Tyler & DCM-H & DCM-M & DCM-P & ADCM-H & ADCM-M & ADCM-P \\ \hline
     $n$=20             & 0.84 & 0.86  & 0.92   & 0.92   & 0.89  & 0.94    & 0.94    & 0.87   \\
@@
     $n$=500            & 0.65 & 0.67  & 0.89   & 0.87   & 0.99  & 0.93    & 0.91    & 1.03   \\ \hline
-    3-variate $t_{25}$ & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
+    3-variate $t_{25}$ & SCM  & Tyler & DCM-H & DCM-M & DCM-P & ADCM-H & ADCM-M & ADCM-P \\ \hline
     $n$=20             & 0.78 & 0.79  & 0.87   & 0.89   & 0.87  & 0.89    & 0.92    & 0.86   \\
@@
     $n$=500            & 0.62 & 0.64  & 0.83   & 0.82   & 0.94  & 0.88    & 0.87    & 0.99   \\ \hline
-    3-variate Normal   & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
+    3-variate Normal   & SCM  & Tyler & DCM-H & DCM-M & DCM-P & ADCM-H & ADCM-M & ADCM-P \\ \hline
     $n$=20             & 0.76 & 0.78  & 0.85   & 0.87   & 0.84  & 0.87    & 0.90    & 0.83   \\
@@
     \end{tabular}
-\end{footnotesize}
+\end{scriptsize}
 \caption{Finite sample efficiencies of several scatter matrices: $p=3$}

### 2018-03-30 MS-new/Signed-peripherality-draft.tex
main paper v1 done, proofs and intro remain
new draft sent to anshu da

@@
 Abstract:
-{(\colrbf will change)}Analyzing principal components for multivariate data from its spatial sign covariance matrix (SCM) has been proposed as a computationally simple and robust alternative to normal PCA, but it suffers from poor efficiency properties and is actually inadmissible with respect to the maximum likelihood estimator.
-Here we use data depth-based spatial ranks in place of spatial signs to obtain the orthogonally equivariant Depth Covariance Matrix (DCM) and use its eigenvector estimates for PCA.
-We derive asymptotic properties of the sample DCM and influence functions of its eigenvectors.
-The shapes of these influence functions indicate robustness of estimated principal components, and good efficiency properties compared to the SCM.
-Finite sample simulation studies show that principal components of the sample DCM are robust with respect to deviations from normality, as well as are more efficient than the SCM and its affine equivariant version, Tyler's shape matrix.
-Through two real data examples, we also show the effectiveness of DCM-based PCA in analyzing high-dimensional data and outlier detection, and compare it with other methods of robust PCA.
+We introduce a notion of multivariate ranking based on the composition of the multivariate sign function and data-dependent weights that are increasing or decreasing functions of a point-to-distribution distance measure in multivariate space, which we call the peripherality function.
+Using this weighted sign vector, we propose estimation and testing methods for the mean vector of an elliptical distribution that improve upon corresponding spatial sign-based procedures.
+When bounded and monotonically decreasing transformations on data depth functions are used as weights, the rank vectors can be used as proxies of the original data to estimate different components of the covariance matrix in the data-generating elliptical distribution: its eigenvectors, eigenvalues and the covariance matrix itself.
+Wimplement our proposed methods to perform robust Sufficient Dimension Reduction \citep{AdragniCook09} and functional outlier detection.
+Throughout the paper, several simulation studies and data examples outline the robustness and efficiency of our methods.
 \vspace{.5cm}
@@
 Keywords:
-Multivariate ranking, data depth, dimension reduction, principal components analysis, robust statistics, functional data
+Multivariate ranking, data depth, high-dimensional location testing, principal component analysis, sufficient dimension reduction, robust PCA, outlier detection
 
@@
 
-\newpage
 \input{7_Appendix}
 
-\newpage
-\input{misc}
+%\newpage
+%\input{misc}
 

### 2018-03-30 Codes/Sim_influenceplot.R

@@ -1,6 +1,6 @@
 ## Sim_influenceplot: Plots to compare influence functions for DCM and SCM
 
-setwd("C:/Study/My projects/Depth-scatter/Codes")
+setwd("d:/Study/My projects/Depth-scatter1/Codes")
 rm(list=ls());
 source('misc_functions.R')
 
@@ -72,12 +72,16 @@ points(Xrank[1001:1003,], col='red', pch=19, cex=1)
 par(mfrow=c(1,1))
 dev.off()
 
+pdf('signs_and_ranks.pdf', width=8, height=3)
 par(mfrow=c(1,3))
-plot(X, pch=19, cex=.5)
-plot(uX, pch=19, cex=.5)
-plot(Xrank, pch=19, cex=.5)
+plot(X[1:1000,], pch=19, cex=.5)
+points(X[1001:1003,], col='red', pch=19, cex=1)
+plot(uX[1:1000,], pch=19, cex=.5)
+points(uX[1001:1003,], col='red', pch=19, cex=1)
+plot(Xrank[1:1000,], pch=19, cex=.5)
+points(Xrank[1001:1003,], col='red', pch=19, cex=1)
 par(mfrow=c(1,1))
-
+dev.off()
 
 ## Influence function plots
 lam = c(2,1)

### 2018-04-01 MS-new/3_Scale.tex
.

@@
 Given a depth function, the peripherality functions in this section can be defined as a bounded monotonically decreasing function of it.
-Consequently, we use the term {\it inverse depth function} in place of peripherality functions in this section, denoting them by $D^-(\bfx,\BF)$, or equivalently $D^-_\bfX(\bfx)$.
+Consequently, we use the term {\it inverse depth function} \citep{MajumdarChatterjeeStat} in place of peripherality functions in this section, denoting them by $D^-(\bfx,\BF)$, or equivalently $D^-_\bfX(\bfx)$.
+For ease of exposition, we stick to the following inverse transformation: $D^-_\bfX(\bfx) = \sup_\bfy D^-_\bfX(\bfy) - D^-_\bfX(\bfx)$ from now on.
+The theoretical results go through with minor changes for other choices of inverse depths.
 
-Given an inverse depth function $D^-_{\bfX}(\bfx)$ we transform the original random variable as: $\tilde \bfX = D^-_\bfX(\bfx) \bfS(\bfx - \bfmu)$.
-We use the transformed data matrix $\tilde \BX = (\tilde \bfx_1, \ldots, \tilde \bfx_n)^T$ as proxy of the original data matrix $\BX$ for improved estimation of the components of the population covariance matrix $\Sigma$ in this section.
+Given a choice of inverse depth function $D^-_{\bfX}(\bfx)$, we transform the original random variable as: $\tilde \bfX = D^-_\bfX(\bfx) \bfS(\bfx - \bfmu)$.
+We use the transformed data matrix $\tilde \BX = (\tilde \bfx_1, \ldots, \tilde \bfx_n)^T$ as proxy of the original data $\BX$ for improved estimation of the components of the population covariance matrix $\Sigma$ in this section.
 To this end, in Section~\ref{subsec:dcm} we give some results characterizing the population covariance matrix of these vectors, i.e.
 $\BV \tilde \bfX$, and its affine equivariant counterpart.
-Section~\ref{subsec:dcm} gives asymptotic properties of their finite sample versions.
+Section~\ref{subsec:sample-DCM} gives asymptotic properties of their finite sample versions.
 In Section~\ref{subsec:robustPCA}, we use eigenvectors of these estimates for robust PCA, deriving their influence functions, as well as asymptotic and finite sample efficiencies.
@@
 \begin{enumerate}
-\item Start from some initial estimates $(\bfmu_{Dw}^{(0)}, \Sigma_{Dw}^{(0)}$. Set $t=0$;
+\item Start from some initial estimates $(\bfmu_{Dw}^{(0)}, \Sigma_{Dw}^{(0)})$. Set $t=0$;
 
@@
 $$
-\bfmu_{Dw}^{(t+1)} = \frac{\sum_{i=1}^n \tilde \bfx_i / \| \bfz_i^{(t)} \| }{\sum_{i=1}^n 1 / \| \bfz_i^{(t)} \|};
+\bfmu_{Dw}^{(t+1)} = \frac{\sum_{i=1}^n \tilde \bfx_i / \| \bfz_i^{(t)} \| }{\sum_{i=1}^n \| \bfz_i^{(t)} \|^{-1} };
 $$

### 2019-08-09 EJSSubmission/WeightedSIgn_EJS_DA_02_24_19_1.tex
EJS revision

\section{Real Data Applications}
\label{Sec:DA}

We  now present an application of our proposed approach to some real data problems.

Robust techniques are useful when in identifying outlying observations, and we illustrate 
below how to make use of our fixed-dimensional methods presented earlier for 
functional (and hence infinite-dimensional)  data.

We follow the approach of \cite{ref:JASA151100_BoenteSalibianBarrera} 
for performing robust principal component 
analysis on functional data using the estimated eigenvectors from 
$\widehat{\tilde{\Sigma}}$. Suppose the data consistents of  $n$ curves, say 
$ \cF = \{ f_1, \ldots , f_n  \} \in L^2[0,1]$, each observed at a set of common design 
points $\{ t_1, ..., t_m \} $. We model each of these functions as a linear combination of 
$p$ mutually orthogonal B-spline basis functions $\cD = \{ \delta_1, ..., \delta_p \}$. We map data for each of the functions onto the coordinate system formed by the spline basis:
%
\begin{equation}
T( \cF, \cD)_{ij} = \sum_{l=2}^m f_i(t_l) \delta_j(t_l) (t_l - t_{l-1}); \quad 1 \leq i \leq n, 1 \leq j \leq p.
\end{equation}
%
We then model  the $i$-th row of the $n \times p$ matrix $T(\cF, \cD) \equiv T$, 
denoted by $\bfT_{i}$ 
as follows:
\ban 
\bfT_i = \mu + P s_i + e_{i},
\ean
where $\mu$ is a location parameter, $P$ is a $p \times q$ loading matrix, $s_{i}$ is 
a $q \times 1$ score vector, and $e_{i}$ is the error term. We obtain robust estimators of 
$\mu$, $P$ and consequently $s_{i}$ using $\widehat{\tilde{\Sigma}}$. Define 
$\widehat{\bfT}_{i} = \hat{\mu} + \hat{P} \hat{s}_{i}$. 
The \textit{orthogonal distance} (OD)  corresponding to this projection is defined as 
\ban 
OD_{i} = | \bfT_i - \widehat{\bfT}_{i} |.
\ean
Analogously, the \textit{score distance} (SD) is defined as 
\ban 
SD_i = \sqrt{ \sum_{j=1}^q \frac{\hat{s}^2_{ij}}{\hat \lambda_j}}; 
\ean
where $\hat \lambda_1,\ldots ,\hat \lambda_q$ are the top eigenvalues from 
$\widehat{\tilde{\Sigma}}$. 
%We also transform this approximation back to the original coordinates: 
%$\hat f_i (t_l) = \sum_{j=1}^p \widehat{\bfT}_{ij} \delta_j (t_l)$. 
For outlier detection, following \cite{ref:Technometrics0564_Hubertetal} 
we set the upper cutoff values for 
score distances at $(\chi^2_{2, .975})^{1/2}$ and orthogonal distances at 
\ban
[\text{median}(OD^{2/3}) + \text{MAD}(OD^{2/3})\Phi^{-1}(0.975)]^{3/2},
\ean
 where 
$\Phi(\cdot)$ is the standard normal cumulative distribution function.

\begin{figure}
\begin{center}
\begin{tabular}{ll}
\includegraphics[width=0.4\textwidth]{./Plots/Elnino_functional1} &
\includegraphics[width=0.4\textwidth]{./Plots/Octane_functional1}\\
\includegraphics[width=0.4\textwidth]{./Plots/Elnino_functional2} &
\includegraphics[width=0.4\textwidth]{./Plots/Octane_functional2}\\
\includegraphics[width=0.4\textwidth]{./Plots/Elnino_functional3} &
\includegraphics[width=0.4\textwidth]{./Plots/Octane_functional3}\\
\end{tabular}
\caption{Actual sample curves, their spline approximations and diagnostic plots respectively for El-Ni\~no (a,c,e) and Octane (b,d,f) datasets}
\label{fig:fPCAfig}
\end{center}
\end{figure}

We apply the above outlier detection method on two data sets. First, we consider the 
monthly average \textit{sea surface temperature anomaly data} 
from June 1970 to May 2004, available 
from \url{http://www.cpc.ncep.noaa.gov/data/}, depicted in  panel (a) 
of Figure~\ref{fig:fPCAfig})).
Second, we consider the \textit{octane data}, which consists of 226 variables and 39 
observations \citep{ref:EsbensenetalBook94}. 
Each sample is a gasoline compound with a certain octane 
number, and has its NIR absorbance spectra measured in 2 nm intervals between 1100 - 1550 
nm. There are 6 outliers here: compounds 25, 26 and 36-39, which contain alcohol. This 
data is presented in  panel (b) of Figure~\ref{fig:fPCAfig})).

In the sea surface temperature data, using a cubic spline basis with knots at alternate 
months starting in June, we get a close approximation as depicted in 
panel (c) of Figure~\ref{fig:fPCAfig}. Using our proposed methodology with $q =1$ 
results in two points having their SD and OD larger than cutoff, depicted in  
panel (e) of Figure~\ref{fig:fPCAfig}. These points correspond to the time periods June 
1982 to May 1983 and June 1997 to May 1998 are marked by black curves in panels a and c, 
and pinpoint the two seasons with strongest El-Ni\~no events.

On the octane data, we use the same methodology, 
 and again the top robust PC turns out to be sufficient in identifying all 6 outliers. 
 Details are available in  panels (b), (d) and (f) of Figure~\ref{fig:fPCAfig}.

### 2019-08-09 EJSSubmission/WeightedSign_EJS_Conclusion_02_24_19_1.tex
EJS revision

\section{Conclusions}
\label{Sec:Conclusion}

We propose the use of a weighted multivariate sign transformation for robust 
estimation and inference, and as demonstrated by theoretical results and several 
simulation studies and data examples, in many situations using a data-depth driven weight 
function leads to considerable efficiency gain without compromising robustness 
properties. Our methodology seems to suggest new ways of identifying 
El-Ni\~no or La-Ni\~na events from the sea-surface temperature anomaly data, 
which will be studied further later.

Several of our results stated above are for data from the Euclidean space $\BR^{p}$, where 
$p$ is fixed. The cases where $p$ increases with sample size and may be higher than sample 
size, and where data are from a separable Hilbert space, will be considered in a future 
work. There are only few conceptual challenges to such extensions, however, there are 
several  technical and algebraic challenges.

### 2019-08-09 EJSSubmission/WeightedSign_EJS_Dispersion_02_24_19_1.tex
EJS revision

\section{A Robust Measure of  Dispersion} 
\label{Sec:WSDispersion1}

From this section onwards, we assume that $\cX = \BR^{p}$, that is, the support of the 
random variable under study is the $p$-dimensional Euclidean plane, and the data 
$X_{1}, \ldots, X_{n}$ are independent and identically distributed from an 
elliptical distribution $\BF$ with parameters $\mu$ and $\Sigma$.  We also 
assume that $X_{1}$ is absolutely continuous, with $\BP [ | X_{1}| = 0] = 0$, 
and that $\Sigma$ is positive definite. This  eliminates technicalities arising from
 rank deficient cases, and makes the weight functions  affine invariant.
Thus, we essentially restrict the rest of this paper to the same  framework as in 
Corollary~\ref{Cor:Elliptic_ARE}. Most of the results below generalize to the case where 
$\cX$ is a separable Hilbert space, however additional technicalities are involved, as in 
\cite{ref:AoS112852_Balietal_PCA_Functional_Robust}, and will be considered 
in a future project.

Consider the spectral decomposition of $\Sigma$ given by
 $\Sigma = \Gamma\Lambda\Gamma^T$, where $\Gamma$ is an orthogonal matrix 
 and $\Lambda$ is diagonal with positive diagonal elements $\lambda_1 \geq \ldots \geq 
 \lambda_p$.
Also denote the $i$-th eigenvector of $\Sigma$ by 
$\bfgamma_{i} = (\gamma_{i, 1}, \ldots, \gamma_{i, p})^T$ for $1 \leq i \leq p$. Thus, the 
$i$-th column of $\Gamma$ is $\bfgamma_{i}$.
  In the rest of this paper we use the notation 
 $\Sigma^{-1/2} = \Lambda^{-1/2} \Gamma^{T}$, and 
 hence $Z = \Lambda^{-1/2} \Gamma^T (X - \mu)$. 
Recall from Section~\ref{Sec:WSQuantiles} that we use the notation $\BF_{Z}$ for 
the distribution of $Z$, and that $\BF_{Z}$ is a spherically symmetric distribution 
and hence depends only on $|z|$.
Additionally, to simplify notations, for any random variable $X \sim \BF$, we occasionally 
use the abbreviated notation $W (X) \equiv W (X, \BF)$. Note that $W (X)$ is a 
\textit{random weight}, and takes the same value as $W (Z, \BF_{Z})$.  
Also, as noted in  Corollary~\ref{Cor:Elliptic_ARE}, 
 $W (Z)$ is a function of $|Z|$ only. 
 We additionally assume that $\BE W^{2} (X) < \infty$.

It is convenient to write 
\ban
X = \mu + R \Gamma \Lambda^{1/2}  U
\ean
where $U$  is a random variable uniformly distributed on the unit sphere 
${\cS}_{0; 1} = \{ x \in \cX: | x | = 1 \}$ and $R$ is another random variable independent 
of $U$ satisfying $\BE R^{2} = p$. Note that  $Z = R U$, and $|Z| = R$, $Z/|Z| = U$. 
Then we have
\ban 
S (X; \mu) & = |X - \mu|^{-1} (X - \mu) 
%\\
%& 
= | \Lambda^{1/2} R U|^{-1} R \Gamma  \Lambda^{1/2}  U\\
& =  | \Lambda^{1/2} U|^{-1} \Gamma \Lambda^{1/2}  U 
%\\
%& 
=  | \Lambda^{1/2} Z|^{-1} \Gamma \Lambda^{1/2}  Z
\ean

The rest of this paper is built on the following transformed random variable:
\baq
\tilde{X} = W (X, \BF) S(X; \mu) \equiv W (Z, \BF_{Z})  
| \Lambda^{1/2} Z|^{-1} \Gamma \Lambda^{1/2}  Z. 
\label{eq:tildeX}
\eaq
We define the notation $\BS (X; \mu) =  S (X; \mu) S( X; \mu)^T$.
Then, we define the following dispersion  parameter:
\baq
\tilde{\Sigma} = \BE \tilde{X} \tilde{X}^{T}
=  \BE W^{2} (X, \BF) \BS (X; \mu). 
\label{eq:tildeSigma}
\eaq
 In the following Theorem, we establish that the eigenvectors of ${\Sigma}$ and 
 $\tilde{\Sigma}$ are identical, although their eigenvalues may be different.

\begin{Theorem}
\label{Thm:WSVariance}
Under the conditions listed above, we have
$\tilde{\Sigma} = \Gamma \tilde{\Lambda} \Gamma^{T}$, where 
$\tilde{\Lambda} = \Lambda^{1/2} \BE W^{2} (X) 
	\BE UU^{T}/(U^{T}\Lambda U) \Lambda^{1/2}$
is a diagonal matrix.  Thus, the eigenvectors of ${\Sigma}$ and 
 $\tilde{\Sigma}$ are identical.
\end{Theorem}

\begin{proof}[Proof of Theorem~\ref{Thm:WSVariance}]

Fix any index $i \in \{1, \ldots, p \}$. Consider the vector $\tilde{U}$ such that 
\ban 
\tilde{U}_{j} = \left\{ \begin{array}{ll}
U_{j} & \text{ if } j \ne i, \\
- U_{i} & \text{ if } j = i. 
\end{array}
\right. 
\ean
Then $\tilde{U}$ and $U$ have the same distribution, and note that 
$U^{T} \Lambda U = \tilde{U}^{T} \Lambda \tilde{U}$ almost surely. Consequently, 
for any $j \ne i$ we have
\ban
\BE {\frac{U_{i} U_{j}}{U^{T} \Lambda U}}  
& = \BE {\frac{\tilde{U}_{i} \tilde{U}_{j}}{\tilde{U}^{T} \Lambda \tilde{U}}} 
%\\
%& 
= - \BE {\frac{{U}_{i} {U}_{j}}{U^{T} \Lambda U}}.
\ean
Consequently, 
$\BE S (X; \mu) S(X; \mu)^{T} = \Gamma \Lambda_{S} \Gamma^{T}$, 
as established in Theorem~1 of \citet{ref:SPL12765_Taskinenetal}.

Also, since the weight $W(X)$ is a function of $|Z| = R$, we have that $W(X)$ is 
independent of $S (X; \mu)$. Consequently, we have  
  \ban
  \tilde{\Sigma} & = \BE \tilde{X} \tilde{X}^{T} 
%  \\
%&
 = \BE W^{2} (X) S (X; \mu) S(X; \mu)^{T} \\
& =  \BE W^{2} (X)  \BE S (X; \mu) S(X; \mu)^{T} 
%\\
%& 
= \Gamma \Lambda_{W} \Gamma^{T}, 
\ean
where $\Lambda_{W}$ is a diagonal matrix.

\end{proof}

We now discuss the properties of the sample version $\widehat{\tilde{\Sigma}}$ 
computed from $\bfX$. 
In practice, we cannot obtain $W (x) \equiv W (x, \BF)$, 
and consequently use  $W (x, \BF_{n})$ instead. We assume the following conditions:
\begin{enumerate}
\item \textbf{Bounded weights:} The weights $W (\cdot, \cdot)$ are bounded functions.

\item \textbf{Uniform convergence:} 
\ban 
\sup_{x \in \cX} | W (x, \BF_{n}) - W (x, \BF) | \rightarrow 0 
\ean 
almost surely as $n \rightarrow \infty $.

\item \textbf{Smoothness under perturbation:}
For all $\BF \in \cF$, there exists a $\delta > 0$, possibly depending on $\BF$, such that 
for any $\epsilon \in (0, \delta)$ 
\ban 
\sup_{x \in \cX} \Bigl| W \bigl( x, \BF \bigr) - 
W \bigl( x, (1 - \epsilon)\BF + \epsilon \delta_{x} \bigr) \Bigr| \leq 
\epsilon.
\ean 
 \end{enumerate}
 In the above, $\delta_{x}$ denotes point mass at $x$. 
These property are easily satisfied under for  weight functions  derived 
from standard depth functions, for example, $W_{HSD} (\cdot)$, 
$W_{MhD} (\cdot)$ and $W_{PD} (\cdot)$ discussed earlier.

The following result allows us to use the empirical, plug-in weights and an 
estimated location parameter in the 
weighted dispersion estimator. A natural choice for the location parameter estimator 
is the solution to $\sum_{i = 1}^{n} \tilde{X}_{i} = 0$.

\begin{Lemma} \label{Lemma:lemma1}
Assume that $\BE \| X - \mu \|^{-4} < \infty$. Also assume that 
we have a location estimator  $\hat{\mu}_n$ satisfying 
$\BE \|\hat{\mu}_n  - \mu \|^{4} = O (n^{-2}) $. Then
\ban
\frac{1}{n} \sum_{i=1}^{n} W_{n}^{2} (X_{i}, \BF_{n}) \BS (X_{i}; \hat{\mu}_{n})  
= \frac{1}{n} \sum_{i=1}^{n} W^{2} (X_{i}, \BF) \BS (X_{i}; {\mu})
+ R_n,
\ean
%
where for any $c \in \BR^{p}$ such that $| c | = $, we have 
$\BE  c^{T} R_{n} c = o (n^{-1})$.
\end{Lemma}

\begin{proof}[Proof of Lemma~\ref{Lemma:lemma1}]
This proof is mostly algebra, and we provide a sketch of the main arguments.
We have
\ban 
& \frac{1}{n} \sum_{i=1}^{n} W_{n}^{2} (X_{i}, \BF_{n}) \BS (X_{i}; \hat{\mu}_{n}) \\
= & \frac{1}{n} \sum_{i=1}^{n} W^{2} (X_{i}, \BF) \BS (X_{i}; {\mu})
+ \frac{1}{n} \sum_{i=1}^{n}  
\bigl\{ W_{n}^{2} (X_{i}, \BF_{n})  -   W^{2} (X_{i}, \BF) \bigr\} \BS (X_{i}; {\mu}) \\
& + \frac{1}{n} \sum_{i=1}^{n} W^{2} (X_{i}, \BF) \bigl\{ 
\BS (X_{i}; \hat{\mu}_{n}) - \BS (X_{i}; {\mu}) \bigr\} \\
& + \frac{1}{n} \sum_{i=1}^{n}  
\bigl\{ W_{n}^{2} (X_{i}, \BF_{n})  -   W^{2} (X_{i}, \BF) \bigr\} 
\bigl\{ \BS (X_{i}; \hat{\mu}_{n}) - \BS (X_{i}; {\mu}) \bigr\}\\
& = \frac{1}{n} \sum_{i=1}^{n} W^{2} (X_{i}, \BF) \BS (X_{i}; {\mu})
+ T_{2} + T_{3} + T_{4}. 
\ean

Using the stated technical conditions, we can now show that 
$\BE  c^{T} T_{j} c = o (n^{-1})$ for $j = 2, 3, 4$. For illutration, we present
the case for $T_{2}$ below.

Notice that the $(j, k)$-th element of $T_{2}$ is given by 
\ban 
n^{-1} \sum_{i=1}^{n}  | X_{i} - \mu |^{-2}
\bigl\{ W_{n}^{2} (X_{i}, \BF_{n})  -   W^{2} (X_{i}, \BF) \bigr\} 
(X_{i, j} - \mu_{j}) (X_{i, k} - \mu_{k}), 
\ean
and hence 
\ban 
& c^{T} T_{2} c  = \sum_{j, k} c_{j} c_{k}T_{2, j, k} \\
& = n^{-1} \sum_{i=1}^{n}  | X_{i} - \mu |^{-2}
\bigl\{ W_{n}^{2} (X_{i}, \BF_{n})  -   W^{2} (X_{i}, \BF) \bigr\} 
\bigl( \sum_{j} c_{j} (X_{i, j} - \mu_{j}) \bigr)^{2} \\
& \leq 
M n^{-1} \sum_{i=1}^{n}  | X_{i} - \mu |^{-2}
\bigl\{ | W_{n} (X_{i}, \BF_{n})  -   W (X_{i}, \BF) | \bigr\} 
\bigl( c^{T} (X_{i} - \mu) \bigr)^{2} \\
& \leq 
M n^{-1} \sum_{i=1}^{n}  | X_{i} - \mu |^{-2}
\bigl\{ | W_{n} (X_{i}, \BF_{n})  -   W_{n} (X_{i}, \BF_{n, -i})  | \bigr\} 
\bigl( c^{T} (X_{i} - \mu) \bigr)^{2} 
\\ & \hspace{1cm}
+ M n^{-1} \sum_{i=1}^{n}  | X_{i} - \mu |^{-2}
\bigl\{ | W_{n} (X_{i}, \BF_{n, -i})  -   W (X_{i}, \BF) | \bigr\} 
\bigl( c^{T} (X_{i} - \mu) \bigr)^{2} 
\\
& =  M n^{-1} \sum_{i=1}^{n}  T_{2 1 i}  + M n^{-1} \sum_{i=1}^{n}   T_{2 2 i} \\
& = T_{21} + T_{22}.
\ean
Let $H (X_{i}) = | X_{i} - \mu |^{-2} \bigl( c^{T} (X_{i} - \mu) \bigr)^{2}$, and notice 
that $H (X_{i}) \leq 1$ almost surely for $|c| = 1$.  
Now notice that conditional on $X_{i}$ except for a null set $A_{i}$ (possibly depending 
on $X_{i}$) we have  
$T_{2 1 i} \leq n^{-1}  H (X_{i}) $. Thus, except for a null set 
$A_{1} \cap \ldots \cap A_{n}$, $T_{21} \leq M n^{-2}  H (X_{i})$ and the conclusion 
follows for this part.

The argument for $T_{22}$ follows a similar argument.
\end{proof}

Let $vec~(\BS (X; \mu))$ be the vectorized version of  $\BS (X; \mu)$.
We are now in a position to state the result for consistency of the sample 
version of $\tilde{\Sigma}$,

\begin{Theorem} \label{Theorem:CLT1}
Assume the conditions of Lemma~\ref{Lemma:lemma1}. Then
\ban
& n^{1/2} \sum_{i = 1}^{n} \Bigl( 
W_{n}^{2} (X_{i}, \BF_{n}) ~vec~(\BS (X_{i}; \hat{\mu}_{n})) 
- \BE W^{2} (X_{i}) ~vec~(\BS (X_{i}; \mu)) \Bigr)\\
& \hspace{0.5cm} \draro
N_{p^2} \bigl( 0, V_{W} \bigr),
\ean
where $V_{W} = \BV [W^{2} (X_{i}, \BF) ~vec~(\BS (X_{i}; {\mu})) ] $.
\end{Theorem}

The asymptotic normality  follows from our assumptions and as a direct consequence 
of Lemma~\ref{Lemma:lemma1}. Incidentally, an expression for $V_{W}$
can be explicitly obtained in terms of $\Gamma$, $\Lambda$ and $\BF$, but is 
algebraic in nature and hence omitted here.

We now use Theorem~\ref{Theorem:CLT1} to obtain consistency results for 
the eigenvectors obtained from $\widehat{\tilde{\Sigma}} = n^{-1} 
\sum_{i=1}^{n} W^{2} (X_{i}, \BF) \BS (X_{i}; \hat{\mu}_{n})$. 
Suppose that  $\tilde{\Lambda}_{1} > \tilde{\Lambda}_{2} > \ldots > \tilde{\Lambda}_{p}$
are the eigenvalues of $\tilde{\Sigma}$, which we assume are all distinct values.

\begin{Theorem} \label{Theorem:Eigen1}
Suppose the  spectral decomposition of $\widehat{\tilde{\Sigma}}$ is given 
by $\widehat{\tilde{\Sigma}} = \widehat{\Gamma} \widehat{\tilde{\Lambda}}
\widehat{\Gamma}^T $. Then the matrix of centered and scaled eigenvectors 
$G_{n} = n^{1/2} (\widehat{\Gamma} - \Gamma) $ 
and the vector of centered and scaled eigenvalues 
$L_{n} = n^{1/2} (\widehat{\tilde{\Lambda}} - {\tilde{\Lambda}}) $ have 
independent distributions. The distribution of the random variable $vec~(G_{n})$ converges 
weakly to a $p^2$-variate normal distribution with mean ${\bf 0}_{p^2}$ and the
variance matrix whose $(i, j)$-th block of $p \times p$ entries are given by
\baq
& \sum_{k=1, {}_{k \neq i}}^{p} 
\Bigl[ \tilde{\Lambda}_{i} -  \tilde{\Lambda}_{k} \Bigr]^{-2}
\BE \Bigl[ 
W^4 (Z, \BF_{Z}) \big( 
\BS_{i, k} ({\Lambda}^{1/2} Z; {\bf 0})
\big)^2 
\Bigr]
\bfgamma_k \bfgamma_k^T, 
\text{ if } i = j, \label{equation:DevEq} \\
& - 
\Bigl[ \tilde{\Lambda}_{i} -  \tilde{\Lambda}_{j} \Bigr]^{-2}
\BE \Bigl[ 
W^4 (Z, \BF_{Z}) \big( 
\BS_{i, j} ({\Lambda}^{1/2} Z; {\bf 0})
\big)^2 
\Bigr]
\bfgamma_i \bfgamma_j^T; \text{ if } i \neq j.
\eaq
The distribution of  $L_{n}$ converges 
weakly to a $p$-dimensional normal distribution with mean ${\bf 0}_{p}$ and the
variance-covariance matrix whose $(i, j)$-the element is
\ban
& \BE \Bigl[ 
W^4 (Z, \BF_{Z}) \big( 
\BS_{i, i} ({\Lambda}^{1/2} Z; {\bf 0})
\big)^2 
\Bigr]
- \tilde{\Lambda}_{i}^2, \text{ if } i = j, \\
& \BE \Bigl[ 
W^4 (Z, \BF_{Z}) \big( 
\BS_{i, j} ({\Lambda}^{1/2} Z; {\bf 0})
\big)^2 
\Bigr]
- \tilde{\Lambda}_{i} \tilde{\Lambda}_{j}, \text{ if } i \neq j.
\ean
\end{Theorem}

The proof of this result follows from using Theorem~\ref{Theorem:CLT1} and using 
techniques similar to a corresponding result in \citet{ref:SPL12765_Taskinenetal}, 
and we omit the  algebraic details here.

Recall that the asymptotic variance of the $i$-th eigenvector of the 
\textit{sample covariance matrix}, say $\hat{\bfgamma}_i$ is \citep{ref:AndersonBook09}:
%
\begin{equation} \label{equation:covevEq}
A\BV( \sqrt n\hat \bfgamma_{i}) = 
\sum_{k=1; k \neq i}^p 
\frac{\lambda_i \lambda_k}{(\lambda_i - \lambda_k)^2} \bfgamma_k \bfgamma_k^T; 
\quad 1 \leq i \leq p.
\end{equation}
%
Suppose $\widehat{\tilde{\bfgamma}}_i$ is the $i$-th eigenvector of 
$\widehat{\tilde{\Sigma}}$, whose asymptotic behavior is presented above in 
Theorem~\ref{Theorem:Eigen1}.

This leads to the following useful result:
\begin{Corollary}
The asymptotic relative efficiency of $\widehat{\tilde{\bfgamma}}_i$, 
relative to $\hat{\bfgamma}_i$, is given by 
\ban
& ARE (\widehat{\tilde{\bfgamma}}_i, \hat{\bfgamma}_i; \BF) \\
& =  
\Bigl[ \sum_{k=1; k \neq i}^p \frac{\lambda_i \lambda_k}{(\lambda_i - \lambda_k)^2} \Bigr]
 \Bigl[
\sum_{k=1, {}_{k \neq i}}^{p} 
\biggl[ \tilde{\Lambda}_{i} -  \tilde{\Lambda}_{k} \biggr]^{-2}
\BE \biggl[ 
W^4 (Z, \BF_{Z}) \big( 
\BS_{i, k} ({\Lambda}^{1/2} Z; {\bf 0})
\big)^2 
\biggr]  
\Bigr]^{-1}.
\ean
\end{Corollary}

The proof of this Corollary is immediate.

\section{An Affine Equivariant Robust Measure of Dispersion}
\label{Sec:WSDispersion2}

A desirable invariance property of any dispersion parameter $T_{X}$ corresponding to 
a random variable $X$ is that under affine transformation $Y = AX + b$ the dispersion 
parameter scales to $T_{Y} = A T_{X} A^{T}$. It is clear that $\tilde{\Sigma}$ does 
not possess this property, since it remains unchanged for $X$ and $Y = c X$ for any 
scalar $c > 0$.

We follow the general framework of M-estimation with data-dependent weights 
\citep{ref:HuberBook81} to construct an affine equivariant counterpart of the 
$\tilde{\Sigma}$. 
Specifically, we implicitly define
\begin{equation} \label{eqn:ADCM}
\Sigma_{*} = \frac{p}{ \BV W (X) } 
\BE \left[ \frac{W^{2}(X) (X - \mu) (X - \mu)^T}
{(X - \mu)^T \Sigma_{*}^{-1}(X - \mu)} \right].
\end{equation}
%

To ensure existence and uniqueness of $\Sigma_{*}$, consider the class of 
dispersion parameters $\Sigma_M$ that are obtained as solutions of the following equation:
%
\begin{equation}
\BE \left[ u( | Z_{M} | )  \frac{Z_{M} Z_{M}^T}{| Z_{M} |^2}  - v( | Z_{M} | ) \BI_p \right] = 0
\end{equation}
%
with $Z_M = \Sigma_M^{-1/2} (X - \mu)$. Under the following assumptions on the scalar valued functions $u$ and $v$, the above equation produces a unique solution \citep{ref:HuberBook81}:
%

\vspace{1em}
\noindent\textbf{(C1)} The function $u(r)/r^2$ is monotone decreasing, 
and $u(r)>0$ for $r > 0$;

\noindent\textbf{(C2)}  The function $v(r)$ is monotone decreasing, and 
$v(r) > 0$ for $r > 0$;

\noindent\textbf{(C3)} Both $u(r)$ and $v(r)$ are bounded and continuous;

\noindent\textbf{(C4)} $u(0) / v(0) < p$;

\noindent\textbf{(C5)} For any hyperplane in the sample space $\mathcal X$, 
(i) $P(H) = \BE \{ \cI_{\{X \in H \}} \} < 1 - p v(\infty) / u(\infty)$ and 
(ii) $P(H) \leq 1/p$.
%

\vspace{1em}
\noindent Putting things into context, in our case we have 
$v (\cdot) = p^{-1}\BV W (X)$, 
$u (\cdot) = W^{2}(X)$. 
%We use the notation $\BF_{|Z|}$ for the cumulative distribution function of $|Z|$.
We proceed to verify the other conditions for the weight functions 
$W_{HSD} (\cdot)$, 
$W_{MhD} (\cdot)$ and $W_{PD} (\cdot)$ discussed earlier.

It is easy to verify that the resulting $u (\cdot)$ from the above choices 
satisfy (C1) and (C3). 
Note that $v (\cdot)$ is a finite positive constant, 
and (C2) and (C3) are also easily satisfied. 
Since $u (0) = 0$ in all the above cases, (C4) is also easy to check. Since $X$ is 
absolutely continuous, (C5) holds trivially.

In order to compute the sample version of $\Sigma_{*}$, we solve (\ref{eqn:ADCM}) 
iteratively by obtaining a sequence of positive definite matrices 
$\hat{\Sigma}^{(k)}_{*}$ until convergence. Thus, using the location 
estimator $\hat{\mu}_{n}$, we may iterate
%
\ban
\hat{\Sigma}^{(k+1)}_{*}  = 
\frac{p}{ \BV W (X) } 
\BE \left[ \frac{W^{2}(X) (X - \hat{\mu}_{n}) (X - \hat{\mu}_{n})^T}
{(X - \hat{\mu}_{n})^T (\hat{\Sigma}^{(k)}_{*})^{-1}(X - \hat{\mu}_{n})} \right].
\ean
%

The asymptotic properties of $\hat{\Sigma}_{*}$ can be obtained using methods similar 
to those of Section~\ref{Sec:WSDispersion1}, and techniques presented in 
\cite{ref:Biometrika00603_CrouxHaesbroeck} and elsewhere. We state the following result and omit its proof.

\begin{Theorem}
\label{Thm:Eigen2}
The asymptotic covariance matrix of an eigenvector of the sample 
affine equivariant scatter functional $\hat{\Sigma}_{*}$ is given by
\ban 
V_{12}
\sum_{k=1, k \neq i}^p \frac{\lambda_i \lambda_k}{\lambda_i - \lambda_k} 
\bfgamma_i \bfgamma_k^T,
\ean
where $V_{12}$  is the asymptotic variance of an off-diagonal element of 
$\hat{\Sigma}_{*}$ when the underlying distribution is $\BF_{Z}$. 
It follows that if $\hat{\bfgamma}_{*, i}$ is the $i$-th eigenvector of $\hat{\Sigma}_{*}$,
%
\begin{equation}
ARE (\hat{\bfgamma}_{*, i}, \hat\bfgamma_{i}; \BF) = V_{12}^{-1} = 
\frac{\left[ \BE ( p u (| Z |)  + u'( | Z |) | Z | ) \right]^2}
{p^2 (p+2)^2 \BE (u (| Z |)^2 \BE (\BS_{12} (Z; {\bf 0}))^2}.
\end{equation}
%
\end{Theorem}

\section{Robust Estimation of Eigenvalues, and a Plug-in Estimator of $\Sigma$}
\label{Sec:Eigen}

As seen in Theorem~\ref{Thm:WSVariance}, eigenvalues of the $\tilde{\Sigma}$ 
are not same as the population eigenvalues. In this section, we discuss on robust 
estimation of $\lambda_{i}$'s using $\tilde{\Sigma}$. Assume the data 
is centered, the robust estimator from Section~\ref{Sec:WSQuantiles} suffices. 
We start by computing 
the sample version $\widehat{\tilde{\Sigma}}$ and its spectral decomposition:
\ban 
\widehat{\tilde{\Sigma}} = \widehat{{\Gamma}} \widehat{\tilde{\Lambda}}
\widehat{{\Gamma}}^{T}
\ean 
We then use the following steps:

\begin{enumerate}
\item Randomly divide the sample indices $\{1,2, \ldots, n\}$ into $k$ disjoint groups $\{G_1,\ldots, G_k \}$ of size $\lfloor n/k \rfloor$ each.

\item Transform the data matrix: 
$\bfS = \widehat{{\Gamma}}^{T} \bfX$.

\item Calculate coordinate-wise variances for each group of indices $G_j$:
%
\ban
\lambda_{i, j}^{\dagger} = \frac{1}{|G_j|} \sum_{l \in G_j} \bigl( 
S_{l i} - \bar{S}_{G_{j}, i} \bigr)^2; \quad i = 1, \ldots, p; \  j = 1, \ldots, k.
\ean
where $\bar{\bfS}_{G_j} = (\bar{S}_{G_j, 1}, \ldots, \bar{S}_{G_j,p})^T$ is the vector of 
column-wise means of $\bfS_{G_j}$, the submatrix of $\bfS$ with row indices in $G_j$.
%

\item Obtain estimates of eigenvalues by taking coordinate-wise medians of these variances:
%
\ban
{\lambda}^{\dagger}_{i} = \text{median} (\lambda_{i,1}^{\dagger}, 
\ldots , \lambda_{i,k}^{\dagger} ); \quad 
i = 1, \ldots, p.
\ean
%
\end{enumerate}
%

We collect ${\lambda}^{\dagger}_{i}$, $ i =1, \ldots, p$ in the diagonal matrix 
${\Lambda}^{\dagger} = \diag ({\lambda}^{\dagger}_{1}, \ldots, 
{\lambda}^{\dagger}_{p})$.
The number of subgroups used to calculate this median-of-small-variances estimator can 
be determined following \cite{ref:Bernoulli152308_Minsker_Median_Banach}. 
There can be other ways of estimating 
the eigenvalues of $\Sigma$ using $\bfS$ also, we will pursue such methods elsewhere.
We construct a consistent 
plug-in estimator of the population covariance matrix $\Sigma$ as 
\ban 
{\Sigma}^{\dagger}
= \widehat{{\Gamma}} {\Lambda}^{\dagger} \widehat{{\Gamma}}^{T}.
\ean
Let $| A |_{F}$ denote the Frobenius norm of a matrix $A$, in other words,
$| A |_{F} = (\text{trace} A^{T} A)^{1/2}$.
The following result establishes that this is a consistent estimator of $\Sigma$:

\begin{Theorem}\label{Thm:pluginSigma}
Suppose that as $n \rightarrow \infty$, $k \rightarrow \infty$ and 
$n/k \rightarrow \infty$.
Then we have
%
\ban
\| {\Sigma}^{\dagger} - \Sigma \|_F \stackrel{P}{\rightarrow} 0.
\ean
%
\end{Theorem}

\begin{proof}[Proof of Theorem \ref{Thm:pluginSigma}]
This proof has many algebraic steps, and we sketch the main arguments below.
Suppose $\hat{A} = \widehat{{\Gamma}}^{T}  \Sigma \widehat{{\Gamma}}$.

Owing to the fact that the Frobenius norm is invariant under rotations and 
that $p$ is finite and fixed, it suffices to show that the off-diagonal elements of 
$\hat{A}$ converge in probability to zero, and that the difference between 
the $i$-th diagonal element of $\hat{A}$ and ${\lambda}^{\dagger}_{i}$ converges to 
zero for any $i = 1, \ldots, p$.

Now notice that from Theorem~\ref{Theorem:Eigen1} we have that $\widehat{{\Gamma}} 
= {{\Gamma}} + R_{n1}$, where the $(i, j)$-th element of the remainder 
$R_{n1, i, j}$ satisfies $\BE  R_{n1, i, j}^{2} = O(n^{-1})$.

We can show, using standard algebra, that 
\ban
\hat{A} = \Lambda + R_{n2}, 
\ean
where the $(i, j)$-th element of the remainder 
$R_{n2, i, j}$ satisfies $\BE  R_{n2, i, j}^{2} = O(n^{-1})$. 
This follows immediately from above, the fact that $p$ is finite and fixed, and all 
elements of $\Lambda$ are constants. This immediately establishes the case for the 
off-diagonal elements.

For the diagonal elements, notice that since $k \rightarrow \infty$, each 
coordinate-wise variance $\lambda_{i, j}^{\dagger}$ for each group of indices $G_j$ 
is a consistent estimator of $\lambda_{i}$. The result follows.

\end{proof}

### 2019-08-09 EJSSubmission/WeightedSign_EJS_IF_02_24_19_1.tex
EJS revision

\section{Influence Functions of Dispersion Measures}
\label{Sec:RE_Dispersion}

We retain the framework adopted in Section~\ref{Sec:WSDispersion1}, and discuss in this 
section the robustness and efficiency properties associated with $\tilde{\Sigma}$ 
and $\Sigma_{*}$, and principal components derived therefrom. 
We do not discuss $\Sigma^{\dagger}$ here, since  the 
properties of that approach follow from those of  $\tilde{\Sigma}$. 
We additionally assume that the eigenvalues of $\Sigma$ are 
distinct, and given by  $\lambda_1 > \lambda_2 > \ldots > \lambda_p$, to avoid 
several additional technical conditions for the theoretical results to follow. 
The case where the eigenvalues of $\Sigma$ can have multiplicity greater than one 
requires no additional conceptual development, but does require considerable algebraic 
manipulations.

For studying 
the robustness aspect, we first present some results relating to influence functions 
in the current context. 
 Influence functions quantify how much influence a sample point, especially 
an infinitesimal contamination, has on any functional of a probability 
distribution \citep{ref:HampelBook86}. Given any probability distribution 
$\BH \in \cM$, the influence function of any point $x_0 \in \mathcal{X}$ for 
some functional $T(\BH)$ on the distribution is defined as
%
\ban
IF(x_0; T,\BH) =
\lim_{\epsilon \rightarrow 0} \frac{1}{\epsilon} (T(\BH_\epsilon) - T(\BH)),
\ean
%
where 
$\BH_\epsilon = (1-\epsilon)\BH + \epsilon \delta_{x_0}$; $\delta_{x_0}$ being 
the distribution with point mass at $x_0$. When $T(\BH) = E_\BH f$ for some 
$\BH$-integrable function $f$, $IF(x_0; T,\BH) = f(x_0) - T(\BH)$.

It now follows that
%
\ban
IF (x_0; \tilde{\Sigma}, \BF) =
W^{2} (x_{0}) \BS(x_0; \mu) - \tilde \Sigma.
\ean
%
Recall that $\tilde{\lambda}_{1} > \tilde{\lambda}_{2} > \ldots > \tilde{\lambda}_{p}$
are the eigenvalues of $\tilde{\Sigma}$, which we assume are all distinct values.

\begin{Proposition}\label{Thm:IF}
The influence function of $\bfgamma_{i}$ as follows: 
\ban
IF(x_0; \bfgamma_{i}, \BF)  & = 
\sum_{k = 1; k \neq i}^p \frac{1}{\tilde{\lambda}_{i} - \tilde{\lambda}_{k}} 
\left\{ \bfgamma^T_k IF(x_0; \tilde \Sigma,\BF)  \bfgamma_{i} \right\} 
\bfgamma_k \notag \\
& =  \sum_{k=1; k \neq i}^p \frac{1}{\tilde{\lambda}_{i} - \tilde{\lambda}_{k}}
W^{2} (x_{0}) \left\{  \bfgamma^T_{k} \BS (x_0; \mu) \bfgamma_{i} \right\} 
\bfgamma_{k}.
\ean
\end{Proposition}

The proof of Proposition~\ref{Thm:IF} follows from \cite{ref:JRSSB79217_Sibson} and 
\cite{ref:Biometrika00603_CrouxHaesbroeck}, we omit the details.

If the weight function $W (\cdot)$ is a bounded function, as is the case of $W_{HSD}$, 
$W_{MhD}$, and $W_{PD}$, 
the influence function given in  Proposition~\ref{Thm:IF} is bounded, indicating good 
robustness properties of the principal component analysis.

We now derive the influence function for $\Sigma_{*}$. 
\begin{Proposition}\label{Thm:IF2}
The influence function of $\Sigma_{*}$ is given by
\ban 
IF ( x_{0}, \Sigma_{*}, \BF) = 
\alpha_{\Sigma_{*}} ( | x_{0} |; \BF_{Z} ) 
\BS( x_0; \mu) 
- \beta_{\Sigma_{*}} (| x_{0} |; \BF_{Z} ) \Sigma_{*}.
\ean
\end{Proposition}

\begin{proof}[Proof of Proposition~\ref{Thm:IF2}:]

Let $z_{0} = \Lambda^{-1/2} \Gamma^T  (x_0 - \mu) = (z_{0 1}, \ldots, z_{0 p})^T$.
As a first step, since $\Sigma_{*}$ is affine equivariant, we obtain from 
\cite{ref:Biometrika00603_CrouxHaesbroeck} 
that 
\ban 
IF ( x_{0}, \Sigma_{*}, \BF) = \Sigma_{*}^{1/2} 
IF ( z_{0}, \Sigma_{*}, \BF_{Z})  \Sigma_{*}^{1/2}.
\ean
From Lemma1 of \citep{ref:HampelBook86}, page 276, we obtain that there exist 
scalar valued functions $\alpha_{\Sigma_{*}} ( | x_{0} |; \BF_{Z} )$ and 
$\beta_{\Sigma_{*}} ( | x_{0} |; \BF_{Z} ) $ such  that 
\ban
IF ( z_{0}, \Sigma_{*}, \BF_{Z}) = \alpha_{\Sigma_{*}} ( | x_{0} |; \BF_{Z} ) 
\BS( z_0; {\mathbf 0}) 
- \beta_{\Sigma_{*}} (| x_{0} |; \BF_{Z} ) \BI_{p}, 
\ean
consequently we obtain
\ban 
IF ( x_{0}, \Sigma_{*}, \BF) = 
\alpha_{\Sigma_{*}} ( | x_{0} |; \BF_{Z} ) 
\BS( x_0; \mu) 
- \beta_{\Sigma_{*}} (| x_{0} |; \BF_{Z} ) \Sigma_{*}.
\ean
\end{proof}

Suppose ${\lambda}_{* 1} > {\lambda}_{* 2} > \ldots > {\lambda}_{* p}$
are the eigenvalues of ${\Sigma}_{*}$, which we assume are all distinct values. 
Also denote the $i$-th eigenvector of $\Sigma_{*}$ by 
$\bfgamma_{* i} = (\gamma_{* i 1}, \ldots, \gamma_{* i p})^T$ for $1 \leq i \leq p$.

\begin{Proposition}\label{Thm:IF3}
The influence function of $\bfgamma_{* i} $ may be obtained as 
\ban
IF(x_0; \bfgamma_{*i}, \BF)  & = 
\sum_{k = 1; k \neq i}^p \frac{1}{{\lambda}_{*i} - {\lambda}_{*k}} 
\left\{ \bfgamma^T_{* k} IF(x_0; \tilde \Sigma,\BF)  \bfgamma_{* i} \right\} 
\bfgamma_{* k} \notag \\
& =  
\alpha_{\Sigma_{*}} ( | x_{0} |; \BF_{Z} ) \sum_{k=1; k \neq i}^p 
\frac{1}{{\lambda}_{*i} - {\lambda}_{*k}}
\left\{ \bfgamma^T_{* k} \BS (x_0; \mu) \bfgamma_{* i} \right\} 
\bfgamma_{* k}.
\ean
\end{Proposition}

We omit the proof of Proposition~\ref{Thm:IF3}, which follows along similar lines to 
to rest of the computations of this section.
It can be shown that when $W (\cdot)$ is a bounded function, 
$\alpha_{\Sigma_{*}} ( | x_{0} |; \BF_{Z} )$ is also bounded, along the lines of 
\cite{ref:HuberBook81}, which in turn implies that the influence function for a 
principal component based on $\Sigma_{*}$ is also bounded.

### 2019-08-09 EJSSubmission/WeightedSign_EJS_Introduction_02_24_19_1.tex
EJS revision

\section{Introduction}
\label{Sec:Introduction}

 Given a point $\mu$ in a normed linear space $\cX$ with norm denoted by $| \cdot |$, 
 the \textit{generalized sign function} 
 $S : \cX \times \cX \mapsto \cX$ with center $\mu$ is  
 defined as
\baq
S (x; \mu) =  \left\{ 
\begin{array}{ll}
| x - \mu|^{-1} ( x - \mu ) &  \text{ if } x \ne \mu, \\
0 & \text{ if } x = \mu.
\end{array}
\right.
\label{eq:GSign}
\eaq
This is a functional and multivariate  generalization of the real-valued 
\textit{sign function}, that 
takes the values one, negative one or zero if the point $x \in \BR$ is to the right, left 
or equal $\mu \in \BR$ respectively. This generalized sign function was  
introduced by \cite{ref:JNonpara95201_MottonenOja95} for $\cX = \BR^{p}$, 
the $p$-dimensional  real Euclidean space.

The function $S$ maps $\mu$ to the origin and all other points of $\cX$ 
to the unit sphere  ${\cS}_{0; 1} = \{ x \in \cX: | x | = 1 \}$. 
Given a dataset  $\{ X_{i} \in \BR^{p}: i =1, \ldots, n \}$,
that we collect together in 
the $n \times p$ matrix $\bfX = ( X_{1}: \ldots : X_{n} )^{T}$,
an approach for robust estimation and inference in multivariate data starts by evaluating  
\eqref{eq:GSign} on each observation, thus defining 
$S_{i} = S ( X_{i}; \mu_x)$ with respect to some suitable center 
$ \mu_x \in \BR^{p}$, and then using these for robust location and scale estimation and 
inference, including inference for $ \mu_x$ 
\citep{ref:Test991_Locantoreetal, ref:OjaBook10, ref:JASA151658_WangPengLi}.
Suppose $\bfS = ( S_{1}: \ldots : S_{n} )^{T} \in \BR^{n \times p}$. 
If the data $\{ X_{i} \in \BR^{p}: i =1, \ldots, n \}$ are independent, identically 
distributed (hereafter, i.i.d.) from an elliptically symmetric distribution, then the 
eigenvectors of $\BE ( X_{1} - \tilde{\mu}) ( X_{1} - \tilde{\mu})^{T}$
and of $\BE S_{1} S_{1}^{T}$ are the same for suitable centering 
parameters $\tilde{\mu}$ and $ \mu_x$, that is, the population principal components 
from the original data and from its sign transformations are the same 
\citep{ref:SPL12765_Taskinenetal}.
However, valuable information is lost in the form of magnitudes of sample points. As a 
result, spatial sign-based procedures suffer from low efficiency. For example, eigenvector 
estimates obtained from the covariance matrix of $\bfS$ are asymptotically inadmissible 
\citep{ref:Biometrika14673_MagyarTyler} and  Tyler's M-estimate of scatter \citep{ref:AoS87234_Tyler} has uniformly 
lower asymptotic risk.

In this paper, we propose to alleviate this low efficiency problem, by associating 
a data-driven weight $W_{i}$ with the generalized sign $S_{i}$, that can be used 
to adaptively trade-off between efficiency and robustness considerations in any given 
application. We demonstrate the utility of using 
the proposed \textit{weighted generalized sign} functions in a number of problems 
of current interest, including robust estimation of location and scatter.

Specifically, we propose using product of the generalized sign function and a 
weight function derived as a transformation of a data-depth function 
\citep{ref:AoS00461_ZuoSerfling, ref:DIMACS061_Serfling}.
 Like data-depth functions, the weight functions 
used in this paper are non-negative reals defined over $\cX \times \cF$, where 
$\cF$ is a fixed family of probability measures.
For every choice of parameters $\mu \in \cX$ and $\BF \in \cF$, in this paper
\begin{align}
R (X_{i}; \mu, \BF) = \mu +  S( X_{i}, \mu) W( X_{i}, \BF).
\label{eqn:rank}
\end{align}
is used as a robust surrogate for observation $X_{i}$.
Notice that for the trivial choice $W( x, \BF) = | x - \mu_{\BF} |$, 
 $\mu = \mu_{\BF}$,  we get $R (X_{i}; \mu, \BF) = X_{i}$, the original observations. 
 With the other trivial choice of  $W( x, \BF) \equiv 1$, we get the 
 generalized  sign $R (X_{i}; \mu, \BF) = S(X_{i}, \mu) = S_{i}$. 
 However, in this paper we illustrate how using other weight functions
 can lead to interesting robustness and efficiency trade-offs in a variety of situations. 
 The various technical conditions and assumptions that we impose on the 
 weight function $W( x, \BF)$ are valid for weights derived 
 from three well-known data depth functions: the \textit{half-space depth}, 
 the \textit{Mahalanobis depth}, and the \textit{projection depth}.

 %\begin{comment}
\begin{figure}[t]
%\captionsetup{justification=centering, font=footnotesize}
\begin{center}
\begin{tabular}{ll}
%%% These ones have sample size = 700, just right  for EJS
\includegraphics[width=0.45\textwidth]{./Plots_SC/WeightedSign_Scatter_700_02_27_19} &
\includegraphics[width=0.45\textwidth]{./Plots_SC/WeightedSign_MD_700_02_27_19} \\
\includegraphics[width=0.45\textwidth]{./Plots_SC/WeightedSign_TD_700_02_27_19} &
\includegraphics[width=0.45\textwidth]{./Plots_SC/WeightedSign_PD_700_02_27_19} \\

%%% These ones have sample size = 300, OK but too small file for EJS
%\includegraphics[width=0.45\textwidth]{../Plots_SC/WeightedSign_Scatter_02_27_19} &
%\includegraphics[width=0.45\textwidth]{../Plots_SC/WeightedSign_MD_02_27_19} \\
%\includegraphics[width=0.45\textwidth]{../Plots_SC/WeightedSign_TD_02_27_19} &
%\includegraphics[width=0.45\textwidth]{../Plots_SC/WeightedSign_PD_02_27_19} \\

%%% These ones have sample size = 1e3, too large file for EJS
%\includegraphics[width=0.45\textwidth]{../Plots_SC/WeightedSign_Scatter_02_24_19} &
%\includegraphics[width=0.45\textwidth]{../Plots_SC/WeightedSign_MD_02_24_19} \\
%\includegraphics[width=0.45\textwidth]{../Plots_SC/WeightedSign_TD_02_24_19} &
%\includegraphics[width=0.45\textwidth]{../Plots_SC/WeightedSign_PD_02_24_19} \\
\end{tabular}
\caption{
An illustrative bivariate scatter plot in the top left panel where the outliers are 
identified with red circles, 
and generalized signs from the same data (black points on the 
unit radius circle, outliers are red points) in the other panels. 
In the top right (bottom left, bottom right) 
panel, weighted signs from the same data with weights obtained using Mahalanobis depth 
(Tukey depth, projection depth respectively) are presented as green triangles 
(outliers are identified by blue triangles). 
}
\label{fig:Fig1}
\end{center}
\end{figure}
%\end{comment}

We primarily focus on the task of \textit{robust dispersion/scatter estimation} and 
\textit{robust principal component analysis} in this paper. Figure~\ref{fig:Fig1} presents an illustrative example of bivariate data with outliers in the top left panel, where the outliers are marked with red points. In the 
other panels, the generalized sign values of the same data are presented as black points 
on the unit circle, with the outliers again marked with red points. Notice that the 
black points from either the top right or bottom panels have very similar eigenvector 
structure as the original data without the outliers. The green and blue triangles 
are examples of 
the proposed \textit{weighted sign} values: the top right (respectively, bottom left, 
bottom right) panels depict these values where the weights have been generated using 
Mahalnobis depth (respectively Tukey's half-space depth and the projection depth). The 
blue triangles are the weighted sign values of the outliers. Notice that the eigenvectors 
from the weighted signs also capture the pattern from the original data without the 
outliers.

\rework{
There are two unknown quantities in the generalized sign function as defined in \eqref{eq:GSign}: $\mu$ and $\BF$, To estimate dispersion and its eigen-structure robustly, we must start with a robust estimator for $\mu$. In Section~\ref{Sec:WSQuantiles} we present the case for \textit{weighted spatial quantiles}, which can be defined and studied in very general spaces 
$\cX$. One special case of this is the {\it weighted spatial median}. As a location estimator, it has several interesting robustness properties and can be shown to be more efficient that some existing robust location estimators, thus making it a perfect candidate to estimate $\mu$. On the other hand, setting $\BF$ as $\BF_X$, i.e. the distribution of $X$ has the clear interpretation of differentially weighting observations based on their inlyingness to the overall data distribution. This mirrors the context of how data depth has been used in the literature (refs). Due to this reason, except for two results in Section~\ref{Sec:WSQuantiles} (Theorem~\ref{Thm:WSMedian} and Corollary~\ref{Cor:ARE}) we assume $\BF \equiv \BF_X$ for the rest of the paper. However, other choices of $\BF$ may lead to interesting interpretations of $W(. ,\BF)$ and the resulting quantities, e.g. (ref), and can potentially be explored further.
}

Following that, we restrict to the $\BR^{p}$ for fixed $p$, and present detailed 
discussions on our primary proposal for a  robust measure of dispersion in 
Section~\ref{Sec:WSDispersion1}, followed by a proposed 
\textit{ affine equivariant version} of 
it in Section~\ref{Sec:WSDispersion2}, robust estimation of eigenvalues and a third 
robust estimator for dispersion in Section~\ref{Sec:Eigen}, and a thorough study of 
robustness and efficiency using influence functions in Section~\ref{Sec:RE_Dispersion}.
We then report multiple simulation-based numeric studies in Section~\ref{Sec:Simulation}, 
present several real data examples in Section~\ref{Sec:DA}, and concluding remarks in 
Section~\ref{Sec:Conclusion}.

In the rest of this paper, all finite-dimensional vectors are 
column vectors, and for a vector or matrix $a$, the notation $a^{T}$ stands for 
its transpose. The Gaussian distribution with mean $\mu$ and variance $\Sigma$ is denoted
by $N (\mu, \Sigma)$. The identity matrix  is denoted by $\BI$, with or without a 
subscript to denote its dimension. The notations $A^{-1}$ and $det (A)$ respectively 
stand for the inverse and determinant of matrix $A$, whenever these are well-defined.

### 2019-08-09 EJSSubmission/WeightedSign_EJS_Simulations_02_24_19_1.tex
EJS revision

\section{Simulation Studies}
\label{Sec:Simulation}

We report numerical simulation studies on several properties relating to 
$\tilde{\Sigma}$ and  $\Sigma_{*}$, and their eigenvalues and eigenvectors, 
on datasets with or without influential points, to illustrate the finite sample 
efficiency and robustness properties of the proposed weighted estimators. We compare 
these proposed estimators with techniques that exists in literature, specifically, 
the Sign Covariance Matrix (SCM) and Tyler's shape matrix \citep{ref:AoS87234_Tyler}.

\subsection{Efficiency of different robust estimators}

We compare the performance of $\tilde{\Sigma}$ and $\Sigma_{*}$ with that of the 
SCM and Tyler's scatter matrix. For this study, we fix the dimension $p = 4$.
We consider six elliptical distributions, 
and from every distribution draw 10000 samples each for sample sizes $n = 20, 50, 100, 
300$ and $500$. All distributions are centered at ${\bf 0}_p$, and have covariance matrix 
$\Sigma = \diag(4, 3, 2, 1)$.

We use the concept of principal angles 
\citep{ref:LinearAlgebraApplications9281_MiaoBenIsrael} 
to find out error estimates for the 
first eigenvector of a scatter matrix. In our case, the first eigenvector is
%
\ban
\bfgamma_1 = (1, \overbrace{0, \ldots, 0}^{p - 1})^T.
\ean
%
We measure the prediction error for an eigenvector estimator (say, $\tilde\bfgamma_{1}$), 
using the smallest angle between the true and predicted vectors, i.e. 
$ \cos^{-1} | \tilde\bfgamma_{1}^T \hat\bfgamma_1 | $. A small absolute value of this 
angle means to better prediction. We repeat this 10,000 times and calculate the 
\textbf{Mean Squared Prediction Angle}:
%
\ban
MSPA(\hat \bfgamma_{1}) =
\frac{1}{10000} \sum_{m=1}^{10000} \left( \cos^{-1} 
\left|\bfgamma_1^T \tilde\bfgamma^{(m)}_{1} \right| \right)^2.
\ean
%
where $\tilde\bfgamma^{(m)}_{1}$ is the value of $\tilde\bfgamma_{1}$ in the 
$m$-th replication, $m = 1, \ldots, 10,000$. 
The finite sample efficiency of $\tilde\bfgamma_{1}$ relative to that 
from the sample covariance matrix, i.e. $\hat\bfgamma_{1}$ is obtained as:
\ban
 FSE ( \hat\bfgamma_{1}, \hat\bfgamma_{1}) = 
 \frac{ MSPA(\hat\bfgamma_{0, 1})}{MSPA(\hat\bfgamma_{1})}.
 \ean

The results from this simulation exercise are presented in Table~\ref{table:FSEtable4}.
It can be seem that  $\tilde{\Sigma}$-based estimators (columns 3-5) 
outperform SCM and Tyler's $M$-estimator of scatter. Among the 3 depth functions 
considered, projection depth gives the best results. Its finite sample performances are 
better than Tyler's and Huber's M-estimators of scatter, as well as their symmetrized 
counterparts that are much more computationally intensive (see Table 4 in 
\cite{ref:JMVA071611_Sirkiaetal}). The affine equivariant ${\Sigma}_{*}$-based estimators
 (columns 6-8) are even more efficient.

\begin{table}[t]
\begin{scriptsize}
    \begin{tabular}{c|cc|ccc|ccc}
    \hline
    4-variate $t_5$    & SCM  & Tyler & $\tilde{\Sigma}$-H & $\tilde{\Sigma}$-M & $\tilde{\Sigma}$-P & ${\Sigma}_{*}$-H & ${\Sigma}_{*}$-M & ${\Sigma}_{*}$-P \\ \hline
    $n$=20             & 1.04 & 1.02  & 1.10   & 1.07   & 1.02  & 1.09    & 1.07    & 0.98   \\
    $n$=50             & 1.08 & 1.08  & 1.16   & 1.16   & 1.13  & 1.19    & 1.19    & 1.13   \\
    $n$=100            & 1.31 & 1.31  & 1.42   & 1.38   & 1.36  & 1.46    & 1.44    & 1.36   \\
    $n$=300            & 1.46 & 1.54  & 1.81   & 1.76   & 1.95  & 1.88    & 1.88    & 1.95   \\
    $n$=500            & 1.92 & 1.93  & 2.23   & 2.03   & 2.31  & 2.35    & 2.19    & 2.39   \\ \hline
    4-variate $t_6$     & SCM  & Tyler & $\tilde{\Sigma}$-H & $\tilde{\Sigma}$-M & $\tilde{\Sigma}$-P & ${\Sigma}_{*}$-H & ${\Sigma}_{*}$-M & ${\Sigma}_{*}$-P \\ \hline
    $n$=20             & 1.00 & 1.05  & 1.03   & 1.05   & 1.00  & 1.04    & 1.04    & 0.95   \\
    $n$=50             & 1.03 & 1.01  & 1.13   & 1.12   & 1.11  & 1.19    & 1.17    & 1.10   \\
    $n$=100            & 1.08 & 1.12  & 1.25   & 1.23   & 1.27  & 1.24    & 1.25    & 1.22   \\
    $n$=300            & 1.34 & 1.36  & 1.64   & 1.52   & 1.60  & 1.67    & 1.61    & 1.68   \\
    $n$=500            & 1.26 & 1.34  & 1.55   & 1.49   & 1.60  & 1.65    & 1.61    & 1.69   \\ \hline
    4-variate $t_{10}$ & SCM  & Tyler & $\tilde{\Sigma}$-H & $\tilde{\Sigma}$-M & $\tilde{\Sigma}$-P & ${\Sigma}_{*}$-H & ${\Sigma}_{*}$-M & ${\Sigma}_{*}$-P \\ \hline
    $n$=20             & 0.90 & 0.89  & 0.95   & 0.98   & 0.98  & 0.96    & 1.01    & 0.95   \\
    $n$=50             & 0.90 & 0.91  & 1.01   & 0.98   & 0.98  & 1.03    & 1.04    & 0.99   \\
    $n$=100            & 0.87 & 0.87  & 0.93   & 0.95   & 1.01  & 0.99    & 1.01    & 1.05   \\
    $n$=300            & 0.87 & 0.87  & 1.09   & 1.09   & 1.17  & 1.14    & 1.16    & 1.23   \\
    $n$=500            & 0.88 & 0.92  & 1.10   & 1.10   & 1.23  & 1.19    & 1.22    & 1.29   \\ \hline
    4-variate $t_{15}$  & SCM  & Tyler & $\tilde{\Sigma}$-H & $\tilde{\Sigma}$-M & $\tilde{\Sigma}$-P & ${\Sigma}_{*}$-H & ${\Sigma}_{*}$-M & ${\Sigma}_{*}$-P \\ \hline
    $n$=20             & 0.92 & 0.90  & 0.94   & 0.94   & 0.96  & 0.95    & 0.97    & 0.89   \\
    $n$=50             & 0.82 & 0.83  & 0.88   & 0.91   & 0.93  & 0.88    & 0.93    & 0.93   \\
    $n$=100            & 0.84 & 0.87  & 0.92   & 0.95   & 1.00  & 0.93    & 0.96    & 1.00   \\
    $n$=300            & 0.73 & 0.75  & 0.96   & 0.99   & 1.10  & 1.00    & 1.06    & 1.12   \\
    $n$=500            & 0.73 & 0.76  & 0.95   & 0.96   & 1.06  & 0.94    & 0.97    & 1.06   \\ \hline
    4-variate $t_{25}$  & SCM  & Tyler & $\tilde{\Sigma}$-H & $\tilde{\Sigma}$-M & $\tilde{\Sigma}$-P & ${\Sigma}_{*}$-H & ${\Sigma}_{*}$-M & ${\Sigma}_{*}$-P \\ \hline
    $n$=20             & 0.89 & 0.92  & 0.92   & 0.92   & 0.90  & 0.96    & 0.95    & 0.89   \\
    $n$=50             & 0.82 & 0.84  & 0.89   & 0.90   & 0.91  & 0.93    & 0.96    & 0.92   \\
    $n$=100            & 0.77 & 0.76  & 0.90   & 0.90   & 0.96  & 0.94    & 0.98    & 1.04   \\
    $n$=300            & 0.73 & 0.77  & 0.93   & 0.91   & 0.98  & 1.00    & 0.98    & 1.03   \\
    $n$=500            & 0.67 & 0.71  & 0.83   & 0.83   & 0.96  & 0.88    & 0.90    & 1.00   \\ \hline
    4-variate Normal   & SCM  & Tyler & $\tilde{\Sigma}$-H & $\tilde{\Sigma}$-M & $\tilde{\Sigma}$-P & ${\Sigma}_{*}$-H & ${\Sigma}_{*}$-M & ${\Sigma}_{*}$-P \\ \hline
    $n$=20             & 0.82 & 0.84  & 0.87   & 0.90   & 0.91  & 0.89    & 0.93    & 0.89   \\
    $n$=50             & 0.80 & 0.81  & 0.87   & 0.88   & 0.88  & 0.88    & 0.92    & 0.88   \\
    $n$=100            & 0.68 & 0.71  & 0.80   & 0.85   & 0.91  & 0.82    & 0.86    & 0.92   \\
    $n$=300            & 0.61 & 0.63  & 0.82   & 0.85   & 0.93  & 0.86    & 0.91    & 0.96   \\
    $n$=500            & 0.60 & 0.64  & 0.77   & 0.80   & 0.90  & 0.82    & 0.86    & 0.96   \\ \hline
    \end{tabular}
\end{scriptsize}
\caption{Finite sample efficiencies of estimators of the first eigenvector based on 
several scatter matrices in dimension $p=4$. The notation
 H, M or P after $\tilde{\Sigma}$ or ${\Sigma}_{*}$ indicates the depth function 
 used for the weights: H = halfspace depth, M = Mahalanobis depth, P = projection depth.}
\label{table:FSEtable4}
\end{table}

\subsection{Influence function comparison}

%\begin{comment}

\begin{figure}[]
	\centering
		\includegraphics[width=0.8\textwidth]{./Plots/IFnorm.png}
	\caption{Plot of the norm of influence function for first eigenvector of (a) sample 
	covariance matrix, (b) SCM, (c) Tyler's scatter matrix and $\tilde{\Sigma}$ for 
	weights obtained from (d) Halfspace depth, (e) Mahalanobis depth, (f) Projection depth 
	for a bivariate normal distribution with $\bfmu = {\bf 0}, \Sigma = \diag(2,1)$}
	\label{fig:IFnorm}
\end{figure}

In Figure \ref{fig:IFnorm} we consider first eigenvectors of $\tilde{\Sigma}$, 
the Sign Covariance Matrix (SCM) 
and Tyler's shape matrix \citep{ref:AoS87234_Tyler}. We generate data from and set
$\BF \equiv \mathcal{N}_2({ 0}, \diag(2,1))$ and plot norms of the 
eigenvector influence functions for different values of $x_0$. 
Let us denote the $i$-th eigenvector of  the Sign Covariance Matrix and Tyler's shape 
matrix by  $\gamma_{S,i}$ and $\gamma_{T,i}$, respectively. 
Their influence functions are given  as follows:
%
\ban
 IF(x_0; \gamma_{S,i}, \BF) & = 
\sum_{k=1; k \neq i}^p \frac{\BS_{ik}(\Lambda^{1/2} z_0, { 0})}{\lambda_{S,i} - \lambda_{S,k}} \gamma_k; \\
%\quad 
& \text{ where }
\lambda_{S,i} = \BE_Z \left( \frac{\lambda_i z_i^2}{\sum_{j=1}^p \lambda_j z_j^2} \right),\\
IF(x_0; \gamma_{T,i}, \BF) & =  (p+2) \sum_{k=1; k \neq i}^p \frac{\sqrt{\lambda_i 
\lambda_k}}{\lambda_i - \lambda_k}\BS_{ik}(z_0; {0}) \gamma_k. 
%\label{eqn:IFeqnTyler}
\ean
%
Panels (b) and (c) in Figure~\ref{fig:IFnorm}, corresponding to  Sign Covariance Matrix 
and Tyler's shape matrix respectively, exhibit an `inlier effect', that is, 
points close to the center  having high influence,  which results in loss of efficiency. 
On the other hand, the influence function for eigenvector estimates of the 
sample covariance matrix  (panel (a)) is 
unbounded and makes the corresponding estimates non-robust. In comparison, the 
$\tilde{\Sigma}$ corresponding to weights derived from projection depth, 
half-space depth and Mahalanobis depth  have bounded influence functions {\it and} 
small values of the influence function at `deep' points.

\subsection{Efficiency of affine equivariant robust estimator}

We study the finite sample efficiency properties of $\Sigma_{*}$ 
using a simulation exercise. 
We consider 6 different elliptic distributions,  namely, the $p$-variate multivariate 
Normal distribution and the multivariate $t$ distributions corresponding to degrees 
of freedom 5, 6, 10, 15 and 25. We compute the ARE of the estimator for the 
first eigenvector using $\Sigma_{*}$, using weights based on the projection depth 
(PD) and the halfspace depth (HSD), thus this simulation is an illustration of how 
different choices of weights affect the results in the context of 
Theorem~\ref{Thm:Eigen2}.  We consider using the sample covariance 
matrix as the baseline method for this study. The ARE values are computed by
using Monte-Carlo simulation of $10^6$ samples and subsequent numerical integration.
We report the results of this exercise in Table~\ref{table:AREtable}.  
Based on these results, we notice that  $\Sigma_{*}$  is particularly efficient in lower 
dimensions for distributions with heavier tails ($t_5$ and $t_6$), while for distributions 
with lighter tails, the AREs increase with data dimension. At higher values of $p$,
note that $\Sigma_{*}$ is almost as efficient as the sample covarnace matrix even
 when the data comes from multivariate normal distribution.

\begin{table}[t]
\centering
\begin{footnotesize}
\begin{tabular}{c|cccc|cccc}
    \hline
    & \multicolumn{4}{c|}{PD} & \multicolumn{4}{c}{HSD} \\\cline{2-9}
    Distribution & $p=2$  & $p=5$  & $p=10$ & $p=20$ & $p=2$  & $p=5$  & $p=10$ & $p=20$ \\ \hline
    $t_5$           & 4.73 & 3.99 & 3.46 & 3.26 & 4.18 & 3.63 & 3.36 & 3.15 \\
    $t_6$           & 2.97 & 3.28 & 2.49 & 2.36 & 2.59 & 2.45 & 2.37 & 2.32 \\
    $t_{10}$          & 1.45 & 1.47 & 1.49 & 1.52 & 1.30 & 1.37 & 1.43 & 1.49 \\
    $t_{15}$          & 1.15 & 1.19 & 1.23 & 1.27 & 1.01 & 1.10 & 1.17 & 1.24 \\
    $t_{25}$          & 0.97 & 1.02 & 1.07 & 1.11 & 0.85 & 0.94 & 1.02 & 1.08 \\
    MVN          & 0.77 & 0.84 & 0.89 & 0.93 & 0.68 & 0.77 & 0.84 & 0.91 \\ 
    \hline
\end{tabular}
\end{footnotesize}
\caption{Table of AREs of the estimator for the first eigenvector estimation using 
$\Sigma_{*}$, relative to using the sample covariance matrix, for different choices of 
dimension $p$. The data-generating distributions are the multivariate Normal (MVN), 
and multivariate $t$-distributions with degrees of freedom 5, 6, 10, 15 and 25. Weights 
for $\Sigma_{*}$ are based on either the projection depth (PD) or the half-space 
depth (HSD).}
\label{table:AREtable}
\end{table}

%\end{comment}

\subsection{Robust sufficient dimension reduction and supervised learning}

One of the main usages of obtaining dispersion estimators and their eigenvalues and 
eigenvectors is in \textit{dimension reduction} techniques. Examples of such uses are in 
\textit{principal component regression, partial least squares} and \textit{envelope 
methods}. We illustrate below the latter technique, in the context of 
\textit{sufficient dimension reduction} (SDR). For details on envelope methods and other 
uses of robust estimators of dispersion and eigen-structures, see 
\citet{ref:Sinica10927_Cooketal, ref:PhilTransRoyalSoc094385_AdragniCook, 
ref:JASA15599_CookZhang} 
and references and citations of these 
articles. In the context of multivariate-response ($Y_{i} \in \BR^{q}$) linear regression, 
the envelope method proposes the model $Y_{i} = \alpha + \Gamma_{1} \eta x_{i} + e_{i}$, 
where $e_{i}$ are independent mean zero Gaussian  noise terms with covariance matrix 
$\Sigma$ whose spectral representation can be written as 
\ban 
\Sigma = \Gamma \Lambda \Gamma^{T}
& = 
\left( \begin{array}{ll}
\Gamma_{0} & \Gamma_{1} 
\end{array}
\right)
\left( \begin{array}{ll}
\Lambda_{0} & 0 \\
0 & \Lambda_{1} 
\end{array}
\right)
\left( \begin{array}{l}
\Gamma_{0} \\
\Gamma_{1} 
\end{array}
\right) \\
& = \Gamma_{0} \Lambda_{0} \Gamma_{0}^{T}
+ \Gamma_{1} \Lambda_{1} \Gamma_{1}^{T}.
\ean
Thus, the eigenvectors of $\Sigma$ are partitioned into two blocks:  
$\Gamma_{1} \in \BR^{q} \times \BR^{d}$ and 
$\Gamma_{0} \in \BR^{q} \times \BR^{q-d}$, and 
the regression coefficient of $Y_{i}$ on $x_{i}$  is given by 
$\Gamma_{1} \eta$ for some $\eta \in \BR^{d} \times \BR^{p}$. 
Dimension reduction is achieved  when $d \ll p$, typically without extraneous 
assumptions like sparsity. The envelope model for generalized linear models is 
discussed in \citet{ref:PhilTransRoyalSoc094385_AdragniCook}, 
and may be used for supervised 
learning. Nonlinear regression models may also be handled similarly.

Given a set of examples $\{ (Y_{i}, X_{i}), i = 1, \ldots, n \}$, an envelope-based 
prediction for the response $Y$ for any $X$ may be obtained from 
\ban
\hat{Y} (X) & = \bigl[ \sum_{i = 1}^{n} w_{i} \bigr]^{-1}
\sum_{i = 1}^{n} w_{i} Y_{i}, 
\text{ where } \\ 
 w_{i} &= \exp \left[ -\frac{1}{\hat\sigma^2}  | \hat\Gamma_{1}^T (X - X_i) |^2 \right].
\ean
The above assumes that the covariates come from the Gaussian distribution 
$N_{p} ({\bf 0}_{p}, \sigma^{2} \BI_{p})$, and appropriate 
changes may be made for other distributions.

We design a robust version of the above, by using weighted spatial medians for location 
parameters corresponding to the distributions of $X$ and $X | Y$, and using the first $d$ 
eigenvectors of $\tilde{\Sigma}$ as $\hat\Gamma_{1}$. A robust location estimator for 
the distribution of $X | Y$ is required for the estimation of $\sigma^2$. 
Details are available in \cite{ref:PhilTransRoyalSoc094385_AdragniCook}.

Ina non-linear regression model, we compare the performance of the robust version of 
SDR with the original method of 
\cite{ref:PhilTransRoyalSoc094385_AdragniCook} 
with or without the presence of bad leverage points in $\Sigma$. 
For any given choice of covariate dimension $p$, we take $n=200$ and $d=1$, 
and generate the responses 
$Y_1, \ldots, Y_n$ as independent standard normal, and 
$X | Y$ as Normal with mean $Y + Y^{2} + Y^3$ in each of the $p$ coordinates, 
and variance $25 \BI_p$.
We measure performances of the SDR models by their mean squared prediction error on 
another set of 200 observations  generated similarly, and taking the average of these 
errors on 100 such training-test pairs of datasets. The above steps 
are repeated for the choices of $p = 5, 10, 25, 50, 75, 100, 125, 150$.

%\begin{comment}
\begin{figure}[t]
%\captionsetup{justification=centering, font=footnotesize}
\begin{center}
\begin{tabular}{ll}
\includegraphics[width=0.4\textwidth]{./Plots/SDRcomparison_noout} &
\includegraphics[width=0.4\textwidth]{./Plots/SDRcomparison_out}
\end{tabular}
\caption{Average prediction errors for two methods of SDR (a) in absence and (b) in presence of outliers}
\label{fig:SDRfig}
\end{center}
\end{figure}
%\end{comment}

Panel (a) of figure \ref{fig:SDRfig} compares prediction errors using both robust and 
maximum likelihood SDR estimates when the covariates contain no outliers: here the two 
methods are virtually indistinguishable. We then introduce outliers in each of the 100 
datasets by adding 100 to first $p/5$ coordinates of the first 10 observed covariate 
values, and repeat the analysis. Panel (b) of the figure shows that the robust SDR method 
remains more accurate in predicting out of sample observations for all values of $p$ than 
the standard SDR.

### 2019-08-09 EJSSubmission/WeightedSign_EJS_WeightedSpatialQuantiles_02_24_19_1.tex
EJS revision

\section{Weighted Spatial Quantiles}
\label{Sec:WSQuantiles}

Suppose the open unit sphere in $\cX$ is given by 
$\textrm{int} {\cX}_{0; 1} = \{ x \in \cX: | x | < 1 \}$, and let
 $u \in \textrm{int} {\cX}_{0; 1}$. We also fix the set of probability measures $\cM$, 
 and select $\BF \in \cM$. Consider a random element $X \in \cX$. 
We define the $(u, \BF)$-th \textit{weighted spatial quantile} of $\cX$ 
as the minimizer $q (u, \BF) \in \cX$ of 
\baq
\Psi (q; u, \BF) = \BE \Bigl[ W (X, \BF) \bigl\{ | X - q | 
+ \langle u, X - q \rangle \bigr\} \Bigr].
\label{eq:WeightedQuantile}
\eaq
%
\rework{
This is a natural generalization of the spatial median \cite{ref:JASA96862_Chaudhuri, ref:Biometrika48414_Haldane,ref:AoS97435_Koltchinskii}, or more general spatial quantiles \cite{ref:AoS17591_Cardotetal_Median_HilbertSpace, ref:AoS141203_ChakrabortyChaudhuri_Banach_Quantile, ref:Bernoulli152308_Minsker_Median_Banach}. In what follows, for brevity we elaborate only the case of the \textit{weighted spatial median} (thus 
$\Psi (q; 0, \BF) = \BE \bigl[ W (X, \BF) | X - q | \bigr] $) for the case of finite dimensional $\cX$. Specifically, we demonstrate the utility of using the {\it weighted} spatial median as opposed to using the traditional, unweighted versions found in literature. The analysis and computation of the general weighted spatial quantiles will largely follow by extending the results of the above cited references, and we postpone details to a future study.
}

Assume that we have independent and identically distributed observations $X_{1}, \ldots, X_{n} \in \cX$, and the sample weighted spatial median is computed by minimizing $\Psi_{n} (q; 0, \BF) = \sum_{i = 1}^{n} \bigl[ W (X_{i}, \BF) | X_{i} - q | \bigr] $, and is denoted by $\hat{q}_{nW}$, the second subscript is in acknowledgement that the weight function is used. We denote the unweighted version of this estimator, ie, the case where $W (X, \BF) \equiv 1$ as $\hat{q}_{n}$. Assume the following technical conditions:

\begin{description}
\item[A1:] $\Psi (q; 0, \BF)$ is finite for all $q \in \cX \subseteq \BR^{p}$ 
and has a unique minimizer $q_{0}$.

 \item[A2:] $\Psi (q; 0, \BF)$ is twice differentiable at $q_{0}$ and the second 
 derivative is positive definite.

 \item[A3:] $\BE W^{2} (X, \BF)  S (X; q) S^{T} (X; q)$ exists for all 
 $q$ in a neighborhood of $q_{0}$. 
 \end{description}
 These assumptions are very broad-based and general. The first one essentially requires 
 the existence of a population parameter, the second one requires that the minimization 
 approach is meaningful in the population, and the third one essentially requires that the 
 weight function has a finite variance. No further restrictions are placed on the tuning parameter $\BF$ or the choice of the weight function.

 \begin{Theorem}
 \label{Thm:WSMedian}
 Under assumptions \textbf{[A1] - [A3]}, we have 
 \ban 
 n^{1/2} (\hat{q}_{nW} - q_{0}) & \draro N(0, \Psi_{2}^{-1} \Psi_{1}^{2} \Psi_{2}^{-1}), 
 \text{ where } \\
 \Psi_{2} & = 
 \BE W (X, \BF) \Bigl[  |X - q|^{-1} \BI_{p} - |X - q|^{-3/2} (X - q) (X - q)^{T}  \Bigr] 
 \\
 \Psi_{1}  & = n \BE   W^{2} (X, \BF)  \bfS (X; q_{0}) \bfS^{T} (X; q_{0}).
 \ean
 \end{Theorem}
Thus, under very standard regularity conditions, the sample weighted spatial median 
is consistent and is asymptotically normal.  
Theorem~\ref{Thm:WSMedian}  can be proved in several different ways. We have used 
techniques following \cite{ref:AoS891631_Haberman, ref:AoS921514_Niemiro}, 
we omit the details.

\subsection{Asymptotic efficiency of weighted spatial median}
Let $V_{W} = \Psi_{2}^{-1} \Psi_{1}^{2} \Psi_{2}^{-1}$ be the asymptotic 
variance of \hl{$\hat{q}_{n,W}$} from Theorem~\ref{Thm:WSMedian}, where we use the 
subscript ``${}_{W}$'' to denote that this depends on the weight function. 
We use the notation 
$V_{1}$ for the case where $W (x, \BF) \equiv 1$, that is, all weights are one.
The asymptotic relative efficiency of two statistics is the $p$-th root of 
the reciprocals of their determinants. That is, 
\ban 
ARE (\hat{q}_{nW}, \hat{q}_{n}) = \Bigl\{\frac{det(V_{1})}{det(V_{W})} \Bigr\}^{1/p}.
\ean
One easy result from Theorem~\ref{Thm:WSMedian} is that under reasonable conditions the
asymptotic relative efficiency of the weighted spatial median over the unweighted version
is always greater than one. We document this in the following corollary:

\begin{Corollary}
\label{Cor:ARE}
Assume that $|X - q_{0}|$ and $S (X; q_{0})$ are independent, and the weight function 
$W (X, \BF)$ is a function of  $|X - q_{0}|$. Then
\ban
& ARE (\hat{q}_{nW}, \hat{q}_{n}) \\
& = 
\Bigl[ \BE \bigg(  |X - q_{0}|^{-1} \bigg) \Bigr]^{-2}
\Bigl[ \BE W^{2} (X, \BF) \Bigr]^{-1}
\Bigl[ \BE \bigg(  |X - q_{0}|^{-1} W (X, \BF) \bigg) \Bigr]^{2}.
\ean
Consequently, if $W (X, \BF) = k   |X - q_{0}|^{-1}$ for some $k \in (0, 1]$, 
then this asymptotic relative efficiency is 
$ \{k^{-1} (\BE ||X - q_{0}|^{-1} )^{2} \BE |X - q_{0}|^{-2} \}^{1/p}> 1$. 
\end{Corollary}

It is possible to make the above asymptotic relative efficiency to tend to infinity with 
$p$, for example by choosing $k = \exp\{- p^{2} \}$. Such tending to infinity efficiencies 
are also achievable for fixed $k$,  for example, if $|X - q_{0}|^{2}$ is a Gamma random 
variable with shape parameter $ = 2 + \exp\{- p^{2} \}$. We leave it to future work to 
study such efficiencies more generally.

We may wish to further explore the conditions of Corollary~\ref{Cor:ARE}. 
Let us concentrate on the case of where the distribution of $X$ is 
elliptically symmetric. Following \cite{ref:Fangetal90_Book}:

\begin{Definition}
A $p$-dimensional random vector $X$ is said to elliptically distributed if 
there exist a vector $\mu \in \BR^p$, a positive semi-definite matrix 
$\Sigma \in \BR^{p \times p}$ and a function 
$\phi: (0, \infty) \rightarrow \BR$ such that the characteristic function 
of $X$ is $\exp \{ i t^{T} \mu \} \phi (\bft^T \Sigma \bft)$ for $\bft \in \BR^p$.
\end{Definition}

There are several alternative formulations, see the above reference and 
citations within it for details. 
%The spherically symmetric case is realized with $\Sigma = \sigma^{2} \BI_{p}$ for some 
%$\sigma^{2} > 0$. 
We fix the notation $Z = \Sigma^{-1/2} (X - \mu)$, and let 
$Z \sim \BF_{Z}$. Note that $\BF_{Z}$ is a spherically symmetric distribution and hence
depends only on $|z|$, and  $\BE Z = \mathbf{0}_{p} \in \BR^{p}$ and $\BV Z = \BI_{p}$.

\begin{Corollary}
\label{Cor:Elliptic_ARE}
Assume that the tuning parameter of the weight function, $\BF$, is  the 
distribution of $X$, and is an elliptically symmetric distribution, and $\mu = q_{0}$. 
Also assume that the weight function is affine invariant, that is:
\ban
W (A x + b, A \BF + b) = W (x, \BF),
\ean
Then  the weight function satisfies $W (X, \BF) = W (Z, \BF_{Z})$, and 
hence may be further restricted to be a function of $|Z|$. Then 
$S (X; q_{0})$ is uniform on the unit ball 
in $\BR^{p}$, and is independent of $|X - q_{0}|$, while 
$W (X, \BF)$ is a function of  $|X - q_{0}|$. That is, the conditions of 
Corollary~\ref{Cor:ARE} are satisfied. 
\end{Corollary}

Obtaining affine invariant weight functions is not challenging, in fact, most 
such functions arising in the context of data-depths are affine invariant. 
Corollary~\ref{Cor:Elliptic_ARE} implies that there is a wide frame of distributions and 
choices of weight functions where there is a benefit to considering weighted spatial 
quantiles. In actual computations, in place of $W (x, \BF)$ we propose 
using $W (x, \BF_{n})$ where 
$\BF_{n} = n^{-1} \sum_{i = 1}^{n} \cI (X_{i} \leq x )$ is the empirical distribution 
function. Up to first order asymptotics, the analysis remain unchanged from the above 
for this modified weight function.

\subsection{Examples of affine invariant weights}

We now illustrate some specific choices of weight functions that are compatible with the 
conditions of Corollary~\ref{Cor:Elliptic_ARE} and the results in the rest of this paper.
 These arise as easy transformations 
of \textit{data-depth functions}. A data depth function 
is defined on $\cX \times \cF$, where $\cF$ is  a fixed set of probability measures.
The main property of a data-depth function is that for every probability measure 
$\BF \in \cF$, there exists a constant 
$\mu_{\BF} \in  \cX$ such that for any $t \in [ 0, 1]$ and $x \in \cX$,
\baq 
D ( \mu_{\BF} ; \BF ) \geq D ( \mu_{\BF} + t ( \bfx - \mu_{\BF} ); \BF ). 
\label{eq:Peripherality}
\eaq
That is, for every fixed $\BF$, the data-depth function achieves a supremum at 
$\mu_{F}$, and is non-decreasing in every direction away from $\mu_{F}$, thus providing 
a  center-outward partial ordering of points in $\cX$. There are generally several 
algebraic and analytic properties assumed for data-depth functions to elicit interesting 
mathematical properties, see for example 
\cite{ref:AoS00461_ZuoSerfling, ref:DIMACS061_Serfling} 
for details.

It is easy to show that results in this paper are valid for the weight functions
($i$) $W_{HSD} (X) = \BF_{Z} (| Z |)$ derived from the \textit{half-space depth},  
($ii$) $W_{MhD} (X) = |Z|^{2}/(1 + | Z |^2)$ derived from the \textit{Mahalanobis depth}, 
and  
($iii$) $W_{PD} (X) = |Z|/(1+ | Z |/MAD(\BF_{Z}))$, where $MAD$ stands for median 
absolute deviation, derived from the \textit{projection depth}. We omit the technical 
details. These three weight functions a center-inward partial ordering, thus essentially 
quantifying \textit{peripherality} instead of \textit{depth}.
Note however, that our results below are of much more general form, and 
these three special choices of weights only serve as important illustrative examples 
to achieve desirable robustness and efficiency balance in data analysis.

### 2019-08-09 EJSSubmission/arxiv/arxiv-conc.tex
EJS revision

--- 2019-08-09 EJSSubmission/WeightedSign_EJS_Conclusion_02_24_19_1.tex
@@
 simulation studies and data examples, in many situations using a data-depth driven weight 
-function leads to considerable efficiency gain without compromising robustness 
+function leads to considerable efficiency gain without compromising on robustness 
 properties. Our methodology seems to suggest new ways of identifying 

### 2019-08-09 EJSSubmission/arxiv/arxiv-da.tex
EJS revision

--- 2019-08-09 EJSSubmission/WeightedSIgn_EJS_DA_02_24_19_1.tex
@@
 
-We  now present an application of our proposed approach to some real data problems.
-
-Robust techniques are useful when in identifying outlying observations, and we illustrate 
-below how to make use of our fixed-dimensional methods presented earlier for 
-functional (and hence infinite-dimensional)  data.
+We now present application of our proposed approach to some real data problems.
+Robust techniques are useful when in identifying outlying observations, and we illustrate below how to make use of our fixed-dimensional methods presented earlier for functional (and hence infinite-dimensional)  data.
 
@@
 %
-We then model  the $i$-th row of the $n \times p$ matrix $T(\cF, \cD) \equiv T$, 
-denoted by $\bfT_{i}$ 
+We then model  the $i$-th row of the $n \times p$ matrix $T(\cF, \cD) \equiv \bfT$, 
+denoted by $T_{i}$ 
 as follows:
 \ban 
-\bfT_i = \mu + P s_i + e_{i},
+T_i = \mu + P s_i + e_{i},
 \ean
@@
 $\mu$, $P$ and consequently $s_{i}$ using $\widehat{\tilde{\Sigma}}$. Define 
-$\widehat{\bfT}_{i} = \hat{\mu} + \hat{P} \hat{s}_{i}$. 
+$\widehat{T}_{i} = \hat{\mu} + \hat{P} \hat{s}_{i}$. 
 The \textit{orthogonal distance} (OD)  corresponding to this projection is defined as 
 \ban 
-OD_{i} = | \bfT_i - \widehat{\bfT}_{i} |.
+OD_{i} = | T_i - \widehat{T}_{i} |.
 \ean
@@
 \begin{center}
-\begin{tabular}{ll}
-\includegraphics[width=0.4\textwidth]{./Plots/Elnino_functional1} &
-\includegraphics[width=0.4\textwidth]{./Plots/Octane_functional1}\\
-\includegraphics[width=0.4\textwidth]{./Plots/Elnino_functional2} &
-\includegraphics[width=0.4\textwidth]{./Plots/Octane_functional2}\\
-\includegraphics[width=0.4\textwidth]{./Plots/Elnino_functional3} &
-\includegraphics[width=0.4\textwidth]{./Plots/Octane_functional3}\\
-\end{tabular}
+\includegraphics[width=0.9\textwidth]{plot2}
 \caption{Actual sample curves, their spline approximations and diagnostic plots respectively for El-Ni\~no (a,c,e) and Octane (b,d,f) datasets}
@@
 
-On the octane data, we use the same methodology, 
- and again the top robust PC turns out to be sufficient in identifying all 6 outliers. 
+On the octane data, we use the same methodology,  and again the top robust PC turns out to be sufficient in identifying all 6 outliers.
 Details are available in  panels (b), (d) and (f) of Figure~\ref{fig:fPCAfig}.

### 2019-08-09 EJSSubmission/arxiv/arxiv-disp.tex
EJS revision

--- 2019-08-09 EJSSubmission/WeightedSign_EJS_Dispersion_02_24_19_1.tex
@@
 and consequently use  $W (x, \BF_{n})$ instead. We assume the following conditions:
-\begin{enumerate}
-\item \textbf{Bounded weights:} The weights $W (\cdot, \cdot)$ are bounded functions.
 
-\item \textbf{Uniform convergence:} 
+\vspace{1em}
+\noindent\textbf{(B1) Bounded weights:} The weights $W (\cdot, \cdot)$ are bounded functions.
+
+\noindent\textbf{(B2) Uniform convergence:} 
 \ban 
@@
 
-\item \textbf{Smoothness under perturbation:}
+\noindent\textbf{(B3) Smoothness under perturbation:}
 For all $\BF \in \cF$, there exists a $\delta > 0$, possibly depending on $\BF$, such that 
@@
 \ean
- \end{enumerate}
- In the above, $\delta_{x}$ denotes point mass at $x$. 
-These property are easily satisfied under for  weight functions  derived 
-from standard depth functions, for example, $W_{HSD} (\cdot)$, 
-$W_{MhD} (\cdot)$ and $W_{PD} (\cdot)$ discussed earlier.
+
+\vspace{1em}
+\noindent In the above, $\delta_{x}$ denotes point mass at $x$.
+These properties are easily satisfied under for weight functions derived from standard depth functions, for example, $W_{HSD} (\cdot)$, $W_{MhD} (\cdot)$ and $W_{PD} (\cdot)$ discussed earlier.
 
@@
 %
-where for any $c \in \BR^{p}$ such that $| c | = $, we have 
+where for any $c \in \BR^{p}$ such that $| c | = 1$, we have 
 $\BE  c^{T} R_{n} c = o (n^{-1})$.
@@
 
-Let $vec~(\BS (X; \mu))$ be the vectorized version of  $\BS (X; \mu)$.
+Let $vec(\BS (X; \mu))$ be the vectorized version of  $\BS (X; \mu)$.
 We are now in a position to state the result for consistency of the sample 
@@
 ${\Lambda}^{\dagger} = \diag ({\lambda}^{\dagger}_{1}, \ldots, 
-{\lambda}^{\dagger}_{p})$.
-The number of subgroups used to calculate this median-of-small-variances estimator can 
-be determined following \cite{ref:Bernoulli152308_Minsker_Median_Banach}. 
-There can be other ways of estimating 
-the eigenvalues of $\Sigma$ using $\bfS$ also, we will pursue such methods elsewhere.
-We construct a consistent 
-plug-in estimator of the population covariance matrix $\Sigma$ as 
+{\lambda}^{\dagger}_{p})$. The number of subgroups used to calculate this median-of-small-variances estimator can be determined following \cite{ref:Bernoulli152308_Minsker_Median_Banach}. 
+There can be other ways of estimating the eigenvalues of $\Sigma$ using $\bfS$ also, we will pursue such methods elsewhere.
+Finally we construct a consistent plug-in estimator of the population covariance matrix $\Sigma$ as
 \ban 
@@
 \ean
-Let $| A |_{F}$ denote the Frobenius norm of a matrix $A$, in other words,
-$| A |_{F} = (\text{trace} A^{T} A)^{1/2}$.
-The following result establishes that this is a consistent estimator of $\Sigma$:
+Let $| A |_{F}$ denote the Frobenius norm of a matrix $A$, in other words, $| A |_{F} = (\text{trace} A^{T} A)^{1/2}$. The following result establishes that this is a consistent estimator of $\Sigma$:
 

### 2019-08-09 EJSSubmission/arxiv/arxiv-if.tex
EJS revision

--- 2019-08-09 EJSSubmission/WeightedSign_EJS_IF_02_24_19_1.tex
@@
 $\BH_\epsilon = (1-\epsilon)\BH + \epsilon \delta_{x_0}$; $\delta_{x_0}$ being 
-the distribution with point mass at $x_0$. When $T(\BH) = E_\BH f$ for some 
+the distribution with point mass at $x_0$. When $T(\BH) = \BE_\BH f$ for some 
 $\BH$-integrable function $f$, $IF(x_0; T,\BH) = f(x_0) - T(\BH)$.
@@
 \ean
-From Lemma1 of \citep{ref:HampelBook86}, page 276, we obtain that there exist 
+From Lemma 1 of \citep{ref:HampelBook86}, page 276, we obtain that there exist 
 scalar valued functions $\alpha_{\Sigma_{*}} ( | x_{0} |; \BF_{Z} )$ and 
@@
 \ean
-consequently we obtain
+consequently
 \ban 
@@
 
-Suppose ${\lambda}_{* 1} > {\lambda}_{* 2} > \ldots > {\lambda}_{* p}$
-are the eigenvalues of ${\Sigma}_{*}$, which we assume are all distinct values. 
-Also denote the $i$-th eigenvector of $\Sigma_{*}$ by 
-$\bfgamma_{* i} = (\gamma_{* i 1}, \ldots, \gamma_{* i p})^T$ for $1 \leq i \leq p$.
+Suppose ${\lambda}_{* 1} > {\lambda}_{* 2} > \ldots > {\lambda}_{* p}$ are the eigenvalues of ${\Sigma}_{*}$, which we assume are all distinct.
+Also denote the $i$-th eigenvector of $\Sigma_{*}$ by $\bfgamma_{* i} = (\gamma_{* i 1}, \ldots, \gamma_{* i p})^T$ for $1 \leq i \leq p$.
 
@@
 to rest of the computations of this section.
-It can be shown that when $W (\cdot)$ is a bounded function, 
-$\alpha_{\Sigma_{*}} ( | x_{0} |; \BF_{Z} )$ is also bounded, along the lines of 
-\cite{ref:HuberBook81}, which in turn implies that the influence function for a 
-principal component based on $\Sigma_{*}$ is also bounded.
+It can be shown that when $W (\cdot)$ is a bounded function, $\alpha_{\Sigma_{*}} ( | x_{0} |; \BF_{Z} )$ is also bounded, along the lines of \cite{ref:HuberBook81}, which in turn implies that the influence function for a principal component based on $\Sigma_{*}$ is bounded as well.

### 2019-08-09 EJSSubmission/arxiv/arxiv-intro.tex
EJS revision

--- 2019-08-09 EJSSubmission/WeightedSign_EJS_Introduction_02_24_19_1.tex
@@
 
+\begin{figure}[t]
+%\captionsetup{justification=centering, font=footnotesize}
+\begin{center}
+%%% These ones have sample size = 700, just right  for EJS
+\includegraphics[width=0.8\textwidth]{plot1}
+\caption{
+An illustrative bivariate scatter plot in the top left panel where the outliers are 
+identified with red circles, 
+and generalized signs from the same data (black points on the 
+unit radius circle, outliers are red points) in the other panels. 
+In the top right (bottom left, bottom right) 
+panel, weighted signs from the same data with weights obtained using Mahalanobis depth 
+(Tukey depth, projection depth respectively) are presented as green triangles 
+(outliers are identified by blue triangles). 
+}
+\label{fig:Fig1}
+\end{center}
+\end{figure}
+
 In this paper, we propose to alleviate this low efficiency problem, by associating 
@@
  can lead to interesting robustness and efficiency trade-offs in a variety of situations. 
- The various technical conditions and assumptions that we impose on the 
+ The various technical conditions and assumptions we impose on the 
  weight function $W( x, \BF)$ are valid for weights derived 
@@
 
- %\begin{comment}
-\begin{figure}[t]
-%\captionsetup{justification=centering, font=footnotesize}
-\begin{center}
-\begin{tabular}{ll}
-%%% These ones have sample size = 700, just right  for EJS
-\includegraphics[width=0.45\textwidth]{./Plots_SC/WeightedSign_Scatter_700_02_27_19} &
-\includegraphics[width=0.45\textwidth]{./Plots_SC/WeightedSign_MD_700_02_27_19} \\
-\includegraphics[width=0.45\textwidth]{./Plots_SC/WeightedSign_TD_700_02_27_19} &
-\includegraphics[width=0.45\textwidth]{./Plots_SC/WeightedSign_PD_700_02_27_19} \\
-
-%%% These ones have sample size = 300, OK but too small file for EJS
-%\includegraphics[width=0.45\textwidth]{../Plots_SC/WeightedSign_Scatter_02_27_19} &
-%\includegraphics[width=0.45\textwidth]{../Plots_SC/WeightedSign_MD_02_27_19} \\
-%\includegraphics[width=0.45\textwidth]{../Plots_SC/WeightedSign_TD_02_27_19} &
-%\includegraphics[width=0.45\textwidth]{../Plots_SC/WeightedSign_PD_02_27_19} \\
-
-%%% These ones have sample size = 1e3, too large file for EJS
-%\includegraphics[width=0.45\textwidth]{../Plots_SC/WeightedSign_Scatter_02_24_19} &
-%\includegraphics[width=0.45\textwidth]{../Plots_SC/WeightedSign_MD_02_24_19} \\
-%\includegraphics[width=0.45\textwidth]{../Plots_SC/WeightedSign_TD_02_24_19} &
-%\includegraphics[width=0.45\textwidth]{../Plots_SC/WeightedSign_PD_02_24_19} \\
-\end{tabular}
-\caption{
-An illustrative bivariate scatter plot in the top left panel where the outliers are 
-identified with red circles, 
-and generalized signs from the same data (black points on the 
-unit radius circle, outliers are red points) in the other panels. 
-In the top right (bottom left, bottom right) 
-panel, weighted signs from the same data with weights obtained using Mahalanobis depth 
-(Tukey depth, projection depth respectively) are presented as green triangles 
-(outliers are identified by blue triangles). 
-}
-\label{fig:Fig1}
-\end{center}
-\end{figure}
-%\end{comment}
-
 We primarily focus on the task of \textit{robust dispersion/scatter estimation} and 
-\textit{robust principal component analysis} in this paper.
-Figure~\ref{fig:Fig1} presents an illustrative example of bivariate data with outliers in the top left panel, where the outliers are marked with red points.
-In the
+\textit{robust principal component analysis} in 
+this paper. Figure~\ref{fig:Fig1} presents an illustrative example of bivariate data with 
+outliers in the top left panel, where the outliers are marked with red points. In the 
 other panels, the generalized sign values of the same data are presented as black points 
@@
 
-\rework{
-There are two unknown quantities in the generalized sign function as defined in \eqref{eq:GSign}: $\mu$ and $\BF$, To estimate dispersion and its eigen-structure robustly, we must start with a robust estimator for $\mu$.
-In Section~\ref{Sec:WSQuantiles} we present the case for \textit{weighted spatial quantiles}, which can be defined and studied in very general spaces
-$\cX$.
-One special case of this is the {\it weighted spatial median}.
-As a location estimator, it has several interesting robustness properties and can be shown to be more efficient that some existing robust location estimators, thus making it a perfect candidate to estimate $\mu$.
-On the other hand, setting $\BF$ as $\BF_X$, i.e.
-the distribution of $X$ has the clear interpretation of differentially weighting observations based on their inlyingness to the overall data distribution.
-This mirrors the context of how data depth has been used in the literature (refs).
-Due to this reason, except for two results in Section~\ref{Sec:WSQuantiles} (Theorem~\ref{Thm:WSMedian} and Corollary~\ref{Cor:ARE}) we assume $\BF \equiv \BF_X$ for the rest of the paper.
-However, other choices of $\BF$ may lead to interesting interpretations of $W(.
-,\BF)$ and the resulting quantities, e.g.
-(ref), and can potentially be explored further.
-}
+To estimate dispersion and its eigen-structure robustly, we must start with a 
+robust location 
+estimator. Consequently in Section~\ref{Sec:WSQuantiles} we present the case for 
+\textit{weighted spatial quantiles}, one special case of which is the weighted spatial 
+median. The weighted spatial quantiles can be defined and studied in very general spaces 
+$\cX$. The \textit{weighted spatial median}, as a location estimator, 
+has several interesting robustness properties and can be 
+shown to be more efficient that some existing robust location estimators.
 
-Following that, we restrict to the $\BR^{p}$ for fixed $p$, and present detailed 
+Following that, we restrict $\cX$ to the $\BR^{p}$ for fixed $p$, and present detailed 
 discussions on our primary proposal for a  robust measure of dispersion in 

### 2019-08-09 EJSSubmission/arxiv/arxiv-sim.tex
EJS revision

--- 2019-08-09 EJSSubmission/WeightedSign_EJS_Simulations_02_24_19_1.tex
@@
 
-We report numerical simulation studies on several properties relating to 
-$\tilde{\Sigma}$ and  $\Sigma_{*}$, and their eigenvalues and eigenvectors, 
-on datasets with or without influential points, to illustrate the finite sample 
-efficiency and robustness properties of the proposed weighted estimators. We compare 
-these proposed estimators with techniques that exists in literature, specifically, 
-the Sign Covariance Matrix (SCM) and Tyler's shape matrix \citep{ref:AoS87234_Tyler}.
+We report numerical simulation studies on several properties relating to $\tilde{\Sigma}$ and  $\Sigma_{*}$, and their eigenvalues and eigenvectors, on datasets with or without influential points, to illustrate the finite sample efficiency and robustness properties of the proposed weighted estimators.
+We compare these proposed estimators with techniques that exists in literature, specifically, the Sign Covariance Matrix (SCM) and Tyler's shape matrix \citep{ref:AoS87234_Tyler}.
 
@@
 
-We compare the performance of $\tilde{\Sigma}$ and $\Sigma_{*}$ with that of the 
-SCM and Tyler's scatter matrix. For this study, we fix the dimension $p = 4$.
-We consider six elliptical distributions, 
-and from every distribution draw 10000 samples each for sample sizes $n = 20, 50, 100, 
-300$ and $500$. All distributions are centered at ${\bf 0}_p$, and have covariance matrix 
-$\Sigma = \diag(4, 3, 2, 1)$.
+For this study, we fix the dimension $p = 4$.
+We consider six elliptical distributions, and from every distribution draw 10000 samples each for sample sizes $n = 20, 50, 100, 300$ and $500$.
+All distributions are centered at ${\bf 0}_p$, and have covariance matrix $\Sigma = \diag(4, 3, 2, 1)$.
 
-We use the concept of principal angles 
-\citep{ref:LinearAlgebraApplications9281_MiaoBenIsrael} 
-to find out error estimates for the 
-first eigenvector of a scatter matrix. In our case, the first eigenvector is
+We use the concept of principal angles \citep{ref:LinearAlgebraApplications9281_MiaoBenIsrael} 
+to find out error estimates for the first eigenvector of a scatter matrix. In our case, the first eigenvector is
 %
@@
 $m$-th replication, $m = 1, \ldots, 10,000$. 
-The finite sample efficiency of $\tilde\bfgamma_{1}$ relative to that 
+The finite sample efficiency (FSE) of $\tilde\bfgamma_{1}$ relative to that 
 from the sample covariance matrix, i.e. $\hat\bfgamma_{1}$ is obtained as:
@@
 The results from this simulation exercise are presented in Table~\ref{table:FSEtable4}.
-It can be seem that  $\tilde{\Sigma}$-based estimators (columns 3-5) 
+It can be seen that  $\tilde{\Sigma}$-based estimators (columns 3-5) 
 outperform SCM and Tyler's $M$-estimator of scatter. Among the 3 depth functions 
@@
 \begin{table}[t]
+\begin{center}
 \begin{scriptsize}
@@
 \label{table:FSEtable4}
+\end{center}
 \end{table}
@@
 
-%\begin{comment}
-
-\begin{figure}[]
+\begin{figure}[t]
 	\centering
-		\includegraphics[width=0.8\textwidth]{./Plots/IFnorm.png}
+		\includegraphics[width=0.9\textwidth]{IFnorm}
 	\caption{Plot of the norm of influence function for first eigenvector of (a) sample 
@@
 
-%\end{comment}
+\subsection{Robust sufficient dimension reduction and supervised learning}
 
-\subsection{Robust sufficient dimension reduction and supervised learning}
+\begin{figure}[t]
+\begin{center}
+\includegraphics[width=0.4\textwidth]{SDRcomparison_noout}
+\includegraphics[width=0.4\textwidth]{SDRcomparison_out}
+\caption{Average prediction errors for two methods of SDR (a) in absence and (b) in presence of outliers}
+\label{fig:SDRfig}
+\end{center}
+\end{figure}
 
@@
 
-Ina non-linear regression model, we compare the performance of the robust version of 
+In a non-linear regression model, we compare the performance of the robust version of 
 SDR with the original method of 
@@
 
-%\begin{comment}
-\begin{figure}[t]
-%\captionsetup{justification=centering, font=footnotesize}
-\begin{center}
-\begin{tabular}{ll}
-\includegraphics[width=0.4\textwidth]{./Plots/SDRcomparison_noout} &
-\includegraphics[width=0.4\textwidth]{./Plots/SDRcomparison_out}
-\end{tabular}
-\caption{Average prediction errors for two methods of SDR (a) in absence and (b) in presence of outliers}
-\label{fig:SDRfig}
-\end{center}
-\end{figure}
-%\end{comment}
-
 Panel (a) of figure \ref{fig:SDRfig} compares prediction errors using both robust and 
@@
 datasets by adding 100 to first $p/5$ coordinates of the first 10 observed covariate 
-values, and repeat the analysis. Panel (b) of the figure shows that the robust SDR method 
-remains more accurate in predicting out of sample observations for all values of $p$ than 
+values, and repeat the analysis. Panel (b) of the figure shows that in this case, the robust SDR method remains more accurate in predicting out of sample observations for all values of $p$ than 
 the standard SDR.

### 2019-08-09 EJSSubmission/arxiv/arxiv-spq.tex
EJS revision

--- 2019-08-09 EJSSubmission/WeightedSign_EJS_WeightedSpatialQuantiles_02_24_19_1.tex
@@
 \eaq
-%
-\rework{
-This is a natural generalization of the spatial median \cite{ref:JASA96862_Chaudhuri, ref:Biometrika48414_Haldane,ref:AoS97435_Koltchinskii}, or more general spatial quantiles \cite{ref:AoS17591_Cardotetal_Median_HilbertSpace, ref:AoS141203_ChakrabortyChaudhuri_Banach_Quantile, ref:Bernoulli152308_Minsker_Median_Banach}.
-In what follows, for brevity we elaborate only the case of the \textit{weighted spatial median} (thus
-$\Psi (q; 0, \BF) = \BE \bigl[ W (X, \BF) | X - q | \bigr] $) for the case of finite dimensional $\cX$.
-Specifically, we demonstrate the utility of using the {\it weighted} spatial median as opposed to using the traditional, unweighted versions found in literature.
-The analysis and computation of the general weighted spatial quantiles will largely follow by extending the results of the above cited references, and we postpone details to a future study.
-}
+This is a natural generalization of the spatial median or more general quantiles 
+studied in 
+\cite{ref:Biometrika48414_Haldane, ref:JASA96862_Chaudhuri, 
+ref:AoS97435_Koltchinskii}, \\
+\cite{ref:AoS141203_ChakrabortyChaudhuri_Banach_Quantile,
+ref:Bernoulli152308_Minsker_Median_Banach, ref:AoS17591_Cardotetal_Median_HilbertSpace}.
+The  analysis and computation of this weighted spatial quantile will largely follow by 
+extending the results of
+the above cited references, and we postpone details to a future study.
 
-Assume that we have independent and identically distributed observations $X_{1}, \ldots, X_{n} \in \cX$, and the sample weighted spatial median is computed by minimizing $\Psi_{n} (q; 0, \BF) = \sum_{i = 1}^{n} \bigl[ W (X_{i}, \BF) | X_{i} - q | \bigr] $, and is denoted by $\hat{q}_{nW}$, the second subscript is in acknowledgement that the weight function is used.
-We denote the unweighted version of this estimator, ie, the case where $W (X, \BF) \equiv 1$ as $\hat{q}_{n}$.
-Assume the following technical conditions:
+Below,  we  demonstrate the utility of using the 
+\textit{weighted spatial quantiles} as opposed to using the traditional, 
+unweighted versions found in literature, for the case of finite dimensional $\cX$. 
+We report only the case of the \textit{weighted spatial median} for brevity, thus 
+$\Psi (q; 0, \BF) = \BE \bigl[ W (X, \BF) | X - q | \bigr] $ for now.
+Assume that we have independent and identically distributed observations 
+$X_{1}, \ldots, X_{n} \in \cX$, and the sample weighted spatial median is computed by 
+minimizing $\Psi_{n} (q; 0, \BF) = \sum_{i = 1}^{n} \bigl[ W (X_{i}, \BF) | X_{i} - q | \bigr] $. We denote it by $\hat{q}_{nW}$, the second subscript being in acknowledgement that the weight 
+function is used. We denote the unweighted version of this estimator, ie, the case where 
+$W (X, \BF) \equiv 1$ as $\hat{q}_{n}$.
 
-\begin{description}
-\item[A1:] $\Psi (q; 0, \BF)$ is finite for all $q \in \cX \subseteq \BR^{p}$ 
+Now let us assume the following technical conditions:
+
+\vspace{1em}
+\noindent\textbf{(A1)} $\Psi (q; 0, \BF)$ is finite for all $q \in \cX \subseteq \BR^{p}$ 
 and has a unique minimizer $q_{0}$.
 
- \item[A2:] $\Psi (q; 0, \BF)$ is twice differentiable at $q_{0}$ and the second 
+\noindent\textbf{(A2)} $\Psi (q; 0, \BF)$ is twice differentiable at $q_{0}$ and the second 
  derivative is positive definite.
 
- \item[A3:] $\BE W^{2} (X, \BF)  S (X; q) S^{T} (X; q)$ exists for all 
- $q$ in a neighborhood of $q_{0}$. 
- \end{description}
- These assumptions are very broad-based and general. The first one essentially requires 
- the existence of a population parameter, the second one requires that the minimization 
- approach is meaningful in the population, and the third one essentially requires that the 
- weight function has a finite variance. No further restrictions are placed on the tuning parameter $\BF$ or the choice of the weight function.
+\noindent\textbf{(A3)} $\BE W^{2} (X, \BF)  \bfS (X; q) \bfS^{T} (X; q)$ exists for all  $q$ in a neighborhood of $q_{0}$.
+
+\vspace{1em}
+%
+\noindent These assumptions are very broad-based and general.
+The first one essentially requires the existence of a population parameter, the second one requires that the minimization approach is meaningful in the population, and the third one essentially requires that the weight function has a finite variance.
+No further restrictions are placed on the distribution $\BF$ or the choice of the weight function.
 
@@
  \label{Thm:WSMedian}
- Under assumptions \textbf{[A1] - [A3]}, we have 
+ Under assumptions (A1)--(A3), we have 
  \ban 
@@
 
-\subsection{Asymptotic efficiency of weighted spatial median}
 Let $V_{W} = \Psi_{2}^{-1} \Psi_{1}^{2} \Psi_{2}^{-1}$ be the asymptotic 
-variance of \hl{$\hat{q}_{n,W}$} from Theorem~\ref{Thm:WSMedian}, where we use the 
+variance of $\hat{q}_{n}$ from Theorem~\ref{Thm:WSMedian}, where we use the 
 subscript ``${}_{W}$'' to denote that this depends on the weight function. 
@@
 
-\begin{Corollary}
-\label{Cor:ARE}
+\begin{Corollary}\label{Cor:ARE}
 Assume that $|X - q_{0}|$ and $S (X; q_{0})$ are independent, and the weight function 
@@
 
-There are several alternative formulations, see the above reference and 
-citations within it for details. 
-%The spherically symmetric case is realized with $\Sigma = \sigma^{2} \BI_{p}$ for some 
-%$\sigma^{2} > 0$. 
-We fix the notation $Z = \Sigma^{-1/2} (X - \mu)$, and let 
-$Z \sim \BF_{Z}$. Note that $\BF_{Z}$ is a spherically symmetric distribution and hence
+There are several alternative formulations for elliptically symmetric distributions, see the above reference and citations within it for details.
+We fix the notation $Z = \Sigma^{-1/2} (X - \mu)$, and let $Z \sim \BF_{Z}$.
+Note that $\BF_{Z}$ is a spherically symmetric distribution and hence
 depends only on $|z|$, and  $\BE Z = \mathbf{0}_{p} \in \BR^{p}$ and $\BV Z = \BI_{p}$.
 
-\begin{Corollary}
-\label{Cor:Elliptic_ARE}
-Assume that the tuning parameter of the weight function, $\BF$, is  the 
-distribution of $X$, and is an elliptically symmetric distribution, and $\mu = q_{0}$. 
-Also assume that the weight function is affine invariant, that is:
+\begin{Corollary}\label{Cor:Elliptic_ARE}
+Assume that $\BF$ is the distribution of $X$, and is an elliptically symmetric distribution, and $\mu = q_{0}$. Also assume that the weight function is affine invariant, that is:
 \ban
@@
 absolute deviation, derived from the \textit{projection depth}. We omit the technical 
-details. These three weight functions a center-inward partial ordering, thus essentially 
+details. These three weight functions give a center-inward partial ordering, thus essentially 
 quantifying \textit{peripherality} instead of \textit{depth}.
-Note however, that our results below are of much more general form, and 
-these three special choices of weights only serve as important illustrative examples 
-to achieve desirable robustness and efficiency balance in data analysis.
+Note however, that our results below are of much more general form, and these three special choices of weights only serve as important illustrative examples to achieve desirable robustness and efficiency balance in data analysis.

### 2019-08-09 EJSSubmission/WeightedSign_EJS_Introduction_02_24_19_1.tex
EJS revision commit 080919

@@
 This mirrors the context of how data depth has been used in the literature (refs).
-Due to this reason, except for two results in Section~\ref{Sec:WSQuantiles} (Theorem~\ref{Thm:WSMedian} and Corollary~\ref{Cor:ARE}) we assume $\BF \equiv \BF_X$ for the rest of the paper.
+Due to this reason, except for the first result in Section~\ref{Sec:WSQuantiles} (Theorem~\ref{Thm:WSMedian}) we assume $\BF \equiv \BF_X$ for the rest of the paper.
 However, other choices of $\BF$ may lead to interesting interpretations of $W(.

### 2019-08-09 EJSSubmission/WeightedSign_EJS_WeightedSpatialQuantiles_02_24_19_1.tex
EJS revision commit 080919

@@
 %
-\rework{
-This is a natural generalization of the spatial median \cite{ref:JASA96862_Chaudhuri, ref:Biometrika48414_Haldane,ref:AoS97435_Koltchinskii}, or more general spatial quantiles \cite{ref:AoS17591_Cardotetal_Median_HilbertSpace, ref:AoS141203_ChakrabortyChaudhuri_Banach_Quantile, ref:Bernoulli152308_Minsker_Median_Banach}.
-In what follows, for brevity we elaborate only the case of the \textit{weighted spatial median} (thus
-$\Psi (q; 0, \BF) = \BE \bigl[ W (X, \BF) | X - q | \bigr] $) for the case of finite dimensional $\cX$.
+%\rework{
+\noindent
+This is a natural generalization of the spatial median \cite{ref:JASA96862_Chaudhuri, ref:Biometrika48414_Haldane,ref:AoS97435_Koltchinskii} ($W(X, \BF) \equiv 1$ and $u = {\bf 0}_p$), or more general spatial quantiles \cite{ref:AoS17591_Cardotetal_Median_HilbertSpace, ref:AoS141203_ChakrabortyChaudhuri_Banach_Quantile, ref:Bernoulli152308_Minsker_Median_Banach} ($W(X, \BF) \equiv 1$).
+
+In what follows, for brevity we elaborate only the case of the \textit{weighted spatial median} (thus $\Psi (q; 0, \BF) = \BE \bigl[ W (X, \BF) | X - q | \bigr] $) for the case of finite dimensional $\cX$.
 Specifically, we demonstrate the utility of using the {\it weighted} spatial median as opposed to using the traditional, unweighted versions found in literature.
 The analysis and computation of the general weighted spatial quantiles will largely follow by extending the results of the above cited references, and we postpone details to a future study.
-}
+%}
 
-Assume that we have independent and identically distributed observations $X_{1}, \ldots, X_{n} \in \cX$, and the sample weighted spatial median is computed by minimizing $\Psi_{n} (q; 0, \BF) = \sum_{i = 1}^{n} \bigl[ W (X_{i}, \BF) | X_{i} - q | \bigr] $, and is denoted by $\hat{q}_{nW}$, the second subscript is in acknowledgement that the weight function is used.
+Assume that we have independent and identically distributed observations $X_{1}, \ldots, X_{n} \in \cX$, and the sample weighted spatial median is computed by minimizing $\Psi_{n} (q; 0, \BF) = \sum_{i = 1}^{n} W (X_{i}, \BF) | X_{i} - q | $, and is denoted by $\hat{q}_{nW}$, the second subscript is in acknowledgement that the weight function is used.
 We denote the unweighted version of this estimator, ie, the case where $W (X, \BF) \equiv 1$ as $\hat{q}_{n}$.
@@
  \label{Thm:WSMedian}
- Under assumptions \textbf{[A1] - [A3]}, we have 
+ Under assumptions [A1]-[A3], we have 
  \ban 
@@
  \Psi_{2} & = 
- \BE W (X, \BF) \Bigl[  |X - q|^{-1} \BI_{p} - |X - q|^{-3/2} (X - q) (X - q)^{T}  \Bigr] 
+ \BE W (X, \BF)\Bigl[  |X - q|^{-1} \BI_{p} - |X - q|^{-3/2} (X - q) (X - q)^{T}  \Bigr] 
  \\
- \Psi_{1}  & = n \BE   W^{2} (X, \BF)  \bfS (X; q_{0}) \bfS^{T} (X; q_{0}).
+ \Psi_{1}  & = \BE   W^{2} (X, \BF)  S (X; q_{0}) S^{T} (X; q_{0}).
  \ean
  \end{Theorem}
+
+%\rework{
 Thus, under very standard regularity conditions, the sample weighted spatial median 
 is consistent and is asymptotically normal.
-Theorem~\ref{Thm:WSMedian}  can be proved in several different ways. We have used 
-techniques following \cite{ref:AoS891631_Haberman, ref:AoS921514_Niemiro}, 
-we omit the details.
+Theorem~\ref{Thm:WSMedian}  can be proved in several different ways.
+Here we use techniques following \cite{ref:AoS891631_Haberman, ref:AoS921514_Niemiro}.
+Specifically, following Theorem 4 in \cite{ref:AoS921514_Niemiro}, which traces back to \cite{ref:AoS891631_Haberman} with slightly relaxed conditions, we get
+%
+\begin{align*}
+n^{1/2} (\hat{q}_{nW} - q_{0}) =
+- \frac{\Psi_2}{\sqrt n} \sum_{i=1}^n W (X_i, \BF)  S (X_i; q_0) + o_P(1).
+\end{align*}
+%
+Theorem~\ref{Thm:WSMedian} follows by applying the central limit theorem.
+%}
 
@@
 \label{Cor:ARE}
-Assume that $|X - q_{0}|$ and $S (X; q_{0})$ are independent, and the weight function 
-$W (X, \BF)$ is a function of  $|X - q_{0}|$. Then
+\hl{Assume that the tuning parameter of the weight function, $\BF$}, is  the distribution of $X$.
+Also assume $|X - q_{0}|$ and $S (X; q_{0})$ are independent, and the weight function $W (X, \BF)$ is a function of  $|X - q_{0}|$.
+Then
 \ban
@@
 then this asymptotic relative efficiency is 
-$ \{k^{-1} (\BE ||X - q_{0}|^{-1} )^{2} \BE |X - q_{0}|^{-2} \}^{1/p}> 1$. 
+$ \{k^{-1} (\BE |X - q_{0}|^{-1} )^{2} \BE |X - q_{0}|^{-2} \}^{1/p}> 1$. 
 \end{Corollary}
@@
 \begin{Definition}
-A $p$-dimensional random vector $X$ is said to elliptically distributed if 
-there exist a vector $\mu \in \BR^p$, a positive semi-definite matrix 
-$\Sigma \in \BR^{p \times p}$ and a function 
-$\phi: (0, \infty) \rightarrow \BR$ such that the characteristic function 
-of $X$ is $\exp \{ i t^{T} \mu \} \phi (\bft^T \Sigma \bft)$ for $\bft \in \BR^p$.
+A $p$-dimensional random vector $X$ is said to elliptically distributed if there exist a vector $\mu \in \BR^p$, a positive semi-definite matrix $\Sigma \in \BR^{p \times p}$ and a function 
+$\phi: (0, \infty) \rightarrow \BR$ such that the characteristic function of $X$ is $\exp \{ i t^{T} \mu \} \phi (\bft^T \Sigma \bft)$ for $\bft \in \BR^p$.
 \end{Definition}
@@
 \label{Cor:Elliptic_ARE}
-Assume that the tuning parameter of the weight function, $\BF$, is  the 
-distribution of $X$, and is an elliptically symmetric distribution, and $\mu = q_{0}$. 
+Assume that $\BF \equiv \BF_X$ is an elliptically symmetric distribution, and $\mu = q_{0}$. 
 Also assume that the weight function is affine invariant, that is:
@@
 absolute deviation, derived from the \textit{projection depth}. We omit the technical 
-details. These three weight functions a center-inward partial ordering, thus essentially 
+details. These three weight functions give a center-inward partial ordering, thus essentially 
 quantifying \textit{peripherality} instead of \textit{depth}.

### 2019-08-14 EJSSubmission/WeightedSign_EJS_Introduction_02_24_19_1.tex
cor 2.2 fixed

@@
 \citep{ref:SPL12765_Taskinenetal}.
-However, valuable information is lost in the form of magnitudes of sample points. As a 
-result, spatial sign-based procedures suffer from low efficiency. For example, eigenvector 
-estimates obtained from the covariance matrix of $\bfS$ are asymptotically inadmissible 
-\citep{ref:Biometrika14673_MagyarTyler} and  Tyler's M-estimate of scatter \citep{ref:AoS87234_Tyler} has uniformly 
-lower asymptotic risk.
+However, valuable information is lost in the form of magnitudes of sample points.
+As a result, spatial sign-based procedures suffer from low efficiency.
+For example, eigenvector estimates obtained from the covariance matrix of $S$ are asymptotically inadmissible \citep{ref:Biometrika14673_MagyarTyler} and  Tyler's M-estimate of scatter \citep{ref:AoS87234_Tyler} has uniformly lower asymptotic risk.
 
@@
 to adaptively trade-off between efficiency and robustness considerations in any given 
-application. We demonstrate the utility of using 
-the proposed \textit{weighted generalized sign} functions in a number of problems 
-of current interest, including robust estimation of location and scatter.
+application.
+We demonstrate the utility of using the proposed \textit{weighted generalized sign} functions in a number of problems of current interest, including robust estimation of location and scatter.
 
-Specifically, we propose using product of the generalized sign function and a 
-weight function derived as a transformation of a data-depth function 
-\citep{ref:AoS00461_ZuoSerfling, ref:DIMACS061_Serfling}.
- Like data-depth functions, the weight functions 
-used in this paper are non-negative reals defined over $\cX \times \cF$, where 
-$\cF$ is a fixed family of probability measures.
+Specifically, we propose using product of the generalized sign function and a weight function derived as a transformation of a data-depth function \citep{ref:AoS00461_ZuoSerfling, ref:DIMACS061_Serfling}.
+Like data-depth functions, the weight functions used in this paper are non-negative reals defined over $\cX \times \cF$, where $\cF$ is a fixed family of probability measures.
 For every choice of parameters $\mu \in \cX$ and $\BF \in \cF$, in this paper
+%
 \begin{align}
@@
 \end{align}
+%
 is used as a robust surrogate for observation $X_{i}$.
@@
 
-\rework{
 There are two unknown quantities in the generalized sign function as defined in \eqref{eq:GSign}: $\mu$ and $\BF$, To estimate dispersion and its eigen-structure robustly, we must start with a robust estimator for $\mu$.
@@
 This mirrors the context of how data depth has been used in the literature (refs).
-Due to this reason, except for the first result in Section~\ref{Sec:WSQuantiles} (Theorem~\ref{Thm:WSMedian}) we assume $\BF \equiv \BF_X$ for the rest of the paper.
-However, other choices of $\BF$ may lead to interesting interpretations of $W(.
-,\BF)$ and the resulting quantities, e.g.
-(ref), and can potentially be explored further.
-}
+Due to this reason, we assume $\BF \equiv \BF_X$ for the rest of the paper.
+As and when required, we shall use sample versions of these quantities, stating the theoretical conditions for the corresponding approximation results to hold.
 

### 2019-08-14 EJSSubmission/WeightedSign_EJS_WeightedSpatialQuantiles_02_24_19_1.tex
cor 2.2 fixed

@@
 
- \begin{Theorem}
- \label{Thm:WSMedian}
+ \begin{Theorem}\label{Thm:WSMedian}
  Under assumptions [A1]-[A3], we have 
  \ban 
- n^{1/2} (\hat{q}_{nW} - q_{0}) & \draro N(0, \Psi_{2}^{-1} \Psi_{1}^{2} \Psi_{2}^{-1}), 
+ n^{1/2} (\hat{q}_{nW} - q_{0}) & \draro N(0, \Psi_{2W}^{-1} \Psi_{1W} \Psi_{2W}^{-1}), 
  \text{ where } \\
- \Psi_{2} & = 
- \BE W (X, \BF)\Bigl[  |X - q|^{-1} \BI_{p} - |X - q|^{-3/2} (X - q) (X - q)^{T}  \Bigr] 
+ \Psi_{2W} & = 
+ \BE W (X, \BF)\Bigl[  |X - q_0|^{-1} ( \BI_{p} - S (X; q_{0}) S^{T} (X; q_{0}))  \Bigr] 
  \\
- \Psi_{1}  & = \BE   W^{2} (X, \BF)  S (X; q_{0}) S^{T} (X; q_{0}).
+ \Psi_{1W}  & = \BE   W^{2} (X, \BF)  S (X; q_{0}) S^{T} (X; q_{0}).
  \ean
@@
 n^{1/2} (\hat{q}_{nW} - q_{0}) =
-- \frac{\Psi_2}{\sqrt n} \sum_{i=1}^n W (X_i, \BF)  S (X_i; q_0) + o_P(1).
+- \frac{\Psi_{2W}}{\sqrt n} \sum_{i=1}^n W (X_i, \BF)  S (X_i; q_0) + o_P(1).
 \end{align*}
@@
 Theorem~\ref{Thm:WSMedian} follows by applying the central limit theorem.
+
+\paragraph{Remark.} Note that for the result in Theorem~\ref{Thm:WSMedian} to go through, it is not necessary for $\BF$ to be the distribution of $X$.
+Other choices of $\BF$, e.g.
+\cite{StatPaper18},  may lead to interesting interpretations of $W(.
+,\BF)$ and the resulting location estimator and can be explored further.
 %}
@@
 \subsection{Asymptotic efficiency of weighted spatial median}
-Let $V_{W} = \Psi_{2}^{-1} \Psi_{1}^{2} \Psi_{2}^{-1}$ be the asymptotic 
+Let $V_{W} = \Psi_{2W}^{-1} \Psi_{1W} \Psi_{2W}^{-1}$ be the asymptotic 
 variance of \hl{$\hat{q}_{n,W}$} from Theorem~\ref{Thm:WSMedian}, where we use the 
@@
 \label{Cor:ARE}
-\hl{Assume that the tuning parameter of the weight function, $\BF$}, is  the distribution of $X$.
-Also assume $|X - q_{0}|$ and $S (X; q_{0})$ are independent, and the weight function $W (X, \BF)$ is a function of  $|X - q_{0}|$.
-Then
+Assume that the weight function $W (X, \BF)$ is bounded above by $k$ for some $k > 0$, and the matrices $\Psi_1 = \BE S(X; q_0) S^T(X; q_0)$ and $\Psi_{1W}$ are positive definite. Then
+%
 \ban
-& ARE (\hat{q}_{nW}, \hat{q}_{n}) \\
-& = 
-\Bigl[ \BE \bigg(  |X - q_{0}|^{-1} \bigg) \Bigr]^{-2}
-\Bigl[ \BE W^{2} (X, \BF) \Bigr]^{-1}
-\Bigl[ \BE \bigg(  |X - q_{0}|^{-1} W (X, \BF) \bigg) \Bigr]^{2}.
+ARE (\hat{q}_{nW}, \hat{q}_{n}) \geq
+\frac{ \lambda_{\min} (\Psi_1) \lambda_{\min}^2 (\Psi_{2W})}
+{k \lambda_{\max} (\Psi_1) \lambda_{\max}^2 (\Psi_2)}
 \ean
-Consequently, if $W (X, \BF) = k   |X - q_{0}|^{-1}$ for some $k \in (0, 1]$, 
-then this asymptotic relative efficiency is 
-$ \{k^{-1} (\BE |X - q_{0}|^{-1} )^{2} \BE |X - q_{0}|^{-2} \}^{1/p}> 1$. 
+%
+Consequently, if $k < r \equiv \lambda_{\min} (\Psi_1) \lambda_{\min}^2 (\Psi_{2W})/(\lambda_{\max} (\Psi_1) \lambda_{\max}^2 (\Psi_2))$ then this asymptotic relative efficiency is larger than 1. 
 \end{Corollary}
+
+\begin{proof}[Proof of Corollary~\ref{Cor:ARE}]
+Using the facts that $det (AB) = det(A) det(B)$ for square matrices $A,B$ and $det (A^{-1}) = 1/det(A)$ for non-singular $A$, we write
+%
+\ban
+\frac{det (V_1)}{det (V_W)} &= det( \Psi_2^{-1} \Psi_1 \Psi_2^{-1} )
+det( \Psi_{2 W} \Psi_{1 W}^{-1} \Psi_{2 W} )\\
+&= det (\Psi_1) det (\Psi_{1 W}^{-1}) [ det(\Psi_2^{-1}) det(\Psi_{2 W}) ]^2
+\ean
+%
+The result follows, using the facts that $\det(A) \geq \lambda_{\min} (A)$ and $\det(A^{-1}) \geq 1/\lambda_{\max} (A)$, and the upper bound on $W$.
+\end{proof}
 
@@
 We may wish to further explore the conditions of Corollary~\ref{Cor:ARE}. 
-Let us concentrate on the case of where the distribution of $X$ is 
-elliptically symmetric. Following \cite{ref:Fangetal90_Book}:
+Let us concentrate on the case of where the distribution of $X$ is spherically symmetric. Following \cite{ref:Fangetal90_Book}:
 
@@
 
-There are several alternative formulations, see the above reference and 
-citations within it for details. 
-%The spherically symmetric case is realized with $\Sigma = \sigma^{2} \BI_{p}$ for some 
-%$\sigma^{2} > 0$. 
+There are several alternative formulations, see the above reference and citations within it for details. The spherically symmetric case is realized with $\Sigma = \sigma^{2} \BI_{p}$ for some 
+$\sigma^{2} > 0$. 
 We fix the notation $Z = \Sigma^{-1/2} (X - \mu)$, and let 
@@
 \label{Cor:Elliptic_ARE}
-Assume that $\BF \equiv \BF_X$ is an elliptically symmetric distribution, and $\mu = q_{0}$. 
+Assume that $\BF \equiv \BF_X$ is an elliptically symmetric distribution, with location parameter $\mu = q_{0}$, $\Sigma$ positive definite.
 Also assume that the weight function is affine invariant, that is:
@@
 \ean
-Then  the weight function satisfies $W (X, \BF) = W (Z, \BF_{Z})$, and 
-hence may be further restricted to be a function of $|Z|$. Then 
-$S (X; q_{0})$ is uniform on the unit ball 
-in $\BR^{p}$, and is independent of $|X - q_{0}|$, while 
-$W (X, \BF)$ is a function of  $|X - q_{0}|$. That is, the conditions of 
-Corollary~\ref{Cor:ARE} are satisfied. 
+Then  the weight function satisfies $W (X, \BF) = W (Z, \BF_{Z})$, and hence may be further restricted to be a function of $|Z|$. Then $S (X; q_0)$ is uniform on the $\sqrt c$-radius ball 
+in $\BR^{p}$ centered at the origin, and is independent of $|X - q_{0}|$, while $W (X, \BF)$ is a function of  $|X - q_{0}|$. That is, the conditions of Corollary~\ref{Cor:ARE} are satisfied. 
 \end{Corollary}
@@
 such functions arising in the context of data-depths are affine invariant. 
-Corollary~\ref{Cor:Elliptic_ARE} implies that there is a wide frame of distributions and 
-choices of weight functions where there is a benefit to considering weighted spatial 
-quantiles. In actual computations, in place of $W (x, \BF)$ we propose 
+%Corollary~\ref{Cor:Elliptic_ARE} implies that there is a wide frame of distributions and  choices of weight functions where there is a benefit to considering weighted spatial quantiles.
+In actual computations, in place of $W (x, \BF)$ we propose 
 using $W (x, \BF_{n})$ where
-$\BF_{n} = n^{-1} \sum_{i = 1}^{n} \cI (X_{i} \leq x )$ is the empirical distribution 
-function. Up to first order asymptotics, the analysis remain unchanged from the above 
-for this modified weight function.
+$ \BF_{n}(z) = (np)^{-1} \sum_{i = 1}^{n} \sum_{j=1}^p
+\cI (X_{ij} \leq z_j ), z \in \BR^p
+$ is the empirical distribution function. Up to first order asymptotics, the analysis remain unchanged from the above for this modified weight function.
 
@@
 algebraic and analytic properties assumed for data-depth functions to elicit interesting 
-mathematical properties, see for example 
-\cite{ref:AoS00461_ZuoSerfling, ref:DIMACS061_Serfling} 
-for details.
+mathematical properties, see for example \cite{ref:DIMACS061_Serfling, ref:AoS00461_ZuoSerfling} for details.
 

### 2019-08-16 EJSSubmission/WeightedSIgn_EJS_DA_02_24_19_1.tex
revision sent to kodu da

@@
 from June 1970 to May 2004, available 
-from \url{http://www.cpc.ncep.noaa.gov/data/}, depicted in  panel (a) 
+from \url{http://www.cpc.ncep.noaa.gov/data}, depicted in  panel (a) 
 of Figure~\ref{fig:fPCAfig})).

### 2019-08-16 EJSSubmission/WeightedSign_EJS_Dispersion_02_24_19_1.tex
cor 2.2 fixed
revision sent to kodu da

@@
-\section{A Robust Measure of  Dispersion} 
+\section{A robust measure of dispersion} 
 \label{Sec:WSDispersion1}
-
 From this section onwards, we assume that $\cX = \BR^{p}$, that is, the support of the 
@@
 
+\subsection{The Weighted Sign Covariance Matrix}
 Consider the spectral decomposition of $\Sigma$ given by
@@
 \eaq
-We define the notation $\BS (X; \mu) =  S (X; \mu) S( X; \mu)^T$.
-Then, we define the following dispersion  parameter:
+We fix the notation $\BS (X; \mu) =  S (X; \mu) S( X; \mu)^T$, and define the following dispersion  parameter:
 \baq
@@
 \eaq
- In the following Theorem, we establish that the eigenvectors of ${\Sigma}$ and 
- $\tilde{\Sigma}$ are identical, although their eigenvalues may be different.
+In the following Theorem, we establish that the eigenvectors of ${\Sigma}$ and $\tilde{\Sigma}$ are identical, although their eigenvalues may be different.
 
@@
 where $\Lambda_{W}$ is a diagonal matrix.
-
 \end{proof}
 
-We now discuss the properties of the sample version $\widehat{\tilde{\Sigma}}$ 
-computed from $\bfX$. 
-In practice, we cannot obtain $W (x) \equiv W (x, \BF)$, 
-and consequently use  $W (x, \BF_{n})$ instead. We assume the following conditions:
-\begin{enumerate}
-\item \textbf{Bounded weights:} The weights $W (\cdot, \cdot)$ are bounded functions.
+\subsection{Sample version of $\tilde \Sigma$}
+We now discuss the properties of the sample version of $\tilde \Sigma$, say $\widehat{\tilde{\Sigma}}$ computed from $\bfX$.
+In practice, we cannot obtain $W (x) \equiv W (x, \BF)$, and consequently use  $W (x, \BF_{n})$ instead.
+We assume the following conditions:
 
-\item \textbf{Uniform convergence:} 
+\begin{description}
+\item[(B1)]{\it Bounded weights}: The weights $W (\cdot, \cdot)$ are bounded functions.
+
+\item[(B2)]{\it Uniform convergence}:
 \ban 
@@
 
-\item \textbf{Smoothness under perturbation:}
-For all $\BF \in \cF$, there exists a $\delta > 0$, possibly depending on $\BF$, such that 
+\item[(B3)]
+{\it Smoothness under perturbation:} For all $\BF \in \cF$, there exists a $\delta > 0$, possibly depending on $\BF$, such that 
 for any $\epsilon \in (0, \delta)$ 
@@
 \ean 
- \end{enumerate}
+\end{description}
+%
 In the above, $\delta_{x}$ denotes point mass at $x$. 
-These property are easily satisfied under for  weight functions  derived 
-from standard depth functions, for example, $W_{HSD} (\cdot)$, 
-$W_{MhD} (\cdot)$ and $W_{PD} (\cdot)$ discussed earlier.
+These properties are easily satisfied under for  weight functions  derived from standard depth functions, for example, $W_{HSD} (\cdot)$, $W_{MhD} (\cdot)$ and $W_{PD} (\cdot)$ discussed earlier.
 
-The following result allows us to use the empirical, plug-in weights and an 
-estimated location parameter in the 
-weighted dispersion estimator. A natural choice for the location parameter estimator 
-is the solution to $\sum_{i = 1}^{n} \tilde{X}_{i} = 0$.
+The following result allows us to use the empirical, plug-in weights and an estimated location parameter in the weighted dispersion estimator.
+A natural choice for the location parameter estimator is the solution to $\sum_{i = 1}^{n} \tilde{X}_{i} = 0$, which is the same as the sample version of the weighted spatial median discussed in Section~\ref{Sec:WSQuantiles}.
 
@@
 \ean
+%
 and hence 
+%
 \ban 
@@
 \ean
+%
 Let $H (X_{i}) = | X_{i} - \mu |^{-2} \bigl( c^{T} (X_{i} - \mu) \bigr)^{2}$, and notice 
@@
 & n^{1/2} \sum_{i = 1}^{n} \Bigl( 
-W_{n}^{2} (X_{i}, \BF_{n}) ~vec~(\BS (X_{i}; \hat{\mu}_{n})) 
-- \BE W^{2} (X_{i}) ~vec~(\BS (X_{i}; \mu)) \Bigr)\\
+W_{n}^{2} (X_{i}, \BF_{n}) vec(\BS (X_{i}; \hat{\mu}_{n})) 
+- \BE W^{2} (X_{i}) vec(\BS (X_{i}; \mu)) \Bigr)\\
 & \hspace{0.5cm} \draro
@@
 \ean
-where $V_{W} = \BV [W^{2} (X_{i}, \BF) ~vec~(\BS (X_{i}; {\mu})) ] $.
+where $V_{W} = \BV [W^{2} (X, \BF) vec(\BS (X; {\mu})) ] $.
 \end{Theorem}
@@
 
-\section{An Affine Equivariant Robust Measure of Dispersion}
+\section{An affine equivariant robust measure of dispersion}
 \label{Sec:WSDispersion2}
-
 A desirable invariance property of any dispersion parameter $T_{X}$ corresponding to 
@@
 
-\vspace{1em}
-\noindent\textbf{(C1)} The function $u(r)/r^2$ is monotone decreasing, 
+\begin{description}
+\item[(C1)] The function $u(r)/r^2$ is monotone decreasing, 
 and $u(r)>0$ for $r > 0$;
 
-\noindent\textbf{(C2)}  The function $v(r)$ is monotone decreasing, and 
+\item[(C2)]  The function $v(r)$ is monotone decreasing, and 
 $v(r) > 0$ for $r > 0$;
 
-\noindent\textbf{(C3)} Both $u(r)$ and $v(r)$ are bounded and continuous;
+\item[(C3)] Both $u(r)$ and $v(r)$ are bounded and continuous,
 
-\noindent\textbf{(C4)} $u(0) / v(0) < p$;
+\item[(C4)] $u(0) / v(0) < p$,
 
-\noindent\textbf{(C5)} For any hyperplane in the sample space $\mathcal X$, 
+\item[(C5)] For any hyperplane in the sample space $\mathcal X$, 
 (i) $P(H) = \BE \{ \cI_{\{X \in H \}} \} < 1 - p v(\infty) / u(\infty)$ and 
 (ii) $P(H) \leq 1/p$.
-%
+\end{description}
 
-\vspace{1em}
-\noindent Putting things into context, in our case we have 
+Putting things into context, in our case we have 
 $v (\cdot) = p^{-1}\BV W (X)$, 
@@
 
-In order to compute the sample version of $\Sigma_{*}$, we solve (\ref{eqn:ADCM}) 
+To compute the sample version of $\Sigma_{*}$, we solve (\ref{eqn:ADCM}) 
 iteratively by obtaining a sequence of positive definite matrices 
@@
 
-\section{Robust Estimation of Eigenvalues, and a Plug-in Estimator of $\Sigma$}
+\section{Robust estimation of eigenvalues, and a plug-in estimator of $\Sigma$}
 \label{Sec:Eigen}
-
 As seen in Theorem~\ref{Thm:WSVariance}, eigenvalues of the $\tilde{\Sigma}$ 
@@
 This proof has many algebraic steps, and we sketch the main arguments below.
+
 Suppose $\hat{A} = \widehat{{\Gamma}}^{T}  \Sigma \widehat{{\Gamma}}$.
-
-Owing to the fact that the Frobenius norm is invariant under rotations and 
-that $p$ is finite and fixed, it suffices to show that the off-diagonal elements of 
-$\hat{A}$ converge in probability to zero, and that the difference between 
-the $i$-th diagonal element of $\hat{A}$ and ${\lambda}^{\dagger}_{i}$ converges to 
-zero for any $i = 1, \ldots, p$.
+Owing to the fact that the Frobenius norm is invariant under rotations and that $p$ is finite and fixed, it suffices to show that the off-diagonal elements of $\hat{A}$ converge in probability to zero, and that the difference between the $i$-th diagonal element of $\hat{A}$ and ${\lambda}^{\dagger}_{i}$ converges to zero for any $i = 1, \ldots, p$.
 
@@
 = {{\Gamma}} + R_{n1}$, where the $(i, j)$-th element of the remainder 
-$R_{n1, i, j}$ satisfies $\BE  R_{n1, i, j}^{2} = O(n^{-1})$.
-
-We can show, using standard algebra, that 
+$R_{n1, i, j}$ satisfies $\BE  R_{n1, i, j}^{2} = O(n^{-1})$. We can show, using standard algebra, that 
 \ban

### 2019-08-16 EJSSubmission/WeightedSign_EJS_IF_02_24_19_1.tex
revision sent to kodu da

@@
 
-\begin{proof}[Proof of Proposition~\ref{Thm:IF2}:]
-
+\begin{proof}[Proof of Proposition~\ref{Thm:IF2}]
 Let $z_{0} = \Lambda^{-1/2} \Gamma^T  (x_0 - \mu) = (z_{0 1}, \ldots, z_{0 p})^T$.

### 2019-08-16 EJSSubmission/WeightedSign_EJS_Introduction_02_24_19_1.tex
revision sent to kodu da

@@
 
-Specifically, we propose using product of the generalized sign function and a weight function derived as a transformation of a data-depth function \citep{ref:AoS00461_ZuoSerfling, ref:DIMACS061_Serfling}.
+Specifically, we propose using product of the generalized sign function and a weight function derived as a transformation of a data-depth function \citep{ref:DIMACS061_Serfling, ref:AoS00461_ZuoSerfling}.
 Like data-depth functions, the weight functions used in this paper are non-negative reals defined over $\cX \times \cF$, where $\cF$ is a fixed family of probability measures.
@@
 \begin{center}
-\begin{tabular}{ll}
+%\begin{tabular}{ll}
 %%% These ones have sample size = 700, just right  for EJS
-\includegraphics[width=0.45\textwidth]{./Plots_SC/WeightedSign_Scatter_700_02_27_19} &
-\includegraphics[width=0.45\textwidth]{./Plots_SC/WeightedSign_MD_700_02_27_19} \\
-\includegraphics[width=0.45\textwidth]{./Plots_SC/WeightedSign_TD_700_02_27_19} &
-\includegraphics[width=0.45\textwidth]{./Plots_SC/WeightedSign_PD_700_02_27_19} \\
+\includegraphics[width=\textwidth]{./Plots_SC/WeightedSignAll}
+%\includegraphics[width=0.45\textwidth]{./Plots_SC/WeightedSign_Scatter_700_02_27_19} &
+%\includegraphics[width=0.45\textwidth]{./Plots_SC/WeightedSign_MD_700_02_27_19} \\
+%\includegraphics[width=0.45\textwidth]{./Plots_SC/WeightedSign_TD_700_02_27_19} &
+%\includegraphics[width=0.45\textwidth]{./Plots_SC/WeightedSign_PD_700_02_27_19} \\
 
@@
 %\includegraphics[width=0.45\textwidth]{../Plots_SC/WeightedSign_PD_02_24_19} \\
-\end{tabular}
+%\end{tabular}
 \caption{
@@
 the distribution of $X$ has the clear interpretation of differentially weighting observations based on their inlyingness to the overall data distribution.
-This mirrors the context of how data depth has been used in the literature (refs).
+This mirrors the context of how data depth has been used in the literature \cite{LiuPareliusSingh99, ref:DIMACS061_Serfling}.
 Due to this reason, we assume $\BF \equiv \BF_X$ for the rest of the paper.
@@
 
-Following that, we restrict to the $\BR^{p}$ for fixed $p$, and present detailed 
-discussions on our primary proposal for a  robust measure of dispersion in 
-Section~\ref{Sec:WSDispersion1}, followed by a proposed 
-\textit{ affine equivariant version} of 
-it in Section~\ref{Sec:WSDispersion2}, robust estimation of eigenvalues and a third 
-robust estimator for dispersion in Section~\ref{Sec:Eigen}, and a thorough study of 
-robustness and efficiency using influence functions in Section~\ref{Sec:RE_Dispersion}.
-We then report multiple simulation-based numeric studies in Section~\ref{Sec:Simulation}, 
-present several real data examples in Section~\ref{Sec:DA}, and concluding remarks in 
-Section~\ref{Sec:Conclusion}.
+Following that, we restrict to the $\BR^{p}$ for fixed $p$, and present detailed discussions on our primary proposal for a  robust measure of dispersion in Section~\ref{Sec:WSDispersion1}, followed by a proposed \textit{ affine equivariant version} of it in Section~\ref{Sec:WSDispersion2}, robust estimation of eigenvalues and a third robust estimator for dispersion in Section~\ref{Sec:Eigen}, and a thorough study of robustness and efficiency using influence functions in Section~\ref{Sec:RE_Dispersion}.
+We then report multiple simulation-based numeric studies in Section~\ref{Sec:Simulation}, present several real data examples in Section~\ref{Sec:DA}, and concluding remarks in Section~\ref{Sec:Conclusion}.
 
-In the rest of this paper, all finite-dimensional vectors are 
-column vectors, and for a vector or matrix $a$, the notation $a^{T}$ stands for 
-its transpose. The Gaussian distribution with mean $\mu$ and variance $\Sigma$ is denoted
-by $N (\mu, \Sigma)$. The identity matrix  is denoted by $\BI$, with or without a 
-subscript to denote its dimension. The notations $A^{-1}$ and $det (A)$ respectively 
-stand for the inverse and determinant of matrix $A$, whenever these are well-defined.
+In the rest of this paper, all finite-dimensional vectors are column vectors, and for a vector or matrix $a$, the notation $a^{T}$ stands for its transpose.
+The Gaussian distribution with mean $\mu$ and variance $\Sigma$ is denoted by $N (\mu, \Sigma)$.
+The identity matrix  is denoted by $\BI$, with or without a subscript to denote its dimension.
+The notations $A^{-1}, det (A), \lambda_{\min} (A), \lambda_{\max} (A)$ respectively stand for the inverse, determinant, minimum and maximum eigenvalues of a matrix $A$, whenever these are well-defined.
+For a scalar or vector valued random variable $Y$, $\BE Y$ denotes its expected value, while $\BV Y$ denotes its variance or covariance matrix.

### 2019-08-16 EJSSubmission/WeightedSign_EJS_Simulations_02_24_19_1.tex
revision sent to kodu da

@@
 
-We report numerical simulation studies on several properties relating to 
+We report a number of numerical simulation studies on several properties relating to 
 $\tilde{\Sigma}$ and  $\Sigma_{*}$, and their eigenvalues and eigenvectors, 

### 2019-08-16 EJSSubmission/WeightedSign_EJS_WeightedSpatialQuantiles_02_24_19_1.tex
revision sent to kodu da

@@
-\section{Weighted Spatial Quantiles}
+\section{The Weighted Spatial Median}
 \label{Sec:WSQuantiles}
@@
 \begin{description}
-\item[A1:] $\Psi (q; 0, \BF)$ is finite for all $q \in \cX \subseteq \BR^{p}$ 
+\item[(A1)] $\Psi (q; 0, \BF)$ is finite for all $q \in \cX \subseteq \BR^{p}$ 
 and has a unique minimizer $q_{0}$.
 
- \item[A2:] $\Psi (q; 0, \BF)$ is twice differentiable at $q_{0}$ and the second 
- derivative is positive definite.
+\item[(A2)] $\Psi (q; 0, \BF)$ is twice differentiable at $q_{0}$ and the second derivative is positive definite.
 
- \item[A3:] $\BE W^{2} (X, \BF)  S (X; q) S^{T} (X; q)$ exists for all 
- $q$ in a neighborhood of $q_{0}$. 
+\item[(A3)] $\BE W^{2} (X, \BF)  S (X; q) S^{T} (X; q)$ exists for all $q$ in a neighborhood of $q_{0}$. 
 \end{description}
@@
 Let $V_{W} = \Psi_{2W}^{-1} \Psi_{1W} \Psi_{2W}^{-1}$ be the asymptotic 
-variance of \hl{$\hat{q}_{n,W}$} from Theorem~\ref{Thm:WSMedian}, where we use the 
+variance of $\hat{q}_{n,W}$ from Theorem~\ref{Thm:WSMedian}, where we use the 
 subscript ``${}_{W}$'' to denote that this depends on the weight function. 
@@
 %
-Consequently, if $k < r \equiv \lambda_{\min} (\Psi_1) \lambda_{\min}^2 (\Psi_{2W})/(\lambda_{\max} (\Psi_1) \lambda_{\max}^2 (\Psi_2))$ then this asymptotic relative efficiency is larger than 1. 
+Consequently, if $k / \lambda_{\min}^2 (\Psi_{2W}) < \lambda_{\min} (\Psi_1) /(\lambda_{\max} (\Psi_1) \lambda_{\max}^2 (\Psi_2))$ then this asymptotic relative efficiency is larger than 1. 
 \end{Corollary}
@@
 
-There are several alternative formulations, see the above reference and citations within it for details. The spherically symmetric case is realized with $\Sigma = \sigma^{2} \BI_{p}$ for some 
-$\sigma^{2} > 0$. 
-We fix the notation $Z = \Sigma^{-1/2} (X - \mu)$, and let 
-$Z \sim \BF_{Z}$. Note that $\BF_{Z}$ is a spherically symmetric distribution and hence
-depends only on $|z|$, and  $\BE Z = \mathbf{0}_{p} \in \BR^{p}$ and $\BV Z = \BI_{p}$.
+There are several alternative formulations, see the above reference and citations within it for details.
 
-\begin{Corollary}
-\label{Cor:Elliptic_ARE}
-Assume that $\BF \equiv \BF_X$ is an elliptically symmetric distribution, with location parameter $\mu = q_{0}$, $\Sigma$ positive definite.
-Also assume that the weight function is affine invariant, that is:
-\ban
-W (A x + b, A \BF + b) = W (x, \BF),
-\ean
-Then  the weight function satisfies $W (X, \BF) = W (Z, \BF_{Z})$, and hence may be further restricted to be a function of $|Z|$. Then $S (X; q_0)$ is uniform on the $\sqrt c$-radius ball 
-in $\BR^{p}$ centered at the origin, and is independent of $|X - q_{0}|$, while $W (X, \BF)$ is a function of  $|X - q_{0}|$. That is, the conditions of Corollary~\ref{Cor:ARE} are satisfied. 
+\begin{Corollary}\label{Cor:Elliptic_ARE}
+Assume that $\BF \equiv \BF_X$ is an elliptically symmetric distribution, with location parameter $\mu = q_{0}$ and the covariance matrix $\Sigma$ satisfies the following conditions:
+%
+\begin{enumerate}
+\item $Tr(\Sigma^4) = o( Tr^2 (\Sigma^2) )$,
+
+\item $\frac{Tr^4(\Sigma)}{ Tr^2 (\Sigma^2)} \exp \left\{ - \frac{Tr^2 (\Sigma)}
+{ 128 \lambda_{\max}^2 (\Sigma)} \right\} = o(1)$,
+
+\item $\exp \left\{ - \frac{Tr^2 (\Sigma)}{ 256 \lambda_{\max}^2 (\Sigma)} \right\} = 
+o\left( \min\left( \frac{\lambda_{\max}(\Sigma) }{Tr( \Sigma)},
+\frac{\lambda_{\min}(\Sigma)}{\lambda_{\max}(\Sigma)} \right) \right)$,
+
+\item $\lambda_{\max}(\Sigma) = o( Tr(\Sigma))$.
+\end{enumerate}
+
+Also assume that the weight function is (a) bounded above by some $W_{\max} > 0$, (b) affine invariant, i.e.
+$ W (Ax + b, A\BF + b) = W (x, \BF)$ for $A \in \BR^{p \times p}, b \in \BR^p$, and (c) satisfies the following:
+%
+\begin{equation}\label{eqn:CorElliptic_ARE_eqn}
+\frac{W_{\max}}{[ \BE | X - q_0|^{-1} W(X, \BF)]^2 } <
+\frac{\lambda_{\min} (\Psi_1)}{\lambda_{\max} (\Psi_1) [ \BE | X - q_0|^{-1}]^2]}.
+\end{equation}
+%
+Then we have $ARE( \hat q_{n,W}, \hat q_n) > 1$.
 \end{Corollary}
 
-Obtaining affine invariant weight functions is not challenging, in fact, most 
-such functions arising in the context of data-depths are affine invariant. 
-%Corollary~\ref{Cor:Elliptic_ARE} implies that there is a wide frame of distributions and  choices of weight functions where there is a benefit to considering weighted spatial quantiles.
-In actual computations, in place of $W (x, \BF)$ we propose 
-using $W (x, \BF_{n})$ where
+The conditions 1-4 in Corollary~\ref{Cor:Elliptic_ARE} are due to \cite{ref:JASA151658_WangPengLi}, and ensure that the eigenvalues of $\Sigma$ are bounded away from 0 and $\infty$.
+Corollary~\ref{Cor:Elliptic_ARE} can be proved using Corollary~\ref{Cor:ARE}, the fact that for elliptical distributions $\Psi_1$ is non-singular \cite{ref:SPL12765_Taskinenetal}, then using and expanding upon Lemma A.5 in \cite{ref:JASA151658_WangPengLi}.
+We give the technical details in the supplementary material.
+
+Obtaining affine invariant weight functions is not challenging.
+Most functions arising in the context of data depths are affine invariant.
+Corollary~\ref{Cor:Elliptic_ARE} implies that there is a wide frame of distributions and  choices of weight functions where there is a benefit to considering weighted spatial medians.
+In fact, the choice of weight functions is even broader: only location invariance is required for Corollary~\ref{Cor:Elliptic_ARE} to hold.
+We only choose to restrict ourselves here because the subsequent analysis uses weights based on affine invariant data depth functions.
+Also note that in case \eqref{eqn:CorElliptic_ARE_eqn} does not hold for the original form of a weight function, one can scale all weights by an appropriate constant to reduce the value in the left hand side of \eqref{eqn:CorElliptic_ARE_eqn} to satisfy the condition.
+
+In actual computations, in place of $W (x, \BF)$ we propose using $W (x, \BF_{n})$ where
 $ \BF_{n}(z) = (np)^{-1} \sum_{i = 1}^{n} \sum_{j=1}^p
@@
 
-It is easy to show that results in this paper are valid for the weight functions
+The spherically symmetric case of an elliptical distribution is realized with $\Sigma = \sigma^{2} \BI_{p}$ for some $\sigma^{2} > 0$. We fix the notation $Z = \Sigma^{-1/2} (X - \mu)$, and let 
+$Z \sim \BF_{Z}$. Note that $\BF_{Z}$ is a spherically symmetric distribution and hence
+depends only on $|z|$, and $\BE Z = \mathbf{0}_{p} \in \BR^{p}$ and $\BV Z = \BI_{p}$.
+Taking affine invariant data depth functions as weights ensures that $W(X, \BF) = W(Z, \BF_Z)$.
+It is now easy to show that results in this paper are valid for the weight functions (with appropriate scaling to satisfy \eqref{eqn:CorElliptic_ARE_eqn})
 ($i$) $W_{HSD} (X) = \BF_{Z} (| Z |)$ derived from the \textit{half-space depth},  
 ($ii$) $W_{MhD} (X) = |Z|^{2}/(1 + | Z |^2)$ derived from the \textit{Mahalanobis depth}, 
-and  
-($iii$) $W_{PD} (X) = |Z|/(1+ | Z |/MAD(\BF_{Z}))$, where $MAD$ stands for median 
+and ($iii$) $W_{PD} (X) = |Z|/(1+ | Z |/MAD(\BF_{Z}))$, where $MAD$ stands for median 
 absolute deviation, derived from the \textit{projection depth}. We omit the technical 

### 2019-09-13 EJSSubmission/WeightedSign_EJS-supp.tex
supple done

\documentclass[ejs]{imsart}

\RequirePackage[OT1]{fontenc}
%\RequirePackage{amsthm,amsmath}
\RequirePackage[numbers]{natbib}
\RequirePackage[colorlinks,citecolor=blue,urlcolor=blue]{hyperref}
\usepackage{amssymb,amsmath,amsthm,color,outlines,subfigure,comment}
\usepackage[small]{caption}
%\usepackage{hyperref} % for linking references
%\hypersetup{colorlinks = true, citecolor = blue, urlcolor = blue}
\usepackage{graphics}
\usepackage{graphicx}
\usepackage{stackrel}
\usepackage{natbib}
\usepackage{soul}
%\usepackage[bordercolor=white,backgroundcolor=gray!30,linecolor=black,colorinlistoftodos]{todonotes}
%\newcommand{\rework}[1]{\todo[color=yellow,inline]{#1}}

% will be filled by editor:
\doi{10.1214/154957804100000000}
\pubyear{0000}
\volume{0}
\firstpage{0}
\lastpage{0}
%\arxiv{}

%%%settings
%\pubyear{2006}
%\volume{0}
%\issue{0}
%\firstpage{1}
%\lastpage{8}

%%%%%% put your definitions there:
\startlocaldefs
%\numberwithin{equation}{section}
%\theoremstyle{plain}
%\newtheorem{thm}{Theorem}[section]

\newcommand{\BA}{{\mathbb{A}}}
\newcommand{\BB}{{\mathbb{B}}}
\newcommand{\BC}{{\mathbb{C}}}
\newcommand{\BE}{{\mathbb{E}}}
\newcommand{\BD}{{\mathbb{D}}}
\newcommand{\BF}{{\mathbb{F}}}
\newcommand{\BG}{{\mathbb{G}}}
\newcommand{\BH}{{\mathbb{H}}}
\newcommand{\BI}{{\mathbb{I}}}
\newcommand{\BJ}{{\mathbb{J}}}
\newcommand{\BK}{{\mathbb{K}}}
\newcommand{\BL}{{\mathbb{L}}}
\newcommand{\BP}{{\mathbb{P}}}
\newcommand{\BR}{{\mathbb{R}}}
\newcommand{\BS}{{\mathbb{S}}}
\newcommand{\BT}{{\mathbb{T}}}
\newcommand{\BU}{{\mathbb{U}}}
\newcommand{\BV}{{\mathbb{V}}}
\newcommand{\BW}{{\mathbb{W}}}
\newcommand{\BX}{{\mathbb{X}}}
\newcommand{\BY}{{\mathbb{Y}}}
\newcommand{\BZ}{{\mathbb{Z}}}

\newcommand{\BCOV}{{\mathbb{COV}}}

\newcommand{\colrit}{\color{red} \it}
\newcommand{\colrbf}{\color{red} \bf}
\newcommand{\colbit}{\color{blue} \it}
\newcommand{\colbbf}{\color{blue} \bf}
\newcommand{\colmit}{\colm \it}
\newcommand{\colmbf}{\colm \bf}

\newcommand{\bfOne}{\bf 1}
\newcommand{\iid}{\stackrel{i.i.d.}{\sim}}
\newcommand{\raro}{\rightarrow}

\newcommand{\cA}{\mathcal{A}}
\newcommand{\cB}{\mathcal{B}}
\newcommand{\cC}{\mathcal{C}}
\newcommand{\cD}{\mathcal{D}}
\newcommand{\cE}{\mathcal{E}}
\newcommand{\cF}{\mathcal{F}}
\newcommand{\cH}{\mathcal{H}}
\newcommand{\cI}{\mathcal{I}}
\newcommand{\cM}{\mathcal{M}}
\newcommand{\cN}{\mathcal{N}}
\newcommand{\cS}{\mathcal{S}}
\newcommand{\cX}{\mathcal{X}}
\newcommand{\cY}{\mathcal{Y}}

\def\baq#1\eaq{\begin{align}#1\end{align}}
\def\ban#1\ean{\begin{align*}#1\end{align*}}
\newcommand{\draro}{ \stackrel{{\mathcal D}}{\Rightarrow} }

\def\bredbf#1\eredbf{{\color{red}{\bf ???? #1 ????}}}
\def\BeginRedComment#1\EndRedComment{({\color{red}{\bf Comment:} {\it #1}}) }
\def\BeginBlueComment#1\EndBlueComment{({\color{blue}{\bf Comment:} {\it #1}}) }

\DeclareMathOperator*{\ve}{vec}
\DeclareMathOperator*{\diag}{diag }
\DeclareMathOperator*{\supp}{supp }
\DeclareMathOperator*{\Tr}{Tr}
\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\Th}{^{\text{th}}}

\makeatletter
\newcommand{\opnorm}{\@ifstar\@opnorms\@opnorm}
\newcommand{\@opnorms}[1]{%
  \left|\mkern-1.5mu\left|\mkern-1.5mu\left|
   #1
  \right|\mkern-1.5mu\right|\mkern-1.5mu\right|
}
\newcommand{\@opnorm}[2][]{%
  \mathopen{#1|\mkern-1.5mu#1|\mkern-1.5mu#1|}
  #2
  \mathclose{#1|\mkern-1.5mu#1|\mkern-1.5mu#1|}
}
\makeatother

\newtheorem{Theorem}{Theorem}[section]
\newtheorem{Lemma}[Theorem]{Lemma}
\newtheorem{Corollary}[Theorem]{Corollary}
\newtheorem{Proposition}[Theorem]{Proposition}
\newtheorem{Conjecture}[Theorem]{Conjecture}
\theoremstyle{definition} \newtheorem{Definition}[Theorem]{Definition}

\endlocaldefs

\begin{document}

\begin{frontmatter}
\title{On Weighted Multivariate Sign Functions: Supplementary Material}
\runtitle{Weighted Sign Functions}
%\thankstext{T1}{Footnote to the title with the `thankstext' command.}

\begin{aug}
\author{\fnms{Subhabrata} \snm{Majumdar}\thanksref{t1}\ead[label=e1]{subho@research.att.com}}
\and
\author{\fnms{Snigdhansu} \snm{Chatterjee}\thanksref{t3}\ead[label=e2]{chatt019@umn.edu}}

\address{School of Statistics,\\
University of Minnesota,\\
313 Ford Hall,\\
224 Church Street S.E., \\
Minneapolis 55455, USA\\
%usually few lines long\\
\printead{e1,e2}}

%\author{\fnms{Third} \snm{Author}
%\ead[label=e3]{third@somewhere.com}
%\ead[label=u1,url]{www.foo.com}}
%
%\address{Address of the Third author\\
%usually few lines long\\
%usually few lines long\\
%\printead{e3}\\
%\printead{u1}}

\thankstext{t1}{Currently at AT\&T Labs Research}
%\thankstext{t2}{First supporter of the project}
\thankstext{t3}{Corresponding author}
\runauthor{Majumdar and Chatterjee}

\affiliation{University of Minnesota and University of Minnesota}

\end{aug}

\end{frontmatter}

\appendix
\renewcommand{\thesection}{\Alph{section}}
\section{Form of $V_W$}\label{sec:appA}
First observe that for $F$ having covariance matrix $\Sigma = \Gamma\Lambda\Gamma^T$,
%
\begin{align}\label{eqn:VWeqn}
V_W  = (\Gamma \otimes \Gamma) V_{W, \Lambda} (\Gamma \otimes \Gamma)^T
\end{align}
%
where $V_{W, \Lambda}$ is the covariance matrix of $\BF_\Lambda$, the elliptic distribution with mean $\mu$ and covariance matrix $\Lambda$. Now,
%
\begin{eqnarray*}
V_{W, \Lambda} &=& \BE \left[ \ve \left\{ \frac{W^2 (Z, \BF_Z) \Lambda^{1/2} ZZ^T \Lambda^{1/2} }{ Z^T \Lambda Z} - \tilde \Lambda \right\} {\ve}^T \left\{ \frac{ W^2(Z, \BF_Z) \Lambda^{1/2} ZZ^T \Lambda^{1/2} }{ Z^T \Lambda Z} - \tilde \Lambda \right\} \right]\\
&=& \BE \left[ \ve \left\{ W^2 (Z, \BF_Z) \BS( \Lambda^{1/2} z; {\bf 0} ) \right\} {\ve}^T \left\{ W^2(Z, \BF_Z) \BS( \Lambda^{1/2}Z; \bf0) \right\} \right]\\
&& - \quad \ve( \tilde \Lambda) {\ve}^T( \tilde \Lambda )
\end{eqnarray*}

The matrix $\ve( \tilde\Lambda) \ve^T(\tilde\Lambda)$ consists of elements $\lambda_i\lambda_j$ at $(i,j)^\text{th}$ position of the $(i,j)^\text{th}$ block, and 0 otherwise. These positions correspond to variance and covariance components of on-diagonal elements. For the expectation matrix, all its elements are of the form $ \BE[ \sqrt{\lambda_a \lambda_b \lambda_c \lambda_d} Z_a Z_b Z_c Z_d . W^4 (Z, \BF_Z) / (Z^T \Lambda Z)^2]$, with $1 \leq a,b,c,d \leq p$. Since $W^4 (Z, \BF_Z) / (Z^T \Lambda Z)^2$ is even in $Z$, which has a spherically symmetric distribution, all such expectations will be 0 unless $a,b,c,d$ are all equal or pairwise equal. Following a similar derivation for spatial sign covariance matrices in \cite{ref:Biometrika14673_MagyarTyler}, we collect the non-zero elements and write the matrix of expectations:
%
$$ (\BI_{p^2} + \BK_{p,p}) \left\{ \sum_{a=1}^p \sum_{b=1}^p \tilde\gamma_{ab} (e_a e_a^T \otimes  e_b e_b^T) - \sum_{a=1}^p \tilde\gamma_{aa} (e_a e_a^T \otimes  e_a e_a^T) \right\} + \sum_{a=1}^p \sum_{b=1}^p \tilde\gamma_{ab} (e_a e_b^T \otimes  e_a e_b^T) $$
%
where $\BI_k = (e_1,...,e_k), \BK_{m,n} = \sum_{i=1}^m \sum_{j=1}^n \BJ_{ij} \otimes \BJ_{ij}^T$ with $\BJ_{ij} \in \BR^{m \times n}$ having 1 as $(i,j)$-th element and 0 elsewhere, and $\tilde\gamma_{mn} = \BE[ \lambda_m \lambda_n Z_m^2 Z_n ^2 . W^4 (Z, \BF_Z) / (Z^T \Lambda Z)^2]; 1 \leq m,n \leq p$.

\paragraph{}Putting everything together, denote by $\hat {\tilde \Lambda}$ the sample version of $\tilde \Lambda$, the weighted covariance matrix obtained from $\BF_\Lambda$, i.e. $\hat {\tilde \Lambda} = \sum_{i=1}^n W_n^2 (Z_i, \BF_{Z,n}) \BS( \Lambda^{1/2} Z_i; \hat \mu_n)/n $. Then the different types of elements in the matrix $\hat {\tilde \Lambda}$ are as given below ($1 \leq a,b,c,d \leq p$):

\begin{itemize}
\item Variance of on-diagonal elements
%
$$ A\BV( \sqrt n \hat {\tilde \Lambda} (a,a) ) = \BE \left[ \frac{ W^4(Z, \BF_Z) \lambda_a^2 Z_a^4}{(Z^T \Lambda Z)^2} \right] - \tilde\lambda_a^2 $$

\item Variance of off-diagonal elements ($a \neq b$)
%
$$ A\BV( \sqrt n \hat {\tilde \Lambda} (a,b) ) = \BE \left[ \frac{W^4 (Z, \BF_Z) \lambda_a \lambda_b Z_a^2 Z_b^2}{(Z^T \Lambda Z)^2} \right] $$

\item Covariance of two on-diagonal elements ($a \neq b$)
%
$$ A\BV(\sqrt n \hat {\tilde \Lambda} (a,a), \sqrt n \hat {\tilde \Lambda} (b,b) )
= \BE \left[ \frac{W^4 (Z, \BF_Z) \lambda_a \lambda_b Z_a^2 Z_b^2}{(Z^T \Lambda Z)^2} \right] - \tilde\lambda_{a} \tilde\lambda_{b} $$

\item Covariance of two off-diagonal elements ($a \neq b, c \neq d$)
%
$$ A\BV(\sqrt n \hat {\tilde \Lambda} (a,b), \sqrt n \hat {\tilde \Lambda} (c,d) ) = 0 $$

\item Covariance of one off-diagonal and one on-diagonal element ($a \neq b \neq c$)
%
$$ A\BV(\sqrt n \hat {\tilde \Lambda} (a,b), \sqrt n \hat {\tilde \Lambda} (c,c) ) = 0 $$
\end{itemize}

\noindent The above give all the elements of $V_{W,\Lambda}$. We plug these in \eqref{eqn:VWeqn} to recover $V_W$.

\section{Proofs}\label{section:appB}

\begin{proof}[Proof sketch of Corollary 2.4]
%A first step to obtain asymptotic normality for the high-dimensional location test statistic $C_{n,w}$ is obtaining an equivalent result of Lemma 2.1 in \cite{ref:JASA151658_WangPengLi}:
%
%\begin{Lemma}\label{Lemma:HDlemma21} Consider a random variable $\epsilon$ having an elliptical distribution with mean ${\bf 0}$ and covariance matrix $\Lambda$. Then, under the conditions 1-2 in Corollary 2.4, we have
%%
%\begin{eqnarray}
%\BE[ (\epsilon_{W1}^T \epsilon_{W2})^4 ] &=& O(1) \BE^2[ (\epsilon_{W1}^T \epsilon_{W2})^2 ]\\
%\BE[ (\epsilon_{W1}^T \Psi_{1W} \epsilon_{W1})^2 ] &=& O(1) \BE^2[ (\epsilon_{W1}^T \Psi_{1W} \epsilon_{W1})^2 ]\\
%\BE[ (\epsilon_{W1}^T \Psi_{1W} \epsilon_{W2})^2 ] &=& o(1) \BE^2[ (\epsilon_{W1}^T \Psi_{1W} \epsilon_{W1})^2 ]
%\end{eqnarray}
%%
%with $\epsilon_W = W(\epsilon, \BF_\epsilon) S(\epsilon)$ where $\BF_\epsilon$ is the distribution of $\epsilon$.
%\end{Lemma}
%%
%A proof of this lemma is derived using results in section 3 of \cite{ElKaroui09}, noticing that any-scalar valued 1-Lipschitz function of $\epsilon_W$ is a $W_\max$-Lipschitz function of $S(\epsilon)$.

%To derive the asymptotic distribution under contiguous alternatives we need the conditions (C3)-(C6) in \cite{ref:JASA151658_WangPengLi}, as well as
We start with slightly modified versions of Lemmas A.4 and A.5 in \cite{ref:JASA151658_WangPengLi}:

\begin{Lemma}\label{lemma:lemmaB1}
Given that condition 1 in Corollary 2.4 holds, we have $\lambda_{\max} (\Psi_{1W}) \leq 2 W_{\max} \frac{\lambda_{\max} (\Sigma) }{\text{Tr} (\Sigma)} (1+o(1))$.
\end{Lemma}

\begin{Lemma}\label{lemma:lemmaB2}
Define $\Psi_{3W} = \BE \left[ \frac{W^2(\epsilon, \BF_\epsilon)}{| \epsilon |^2} (\BI_p - S(\epsilon) S(\epsilon)^T )\right] $. Then $\lambda_{\max} (\Psi_{2W}) \leq W_{\max} \BE(| \epsilon |^{-1})$ and $\lambda_{\max} (\Psi_{3W}) \leq (W_{\max})^2 \BE( | \epsilon|^{-2})$. Further, if conditions 1 and 2 of Corollary 2.4 hold then $\lambda_{\min} (\Psi_{2W}) \geq \BE( W(\epsilon, \BF_\epsilon)/ | \epsilon |)(1+o(1))/\sqrt 3$.
\end{Lemma}
%
The lemmas can be proved using similar steps as the proofs of the original lemmas in \cite{ref:JASA151658_WangPengLi} and using the upper bound on the weight function. Corollary 2.4 is now proved by applying Corollary 2.2, plugging in upper bound of $\lambda_{\max} (\Psi_{1W})$ from Lemma~\ref{lemma:lemmaB1} and lower bound of $\lambda_{\max} (\Psi_{1W})$ from Lemma~\ref{lemma:lemmaB2} into the ARE expression.
\end{proof}

\begin{proof}[Proof of Theorem 3.4]
We suppose $G_n = (g_1, \ldots, g_p), L_n = \diag(l_1, \ldots, l_p)$. In spirit, this corollary is similar to Theorem 13.5.1 in \cite{ref:AndersonBook09}. We start with the following result, due to \citep{ref:SPL12765_Taskinenetal}, allows us to obtain asymptotic joint distributions of eigenvectors and eigenvalues of $\hat{\tilde \Sigma}$, provided we know the limiting distribution of $\hat{\tilde \Sigma}$ itself:

\begin{Theorem} \label{Theorem:decomp} 
Let $\BF_\Lambda$ be defined as before, and $\hat C$ be any positive definite symmetric $p \times p$ matrix such that at $F_\Lambda$ the limiting distribution of $\sqrt n \ve(\hat C - \Lambda)$ is a $p^2$-variate (singular) normal distribution with mean zero. Write the spectral decomposition of $\hat C$ as $\hat C = \hat P \hat\Lambda \hat P^T$. Then the limiting distributions of $\sqrt n \ve(\hat P - \BI_p)$ and $\sqrt n \ve( \hat\Lambda - \Lambda)$ are multivariate (singular) normal and
%
\begin{equation} \label{equation:decompEq}
\sqrt n \ve (\hat C - \Lambda)  = \left[ (\Lambda \otimes \BI_p) - (\BI_p \otimes \Lambda) \right] \sqrt n \ve (\hat P - \BI_p) + \sqrt n \ve (\hat \Lambda - \Lambda) + o_P(1)
\end{equation}
\end{Theorem}

The first matrix picks only off-diagonal elements of the left-hand side and the second one only diagonal elements. We shall now use this as well as the form of the asymptotic covariance matrix of the vectorized $\hat {\tilde \Sigma}$, i.e. $V_W$ to obtain limiting variance and covariances of eigenvalues and eigenvectors.

Due to the decomposition \eqref{equation:decompEq} we have, for $\BF_\Lambda$, the following relation between any off-diagonal element of $\hat{\tilde \Lambda}$ and the corresponding element in the estimate of eigenvectors, say $\hat {\tilde \Gamma}_\Lambda$:

$$ \sqrt n \hat {\tilde \gamma}_{\Lambda, ij} = \sqrt n \frac{\hat {\tilde \Lambda} (i,j) }{\tilde \lambda_i - \tilde \lambda_j}; \quad i \neq j$$

So that for eigenvector estimates of the original $\BF$ we have
%
\begin{equation}\label{equation:app1}
\sqrt n ( \hat{\tilde \gamma}_{i} - \gamma_i) =
\sqrt n \Gamma ( \hat {\tilde \gamma}_{\Lambda, i} - e_i ) =
\sqrt n \left[ \sum_{k=1; k \neq i}^p \hat {\tilde \gamma}_{\Lambda,i,k} \gamma_k + (\hat {\tilde \gamma}_{\Lambda,i,i} - 1) \gamma_i \right]
\end{equation}
%
Now $\sqrt n (\hat {\tilde \gamma}_{\Lambda,i,i} - 1) - 1) =  o_P(1)$ and $A\BV(\sqrt n \hat {\tilde \Lambda} (i,k), \sqrt n \hat {\tilde \Lambda} (i,l) ) = 0$ for $k \neq l$, so the above equation implies
%
$$ A\BV(g_i) = A \BV (\sqrt n ( \hat{\tilde \gamma}_{i} - \gamma_i)) = \sum_{k=1; k \neq i}^p \frac{A\BV(\sqrt n \hat {\tilde \Lambda} (i,k))}{(\tilde \lambda_i - \tilde \lambda_k)^2} \Gamma_k \Gamma_k^T $$
%

For the covariance terms, from \eqref{equation:app1} we get, for $i \neq j$,
%
\begin{eqnarray*}
A\BV(g_i, g_j) &=&
A\BV(\sqrt n ( \hat{\tilde \gamma}_{i} - \gamma_i),
\sqrt n ( \hat{\tilde \gamma}_{j} - \gamma_j))\\
&=& A\BV \left(
\sum_{k=1; k \neq i}^p \sqrt n \hat {\tilde \gamma}_{\Lambda,ik} \gamma_k,
\sum_{k=1; k \neq j}^p \sqrt n \hat {\tilde \gamma}_{\Lambda,jk} \gamma_k \right)\\
&=& A\BV \left(
\sqrt n \hat {\tilde \gamma}_{\Lambda,ik} \gamma_j,
\sqrt n \hat {\tilde \gamma}_{\Lambda,ik} \gamma_i \right)\\
&=& - \frac{A\BV(\sqrt n \hat {\tilde \Lambda} (i,j))}
{(\tilde \lambda_i - \tilde \lambda_j)^2} \gamma_j \gamma_i^T
\end{eqnarray*}
%
The exact forms given in the statement of the corollary now follows from the  Form of $V_W$ in Section~\ref{sec:appA}.

\paragraph{}For the on-diagonal elements of $\hat {\tilde \Lambda}$, using Theorem \ref{Theorem:decomp} we have for the $i^\text{th}$ eigenvalue of $\hat {\tilde \Lambda}$, say $\lambda_{\Lambda,i}$,
%
$$ \sqrt n \hat {\tilde \lambda}_{\Lambda,i} = \sqrt n \hat {\tilde \Lambda} (i,i), $$
%
for $i = 1,...,p$. Hence

\begin{eqnarray*}
A\BV(l_i) &=& A\BV( \sqrt n (\hat {\tilde \lambda}_{\Lambda,i} - \tilde \lambda_i) )\\
&=& A\BV( \sqrt n (\hat {\tilde \lambda}_{\Lambda,i} - \tilde \lambda_{\Lambda,i}) )\\
&=& A\BV(\sqrt n \hat {\tilde \Lambda} (i,i))
\end{eqnarray*}

A similar derivation gives the expression for $A\BV(l_i,l_j); i \neq j$. Finally, since the asymptotic covariance between an on-diagonal and an off-diagonal element of $\hat {\tilde \Lambda}$, it follows that the elements of $G_n$ and diagonal elements of $L_n$ are independent.
\end{proof}

\bibliographystyle{apalike}
\bibliography{WeightedSignBib_01_29_19}

\end{document}

### 2019-09-13 EJSSubmission/WeightedSign_EJS_Dispersion_02_24_19_1.tex
supple done

@@
 can be explicitly obtained in terms of $\Gamma$, $\Lambda$ and $\BF$, but is 
-algebraic in nature and hence omitted here.
+algebraic in nature. We present it in the supplementary material.
 
@@
 The proof of this result follows from using Theorem~\ref{Theorem:CLT1} and using 
-techniques similar to a corresponding result in \citet{ref:SPL12765_Taskinenetal}, 
-and we omit the  algebraic details here.
+techniques similar to a corresponding result in \citet{ref:SPL12765_Taskinenetal}. We omit the algebraic details here and put it in the supplementary material.
 

### 2019-09-13 EJSSubmission/WeightedSign_EJS_WeightedSpatialQuantiles_02_24_19_1.tex
supple done

@@
 \frac{ \lambda_{\min} (\Psi_1) \lambda_{\min}^2 (\Psi_{2W})}
-{k \lambda_{\max} (\Psi_1) \lambda_{\max}^2 (\Psi_2)}
+{k \lambda_{\max} (\Psi_{1W}) \lambda_{\max}^2 (\Psi_2)}
 \ean
 %
-Consequently, if $k / \lambda_{\min}^2 (\Psi_{2W}) < \lambda_{\min} (\Psi_1) /(\lambda_{\max} (\Psi_1) \lambda_{\max}^2 (\Psi_2))$ then this asymptotic relative efficiency is larger than 1. 
+Consequently, if $k / \lambda_{\min}^2 (\Psi_{2W}) < \lambda_{\min} (\Psi_1) /(\lambda_{\max} (\Psi_{1W}) \lambda_{\max}^2 (\Psi_2))$ then this asymptotic relative efficiency is larger than 1. 
 \end{Corollary}
@@
 \begin{enumerate}
-\item $Tr(\Sigma^4) = o( Tr^2 (\Sigma^2) )$,
+%\item $Tr(\Sigma^4) = o( Tr^2 (\Sigma^2) )$,
 
-\item $\frac{Tr^4(\Sigma)}{ Tr^2 (\Sigma^2)} \exp \left\{ - \frac{Tr^2 (\Sigma)}
-{ 128 \lambda_{\max}^2 (\Sigma)} \right\} = o(1)$,
+%\item $\frac{Tr^4(\Sigma)}{ Tr^2 (\Sigma^2)} \exp \left\{ - \frac{Tr^2 (\Sigma)}
+%{ 128 \lambda_{\max}^2 (\Sigma)} \right\} = o(1)$,
 
@@
 
-The conditions 1-4 in Corollary~\ref{Cor:Elliptic_ARE} are due to \cite{ref:JASA151658_WangPengLi}, and ensure that the eigenvalues of $\Sigma$ are bounded away from 0 and $\infty$.
+The conditions 1 and 2 in Corollary~\ref{Cor:Elliptic_ARE} are due to \cite{ref:JASA151658_WangPengLi}, and ensure that the eigenvalues of $\Sigma$ are bounded away from 0 and $\infty$.
 Corollary~\ref{Cor:Elliptic_ARE} can be proved using Corollary~\ref{Cor:ARE}, the fact that for elliptical distributions $\Psi_1$ is non-singular \cite{ref:SPL12765_Taskinenetal}, then using and expanding upon Lemma A.5 in \cite{ref:JASA151658_WangPengLi}.

### 2019-09-13 EJSSubmission/WeightedSign_EJS-supp.tex
.

@@
 %
-Now $\sqrt n (\hat {\tilde \gamma}_{\Lambda,i,i} - 1) - 1) =  o_P(1)$ and $A\BV(\sqrt n \hat {\tilde \Lambda} (i,k), \sqrt n \hat {\tilde \Lambda} (i,l) ) = 0$ for $k \neq l$, so the above equation implies
+Now $\sqrt n (\hat {\tilde \gamma}_{\Lambda,i,i} - 1) =  o_P(1)$ and $A\BV(\sqrt n \hat {\tilde \Lambda} (i,k), \sqrt n \hat {\tilde \Lambda} (i,l) ) = 0$ for $k \neq l$, so the above equation implies
 %
-$$ A\BV(g_i) = A \BV (\sqrt n ( \hat{\tilde \gamma}_{i} - \gamma_i)) = \sum_{k=1; k \neq i}^p \frac{A\BV(\sqrt n \hat {\tilde \Lambda} (i,k))}{(\tilde \lambda_i - \tilde \lambda_k)^2} \Gamma_k \Gamma_k^T $$
+$$ A\BV(g_i) = A \BV (\sqrt n ( \hat{\tilde \gamma}_{i} - \gamma_i)) = \sum_{k=1; k \neq i}^p \frac{A\BV(\sqrt n \hat {\tilde \Lambda} (i,k))}{(\tilde \lambda_i - \tilde \lambda_k)^2} \gamma_k \gamma_k^T $$
 %

### 2019-11-12 EJSSubmission/WeightedSign_EJS-R1-rebuttal.tex
started rebuttal draft

%\documentclass[ejs]{imsart}
\documentclass[11pt,letterpaper]{article}
\pdfoutput=1

\RequirePackage[OT1]{fontenc}
\RequirePackage[colorlinks,citecolor=blue,urlcolor=blue]{hyperref}
\usepackage{amssymb,amsmath,amsthm,color,outlines,subfigure,comment}
\usepackage[small]{caption}
\usepackage{graphics}
\usepackage{graphicx}
\usepackage{stackrel}
\usepackage[round]{natbib}

% DON'T change margins - should be 1 inch all around.
\addtolength{\evensidemargin}{-.5in}
\addtolength{\oddsidemargin}{-.5in}
\addtolength{\textwidth}{0.9in}
\addtolength{\textheight}{0.9in}
\addtolength{\topmargin}{-.4in}

%%%%%% put your definitions there:
%\startlocaldefs
\newcommand{\bfa}{{\bf{a}}}
\newcommand{\bfb}{{\bf{b}}}
\newcommand{\bfc}{{\bf{c}}}
\newcommand{\bfd}{{\bf{d}}}
\newcommand{\bfe}{{\bf{e}}}
\newcommand{\bff}{{\bf{f}}}
\newcommand{\bfg}{{\bf{g}}}
\newcommand{\bfl}{{\bf{l}}}
\newcommand{\bfp}{{\bf{p}}}
\newcommand{\bfq}{{\bf{q}}}
\newcommand{\bfr}{{\bf{r}}}
\newcommand{\bfs}{{\bf{s}}}
\newcommand{\bft}{{\bf{t}}}
\newcommand{\bfu}{{\bf{u}}}
\newcommand{\bfv}{{\bf{v}}}
\newcommand{\bfw}{{\bf{w}}}
\newcommand{\bfx}{{\bf{x}}}
\newcommand{\bfy}{{\bf{y}}}
\newcommand{\bfz}{{\bf{z}}}

\newcommand{\bfA}{{\mathbf{A}}}
\newcommand{\bfB}{{\mathbf{B}}}
\newcommand{\bfC}{{\mathbf{C}}}
\newcommand{\bfD}{{\mathbf{D}}}
\newcommand{\bfE}{{\mathbf{E}}}
\newcommand{\bfF}{{\mathbf{F}}}
\newcommand{\bfG}{{\mathbf{G}}}
\newcommand{\bfH}{{\mathbf{H}}}
\newcommand{\bfI}{{\mathbf{I}}}
\newcommand{\bfL}{{\mathbf{L}}}
\newcommand{\bfP}{{\mathbf{P}}}
\newcommand{\bfR}{{\mathbf{R}}}
\newcommand{\bfS}{{\mathbf{S}}}
\newcommand{\bfT}{{\mathbf{T}}}
\newcommand{\bfU}{{\mathbf{U}}}
\newcommand{\bfV}{{\mathbf{V}}}
\newcommand{\bfW}{{\mathbf{W}}}
\newcommand{\bfX}{{\mathbf{X}}}
\newcommand{\bfY}{{\mathbf{Y}}}
\newcommand{\bfZ}{{\mathbf{Z}}}

\newcommand{\BA}{{\mathbb{A}}}
\newcommand{\BB}{{\mathbb{B}}}
\newcommand{\BC}{{\mathbb{C}}}
\newcommand{\BE}{{\mathbb{E}}}
\newcommand{\BD}{{\mathbb{D}}}
\newcommand{\BF}{{\mathbb{F}}}
\newcommand{\BG}{{\mathbb{G}}}
\newcommand{\BH}{{\mathbb{H}}}
\newcommand{\BI}{{\mathbb{I}}}
\newcommand{\BJ}{{\mathbb{J}}}
\newcommand{\BK}{{\mathbb{K}}}
\newcommand{\BL}{{\mathbb{L}}}
\newcommand{\BP}{{\mathbb{P}}}
\newcommand{\BR}{{\mathbb{R}}}
\newcommand{\BS}{{\mathbb{S}}}
\newcommand{\BT}{{\mathbb{T}}}
\newcommand{\BU}{{\mathbb{U}}}
\newcommand{\BV}{{\mathbb{V}}}
\newcommand{\BW}{{\mathbb{W}}}
\newcommand{\BX}{{\mathbb{X}}}
\newcommand{\BY}{{\mathbb{Y}}}
\newcommand{\BZ}{{\mathbb{Z}}}

\newcommand{\BCOV}{{\mathbb{COV}}}

\newcommand{\colrit}{\color{red} \it}
\newcommand{\colrbf}{\color{red} \bf}
\newcommand{\colbit}{\color{blue} \it}
\newcommand{\colbbf}{\color{blue} \bf}
\newcommand{\colmit}{\colm \it}
\newcommand{\colmbf}{\colm \bf}

\newcommand{\bfalpha}{{\boldsymbol{\alpha}}}
\newcommand{\bfbeta}{{\boldsymbol{\beta}}}
\newcommand{\bfepsilon}{{\boldsymbol{\epsilon}}}
\newcommand{\bftheta}{{\boldsymbol{\theta}}}
\newcommand{\bfgamma}{{\boldsymbol{\gamma}}}
\newcommand{\bfmu}{{\boldsymbol{\mu}}}
\newcommand{\bfpi}{{\boldsymbol{\pi}}}

\newcommand{\bfBeta}{{\boldsymbol{\Beta}}}
\newcommand{\bfGamma}{{\boldsymbol{\Gamma}}}
\newcommand{\bfOmega}{{\boldsymbol{\Omega}}}
\newcommand{\bfSigma}{{\boldsymbol{\Sigma}}}
\newcommand{\bfPhi}{{\boldsymbol{\Phi}}}

\newcommand{\bfZero}{\bf 0}
\newcommand{\bfOne}{\bf 1}
\newcommand{\iid}{\stackrel{i.i.d.}{\sim}}
\newcommand{\raro}{\rightarrow}

\newcommand{\cA}{\mathcal{A}}
\newcommand{\cB}{\mathcal{B}}
\newcommand{\cC}{\mathcal{C}}
\newcommand{\cD}{\mathcal{D}}
\newcommand{\cE}{\mathcal{E}}
\newcommand{\cF}{\mathcal{F}}
\newcommand{\cH}{\mathcal{H}}
\newcommand{\cI}{\mathcal{I}}
\newcommand{\cM}{\mathcal{M}}
\newcommand{\cN}{\mathcal{N}}
\newcommand{\cS}{\mathcal{S}}
\newcommand{\cX}{\mathcal{X}}
\newcommand{\cY}{\mathcal{Y}}

\def\baq#1\eaq{\begin{align}#1\end{align}}
\def\ban#1\ean{\begin{align*}#1\end{align*}}
\newcommand{\draro}{ \stackrel{{\mathcal D}}{\Rightarrow} }

\def\bredbf#1\eredbf{{\color{red}{\bf ???? #1 ????}}}
\def\BeginRedComment#1\EndRedComment{({\color{red}{\bf Comment:} {\it #1}}) }
\def\BeginBlueComment#1\EndBlueComment{({\color{blue}{\bf Comment:} {\it #1}}) }

\DeclareMathOperator*{\ve}{vec}
\DeclareMathOperator*{\diag}{diag }
\DeclareMathOperator*{\supp}{supp }
\DeclareMathOperator*{\Tr}{Tr}
\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\Th}{^{\text{th}}}

\makeatletter
\newcommand{\opnorm}{\@ifstar\@opnorms\@opnorm}
\newcommand{\@opnorms}[1]{%
  \left|\mkern-1.5mu\left|\mkern-1.5mu\left|
   #1
  \right|\mkern-1.5mu\right|\mkern-1.5mu\right|
}
\newcommand{\@opnorm}[2][]{%
  \mathopen{#1|\mkern-1.5mu#1|\mkern-1.5mu#1|}
  #2
  \mathclose{#1|\mkern-1.5mu#1|\mkern-1.5mu#1|}
}
\makeatother

\newtheorem{Theorem}{Theorem}[section]
\newtheorem{Lemma}[Theorem]{Lemma}
\newtheorem{Corollary}[Theorem]{Corollary}
\newtheorem{Proposition}[Theorem]{Proposition}
\newtheorem{Conjecture}[Theorem]{Conjecture}
\theoremstyle{definition} \newtheorem{Definition}[Theorem]{Definition}

%\endlocaldefs

\begin{document}

\title{On Weighted Multivariate Sign Functions}
\date{}
\author{
Subhabrata Majumdar and Snigdhansu Chatterjee
}
\maketitle

\section*{Response to referee comments}

\paragraph{Referee:}
Do I understand correctly that your weights are not allowed to depend on $q$? Then your claim on top of page 3 that this is the same object that has been studied before (e.g., in \cite{ref:AoS97435_Koltchinskii}) is incorrect. If it is allowed to depend on $q$, then please explain how your results
are different from the existing literature.

\paragraph{Authors:} 
We think this ambiguity was a result of assuming $\BF$ as a general distribution in the beginning, but later having $\BF \equiv \BF_X$ in all our applications. In that case, $W(X,\BF)$ shall depend on $q$ implicitly since $q$ is a parameter of $\BF$. To bypass this confusion, we now assume $X \sim \BF$ from the beginning (highlighted in the introduction, page 2), and then add a remark after theorem 2.1 saying it still goes through if $\BF$ is not $\BF_X$.

While theoretical properties of related quantities have been established in papers like \cite{ref:AoS97435_Koltchinskii}, sometimes under different formulations (e.g. the weight function in \cite{ref:AoS97435_Koltchinskii} is a convex non-decreasing function of $|x - \mu|$), we start off from a broad-based formulation of the weights and then concentrate on the more practical aspects of how weights affect robustness and efficiency. We add a discussion on this in the introduction {\color{red} (have to add that)}.

\subsection*{Comment (b)}

\paragraph{Referee:}
Regarding the proof of Theorem 2.1: if you claim that this is a new result, the proof can not be omitted completely: please include it in the supplementary material. If it is not new please give a precise reference.

\paragraph{Authors:}
We have included a proof sketch of the theorem, following arguments from \cite{ref:AoS921514_Niemiro} and \cite{ref:AoS891631_Haberman}. Please see highlighted text in page 4.

\subsection*{Comment (c)}
\paragraph{Referee:}
I could not understand Corollary 2.2: is $q_0$ still a minimizer of $\Psi(q; 0; \BF)$? If so, how can the weight depend on this unknown quantity? Even if $q_0$ is a fixed vector, this still does not make sense to me. Additionally, please show that conditions A1-A3 hold in your examples.

\paragraph{Authors:}
This ambiguity was also the result of not assuming $X \sim \BF$ from the beginning. In any case, under the present setup we replace this with a more general result that does not need the assumption on $W(X,\BF)$. Please see the response to comment (e) for more detail on the new Corollary 2.2.

\subsection*{Comment (d)}
\paragraph{Referee:}
Page 3 states “We report only the case of the weighted spatial median for brevity..” In this case, it could be better to focus on the median everywhere and avoid mentioning general quantiles.

\paragraph{Authors:}
We indeed do not elaborate on weighted spatial quantiles in this paper. Following the referee's suggestion, now we only give their general definition in Section 2, and then discuss the weighted spatial median in detail. The modifications are highlighted in page 3.

\subsection*{Comment (e)}
\paragraph{Referee:}
Corollary 2.4 states “then $S(X; q_0)$ is uniform on the unit ball in $\BR^p$..” – do you mean $S(Z; q_0)$? If $X$ has arbitrary elliptically symmetric distribution, this is not true. Moreover, why is it interesting in this case to consider the case when $\BF$ is the (unknown) distribution of $X$?

\paragraph{Authors:}
The referee is right, the spatial sign is indeed not independent of the norm for non-spherical but elliptical distributions. Fortunately, with a few weak conditions on $\Sigma$ from \cite{ref:JASA151658_WangPengLi} we were able to prove that the ARE is larger than 1 for general elliptical distributions. To accommodate this we have changed Corollary 2.2 to make it more general, and then changed Corollary 2.4 to accommodate this (highlighted in pages 4-6).

We thank the referee for this comment, which led to a rigorous revision of the theoretical conditions for the weighted spatial median.

\subsection*{Comment (f)}
\paragraph{Referee:}
Page 5: “..we propose using $W(x; \BF_n)$: please define what you mean by an empirical distribution function here, as $X$ is a vector.

\paragraph{Authors:}
This was a typo. We have corrected it.

\subsection*{Comment (g)}
\paragraph{Referee:}
The weight functions discussed in section 2.1 can only be computed if the distribution of $X$ is known. Why would such functions be of any use in statistical context? If the unknown distribution is replaced by its empirical version, why would all the useful properties be
preserved? I suggest explaining these points clearly in the beginning.

\paragraph{Authors:}
We have added a paragraph in the Introduction to motivate the use of weighted signs, emphasizing on the unknown quantities $\mu$ and $\BF$, and that they need to be replaced by their empirical version in a practical scenario. Please see the highlighted part in Page 2 for this discussion.

\subsection*{Comment (h)}
\paragraph{Referee:}
Equation (5): is $\tilde X$ a statistic?

\paragraph{Authors:}
$\tilde X$ is a random variable obtained by replacing the magnitude of $X$ with its weight. We mention this in page 7 (highlighted).

\subsection*{Comment (i)}
\paragraph{Referee:} On page 7, it is stated that “We now discuss the properties of the sample version $\tilde \Sigma$ computed from $X$. In practice, we cannot obtain $W(x)?W(x; F)$, and consequently use $W(x; \BF_n)$ instead..” – this is a good point, but I suggest discussing it earlier in the paper, as it affects many assumptions made prior to this statement.

\paragraph{Authors:}
The added paragraph in Page 2 (please see response to comment (g)) clarifies this earlier now.

\subsection*{Minor comment (a)}
\paragraph{Referee:}
Last paragraph of page 3: should $\hat q_n$ be $\hat q_{n W}$?

\paragraph{Authors:}
This was a typo. We have corrected it.

%\newpage
%\input{misc}

\bibliographystyle{apalike}
\bibliography{WeightedSignBib_01_29_19}

\end{document}

### 2020-09-17 EJSSubmission/R1/WeightedSign_EJS_Conclusion_02_24_19_1.tex
.

--- 2019-08-09 EJSSubmission/WeightedSign_EJS_Conclusion_02_24_19_1.tex
@@
-\section{Conclusions}
+\section{Conclusion}
 \label{Sec:Conclusion}
-
 We propose the use of a weighted multivariate sign transformation for robust 
@@
 size, and where data are from a separable Hilbert space, will be considered in a future 
-work. There are only few conceptual challenges to such extensions, however, there are 
+work. There are few conceptual difficulties to such extensions, however, there are 
 several technical and algebraic challenges.

### 2020-09-20 EJSSubmission/R1/WeightedSign_EJS_Introduction_09_17_20_1.tex
almost submitted R&R

--- 2019-08-16 EJSSubmission/WeightedSign_EJS_Introduction_02_24_19_1.tex
@@
  from three well-known data depth functions: the \textit{half-space depth}, 
- the \textit{Mahalanobis depth}, and the \textit{projection depth}.
+ the \textit{Mahalanobis depth}, and the \textit{projection depth}. Note that for i.i.d. data, there are three parameters involved here: the location parameter $\mu$ in 
+ \eqref{eq:GQSign}, the distribution $\BF$ used for the weight function, and the distribution $\BF_{X}$ of $X_{1}$.
+For clarity and to mirror the contexts of how data depth has been used in the literature \cite{LiuPareliusSingh99, ref:DIMACS061_Serfling}, we fix $\BF = \BF_{X}$ for this paper, although in Section~\ref{Sec:WSQuantiles} we briefly remark on the case when these  distributions are different.
+Also note that
+ in many problems of interest, $\BF$ is 
+unknown and  data-depths are computed using $\BF_{n}$, however, under very standard regularity conditions (for example, see assumptions \textbf{B1-B3} below), the 
+properties of $W (x, \BF)$ and $W (x, \BF_{n})$ are close enough for both asymptotic theory and practical applicability.
 
  %\begin{comment}
-\begin{figure}[t]
+\begin{figure}[t!]
 %\captionsetup{justification=centering, font=footnotesize}
@@
 %%% These ones have sample size = 700, just right  for EJS
-\includegraphics[width=\textwidth]{./Plots_SC/WeightedSignAll}
+\includegraphics[width=\textwidth]{./Plots/WeightedSignAll}
 %\includegraphics[width=0.45\textwidth]{./Plots_SC/WeightedSign_Scatter_700_02_27_19} &
@@
 bottom right) panels depict these values where the weights have been generated using 
-Mahalnobis depth (respectively Tukey's half-space depth and the projection depth). The 
+Mahalanobis depth (respectively Tukey's half-space depth and the projection depth). The 
 blue triangles are the weighted sign values of the outliers. Notice that the eigenvectors 
@@
 As a location estimator, it has several interesting robustness properties and can be shown to be more efficient that some existing robust location estimators, thus making it a perfect candidate to estimate $\mu$.
-On the other hand, setting $\BF$ as $\BF_X$, i.e.
+%On the other hand, setting $\BF$ as $\BF_X$, i.e.
 the distribution of $X$ has the clear interpretation of differentially weighting observations based on their inlyingness to the overall data distribution.

### 2020-09-20 EJSSubmission/R1/WeightedSign_EJS_WeightedSpatialQuantiles_09_17_20_1.tex
almost submitted R&R

--- 2019-09-13 EJSSubmission/WeightedSign_EJS_WeightedSpatialQuantiles_02_24_19_1.tex
@@
  $u \in \textrm{int} {\cX}_{0; 1}$. We also fix the set of probability measures $\cM$, 
- and select $\BF \in \cM$. Consider a random element $X \in \cX$. 
+ and select $\BF \in \cM$. Consider a random element $X \in \cX$, and define the 
+ function $\Phi (q; X, u, \BF) = W (X, \BF) \bigl\{ | X - q | 
++ \langle u, X - q \rangle \bigr\}$. 
 We define the $(u, \BF)$-th \textit{weighted spatial quantile} of $\cX$ 
-as the minimizer $q (u, \BF) \in \cX$ of 
+as the minimizer $q (u, \BF) \in \cX$ of the expectation of $\Phi (q; X, u, \BF)$, 
+that is
 \baq
 \Psi (q; u, \BF) = \BE \Bigl[ W (X, \BF) \bigl\{ | X - q | 
-+ \langle u, X - q \rangle \bigr\} \Bigr].
++ \langle u, X - q \rangle \bigr\} \Bigr] = \BE \Phi (q; X, u, \BF).
 \label{eq:WeightedQuantile}
@@
 This is a natural generalization of the spatial median \cite{ref:JASA96862_Chaudhuri, ref:Biometrika48414_Haldane,ref:AoS97435_Koltchinskii} ($W(X, \BF) \equiv 1$ and $u = {\bf 0}_p$), or more general spatial quantiles \cite{ref:AoS17591_Cardotetal_Median_HilbertSpace, ref:AoS141203_ChakrabortyChaudhuri_Banach_Quantile, ref:Bernoulli152308_Minsker_Median_Banach} ($W(X, \BF) \equiv 1$).
+We assume that
+$\Phi (q; X, u, \BF)$ is convex in $q$ for $\BF$-almost all values of $x \in \cX$.
 
@@
 
-\item[(A3)] $\BE W^{2} (X, \BF)  S (X; q) S^{T} (X; q)$ exists for all $q$ in a neighborhood of $q_{0}$. 
+\item[(A3)] $ {\frac{\partial^{2}} {\partial q^{2}}} \Psi (q; 0, \BF)$
+exists for all $q$ in a neighborhood of $q_{0}$, and we use the notations
+\ban
+\Psi_{1W}   & = 
+\Bigl( {\frac{\partial} {\partial q}} \Psi (q_{0}; 0, \BF) \Bigr)
+ \Bigl( {\frac{\partial} {\partial q}} \Psi (q_{0}; 0, \BF) \Bigr)^{T}, \\
+\Psi_{2W}   & = {\frac{\partial^{2}} {\partial q^{2}}} \Psi (q_{0}; 0, \BF). 
+\ean
  \end{description}
@@
  \ban 
- n^{1/2} (\hat{q}_{nW} - q_{0}) & \draro N(0, \Psi_{2W}^{-1} \Psi_{1W} \Psi_{2W}^{-1}), 
- \text{ where } \\
- \Psi_{2W} & = 
- \BE W (X, \BF)\Bigl[  |X - q_0|^{-1} ( \BI_{p} - S (X; q_{0}) S^{T} (X; q_{0}))  \Bigr] 
- \\
- \Psi_{1W}  & = \BE   W^{2} (X, \BF)  S (X; q_{0}) S^{T} (X; q_{0}).
+ n^{1/2} (\hat{q}_{nW} - q_{0}) & \draro N(0, \Psi_{2W}^{-1} \Psi_{1W} \Psi_{2W}^{-1}).
  \ean
@@
 n^{1/2} (\hat{q}_{nW} - q_{0}) =
-- \frac{\Psi_{2W}}{\sqrt n} \sum_{i=1}^n W (X_i, \BF)  S (X_i; q_0) + o_P(1).
+- \frac{\Psi_{2W}}{\sqrt n} 
+\sum_{i=1}^n \nabla \Phi (q; X_{i}, u, \BF)
++ o_P(1),
 \end{align*}
 %
+where $\nabla \Phi (q; X_{i}, u, \BF)$ is any measurable subgradient of 
+$\Phi (q; X_{i}, u, \BF)$. 
 Theorem~\ref{Thm:WSMedian} follows by applying the central limit theorem.
 
-\paragraph{Remark.} Note that for the result in Theorem~\ref{Thm:WSMedian} to go through, it is not necessary for $\BF$ to be the distribution of $X$.
-Other choices of $\BF$, e.g.
-\cite{StatPaper18},  may lead to interesting interpretations of $W(.
-,\BF)$ and the resulting location estimator and can be explored further.
-%}
+\paragraph{Remark.} Note that the technical conditions for the result presented in Theorem~\ref{Thm:WSMedian} is one of several alternatives that can conceived, and the scope of this result is broader than what is presented above.
+First, note that if $\BF$
+and $\BF_{X}$ are different and the weights are not a function of $q$, 
+a situation that may arise in hypothesis testing problems where the weights are based 
+on the null distribution, the convexity of $\Phi (q; X_{i}, u, \BF)$ follows automatically 
+and is not an assumption.
+Second, even if $\Phi (q; X_{i}, u, \BF)$ is not convex but sufficiently smooth, we can have a central limit theorem, for example, by using techniques similar to \cite{ref:CBose_AoS05414}.
+Choices of $\BF$ other than $\BF_{X}$, e.g. \cite{StatPaper18},  may lead to interesting interpretations of $W(. ,\BF)$ and the resulting location estimator and will be explored further in future.
 
@@
 
+%A context where 
 It is possible to make the above asymptotic relative efficiency to tend to infinity with 
 $p$, for example by choosing $k = \exp\{- p^{2} \}$. Such tending to infinity efficiencies 
-are also achievable for fixed $k$,  for example, if $|X - q_{0}|^{2}$ is a Gamma random 
-variable with shape parameter $ = 2 + \exp\{- p^{2} \}$. We leave it to future work to 
+are also achievable for fixed $k$,  for example, in the context of some hypothesis tests.
+%ing problems.
+%f $|X - q_{0}|^{2}$ is a Gamma random 
+%variable with shape parameter $ = 2 + \exp\{- p^{2} \}$. 
+We leave it to future work to 
 study such efficiencies more generally.
@@
 Corollary~\ref{Cor:Elliptic_ARE} implies that there is a wide frame of distributions and  choices of weight functions where there is a benefit to considering weighted spatial medians.
-In fact, the choice of weight functions is even broader: only location invariance is required for Corollary~\ref{Cor:Elliptic_ARE} to hold.
-We only choose to restrict ourselves here because the subsequent analysis uses weights based on affine invariant data depth functions.
+In fact, Corollary~\ref{Cor:Elliptic_ARE} can be established under just
+location invariance condition on weights, we use the stronger affine invariance condition
+here only because the subsequent sections use weights based on affine invariant 
+data depth functions.
 Also note that in case \eqref{eqn:CorElliptic_ARE_eqn} does not hold for the original form of a weight function, one can scale all weights by an appropriate constant to reduce the value in the left hand side of \eqref{eqn:CorElliptic_ARE_eqn} to satisfy the condition.
@@
 In actual computations, in place of $W (x, \BF)$ we propose using $W (x, \BF_{n})$ where
-$ \BF_{n}(z) = (np)^{-1} \sum_{i = 1}^{n} \sum_{j=1}^p
+$ \BF_{n}(z) = n^{-1} \sum_{i = 1}^{n} \prod_{j=1}^{p}
 \cI (X_{ij} \leq z_j ), z \in \BR^p

### 2020-09-20 EJSSubmission/WeightedSign_EJS_R1_ResponseToComments_09_20_20.tex
almost submitted R&R

%\documentclass[ejs]{imsart}
\documentclass[11pt,letterpaper]{article}
\pdfoutput=1

\RequirePackage[OT1]{fontenc}
\RequirePackage[colorlinks,citecolor=blue,urlcolor=blue]{hyperref}
\usepackage{amssymb,amsmath,amsthm,color,outlines,subfigure,comment}
\usepackage[small]{caption}
\usepackage{graphics}
\usepackage{graphicx}
\usepackage{stackrel}
\usepackage[round]{natbib}

% DON'T change margins - should be 1 inch all around.
\addtolength{\evensidemargin}{-.5in}
\addtolength{\oddsidemargin}{-.5in}
\addtolength{\textwidth}{0.9in}
\addtolength{\textheight}{0.9in}
\addtolength{\topmargin}{-.4in}

%%%%%% put your definitions there:
%\startlocaldefs
\newcommand{\bfa}{{\bf{a}}}
\newcommand{\bfb}{{\bf{b}}}
\newcommand{\bfc}{{\bf{c}}}
\newcommand{\bfd}{{\bf{d}}}
\newcommand{\bfe}{{\bf{e}}}
\newcommand{\bff}{{\bf{f}}}
\newcommand{\bfg}{{\bf{g}}}
\newcommand{\bfl}{{\bf{l}}}
\newcommand{\bfp}{{\bf{p}}}
\newcommand{\bfq}{{\bf{q}}}
\newcommand{\bfr}{{\bf{r}}}
\newcommand{\bfs}{{\bf{s}}}
\newcommand{\bft}{{\bf{t}}}
\newcommand{\bfu}{{\bf{u}}}
\newcommand{\bfv}{{\bf{v}}}
\newcommand{\bfw}{{\bf{w}}}
\newcommand{\bfx}{{\bf{x}}}
\newcommand{\bfy}{{\bf{y}}}
\newcommand{\bfz}{{\bf{z}}}

\newcommand{\bfA}{{\mathbf{A}}}
\newcommand{\bfB}{{\mathbf{B}}}
\newcommand{\bfC}{{\mathbf{C}}}
\newcommand{\bfD}{{\mathbf{D}}}
\newcommand{\bfE}{{\mathbf{E}}}
\newcommand{\bfF}{{\mathbf{F}}}
\newcommand{\bfG}{{\mathbf{G}}}
\newcommand{\bfH}{{\mathbf{H}}}
\newcommand{\bfI}{{\mathbf{I}}}
\newcommand{\bfL}{{\mathbf{L}}}
\newcommand{\bfP}{{\mathbf{P}}}
\newcommand{\bfR}{{\mathbf{R}}}
\newcommand{\bfS}{{\mathbf{S}}}
\newcommand{\bfT}{{\mathbf{T}}}
\newcommand{\bfU}{{\mathbf{U}}}
\newcommand{\bfV}{{\mathbf{V}}}
\newcommand{\bfW}{{\mathbf{W}}}
\newcommand{\bfX}{{\mathbf{X}}}
\newcommand{\bfY}{{\mathbf{Y}}}
\newcommand{\bfZ}{{\mathbf{Z}}}

\newcommand{\BA}{{\mathbb{A}}}
\newcommand{\BB}{{\mathbb{B}}}
\newcommand{\BC}{{\mathbb{C}}}
\newcommand{\BE}{{\mathbb{E}}}
\newcommand{\BD}{{\mathbb{D}}}
\newcommand{\BF}{{\mathbb{F}}}
\newcommand{\BG}{{\mathbb{G}}}
\newcommand{\BH}{{\mathbb{H}}}
\newcommand{\BI}{{\mathbb{I}}}
\newcommand{\BJ}{{\mathbb{J}}}
\newcommand{\BK}{{\mathbb{K}}}
\newcommand{\BL}{{\mathbb{L}}}
\newcommand{\BP}{{\mathbb{P}}}
\newcommand{\BR}{{\mathbb{R}}}
\newcommand{\BS}{{\mathbb{S}}}
\newcommand{\BT}{{\mathbb{T}}}
\newcommand{\BU}{{\mathbb{U}}}
\newcommand{\BV}{{\mathbb{V}}}
\newcommand{\BW}{{\mathbb{W}}}
\newcommand{\BX}{{\mathbb{X}}}
\newcommand{\BY}{{\mathbb{Y}}}
\newcommand{\BZ}{{\mathbb{Z}}}

\newcommand{\BCOV}{{\mathbb{COV}}}

\newcommand{\colrit}{\color{red} \it}
\newcommand{\colrbf}{\color{red} \bf}
\newcommand{\colbit}{\color{blue} \it}
\newcommand{\colbbf}{\color{blue} \bf}
\newcommand{\colmit}{\colm \it}
\newcommand{\colmbf}{\colm \bf}

\newcommand{\bfalpha}{{\boldsymbol{\alpha}}}
\newcommand{\bfbeta}{{\boldsymbol{\beta}}}
\newcommand{\bfepsilon}{{\boldsymbol{\epsilon}}}
\newcommand{\bftheta}{{\boldsymbol{\theta}}}
\newcommand{\bfgamma}{{\boldsymbol{\gamma}}}
\newcommand{\bfmu}{{\boldsymbol{\mu}}}
\newcommand{\bfpi}{{\boldsymbol{\pi}}}

\newcommand{\bfBeta}{{\boldsymbol{\Beta}}}
\newcommand{\bfGamma}{{\boldsymbol{\Gamma}}}
\newcommand{\bfOmega}{{\boldsymbol{\Omega}}}
\newcommand{\bfSigma}{{\boldsymbol{\Sigma}}}
\newcommand{\bfPhi}{{\boldsymbol{\Phi}}}

\newcommand{\bfZero}{\bf 0}
\newcommand{\bfOne}{\bf 1}
\newcommand{\iid}{\stackrel{i.i.d.}{\sim}}
\newcommand{\raro}{\rightarrow}

\newcommand{\cA}{\mathcal{A}}
\newcommand{\cB}{\mathcal{B}}
\newcommand{\cC}{\mathcal{C}}
\newcommand{\cD}{\mathcal{D}}
\newcommand{\cE}{\mathcal{E}}
\newcommand{\cF}{\mathcal{F}}
\newcommand{\cH}{\mathcal{H}}
\newcommand{\cI}{\mathcal{I}}
\newcommand{\cM}{\mathcal{M}}
\newcommand{\cN}{\mathcal{N}}
\newcommand{\cS}{\mathcal{S}}
\newcommand{\cX}{\mathcal{X}}
\newcommand{\cY}{\mathcal{Y}}

\def\baq#1\eaq{\begin{align}#1\end{align}}
\def\ban#1\ean{\begin{align*}#1\end{align*}}
\newcommand{\draro}{ \stackrel{{\mathcal D}}{\Rightarrow} }

\def\bredbf#1\eredbf{{\color{red}{\bf ???? #1 ????}}}
\def\BeginRedComment#1\EndRedComment{({\color{red}{\bf Comment:} {\it #1}}) }
\def\BeginBlueComment#1\EndBlueComment{({\color{blue}{\bf Comment:} {\it #1}}) }

\DeclareMathOperator*{\ve}{vec}
\DeclareMathOperator*{\diag}{diag }
\DeclareMathOperator*{\supp}{supp }
\DeclareMathOperator*{\Tr}{Tr}
\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\Th}{^{\text{th}}}

\makeatletter
\newcommand{\opnorm}{\@ifstar\@opnorms\@opnorm}
\newcommand{\@opnorms}[1]{%
  \left|\mkern-1.5mu\left|\mkern-1.5mu\left|
   #1
  \right|\mkern-1.5mu\right|\mkern-1.5mu\right|
}
\newcommand{\@opnorm}[2][]{%
  \mathopen{#1|\mkern-1.5mu#1|\mkern-1.5mu#1|}
  #2
  \mathclose{#1|\mkern-1.5mu#1|\mkern-1.5mu#1|}
}
\makeatother

\newtheorem{Theorem}{Theorem}[section]
\newtheorem{Lemma}[Theorem]{Lemma}
\newtheorem{Corollary}[Theorem]{Corollary}
\newtheorem{Proposition}[Theorem]{Proposition}
\newtheorem{Conjecture}[Theorem]{Conjecture}
\theoremstyle{definition} \newtheorem{Definition}[Theorem]{Definition}

%\endlocaldefs

\begin{document}

\title{On Weighted Multivariate Sign Functions}
\date{}
\author{
Subhabrata Majumdar and Snigdhansu Chatterjee
}
\maketitle

\section*{Response to Comments by the Reviewer}

We thank the reviewer for their considered comments, and apologize for the delay in 
preparing the response. We had some personal emergencies, followed by the pandemic, which greatly delayed the revision of our paper. Again, we apologize. The comments by the reviewer led to a substantial revision of the manuscript, primarily in Section~2 of the paper. We address the reviewer's comments in detail below.

\paragraph{Reviewer comment:}
\textit{The paper introduces generalizations to the spatial median that employ data-dependent weights, and applies proposed methods to robust scatter estimation of elliptically symmetric distributions as well as closely related problems. Presented ideas certainly deserve attention, however, I feel that the manuscript requires significant work. In particular, it was not clear to me that proposed estimators can be actually computed without knowledge of parameters of the distribution that are not available. I suggest that authors clarify this point early on.}

\paragraph{Author response:} We thank the reviewer for finding that the ideas 
presented in this paper deserve attention. Based on the comments by the reviewer, we made significant changes in the paper, primarily in Section~2.

The proposed estimators can indeed be estimated without knowing the parameters, otherwise 
this would have been a meaningless exercise. It was our fault in not making the writing of the previous version of the paper clear enough: with the help of the reviewer's comments we hope that the present version is very transparent on this matter. In the previous version of this paper, there were three significant confusing issues, which we have now fixed.

First, as the reviewer commented in her/his detailed comment (a), there was the question of whether the weights depend on $q$, the parameter we wish to estimate 
in Section~2 of the paper. We make a detailed response to this comment below, but in short, we have now restricted the parameter $\BF$ (the distribution parameter in the weight function) to match $\BF_{X}$ (the distribution from where the data is generated), 
and we substantially revised Theorem~2.1, Corollary~2.2, Corollary~2.4, to make sure that our results are valid even if the weights depend on $q$. More details on this are given in response to the reviewer's comment (a) below.

Second, there was the issue of how to compute the weights since $\BF$ is unknown. We have used the reviewer's suggestion in their detailed comment (i), and introduced the computation of weights based on the empirical distribution function $\BF_{n}$ early on, in 
Section~1. We hope this step will greatly alleviate the reviewer's concerns about the usability and computation of the proposed estimators without knowing the underlying distribution (or its parameters).

Third, we have now changed completely the technical conditions and proofs of Corolloary~2.2 and Corollary~2.4, so that these no longer have any part that assumes that the value of $q_{0}$ is known. Our previous manuscript was partially written keeping hypothesis tests in mind (and hence the presence of a known value in the earlier incarnation of the corollaries), but these were both incompletely developed as well as poorly presented. In the revised version of the manuscript, the new corollaries have a different set of technical conditions that broadens their appeal, and completely different proofs.

We trust these changes will address the major concern of the reviewer. We address their specific detailed and minor comments point-by-point below.

\paragraph{Reviewer detailed comment (a):}
\textit{Do I understand correctly that your weights are not allowed to depend on $q$? Then your claim on top of page 3 that this is the same object that has been studied before (e.g., in \cite{ref:AoS97435_Koltchinskii}) is incorrect. If it is allowed to depend on $q$, then please explain how your results are different from the existing literature.}

\paragraph{Author response:}
The framework of our paper is somewhat different that that of \cite{ref:AoS97435_Koltchinskii} (and related papers). 
In principle, the idea of of replacing an observation with a weighted version of its (generalized) sign can be used in numerous ways, only some of which may need the theoretical machinery developed in \cite{ref:AoS97435_Koltchinskii} or related papers. 
For example, in a testing context (not presented in the current manuscript), 
under the null hypothesis, $\BF$ may be entirely known, hence the weights may not 
depend at all on $\BF_{X}$ or its related parameter $q$. 
 However, in many other contexts, there may be implicit dependence between the
weights $W (\cdot, \BF)$ and a multivariate quantile $q$. For example, if 
$\BF = \BF_{X} = N( \mu, \Sigma)$, both the quantile  and the weight depend on the 
parameters $\mu$ and $\Sigma$, so there may be implicit dependence between the two.

We thought deeply about this issue and decided that the best course of action for the present paper is restrict our attention to the case of $\BF = \BF_{X}$, and 
make explicit the fact that the weights $W (\cdot, \BF)$ may implicitly depend on 
$q$. That way, we are not only able to stay within the paradigm developed in the elegant paper by Koltchinskii (\cite{ref:AoS97435_Koltchinskii} and elsewhere) and leverage the 
theoretical understandings developed in these papers and related literature, we are actually able to bring those results into the application domain. 
Also, with the assumption that $\BF = \BF_{X}$, there is no room for ambiguity whether
$W (\cdot, \BF)$ and $q$ may be related: they are indeed related (except for  
perhaps simple instances).

With this assumption, our Theorem~2.1 does indeed strongly relate to existing literature, 
and we present a brief sketch of how that result is established following 
\cite{ref:AoS921514_Niemiro} and \cite{ref:AoS891631_Haberman}. 
\textbf{\textit{However,
all other results in our manuscript are new}}, and relate to issues that have not been discussed in the the literature before, to the best of our knowledge. Following Theorem~2.1, we present two corollaries that show the efficiencies that may be achieved
by careful choice of weights. Section~3 onwards, the discussion is on the robust dispersion measures, eigenvalues and principal components, influence functions in the context of robust estimators of dispersion, and numerical results. To the best our 
knowledge, the theoretical results from these sections are completely new. Also, the methodological parts of these sections typically compare favorably to the \textit{ad hoc}
or otherwise robust dispersion estimators that may be found in statistics literature, as demonstrated by the numerical results in our paper.

As mentioned in the introduction, our focus is primarily on robust dispersion and principal component analysis. We believe we have been able to build a bridge between the 
elegant theoretical development on $M$-quantiles and the methodological aspects of robust dispersion estimation.

%We think this ambiguity was a result of assuming $\BF$ as a general distribution in the beginning, but later having $\BF \equiv \BF_X$ in all our applications. In that case, $W(X,\BF)$ shall depend on $q$ implicitly since $q$ is a parameter of $\BF$. To bypass this confusion, we now assume $X \sim \BF$ from the beginning (highlighted in the introduction, page 2), and then add a remark after theorem 2.1 saying it still goes through if $\BF$ is not $\BF_X$.
%
%While theoretical properties of related quantities have been established in papers like \cite{ref:AoS97435_Koltchinskii}, sometimes under different formulations (e.g. the weight function in \cite{ref:AoS97435_Koltchinskii} is a convex non-decreasing function of $|x - \mu|$), we start off from a broad-based formulation of the weights and then concentrate on the more practical aspects of how weights affect robustness and efficiency. We add a discussion on this in the introduction {\color{red} (have to add that)}.

\paragraph{Reviewer detailed comment (b):}
\textit{Regarding the proof of Theorem 2.1: if you claim that this is a new result, the proof can not be omitted completely: please include it in the supplementary material. If it is not new please give a precise reference.}

\paragraph{Author response:}
We do not claim that this result is substantially new (see detailed comments above). Consequently, in the present manuscript we have included a proof sketch of the theorem, that follows the arguments presented in \cite{ref:AoS921514_Niemiro} and \cite{ref:AoS891631_Haberman}. Please find this sketch of proof right after Theorem~2.1. If needed, we can present a complete proof of this in the supplementary material.

\paragraph{Reviewer detailed comment (c):}
\textit{I could not understand Corollary 2.2: is $q_0$ still a minimizer of $\Psi(q; 0; \BF)$? If so, how can the weight depend on this unknown quantity? Even if $q_0$ is a fixed vector, this still does not make sense to me. Additionally, please show that conditions A1-A3 hold in your examples.
}

\paragraph{Author response:}
We have now completely changed this corollary. Thus, this issue is no longer present in the current manuscript.

\paragraph{Reviewer detailed comment (d):}
\textit{Page 3 states “We report only the case of the weighted spatial median for brevity..” In this case, it could be better to focus on the median everywhere and avoid mentioning general quantiles.
}

\paragraph{Author response:}
We thank the reviewer for this suggestion, and have adopted it, and do not elaborate on weighted spatial quantiles in this paper. Following the referee's suggestion, in the present manuscript we only mention their general definition in Section~2, and then discuss the weighted spatial median in detail.

\paragraph{Reviewer detailed comment (e):}
\textit{Corollary 2.4 states “then $S(X; q_0)$ is uniform on the unit ball in $\BR^p$..” – do you mean $S(Z; q_0)$? If $X$ has arbitrary elliptically symmetric distribution, this is not true. Moreover, why is it interesting in this case to consider the case when $\BF$ is the (unknown) distribution of $X$?
}

\paragraph{Author response:}
The reviewer is absolutely correct, the spatial sign is indeed not independent of the norm for non-spherical but elliptical distributions. We have now completely changed this corollary.

With a few weak conditions on $\Sigma$ from \cite{ref:JASA151658_WangPengLi} 
we are able to prove that the ARE is larger than 1 for general elliptical distributions.

We thank the referee for this comment, which led to a rigorous revision in this part.

\paragraph{Reviewer detailed comment (f):}
\textit{Page 5: “..we propose using $W(x; \BF_n)$: please define what you mean by an empirical distribution function here, as $X$ is a vector.
}

\paragraph{Author response:}
Thank you for pointing this out, we have now put in the proper definition. Please see 
page 7 of the current manuscript.

\paragraph{Reviewer detailed comment (g):}
\textit{The weight functions discussed in section 2.1 can only be computed if the distribution of $X$ is known. Why would such functions be of any use in statistical context? If the unknown distribution is replaced by its empirical version, why would all the useful properties be
preserved? I suggest explaining these points clearly in the beginning.
}

\paragraph{Author response:}
This is an excellent suggestion and we are happy to accept it.
We have now put a brief discussion on this in the Introduction, where we explain that 
in practice $\BF$ is replaced by its empirical version $\BF_{n}$, and mention a set of 
conditions presented later in the paper, that allows such plug-in estimators to be used 
while retaining asymptotic properties. See the top part of page 2.

\paragraph{Reviewer detailed comment (h):}
\textit{
Equation (5): is $\tilde X$ a statistic?
}

\paragraph{Author response:}
No. The quantity $\tilde X$ is a random variable that acts as a robust counterpart of 
$X - \mu$ in the population, and involves the unknown parameters $\mu$ and $\BF$. 
However, with standard plug-in estimators for $\mu$ and $\BF$, we can get a 
sample equivalent of $\tilde{X}$, and the theoretical aspects of using  such plug-in 
estimators in place of the true parameters is considered in the results that follow, see 
for example Lemma~3.2 or Theorem 3.3.

To make the discussion on this transparent, in page 8 of the manuscript, we have now 
rewritten this part to say:
\textit{
As a robust surrogate for $X - \mu$, we consider the  following  random variable 
\ban
\tilde{X} = W (X, \BF) S(X; \mu) \equiv W (Z, \BF_{Z})  
| \Lambda^{1/2} Z|^{-1} \Gamma \Lambda^{1/2}  Z. 
%\label{eq:tildeX}
\ean
In samples, the equivalent for $\tilde{X} $ is 
$\hat{\tilde{X}} = W (X, \BF_{n}) S(X; \hat{\mu})$ for a suitable location estimator 
$\hat{\mu}$, for example, the weighted spatial median. 
}

\paragraph{Reviewer detailed comment (i):}
\textit{
On page 7, it is stated that “We now discuss the properties of the sample version $\tilde \Sigma$ computed from $X$. In practice, we cannot obtain $W(x)?W(x; F)$, and consequently use $W(x; \BF_n)$ instead..” – this is a good point, but I suggest discussing it earlier in the paper, as it affects many assumptions made prior to this statement.}

\paragraph{Author response:}
We thank the reviewer for this excellent suggestion, this greatly helps in bringing clarity to our paper. We have now stated this right upfront in the introduction, see 
page 2.

\paragraph{Reviewer minor comment (a):}
\textit{
Last paragraph of page 3: should $\hat q_n$ be $\hat q_{n W}$?}

\paragraph{Author response:}
Thank you for pointing, we have now corrected this typo.

%\newpage
%\input{misc}

\bibliographystyle{apalike}
\bibliography{WeightedSignBib_09_17_20}

\end{document}

### 2020-09-21 EJSSubmission/RR/WeightedSIgn_EJS_DA_09_21_20_1.tex
ejs resubmitted

--- 2019-08-16 EJSSubmission/WeightedSIgn_EJS_DA_02_24_19_1.tex
@@
 
-\begin{figure}
+\begin{figure}[t!]
 \begin{center}
@@
 \end{tabular}
-\caption{Actual sample curves, their spline approximations and diagnostic plots respectively for El-Ni\~no (a,c,e) and Octane (b,d,f) datasets}
+\caption{Actual sample curves, their spline approximations and diagnostic plots respectively for El-Ni\~no (left side plots) and Octane (right side plots) datasets}
 \label{fig:fPCAfig}
@@
 from June 1970 to May 2004, available 
-from \url{http://www.cpc.ncep.noaa.gov/data}, depicted in  panel (a) 
+from \url{http://www.cpc.ncep.noaa.gov/data}, depicted in  top-left panel
 of Figure~\ref{fig:fPCAfig})).
@@
 nm. There are 6 outliers here: compounds 25, 26 and 36-39, which contain alcohol. This 
-data is presented in  panel (b) of Figure~\ref{fig:fPCAfig})).
+data is presented in  top-right panel  of Figure~\ref{fig:fPCAfig})).
 
 In the sea surface temperature data, using a cubic spline basis with knots at alternate 
-months starting in June, we get a close approximation as depicted in 
-panel (c) of Figure~\ref{fig:fPCAfig}. Using our proposed methodology with $q =1$ 
+months starting in June, we get a close approximation as depicted in middle-left
+panel  of Figure~\ref{fig:fPCAfig}. Using our proposed methodology with $q =1$ 
 results in two points having their SD and OD larger than cutoff, depicted in  
-panel (e) of Figure~\ref{fig:fPCAfig}. These points correspond to the time periods June 
+bottom-left panel  of Figure~\ref{fig:fPCAfig}. These points correspond to the time periods June 
 1982 to May 1983 and June 1997 to May 1998 are marked by black curves in panels a and c, 
@@
  and again the top robust PC turns out to be sufficient in identifying all 6 outliers. 
- Details are available in  panels (b), (d) and (f) of Figure~\ref{fig:fPCAfig}.
+ Details are available in the right side panels  of Figure~\ref{fig:fPCAfig}.

### 2020-09-21 EJSSubmission/RR/WeightedSign_EJS_Dispersion_09_19_20_1.tex
ejs resubmitted

--- 2019-09-13 EJSSubmission/WeightedSign_EJS_Dispersion_02_24_19_1.tex
@@
 
-The rest of this paper is built on the following transformed random variable:
+As a robust surrogate for $X - \mu$, we consider the  following  random variable 
 \baq
@@
 \eaq
+In samples, the equivalent for $\tilde{X} $ is 
+$\hat{\tilde{X}} = W (X, \BF_{n}) S(X; \hat{\mu})$ for a suitable location estimator 
+$\hat{\mu}$, for example, the weighted spatial median. 
 We fix the notation $\BS (X; \mu) =  S (X; \mu) S( X; \mu)^T$, and define the following dispersion  parameter:
@@
 In the above, $\delta_{x}$ denotes point mass at $x$. 
-These properties are easily satisfied under for  weight functions  derived from standard depth functions, for example, $W_{HSD} (\cdot)$, $W_{MhD} (\cdot)$ and $W_{PD} (\cdot)$ discussed earlier.
+These properties are easily satisfied  for  weight functions  derived from standard depth functions, for example, $W_{HSD} (\cdot)$, $W_{MhD} (\cdot)$ and $W_{PD} (\cdot)$ discussed earlier.
 
@@
 \begin{Lemma} \label{Lemma:lemma1}
-Assume that $\BE \| X - \mu \|^{-4} < \infty$. Also assume that 
+Assume that $\BE | X - \mu |^{-4} < \infty$. Also assume that 
 we have a location estimator  $\hat{\mu}_n$ satisfying 
-$\BE \|\hat{\mu}_n  - \mu \|^{4} = O (n^{-2}) $. Then
+$\BE |\hat{\mu}_n  - \mu |^{4} = O (n^{-2}) $. Then
 \ban
@@
 %
-where for any $c \in \BR^{p}$ such that $| c | = $, we have 
+where for any $c \in \BR^{p}$ such that for $| c | = 1$, we have 
 $\BE  c^{T} R_{n} c = o (n^{-1})$.

### 2020-09-21 EJSSubmission/RR/WeightedSign_EJS_WeightedSpatialQuantiles_09_17_20_1.tex
ejs resubmitted

--- 2020-09-20 EJSSubmission/R1/WeightedSign_EJS_WeightedSpatialQuantiles_09_17_20_1.tex
@@
 In fact, Corollary~\ref{Cor:Elliptic_ARE} can be established under just
-location invariance condition on weights, we use the stronger affine invariance condition
+location invariance condition on weights. We use the stronger affine invariance condition
 here only because the subsequent sections use weights based on affine invariant 

### 2020-09-21 EJSSubmission/arxiv/arxiv-sim.tex
ejs resubmitted

--- 2019-08-09 EJSSubmission/WeightedSign_EJS_Simulations_02_24_19_1.tex
@@
 
-The results from this simulation exercise are presented in Table~\ref{table:FSEtable4}.
-It can be seem that  $\tilde{\Sigma}$-based estimators (columns 3-5) 
-outperform SCM and Tyler's $M$-estimator of scatter. Among the 3 depth functions 
-considered, projection depth gives the best results. Its finite sample performances are 
-better than Tyler's and Huber's M-estimators of scatter, as well as their symmetrized 
-counterparts that are much more computationally intensive (see Table 4 in 
-\cite{ref:JMVA071611_Sirkiaetal}). The affine equivariant ${\Sigma}_{*}$-based estimators
- (columns 6-8) are even more efficient.
-
  \begin{table}[t]
+ \centering
 \begin{scriptsize}
@@
 
+The results from this simulation exercise are presented in Table~\ref{table:FSEtable4}.
+It can be seem that  $\tilde{\Sigma}$-based estimators (columns 3-5) 
+outperform SCM and Tyler's $M$-estimator of scatter. Among the 3 depth functions 
+considered, projection depth gives the best results. Its finite sample performances are 
+better than Tyler's and Huber's M-estimators of scatter, as well as their symmetrized 
+counterparts that are much more computationally intensive (see Table 4 in 
+\cite{ref:JMVA071611_Sirkiaetal}). The affine equivariant ${\Sigma}_{*}$-based estimators (columns 6-8) are even more efficient.
+
 \subsection{Influence function comparison}
 
-%\begin{comment}
-
-\begin{figure}[]
+\begin{figure}[t!]
 	\centering
-		\includegraphics[width=0.8\textwidth]{./Plots/IFnorm.png}
+		\includegraphics[width=0.8\textwidth]{IFnorm}
 	\caption{Plot of the norm of influence function for first eigenvector of (a) sample 
@@
 Details are available in \cite{ref:PhilTransRoyalSoc094385_AdragniCook}.
-
-Ina non-linear regression model, we compare the performance of the robust version of 
+%
+\begin{figure}[t!]
+\begin{center}
+\begin{tabular}{ll}
+\includegraphics[width=0.4\textwidth]{SDRcomparison_noout} &
+\includegraphics[width=0.4\textwidth]{SDRcomparison_out}
+\end{tabular}
+\caption{Average prediction errors for two methods of SDR (a) in absence and (b) in presence of outliers}
+\label{fig:SDRfig}
+\end{center}
+\end{figure}
+%
+In a non-linear regression model, we compare the performance of the robust version of 
 SDR with the original method of 

### 2020-09-21 EJSSubmission/arxiv/arxiv-supp.tex
ejs resubmitted

--- 2019-09-13 EJSSubmission/WeightedSign_EJS-supp.tex
@@
-\documentclass[ejs]{imsart}
-
-\RequirePackage[OT1]{fontenc}
-%\RequirePackage{amsthm,amsmath}
-\RequirePackage[numbers]{natbib}
-\RequirePackage[colorlinks,citecolor=blue,urlcolor=blue]{hyperref}
-\usepackage{amssymb,amsmath,amsthm,color,outlines,subfigure,comment}
-\usepackage[small]{caption}
-%\usepackage{hyperref} % for linking references
-%\hypersetup{colorlinks = true, citecolor = blue, urlcolor = blue}
-\usepackage{graphics}
-\usepackage{graphicx}
-\usepackage{stackrel}
-\usepackage{natbib}
-\usepackage{soul}
-%\usepackage[bordercolor=white,backgroundcolor=gray!30,linecolor=black,colorinlistoftodos]{todonotes}
-%\newcommand{\rework}[1]{\todo[color=yellow,inline]{#1}}
-
-% will be filled by editor:
-\doi{10.1214/154957804100000000}
-\pubyear{0000}
-\volume{0}
-\firstpage{0}
-\lastpage{0}
-%\arxiv{}
-
-%%%settings
-%\pubyear{2006}
-%\volume{0}
-%\issue{0}
-%\firstpage{1}
-%\lastpage{8}
-
-%%%%%% put your definitions there:
-\startlocaldefs
-%\numberwithin{equation}{section}
-%\theoremstyle{plain}
-%\newtheorem{thm}{Theorem}[section]
-
-\newcommand{\BA}{{\mathbb{A}}}
-\newcommand{\BB}{{\mathbb{B}}}
-\newcommand{\BC}{{\mathbb{C}}}
-\newcommand{\BE}{{\mathbb{E}}}
-\newcommand{\BD}{{\mathbb{D}}}
-\newcommand{\BF}{{\mathbb{F}}}
-\newcommand{\BG}{{\mathbb{G}}}
-\newcommand{\BH}{{\mathbb{H}}}
-\newcommand{\BI}{{\mathbb{I}}}
-\newcommand{\BJ}{{\mathbb{J}}}
-\newcommand{\BK}{{\mathbb{K}}}
-\newcommand{\BL}{{\mathbb{L}}}
-\newcommand{\BP}{{\mathbb{P}}}
-\newcommand{\BR}{{\mathbb{R}}}
-\newcommand{\BS}{{\mathbb{S}}}
-\newcommand{\BT}{{\mathbb{T}}}
-\newcommand{\BU}{{\mathbb{U}}}
-\newcommand{\BV}{{\mathbb{V}}}
-\newcommand{\BW}{{\mathbb{W}}}
-\newcommand{\BX}{{\mathbb{X}}}
-\newcommand{\BY}{{\mathbb{Y}}}
-\newcommand{\BZ}{{\mathbb{Z}}}
-
-\newcommand{\BCOV}{{\mathbb{COV}}}
-
-\newcommand{\colrit}{\color{red} \it}
-\newcommand{\colrbf}{\color{red} \bf}
-\newcommand{\colbit}{\color{blue} \it}
-\newcommand{\colbbf}{\color{blue} \bf}
-\newcommand{\colmit}{\colm \it}
-\newcommand{\colmbf}{\colm \bf}
-
-\newcommand{\bfOne}{\bf 1}
-\newcommand{\iid}{\stackrel{i.i.d.}{\sim}}
-\newcommand{\raro}{\rightarrow}
-
-\newcommand{\cA}{\mathcal{A}}
-\newcommand{\cB}{\mathcal{B}}
-\newcommand{\cC}{\mathcal{C}}
-\newcommand{\cD}{\mathcal{D}}
-\newcommand{\cE}{\mathcal{E}}
-\newcommand{\cF}{\mathcal{F}}
-\newcommand{\cH}{\mathcal{H}}
-\newcommand{\cI}{\mathcal{I}}
-\newcommand{\cM}{\mathcal{M}}
-\newcommand{\cN}{\mathcal{N}}
-\newcommand{\cS}{\mathcal{S}}
-\newcommand{\cX}{\mathcal{X}}
-\newcommand{\cY}{\mathcal{Y}}
-
-\def\baq#1\eaq{\begin{align}#1\end{align}}
-\def\ban#1\ean{\begin{align*}#1\end{align*}}
-\newcommand{\draro}{ \stackrel{{\mathcal D}}{\Rightarrow} }
-
-\def\bredbf#1\eredbf{{\color{red}{\bf ???? #1 ????}}}
-\def\BeginRedComment#1\EndRedComment{({\color{red}{\bf Comment:} {\it #1}}) }
-\def\BeginBlueComment#1\EndBlueComment{({\color{blue}{\bf Comment:} {\it #1}}) }
-
-\DeclareMathOperator*{\ve}{vec}
-\DeclareMathOperator*{\diag}{diag }
-\DeclareMathOperator*{\supp}{supp }
-\DeclareMathOperator*{\Tr}{Tr}
-\DeclareMathOperator*{\argmin}{arg\,min}
-\DeclareMathOperator*{\argmax}{arg\,max}
-\DeclareMathOperator*{\Th}{^{\text{th}}}
-
-\makeatletter
-\newcommand{\opnorm}{\@ifstar\@opnorms\@opnorm}
-\newcommand{\@opnorms}[1]{%
-  \left|\mkern-1.5mu\left|\mkern-1.5mu\left|
-   #1
-  \right|\mkern-1.5mu\right|\mkern-1.5mu\right|
-}
-\newcommand{\@opnorm}[2][]{%
-  \mathopen{#1|\mkern-1.5mu#1|\mkern-1.5mu#1|}
-  #2
-  \mathclose{#1|\mkern-1.5mu#1|\mkern-1.5mu#1|}
-}
-\makeatother
-
-\newtheorem{Theorem}{Theorem}[section]
-\newtheorem{Lemma}[Theorem]{Lemma}
-\newtheorem{Corollary}[Theorem]{Corollary}
-\newtheorem{Proposition}[Theorem]{Proposition}
-\newtheorem{Conjecture}[Theorem]{Conjecture}
-\theoremstyle{definition} \newtheorem{Definition}[Theorem]{Definition}
-
-\endlocaldefs
-
-\begin{document}
-
-\begin{frontmatter}
-\title{On Weighted Multivariate Sign Functions: Supplementary Material}
-\runtitle{Weighted Sign Functions}
-%\thankstext{T1}{Footnote to the title with the `thankstext' command.}
-
-\begin{aug}
-\author{\fnms{Subhabrata} \snm{Majumdar}\thanksref{t1}\ead[label=e1]{subho@research.att.com}}
-\and
-\author{\fnms{Snigdhansu} \snm{Chatterjee}\thanksref{t3}\ead[label=e2]{chatt019@umn.edu}}
-
-\address{School of Statistics,\\
-University of Minnesota,\\
-313 Ford Hall,\\
-224 Church Street S.E., \\
-Minneapolis 55455, USA\\
-%usually few lines long\\
-\printead{e1,e2}}
-
-%\author{\fnms{Third} \snm{Author}
-%\ead[label=e3]{third@somewhere.com}
-%\ead[label=u1,url]{www.foo.com}}
-%
-%\address{Address of the Third author\\
-%usually few lines long\\
-%usually few lines long\\
-%\printead{e3}\\
-%\printead{u1}}
-
-\thankstext{t1}{Currently at AT\&T Labs Research}
-%\thankstext{t2}{First supporter of the project}
-\thankstext{t3}{Corresponding author}
-\runauthor{Majumdar and Chatterjee}
-
-\affiliation{University of Minnesota and University of Minnesota}
-
-\end{aug}
-
-\end{frontmatter}
-
 \appendix
+\section*{Supplementary material}
 \renewcommand{\thesection}{\Alph{section}}
@@
 \end{proof}
-
-\bibliographystyle{apalike}
-\bibliography{WeightedSignBib_01_29_19}
-
-\end{document}

### 2020-12-24 EJSSubmission/arxiv/arxiv-disp.tex
IEEE TIT sobmitted

--- 2019-08-09 EJSSubmission/WeightedSign_EJS_Dispersion_02_24_19_1.tex
@@
 assume that $X_{1}$ is absolutely continuous, with $\BP [ | X_{1}| = 0] = 0$, 
-and that $\Sigma$ is positive definite. This  eliminates technicalities arising from
- rank deficient cases, and makes the weight functions  affine invariant.
-Thus, we essentially restrict the rest of this paper to the same  framework as in 
-Corollary~\ref{Cor:Elliptic_ARE}. Most of the results below generalize to the case where 
+and that $\Sigma$ is positive definite. This eliminates technicalities arising from rank deficient cases, and makes the weight functions affine invariant.
+Thus, we essentially restrict the rest of this paper to the same  framework as in Corollary~\ref{Cor:Elliptic_ARE}. 
+Most of the results below generalize to the case where 
 $\cX$ is a separable Hilbert space, however additional technicalities are involved, as in 
@@
 \ban
-X = \mu + R \Gamma \Lambda^{1/2}  U
+X = \mu + R \Gamma \Lambda^{1/2}  U,
 \ean
@@
 %& 
-=  | \Lambda^{1/2} Z|^{-1} \Gamma \Lambda^{1/2}  Z
+=  | \Lambda^{1/2} Z|^{-1} \Gamma \Lambda^{1/2}  Z.
 \ean
+%
 
-The rest of this paper is built on the following transformed random variable:
+As a robust surrogate for $X - \mu$, we consider the  following  random variable 
 \baq
@@
 \eaq
-We define the notation $\BS (X; \mu) =  S (X; \mu) S( X; \mu)^T$.
-Then, we define the following dispersion  parameter:
+In samples, the equivalent for $\tilde{X} $ is 
+$\hat{\tilde{X}} = W (X, \BF_{n}) S(X; \hat{\mu})$ for a suitable location estimator 
+$\hat{\mu}$, for example, the weighted spatial median. 
+We fix the notation $\BS (X; \mu) =  S (X; \mu) S( X; \mu)^T$, and define the following dispersion  parameter:
 \baq
@@
 $\tilde{\Lambda} = \Lambda^{1/2} \BE W^{2} (X) 
-	\BE UU^{T}/(U^{T}\Lambda U) \Lambda^{1/2}$
+	\BE [UU^{T}/(U^{T}\Lambda U)] \Lambda^{1/2}$
 is a diagonal matrix.  Thus, the eigenvectors of ${\Sigma}$ and 
@@
 \ean 
- \end{enumerate}
+\end{description}
+%
 In the above, $\delta_{x}$ denotes point mass at $x$. 
-These property are easily satisfied under for  weight functions  derived 
-from standard depth functions, for example, $W_{HSD} (\cdot)$, 
-$W_{MhD} (\cdot)$ and $W_{PD} (\cdot)$ discussed earlier.
+These properties are easily satisfied  for  weight functions  derived from standard depth functions, for example, $W_{HSD} (\cdot)$, $W_{MhD} (\cdot)$ and $W_{PD} (\cdot)$ discussed earlier.
 
-The following result allows us to use the empirical, plug-in weights and an 
-estimated location parameter in the 
-weighted dispersion estimator. A natural choice for the location parameter estimator 
-is the solution to $\sum_{i = 1}^{n} \tilde{X}_{i} = 0$.
+The following result allows us to use the empirical, plug-in weights and an estimated location parameter in the weighted dispersion estimator.
+A natural choice for the location parameter estimator is the solution to $\sum_{i = 1}^{n} \tilde{X}_{i} = 0$, which is the same as the sample version of the weighted spatial median discussed in Section~\ref{Sec:WSQuantiles}.
 
 \begin{Lemma} \label{Lemma:lemma1}
-Assume that $\BE \| X - \mu \|^{-4} < \infty$. Also assume that 
+Assume that $\BE | X - \mu |^{-4} < \infty$. Also assume that 
 we have a location estimator  $\hat{\mu}_n$ satisfying 
-$\BE \|\hat{\mu}_n  - \mu \|^{4} = O (n^{-2}) $. Then
+$\BE |\hat{\mu}_n  - \mu |^{4} = O (n^{-2}) $. Then
 \ban
@@
 \begin{proof}[Proof of Lemma~\ref{Lemma:lemma1}]
-This proof is mostly algebra, and we provide a sketch of the main arguments.
+Note that the moment condition above is satisfied by default since $X$ has an elliptical distribution \citep{durre14}. The proof is mostly algebra, and we provide a sketch of the main arguments.
 We have
@@
 \baq
-& \sum_{k=1, {}_{k \neq i}}^{p} 
+& \sum_{k=1, {k \neq i}}^{p} 
 \Bigl[ \tilde{\Lambda}_{i} -  \tilde{\Lambda}_{k} \Bigr]^{-2}
@@
  \Bigl[
-\sum_{k=1, {}_{k \neq i}}^{p} 
+\sum_{k=1, {k \neq i}}^{p} 
 \biggl[ \tilde{\Lambda}_{i} -  \tilde{\Lambda}_{k} \biggr]^{-2}
@@
 \begin{equation}
-\BE \left[ u( | Z_{M} | )  \frac{Z_{M} Z_{M}^T}{| Z_{M} |^2}  - v( | Z_{M} | ) \BI_p \right] = 0
+\BE \left[ u( | Z_{M} | )  \frac{Z_{M} Z_{M}^T}{| Z_{M} |^2}  - v( | Z_{M} | ) \BI_p \right] = 0,
 \end{equation}
@@
 \widehat{\tilde{\Sigma}} = \widehat{{\Gamma}} \widehat{\tilde{\Lambda}}
-\widehat{{\Gamma}}^{T}
+\widehat{{\Gamma}}^{T}.
 \ean 

### 2020-12-24 EJSSubmission/arxiv/arxiv-intro.tex
IEEE TIT sobmitted

--- 2019-08-09 EJSSubmission/WeightedSign_EJS_Introduction_02_24_19_1.tex
@@
 \eqref{eq:GSign} on each observation, thus defining 
-$S_{i} = S ( X_{i}; \mu_x)$ with respect to some suitable center 
-$ \mu_x \in \BR^{p}$, and then using these for robust location and scale estimation and 
-inference, including inference for $ \mu_x$ 
-\citep{ref:Test991_Locantoreetal, ref:OjaBook10, ref:JASA151658_WangPengLi}.
+$S_{i} = S ( X_{i}; \mu_i)$ with respect to some suitable center 
+$ \mu_i \in \BR^{p}$, and then using these for robust location and scale estimation and 
+inference, including inference for $ \mu_i$ \citep{ref:Test991_Locantoreetal, ref:OjaBook10, ref:JASA151658_WangPengLi}.
 Suppose $\bfS = ( S_{1}: \ldots : S_{n} )^{T} \in \BR^{n \times p}$. 
@@
 and of $\BE S_{1} S_{1}^{T}$ are the same for suitable centering 
-parameters $\tilde{\mu}$ and $ \mu_x$, that is, the population principal components 
+parameter $\tilde{\mu} \equiv \mu_i$, that is, the population principal components 
 from the original data and from its sign transformations are the same 
 \citep{ref:SPL12765_Taskinenetal}.
-However, valuable information is lost in the form of magnitudes of sample points. As a 
-result, spatial sign-based procedures suffer from low efficiency. For example, eigenvector 
-estimates obtained from the covariance matrix of $\bfS$ are asymptotically inadmissible 
-\citep{ref:Biometrika14673_MagyarTyler} and  Tyler's M-estimate of scatter \citep{ref:AoS87234_Tyler} has uniformly 
-lower asymptotic risk.
+However, valuable information is lost in the form of magnitudes of sample points.
+As a result, spatial sign-based procedures suffer from low efficiency.
+For example, eigenvector estimates obtained from the covariance matrix of $S$ are asymptotically inadmissible \citep{ref:Biometrika14673_MagyarTyler} and  Tyler's M-estimate of scatter \citep{ref:AoS87234_Tyler} has uniformly lower asymptotic risk.
 
@@
 to adaptively trade-off between efficiency and robustness considerations in any given 
-application. We demonstrate the utility of using 
-the proposed \textit{weighted generalized sign} functions in a number of problems 
-of current interest, including robust estimation of location and scatter.
+application.
+We demonstrate the utility of using the proposed \textit{weighted generalized sign} functions in a number of problems of current interest, including robust estimation of location and scatter.
 
-Specifically, we propose using product of the generalized sign function and a 
-weight function derived as a transformation of a data-depth function 
-\citep{ref:AoS00461_ZuoSerfling, ref:DIMACS061_Serfling}.
- Like data-depth functions, the weight functions 
-used in this paper are non-negative reals defined over $\cX \times \cF$, where 
-$\cF$ is a fixed family of probability measures.
+Specifically, we propose using product of the generalized sign function and a weight function derived as a transformation of a data-depth function \citep{ref:DIMACS061_Serfling, ref:AoS00461_ZuoSerfling}.
+Like data-depth functions, the weight functions used in this paper are non-negative reals defined over $\cX \times \cF$, where $\cF$ is a fixed family of probability measures.
 For every choice of parameters $\mu \in \cX$ and $\BF \in \cF$, in this paper
+%
 \begin{align}
-R (X_{i}; \mu, \BF) = \mu +  S( X_{i}, \mu) W( X_{i}, \BF).
+%R (X_{i}; \mu, \BF) = \mu + S( X_{i}, \mu) W( X_{i}, \BF).
+R (X_{i}; \mu, \BF) = S( X_{i}, \mu) W( X_{i}, \BF).
 \label{eqn:rank}
 \end{align}
+%
 is used as a robust surrogate for observation $X_{i}$.
 Notice that for the trivial choice $W( x, \BF) = | x - \mu_{\BF} |$, 
- $\mu = \mu_{\BF}$,  we get $R (X_{i}; \mu, \BF) = X_{i}$, the original observations. 
+ $\mu = \mu_{\BF}$,  we get $R (X_{i}; \mu, \BF) = X_{i}-\mu_{\BF}$, the original centered observations. 
  With the other trivial choice of  $W( x, \BF) \equiv 1$, we get the 
@@
  from three well-known data depth functions: the \textit{half-space depth}, 
- the \textit{Mahalanobis depth}, and the \textit{projection depth}.
+ the \textit{Mahalanobis depth}, and the \textit{projection depth}. Note that for i.i.d. data, there are three parameters involved here: the location parameter $\mu$ in 
+ \eqref{eq:GSign}, the distribution $\BF$ used for the weight function, and the distribution $\BF_{X}$ of $X_{1}$.
+For clarity and to mirror the contexts of how data depth has been used in the literature \citep{LiuPareliusSingh99, ref:DIMACS061_Serfling}, we fix $\BF = \BF_{X}$ for this paper, although in Section~\ref{Sec:WSQuantiles} we briefly remark on the case when these  distributions are different.
+Also note that
+ in many problems of interest, $\BF$ is 
+unknown and  data-depths are computed using $\BF_{n}$, however, under very standard regularity conditions (for example, see assumptions \textbf{B1-B3} below), the 
+properties of $W (x, \BF)$ and $W (x, \BF_{n})$ are close enough for both asymptotic theory and practical applicability.
 
  %\begin{comment}
-\begin{figure}[t]
+\begin{figure}[t!]
 %\captionsetup{justification=centering, font=footnotesize}
 \begin{center}
-\begin{tabular}{ll}
+%\begin{tabular}{ll}
 %%% These ones have sample size = 700, just right  for EJS
-\includegraphics[width=0.45\textwidth]{./Plots_SC/WeightedSign_Scatter_700_02_27_19} &
-\includegraphics[width=0.45\textwidth]{./Plots_SC/WeightedSign_MD_700_02_27_19} \\
-\includegraphics[width=0.45\textwidth]{./Plots_SC/WeightedSign_TD_700_02_27_19} &
-\includegraphics[width=0.45\textwidth]{./Plots_SC/WeightedSign_PD_700_02_27_19} \\
+\includegraphics[width=\textwidth]{WeightedSignAll}
+%\includegraphics[width=0.45\textwidth]{./Plots_SC/WeightedSign_Scatter_700_02_27_19} &
+%\includegraphics[width=0.45\textwidth]{./Plots_SC/WeightedSign_MD_700_02_27_19} \\
+%\includegraphics[width=0.45\textwidth]{./Plots_SC/WeightedSign_TD_700_02_27_19} &
+%\includegraphics[width=0.45\textwidth]{./Plots_SC/WeightedSign_PD_700_02_27_19} \\
 
@@
 As a location estimator, it has several interesting robustness properties and can be shown to be more efficient that some existing robust location estimators, thus making it a perfect candidate to estimate $\mu$.
-On the other hand, setting $\BF$ as $\BF_X$, i.e.
+%On the other hand, setting $\BF$ as $\BF_X$, i.e.
 the distribution of $X$ has the clear interpretation of differentially weighting observations based on their inlyingness to the overall data distribution.
-This mirrors the context of how data depth has been used in the literature (refs).
-Due to this reason, except for two results in Section~\ref{Sec:WSQuantiles} (Theorem~\ref{Thm:WSMedian} and Corollary~\ref{Cor:ARE}) we assume $\BF \equiv \BF_X$ for the rest of the paper.
-However, other choices of $\BF$ may lead to interesting interpretations of $W(.
-,\BF)$ and the resulting quantities, e.g.
-(ref), and can potentially be explored further.
-}
+This mirrors the context of how data depth has been used in the literature \cite{LiuPareliusSingh99, ref:DIMACS061_Serfling}.
+Due to this reason, we assume $\BF \equiv \BF_X$ for the rest of the paper.
+As and when required, we shall use sample versions of these quantities, stating the theoretical conditions for the corresponding approximation results to hold.
 
-Following that, we restrict to the $\BR^{p}$ for fixed $p$, and present detailed 
-discussions on our primary proposal for a  robust measure of dispersion in 
-Section~\ref{Sec:WSDispersion1}, followed by a proposed 
-\textit{ affine equivariant version} of 
-it in Section~\ref{Sec:WSDispersion2}, robust estimation of eigenvalues and a third 
-robust estimator for dispersion in Section~\ref{Sec:Eigen}, and a thorough study of 
-robustness and efficiency using influence functions in Section~\ref{Sec:RE_Dispersion}.
-We then report multiple simulation-based numeric studies in Section~\ref{Sec:Simulation}, 
-present several real data examples in Section~\ref{Sec:DA}, and concluding remarks in 
-Section~\ref{Sec:Conclusion}.
+Following that, we restrict to the $\BR^{p}$ for fixed $p$, and present detailed discussions on our primary proposal for a  robust measure of dispersion in Section~\ref{Sec:WSDispersion1}, followed by a proposed \textit{ affine equivariant version} of it in Section~\ref{Sec:WSDispersion2}, robust estimation of eigenvalues and a third robust estimator for dispersion in Section~\ref{Sec:Eigen}, and a thorough study of robustness and efficiency using influence functions in Section~\ref{Sec:RE_Dispersion}.
+We then report multiple simulation-based numeric studies in Section~\ref{Sec:Simulation}, present several real data examples in Section~\ref{Sec:DA}, and concluding remarks in Section~\ref{Sec:Conclusion}.
 
-In the rest of this paper, all finite-dimensional vectors are 
-column vectors, and for a vector or matrix $a$, the notation $a^{T}$ stands for 
-its transpose. The Gaussian distribution with mean $\mu$ and variance $\Sigma$ is denoted
-by $N (\mu, \Sigma)$. The identity matrix  is denoted by $\BI$, with or without a 
-subscript to denote its dimension. The notations $A^{-1}$ and $det (A)$ respectively 
-stand for the inverse and determinant of matrix $A$, whenever these are well-defined.
+In the rest of this paper, all finite-dimensional vectors are column vectors, and for a vector or matrix $a$, the notation $a^{T}$ stands for its transpose.
+The Gaussian distribution with mean $\mu$ and variance $\Sigma$ is denoted by $N (\mu, \Sigma)$.
+The identity matrix  is denoted by $\BI$, with or without a subscript to denote its dimension.
+The notations $A^{-1}, det (A), \lambda_{\min} (A), \lambda_{\max} (A)$ respectively stand for the inverse, determinant, minimum and maximum eigenvalues of a matrix $A$, whenever these are well-defined.
+For a scalar or vector valued random variable $Y$, $\BE Y$ denotes its expected value, while $\BV Y$ denotes its variance or covariance matrix.

### 2020-12-24 EJSSubmission/arxiv/arxiv-spq.tex
IEEE TIT sobmitted

--- 2019-08-09 EJSSubmission/WeightedSign_EJS_WeightedSpatialQuantiles_02_24_19_1.tex
@@
 %
-\rework{
-This is a natural generalization of the spatial median \cite{ref:JASA96862_Chaudhuri, ref:Biometrika48414_Haldane,ref:AoS97435_Koltchinskii}, or more general spatial quantiles \cite{ref:AoS17591_Cardotetal_Median_HilbertSpace, ref:AoS141203_ChakrabortyChaudhuri_Banach_Quantile, ref:Bernoulli152308_Minsker_Median_Banach}.
-In what follows, for brevity we elaborate only the case of the \textit{weighted spatial median} (thus
-$\Psi (q; 0, \BF) = \BE \bigl[ W (X, \BF) | X - q | \bigr] $) for the case of finite dimensional $\cX$.
+%\rework{
+\noindent
+This is a natural generalization of the spatial median \citep{ref:JASA96862_Chaudhuri, ref:Biometrika48414_Haldane,ref:AoS97435_Koltchinskii} ($W(X, \BF) \equiv 1$ and $u = {\bf 0}_p$), or more general spatial quantiles \citep{ref:AoS17591_Cardotetal_Median_HilbertSpace, ref:AoS141203_ChakrabortyChaudhuri_Banach_Quantile, ref:Bernoulli152308_Minsker_Median_Banach} ($W(X, \BF) \equiv 1$).
+We assume that
+$\Phi (q; X, u, \BF)$ is convex in $q$ for $\BF$-almost all values of $x \in \cX$.
+
+In what follows, for brevity we elaborate only the case of the \textit{weighted spatial median} (thus $\Psi (q; 0, \BF) = \BE \bigl[ W (X, \BF) | X - q | \bigr] $) for the case of finite dimensional $\cX$.
 Specifically, we demonstrate the utility of using the {\it weighted} spatial median as opposed to using the traditional, unweighted versions found in literature.
 The analysis and computation of the general weighted spatial quantiles will largely follow by extending the results of the above cited references, and we postpone details to a future study.
-}
+%}
 
-Assume that we have independent and identically distributed observations $X_{1}, \ldots, X_{n} \in \cX$, and the sample weighted spatial median is computed by minimizing $\Psi_{n} (q; 0, \BF) = \sum_{i = 1}^{n} \bigl[ W (X_{i}, \BF) | X_{i} - q | \bigr] $, and is denoted by $\hat{q}_{nW}$, the second subscript is in acknowledgement that the weight function is used.
+Assume that we have independent and identically distributed observations $X_{1}, \ldots, X_{n} \in \cX$, and the sample weighted spatial median is computed by minimizing $\Psi_{n} (q; 0, \BF) = \sum_{i = 1}^{n} W (X_{i}, \BF) | X_{i} - q | $, and is denoted by $\hat{q}_{nW}$, the second subscript is in acknowledgement that the weight function is used.
 We denote the unweighted version of this estimator, ie, the case where $W (X, \BF) \equiv 1$ as $\hat{q}_{n}$.
@@
 \begin{description}
-\item[A1:] $\Psi (q; 0, \BF)$ is finite for all $q \in \cX \subseteq \BR^{p}$ 
+\item[(A1)] $\Psi (q; 0, \BF)$ is finite for all $q \in \cX \subseteq \BR^{p}$ 
 and has a unique minimizer $q_{0}$.
 
- \item[A2:] $\Psi (q; 0, \BF)$ is twice differentiable at $q_{0}$ and the second 
- derivative is positive definite.
+\item[(A2)] $\Psi (q; 0, \BF)$ is twice differentiable at $q_{0}$ and the second derivative is positive definite.
 
- \item[A3:] $\BE W^{2} (X, \BF)  S (X; q) S^{T} (X; q)$ exists for all 
- $q$ in a neighborhood of $q_{0}$. 
+\item[(A3)] $ {\frac{\partial^{2}} {\partial q^{2}}} \Psi (q; 0, \BF)$
+exists for all $q$ in a neighborhood of $q_{0}$, and we use the notations
+\ban
+\Psi_{1W}   & = 
+\Bigl( {\frac{\partial} {\partial q}} \Psi (q_{0}; 0, \BF) \Bigr)
+ \Bigl( {\frac{\partial} {\partial q}} \Psi (q_{0}; 0, \BF) \Bigr)^{T}, \\
+\Psi_{2W}   & = {\frac{\partial^{2}} {\partial q^{2}}} \Psi (q_{0}; 0, \BF). 
+\ean
  \end{description}
@@
 
- \begin{Theorem}
- \label{Thm:WSMedian}
- Under assumptions \textbf{[A1] - [A3]}, we have 
+ \begin{Theorem}\label{Thm:WSMedian}
+ Under assumptions [A1]-[A3], we have 
  \ban 
- n^{1/2} (\hat{q}_{nW} - q_{0}) & \draro N(0, \Psi_{2}^{-1} \Psi_{1}^{2} \Psi_{2}^{-1}), 
- \text{ where } \\
- \Psi_{2} & = 
- \BE W (X, \BF) \Bigl[  |X - q|^{-1} \BI_{p} - |X - q|^{-3/2} (X - q) (X - q)^{T}  \Bigr] 
- \\
- \Psi_{1}  & = n \BE   W^{2} (X, \BF)  \bfS (X; q_{0}) \bfS^{T} (X; q_{0}).
+ n^{1/2} (\hat{q}_{nW} - q_{0}) & \draro N(0, \Psi_{2W}^{-1} \Psi_{1W} \Psi_{2W}^{-1}).
  \ean
  \end{Theorem}
+
+%\rework{
 Thus, under very standard regularity conditions, the sample weighted spatial median 
 is consistent and is asymptotically normal.
-Theorem~\ref{Thm:WSMedian}  can be proved in several different ways. We have used 
-techniques following \cite{ref:AoS891631_Haberman, ref:AoS921514_Niemiro}, 
-we omit the details.
+Theorem~\ref{Thm:WSMedian}  can be proved in several different ways.
+Here we use techniques following \cite{ref:AoS891631_Haberman, ref:AoS921514_Niemiro}.
+Specifically, following Theorem 4 in \cite{ref:AoS921514_Niemiro}, which traces back to \cite{ref:AoS891631_Haberman} with slightly relaxed conditions, we get
+%
+\begin{align*}
+n^{1/2} (\hat{q}_{nW} - q_{0}) =
+- \frac{\Psi_{2W}}{\sqrt n} 
+\sum_{i=1}^n \nabla \Phi (q; X_{i}, u, \BF)
++ o_P(1),
+\end{align*}
+%
+where $\nabla \Phi (q; X_{i}, u, \BF)$ is any measurable subgradient of 
+$\Phi (q; X_{i}, u, \BF)$. 
+Theorem~\ref{Thm:WSMedian} follows by applying the central limit theorem.
+
+\paragraph{Remark.} Note that the technical conditions for the result presented in Theorem~\ref{Thm:WSMedian} is one of several alternatives that can conceived, and the scope of this result is broader than what is presented above.
+First, note that if $\BF$
+and $\BF_{X}$ are different and the weights are not a function of $q$, 
+a situation that may arise in hypothesis testing problems where the weights are based 
+on the null distribution, the convexity of $\Phi (q; X_{i}, u, \BF)$ follows automatically 
+and is not an assumption.
+Second, even if $\Phi (q; X_{i}, u, \BF)$ is not convex but sufficiently smooth, we can have a central limit theorem, for example, by using techniques similar to \cite{ref:CBose_AoS05414}.
+Choices of $\BF$ other than $\BF_{X}$, e.g. \cite{StatPaper18},  may lead to interesting interpretations of $W(. ,\BF)$ and the resulting location estimator and will be explored further in future.
 
 \subsection{Asymptotic efficiency of weighted spatial median}
-Let $V_{W} = \Psi_{2}^{-1} \Psi_{1}^{2} \Psi_{2}^{-1}$ be the asymptotic 
-variance of \hl{$\hat{q}_{n,W}$} from Theorem~\ref{Thm:WSMedian}, where we use the 
+Let $V_{W} = \Psi_{2W}^{-1} \Psi_{1W} \Psi_{2W}^{-1}$ be the asymptotic 
+variance of $\hat{q}_{n,W}$ from Theorem~\ref{Thm:WSMedian}, where we use the 
 subscript ``${}_{W}$'' to denote that this depends on the weight function. 
@@
 \label{Cor:ARE}
-Assume that $|X - q_{0}|$ and $S (X; q_{0})$ are independent, and the weight function 
-$W (X, \BF)$ is a function of  $|X - q_{0}|$. Then
+Assume that the weight function $W (X, \BF)$ is bounded above by some $W_{\max} > 0$, and the matrices $\Psi_1 = \BE S(X; q_0) S^T(X; q_0)$ and $\Psi_{1W}$ are positive definite. Then
+%
 \ban
-& ARE (\hat{q}_{nW}, \hat{q}_{n}) \\
-& = 
-\Bigl[ \BE \bigg(  |X - q_{0}|^{-1} \bigg) \Bigr]^{-2}
-\Bigl[ \BE W^{2} (X, \BF) \Bigr]^{-1}
-\Bigl[ \BE \bigg(  |X - q_{0}|^{-1} W (X, \BF) \bigg) \Bigr]^{2}.
+ARE (\hat{q}_{nW}, \hat{q}_{n}) \geq
+\frac{ \lambda_{\min} (\Psi_1) \lambda_{\min}^2 (\Psi_{2W})}
+{W_{\max} \lambda_{\max} (\Psi_{1W}) \lambda_{\max}^2 (\Psi_2)}.
 \ean
-Consequently, if $W (X, \BF) = k   |X - q_{0}|^{-1}$ for some $k \in (0, 1]$, 
-then this asymptotic relative efficiency is 
-$ \{k^{-1} (\BE ||X - q_{0}|^{-1} )^{2} \BE |X - q_{0}|^{-2} \}^{1/p}> 1$. 
+%
+Consequently, if $W_{\max} / \lambda_{\min}^2 (\Psi_{2W}) < \lambda_{\min} (\Psi_1) /(\lambda_{\max} (\Psi_{1W}) \lambda_{\max}^2 (\Psi_2))$ then this asymptotic relative efficiency is larger than 1. 
 \end{Corollary}
 
-It is possible to make the above asymptotic relative efficiency to tend to infinity with 
-$p$, for example by choosing $k = \exp\{- p^{2} \}$. Such tending to infinity efficiencies 
-are also achievable for fixed $k$,  for example, if $|X - q_{0}|^{2}$ is a Gamma random 
-variable with shape parameter $ = 2 + \exp\{- p^{2} \}$. We leave it to future work to 
-study such efficiencies more generally.
+\begin{proof}[Proof of Corollary~\ref{Cor:ARE}]
+Using the facts that $det (AB) = det(A) det(B)$ for square matrices $A,B$ and $det (A^{-1}) = 1/det(A)$ for non-singular $A$, we write
+%
+\ban
+\frac{det (V_1)}{det (V_W)} &= det( \Psi_2^{-1} \Psi_1 \Psi_2^{-1} )
+det( \Psi_{2 W} \Psi_{1 W}^{-1} \Psi_{2 W} )\\
+&= det (\Psi_1) det (\Psi_{1 W}^{-1}) [ det(\Psi_2^{-1}) det(\Psi_{2 W}) ]^2.
+\ean
+%
+The result follows, using the facts that $\det(A) \geq \lambda_{\min} (A)$ and $\det(A^{-1}) \geq 1/\lambda_{\max} (A)$, and the upper bound on $W$.
+\end{proof}
+
+%A context where 
+%It is possible to make the above asymptotic relative efficiency to tend to infinity with 
+%$p$, for example by choosing $W_{\max} = \exp\{- p^{2} \}$. Such tending to infinity efficiencies 
+%are also achievable for fixed $W_{\max}$,  for example, in the context of some hypothesis tests.
+%ing problems.
+%f $|X - q_{0}|^{2}$ is a Gamma random 
+%variable with shape parameter $ = 2 + \exp\{- p^{2} \}$. 
+%We leave it to future work to study such efficiencies more generally.
 
 We may wish to further explore the conditions of Corollary~\ref{Cor:ARE}. 
-Let us concentrate on the case of where the distribution of $X$ is 
-elliptically symmetric. Following \cite{ref:Fangetal90_Book}:
+Let us concentrate on the case of where the distribution of $X$ is spherically symmetric. Following \cite{ref:Fangetal90_Book}:
 
 \begin{Definition}
-A $p$-dimensional random vector $X$ is said to elliptically distributed if 
-there exist a vector $\mu \in \BR^p$, a positive semi-definite matrix 
-$\Sigma \in \BR^{p \times p}$ and a function 
-$\phi: (0, \infty) \rightarrow \BR$ such that the characteristic function 
-of $X$ is $\exp \{ i t^{T} \mu \} \phi (\bft^T \Sigma \bft)$ for $\bft \in \BR^p$.
+A $p$-dimensional random vector $X$ is said to elliptically distributed if there exist a vector $\mu \in \BR^p$, a positive semi-definite matrix $\Sigma \in \BR^{p \times p}$ and a function 
+$\phi: (0, \infty) \rightarrow \BR$ such that the characteristic function of $X$ is $\exp \{ i t^{T} \mu \} \phi (\bft^T \Sigma \bft)$ for $\bft \in \BR^p$.
 \end{Definition}
 
-There are several alternative formulations, see the above reference and 
-citations within it for details. 
-%The spherically symmetric case is realized with $\Sigma = \sigma^{2} \BI_{p}$ for some 
-%$\sigma^{2} > 0$. 
-We fix the notation $Z = \Sigma^{-1/2} (X - \mu)$, and let 
-$Z \sim \BF_{Z}$. Note that $\BF_{Z}$ is a spherically symmetric distribution and hence
-depends only on $|z|$, and  $\BE Z = \mathbf{0}_{p} \in \BR^{p}$ and $\BV Z = \BI_{p}$.
+There are several alternative formulations, see the above reference and citations within it for details.
 
-\begin{Corollary}
-\label{Cor:Elliptic_ARE}
-Assume that the tuning parameter of the weight function, $\BF$, is  the 
-distribution of $X$, and is an elliptically symmetric distribution, and $\mu = q_{0}$. 
-Also assume that the weight function is affine invariant, that is:
-\ban
-W (A x + b, A \BF + b) = W (x, \BF),
-\ean
-Then  the weight function satisfies $W (X, \BF) = W (Z, \BF_{Z})$, and 
-hence may be further restricted to be a function of $|Z|$. Then 
-$S (X; q_{0})$ is uniform on the unit ball 
-in $\BR^{p}$, and is independent of $|X - q_{0}|$, while 
-$W (X, \BF)$ is a function of  $|X - q_{0}|$. That is, the conditions of 
-Corollary~\ref{Cor:ARE} are satisfied. 
+\begin{Corollary}\label{Cor:Elliptic_ARE}
+Assume that $\BF \equiv \BF_X$ is an elliptically symmetric distribution, with location parameter $\mu = q_{0}$ and the covariance matrix $\Sigma$ satisfies the following conditions:
+%
+\begin{enumerate}
+%\item $Tr(\Sigma^4) = o( Tr^2 (\Sigma^2) )$,
+
+%\item $\frac{Tr^4(\Sigma)}{ Tr^2 (\Sigma^2)} \exp \left\{ - \frac{Tr^2 (\Sigma)}
+%{ 128 \lambda_{\max}^2 (\Sigma)} \right\} = o(1)$,
+
+\item $\exp \left\{ - \frac{Tr^2 (\Sigma)}{ 256 \lambda_{\max}^2 (\Sigma)} \right\} = 
+o\left( \min\left( \frac{\lambda_{\max}(\Sigma) }{Tr( \Sigma)},
+\frac{\lambda_{\min}(\Sigma)}{\lambda_{\max}(\Sigma)} \right) \right)$,
+
+\item $\lambda_{\max}(\Sigma) = o( Tr(\Sigma))$.
+\end{enumerate}
+
+Also assume that the weight function is (a) affine invariant, i.e. $ W (Ax + b, A\BF + b) = W (x, \BF)$ for $A \in \BR^{p \times p}, b \in \BR^p$, and (b) satisfies the following:
+%
+\begin{equation}\label{eqn:CorElliptic_ARE_eqn}
+\frac{W_{\max}}{[ \BE | X - q_0|^{-1} W(X, \BF)]^2 } <
+\frac{\lambda_{\min} (\Psi_1)}{\lambda_{\max} (\Psi_1) [ \BE | X - q_0|^{-1}]^2]}.
+\end{equation}
+%
+Then we have $ARE( \hat q_{n,W}, \hat q_n) > 1$.
 \end{Corollary}
 
-Obtaining affine invariant weight functions is not challenging, in fact, most 
-such functions arising in the context of data-depths are affine invariant. 
-Corollary~\ref{Cor:Elliptic_ARE} implies that there is a wide frame of distributions and 
-choices of weight functions where there is a benefit to considering weighted spatial 
-quantiles. In actual computations, in place of $W (x, \BF)$ we propose 
-using $W (x, \BF_{n})$ where 
-$\BF_{n} = n^{-1} \sum_{i = 1}^{n} \cI (X_{i} \leq x )$ is the empirical distribution 
-function. Up to first order asymptotics, the analysis remain unchanged from the above 
-for this modified weight function.
+The conditions 1 and 2 in Corollary~\ref{Cor:Elliptic_ARE} are due to \cite{ref:JASA151658_WangPengLi}, and ensure that as $p \equiv p_n$ diverges with $n$, the eigenvalues of $\Sigma \in \BR^{p \times p}$ are bounded away from 0 and $\infty$.
+Corollary~\ref{Cor:Elliptic_ARE} can be proved using Corollary~\ref{Cor:ARE}, the fact that for elliptical distributions $\Psi_1$ is non-singular \citep{ref:SPL12765_Taskinenetal}, then using and expanding upon Lemma A.5 in \cite{ref:JASA151658_WangPengLi}.
+We give the technical details in the supplementary material.
+
+Obtaining affine invariant weight functions is not challenging.
+Most functions arising in the context of data depths are affine invariant.
+Corollary~\ref{Cor:Elliptic_ARE} implies that there is a wide frame of distributions and  choices of weight functions where there is a benefit to considering weighted spatial medians.
+In fact, Corollary~\ref{Cor:Elliptic_ARE} can be established under just
+location invariance condition on weights. We use the stronger affine invariance condition
+here only because the subsequent sections use weights based on affine invariant 
+data depth functions.
+Also note that in case \eqref{eqn:CorElliptic_ARE_eqn} does not hold for the original form of a weight function, one can scale all weights by an appropriate constant to reduce the value in the left hand side of \eqref{eqn:CorElliptic_ARE_eqn} to satisfy the condition.
+
+In actual computations, in place of $W (x, \BF)$ we propose using $W (x, \BF_{n})$ where
+$ \BF_{n}(z) = n^{-1} \sum_{i = 1}^{n} \prod_{j=1}^{p}
+\cI (X_{ij} \leq z_j ), z \in \BR^p
+$ is the empirical distribution function. Up to first order asymptotics, the analysis remain unchanged from the above for this modified weight function.
 
@@
 algebraic and analytic properties assumed for data-depth functions to elicit interesting 
-mathematical properties, see for example 
-\cite{ref:AoS00461_ZuoSerfling, ref:DIMACS061_Serfling} 
-for details.
+mathematical properties, see for example \cite{ref:DIMACS061_Serfling, ref:AoS00461_ZuoSerfling} for details.
 
-It is easy to show that results in this paper are valid for the weight functions
-($i$) $W_{HSD} (X) = \BF_{Z} (| Z |)$ derived from the \textit{half-space depth},  
+The spherically symmetric case of an elliptical distribution is realized with $\Sigma = \sigma^{2} \BI_{p}$ for some $\sigma^{2} > 0$. We fix the notation $Z = \Sigma^{-1/2} (X - \mu)$, and let 
+$Z \sim \BF_{Z}$. Note that $\BF_{Z}$ is a spherically symmetric distribution and hence
+depends only on $|z|$, and $\BE Z = \mathbf{0}_{p} \in \BR^{p}$ and $\BV Z = \BI_{p}$.
+Taking affine invariant data depth functions as weights ensures that $W(X, \BF) = W(Z, \BF_Z)$.
+It is now easy to show that results in this paper are valid for the weight functions (with appropriate scaling to satisfy \eqref{eqn:CorElliptic_ARE_eqn})
+($i$) $W_{HSD} (X) = \BF_{Z_1} (| Z |)$ derived from the \textit{half-space depth},  
 ($ii$) $W_{MhD} (X) = |Z|^{2}/(1 + | Z |^2)$ derived from the \textit{Mahalanobis depth}, 
-and  
-($iii$) $W_{PD} (X) = |Z|/(1+ | Z |/MAD(\BF_{Z}))$, where $MAD$ stands for median 
+and ($iii$) $W_{PD} (X) = |Z|/(1+ | Z |/MAD(Z_1))$, where $MAD$ stands for median 
 absolute deviation, derived from the \textit{projection depth}. We omit the technical 
-details. These three weight functions a center-inward partial ordering, thus essentially 
+details. These three weight functions give a center-inward partial ordering, thus essentially 
 quantifying \textit{peripherality} instead of \textit{depth}.

### 2020-12-24 Codes/Sim_ARE2.R

@@ -1,0 +1,111 @@
+## Sim_efficiency: Asymptotic relative efficiency for depth-based scatter estimator
+set.seed(03092016)
+df.list = c(5,6,10,15,25,Inf)
+p.list = c(2,5,10,20)
+N = 1e6
+
+ARE.mat1 = matrix(0, nrow=length(p.list), ncol=length(df.list))
+for(i in 1:length(p.list)){
+    pi = p.list[i]
+    lambda = rev(1:pi)
+    sqrtLambda = sqrt(lambda)
+    # lamratio = outer(lambda,lambda,"*")/outer(lambda,lambda,"-")^2
+    # diag(lamratio) = 0
+    for(j in 1:length(df.list)){
+        dfj = df.list[j]
+        
+        # calculate MAD
+        if(dfj==Inf){
+            c = qnorm(.75)
+        } else{
+            c = 2*sqrt(dfj)/((dfj-1)*beta(dfj/2,1/2))
+        }
+        
+        # ARE for PD
+        Z = matrix(rt(N*pi, df=dfj), ncol=pi)
+        U = sweep(Z, 1, nZ, FUN="/")
+        nZ = sqrt(rowSums(Z^2))
+        W = nZ/(1+nZ/c)
+        X = Z %*% diag(sqrtLambda)
+        S = sweep(X, 1, sqrt(rowSums(X^2)), FUN="/")
+        WS = sweep(S, 1, W, FUN="*")
+        lamw = diag(cov(WS))
+        lamwdiff = outer(lamw, lamw, FUN = "-")
+        W2SS1 = sweep(WS, 1, WS[,1], FUN="*")
+        d.vec = colMeans(W2SS1^2)[-1]/lamwdiff[-1,1]^2
+        lam = diag(cov(S))
+        lamdiff = outer(lam, lam, FUN = "-")
+        SS1 = sweep(S, 1, S[,1], FUN="*")
+        n.vec = colMeans(SS1^2)[-1]/lamdiff[-1,1]^2
+        ARE.mat1[i,j] = sum(n.vec) / sum(d.vec)
+    }
+}
+
[…]
